\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{booktabs,longtable,array,tabularx}
\usepackage[shortlabels]{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{microtype}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\setlength{\emergencystretch}{3em}
\renewcommand{\arraystretch}{1.12}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\numberwithin{equation}{section}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\OPH}{\mathrm{OPH}}
\newcommand{\chinu}{\chi_\nu}
\newcommand{\chican}{\chi_\nu^{\mathrm{can}}}
\newcommand{\chieng}{\chi_\nu^{\mathrm{eng}}}
\newcommand{\scoh}{S_{\mathrm{coh}}}
\newcommand{\scohcan}{S_{\mathrm{coh}}^{\mathrm{can}}}
\newcommand{\scoheng}{S_{\mathrm{coh}}^{\mathrm{eng}}}
\newcommand{\Ncoh}{N_{\mathrm{coh}}}
\newcommand{\nueff}{\nu_{\mathrm{eff}}}
\newcommand{\nuoph}{\nu_{\mathrm{OPH}}}
\newcommand{\gbar}{\mathbf g_b}
\newcommand{\A}{\mathcal A}
\newcommand{\I}{\mathcal I}
\newcommand{\Ralg}{\mathcal R}
\newcommand{\U}{\mathcal U}
\newcommand{\Zrec}{\mathcal Z^{\mathrm{rec}}}
\newcommand{\RecCap}{\operatorname{Cap}}
\newcommand{\Law}{\operatorname{Law}}
\newcommand{\TV}{\mathrm{TV}}
\newcommand{\dd}{\,\mathrm d}
\newcommand{\eps}{\varepsilon}
\newcommand{\rhoa}{\rho_A}
\newcommand{\Cgeom}{C_g}
\newcommand{\Gammaeff}{\Gamma_{\mathrm{eff}}}
\newcommand{\lambdac}{\lambda_{\mathrm{collar}}}
\newcommand{\Zsix}{\mathbb Z_6}

\title{\textbf{Theoretical Bounds on \(\chinu\) in Observer-Patch Holography}\\
\large Coherent-Matter Susceptibility and the Construction Window}
\author{Bernhard Mueller, Alex Osika, and David Matscheko}
\date{Draft of May 24, 2026}
\input{../paper/release_info}

\begin{document}
\maketitle
\begin{center}
\small\textbf{Paper release:} \OPHPaperReleaseID\quad
\textbf{Released:} \OPHPaperReleaseDate
\end{center}

\begin{abstract}
The OPH coherent-matter scalar branch contains a susceptibility coefficient. On
the uniform product-thickening branch with slice-wise scalar-reserve
unbiasedness, the canonical value is
\(\chi_\nu=e^{-P/24}=0.9343006394893864\ldots\), with \(P\) the public endpoint
scalar. In the engineering chart used here, the same invariant coefficient
appears as a very small vertical response.

The estimate turns the branch into a laboratory target. For a \(100\,\mathrm{kg\,m^{-2}}\) platform, full weight response asks for coherence contrast near \(10^{-8}\). Ten percent assist asks for contrast near \(10^{-9}\). The substrate question is open: a controlled experiment must show whether real materials can produce that scalar contrast.
\end{abstract}

\section*{What This Paper Contributes}

This note takes one dark-sector scalar coefficient and turns it into an
experimental target. The OPH core supplies the observer carrier, record
algebras, quotient observables, and canonical collar scalar channel. The added
branch supplies a finite source-generator test for whether coherent matter can
source that same channel in a controlled material system.

The result is useful because it separates the invariant coefficient from the
engineering chart. The canonical susceptibility is order one on the exact
uniform branch, while the laboratory response can look tiny after stored
coherent energy and effective capacity are folded into the scalar. The paper
therefore gives a narrow construction window: what contrast a platform must
produce, what a null result would mean, and which part is a continuation
instead of a recovered-core OPH claim.

\tableofcontents

\section{Introduction}

Four layers are separated throughout the note.  The recovered OPH core supplies
the fixed-cutoff observer carrier, record algebras, quotient-local observables,
the Einstein branch, and the canonical scalar source surface.  Tier A alone
leaves \(\chinu\) unassigned.

Coherent-matter same-channel forcing supplies the finite source theorem.  A
nondegenerate OPH-coherent material subfederation has a canonical scalar source
\[
S_{\mathrm{coh}}^{\mathrm{can}}
=\mathbf 1_{\rm self-read}\,\mathsf R_U\,\mathsf P_U\,\mathsf C_U ,
\]
and Scalar Edge-Center Exhaustion forces that source into the same edge-center
scalar register priced by the \(Z_6\) collar theorem.  The zero branch is the
branch where at least one coherent-material receipt vanishes.

The protected-reserve collar theorem fixes the canonical coefficient on the
closed collar branch.  Granting the dark-sector collar lemmas on that shared
register, the canonical susceptibility is the collar survival coefficient:
\[
\chican=\lambdac.
\]

Engineering calculations often use a different chart. They fold stored coherent
energy into the scalar. That makes the coefficient look tiny, although the
canonical coefficient is order one.

The canonical number is the OPH-invariant number. It uses the per-channel
observer-facing scalar after the effective patch capacity has been divided out.
On the exact uniform product-thickening branch,
\[
\chican=e^{-P/24}=0.9343006394893864\ldots .
\]
With finite-thickness averaging and the protected reserve mean \(P/24\), the
theorem-level band is
\[
\boxed{
0.9343006394893864
\le
\chican
\le
1.
}
\]
The interval is narrow enough for engineering purposes. The exact branch is at
the lower end of this interval.

The engineering chart number is
\[
\scoheng=\Ncoh\scohcan,
\qquad
\Ncoh=\eps_{\mathrm{sub}}\frac{u_{\mathrm{stored}}}{u_0}.
\]
The coefficient in that chart is smaller by the same factor:
\[
\boxed{
\chieng=\frac{\chican}{\Ncoh}.
}
\]
This gives the engineering band
\[
\boxed{
\frac{0.9343006394893864}{\Ncoh}
\le
\chieng
\le
\frac{1}{\Ncoh}.
}
\]

The translation is simple:
\[
\begin{array}{c|c}
\Ncoh & \chieng\ \mathrm{range}\\
\hline
10^{20} & 9.34\times10^{-21}\text{ to }1.00\times10^{-20}\\
10^{21} & 9.34\times10^{-22}\text{ to }1.00\times10^{-21}\\
10^{22} & 9.34\times10^{-23}\text{ to }1.00\times10^{-22}\\
10^{23} & 9.34\times10^{-24}\text{ to }1.00\times10^{-23}\\
10^{24} & 9.34\times10^{-25}\text{ to }1.00\times10^{-24}
\end{array}
\]

The engineering consequence is direct. The coefficient is large enough in the
canonical chart. The hard part is the scalar: build a substrate with enough
vertical canonical coherence contrast, keep ordinary ambient matter from
creating the same scalar accidentally, and measure the force with clean
controls. Values around \(10^{-22}\) mean \(\Ncoh\sim10^{22}\), while the
canonical coefficient stays order one.

\section{What the Bound Says for Devices}

The branch theorem gives the canonical coefficient:
\[
0.9343006394893864
\le
\chican
\le
1.
\]
On the exact uniform product-thickening branch it is the single number
\[
\chican=0.9343006394893864\ldots .
\]
The susceptibility bound belongs to the closed quotient-edge collar branch. It
is an order-one coefficient. Zero is excluded for nondegenerate
coherent-material sources on that branch.

A room-scale lift or weight-reduction device needs only tiny \(\Delta\nu\). For
areal load \(\Sigma=M/A_\perp\) and target weight fraction \(f\), the required
response is
\[
\Delta\nu_{\mathrm{req}}
=
f\,\frac{4\pi G\Sigma}{g}
=
8.5525\times10^{-9}\,f\,\Sigma_2,
\qquad
\Sigma_2=\frac{\Sigma}{10^2\,\mathrm{kg\,m^{-2}}}.
\]
The forced \(\chican\) band converts this into the required canonical coherence
contrast:
\[
\boxed{
8.55\times10^{-9}\,f\,\Sigma_2
\le
\Delta S_{\mathrm{coh,req}}^{\mathrm{can}}
\le
9.15\times10^{-9}\,f\,\Sigma_2.
}
\]
For devices, the number to build is the coherence contrast. A
\(100\,\mathrm{kg\,m^{-2}}\) room-scale platform requires a vertical canonical
coherence contrast of roughly \(8.6\times10^{-9}\) to \(9.2\times10^{-9}\) for
full weight compensation. Ten percent compensation requires roughly
\(8.6\times10^{-10}\) to \(9.2\times10^{-10}\).

\begin{table}[h]
\centering
\small
\begin{tabularx}{\textwidth}{@{}L{0.23\textwidth}R{0.15\textwidth}R{0.08\textwidth}R{0.18\textwidth}X@{}}
\toprule
Device-scale case &
\(\Sigma\,[\mathrm{kg\,m^{-2}}]\) &
\(f\) &
\(\Delta\nu_{\mathrm{req}}\) &
\(\Delta S_{\mathrm{coh,req}}^{\mathrm{can}}\) \\
\midrule
light room platform & \(50\) & \(1\) & \(4.28\times10^{-9}\) & \(4.28\times10^{-9}\) to \(4.58\times10^{-9}\) \\
room-scale platform & \(100\) & \(1\) & \(8.55\times10^{-9}\) & \(8.55\times10^{-9}\) to \(9.15\times10^{-9}\) \\
heavy room platform & \(250\) & \(1\) & \(2.14\times10^{-8}\) & \(2.14\times10^{-8}\) to \(2.29\times10^{-8}\) \\
ten percent assist & \(100\) & \(0.1\) & \(8.55\times10^{-10}\) & \(8.55\times10^{-10}\) to \(9.15\times10^{-10}\) \\
\bottomrule
\end{tabularx}
\caption{Room-scale response requirements implied by the branch-theorem canonical band. The table is independent of the engineering chart normalization.}
\label{tab:room-scale-canonical}
\end{table}

For a hoverboard-class footprint the areal load is usually higher. A rider plus
board spread over \(0.5\,\mathrm{m^2}\) gives
\(\Sigma\simeq200\) to \(300\,\mathrm{kg\,m^{-2}}\). Full response then asks for
\[
\Delta S_{\mathrm{coh,req}}^{\mathrm{can}}
\simeq
1.7\times10^{-8}\text{ to }2.7\times10^{-8}.
\]
A compact footprint near \(600\,\mathrm{kg\,m^{-2}}\) asks for about
\[
5.1\times10^{-8}\text{ to }5.5\times10^{-8}.
\]
Ten percent assist divides these numbers by ten. The coefficient is in the
useful range for hoverboard-class experiments. A practical hoverboard
depends on whether a real substrate can produce and hold that vertical scalar
contrast under load.

The engineering coefficient is a chart value:
\[
\chieng=\frac{\chican}{\Ncoh}.
\]
The small engineering numbers are useful only together with the large
engineering scalar. The response depends on the product
\[
\chieng\,\Delta S_{\mathrm{coh}}^{\mathrm{eng}}
=
\chican\,\Delta S_{\mathrm{coh}}^{\mathrm{can}}.
\]
For \(\Ncoh=10^{22}\), the forced engineering band is
\[
9.34\times10^{-23}
\le
\chieng
\le
1.00\times10^{-22}.
\]
A \(100\,\mathrm{kg\,m^{-2}}\) full-response platform then needs
\[
\Delta S_{\mathrm{coh,req}}^{\mathrm{eng}}\simeq
8.6\times10^{13}\text{ to }9.2\times10^{13}.
\]
It equals \(10^{22}\) times the canonical contrast in
Table~\ref{tab:room-scale-canonical}. The large scalar and small coefficient
are the same normalization written in different coordinates.

On the closed collar branch, the coefficient is in the useful mathematical range for
macroscopic weight-reduction devices. No room-temperature material claim follows
from this bound alone. The engineering task is specific: generate a stable vertical
\(\Delta S_{\mathrm{coh}}^{\mathrm{can}}\) near \(10^{-9}\) for assist and near
\(10^{-8}\) to \(10^{-7}\) for full hoverboard-class response, keep ambient
ordinary matter from creating the same scalar accidentally, and measure the
force with controls that separate the effect from acoustic, thermal,
electromagnetic, and mechanical couplings.

\section{Support Boundary}

The paper uses three support levels.

Tier A is the recovered OPH core: finite patch carriers, mismatch-lowering
repair, observer-accessible record algebras, quotient normal forms, checkpoint
continuation, controlled BW scaling, fixed-cap generalized-entropy
stationarity, and the Jacobson-type Einstein branch. These ingredients are
supplied by the consensus, microphysics, synthesis, and compact SM/GR
papers~\cite{oph-consensus,oph-micro,oph-synthesis,oph-compact}. This tier leaves
\(\chinu\) unfixed.

Tier B0 is the finite coherent-matter source theorem. It defines a self-reading
material subfederation, its quotient-visible scalar-source readout, and a finite
edge-center source generator. Under Scalar Edge-Center Exhaustion, every
nondegenerate source \(S_{\mathrm{coh}}^{\mathrm{can}}\) is forced into the same
quotient-edge scalar register used by the dark-sector collar channel. Tier B0
derives the channel identity; it does not assign the reserve survival
coefficient.

Tier B1 is the coherent-matter response law
\begin{equation}
\delta\nu
=
\chican\scohcan
=
\chieng\scoheng.
\label{eq:chinu-law}
\end{equation}
This tier states linear weak-field response and the two charts without assigning
a value for \(\chinu\).

Tier C is the conditional quotient-edge collar branch. It adds the dark-sector
collar lemmas stated in Section~\ref{sec:canonical-quotient-edge}. On this
branch, coherent scalar opportunities are co-registered with the canonical
dark-sector scalar repair channel, and \(\chican\) is forced to equal
\(\lambdac\).

The dark-sector paper supplies the settled weak-field anomaly law
\begin{equation}
\rhoa
=
-\frac{1}{4\pi G}
\nabla\cdot[(\nuoph-1)\gbar],
\label{eq:canonical-dark}
\end{equation}
interpreting the anomaly as a transported modular/collar information-defect
remainder, with no additional particle species postulated~\cite{oph-dark}.

Here \(\scohcan\) is the per-channel observer-facing scalar. It enters the
dark-sector scalar channel only through the finite source lift in
Section~\ref{sec:finite-coherent-source-generator}. The scalar \(\scoheng\) is
the stored-energy engineering scalar. The small values useful in device
estimates are the engineering chart values \(\chieng=\chican/\Ncoh\).

\section{Canonical Chain}

\subsection{Fixed-cutoff carrier}

At fixed cutoff, an observer-facing OPH implementation surface is a federated
patch carrier
\begin{equation}
\mathfrak F
=
\bigl(V,E,\{\A_i\}_{i\in V},\{\I_e\}_{e\in E},
\{\pi_{i,e}\},\{\Ralg_i\},\{\U_i\}\bigr).
\end{equation}
Here \(\A_i\) are local finite algebras, \(\I_e\) are overlap interfaces,
\(\pi_{i,e}\) are visible restriction maps, \(\Ralg_i\subseteq Z(\A_i)\) are
record algebras, and \(\U_i\) are local update and repair interfaces. Physical
claims are made through visible restrictions, record algebras, and quotient-local
observables, without choosing hidden microscopic representatives~\cite{oph-micro}.

\subsection{Mismatch and repair}

The consensus paper gives a nonnegative visible mismatch functional \(\Phi\).
Accepted repairs lower the relevant mismatch on finite state spaces. Under the
declared local-diamond and repair-completeness hypotheses, the terminal
observer-facing normal form from a fixed initial physical quotient state is unique and independent
of asynchronous update schedule~\cite{oph-consensus}.

\subsection{Records and checkpoints}

For an observer-supporting subfederation \(U\), the microphysics paper uses a
checkpoint of the form
\begin{equation}
\mathrm{Chk}_U(t)=
\bigl(
\Ralg_U(t),
\rho_U^{\mathrm{acc}}(t),
\mathfrak I_U^{\mathrm{ext}}(t),
\nu_{\ge t},
\mathfrak B_U(t)
\bigr).
\end{equation}
If two checkpoints agree on the accessible record algebra, accessible state,
external interface, boundary-update schedule class, and provenance bundle, they
induce the same continuation law on the observer-accessible event algebra. Approximate
agreement gives a controlled total-variation bound~\cite{oph-micro}.

\subsection{Gravity and dark response}

The compact SM/GR paper keeps the recovered core and downstream continuations
separate. On the stated controlled scaling branch, the OPH stack gives a
Jacobson-type Einstein relation; dark-sector response laws are phenomenological
continuations outside that recovered-core tier~\cite{oph-compact}.
The dark paper then models the anomaly by Eq.~\eqref{eq:canonical-dark}.

On Earth, \(g_b/a_0\sim 10^{11}\), so the canonical \(\nuoph\) term is pinned
near unity. A terrestrial tabletop anomaly attributed only to the canonical OPH
dark sector should read null. The \(\chinu\) continuation is tested against
that null baseline as a separate effect.

\section{The Coherence Scalar}

\begin{definition}[Patch coherence factors and channel count]
Let \(U\) be an observer-supporting patch subfederation at cycle \(t\), with
observer-accessible record algebra \(\Zrec_U(t)\). Let \(Y_U(t)\) be the induced
record outcome variable, \(X_{\partial U,t+1:t+h}\) the boundary packet
over horizon \(h\), and \(\Phi_U(t)\) the visible mismatch on the relevant
support. Define
\begin{align}
R_U(t;h)
&=
\left[
1-
d_{\TV}\!\left(
\Law(Y_U(t+h)),\Law(Y_U(t))
\right)
\right]e^{-\delta_{\mathrm{rec}}(t)},
\label{eq:R-factor}\\
P_U(t;h)
&=
\frac{
I\!\left(Y_U(t);X_{\partial U,t+1:t+h}\right)
}{
H\!\left(X_{\partial U,t+1:t+h}\right)+\epsilon
},
\label{eq:P-factor}\\
C_U(t)
&=
\left[
1-\frac{\Phi_U(t)}{\Phi_U^{\max}+\epsilon}
\right]_+.
\label{eq:C-factor}
\end{align}
On the screen or hardware branch, set the finite coherent channel count to
\begin{equation}
N_U(t):=\RecCap(\Zrec_U(t)).
\label{eq:channel-count}
\end{equation}
The exponent-free observer core is
\begin{equation}
\mathfrak c_U(t;h)=
\mathbf 1_{\mathrm{self\mbox{-}read}}\,
R_U(t;h)\,
P_U(t;h)\,
C_U(t).
\label{eq:canonical-core}
\end{equation}
\end{definition}

\begin{definition}[Canonical and engineering coherence scalars]
The capacity-weighted observer scalar is
\begin{equation}
\mathbb C_U(t;h)=N_U(t)\,\mathfrak c_U(t;h).
\label{eq:canonical-mass}
\end{equation}
The canonical per-channel scalar is
\begin{equation}
\boxed{
\scohcan(U,t;h)=\frac{\mathbb C_U(t;h)}{N_U(t)}
=
\mathfrak c_U(t;h).
}
\label{eq:Scoh-can-patch}
\end{equation}
Under coherent-matter same-channel forcing and Scalar Edge-Center Exhaustion,
Section~\ref{sec:finite-coherent-source-generator} routes
\(\scohcan\in[0,1]\) into the edge-center scalar-slot register. Without that
source lift, \(\scohcan\) is only an operational observer receipt.
Let \(u_{\mathrm{stored}}(U,t)\) be the stored coherent matter energy density in
the substrate mode supported by \(U\), let \(u_0\) be a fixed reference energy
density, and let \(\eps_{\mathrm{sub}}(U)\in[0,1]\) be the substrate directness
factor. The engineering scalar is
\begin{equation}
\scoheng(U,t;h)
=
\eps_{\mathrm{sub}}(U)
\frac{u_{\mathrm{stored}}(U,t)}{u_0}
\scohcan(U,t;h)
=
\Ncoh(U,t)\scohcan(U,t;h),
\label{eq:Scoh-eng-patch}
\end{equation}
where
\begin{equation}
\boxed{
\Ncoh(U,t)=
\eps_{\mathrm{sub}}(U)\frac{u_{\mathrm{stored}}(U,t)}{u_0}.
}
\label{eq:Ncoh}
\end{equation}
Given a partition of unity \(w_U(x)\) over observer-supporting subfederations,
define the coarse-grained field
\begin{equation}
\scohcan(x,t)=\sum_U w_U(x)\scohcan(U,t;h),
\qquad
\scoheng(x,t)=\sum_U w_U(x)\scoheng(U,t;h),
\qquad
\sum_U w_U(x)=1.
\label{eq:Scoh-field}
\end{equation}
\end{definition}

With the source lift and linear weak-field response, the response law can be
written in either chart:
\begin{equation}
\boxed{
\nueff(x,t)
=
\nuoph(x,t)+\chican\scohcan(x,t)
=
\nuoph(x,t)+\chieng\scoheng(x,t).
}
\label{eq:continuation-axiom}
\end{equation}
On a region with representative \(\Ncoh\),
\begin{equation}
\boxed{
\chieng=\frac{\chican}{\Ncoh}.
}
\label{eq:chart-map}
\end{equation}

\section{Structural Properties}

\begin{proposition}[Observer-facing quotient well-definedness]
Assume two microscopic representatives induce the same observer-accessible
continuation law on \(U\), preserve the same visible mismatch score, and expose the
same stored coherent energy density and substrate class. Then they give the same
\(\scohcan(U,t;h)\) and \(\scoheng(U,t;h)\).
\end{proposition}

\begin{proof}
The factors \(R_U\), \(P_U\), and \(C_U\) are defined from observer-accessible
records, boundary-law variables, and visible mismatch data. The channel count
\(N_U\) cancels in the per-channel scalar. These are precisely the quantities
that survive the observer-facing quotient. Multiplying by \(u_{\mathrm{stored}}\)
and \(\eps_{\mathrm{sub}}\), which are declared observable substrate data for
the engineering chart, preserves hidden-representative independence.
\end{proof}

\begin{proposition}[Null conditions]\label{prop:chi-null-conditions}
If \(U\) has no self-read, no stable record algebra, or no predictive boundary
coupling at horizon \(h\), then \(\scohcan(U,t;h)=0\) and
\(\scoheng(U,t;h)=0\).
\end{proposition}

\begin{proof}
If there is no self-read, then
\(\mathbf 1_{\mathrm{self\mbox{-}read}}=0\). If no stable record algebra is
available, then the stability factor \(R_U\) vanishes on the declared readout.
If predictive boundary coupling is absent, then \(P_U=0\). In each case
\(\mathfrak c_U=0\), hence both scalars vanish.
\end{proof}

\begin{proposition}[Exact normalization map]
For the canonical and engineering scalars in Eqs.~\eqref{eq:Scoh-can-patch}
and \eqref{eq:Scoh-eng-patch},
\begin{equation}
\boxed{
\frac{\scoheng(U,t;h)}{\scohcan(U,t;h)}
=
\Ncoh(U,t)
=
\eps_{\mathrm{sub}}(U)\frac{u_{\mathrm{stored}}(U,t)}{u_0}.
}
\label{eq:normalization-map}
\end{equation}
\end{proposition}

\begin{proof}
Substitute Eq.~\eqref{eq:Scoh-can-patch} into
Eq.~\eqref{eq:Scoh-eng-patch}. The quotient is exactly
\(\eps_{\mathrm{sub}}u_{\mathrm{stored}}/u_0\).
\end{proof}

\begin{proposition}[Saturated-limit reduction]
If
\[
\mathbf 1_{\mathrm{self\mbox{-}read}}\simeq1,\quad
R_U\simeq1,\quad
P_U\simeq1,\quad
C_U\simeq1,
\]
then
\[
\scohcan(U,t;h)\simeq1,
\qquad
\scoheng(U,t;h)\simeq
\eps_{\mathrm{sub}}(U)\frac{u_{\mathrm{stored}}(U,t)}{u_0}.
\]
\end{proposition}

\begin{proof}
Substitute the saturated factor values into Eqs.~\eqref{eq:Scoh-can-patch}
and \eqref{eq:Scoh-eng-patch}.
\end{proof}

\section{Finite Coherent-Matter Source Generator}
\label{sec:finite-coherent-source-generator}

The channel identity is supplied by importing the finite scalar-slot register,
Scalar Edge-Center Exhaustion, and the coherent-matter same-channel theorem from
the microphysics paper~\cite{oph-micro}. The empirical question is separate:
whether any real substrate can emit a nonzero, signed, controlled \(\scohcan\)
receipt at useful magnitude.

At fixed regulator \(r\), collar or support \(C\), and physical quotient
\(Q_r=\Sigma_r/\Gamma_r\), write the imported edge-center scalar-slot register as
\[
E_{\nu,r}(C),\qquad
p_{e,\nu}:Q_r\to\{0,1\},\qquad
\mathcal N_{\nu,r,C}(q)
=
\sum_{e\in E_{\nu,r}(C)}a_e\,p_{e,\nu}(q).
\]
Scalar-slot completeness says that, on the quotient-edge scalar branch,
the first-order scalar subspace is
\[
\mathcal S^{(1)}_{\mathrm{sc}}(C)
=
\operatorname{span}\{\mathcal N_{\nu,r,C}\}
\]
after constants are removed. Thus a quotient-local, central, edge-center scalar
perturbation has no second scalar channel available on that branch.

\begin{definition}[B.3. Self-reading coherent material subfederation]
\label{def:self-reading-coherent-material-subfederation}
Let \(U\subset\mathfrak F_r\) be an observer-supporting material subfederation
with accessible record algebra \(\mathcal Z^{\mathrm{rec}}_U(t)\), record
outcome \(Y_U(t)\), future boundary packet \(X_{\partial U,t+1:t+h}\), and
visible mismatch \(\Phi_U(t)\). Its canonical coherent scalar is
\[
S_U(q;t,h)
:=
\scohcan(U,t;h)
=
\mathbf 1_{\mathrm{self\mbox{-}read}}\,
R_U(t;h)P_U(t;h)C_U(t).
\]
The operational observer-side requirement is the screen-microphysics observer
test: bounded accessible interface, durable re-readable records, self-read or
internal state estimation, record-conditioned future behavior, boundary
prediction better than shuffled controls, and checkpoint continuation within
declared error.
\end{definition}

\begin{definition}[B.4. Scalar-slot footprint]
\label{def:scalar-slot-footprint}
The material subfederation \(U\) induces a quotient-visible footprint
\[
b_{U,r,C}:E_{\nu,r}(C)\times Q_r\to\mathbb R_{\ge0}
\]
with
\[
\sum_{e\in E_{\nu,r}(C)}b_{U,r,C}(e;q)=1
\]
on the active support of \(U\), and \(b_{U,r,C}(e;q)=0\) outside the scalar
slots exposed by the visible boundary of \(U\). Define the local material slot
count and availability factor
\[
\mathcal N_{\nu,U}(q)
=
\sum_{e\in E_{\nu,r}(C)}
b_{U,r,C}(e;q)a_e\,p_{e,\nu}(q),
\qquad
\mathcal O_U(q)
=
\sum_{e\in E_{\nu,r}(C)}
b_{U,r,C}(e;q)p_{e,\nu}(q),
\]
and
\[
A_{U,r,C}(q)
=
\sum_{e\in E_{\nu,r}(C)}
b_{U,r,C}(e;q)a_e\,[1-p_{e,\nu}(q)].
\]
The source is non-saturated at \(q\) when \(A_{U,r,C}(q)>0\).
\end{definition}

The footprint is not a new field. It is a quotient-visible map from the material
boundary to the scalar slots it can touch. If the material has no self-read, no
stable record algebra, or no predictive boundary coupling,
Proposition~\ref{prop:chi-null-conditions} forces \(\scohcan=0\).

\begin{definition}[B.5. Unit-normalized coherent scalar source generator]
\label{def:coherent-source-generator}
For \(q\in Q_r\) and \(e\in E_{\nu,r}(C)\), define
\[
q\oplus e
:=
n_r(q\ \text{with scalar slot }e\text{ activated}),
\]
where \(n_r\) is the quotient normal-form map. If the slot is active in \(q\),
set \(q\oplus e=q\). For any test function \(f:Q_r\to\mathbb R\), define
\[
(\mathcal L^{\mathrm{coh}}_{U,r,C}f)(q)
=
S_U(q;t,h)
\sum_{e\in E_{\nu,r}(C)}
b_{U,r,C}(e;q)
\bigl[f(q\oplus e)-f(q)\bigr].
\]
This is the unit-normalized canonical generator. Engineering inefficiencies,
stored-energy amplification, substrate directness, and geometry factors belong
to the engineering chart, not to the canonical channel identity.
\end{definition}

\begin{lemma}[B.6. Quotient descent]\label{lem:coherent-source-quotient-descent}
\(\mathcal L^{\mathrm{coh}}_{U,r,C}\) is a well-defined finite generator on the
physical quotient \(Q_r\).
\end{lemma}

\begin{proof}
\(S_U\) is built from the self-read gate, record stability, predictive boundary
coupling, and visible mismatch data. The footprint \(b_{U,r,C}\) is
quotient-visible by definition. The update \(q\oplus e\) is normal-formed by
\(n_r\). Therefore replacing a microscopic representative of \(q\) by a
gauge-equivalent representative changes none of \(S_U\), \(b_{U,r,C}\),
\(q\oplus e\), or the value of the generator. Since \(Q_r\) and
\(E_{\nu,r}(C)\) are finite, the generator is finite.
\end{proof}

\begin{theorem}[B.7. Coherent material perturbs the canonical scalar count]
\label{thm:coherent-material-perturbs-canonical-count}
Assume the finite scalar-slot register, scalar-slot completeness, a coherent
material footprint, and the source generator above. If \(S_U(q;t,h)>0\) and
\(A_{U,r,C}(q)>0\), then the coherent material subfederation \(U\) perturbs the
same quotient-edge scalar opportunity count \(\mathcal N_{\nu,r,C}\) that
appears in the dark-sector collar channel:
\[
(\mathcal L^{\mathrm{coh}}_{U,r,C}\mathcal N_{\nu,r,C})(q)
=
S_U(q;t,h)A_{U,r,C}(q)
>
0.
\]
By scalar-slot completeness, the scalar projection of the
coherent-matter perturbation lies in
\[
\operatorname{span}\{\mathcal N_{\nu,r,C}\},
\]
so it cannot define an independent scalar channel.
\end{theorem}

\begin{proof}
Evaluate the generator on \(\mathcal N_{\nu,r,C}\):
\[
(\mathcal L^{\mathrm{coh}}_{U,r,C}\mathcal N_{\nu,r,C})(q)
=
S_U(q;t,h)
\sum_e b_{U,r,C}(e;q)
\left[
\mathcal N_{\nu,r,C}(q\oplus e)
-
\mathcal N_{\nu,r,C}(q)
\right].
\]
By definition of \(q\oplus e\), activating an inactive slot \(e\) increases
\(\mathcal N_{\nu,r,C}\) by \(a_e\). A slot active in \(q\) contributes zero:
\[
\mathcal N_{\nu,r,C}(q\oplus e)-\mathcal N_{\nu,r,C}(q)
=
a_e[1-p_{e,\nu}(q)].
\]
Substitution gives
\[
(\mathcal L^{\mathrm{coh}}_{U,r,C}\mathcal N_{\nu,r,C})(q)
=
S_U(q;t,h)
\sum_e b_{U,r,C}(e;q)a_e[1-p_{e,\nu}(q)]
=
S_U(q;t,h)A_{U,r,C}(q).
\]
The positivity follows from the two nonzero hypotheses. The generator changes
only the central edge-center scalar-slot indicators \(p_{e,\nu}\). By
scalar-slot completeness, the first-order scalar projection is generated by
\(\mathcal N_{\nu,r,C}\), with constants removed. Hence the material
perturbation acts in the canonical quotient-edge scalar channel itself.
\end{proof}

\begin{definition}[B.8. Oriented coherent scalar contrast]
\label{def:oriented-coherent-scalar-contrast}
For a two-zone device or material body, let \(U_+\) and \(U_-\) be the two
observer-supporting subfederations separated by the declared vertical
orientation. In the lab force convention used below, \(U_+\) is the bottom zone
and \(U_-\) is the top zone. Define
\[
\Delta\scohcan
=
\scohcan(U_+,t;h)-\scohcan(U_-,t;h).
\]
The signed source generator is
\[
\mathcal L^{\mathrm{coh}}_{\Delta}
=
\mathcal L^{\mathrm{coh}}_{U_+}
-
\mathcal L^{\mathrm{coh}}_{U_-},
\]
with scalar projection
\[
\mathcal L^{\mathrm{coh}}_{\Delta}\mathcal N_{\nu}
=
S_{U_+}A_{U_+}-S_{U_-}A_{U_-}.
\]
On a symmetric footprint branch where \(A_{U_+}=A_{U_-}=1\), this reduces to
\[
\mathcal L^{\mathrm{coh}}_{\Delta}\mathcal N_{\nu}
=
\Delta\scohcan.
\]
\end{definition}

\begin{definition}[B.9. Coherent scalar source action]
\label{def:coherent-scalar-source-action}
Let \(\mu_{0,r}\) be the unperturbed quotient law on \(Q_r\), with action
\(I_{0,r}\). Define
\[
I_{\eta,r,U}(q)
=
I_{0,r}(q)
-
\eta\,S_U(q;t,h)\mathcal N_{\nu,U}(q).
\]
The source-perturbed finite quotient law is
\[
\mu_{\eta,r,U}(q)
=
Z_{\eta}^{-1}\exp[-I_{\eta,r,U}(q)].
\]
\end{definition}

\begin{proposition}[B.10. Linear response through the canonical scalar count]
\label{prop:coherent-source-linear-response}
For any bounded quotient observable \(F:Q_r\to\mathbb R\),
\[
\left.
\frac{\dd}{\dd\eta}
\mathbb E_{\eta}[F]
\right|_{\eta=0}
=
\operatorname{Cov}_{0}
\left(
F,\,
S_U\mathcal N_{\nu,U}
\right).
\]
In particular,
\[
\left.
\frac{\dd}{\dd\eta}
\mathbb E_{\eta}[\mathcal N_{\nu,r,C}]
\right|_{\eta=0}
=
\operatorname{Cov}_{0}
\left(
\mathcal N_{\nu,r,C},\,
S_U\mathcal N_{\nu,U}
\right).
\]
On the nondegenerate scalar branch this covariance is nonzero whenever
\(S_U\) is nonzero, the footprint is nonzero, and
\(\mathcal N_{\nu,U}\) is not \(\mu_0\)-almost surely constant.
\end{proposition}

\begin{proof}
Differentiate the finite partition function
\[
\mathbb E_{\eta}[F]
=
\frac{\sum_q F(q)e^{-I_{0,r}(q)+\eta S_U(q;t,h)\mathcal N_{\nu,U}(q)}}
{\sum_q e^{-I_{0,r}(q)+\eta S_U(q;t,h)\mathcal N_{\nu,U}(q)}}.
\]
At \(\eta=0\), the numerator derivative gives
\(\mathbb E_0[F\,S_U\mathcal N_{\nu,U}]\), and the partition-function
derivative subtracts
\(\mathbb E_0[F]\mathbb E_0[S_U\mathcal N_{\nu,U}]\). This is the displayed
covariance. Since \(\mathcal N_{\nu,U}\) is built from the same
\(p_{e,\nu}\) slots, scalar-slot completeness again puts the scalar response in
the \(\mathcal N_{\nu,r,C}\) channel.
\end{proof}

\begin{corollary}[B.11. Tier-B response law from the finite generator]
\label{cor:tier-b-response-from-generator}
On the finite quotient-edge branch above, coherent matter changes the canonical
scalar opportunity count by a term proportional to \(\scohcan\). Linear
weak-field response therefore has the Tier-B1 form
\[
\delta\nu=\chican\scohcan.
\]
If the Tier-C co-registered collar survival assumptions are also granted, then
\[
\chican=\lambdac,
\qquad
\nueff=\nuoph+\lambdac\scohcan.
\]
In the stored-energy engineering chart,
\[
\scoheng=\Ncoh\scohcan,
\qquad
\chieng=\frac{\chican}{\Ncoh},
\qquad
\nueff=\nuoph+\chieng\scoheng.
\]
\end{corollary}

\begin{proof}
Theorem~\ref{thm:coherent-material-perturbs-canonical-count} proves that the
material source perturbs the same quotient-edge scalar count used by the
dark-sector collar channel. Linear weak-field response makes the induced
perturbation of \(\nu\) proportional to that count in canonical normalization.
The Tier-C collar theorem identifies the proportionality coefficient with the
collar survival coefficient. The engineering formulas are the chart change
\(\scoheng=\Ncoh\scohcan\).
\end{proof}

\begin{proposition}[Finite channel bridge: slots and slices are one family]
\label{prop:finite-channel-bridge}
Let \(E\) be one finite indexed family equipped with both a record panel
\[
(p_e(q),a_e,q\mapsto q\oplus e)_{e\in E}
\]
and a collar panel
\[
(w_e,\epsilon_e)_{e\in E},
\qquad
w_e\ge0,\quad \sum_{e\in E}w_e=1,\quad \epsilon_e\ge0.
\]
The record panel defines the scalar-slot register of
Definition~\ref{def:scalar-slot-footprint} and the coherent generator of
Definition~\ref{def:coherent-source-generator}.  The collar panel defines the
finite-slice survival coefficient
\[
\lambda_{\mathrm{collar}}=\sum_{e\in E}w_e\,e^{-\epsilon_e}.
\]
Because both panels use the same index family \(E\), the statement that
coherent matter perturbs the same counter priced by the collar is not an
extra equality between two unrelated constructions.  It is a single-channel
structure.
\end{proposition}

\begin{corollary}[Composite Tier-B1 channel law]\label{cor:composite-tier-b1-channel}
Under the hypotheses of
Theorem~\ref{thm:coherent-material-perturbs-canonical-count}, and under the
uniform product-thickening clause \(\epsilon_e=P/24\) for every \(e\in E\),
the record-source increment and the collar survival factor compose as
\[
\lambda_{\mathrm{collar}}\,
(\mathcal L^{\mathrm{coh}}_{U,r,C}\mathcal N_{\nu,r,C})(q)
=
e^{-P/24}\,S_U(q;t,h)\,A_{U,r,C}(q).
\]
\end{corollary}

\begin{proof}
Theorem~\ref{thm:coherent-material-perturbs-canonical-count} gives
\[
(\mathcal L^{\mathrm{coh}}_{U,r,C}\mathcal N_{\nu,r,C})(q)
=S_U(q;t,h)\,A_{U,r,C}(q).
\]
The finite collar gate gives \(\lambda_{\mathrm{collar}}=e^{-P/24}\) under
slice-wise reserve unbiasedness.  Multiplying the two identities gives the
displayed composite law.
\end{proof}

\begin{remark}[What the channel bridge does not close]
Proposition~\ref{prop:finite-channel-bridge} removes a bookkeeping ambiguity:
the record slots and collar slices can be represented as one finite channel.
Two physical residues remain.  First, an actual material system must supply
receipts showing that its record channel and collar channel instantiate this
one structure rather than two unrelated counters.  Second, the numerical
record-\(\Delta S\) to gravity-\(\Delta S\) calibration, denoted G9 in the
audit ledger, remains an external calibration.  A null experiment therefore
bounds the product \(\chi_\nu\Delta S\), not \(\chi_\nu\) and \(\Delta S\)
separately.
\end{remark}

\begin{remark}[Generator realization is not a law selector]
The generator above is a realization after the quotient branch, scalar-slot
register, and source law have been selected. It is not a selector of a unique
physical probability law by itself. The probability-law statement is the finite
action formulation in Definition~\ref{def:coherent-scalar-source-action}.
\end{remark}

\subsection{Source-generator proof ledger}

\begin{center}
\begin{tabularx}{\textwidth}{@{}L{0.25\textwidth}X L{0.25\textwidth}@{}}
\toprule
Target & Closure & Status \\
\midrule
Coherent matter sources same scalar channel &
Finite source generator \(\mathcal L^{\mathrm{coh}}_{U,r,C}\) acts on
edge-center scalar slots; scalar-slot completeness makes the scalar projection
rank-one, generated by \(\mathcal N_{\nu,r,C}\). &
Theorem-level on the finite quotient-edge branch; empirical nonzero
\(\scohcan\) is a hardware receipt. \\
Finite channel bridge &
The record-side source generator and collar-side reserve coefficient are
represented by one finite indexed family of slots/slices, yielding the
composite law of Corollary~\ref{cor:composite-tier-b1-channel}. &
Bookkeeping theorem; nature-instantiation and G9 numerical calibration remain
physical obligations. \\
Switchable-force energy cage &
Any conservative ABBA cycle obeys
\(W_{\mathrm{ABBA}}=\operatorname{Toggle}(q_1)-\operatorname{Toggle}(q_2)\). &
Theorem-level accounting constraint; the local response law
Eq.~\eqref{eq:force-law} remains a branch law, not derived local dynamics. \\
\bottomrule
\end{tabularx}
\end{center}

\subsection{Deterministic source-generator receipts}

Implementation evidence for this branch should expose the following deterministic
receipt names.
\begin{description}[leftmargin=*,style=nextline]
\item[\texttt{SELF\_READ\_PATCH\_RECEIPT}]
Passes when \(U\) satisfies the operational observer test: bounded interface,
durable re-readable records, self-read or internal state estimation,
record-conditioned future behavior, boundary prediction better than shuffled
controls, and checkpoint continuation.
\item[\texttt{SCOH\_CANONICAL\_RECEIPT}]
Emits \(R_U(t;h)\), \(P_U(t;h)\), \(C_U(t)\),
\(\mathbf 1_{\mathrm{self\mbox{-}read}}\), \(N_U(t)\), and \(\scohcan\), with
record-algebra hash, boundary-packet hash, mismatch-functional hash, and
shuffled-record controls.
\item[\texttt{EDGE\_SOURCE\_LIFT\_RECEIPT}]
Emits the footprint \(b_{U,r,C}\), proves it factors through the quotient-edge
scalar register, and proves invariance under port relabeling, hidden carrier
coordinates, mesh labels, and accepted repair schedule changes.
\item[\texttt{FINITE\_CHANNEL\_BRIDGE\_RECEIPT}]
Emits the shared finite index family \(E\) and its two panels: record activity,
opportunity weights, and activation maps on the source side; slice weights and
protected-reserve means on the collar side. Fails if the source generator and
collar survival factor are computed over unrelated counters.
\item[\texttt{NO\_SEPARATE\_SCALAR\_CHANNEL\_RECEIPT}]
Fails if the coherent material source depends on bulk labels, screen-area
labels, noncentral collar variables, heat, rest mass, electrical power, or any
presentation variable not carried by the scalar-slot register.
\item[\texttt{SOURCE\_NONDEGENERACY\_RECEIPT}]
Checks
\[
\operatorname{Cov}_{0}
(\mathcal N_{\nu,r,C},S_U\mathcal N_{\nu,U})\ne0
\]
or reports the selected ensemble as source-degenerate.
\item[\texttt{VERTICAL\_CONTRAST\_RECEIPT}]
Emits the signed bottom-minus-top \(\Delta\scohcan\), plus sign-reversal runs,
sham runs, thermal/electromagnetic/mechanical controls, and record-shuffle
controls.
\item[\texttt{FINITE\_GENERATOR\_REALIZATION\_RECEIPT}]
Optional. Emits the slot update maps or repair projections implementing
\(\mathcal L^{\mathrm{coh}}_{U,r,C}\), while labeling the generator as a
realization of an externally selected source law.
\item[\texttt{DARK\_SECTOR\_SIMULATION\_PLAN\_RECEIPT}]
Optional integration receipt.  It records which dark-sector simulator gates are
present across the static galaxy, finite covariant parent, finite-collar
Boltzmann, Boltzmann-input, anomaly, and frozen-likelihood reports, and names
the next blocked command.  It is not a force receipt, not a susceptibility
measurement, and not a replacement for the source-lift receipts above.
\end{description}

\section{Canonical Quotient-Edge Susceptibility}
\label{sec:canonical-quotient-edge}

This section is conditional on the closed quotient-edge collar branch. The
recovered OPH core and the coherent-matter same-channel theorem supply the
observer-facing carrier, the coherent scalar source readout, and the scalar
channel. The nonzero coefficient follows after the collar lemmas below are
granted.

\begin{assumption}[Imported quotient-edge collar theorem stack]
\label{ass:dark-collar-lemmas}
The \(\chinu\) branch imports the following theorem-level source package from
the screen microphysics paper~\cite{oph-micro}:
\[
\begin{gathered}
\texttt{def:oph-coherent-material-subfederation},\quad
\texttt{def:canonical-coherent-matter-scalar-source},\\
\texttt{lem:coherent-material-source-quotient-descent},\quad
\texttt{thm:nonzero-coherent-scalar-source},\\
\texttt{thm:coherent-matter-same-channel-forcing},\quad
\texttt{thm:unique-scalar-linear-response}.
\end{gathered}
\]
These imports state that a nondegenerate OPH-coherent material subfederation has
\[
S_{\mathrm{coh}}^{\mathrm{can}}
=\mathbf 1_{\rm self-read}\,\mathsf R_U\,\mathsf P_U\,\mathsf C_U>0
\]
and that this source lies in the same edge-center scalar register as the
protected \(Z_6\) collar channel under Scalar Edge-Center Exhaustion.  The
collar coefficient uses the following branch-local inputs.

\begin{enumerate}[label=L\arabic*.,leftmargin=*]
\item Positive scalar source branch: the scalar repair defect is the minimal
recoverability defect
\[
R_C=I(A:D\mid B)\ge0.
\]

\item Quotient-edge scalar locality: every quotient-local scalar recoverability
event is resolved on the edge-center cut register. This is imported from the
microphysics theorem labeled \texttt{thm:scalar-activation-edge-center}, under
the branch assumption labeled
\texttt{ass:edge-center-scalar-completeness}~\cite{oph-micro}.

\item Co-registration with the protected reserve: scalar activation and the
protected \(\Zsix\) reserve live on the same edge-center resolution and
commute. This is imported from the microphysics theorem labeled
\texttt{thm:scalar-z6-same-register-commute}.

\item Scalar-channel exhaustion and no separate scalar carrier: the scalar
activation channel is exhausted by the scalar activation projector, and any
separate bulk, screen-area, noncentral, or hidden-carrier scalar channel either
changes quotient observables or is inert. This is imported from the
microphysics theorems labeled \texttt{thm:scalar-channel-exhaustion} and
\texttt{thm:no-separate-scalar-carrier}.

\item Local Poisson reserve survival: on a co-registered scalar slot at
transverse coordinate \(y\),
\[
\lambda_{\mathrm{slot}}(y)=\exp[-\epsilon_{\Zsix}(y)].
\]
This is a declared Poisson branch unless separately derived from a finite
MaxEnt/occupancy theorem.

\item Finite-thickness averaging with scalar-weighted reserve mean:
\[
\lambdac=
\int \dd y\,w(y)\exp[-\epsilon_{\Zsix}(y)],
\]
with
\[
\int \dd y\,w(y)\epsilon_{\Zsix}(y)=\frac{P}{24}.
\]
The profile definitions, mean-reserve disintegration, and survival formula are
imported from the microphysics definitions and theorems labeled
\texttt{def:finite-thickness-scalar-profile},
\texttt{thm:finite-thickness-mean-reserve}, and
\texttt{thm:finite-thickness-collar-survival}.

\item Exact uniform branch: on the uniform product-thickening branch, including
product algebra, product trace, reserve pullback, scalar activation
disintegration, and slice-wise scalar-reserve unbiasedness,
\[
\lambdac=e^{-P/24}.
\]
This is imported from the microphysics definition and theorem labeled
\texttt{def:uniform-product-thickening-branch} and
\texttt{thm:exact-uniform-product-thickening-coefficient}.
\end{enumerate}
\end{assumption}

The public OPH readout gives
\begin{equation}
P=1.630968209403959.
\end{equation}
The normalized quotient reserve mean is
\begin{equation}
\boxed{
\tau_q(Z_{6,r,C})=\frac{P}{24}=0.06795700872516496.
}
\label{eq:z6-reserve}
\end{equation}
The reciprocal reserve-depth trace is
\begin{equation}
\boxed{
\operatorname{Tr}^{\#}_q(Z_{6,r,C})=\frac{24}{P}
=14.715185655746689.
}
\end{equation}
Only the normalized mean \(P/24\) enters the Poisson exponent.

\begin{theorem}[Forced canonical susceptibility on the co-registered branch]
Assume L1 to L6 of Assumption~\ref{ass:dark-collar-lemmas}. Then the canonically
normalized coherent-matter susceptibility is the collar survival coefficient:
\begin{equation}
\boxed{
\chican=\lambdac.
}
\label{eq:chi-can-lambda}
\end{equation}
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:coherent-material-perturbs-canonical-count} and
Corollary~\ref{cor:tier-b-response-from-generator}, \(\scohcan\) enters the
same quotient-edge scalar opportunity count before the protected reserve acts.
By L3, the \(\Zsix\) reserve acts on that same register. By L5, each local
coherent scalar opportunity survives the reserve with factor
\(\exp[-\epsilon_{\Zsix}(y)]\). By L6, finite-thickness averaging gives the
surviving coherent scalar fraction
\[
S_{\mathrm{coh,after}}^{\mathrm{can}}
=
\lambdac S_{\mathrm{coh,before}}^{\mathrm{can}}.
\]
The continuation law writes the same surviving fraction as
\[
S_{\mathrm{coh,after}}^{\mathrm{can}}
=
\chican S_{\mathrm{coh,before}}^{\mathrm{can}}.
\]
For any nonzero canonical coherent fraction, the coefficients are equal.
\end{proof}

\begin{corollary}[Theorem-level nonzero band]
Under L1 to L6,
\begin{equation}
\boxed{
0.9343006394893864\ldots
\le
\chican
\le
1.
}
\label{eq:chi-can-band}
\end{equation}
\end{corollary}

\begin{proof}
The function \(e^{-x}\) is convex, so the Jensen inequality gives
\[
\chican=\int \dd y\,w(y)e^{-\epsilon_{\Zsix}(y)}
\ge
\exp\!\left[-\int \dd y\,w(y)\epsilon_{\Zsix}(y)\right]
=e^{-P/24}.
\]
Using Eq.~\eqref{eq:z6-reserve},
\[
e^{-P/24}=0.9343006394893864\ldots .
\]
Reserve survival factors are at most one, so \(\chican\le1\).
\end{proof}

\begin{corollary}[Exact canonical value on the uniform branch]
Assume L7 in addition to L1 to L6. Then
\begin{equation}
\boxed{
\chican
=
e^{-P/24}
=
0.9343006394893864\ldots .
}
\label{eq:chi-can-exact}
\end{equation}
\end{corollary}

\begin{proof}
By L7, \(\lambdac=e^{-P/24}\). Use
Eq.~\eqref{eq:chi-can-lambda}.
\end{proof}

\begin{remark}[Uniformity is stronger than product trace]
The exact value \(e^{-P/24}\) does not follow from the unconditioned trace
\(\tau_q(Z_6)=P/24\) alone. It requires the scalar-active edge-slot sampler to
be reserve-unbiased. Equivalently, for every scalar-active transverse slice,
\[
\frac{\tau(\Pi^{\rm scal}(y)Z_6)}
{\tau(\Pi^{\rm scal}(y))}
=
\frac{P}{24}.
\]
If scalar activation is correlated with the protected reserve inside the
edge-center algebra, then \(\epsilon_{\Zsix}(y)\) may vary and the exact
coefficient is not licensed. The valid coefficient is then the profile integral
\[
\lambdac
=
\int \dd y\,w(y)e^{-\epsilon_{\Zsix}(y)}.
\]
\end{remark}

\begin{remark}[Profile-envelope number]
The dark-sector correction note also lists profile targets: best same-function
RAR \(0.958802256\), binned RAR \(0.936737944\), and the OPH
\(\Zsix\)/Poisson value \(0.934300639\). If an extra numerical selector keeps
the coherent continuation inside that same-function profile envelope, one may
quote the practical profile range
\[
0.934300639\le\chican\le0.958802256.
\]
The range is selector-dependent. The theorem-level band used in the
rest of this paper is Eq.~\eqref{eq:chi-can-band}, with the exact value
Eq.~\eqref{eq:chi-can-exact} on L7.
\end{remark}

\begin{corollary}[Engineering chart band]
On any engineering chart with representative normalization \(\Ncoh\),
\begin{equation}
\boxed{
\frac{0.9343006394893864}{\Ncoh}
\le
\chieng
\le
\frac{1}{\Ncoh}.
}
\label{eq:chi-eng-band}
\end{equation}
On the exact uniform branch,
\begin{equation}
\boxed{
\chieng=\frac{e^{-P/24}}{\Ncoh}.
}
\label{eq:chi-eng-exact}
\end{equation}
\end{corollary}

\begin{table}[h]
\centering
\begin{tabular}{@{}R{0.24\textwidth}R{0.31\textwidth}R{0.31\textwidth}@{}}
\toprule
\(\Ncoh\) &
theorem-level \(\chieng\) band &
exact-branch \(\chieng\) \\
\midrule
\(10^{20}\) & \(9.34\times10^{-21}\text{ to }1.00\times10^{-20}\) & \(9.34\times10^{-21}\) \\
\(10^{21}\) & \(9.34\times10^{-22}\text{ to }1.00\times10^{-21}\) & \(9.34\times10^{-22}\) \\
\(10^{22}\) & \(9.34\times10^{-23}\text{ to }1.00\times10^{-22}\) & \(9.34\times10^{-23}\) \\
\(10^{23}\) & \(9.34\times10^{-24}\text{ to }1.00\times10^{-23}\) & \(9.34\times10^{-24}\) \\
\(10^{24}\) & \(9.34\times10^{-25}\text{ to }1.00\times10^{-24}\) & \(9.34\times10^{-25}\) \\
\bottomrule
\end{tabular}
\caption{Translation from the theorem-level canonical band to the engineering chart. Here \(\Ncoh=\eps_{\mathrm{sub}}u_{\mathrm{stored}}/u_0\).}
\label{tab:engineering-band}
\end{table}

\section{Weak-Field Response}

Insert Eq.~\eqref{eq:continuation-axiom} into the settled weak-field density:
\begin{equation}
\rhoa^{\mathrm{eff}}
=
-\frac{1}{4\pi G}
\nabla\cdot
\Bigl[
\bigl(\nuoph-1+\chieng\scoheng\bigr)\gbar
\Bigr].
\label{eq:rho-eff}
\end{equation}
In a small terrestrial laboratory region with \(\gbar\simeq -g\,\hat z\) and
canonical \(\nuoph-1\) negligible, this becomes
\begin{equation}
\rhoa^{\mathrm{lab}}
\simeq
-\frac{1}{4\pi G}
\nabla\cdot
\bigl[\chieng\scoheng\,\mathbf g\bigr].
\label{eq:rho-lab}
\end{equation}
Equation~\eqref{eq:rho-lab} uses \(\scoh\) only after the coherent material
source-generator theorem has routed \(\scoh\) into the quotient-edge scalar
opportunity count. Heat, rest mass, and ordinary stored energy do not enter
unless they pass the self-read, record, prediction, and quotient-edge footprint
receipts.

\begin{theorem}[Planar response law]
Let a thin device have horizontal projected area \(A_\perp\), and define the
bottom-to-top coherence contrast
\[
\Delta\scoheng={\scoheng}_{\mathrm{bottom}}-{\scoheng}_{\mathrm{top}}.
\]
Then, to leading order in the thin-device approximation, the apparent vertical
force generated by the engineering-chart continuation is
\begin{equation}
\boxed{
F_\chi
=
\frac{g^2}{4\pi G}A_\perp\,\chieng\,\Delta\scoheng .
}
\label{eq:force-law}
\end{equation}
\end{theorem}

\begin{proof}
With \(\mathbf g=-g\hat z\), Eq.~\eqref{eq:rho-lab} gives
\[
\rhoa^{\mathrm{lab}}
=
\frac{g\chieng}{4\pi G}\frac{\partial\scoheng}{\partial z}
\]
up to the sign convention for \(z\). Integrating through a thin column gives
\[
M_A=
\int\rhoa^{\mathrm{lab}}\dd V
=
-\frac{g\chieng}{4\pi G}A_\perp\,\Delta\scoheng
\]
when \(\Delta\scoheng\) is bottom minus top. The apparent weight change is
\(F_\chi=-gM_A\), yielding Eq.~\eqref{eq:force-law}.
\end{proof}

\begin{corollary}[Geometric ceiling]
If \(|\Delta\nu|\lesssim 1\), then
\begin{equation}
\frac{|F_\chi|}{A_\perp}
\lesssim
\Cgeom
\equiv
\frac{g^2}{4\pi G}
=
1.1466\times10^{11}\,\mathrm{N\,m^{-2}}
\label{eq:geometric-ceiling}
\end{equation}
for \(g=9.80665\,\mathrm{m\,s^{-2}}\) and
\(G=6.67430\times10^{-11}\,\mathrm{m^3\,kg^{-1}\,s^{-2}}\).
\end{corollary}

The ceiling is algebraic. Material reachability of \(|\Delta\nu|=1\) is a
separate claim.

\section{Engineering Susceptibility Window}

For bounds it is useful to package the contrast geometry, substrate directness,
and OPH coherence factors into one dimensionless number:
\begin{equation}
\Delta\scoheng
=
\Gammaeff\frac{u}{u_0},
\qquad
0\le \Gammaeff\le 1.
\label{eq:Gamma-definition}
\end{equation}
Here \(u\) is the representative stored coherent energy density in the active
mode. The factor \(\Gammaeff\) includes vertical contrast, substrate directness,
and effective canonical observer coherence.

\begin{theorem}[Nonempty macroscopic linear-response window]
Let \(\Sigma=M/A_\perp\) be the areal load, let \(f\in[0,1]\) be the target
fraction of the ordinary weight \(Mg\), and let \(\epsilon_{\mathrm{lin}}\le 1\)
be the maximum allowed \(|\Delta\nu|\) in the chosen linear-response regime.
Assume \(\Gammaeff>0\). If
\begin{equation}
f\,\frac{4\pi G\Sigma}{g}
<
\epsilon_{\mathrm{lin}},
\label{eq:window-condition}
\end{equation}
then the interval
\begin{equation}
\boxed{
\frac{4\pi G\Sigma f}{g}\,
\frac{u_0}{\Gammaeff u}
\le
|\chieng|
\le
\epsilon_{\mathrm{lin}}
\frac{u_0}{\Gammaeff u}
}
\label{eq:chi-eng-window}
\end{equation}
is nonempty. Values in this interval produce at least fraction \(f\) of the
ordinary weight inside the declared linear-response bound. Conversely, any
value that produces at least fraction \(f\) while staying inside that
linear-response bound lies in this interval.
\end{theorem}

\begin{proof}
The force law gives
\[
\frac{|F_\chi|}{Mg}
=
\frac{g}{4\pi G\Sigma}|\chieng|\Delta\scoheng.
\]
Requiring \(|F_\chi|/(Mg)\ge f\) gives the lower bound in
Eq.~\eqref{eq:chi-eng-window}. Requiring
\(|\Delta\nu|=|\chieng|\Delta\scoheng\le\epsilon_{\mathrm{lin}}\) gives the upper
bound. The interval is nonempty exactly when the lower bound is smaller than the
upper bound, which is Eq.~\eqref{eq:window-condition}.
\end{proof}

\begin{corollary}[Numerical width in normalized areal load]
Let
\[
\Sigma_2=\frac{\Sigma}{10^2\,\mathrm{kg\,m^{-2}}}.
\]
Then
\[
\frac{4\pi G\Sigma}{g}=8.5525\times10^{-9}\,\Sigma_2.
\]
The full-response \((f=1)\), order-unity linear window has width
\[
\frac{\chi_{\mathrm{upper}}}{\chi_{\mathrm{lower}}}
=
1.1692\times10^8\,\Sigma_2^{-1},
\]
independent of \(u\) and \(\Gammaeff\). With
\(\epsilon_{\mathrm{lin}}=0.1\), the window width is
\(1.1692\times10^7\,\Sigma_2^{-1}\).
\end{corollary}

\begin{table}[h]
\centering
\begin{tabular}{@{}R{0.19\textwidth}R{0.23\textwidth}R{0.25\textwidth}R{0.20\textwidth}@{}}
\toprule
\(u\,[\mathrm{J\,m^{-3}}]\) &
\(u/u_0\) &
\(|\chieng|_{\mathrm{req}}\) for \(f\Sigma_2/\Gammaeff=1\) &
\(|\chieng|_{\mathrm{lin}}\) for \(\epsilon_{\mathrm{lin}}/\Gammaeff=1\) \\
\midrule
\(1.0\times10^5\) & \(1.18\times10^{14}\) & \(7.27\times10^{-23}\) & \(8.5\times10^{-15}\) \\
\(5.5\times10^5\) & \(6.47\times10^{14}\) & \(1.32\times10^{-23}\) & \(1.55\times10^{-15}\) \\
\(1.0\times10^6\) & \(1.18\times10^{15}\) & \(7.27\times10^{-24}\) & \(8.5\times10^{-16}\) \\
\(4.0\times10^6\) & \(4.71\times10^{15}\) & \(1.82\times10^{-24}\) & \(2.13\times10^{-16}\) \\
\(1.0\times10^7\) & \(1.18\times10^{16}\) & \(7.27\times10^{-25}\) & \(8.5\times10^{-17}\) \\
\bottomrule
\end{tabular}
\caption{Full-response susceptibility bounds for \(u_0=8.5\times10^{-10}\,\mathrm{J\,m^{-3}}\) and \(\Sigma_2=\Sigma/(10^2\,\mathrm{kg\,m^{-2}})\). The third column should be multiplied by \(f\Sigma_2/\Gammaeff\). The fourth column should be multiplied by \(\epsilon_{\mathrm{lin}}/\Gammaeff\).}
\label{tab:window}
\end{table}

The table gives the bound in numerical form. It says that
ordinary material stress and coherent phonon energy densities put the
macroscopic response threshold in the \(\chieng\sim10^{-22}\) to \(10^{-24}\)
range for macroscopic areal loads and \(\Gammaeff\) near unity. Smaller
\(\Gammaeff\) shifts the required value upward by \(1/\Gammaeff\).

\section{Power and Stored-Energy Bounds}

\subsection{Conservation-law cage for switchable force claims}
\label{subsec:conservation-law-cage}

The force law fixes stored energy. Input power depends on how the coherent state
is maintained.  A stronger bookkeeping constraint applies to any switchable
force claim.  Let \(q\) denote a device position and \(s\in\{\mathrm{off},
\mathrm{on}\}\) its internal state.  In any conservative sector with state
energy \(E(q,s)\), define the toggle ledger
\[
\operatorname{Toggle}(q):=E(q,\mathrm{on})-E(q,\mathrm{off})
\]
and the work extracted by the ABBA cycle
\[
(\mathrm{on\ at}\ q_1)\to(q_2,\mathrm{on})\to
(\mathrm{off\ at}\ q_2)\to(q_1,\mathrm{off}).
\]
Then
\[
W_{\mathrm{ABBA}}
=
\operatorname{Toggle}(q_1)-\operatorname{Toggle}(q_2).
\]
Thus a claimed position-dependent switchable force with no toggle-energy
ledger is a perpetual-motion claim: if the toggle cost is zero everywhere, the
cycle work is zero.  If the cycle extracts \(W>0\), some position pair must
carry a toggle-ledger difference of at least \(W\), and at least one endpoint
must carry a ledger entry of order \(W/2\) or larger relative to the pair.

This is the G10 conservation-law cage.  It prices any positive
\(\chi_\nu\) detection, but it does not derive the response law
Eq.~\eqref{eq:force-law}.  A detection must therefore arrive with both the
ordinary force controls and a toggle/maintenance energy ledger large enough to
account for the measured cycle work.

\subsection{Driven coherent oscillations}

For a driven oscillator with angular frequency \(\omega\), mode volume
\(V_{\mathrm{mode}}\), quality factor \(Q\), and stored density \(u\),
\begin{equation}
P_{\mathrm{loss}}
=
\frac{uV_{\mathrm{mode}}\omega}{Q}.
\label{eq:loss-power}
\end{equation}
Combining Eq.~\eqref{eq:loss-power} with the required density from the
macroscopic response law gives
\begin{equation}
\boxed{
P_{\mathrm{loss}}
=
\frac{4\pi G\Sigma f\,u_0\,V_{\mathrm{mode}}\omega}
{g\,Q\,\Gammaeff\,|\chieng|}.
}
\label{eq:power-bound}
\end{equation}

For \(\Sigma_2=1\),
\(V_{\mathrm{mode}}=10^{-3}\,\mathrm{m^3}\),
\(\omega=2\pi(4.0\times10^4)\,\mathrm{s^{-1}}\),
\(Q=10^5\), \(f=1\), and \(\Gammaeff=1\), this gives:
\[
\begin{array}{c|c}
|\chieng| & P_{\mathrm{loss}}\\
\hline
10^{-20} & 1.8\,\mathrm{W}\\
10^{-21} & 18\,\mathrm{W}\\
10^{-22} & 183\,\mathrm{W}\\
10^{-23} & 1.8\,\mathrm{kW}\\
10^{-24} & 18\,\mathrm{kW}
\end{array}
\]
The scaling is \(P_{\mathrm{loss}}\propto(Q\Gammaeff|\chieng|)^{-1}\).

\subsection{Static elastic storage}

For a static elastic-strain coherent variable, the stored density is
\begin{equation}
u_{\mathrm{elastic}}=\frac{\sigma^2}{2E},
\label{eq:elastic-density}
\end{equation}
where \(\sigma\) is stress and \(E\) is the Young modulus. In that interpretation
there is no oscillator decay factor \(\omega/Q\). Maintaining the state is then
limited by creep, relaxation, and mechanical failure. Its loss law differs from
Eq.~\eqref{eq:loss-power}. The same susceptibility bounds apply, because they
depend only on \(u\), \(\Gammaeff\), and \(\Sigma\).

\section{Construction-Scale Consequences}

The bounds are algebraic. Substrate reachability of \(\Gammaeff\simeq1\) and
safe maintenance of a high-energy coherent state are separate engineering
claims. The bounds specify the requirements for a macroscopic force device if
the continuation is real.

A force device, in this narrow sense, is a bounded substrate whose active region
creates a vertical engineering-coherence contrast \(\Delta\scoheng\). The apparent weight
fraction is
\begin{equation}
\frac{|F_\chi|}{Mg}
=
\frac{g}{4\pi G\Sigma}\,
|\chieng|\,\Gammaeff\frac{u}{u_0}.
\label{eq:force-fraction}
\end{equation}
All construction choices enter through the product
\begin{equation}
|\chieng|\,\Gammaeff\,u.
\label{eq:construction-product}
\end{equation}
The product makes \(\chieng\) the governing chart number. Geometry fixes the coefficient
\(g/(4\pi G\Sigma)\). Better materials can raise \(u\). Better mode design can
raise \(\Gammaeff\). A smaller \(\chieng\) must be paid for linearly by higher
stored energy density, larger active volume, better quality factor, or a smaller
target response fraction. If \(\chieng=0\), no amount of construction produces the
continuation force.

For the normalized areal load \(\Sigma_2=1\), the full-response condition is
\begin{equation}
\Delta\nu_{\mathrm{full}}(\Sigma_2=1)
=
\frac{4\pi G\Sigma}{g}
=
8.5525\times10^{-9}.
\label{eq:full-response-dnu}
\end{equation}
The value is far below even a conservative \(\epsilon_{\mathrm{lin}}=0.1\) linear
bound. The required \(\Delta\nu\) lies inside the theorem window. Construction
depends on the required \(\Gammaeff u\) product, mode volume, quality factor,
and material stress.

\begin{table}[p]
\centering
\small
\begin{tabularx}{\textwidth}{@{}R{0.12\textwidth}R{0.16\textwidth}R{0.16\textwidth}L{0.19\textwidth}X@{}}
\toprule
\(|\chieng|\) &
\(u_{\mathrm{req}}\) at \(f\Sigma_2/\Gammaeff=1\) &
\(P_{\mathrm{loss}}\) at \(f\Sigma_2/\Gammaeff=1,Q=10^5\) &
Construction class &
Interpretation \\
\midrule
\(10^{-20}\) &
\(7.3\times10^2\,\mathrm{J\,m^{-3}}\) &
\(1.8\,\mathrm{W}\) &
small bench article &
The force is easy to produce if the coherence scalar is real. Existing ambient-coherence nulls become the primary consistency check. \\
\(10^{-21}\) &
\(7.3\times10^3\,\mathrm{J\,m^{-3}}\) &
\(18\,\mathrm{W}\) &
tabletop module &
Accessible to modest driven resonators or static strain specimens. A direct balance or pendulum experiment should see it cleanly. \\
\(10^{-22}\) &
\(7.3\times10^4\,\mathrm{J\,m^{-3}}\) &
\(183\,\mathrm{W}\) &
high-Q insert / compact platform &
The first useful construction band. Full response is compatible with ordinary high-Q crystal or metal inserts. Thermal management matters. \\
\(10^{-23}\) &
\(7.3\times10^5\,\mathrm{J\,m^{-3}}\) &
\(1.8\,\mathrm{kW}\) &
engineered crystal or metal module &
Inside high-strength material energy densities. Continuous driven operation becomes hard. Static elastic storage becomes much more attractive. \\
\(10^{-24}\) &
\(7.3\times10^6\,\mathrm{J\,m^{-3}}\) &
\(18\,\mathrm{kW}\) &
industrial multi-module system &
Near the upper end of practical stored-density claims. Driven operation needs large area, high \(Q\), cryogenic or exceptional materials, or partial-lift use. \\
\(10^{-25}\) &
\(7.3\times10^7\,\mathrm{J\,m^{-3}}\) &
\(183\,\mathrm{kW}\) &
large array / static-only candidate &
Inside the response window. Compact driven construction is implausible. Static prestress, very high \(\Gammaeff\), or large arrays are the plausible routes. \\
\(10^{-26}\) &
\(7.3\times10^8\,\mathrm{J\,m^{-3}}\) &
\(1.8\,\mathrm{MW}\) &
outside compact construction &
The response inequalities are satisfied. Material and power requirements exceed the intended compact-device scale. For compact devices, this row is effectively a null. \\
\bottomrule
\end{tabularx}
\caption{Construction regimes inside the response-window theorem for \(\Sigma_2=1\), \(f=1\), \(u_0=8.5\times10^{-10}\,\mathrm{J\,m^{-3}}\), \(V_{\mathrm{mode}}=10^{-3}\,\mathrm{m^3}\), \(\omega=2\pi(4.0\times10^4)\,\mathrm{s^{-1}}\), and \(Q=10^5\). Every row has \(\Delta\nu=8.5525\times10^{-9}\), so construction difficulty changes while algebraic admissibility is the same. Multiply the listed material and power requirements by \(f\Sigma_2/\Gammaeff\).}
\label{tab:construction-regimes}
\end{table}

Two consequences follow.

First, a measurement of \(\chieng\) selects a construction class. If
\(|\chieng|\gtrsim10^{-22}\) and \(\Gammaeff\) is reasonably large, compact
demonstrators are in the ordinary resonator and high-strength-substrate regime.
If \(|\chieng|\sim10^{-23}\) to \(10^{-24}\), the design must move toward high-Q
crystals, larger active area, static strain, or partial lift. If
\(|\chieng|\lesssim10^{-25}\), compact force-device construction stops being the
right first target. The useful output is a bound on the continuation.

Second, the static-versus-driven distinction is decisive. The driven column pays
\(uV_{\mathrm{mode}}\omega/Q\). Static elastic storage pays no oscillator
maintenance cost. It must survive creep and fracture. The same
\(\chieng\) value can be impractical for a driven phonon design and practical for
a static strain design. The static-stress experiment decides which maintenance
law applies to the construction table.

\section{Experimental Bound Formula}

Let an experiment have force sensitivity \(F_{\min}\), projected area
\(A_\perp\), and known engineering-coherence contrast \(\Delta\scoheng\). A null result gives
\begin{equation}
\boxed{
|\chieng|
\le
\frac{4\pi G F_{\min}}{g^2 A_\perp|\Delta\scoheng|}.
}
\label{eq:null-bound-general}
\end{equation}
If the mode is a driven oscillator, with
\(\Delta\scoheng=\Gammaeff QP_{\mathrm{in}}/(u_0\omega V_{\mathrm{mode}})\), then
\begin{equation}
\boxed{
|\chieng|
\le
\frac{4\pi G F_{\min}u_0\omega V_{\mathrm{mode}}}
{g^2 A_\perp\Gammaeff QP_{\mathrm{in}}}.
}
\label{eq:null-bound-driven}
\end{equation}
If the mode is static elastic storage, replace the driven density by
\(u_{\mathrm{elastic}}\) from Eq.~\eqref{eq:elastic-density}.

\section{Compatibility with Existing Nulls}

\begin{proposition}[No ordinary-matter anomaly from null coherence]
If ordinary non-engineered configurations have \(\mathfrak c_U=0\) on the
observer-facing scalar of Eq.~\eqref{eq:canonical-core}, then they impose no direct
bound on \(\chieng\), because \(\delta\nu=\chieng\scoheng=0\) for those
configurations.
\end{proposition}

\begin{proof}
Equation~\eqref{eq:Scoh-eng-patch} gives the statement immediately. The response
law couples only to the OPH-native coherent scalar. Undifferentiated rest mass
or heat is outside this ansatz.
\end{proof}

If ordinary matter has a small nonzero ambient scalar
\({\scoheng}_{\mathrm{amb}}\), then existing gravitational null tests bound the
product:
\begin{equation}
|\chieng|\,{\scoheng}_{\mathrm{amb}}
\le
\delta\nu_{\mathrm{test}}.
\label{eq:ambient-bound}
\end{equation}
The condition is real. It becomes a theorem-grade number when the ambient scalar
is specified. The scalar branch is falsifiable in two ways: by direct \(\chieng\)
searches through Eq.~\eqref{eq:null-bound-general} and by ordinary-gravity null
tests once a model for \({\scoheng}_{\mathrm{amb}}\) is fixed.

\section{Source-Lift Falsifiers}

The finite source-generator branch fails if any of the following tests is
confirmed under the declared receipt discipline:
\begin{enumerate}[leftmargin=2em]
\item a record-shuffled dummy with the same stored energy gives the same force
signal as the active coherent material branch;
\item the inferred source changes under port relabeling, hidden carrier
re-presentation, mesh relabeling, or accepted repair-schedule changes;
\item the source requires a bulk, screen-area, noncentral collar, heat, rest
mass, or electrical-power scalar not carried by the edge-center scalar-slot
register;
\item \(\scohcan=0\) on the self-read, record, prediction, and mismatch receipts
while the force is nonzero;
\item the sign of the force fails to follow the signed bottom-minus-top
\(\Delta\scohcan\) contrast after orientation reversal and sham controls.
\end{enumerate}

The dark-sector simulation planner can audit downstream galaxy, parent,
Boltzmann, anomaly, and likelihood gates, but it cannot close any item in this
source-lift falsifier list.  In particular, a passed planner receipt does not
establish \texttt{EDGE\_SOURCE\_LIFT\_RECEIPT},
\texttt{SOURCE\_NONDEGENERACY\_RECEIPT}, or
\texttt{VERTICAL\_CONTRAST\_RECEIPT}.

\section{How to Read the Two Bands}

The canonical band in Eq.~\eqref{eq:chi-can-band} is the quotient-edge
continuation statement. It is dimensionless and independent of material energy
density. It belongs to the branch where coherent scalar sourcing is
co-registered with the dark-sector scalar repair channel. On the exact
uniform product-thickening branch, the value is the single number
\(0.9343006394893864\ldots\).

The engineering band in Eq.~\eqref{eq:chi-eng-band} is the same statement in a
stored-energy chart. It depends on the declared normalization
\(\Ncoh=\eps_{\mathrm{sub}}u_{\mathrm{stored}}/u_0\). Large coherent stored
energy densities make \(\chieng\) numerically small because the scalar itself
has been scaled up.

The response window in Eq.~\eqref{eq:chi-eng-window} is an operating condition
for a chosen device geometry and linear-response allowance. A design with
fixed \(\Sigma\), \(f\), \(u\), and \(\Gammaeff\) is compatible with the OPH
continuation coefficient when the forced engineering band intersects that
operating window.
If the forced band sits above the chosen linear ceiling, the design is outside
that linear chart. If it sits below the target threshold, the target response is
too large for that design.

\section{Chart Choices}

The canonical scalar uses the exponent-free observer core
\(\mathbf 1_{\mathrm{self\mbox{-}read}}R_UP_UC_U\). Optional empirical
exponents or refinement factors are calibrated-chart data. They are outside
the canonical quotient-edge coefficient.

The coarse-grained partition weights \(w_U(x)\) should be induced by a declared
observer-supporting subcover. Only the contrast entering the force law is used
in the response bounds.

The exact value \(e^{-P/24}\) uses the uniform product-thickening branch,
including slice-wise scalar-reserve unbiasedness. The wider numerical interval
in Eq.~\eqref{eq:chi-can-band} uses finite-thickness averaging and the
scalar-weighted protected reserve mean. The profile-envelope range in the
remark after the exact-value corollary needs an extra numerical selector.

\section{Conclusion}

This note separates channel identity, coefficient value, chart conversion, and
device evidence.  Coherent-matter same-channel forcing gives a theorem-grade
scalar-channel identity for nondegenerate OPH-coherent material sources under
Scalar Edge-Center Exhaustion.  The canonical quotient-edge chart and the
engineering stored-energy chart are
\[
\nueff
=
\nuoph+\chican\scohcan
=
\nuoph+\chieng\scoheng.
\]
On the quotient-edge co-registered collar branch, the protected-reserve lemmas
force the canonical coefficient to equal the collar survival coefficient:
\[
\chican=\lambdac.
\]
L1 to L6 give the theorem-grade band
\[
0.9343006394893864\ldots
\le
\chican
\le
1.
\]
L7 gives the exact value
\[
\chican=e^{-P/24}=0.9343006394893864\ldots .
\]
This excludes \(\chican=0\) for nondegenerate coherent-material sources on the
closed quotient-edge collar branch.

In the engineering chart,
\[
\chieng=\frac{\chican}{\Ncoh},
\qquad
\Ncoh=\eps_{\mathrm{sub}}\frac{u_{\mathrm{stored}}}{u_0}.
\]
This gives
\[
\frac{0.9343006394893864}{\Ncoh}
\le
\chieng
\le
\frac{1}{\Ncoh}.
\]
Engineering values near \(10^{-22}\) correspond to
\(\Ncoh\sim10^{22}\). The response-window inequalities then decide which
device geometries and material states stay inside the chosen linear-response
chart.

For \(\Sigma=100\,\mathrm{kg\,m^{-2}}\), full weight response requires
\[
\Delta S_{\mathrm{coh,req}}^{\mathrm{can}}
\simeq
8.6\times10^{-9}\text{ to }9.2\times10^{-9},
\]
and ten percent assist requires about \(8.6\times10^{-10}\) to
\(9.2\times10^{-10}\). A hoverboard-class areal load around
\(200\) to \(600\,\mathrm{kg\,m^{-2}}\) moves the full-response target to about
\(2\times10^{-8}\) to \(6\times10^{-8}\). The coefficient is compatible with
those room-scale response levels on the closed branch. A device claim requires
a substrate that produces the required signed vertical canonical contrast, plus
force controls that separate acoustic, thermal, electromagnetic, and mechanical
couplings. A cosmological use requires a finite covariant dark-stress parent
with refinement convergence and likelihood-facing stress observables.

\begin{thebibliography}{99}

\bibitem{oph-synthesis}
B.\ M\"uller, A.\ Osika, M.\ Poneder, K.\ Xue, B.\ Cassie, P.\ Nguyen, M.\ A.\ Visser, K.\ A.\ Anirudha, D.\ Matscheko, and J.\ Hill,
\emph{Observers Are All You Need}.
\href{https://github.com/FloatingPragma/observer-patch-holography/releases/download/\OPHPaperReleaseID/observers_are_all_you_need.pdf}{release PDF}.

\bibitem{oph-compact}
B.\ M\"uller, A.\ Osika, M.\ Poneder, K.\ Xue, P.\ Nguyen, and M.\ A.\ Visser,
\emph{Recovering Relativity and the Standard Model from Observer Overlap Consistency}.
\href{https://github.com/FloatingPragma/observer-patch-holography/releases/download/\OPHPaperReleaseID/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.pdf}{release PDF}.

\bibitem{oph-consensus}
B.\ M\"uller, K.\ Xue, K.\ A.\ Anirudha, and J.\ Hill,
\emph{Reality as a Consensus Protocol: The Fixed-Point Computation That Implements Physics}.
\href{https://github.com/FloatingPragma/observer-patch-holography/releases/download/\OPHPaperReleaseID/reality_as_consensus_protocol.pdf}{release PDF}.

\bibitem{oph-micro}
B.\ M\"uller, A.\ Osika, K.\ Xue, B.\ Cassie, and M.\ A.\ Visser,
\emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer Synchronization in OPH}.
\href{https://github.com/FloatingPragma/observer-patch-holography/releases/download/\OPHPaperReleaseID/screen_microphysics_and_observer_synchronization.pdf}{release PDF}.

\bibitem{oph-dark}
B.\ M\"uller and D.\ Matscheko,
\emph{Observer-Patch Holography and the Dark Matter Phenomenon}.
\href{https://github.com/FloatingPragma/observer-patch-holography/releases/download/\OPHPaperReleaseID/oph_dark_matter_paper.pdf}{release PDF}.

\end{thebibliography}

\end{document}
