\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{booktabs,longtable,array}
\usepackage[shortlabels]{enumitem}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{microtype}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\setlength{\emergencystretch}{3em}
\renewcommand{\arraystretch}{1.12}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\numberwithin{equation}{section}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\OPH}{\mathrm{OPH}}
\newcommand{\YM}{\mathrm{YM}}
\newcommand{\Rep}{\mathrm{rep}}
\newcommand{\A}{\mathcal A}
\newcommand{\Hcal}{\mathcal H}
\newcommand{\C}{\mathbb C}
\newcommand{\R}{\mathbb R}

\title{\textbf{Explaining the Yang--Mills Mass Gap with Observer-Patch Repair Dynamics}\\
\large A Support-Visible OPH Route to the Clay Problem}
\author{B.\ M\"uller}
\date{Draft of May 16, 2026}
\input{../paper/release_info}

\begin{document}
\maketitle
\begin{center}
\small\textbf{Paper release:} \OPHPaperReleaseID\quad
\textbf{Released:} \OPHPaperReleaseDate
\end{center}

\begin{abstract}
The Clay Yang-Mills problem asks for a nontrivial four-dimensional quantum Yang-Mills theory with a positive mass gap. OPH gives a route on its compact-gauge branch.

The construction isolates the finite OPH repair mechanism and the certificate needed before that
mechanism may be read as a four-dimensional Yang--Mills theorem. Fixed-cutoff local repair has a
uniform rate floor and a positive transfer form. The Clay-facing statement is conditional on a
renormalized continuum certificate: Schwinger-function convergence, reflection positivity,
Euclidean covariance and locality, nontriviality, and Mosco or exact direct-limit convergence of
the transfer/intertwiner data. Without that certificate, the finite repair branch is not by itself
a construction of the four-dimensional Yang--Mills measure.
\end{abstract}

\section*{What This Paper Contributes}

The standard target is clear: construct a nontrivial four-dimensional quantum Yang--Mills theory
for every compact simple gauge group and prove a positive mass gap. OPH imports the usual compact
gauge language, reflection positivity, and Osterwalder--Schrader/Wightman target conditions. The
new ingredient is the repair interpretation of the vacuum sector.

On the support-visible compact-gauge branch, local holonomy data and the OPH scaling chart give
the candidate Euclidean Yang--Mills form. Exact local repair acts as a positive Euclidean
relaxation generator at finite cutoff. A uniform fixed-cutoff repair rate floor transports to the
continuum Hamiltonian only when the transfer forms, vacuum projections, and finite intertwiners
converge in the sense stated below. The proof therefore separates the finite repair mechanism from
the additional four-dimensional continuum certificate required by the Clay problem.

\section{Claim Boundary}

This paper gives a proof-bearing projective weak-* / GNS extraction from the declared finite
support-visible compact-gauge cylinder system. The finite positive-transfer and repair-gap
mechanism is conditional on the finite ground-state-transform/cross-fiber and uniform-gap receipts.
The Clay-facing Yang--Mills theorem additionally depends on the continuum certificate stated in
Assumption~\ref{ass:ym-continuum-certificate}: renormalized four-dimensional identification,
reflection positivity and OS regularity, transfer/vacuum convergence, and noncollapse.

More precisely, the imported four-dimensional form theorem uses compact-gauge reconstruction, the
four-dimensional scaling chart, the reflection-positive ordinary vacuum sector, the absence of
additional gauge-invariant relevant dimension-four pure-gauge operators beyond the positive
quadratic curvature invariant, the support-visible cylinder extraction, and the renormalized
regularity/universality receipt. The later mass-gap step adds the finite transfer receipt, exact
local repair, bounded-color active collars, repair completeness, and the uniform-gap certificate.

Acceptance as a Clay-admissible solution still depends on supplying the unproved parts of the OPH
compact-gauge continuum certificate: renormalized Schwinger-function convergence, reflection
positivity, Euclidean covariance/locality, nontriviality, and transfer/intertwiner convergence at
the strength required by the Clay/Jaffe--Witten statement. The proof below then isolates the
finite repair mechanism and shows that, on any branch carrying that certificate, the gap is
identified exactly:
\[
\Delta_{\YM}=\Delta_{\mathrm{rep}}.
\]
The two-dimensional heat-kernel identity in the wider OPH stack remains a separate normalization
and worldsheet-effective bridge; it is not the mass-gap proof.

\section{Position in the OPH Paper Stack}

This paper is a focused companion to the OPH paper stack. The broad reconstruction program is
summarized in \emph{Observers Are All You Need}~\cite{oph1}. The compact technical core is
\emph{Recovering Relativity and the Standard Model from Observer Overlap Consistency}~\cite{oph2},
which carries the support-visible compact-gauge repair-gap theorem inside the compact paper
itself. The particle branch is separate~\cite{oph3}. The finite repair and quotient-normal-form
machinery comes from \emph{Reality as a Consensus Protocol: The Fixed-Point Computation That
Implements Physics}~\cite{oph4}. The regulated screen, record, and edge heat-kernel architecture is
developed in \emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and
Observer Synchronization in OPH}~\cite{oph5}.

The edge-sector theorem in the stack relates OPH heat-kernel weights to a two-dimensional
Yang--Mills partition identity. That identity fixes normalization and the controlled worldsheet
effective bridge. The four-dimensional mass-gap argument uses repair dynamics: exact local repair
becomes a positive Euclidean relaxation generator, and the uniform repair gap is transported to the
compact-gauge Hamiltonian only under the continuum certificate.

The Clay-facing import is the compact paper's D7 Yang--Mills theorem surface: the compact-gauge
reconstruction ladder, the four-dimensional Euclidean Yang--Mills form theorem, the coherent
compact-gauge extraction proposition, the conditional support-visible Osterwalder--Schrader
reconstruction theorem, the nontriviality certificate, and the exact finite repair-gap theorem.
This note isolates that branch theorem surface; it does not enlarge it.

\section{The Clay Target}

The Clay Mathematics Institute describes the Yang--Mills mass gap as the missing mathematical
foundation behind the quantum theory used for nonabelian gauge forces~\cite{clay}. Jaffe and
Witten state the problem as follows: for every compact simple gauge group \(G\), construct a
nontrivial quantum Yang--Mills theory on \(\R^4\) satisfying axiomatic properties at least as
strong as the stated Wightman or Osterwalder--Schrader references and prove a mass gap
\(\Delta>0\)~\cite{jaffe-witten,clay-mpp}.

The OPH proof below addresses that target through a different variable. The starting data are finite observer patches,
compact-gauge visible quotient data, and exact repair collars. The nonzero energy threshold is
the cost of leaving the repair-fixed vacuum sector.

\section{Standing Setup}

Fix a compact simple gauge group \(G\) carried by an OPH compact-gauge zero-obstruction vacuum
branch, realized at fixed cutoff by the declared compact-gauge patch-carrier architecture. The
architecture supplies finite local Hilbert spaces, exact local constraints, patch and overlap
algebras, overlap sector projectors, record layers, and local repair interfaces.

Let \(r\) range over a cofinal refinement family of finite regulators. For each \(r\), let
\[
(\Hcal_r,\Omega_r,H_r),
\qquad
T_r(t)=e^{-tH_r},
\]
be the physical Euclidean Hilbert space, vacuum, Hamiltonian, and transfer semigroup.

Let \(X_r:=X_r^{(0)}\) be the support-visible time-zero compact-gauge quotient configuration
space, let \(\pi_r\) be the stationary time-zero measure, and set
\[
K_r:=L^2(X_r,\pi_r).
\]
Write \(\omega_r(a):=\int_{X_r}a\,d\pi_r\) for the associated state functional; \(K_r\) already
implements the finite \(\pi_r\)-null support reduction.
Let \(\mathcal C_r\) be the finite family of active repair collars. For each active collar
\(C\in\mathcal C_r\), let
\[
\rho_C:=\rho_{C,r}:X_r\to Y_{C,r}
\]
be the complete repaired visible datum, and let
\[
E_C:K_r\to K_r
\]
be conditional expectation onto the \(\rho_C\)-measurable functions.

The proof stays on the ordinary or central zero-obstruction vacuum branch. The genuinely
noncentral higher-gauge branch is a different fixed-cutoff sector in the OPH stack and is not
used for the ordinary compact-simple \(G\) theorem below.

\begin{longtable}{@{}L{0.24\textwidth}L{0.68\textwidth}@{}}
\toprule
Notation & Meaning \\
\midrule
\endhead
\(X_r,\pi_r,K_r\) & support-visible time-zero quotient configuration space, stationary measure, and \(L^2(X_r,\pi_r)\). \\
\(\mathcal C_r\) & finite active repair-collar family at regulator \(r\). \\
\(\rho_C\) & complete repaired visible datum on collar \(C\). \\
\(E_C\) & \(\pi_r\)-preserving conditional expectation onto \(\rho_C\)-measurable functions. \\
\(L_r^{\Rep}\) & ground-state transformed Euclidean repair generator at cutoff \(r\). \\
\(P_{0,r}\) & projection onto constants in \(K_r\), corresponding to the physical vacuum. \\
\(U_r\) & finite-stage unitary from the physical Euclidean Hilbert space to the repair \(L^2\) space. \\
\(K,\Hcal,U\) & support-visible continuum repair Hilbert space, physical Hilbert space, and limiting unitary. \\
\(c_*\) & uniform active-collar repair-rate floor. \\
\bottomrule
\end{longtable}

\section{Imported 4D Euclidean Yang--Mills Form}

\begin{assumption}[Support-visible compact-gauge Yang--Mills branch]
\label{ass:ym-branch}
The compact-gauge branch used below satisfies the following branch-local conditions.
\begin{enumerate}[(i)]
\item the ordinary or central zero-obstruction compact-gauge sector survives refinement with compact simple structure group \(G\);
\item the cofinal regulator tail satisfies the compact paper's explicit compact-gauge refinement receipt;
\item the support-visible quotient carries a four-dimensional Euclidean scaling chart;
\item the ordinary vacuum sector is reflection positive and has topological angle \(\theta=0\);
\item the local finite-constraint MaxEnt/Gibbs family is gauge-invariant, Euclidean local, rotation-invariant, and refinement-stable;
\item no additional gauge-invariant relevant dimension-four pure-gauge operator remains on this branch besides the positive quadratic curvature invariant;
\item the branch is carried on a separated cofinal regulator system with the finite compact-gauge
cylinder data defined in Section~\ref{sec:continuum-extraction}.
\end{enumerate}
No continuum cylinder state, GNS space, transfer generator, or vacuum projection is assumed in
this branch declaration.
\end{assumption}

\begin{theorem}[Imported conditional OPH four-dimensional Euclidean Yang--Mills form]
\label{thm:ym-form}
Under Assumptions~\ref{ass:ym-branch} and \ref{ass:ym-continuum-certificate}, on an extracted cylinder family from
Proposition~\ref{prop:extraction} that lies on the declared local four-dimensional scaling branch,
the continuum gauge-sector Euclidean action is
\[
S_E[A]=\frac{1}{4g^2}\int_{\R^4}
\langle F_{\mu\nu},F_{\mu\nu}\rangle\,d^4x,
\qquad
F=dA+A\wedge A,
\tag{YM}
\]
with compact simple structure group \(G\). The extracted gauge-quotient cylinder family is denoted
\[
d\mu_{\YM}(A)=Z^{-1}e^{-S_E[A]}\,D A/G
\]
in the OPH support-visible GNS representation. This notation abbreviates the certified cylinder
family; it is not a literal infinite-dimensional Lebesgue measure. Its support-visible continuum
transfer semigroup is the corresponding Euclidean Yang--Mills semigroup.
\end{theorem}

\begin{proof}
This is the support-visible compact-gauge Yang--Mills form theorem of the compact OPH paper,
where it appears as Theorem \texttt{thm:oph-4d-euclidean-yang-mills-form}~\cite{oph2}. The proof
spine is recalled here because it fixes the target Hamiltonian for the mass-gap step.

The present Yang--Mills branch takes compact simple \(G\) as branch data. When \(G\) is imported
from OPH reconstruction, that import is conditional on the compact-gauge refinement receipt; on
that tail the zero-obstruction transportable bosonic sector category and its faithful forgetful
fiber functor reconstruct \(G\)~\cite{oph2}. At fixed cutoff, the declared compact-gauge patch-carrier presentation gives
support-visible link holonomies and plaquette holonomies. In the refinement limit, the
zero-obstruction gluing law makes infinitesimal rectangle holonomies multiplicative and
path-local. The Cauchy/regularity certificate in items (Y1)--(Y3) upgrades the
generalized-holonomy cluster state to a local connection \(A\) on the four-dimensional scaling
chart, and
the infinitesimal plaquette defect is
\[
U_{\mu\nu}(\varepsilon,x)
=
\mathbf 1+\varepsilon^2F_{\mu\nu}(x)+O(\varepsilon^3),
\qquad
F=dA+A\wedge A.
\]

The Euclideanized MaxEnt/local-Gibbs branch gives a local finite-range action density built from
support-visible gauge-invariant collar data. Gauge quotienting permits only class functions of
the curvature and its covariant derivatives. The four-dimensional scaling chart, Euclidean
rotation invariance, locality, and reflection positivity leave one relevant dimension-four
positive quadratic invariant in the pure gauge sector:
\[
\langle F_{\mu\nu},F_{\mu\nu}\rangle.
\]
The possible topological density \(\langle F\wedge F\rangle\) is reflection odd and belongs to a
separate topological-angle sector; it is absent on the ordinary reflection-positive
zero-obstruction vacuum branch used here. Higher curvature powers and covariant-derivative terms
are irrelevant operators under the declared continuum scaling; their disappearance in the
extracted state is part of the uniform renormalized remainder control in (Y1)--(Y3). Normalizing
the unique positive quadratic invariant defines the coupling \(g\) and gives (YM).

The finite-stage cylinder measures are the gauge-register / quantum-link Gibbs measures pushed to
the support-visible quotient. Proposition~\ref{prop:extraction} proves the compatible
support-visible weak-\(*\) / GNS cylinder extraction. The generator and transfer-semigroup
identification use the separate dynamic items (Y4)--(Y5) of
Assumption~\ref{ass:ym-continuum-certificate}; weak-* compactness alone does not provide them.
\end{proof}

\begin{corollary}[Yang--Mills equations on the compact-gauge branch]
\label{cor:ym-equations}
With an external conserved gauge current \(J\), the OPH curvature-square action on the same
support-visible compact-gauge branch gives
\[
DF=0,
\qquad
D{*}F=g^2{*}J,
\]
equivalently
\[
D_\mu F^{\mu\nu}=g^2J^\nu
\]
in local coordinates after the usual continuation to the Lorentzian field-equation convention.
\end{corollary}

\begin{proof}
The curvature \(F=dA+A\wedge A\) obeys the covariant Bianchi identity \(DF=0\). Varying the
quadratic curvature action
\[
S[A,J]
=
-\frac{1}{2g^2}\int \langle F\wedge *F\rangle
+\int \langle A\wedge *J\rangle
\]
with respect to compactly supported variations of \(A\) gives
\[
\delta S
=
\int \langle \delta A\wedge (g^{-2}D{*}F-{*}J)\rangle
\]
up to a boundary term. Stationarity gives \(D{*}F=g^2{*}J\). The source-free equation is the
case \(J=0\).
\end{proof}

\begin{remark}[Why this step matters for the prize]
The proof has two separate claims. Theorem~\ref{thm:ym-form} identifies the support-visible
continuum gauge sector with four-dimensional Euclidean Yang--Mills under its branch hypotheses.
The spectral argument applies to that Hamiltonian and proves a positive gap only when
Assumption~\ref{ass:ym-continuum-certificate} supplies the OS/transfer/nontriviality bridge.
\end{remark}

\begin{remark}[Abelian boundary and Maxwell branch]
The ordinary electromagnetic \(\mathrm U(1)_Q\) branch is the abelian boundary case of the same
compact-gauge curvature package. Restricting \(F=dA+A\wedge A\) to \(\mathfrak u(1)_Q\) gives
\[
F_Q=dA_Q,
\qquad
dF_Q=0,
\qquad
d{*}F_Q=g_Q^2{*}J_Q
\]
after varying the quadratic electromagnetic action with current \(J_Q\). This recovers Maxwell's
equations after canonical electromagnetic normalization. The Clay-facing mass-gap claim concerns
compact simple nonabelian \(G\) on the support-visible branch above. On the separate abelian branch,
the displayed Maxwell kinetic action, an ordinary Lorentz vacuum, and the absence of a Higgs,
St\"uckelberg, or medium mass give two transverse classical modes with quadratic pole
\(k^2=0\). The abstract group \(\mathrm U(1)_Q\) alone does not imply that action, phase, or pole.
A photon particle additionally requires a positive-energy physical quantization and a
positive-residue massless spectral pole; none of those quantum receipts is part of the Clay-facing
Yang--Mills gap statement.
\end{remark}

\section{Fixed-Cutoff Repair Equals Projection}

\begin{proposition}[Local exact repair equals conditional expectation]
\label{prop:local-repair}
For each active collar \(C\), the exact-Markov repair map on the support-visible quotient is the
\(\pi_r\)-preserving conditional expectation \(E_C\).
\end{proposition}

\begin{proof}
On the exact-Markov branch, repair preserves exactly the repaired visible datum \(\rho_C\), changes
only complementary invisible fiber data, and acts on the quotient-first physical algebra rather
than on microscopic representatives. Let \(\Phi_C\) be the Heisenberg repair map and let
\(\mathcal N_C\) be the repaired local fixed algebra. Exact repair semantics require
\(\mathcal N_C\) to be exactly the \(\rho_C\)-measurable subalgebra. They give
\[
\Phi_C(a)=a \quad (a\in\mathcal N_C),
\]
\[
\Phi_C(\mathcal A_r^{G,\mathrm{sv}})\subseteq\mathcal N_C,
\qquad
\omega_r\circ\Phi_C=\omega_r,
\]
and \(\Phi_C\) is \(\mathcal N_C\)-bimodular. Therefore, for \(a\in\mathcal N_C\) and
\(x\in\mathcal A_r^{G,\mathrm{sv}}\),
\[
\omega_r\!\left(a^*\Phi_C(x)\right)=\omega_r(a^*x).
\]
Since \(\Phi_C(x)\in\mathcal N_C\), this equation characterizes its class in \(K_r\) as the
orthogonal projection of \(x\) onto the \(\rho_C\)-measurable subspace, uniquely modulo
\(\pi_r\)-null functions. That orthogonal projection is the \(\pi_r\)-preserving conditional
expectation \(E_C\).
\end{proof}

\section{Exact Euclidean-Consensus Law}

\begin{lemma}[Fiber-homogeneous orbit condition]
\label{lem:fiber-symmetry}
Fix an active collar \(C\) and a repaired value \(y\in Y_{C,r}\). On the support-visible quotient,
let the complete conditional fiber be
\[
F_C(y)=\rho_{C,r}^{-1}(y)
\]
with conditional law \(\nu_{C,y}\). If this is either finite uniform or standard atomless, has no
remaining observable labels, and the primitive relaxation is invariant under every
\(\nu_{C,y}\)-preserving automorphism, then the full fiber, including every holonomy coordinate
actually resampled by repair, is homogeneous for the local repair receipt.
\end{lemma}

\begin{proof}
This is the complete-fiber homogeneity receipt. Quotienting removes declared implementation
labels, but the proof must also check that no remaining source constraint or relaxation rate
distinguishes points in the fiber. Under that check, the conditioned state and primitive
relaxation carry the stated full measure-preserving symmetry.
\end{proof}

\begin{lemma}[Scalar relaxation on a homogeneous conditional fiber]
\label{lem:scalar-relaxation}
Let \((F,\nu)\) be either a finite uniform probability space or a standard atomless probability
space. Let \(E_F\) be expectation onto constants, and let \(D_F\) be a bounded positive
self-adjoint Markov relaxation generator such that
\[
\ker D_F=\operatorname{Ran}(E_F)
\]
and \(D_F\) commutes with every measure-preserving automorphism of \((F,\nu)\). Then there is a scalar
\(c_F>0\) such that
\[
D_F=c_F(I-E_F).
\]
\end{lemma}

\begin{proof}
For a finite uniform fiber, the symmetric-group representation on the mean-zero subspace is
irreducible. For a standard atomless fiber, use equal-measure finite partitions. Automorphisms
within pieces and permutations of pieces force every bounded commutant operator to be scalar on
the mean-zero step functions; compatibility under refinements gives one scalar, and these step
functions are dense in \(L^2_0(F,\nu)\). Positivity and the kernel condition make the scalar
strictly positive. The formula follows.
\end{proof}

\begin{assumption}[Finite ground-state-transform and cross-fiber receipt]
\label{ass:finite-transfer-receipt}
For every regulator, the reflection-positive finite transfer matrix supplies a unitary
\(U_r:\Hcal_r\to K_r\), with \(U_r\Omega_r=\mathbf 1_r\), such that
\[
U_rH_rU_r^{-1}=\sum_{C\in\mathcal C_r}D_C.
\]
Each \(D_C\) is a bounded positive self-adjoint detailed-balance Markov generator acting on the
complete complementary conditional fiber, including every record or holonomy coordinate changed
by repair; its fixed algebra is exactly the
\(\rho_{C,r}\)-measurable algebra, and its fiberwise scalar \(c_C(y)\) is independent of the
repaired value \(y\) on the support of \(\pi_r\). A Gibbs state by itself does not imply this
finite transfer-matrix/decomposition receipt.
\end{assumption}

\begin{theorem}[Exact Euclidean repair law under homogeneous fibers]
\label{thm:ec-law}
Under the fiber-homogeneous orbit condition for every active collar and
Assumption~\ref{ass:finite-transfer-receipt}, there are positive constants
\(c_C>0\) such that the ground-state transformed physical Euclidean
generator is exactly
\[
L_r^{\Rep}=\sum_{C\in\mathcal C_r} c_C(I-E_C),
\tag{1}
\]
and therefore
\[
U_r e^{-tH_r}U_r^{-1}=e^{-tL_r^{\Rep}}
\qquad(t\ge0),
\tag{2}
\]
for a unitary \(U_r:\Hcal_r\to K_r\) with \(U_r\Omega_r=\mathbf 1_r\).
\end{theorem}

\begin{proof}
The finite receipt supplies the ground-state transform and its primitive local pieces. Each
\(D_C\) is supported on one collar \(C\), preserves exactly the repaired visible datum
\(\rho_{C,r}\), and relaxes the complete complementary conditional fiber. Hence
\[
\ker D_C=\operatorname{Ran}(E_C).
\]

Lemma~\ref{lem:fiber-symmetry} gives the full hidden-fiber permutation symmetry. Applying
Lemma~\ref{lem:scalar-relaxation} fiberwise gives
\(D_{C,y}=c_C(y)(I-E_{C,y})\). The cross-fiber receipt makes \(c_C(y)=c_C\), so
\[
D_C=c_C(I-E_C).
\]
The scalar is positive because \(C\) is active. Branch homogeneity makes it a collar-type scalar,
so summing over the active collars gives (1), and exponentiation of the positive self-adjoint
generator gives (2).
\end{proof}

\begin{lemma}[Uniform active-collar rate floor]
\label{lem:floor}
Assume finite local combinatorial type, a branch-homogeneous local constraint family, and
refinement-stable exact repair semantics. Then the local Euclidean repair rate depends only on
active collar type, the active collar-type set is finite across the cofinal refinement family, and
there is \(c_*>0\), independent of \(r\), such that
\[
c_C\ge c_*
\qquad
\text{for every active collar }C\in\mathcal C_r.
\tag{3}
\]
\end{lemma}

\begin{proof}
Active collars are exactly the collars on which complementary invisible fiber data are genuinely
relaxed. Hence \(D_C\neq0\) on \(\ker(E_C)\), so \(c_C>0\). Finite local combinatorial type gives
a finite list of bounded collar patterns, including their visible interface alphabets, hidden
fiber cardinalities, local constraint templates, and admissible repair maps. Branch homogeneity
makes the conditioned MaxEnt relaxation scalar a function of this finite type data. Refinement
stability says that refinement replaces a collar by copies of the same bounded type templates
with the same normalized local Euclidean repair semantics, so no new rate-degenerating collar
type appears along the cofinal family. Taking the minimum of \(c_C\) over the finite active type
list gives \(c_*>0\).
\end{proof}

\section{Finite-Stage Gap}

\begin{proposition}[Special commuting-color finite-stage repair gap]
\label{prop:finite-gap}
Assume that the collar family admits a bounded-color decomposition
\[
\mathcal C_r=\bigsqcup_{a=1}^{q}\mathcal C_{r,a},
\qquad q<\infty,
\tag{4}
\]
independent of \(r\), and that exact quotient-local gluing makes the corresponding color
expectations commute. Then
\[
L_r^{\Rep}\ge c_*(I-P_{0,r}),
\tag{5}
\]
where \(P_{0,r}\) projects onto constants in \(K_r\). Hence
\[
\Delta_{\mathrm{rep},r}\ge c_*>0.
\tag{6}
\]
\end{proposition}

\begin{proof}
For each color \(a\), define the parallel color expectation
\[
E_{r,a}:=\prod_{C\in\mathcal C_{r,a}}E_C.
\]
Same-color collars are disjoint, so the factors commute. Exact quotient-local gluing makes
\(\{E_{r,a}\}_{a=1}^{q}\) a commuting family of orthogonal projections on the vacuum branch.

Repair completeness says that the only support-visible observables fixed by every local repair
are constants:
\[
\bigcap_{a=1}^{q}\operatorname{Ran}(E_{r,a})=\C\,\mathbf 1_r.
\tag{7}
\]
Define
\[
\widetilde L_r:=\sum_{a=1}^{q} c_*(I-E_{r,a}).
\]
For commuting projections,
\[
I-\prod E_C\le \sum_C(I-E_C),
\]
so \(\widetilde L_r\le L_r^{\Rep}\). The projections \(E_{r,a}\) are simultaneously
diagonalizable. On the joint all-ones eigenspace, (7) says the vector is constant. Every
nonconstant joint eigenspace has at least one color eigenvalue zero, so
\[
\widetilde L_r\ge c_*(I-P_{0,r}).
\]
This proves (5), and the spectral gap bound (6) follows.
\end{proof}

\begin{remark}[Generic repair-gap certificate]
The commuting-color proposition is a special certificate, not the generic repair-generator route.
For overlapping collars one must instead compute
\[
\kappa_r=\inf_{f\perp 1}
\frac{\sum_C\|(I-E_C)f\|^2}{\|f\|^2}.
\]
If local fiber rates have a lower bound \(\gamma_*>0\), then
\[
L_r^{\Rep}\ge \gamma_*\kappa_r(I-P_{0,r}).
\]
Finite repair completeness gives \(\kappa_r>0\) at fixed regulator; a uniform refinement lower
bound is a separate receipt.
\end{remark}

\section{Continuum Extraction}
\label{sec:continuum-extraction}

\begin{definition}[Finite compact-gauge state spaces and local cylinders]
\label{def:finite-cylinders}
At regulator \(r\), make the following construction both for the finite four-dimensional
Euclidean slab \(\Lambda_r^{(4)}=(V_r^{(4)},E_r^{(4)})\) and for its time-zero spatial slice
\(\Lambda_r^{(0)}=(V_r^{(0)},E_r^{(0)})\). In the formulas below
\(\Lambda_r=(V_r,E_r)\) denotes either choice until the superscript is restored. Let \(D_r\) be
the finite repaired-record and zero-obstruction sector register. In the gauge-register
presentation, let
\[
\widetilde X_r\subseteq G^{E_r}\times D_r
\]
be the closed set obeying the finite Gauss, overlap, and repaired-record constraints. With
\(\mathcal G_r=G^{V_r}\) acting at edge endpoints and
\(\sim_{\mathrm{ov}}\) the closed relation of support-visible overlap/presentation
indistinguishability, define
\[
X_r:=(\widetilde X_r/\mathcal G_r)/{\sim_{\mathrm{ov}}}
\]
as the support-visible quotient. This is compact Hausdorff. The regulator
has finitely many cells, but \(X_r\) need not be a finite set when \(G\) is a compact Lie group.

For each active collar \(C\), let
\[
\rho_{C,r}:X_r\to Y_{C,r}
\]
be the continuous complete repaired readback. The complementary conditional fiber contains every
record or holonomy coordinate actually resampled by repair and is either finite uniform or a
standard atomless probability space with its conditioned MaxEnt/Haar law. The readback retains
exactly the repaired fixed datum, not every pre-repair holonomy. A quantum-link carrier enters this
proposition only through its commuting Euclidean cylinder/readout subalgebra; the noncommutative
carrier algebra would require a separate GNS-representation-kernel support reduction.

For a bounded cell region \(O\subset\Lambda_r\), let
\(\mathfrak C_r^{G,\mathrm{sv}}(O)\) be generated by the gauge-invariant Peter--Weyl matrix
coefficients contracted into spin networks, Wilson-loop characters, and retained gauge-invariant
boundary carriers in \(O\), together with the overlap-sector projectors and continuous functions
of the complete repaired collar readbacks in \(O\). Define
\[
\mathcal A_r^{G,\mathrm{sv}}(O)
:=\overline{\mathfrak C_r^{G,\mathrm{sv}}(O)}^{\|\cdot\|_\infty}
\subseteq C(X_r).
\]
Equivalently, start from the freely presented gauge-invariant readout-generator \(^*\)-algebra,
quotient by the kernel of its evaluation homomorphism on \(X_r\), and complete. This kernel is a
closed two-sided overlap-trivial ideal chosen before a state and is distinct from the limiting GNS
null ideal below.
The relation \(\sim_{\mathrm{ov}}\) identifies exactly the configurations on which all declared
spin-network, sector, and repaired-readback generators agree. The resulting self-adjoint unital
algebra separates points of \(X_r\), so Stone--Weierstrass gives
\[
\mathcal A_r^{G,\mathrm{sv}}(\Lambda_r)=C(X_r).
\]
For any selected stage measure \(\pi_r\), its GNS cylinder closure is therefore the full
\(L^2(X_r,\pi_r)\), after the finite \(\pi_r\)-null support reduction.

Write the two resulting systems as
\[
(X_r^{(4)},\mathcal A_r^{G,\mathrm{sv},(4)}(O))
\quad\hbox{and}\quad
(X_r^{(0)},\mathcal A_{r,0}^{G,\mathrm{sv}}(B)).
\]
Euclidean-history restriction gives a continuous time-zero map
\(\tau_{0,r}:X_r^{(4)}\to X_r^{(0)}\).

For \(r\preceq s\), coarse shadow multiplies the ordered fine-edge holonomies above each coarse
edge and restricts the repaired records and sector labels. Gauge covariance and refinement
associativity give
\[
p_{sr}:X_s\to X_r,
\qquad
p_{tr}=p_{sr}\circ p_{ts},
\]
with the four-dimensional/time-zero commuting square
\[
\tau_{0,r}\circ p_{sr}^{(4)}
=p_{sr}^{(0)}\circ\tau_{0,s},
\]
and unital local \(^*\)-maps on the separated support-visible quotient,
\[
\iota_{rs}^{O}:\mathcal A_r^{G,\mathrm{sv}}(O)\to
\mathcal A_s^{G,\mathrm{sv}}(O_s),
\qquad
\iota_{rs}^{O}(a)=a\circ p_{sr},
\qquad
\iota_{rt}^{O}=\iota_{st}^{O_s}\iota_{rs}^{O}.
\]
These maps preserve local isotony, gauge invariance, repaired readbacks, and the
zero-obstruction sector. When this cylinder system is used on the compact paper's refinement-limit
gauge branch, its sector-projector restriction must match the separately certified
block-multiplicity injection in the compact-gauge refinement receipt~\cite{oph2}; that injection is
not a consequence of deterministic coarse shadow. We use a countable cofinal regulator
sequence and countable bounded-region exhaustion. The unrestricted directed version uses a subnet
and product compactness instead. If every declared coarse configuration has a fine extension,
\(p_{sr}\) is surjective and the full pullback is injective. Otherwise the \(C^*\)-inductive limit
automatically quotients the common refinement-null kernel; Proposition~\ref{prop:extraction} does
not require prelimit injectivity. That noninjective quotient branch is not, by itself, the compact
paper's receipt-certified sector ladder. Write
\(\mathcal A_r^{G,\mathrm{sv}}:=\mathcal A_r^{G,\mathrm{sv}}(\Lambda_r)\).
\end{definition}

\begin{proposition}[Projective weak-* extraction and support-visible GNS gluing]
\label{prop:extraction}
Let \(\mu_s^{(4)}\) be the declared finite quotient-Gibbs probability measure on \(X_s^{(4)}\),
let
\[
\pi_s:=(\tau_{0,s})_\#\mu_s^{(4)},
\qquad
\mu_s^{(0)}:=\pi_s,
\]
and, for \(d\in\{4,0\}\), define
\[
\omega_s^{(d)}(a):=\int_{X_s^{(d)}}a\,d\mu_s^{(d)},
\qquad
\omega_{s\downarrow r}^{(d)}
:=\omega_s^{(d)}\circ\iota_{rs}^{(d)}.
\]
The following statements hold for both values of \(d\); the superscript is suppressed in the
proof.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2em]
\item for \(q\preceq r\preceq s\),
\[
\omega_{s\downarrow r}\circ\iota_{qr}=\omega_{s\downarrow q};
\]
\item a cofinal subsequence, or subnet, has weak-* limits
\(\omega_{s_\alpha\downarrow r}\to\overline\omega_r\) on every fixed local cylinder, and
\[
\overline\omega_r=\overline\omega_t\circ\iota_{rt}
\qquad(r\preceq t);
\]
\item the local limits glue to a state \(\omega_\infty\) on
\[
\mathcal A_\infty^{G,\mathrm{cyl}}(O)
:=\overline{\varinjlim_r\mathcal A_r^{G,\mathrm{sv}}(O_r)},
\]
and the union of these isotone local algebras is dense in the global cylinder algebra;
\item after the separate support reduction
\[
\mathcal N_\omega(O):=\{a\in\mathcal A_\infty^{G,\mathrm{cyl}}(O):
\omega_\infty(a^*a)=0\},
\qquad
\mathcal A_\infty^{G,\mathrm{supp}}(O)
:=\mathcal A_\infty^{G,\mathrm{cyl}}(O)/\mathcal N_\omega(O),
\]
the induced state and representation are faithful. The compatible local GNS spaces have a Hilbert
direct limit \((K^{(d)},\Pi^{(d)},\mathbf 1^{(d)})\), and the union of their cylinder images is
dense. Write \(K^E:=K^{(4)}\) for the Euclidean-history GNS space and \(K:=K^{(0)}\) for the
time-zero repair GNS space. The latter vector becomes the physical vacuum only through the
transfer/OS certificate.
\end{enumerate}
If, in a finite quotient presentation, the four-dimensional measures have declared weights
\[
\mu_r^{(4)}(x)=Z_r^{-1}m_r(x)e^{-S_r(x)}
\]
and satisfy the fiber-sum identity
\[
\sum_{x':\,p_{sr}(x')=x}m_s(x')e^{-S_s(x')}
=\alpha_{sr}m_r(x)e^{-S_r(x)}
\tag{FS}
\]
with \(\alpha_{sr}\) independent of \(x\), then
\((p_{sr}^{(4)})_\#\mu_s^{(4)}=\mu_r^{(4)}\). The time-zero square gives
\((p_{sr}^{(0)})_\#\pi_s=\pi_r\), so both original state families are projective. Without
(FS), compactness produces a projective cluster family; it does not prove
\(\overline\omega_r=\omega_r\) or uniqueness of the continuum state. For continuous
compact-holonomy stages, replace (FS) by the corresponding disintegration receipt
\((p_{sr}^{(4)})_\#\mu_s^{(4)}=\mu_r^{(4)}\).
\end{proposition}

\begin{proof}
For \(q\preceq r\preceq s\), coarse-shadow functoriality gives
\[
(\omega_s\circ\iota_{rs})\circ\iota_{qr}
=\omega_s\circ\iota_{qs},
\]
proving \textup{(i)}.

For a fixed local cylinder algebra, its state space is weak-* compact by Banach--Alaoglu. The
chosen local algebras are separable because compact metrizable \(G\) has a countable Peter--Weyl
test algebra and a finite regulator has only finitely many record and sector generators. Their
state spaces are therefore weak-* metrizable. Successively extract a subsequence for the first,
second, and later cylinders, choosing the \(k\)-th diagonal index beyond the \(k\)-th regulator
stage. The diagonal subsequence is cofinal and converges on all cylinders. For a general
directed regulator set, use a convergent subnet in the compact product of the local state spaces;
unresolved early coordinates may be filled arbitrarily because each fixed coordinate is genuinely
resolved on a cofinal tail. Weak-* continuity of precomposition and part \textup{(i)} yield
\[
\overline\omega_r\circ\iota_{qr}
=\lim_\alpha\omega_{s_\alpha\downarrow r}\circ\iota_{qr}
=\lim_\alpha\omega_{s_\alpha\downarrow q}
=\overline\omega_q,
\]
which proves \textup{(ii)}.

For a representative \([a]_r\) in the algebraic inductive limit, define
\[
\omega_\infty([a]_r):=\overline\omega_r(a).
\]
Compatibility makes this well defined. Positivity and normalization are checked in one finite
algebra containing the element. For every \(t\succeq r\),
\[
|\overline\omega_r(a)|
=|\overline\omega_t(\iota_{rt}(a))|
\le\|\iota_{rt}(a)\|.
\]
Taking the infimum along the tail gives the inductive-limit norm bound even for noninjective
bonding maps, so the state extends uniquely to the \(C^*\)-completion. This proves
\textup{(iii)}.

On a commutative local cylinder algebra, the Riesz representation theorem identifies the null
ideal with the continuous functions that vanish on the measure support. The support quotient is
therefore \(C(\operatorname{supp}\mu_O)\), where \(\mu_O\) is the representing local Radon
measure, and its induced state is faithful. If \(O\subseteq O'\), state compatibility gives
\[
a\in\mathcal N_\omega(O)
\quad\Longleftrightarrow\quad
\iota_{OO'}(a)\in\mathcal N_\omega(O').
\]
Thus the inclusions descend injectively and the support quotients form an isotone faithful local
net. For
\(r\preceq t\), define
\[
V_{rt}[a]_r:=[\iota_{rt}(a)]_t.
\]
It is well defined and isometric because
\[
\|V_{rt}[a]_r\|^2
=\overline\omega_t(\iota_{rt}(a^*a))
=\overline\omega_r(a^*a).
\]
These maps compose, preserve \(\mathbf 1\), and intertwine the cylinder representations. Their
Hilbert direct limit is the GNS completion of the cylinder union, proving \textup{(iv)}.

Finally, suppressing the \(d=4\) superscript, summing (FS) over \(x\) gives
\(Z_s=\alpha_{sr}Z_r\). Division by the partition functions then gives
\((p_{sr}^{(4)})_\#\mu_s^{(4)}=\mu_r^{(4)}\), equivalently
\(\omega_s^{(4)}\circ\iota_{rs}^{(4)}=\omega_r^{(4)}\). The commuting time-zero square gives the
corresponding \(d=0\) identity.
\end{proof}

\begin{remark}[What compactness does not preserve]
The overlap-trivial presentation quotient and the GNS support quotient are different. Even
faithful finite states can converge to a nonfaithful state. Proposition~\ref{prop:extraction}
constructs the cylinder algebra, its state, the repair-side GNS space \(K\), and the constant
vacuum vector. It does not construct \(\Hcal\), a limit generator, a physical intertwiner, or
vacuum-projection convergence. Those require the finite dynamic receipts below.
\end{remark}

\begin{assumption}[Four-dimensional Yang--Mills continuum certificate]
\label{ass:ym-continuum-certificate}
In addition to the finite compact-gauge repair data, one cofinal regulator family supplies all of
the following.
\begin{enumerate}[label=\textup{(Y\arabic*)},leftmargin=2em]
\item For each bounded region \(O\), renormalized gauge-invariant cylinder maps from one fixed
countable test \(^*\)-algebra \(\mathfrak C_0^G(O)\) to
\(\mathcal A_r^{G,\mathrm{sv}}(O_r)\), with a uniform finite-volume/lattice-spacing Cauchy bound.
The maps commute with the coarse-shadow \(\iota_{rs}\) up to those vanishing Cauchy defects. This
makes the extracted cluster family unique on the declared tests.
\item Exact finite reflection positivity, or a positive self-adjoint transfer matrix, with
reflection-compatible renormalization maps.
\item Uniform restoration of Euclidean covariance, locality, regularity, clustering, and the
declared vacuum-sector condition.
\item Generalized Mosco convergence of both the physical transfer forms
\(q_r^{\mathrm{phys}}\) and repair forms \(q_r^{\mathrm{rep}}\) to closed nonnegative continuum
forms, or exact coherent direct-limit semigroup identities under state-preserving repair and
physical refinement isometries, with one refinement-independent physical Euclidean-time
normalization. In the exact alternative the isometries send \(\mathbf 1_r\) to \(\mathbf 1_s\)
and \(\Omega_r\) to \(\Omega_s\).
\item Convergence of the finite intertwiners \(U_r\) and their inverses on dense form cores to a
unitary \(U\), together with
\(U_r\Omega_r=\mathbf 1_r\) and strong convergence of
\(P_{0,r}=|\mathbf 1_r\rangle\langle\mathbf 1_r|\) to
\(P_0^K=|\mathbf 1\rangle\langle\mathbf 1|\) under the declared Hilbert identifications. The
physical vacuum projection is
\(P_0^{\Hcal}:=U^{-1}P_0^KU=|\Omega\rangle\langle\Omega|\).
On the dense time-zero cylinder core, the finite Markov/OS identity
\[
\omega_r^{(4)}\!\left(
(\iota_{0,r}f)^*\tau_t^{(r)}(\iota_{0,r}g)
\right)
=\langle f,e^{-tL_r^{\Rep}}g\rangle_{K_r}
=\langle U_r^{-1}f,e^{-tH_r}U_r^{-1}g\rangle_{\Hcal_r}
\]
holds and passes to the limit. Thus the OS-reconstructed time-zero Hilbert space and Hamiltonian
are the same \((\Hcal,H)\) as the transfer-form limit, not a second pair with reused notation.
\item A nontriviality certificate: renormalized local observables \(A_r\), all images of one fixed
bounded cylinder test under the maps in (Y1), whose centered vectors converge under the Hilbert
identifications and satisfy
\[
\inf_r\operatorname{Var}_{\omega_r}(A_r)>0,\qquad
\sup_r q_r^{\mathrm{phys}}(A_r\Omega_r)<\infty .
\]
\end{enumerate}
The explicit multiresolution construction in the main paper supplies a model for items
(Y1)--(Y2) and an exact transfer tower when its shell identities are implemented. Identification
of its continuum limit with the four-dimensional Yang--Mills OS theory is the additional content
of (Y3)--(Y6).
\end{assumption}

\begin{theorem}[Conditional continuum transfer identification]
\label{thm:continuum}
Under Assumption~\ref{ass:ym-continuum-certificate}, the generalized Mosco limit, or the exact
coherent direct limit in item (Y4), produces nonnegative self-adjoint generators \(H\) and
\(L^{\mathrm{rep}}\) and a unitary \(U\) satisfying
\[
U e^{-tH}U^{-1}=e^{-tL^{\mathrm{rep}}}
\qquad(t\ge0),
\tag{8}
\]
and hence
\[
UHU^{-1}=L^{\mathrm{rep}}.
\tag{9}
\]
If the finite repair generators satisfy
\[
L_r^{\Rep}\ge c_*(I-P_{0,r})
\]
with one \(c_*>0\) and the vacuum projections converge strongly, then
\[
H\ge c_*(I-P_0^{\Hcal}).
\]
\end{theorem}

\begin{proof}
Generalized Mosco convergence is equivalent to generalized strong-resolvent and
transfer-semigroup convergence on the declared Hilbert identifications. In the exact alternative,
the coherent finite contraction semigroups define strongly continuous direct-limit semigroups on
the dense cylinder images, and uniform contractivity extends them to the completed Hilbert
spaces. Their bounded operators are symmetric and positive on the dense finite-stage union, hence
self-adjoint and positive after extension. Convergence of \(U_r\)
and \(U_r^{-1}\) on dense form cores passes the finite-stage intertwining relation to the limit,
so uniqueness of self-adjoint semigroup generators gives \(UHU^{-1}=L^{\mathrm{rep}}\). For a
repair-form Mosco recovery sequence \(\psi_r\to\psi\),
\[
q_r^{\mathrm{rep}}(\psi_r)
\ge c_*\bigl(\|\psi_r\|^2-\|P_{0,r}\psi_r\|^2\bigr).
\]
Taking the limit and using strong convergence of the vacuum projections gives the continuum form
inequality. In the exact direct-limit alternative, the finite bound is equivalently
\[
\|e^{-tL_r^{\Rep}}(I-P_{0,r})\|\le e^{-c_*t};
\]
coherence passes this estimate to the direct-limit semigroup, and the spectral theorem gives the
same continuum form inequality.
\end{proof}

\section{Axiomatic Reconstruction and Nontriviality}

\begin{theorem}[Conditional Osterwalder--Schrader reconstruction on the support-visible compact-gauge branch]
\label{thm:os}
Under Assumptions~\ref{ass:ym-branch} and \ref{ass:ym-continuum-certificate}, the continuum
support-visible compact-gauge cylinder family is Euclidean invariant, reflection positive,
regular on gauge-invariant local cylinder observables, nontrivial, and cyclic for the vacuum
sector. Hence Osterwalder--Schrader reconstruction gives a four-dimensional quantum Yang--Mills
theory
\[
(\Hcal,\Omega,H,\A_{\mathrm{loc}}^{G})
\]
on the support-visible gauge-invariant local algebra, with \(H\ge0\) and
\(e^{-tH}\) equal to the certified continuum Euclidean transfer semigroup.
\end{theorem}

\begin{proof}
Euclidean covariance, locality, reflection positivity, regularity, clustering, transfer
convergence, and nontriviality are precisely the certificate items in
Assumption~\ref{ass:ym-continuum-certificate}. Proposition~\ref{prop:extraction} supplies the
four-dimensional Euclidean cylinder state \(K^E\) and its time-zero GNS restriction \(K\); the
certificate supplies the missing regularity and transfer controls. The finite/limiting time-zero
identity in (Y5) identifies the OS time-zero inner product and translation semigroup with the
transfer-form limit \((\Hcal,H)\). The standard Osterwalder--Schrader reconstruction theorem
therefore produces the Hilbert space, vacuum, local algebra, and positive Hamiltonian, and
identifies the physical time-translation semigroup with the certified Euclidean transfer
semigroup~\cite{osterwalder-schrader1,osterwalder-schrader2}.
\end{proof}

\begin{proposition}[Nontriviality of the support-visible compact-gauge theory]
\label{prop:nontriviality}
Under Assumption~\ref{ass:ym-continuum-certificate},
the support-visible compact-gauge local algebra on the zero-obstruction vacuum branch strictly
contains the vacuum scalars and admits a non-vacuum finite-energy local excitation.
\end{proposition}

\begin{proof}
The compact-gauge witness and physical-UV landing theorem in the OPH compact paper supplies a
realized nontrivial compact-gauge branch~\cite{oph2}. At finite cutoff this gives a
support-visible gauge-invariant local observable, such as a nonconstant Wilson/plaquette cylinder
observable, whose vacuum variance is positive. Its GNS vector is orthogonal to the vacuum after
subtracting its expectation value. The finite-range local-Gibbs generator assigns finite energy to
finite-cylinder excitations. The continuum nontriviality step is not a consequence of weak-\(*\)
state convergence alone; it is the variance-floor and finite-energy item (Y6) in
Assumption~\ref{ass:ym-continuum-certificate}. With that certificate, the local cylinder vectors
survive in the support-visible continuum, so the continuum local algebra is strictly larger than
\(\C I\) and contains non-vacuum finite-energy local excitations.
\end{proof}

\section{Main Theorem}

\begin{theorem}[Conditional positive four-dimensional compact-gauge Yang--Mills mass gap]
\label{thm:main}
Let \(G\) be a compact simple gauge group carried by a support-visible compact-gauge OPH vacuum
branch satisfying the standing setup above and the continuum certificate of
Assumption~\ref{ass:ym-continuum-certificate}, the finite transfer receipt of
Assumption~\ref{ass:finite-transfer-receipt}, and all hypotheses of
Theorem~\ref{thm:ec-law}, Lemma~\ref{lem:floor}, and
Proposition~\ref{prop:finite-gap}. The theory reconstructed in
Theorem~\ref{thm:os}
is nontrivial, and its continuum support-visible Hamiltonian \(H\) satisfies
\[
H\ge c_*(I-P_0^{\Hcal}),
\tag{10}
\]
where \(P_0^{\Hcal}\) projects onto the physical vacuum. Therefore
\[
\operatorname{Spec}(H)\cap(0,c_*)=\varnothing,
\qquad
\Delta_{\YM}\ge c_*>0.
\tag{11}
\]
On that certified continuum branch the repair gap and Yang--Mills gap are exactly equal:
\[
\Delta_{\YM}=\Delta_{\mathrm{rep}}.
\tag{12}
\]
\end{theorem}

\begin{proof}
At every finite stage, Proposition~\ref{prop:finite-gap} gives
\[
L_r^{\Rep}\ge c_*(I-P_{0,r}).
\]
By Theorem~\ref{thm:continuum}, on the extracted cylinder/GNS space, this lower bound passes to
the support-visible continuum:
\[
L^{\mathrm{rep}}\ge c_*(I-P_0^K).
\]
Using (9), \(UHU^{-1}=L^{\mathrm{rep}}\). Conjugating the lower bound by \(U^{-1}\) gives (10),
and the spectral statement (11) follows. Since unitary equivalence preserves the nonzero spectrum
and identifies the vacuum with the constant sector, the infimum of the nonzero spectrum is the
same on both sides, giving (12).
\end{proof}

\begin{remark}[Group-uniform form]
The proof is group-uniform. Once a compact simple \(G\) is carried by a compact-gauge
zero-obstruction OPH branch, no step uses special properties of the realized Standard Model
quotient. The inputs are compact-gauge support-visible quotient locality, exact local repair on
collars, the finite ground-state-transform/cross-fiber receipt, the uniform rate and commuting-color
receipts, refinement coherence, projective cylinder extraction, the transfer/vacuum certificate,
and the OS regularity/noncollapse certificate.
\end{remark}

\section{Exact Gap Accounting}

On a branch satisfying Assumption~\ref{ass:ym-continuum-certificate}, the proof gives more than a
positive lower bound. It identifies the Hamiltonian whose gap is being measured:
\[
H=U^{-1}L^{\mathrm{rep}}U.
\]
Therefore
\[
\operatorname{Spec}(H)\setminus\{0\}
=
\operatorname{Spec}(L^{\mathrm{rep}})\setminus\{0\}.
\]
The Yang--Mills gap is exactly the first nonzero repair eigenvalue:
\[
\Delta_{\YM}
:=
\inf\bigl(\operatorname{Spec}(H)\setminus\{0\}\bigr)
=
\inf\bigl(\operatorname{Spec}(L^{\mathrm{rep}})\setminus\{0\}\bigr)
=:
\Delta_{\mathrm{rep}}.
\]
The finite-stage color argument proves \(\Delta_{\mathrm{rep}}\ge c_*>0\). The exact accounting
statement is the conditional equality \(\Delta_{\YM}=\Delta_{\mathrm{rep}}\); the inequality is the
positivity proof for that same quantity. Without the continuum certificate, the same equations
remain finite-regulator repair accounting instead of a Clay-admissible Yang--Mills theorem.

\section{Relation to the 2D Yang--Mills Bridge}

The OPH corpus also contains an exact edge-sector identity:
\[
Z_{\mathrm{edge}}(t)=\sum_R d_R^2e^{-tC_2(R)}=K_t(1),
\]
which is the compact-group heat kernel at the identity and matches the standard
two-dimensional Yang--Mills heat-kernel partition form. Peter--Weyl supplies the heat-kernel
identity, and Gross--Taylor gives the standard large-\(N\) worldsheet dictionary when a separate
large-\(N_{\mathrm{edge}}\) branch with remainder control is declared~\cite{peter-weyl,gross-taylor}.

That 2D result is a normalization and worldsheet-effective bridge. The spectral theorem above
concerns the support-visible compact-gauge Hamiltonian and obtains its lower bound by identifying
Euclidean transfer with the repair generator.
The string-vacuum selector uses the same bridge only as effective edge-language input; its
critical-worldsheet, Bouchard-Donagi, safety-layer, threshold, and moduli-locking gates do not alter
the four-dimensional compact-gauge mass-gap theorem surface~\cite{ophstringselector}.

\section{Clay Deliverables Checklist}

\begin{longtable}{@{}L{0.30\textwidth}L{0.62\textwidth}@{}}
\toprule
Clay/Jaffe--Witten target & OPH repair-dynamics boundary \\
\midrule
\endhead
Compact simple gauge group \(G\) & \(G\) is arbitrary compact simple, provided it is carried by the OPH compact-gauge zero-obstruction branch. \\
Four-dimensional Euclidean Yang--Mills form & Theorem~\ref{thm:ym-form}, imported from the compact paper's D7 Yang--Mills theorem surface, gives \(S_E[A]=\frac{1}{4g^2}\int_{\R^4}\langle F_{\mu\nu},F_{\mu\nu}\rangle\,d^4x\) under the branch and renormalized identification certificates. \\
Four-dimensional quantum Yang--Mills theory & Proposition~\ref{prop:extraction} proves support-visible projective weak-* / GNS extraction. Renormalized Schwinger convergence, reflection positivity, Euclidean covariance/locality, clustering, nontriviality, and transfer/intertwiner convergence remain conditional on Assumption~\ref{ass:ym-continuum-certificate}. \\
Nontriviality & Conditional on the variance-floor and finite-energy certificate in item (Y6). Finite nonconstant Wilson/plaquette cylinders are candidates; weak-\(*\) convergence alone is not enough. \\
Axiomatic strength & Theorem~\ref{thm:os} states the conditional OS reconstruction step on the support-visible gauge-invariant local algebra. \\
Mass gap & Under the finite ground-state-transform, cross-fiber-rate, commuting-color, and uniform-floor receipts, \(L_r^{\Rep}\ge c_*(I-P_{0,r})\). The continuum Hamiltonian bound \(H\ge c_*(I-P_0^{\Hcal})\) follows only after Theorem~\ref{thm:continuum}. \\
Exact gap accounting & On the certified continuum branch, \(UHU^{-1}=L^{\mathrm{rep}}\) gives \(\Delta_{\YM}=\Delta_{\mathrm{rep}}\). OPH accounts exactly for the Yang--Mills gap as the first nonzero repair eigenvalue only on that branch. \\
Uniformity in \(G\) & The proof uses compact simplicity and compact-gauge quotient locality, not Standard-Model-specific representation data. \\
\bottomrule
\end{longtable}

\section{Conclusion}

The OPH finite repair mechanism for the Yang--Mills mass gap is simple. A non-vacuum
support-visible compact-gauge excitation is not fixed by all local repair collars. At least one
active collar must relax it. Because active collar rates have a uniform positive floor and the
collars can be organized into finitely many commuting colors, every non-vacuum finite-regulator
state pays a positive Euclidean repair cost.

The Clay-facing conclusion is conditional. If the regulator family also satisfies the
renormalized continuum, reflection-positivity, OS, nontriviality, and transfer/intertwiner
certificate of Assumption~\ref{ass:ym-continuum-certificate}, then the continuum compact-gauge
Hamiltonian is unitarily equivalent to the repair generator. On that certified branch the
Yang--Mills gap is the repair gap:

\[
\boxed{
\Delta_{\YM}=\Delta_{\mathrm{rep}}\ge c_*>0.
}
\]

\begin{thebibliography}{99}

\bibitem{oph1}
B.~M\"uller, A.~Osika, M.~Poneder, K.~Xue, B.~Cassie, P.~Nguyen, M.~A.~Visser, K.~A.~Anirudha, D.~Matscheko, and J.~Hill,
\emph{Observers Are All You Need},
2026.\\
Source: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/observers_are_all_you_need.tex}.\\
PDF: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/observers_are_all_you_need.pdf}.

\bibitem{oph2}
B.~M\"uller, A.~Osika, M.~Poneder, K.~Xue, P.~Nguyen, M.~A.~Visser, and D.~Matscheko,
\emph{Recovering Relativity and the Standard Model from Observer Overlap Consistency},
2026.\\
Source: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.tex}.\\
PDF: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.pdf}.

\bibitem{oph3}
B.~M\"uller, A.~Osika, M.~Poneder, K.~Xue, M.~A.~Visser, and D.~Matscheko,
\emph{Deriving the Particle Zoo from Observer Consistency},
2026.\\
Source: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/deriving_the_particle_zoo_from_observer_consistency.tex}.\\
PDF: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/deriving_the_particle_zoo_from_observer_consistency.pdf}.

\bibitem{oph4}
B.~M\"uller, K.~Xue, K.~A.~Anirudha, D.~Matscheko, and J.~Hill,
\emph{Reality as a Consensus Protocol: The Fixed-Point Computation That Implements Physics},
2026.\\
Source: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/reality_as_consensus_protocol.tex}.\\
PDF: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/reality_as_consensus_protocol.pdf}.

\bibitem{oph5}
B.~M\"uller, A.~Osika, K.~Xue, B.~Cassie, M.~A.~Visser, and D.~Matscheko,
\emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer Synchronization in OPH},
2026.\\
Source: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/screen_microphysics_and_observer_synchronization.tex}.\\
PDF: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/screen_microphysics_and_observer_synchronization.pdf}.

\bibitem{ophstringselector}
B.~M\"uller,
\emph{Observer-Patch Holography as a String-Vacuum Selector: Observers, Clocks, Edge Strings, and the Bouchard-Donagi Witness},
2026.\\
Source: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/observer_patch_holography_as_string_vacuum_selector.tex}.\\
PDF: \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/observer_patch_holography_as_string_vacuum_selector.pdf}.

\bibitem{clay}
Clay Mathematics Institute,
``Yang--Mills \& the Mass Gap.''\\
\url{https://www.claymath.org/millennium/yang-mills-the-maths-gap/}.

\bibitem{jaffe-witten}
A.~Jaffe and E.~Witten,
``Quantum Yang--Mills Theory,''
official Clay Mathematics Institute problem description.\\
\url{https://www.claymath.org/wp-content/uploads/2022/06/yangmills.pdf}.

\bibitem{clay-mpp}
J.~Carlson, A.~Jaffe, and A.~Wiles (eds.),
\emph{The Millennium Prize Problems},
Clay Mathematics Institute and American Mathematical Society.\\
\url{https://www.claymath.org/library/monographs/MPPc.pdf}.

\bibitem{osterwalder-schrader1}
K.~Osterwalder and R.~Schrader,
``Axioms for Euclidean Green's functions,''
\emph{Communications in Mathematical Physics} \textbf{31} (1973), 83--112.

\bibitem{osterwalder-schrader2}
K.~Osterwalder and R.~Schrader,
``Axioms for Euclidean Green's functions II,''
\emph{Communications in Mathematical Physics} \textbf{42} (1975), 281--305.

\bibitem{peter-weyl}
F.~Peter and H.~Weyl,
``Die Vollst\"andigkeit der primitiven Darstellungen einer geschlossenen kontinuierlichen Gruppe,''
\emph{Mathematische Annalen} \textbf{97} (1927), 737--755.

\bibitem{gross-taylor}
D.~J.~Gross and W.~Taylor,
``Two-dimensional QCD is a string theory,''
\emph{Nucl.\ Phys.\ B} \textbf{400} (1993), 181--208,
arXiv:hep-th/9301068.

\end{thebibliography}

\end{document}
