\section{Supplemented Gravity and Structural Gauge Details}
\label{app:compact-technical-port}

This appendix carries the gravity-side and structural gauge items that support the compact paper's
technical surface. They sharpen the compact paper's Lorentz,
Einstein, cosmological-constant, and product-group claim surfaces without widening the recovered
core beyond its stated branch conditions.

\subsection{Lorentz and Einstein Bridge}

\begin{theorem}[Conformal group isomorphism]
The orientation-preserving conformal group of \(S^2\) is isomorphic to the connected Lorentz
group:
\[
\mathrm{Conf}^+(S^2)\cong \mathrm{PSL}(2,\mathbb C)\cong \mathrm{SO}^+(3,1).
\]
\end{theorem}

\begin{theorem}[Support-visible geometric modular flow on caps on the extracted prime geometric subnet]
Assume the OPH axioms, the derived fixed-cutoff collar package, and the support-visible BW
scaling theorem on the extracted prime geometric subnet. Then the scaling-limit modular
automorphism group of the cap pair is geometric conformal dilation on that
subnet, with the standard \(2\pi\) normalization supplied by the finite cap-normal certificate.
If the emitted scaling-limit cap algebra is type I, this may be written as
\(K_C=2\pi B_C+Z_C\) with \(Z_C\) central; in the generic continuum case the theorem is the
automorphism statement on a non-type-I cap algebra with outer geometric modular action. The collar
replacements used in this branch are exact only at exact Markovity or in
controlled fixed-collar families with \(\delta^{\mathrm M}\to0\); small CMI supplies a
Fawzi--Renner recovered comparison state, not a dimension-free one-shot exact Markov normal form.
\end{theorem}

\begin{definition}[BW-branch observer-relative time reading]
On the branch satisfying the hypotheses of the preceding geometric modular-flow theorem, OPH uses
the modular automorphism parameter \(t\) of the extracted cap pair as that cap observer's relative
time parameter. This is a declared BW-branch reading of the derived geometric modular flow; it is
not an additional proof that arbitrary operational clocks, global time, or the full problem of time
have been derived from the axioms.
\end{definition}

\paragraph{BW-side UV scaffold.}
The UV data on this branch are not a separate cap-isotropy or Euclidean-regularity
selector. The fixed-cutoff cap algebras are type-I regulators, but the scaling-limit observer
algebra may leave that class, and MaxEnt alone does not select the BW / canonical cap phase. The
UV package is the realized transported geometric cap-local system together with the
carried-collar schedule derived from the transported fixed-local-collar Markov/faithfulness datum
on each fixed local collar model, followed by support-readable modular covariance and ordered
cut-pair rigidity on the emitted scaling-limit geometric cap pair.

\paragraph{Null-strip completion boundary.}
On the D4 side, the fixed-cutoff strip package is more specific than the generic inherited-strip summary.
The null cuts first transfer the same cut-center data as the spatial collar branch, which fixes
the central sector-pair decomposition of the strip algebra. The stronger left/right tensor
decomposition used by the null modular bridge then requires the extra inherited strip-split
condition on the multiplicity spaces, together with the exact-or-controlled Markov hypotheses on
one fixed inherited strip model. On that same fixed strip model, the renormalized half-line family
is endpoint-Lipschitz, hence defines the weak tail generator, and on the scaling-limit
geometric-cap branch the half-line blow-up net carries the derived half-sided modular pair.
Borchers--Wiesbrock then supplies the positive null-translation generator on its Stone domain
together with the affine half-line modular relation \(K_a(\Omega)=K_0(\Omega)-2\pi aP_\Omega\),
and the same half-line family fixes the generator/charge identification internally.
Bounded-interval formulas are downstream of the E0.5 affine/projective kernel in the Einstein bridge.

\begin{lemma}[Null data ambiguity]
If a symmetric tensor \(X_{ab}\) satisfies
\[
X_{ab}k^ak^b=0
\]
for every null vector \(k\), then \(X_{ab}=\phi\,g_{ab}\) for some scalar \(\phi\).
\end{lemma}

\begin{corollary}[Null modular data determine Einstein only up to the metric term]
Null modular data determine \(T_{ab}\) only up to \(\phi g_{ab}\). Consequently the Einstein
equation is fixed locally only up to \(\Lambda g_{ab}\).
\end{corollary}

\begin{theorem}[Jacobson-type rest-frame relation]
In the local Lorentzian scaling regime, once the realized cap-label-preserving MaxEnt family satisfies the derived fixed-cap generalized-entropy stationarity theorem for admissible fixed-cap variations, the half-line
generator/charge identification of the null bridge, the bounded-interval transport input used in
the local Lorentzian regime, and the internal small-ball bridge yield the rest-frame first-variation
relation that drives the compact paper's local Einstein branch; on the same scaling branch, if that
rest-frame relation holds for all local observer four-velocities and all reference states, the
compact paper upgrades it to the full tensor equation by the explicit local quadratic-polarization
argument of Corollary~\ref{cor:einstein}.
\end{theorem}

\begin{theorem}[Newton coupling from the scale certificate and edge entropy density]
The geometric coupling read by the Newton area law is
\[
G_{\mathrm{geom}}=\frac{a_{\mathrm{cell}}}{4\bar{\ell}(t)}.
\]
On the OPH gravity row the scale is supplied first by
\(\gamma_\star=\ell_\star\nu_{\mathrm{Cs}}/c\), equivalently
\(B_\star=3\pi/\ell_\star^2\), as an independent scale certificate rather than a consequence of
\(P_\star\) and \(N_\star\) alone. With
\(a_{\mathrm{cell}}=P\ell_\star^2\) and \(\bar{\ell}_{\mathrm{shared}}=P/4\), this gives
\[
G_{\mathrm{geom}}=\ell_\star^2,
\qquad
G_{\mathrm{SI}}=\frac{c^3\ell_\star^2}{\hbar}.
\]
Here \(\bar{\ell}_{\mathrm{shared}}\) is a shared-cut density. It is not the logarithm of an
independent cell Hilbert-space dimension and does not select a fixed primitive observer capacity.
\end{theorem}

\subsection{Cosmological-Constant / Screen-Capacity Closure}

\begin{lemma}[Vacuum energy blindness]
For any null vector \(k\),
\[
T^{\mathrm{vac}}_{kk}
=
T^{\mathrm{vac}}_{ab}k^ak^b
=
-\rho_{\mathrm{vac}}\,g_{ab}k^ak^b
=
0.
\]
Vacuum-energy contributions therefore lie in the kernel of the null map
\(T_{ab}\mapsto T_{kk}\).
\end{lemma}

\begin{proposition}[Structural separation]
Within the structural split used here:
\begin{enumerate}[leftmargin=2em]
\item local modular/null data fix \(T_{ab}\) only up to \(\phi g_{ab}\); and
\item the dimensionless \(\Lambda\)-capacity relation is fixed by global screen capacity, not by local null data.
\end{enumerate}
So the large vacuum-energy bookkeeping of EFT is not itself the local quantity determining
curvature on this branch.
\end{proposition}

\begin{theorem}[No local \(\Lambda\) prediction]
Within the null-modular reconstruction used here:
\begin{enumerate}[leftmargin=2em]
\item all \(T_{kk}\) data are unchanged under \(T_{ab}\to T_{ab}+\phi g_{ab}\);
\item therefore \(\Lambda\) cannot be fixed by local overlap consistency alone; and
\item the dimensionless \(\Lambda\)-capacity relation requires the global screen-capacity closure that closes the same Einstein branch beyond the local null data; the intended self-closure is the cosmic record-closure fixed point \(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})\) (readback map constructed conditionally by the coupling theorem G2-GAP-1, proven modulo the declared premises CP-1 to CP-3; CL-7), with \(N_\star\) as its count-density representation, and SI curvature values additionally use the selected scale certificate.
\end{enumerate}
\end{theorem}

\begin{corollary}[Benchmark cosmological readout on the D6 branch]\label{cor:lambda-benchmark}
On the same D6 branch as Corollaries~\ref{cor:lambda}--\ref{cor:lambda-parameters}, inserting the observed value \(\Lambda\approx 1.09\times 10^{-52}\,\mathrm{m^{-2}}\) gives
\[
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}}\approx 1.66\times 10^{26}\ \mathrm{m},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c}\approx 17.5\ \mathrm{Gyr},
\]
\[
N_{\mathrm{patch}}=\left(\frac{r_{\mathrm{dS}}}{\ell_P}\right)^2
\approx 1.05\times 10^{122},
\qquad
N_{\mathrm{scr}}=S_{\mathrm{dS}}=\pi N_{\mathrm{patch}}
\approx 3.31\times 10^{122},
\]
\[
\Lambda\ell_P^2\approx 2.85\times10^{-122}.
\]
\end{corollary}

\begin{proof}
Immediate from Corollary~\ref{cor:lambda-parameters}.
\end{proof}

\paragraph{Observed-age benchmark boundary.}
The branch quantity \(t_\Lambda\) is the de Sitter static-patch timescale. The usual cosmic age \(t_0\) is a compare-only FLRW benchmark, with no additional D6 theorem output. On the flat \(\Lambda\)CDM benchmark
\[
t_0=\frac{2}{3H_0\sqrt{\Omega_\Lambda}}
\sinh^{-1}\!\left(\sqrt{\frac{\Omega_\Lambda}{\Omega_m}}\right)
\]
one gets the standard comparison value \(t_0\approx 13.8\,\mathrm{Gyr}\) at
\(H_0\approx 67.4\,\mathrm{km\,s^{-1}\,Mpc^{-1}}\) and \(\Omega_\Lambda\approx 0.685\).

\begin{lemma}[FLRW curvature as visible scalar holonomy]
On a homogeneous-isotropic spatial slice with constant sectional curvature \(K\), small spatial
loop holonomy obeys
\[
\operatorname{Hol}_{\Box_{uv}}=\exp\!\left(KA_\Box J_{uv}+O(A_\Box^{3/2})\right).
\]
On a visibly separated OPH refinement system, the refinement-limit scalar spatial holonomy vanishes
if and only if \(K=0\). Thus a flat FLRW branch is the zero-visible-spatial-holonomy branch.
\end{lemma}

\paragraph{Flatness boundary.}
This holonomy statement names a conditional cosmology bridge only. It does not add a D6 theorem
output and does not solve the inflationary flatness or horizon problems. Selecting \(K=0\) requires
an additional continuation theorem or premise: a direct flatness theorem, a conditional
cosmological-minimal-holonomy selector on a clocked FLRW boundary, or an explicit flat-branch
assumption. Minimal Admissible Realization (MAR) acts on low-energy gauge/matter packages and is not a cosmological flatness
selector.

\begin{theorem}[D5--D6 cosmological-capacity closure stack]
Assume the compact paper's local Einstein branch, the cosmic record-capacity fixed point
\[
N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}}),
\]
its observed-branch de Sitter entropy readout
\[
N_{\mathrm{CRC}}=S_{\mathrm{dS}},
\]
\noindent the standard de Sitter entropy relation
\[
S_{\mathrm{dS}}=\frac{A_{\mathrm{dS}}}{4G}=\frac{3\pi}{G\Lambda},
\]
and the standard static-patch formulas
\[
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c}.
\]
Then the cosmological-constant package is one local/global theorem stack: local null data fix the
Einstein branch only modulo \(\Lambda g_{ab}\), and with the selected scale certificate the same branch
has the global display
\[
G_{ab}+\frac{3\pi}{G N_{\mathrm{CRC}}}\,g_{ab}=8\pi G\,\langle T_{ab}\rangle,
\]
while the D6 closure itself fixes the entropy and dimensionless capacity relations
\[
S_{\mathrm{dS}}=N_{\mathrm{CRC}},
\qquad
A_{\mathrm{dS}}=4G N_{\mathrm{CRC}},
\qquad
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c},
\]
and the observed cosmic age is a downstream FLRW benchmark, with no additional theorem
output.
\end{theorem}

\paragraph{Scope boundary.}
The D6 hypotheses are exactly the D5 local Einstein branch, the cosmic record-capacity fixed point
\(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})\), its observed-branch de Sitter entropy readout
\(N_{\mathrm{CRC}}=S_{\mathrm{dS}}\), the standard de Sitter entropy relation, and the standard
static-patch formulas. The local null-data route does not by itself determine the global capacity;
that value is fixed by the readback closure. The capacity closure fixes
\(\Lambda_{\mathrm{CRC}}\ell_\star^2=3\pi/N_{\mathrm{CRC}}\); the SI static-patch scale
additionally requires the selected scale certificate. CMB kernels, inflation-replacement claims,
\(H_0/S_8\) branches, dark/anomaly growth kernels, and baryogenesis continuations require separate
continuation theorems or likelihood contracts.

\begin{theorem}[Conditional OPH screen-spectrum theorem]\label{thm:compact-conditional-screen-spectrum}
Let \((\mathcal S_r)\) be a cofinal finite spherical OPH screen system with a
schedule-independent quotient-normal-form scalar \(q_r\), removal of the background and dipole
sector, and a target-free positive quadratic repair operator \(K_r\). If \(K_r\to K\), the finite
scalar release energy satisfies \(E_r/d_r\to A_q\), and local MaxEnt is imposed at fixed expected
quadratic release energy, then \(q_r\) converges in finite harmonic distributions to the centered
Gaussian screen field with covariance \(A_qK^{-1}\). Exact per-sample release energy would instead
give a microcanonical ellipsoid. If the certified repair-scale measure is
\(t^{\theta/2}\,dt/\Gamma(1+\theta/2)\), then
\[
K_{\rm asy}=(-\Delta_{S^2})^{1+\theta/2},
\qquad
C_{\ell,{\rm asy}}^q=A_q[\ell(\ell+1)]^{-1-\theta/2},
\]
as the large-\(\ell\) asymptotic model.  The theorem-grade finite-\(\ell\) conformal-shell family
uses the normalized gamma-ratio precision
\[
\kappa_\ell(\theta)=
\frac{\Gamma(\ell+2+\theta/2)}{\Gamma(\ell-\theta/2)},
\]
with
\[
C_\ell^q=A_q\frac{\Gamma(\ell-\theta/2)}{\Gamma(\ell+2+\theta/2)}.
\]
If \(q\) is additionally certified as the thin-shell pullback of a homogeneous curvature field with
\(\Delta_\zeta^2(k)=A_\zeta(k/k_\star)^{-\theta}\), the corresponding inverse amplitude relation is
\[
A_\zeta=
\frac{A_q^{\rm shell}\Gamma(3/2+\theta/2)}
{\pi^{3/2}Z_\star^2(k_\star D_\star)^\theta\Gamma(1+\theta/2)}.
\]
The numerical value of \(\theta\), the expected quadratic release energy, and the lift normalization remain
conditional on their finite certificates. A Fawzi--Renner/Markov-collar observable estimate gives an
upper bound on release observables, not an amplitude equality. No physical TT/TE/EE statement
follows without independent Boltzmann transfer and likelihood closure.
\end{theorem}

\paragraph{Screen-spectrum boundary.}
The theorem licenses a Phase III conditional continuation only. A derived screen spectrum requires
the quotient-normal-form scalar field, positive repair operator, operator-tilt, and scalar-release
energy receipts. A derived primordial curvature spectrum additionally requires the radial lift
receipt: the heuristic \(\ell\simeq kD_\star\) assignment is only a scaffold, while the exact
thin-shell power-law lift uses the gamma-ratio operator above and finite-width windows require their
own Bessel-kernel error certificate.

\paragraph{Separate pixel-side benchmarks.}
The companion pixel numbers
\[
a_{\mathrm{cell}}\approx 1.63\,\ell_\star^2,
\qquad
\ell_{\mathrm{UV}}=\sqrt{a_{\mathrm{cell}}}\approx 1.28\,\ell_\star,
\qquad
\bar{\ell}\approx 0.408
\]
belong to the separate pixel-closure/local-readout package, outside the D6 cosmological-parameter corollary itself. After the selected scale certificate is supplied, \(\ell_\star\) is displayed as the usual Planck length.

\subsection{Product-Group Structural Corollaries}

\begin{theorem}[Factorization equivalence]
\[
\text{Factorizing edge weights}
\Longleftrightarrow
\text{Additive boundary Laplacian}
\Longleftrightarrow
\text{Product gauge group}.
\]
If
\[
H_\partial=H_\partial^{(1)}+H_\partial^{(2)}+H_\partial^{(3)}
\qquad\text{with}\qquad
[H_\partial^{(i)},H_\partial^{(j)}]=0,
\]
then
\[
p(R_1,R_2,R_3)\propto\prod_{i=1}^3 d_{R_i}e^{-t_iC_2(R_i)}.
\]
Applied to the assumed transportable refinement-directed edge-sector colimit on the realized
branch, together with the rigid symmetric
\(C^*\)-tensor and faithful bosonic fiber-functor conditions of the compact-gauge theorem,
Tannaka--Krein reconstruction first yields some compact group \(G\). Under the MAR admissibility
package, and once the admissible class includes one connected abelian charge factor, the selected
connected Lie realization is \(SU(3)\times SU(2)\times U(1)\) up to finite quotient.
\end{theorem}

\begin{corollary}[No leptoquarks, hence no gauge-mediated proton decay]
With product gauge group, the adjoint representation of the full connected gauge group is
\[
(8,1,0)\oplus(1,3,0)\oplus(1,1,0),
\]
equivalently the derived nonabelian adjoint is
\[
(8,1,0)\oplus(1,3,0).
\]
There are therefore no gauge generators in mixed representations \((3,2,\pm 5/6)\), i.e. no
simple-GUT \(X,Y\) bosons on the realized branch. The structural claim is exactly
\[
\tau_p^{(\mathrm{gauge})}=\infty,
\]
{\emergencystretch=8em\relax meaning that the gauge-boson proton-decay channel is absent. Scalar-mediated or
higher-dimensional baryon-violating operators are outside this structural corollary.\par}
\end{corollary}

\paragraph{Proton-spin continuation benchmark.}
On the realized D8--D9 branch the color factor is \(\mathrm{SU}(3)\), so the structural OPH
input for proton-spin bookkeeping is
\[
C_F=\frac43,
\qquad
C_A=3.
\]
If one adds the QCD-dependent continuation ansatz that quark/gluon spin sharing equilibrates
according to these Casimirs, then
\[
\Delta\Sigma\approx \frac{C_F}{C_F+C_A}=\frac{4}{13}\approx 0.308.
\]
Against a representative lattice benchmark \(\Delta\Sigma\approx 0.286\), this lands within about
\(8\%\), but it is only a deferred continuation benchmark. A first-principles OPH derivation of
proton spin would require the nonperturbative light-quark/hadron completion plus an explicit map
from OPH data to renormalized proton matrix elements.

\subsection{Controlled Worldsheet Effective Description}

\paragraph{Exact OPH-to-2D-Yang--Mills bridge.}
On the compact-group heat-kernel branch, Theorem~\ref{thm:edge-2dym} proves the exact identity
\[
Z_{\mathrm{edge}}(t)=K_t(1)
\]
by gluing the open-edge weights \(p_R(t)\propto d_R e^{-tC_2(R)}\) into the closed partition sum
\[
Z_{\mathrm{edge}}(t)=\sum_R d_R^2 e^{-tC_2(R)}.
\]
This is the precise theorem-level sense in which the OPH edge-sector partition reorganizes into
the two-dimensional Yang--Mills heat-kernel surface, and the Chapman--Kolmogorov law supplies the
matching collar-sewing rule.
This bridge is a two-dimensional heat-kernel partition identity on the stated compact-group
branch. The four-dimensional compact-gauge repair-gap theorem is the separate support-visible
result in Theorem~\ref{thm:oph-yang-mills-gap}.

\paragraph{Large-\(N_{\mathrm{edge}}\) boundary.}
The large-\(N_{\mathrm{edge}}\)
worldsheet interpretation is carried only when one fixes a distinct large-\(N_{\mathrm{edge}}\)
sequence, with \(N_{\mathrm{edge}}\neq N_c=3\), a fixed-\(\tau\) window for
\[
\tau=tN_{\mathrm{edge}},
\]
and the uniform genus-remainder control of Theorem~\ref{thm:worldsheet-largeN}. On that branch the
edge free energy satisfies the compact paper's theorem-level criterion for a controlled genus
expansion, so the standard Gross--Taylor rewriting becomes a controlled worldsheet effective
description of edge dynamics.

\paragraph{External items.}
The exact bridge theorem uses the compact-group heat-kernel branch and the quadratic-Casimir
normalization declared in the compact paper. The continuation theorem uses the declared
large-\(N_{\mathrm{edge}}\) regime and the imported Gross--Taylor large-\(N\) worldsheet dictionary
for two-dimensional Yang--Mills. It does not identify a critical worldsheet CFT. Worldsheet
supersymmetry, critical dimension, modular invariance, anomaly cancellation, GSO projection, and
full massless-spectrum matching use separate continuation inputs beyond the compact recovered-core
chain.

\subsection{Support-Visible Yang--Mills Gap from Repair Dynamics}
\label{app:yang-mills-repair-gap}

\begin{assumption}[Support-visible compact-gauge Yang--Mills branch]
\label{ass:oph-yang-mills-branch}
The compact-gauge branch used in this subsection is the ordinary or central zero-obstruction
compact-gauge sector with compact simple structure group \(G\), a four-dimensional Euclidean
scaling chart, and a cofinal tail carrying the compact-gauge refinement receipt of
Definition~\ref{def:compact-gauge-refinement-receipt}. It also has a reflection-positive ordinary
vacuum, topological angle \(\theta=0\), gauge-invariant
local finite-constraint MaxEnt/Gibbs refinement, no additional relevant dimension-four pure-gauge
operator on the branch besides the positive quadratic curvature invariant, active exact-Markov
repair collars, bounded-color collar covers, and repair completeness. It is carried on the
separated cofinal regulator system of Theorem~\ref{thm:consensusrefinement}. No continuum
cylinder state, GNS space, transfer generator, or vacuum projection is included in this
assumption; those objects are constructed, or separately certified, below.
\end{assumption}

\begin{definition}[Finite support-visible compact-gauge cylinder system]
\label{def:finite-compact-gauge-cylinder-system}
At regulator \(r\), make the following construction twice: for the finite four-dimensional
Euclidean slab \(\Lambda_r^{(4)}=(V_r^{(4)},E_r^{(4)})\) cut out by the scaling chart, and for its
time-zero spatial slice \(\Lambda_r^{(0)}=(V_r^{(0)},E_r^{(0)})\). In the formulas below,
\(\Lambda_r=(V_r,E_r)\) denotes either choice and the superscript is restored whenever the two
must be distinguished. Let \(D_r\) be the finite collection of repaired collar records and
zero-obstruction sector labels retained by the compact-gauge patch carrier. In the gauge-register
presentation, let
\[
\widetilde X_r\subseteq G^{E_r}\times D_r
\]
be the closed set satisfying the finite Gauss, overlap, and repaired-record constraints, let
\(\mathcal G_r=G^{V_r}\) act by endpoint gauge transformations, and let
\(\sim_{\mathrm{ov}}\) be the closed equivalence relation of support-visible
overlap/presentation indistinguishability. The finite-stage support-visible configuration space is
\[
X_r:=(\widetilde X_r/\mathcal G_r)/{\sim_{\mathrm{ov}}}.
\]
Thus \(X_r\) is compact
Hausdorff. ``Finite stage'' means that \(\Lambda_r\) and \(D_r\) are finite; \(X_r\) need not be
a finite set when \(G\) is a compact Lie group. A finite quantum-link truncation gives the same
commuting Euclidean readout algebra after restriction to its joint cylinder spectrum; no
noncommutative support-quotient claim is made here.

For each active collar \(C\), let
\[
\rho_{C,r}:X_r\longrightarrow Y_{C,r}
\]
be the continuous complete repaired readback. On the classical compact-holonomy branch used by
the repair lemma, the complementary conditional fiber contains every record or holonomy coordinate
actually resampled by collar repair. It is either finite with its uniform conditional law or a
standard atomless probability space with its conditioned MaxEnt/Haar law. The complete readback
retains exactly the fixed repaired datum, not every pre-repair holonomy; otherwise nonconstant
Wilson cylinders would incorrectly lie in the repair kernel.

For a bounded cell region \(O\subset\Lambda_r\), let
\(\mathfrak C_r^{G,\mathrm{sv}}(O)\) be the unital \(^*\)-algebra generated by
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=2em]
\item contracted Peter--Weyl spin-network functions, Wilson-loop characters, and any explicitly
retained gauge-invariant boundary-carrier contractions supported in \(O\);
\item the overlap-sector projectors whose collars lie in \(O\); and
\item continuous functions of the complete repaired readbacks \(\rho_{C,r}\) for those collars.
\end{enumerate}
Its uniform closure
\[
\mathcal A_r^{G,\mathrm{sv}}(O)
:=\overline{\mathfrak C_r^{G,\mathrm{sv}}(O)}^{\|\cdot\|_\infty}
\subseteq C(X_r)
\]
is the finite-stage local cylinder algebra. Equivalently, start from the freely presented
readout-generator \(^*\)-algebra and quotient by the kernel of its evaluation homomorphism on
\(X_r\), then complete. That kernel is a closed two-sided overlap-trivial ideal fixed before a
state is chosen.
The relation \(\sim_{\mathrm{ov}}\) identifies exactly the configurations on which all declared
spin-network, sector, and repaired-readback generators agree. These generators are self-adjoint,
contain the constants, and therefore separate points of \(X_r\). Stone--Weierstrass gives
\[
\mathcal A_r^{G,\mathrm{sv}}(\Lambda_r)=C(X_r).
\]
Consequently, for any selected stage measure \(\pi_r\), their GNS cylinder closure is the full
\(L^2(X_r,\pi_r)\) after the finite \(\pi_r\)-null support reduction.

Write the resulting spaces and algebras as
\[
(X_r^{(4)},\mathcal A_r^{G,\mathrm{sv},(4)}(O))
\quad\hbox{and}\quad
(X_r^{(0)},\mathcal A_{r,0}^{G,\mathrm{sv}}(B)).
\]
Restriction of a Euclidean history to the time-zero slice gives a continuous map
\[
\tau_{0,r}:X_r^{(4)}\longrightarrow X_r^{(0)}
\]
and the corresponding pullback embeds time-zero cylinders into four-dimensional cylinders.

For \(r\preceq s\), the deterministic coarse shadow multiplies the ordered fine-edge
holonomies lying over each coarse edge, restricts collar readbacks, and sends a fine sector label
to its coarse shadow. Gauge covariance makes this a map
\[
p_{sr}:X_s\longrightarrow X_r,
\qquad
p_{tr}=p_{sr}\circ p_{ts}\quad(r\preceq s\preceq t).
\]
The four-dimensional and time-zero coarse shadows satisfy the finite commuting square
\[
\tau_{0,r}p_{sr}^{(4)}=p_{sr}^{(0)}\tau_{0,s}.
\]
On local cylinders it gives the unital \(^*\)-map
\[
\iota_{rs}^{O}:\mathcal A_r^{G,\mathrm{sv}}(O)\longrightarrow
\mathcal A_s^{G,\mathrm{sv}}(O_s),
\qquad
\iota_{rs}^{O}(a)=a\circ p_{sr}.
\]
On the compact-gauge refinement branch, the sector-projector part must agree with the separately
supplied block-multiplicity injection \(\jmath_{rs}^{B}\) of
Definition~\ref{def:compact-gauge-refinement-receipt}; it is not inferred from the deterministic
coarse-shadow map. The holonomy and readback parts are its declared compatible extension. The maps
preserve isotony and obey
\[
\iota_{rt}^{O}=\iota_{st}^{O_s}\iota_{rs}^{O}.
\]
If every coarse configuration on the selected branch has a fine extension, \(p_{sr}\) is
surjective and \(\iota_{rs}^{O}\) is injective. Without that finite extendability receipt, the
\(C^*\)-inductive limit quotients the common refinement-null kernel; the extraction proof below
does not assume prelimit injectivity of the full cylinder map. That broader quotient extraction is
not, by itself, the receipt-certified sector ladder of
Theorem~\ref{thm:refinement-functor-fiber-descent}.
Write \(\mathcal A_r^{G,\mathrm{sv}}:=
\mathcal A_r^{G,\mathrm{sv}}(\Lambda_r)\).
Choose a countable cofinal regulator sequence and a countable bounded-region exhaustion of the
four-dimensional chart. This is the cylinder family used below. For a non-countable regulator
presentation, the same construction uses the full directed family and a subnet instead of this
cofinal sequence.
\end{definition}

\begin{proposition}[Projective compact-gauge cylinder extraction]
\label{prop:compact-gauge-extraction-yang-mills}
For every regulator \(s\), let \(\mu_s^{(4)}\) be the declared finite quotient-Gibbs probability
measure on \(X_s^{(4)}\), let
\[
\pi_s:=(\tau_{0,s})_\#\mu_s^{(4)}
\]
be its stationary time-zero marginal on \(X_s^{(0)}\), and put
\(\mu_s^{(0)}:=\pi_s\). For \(d\in\{4,0\}\), write
\[
\omega_s^{(d)}(a):=\int_{X_s^{(d)}}a\,d\mu_s^{(d)},
\qquad
\omega_{s\downarrow r}^{(d)}
:=\omega_s^{(d)}\circ\iota_{rs}^{(d)}.
\]
The statements below hold for both \(d=4\) and \(d=0\); the superscript is suppressed in the
displayed proof.
Then the following statements hold.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2em]
\item The marginals of any one fine state are exactly projective: for
\(q\preceq r\preceq s\),
\[
\omega_{s\downarrow r}\circ\iota_{qr}=\omega_{s\downarrow q}.
\]
\item There is a cofinal subsequence, or a cofinal subnet in the general directed case, and states
\(\overline\omega_r\in S(\mathcal A_r^{G,\mathrm{sv}})\) such that
\[
\omega_{s_\alpha\downarrow r}\xrightarrow[\alpha]{}\overline\omega_r
\quad\hbox{weak-*}
\]
on every fixed local cylinder algebra. The limit family is projective:
\[
\overline\omega_r=\overline\omega_t\circ\iota_{rt}
\qquad(r\preceq t).
\]
\item The compatible local states define a state \(\omega_\infty\) on the algebraic inductive
limit and extend uniquely to its local \(C^*\)-completion
\[
\mathcal A_\infty^{G,\mathrm{cyl}}(O)
:=\overline{\varinjlim_r\mathcal A_r^{G,\mathrm{sv}}(O_r)}.
\]
The resulting local algebras are isotone and their union is dense in the global cylinder algebra.
\item Let \(\mathcal N_\omega(O)\) be the null ideal of the limiting cylinder measure,
\[
\mathcal N_\omega(O)
:=\{a\in\mathcal A_\infty^{G,\mathrm{cyl}}(O):
\omega_\infty(a^*a)=0\}.
\]
Because the Euclidean cylinder algebra is commutative, this is a closed two-sided ideal. On
\[
\mathcal A_\infty^{G,\mathrm{supp}}(O)
:=\mathcal A_\infty^{G,\mathrm{cyl}}(O)/\mathcal N_\omega(O)
\]
the induced state is faithful. The local GNS spaces glue isometrically, their local cylinder
images have dense union, and their Hilbert direct limit is the GNS space
\((K^{(d)},\Pi^{(d)},\mathbf 1^{(d)})\) of \(\omega_\infty^{(d)}\). Denote the
four-dimensional Euclidean cylinder GNS space by \(K^E:=K^{(4)}\) and the time-zero repair GNS
space by \(K:=K^{(0)}\). Each is a faithful cyclic GNS pair on its support quotient; the
time-zero vector is identified as the physical vacuum only by the transfer/OS receipt below.
\end{enumerate}
If, in addition, the finite four-dimensional quotient presentation satisfies the fiber-sum
identity stated after Axiom~\ref{ax:maxent}, then
\((p_{sr}^{(4)})_\#\mu_s^{(4)}=\mu_r^{(4)}\). The time-zero commuting square gives
\((p_{sr}^{(0)})_\#\pi_s=\pi_r\), so both original state families are projective. Without that
finite receipt, the bars on
\(\overline\omega_r\) are essential: compactness extracts a projective cluster family but does
not turn the originally chosen coarse Gibbs measures into an exactly projective family. In the
continuous compact-holonomy presentation, the corresponding receipt is the pushforward identity
\((p_{sr}^{(4)})_\#\mu_s^{(4)}=\mu_r^{(4)}\), expressed through disintegration rather than a
finite sum.
\end{proposition}

\begin{proof}
Functoriality of the coarse shadows gives
\[
(\omega_s\circ\iota_{rs})\circ\iota_{qr}
=\omega_s\circ\iota_{qs},
\]
which proves \textup{(i)} without a continuum assumption.

For each fixed cylinder algebra, its state space is weak-* compact by Banach--Alaoglu. The
algebras in the chosen cylinder exhaustion are separable: compact metrizable \(G\) has a
countable Peter--Weyl test algebra, and only finitely many readbacks and sector projectors occur at
one stage. Their state spaces are therefore weak-* metrizable. Starting with the first cylinder,
extract a subsequence on which its marginals converge; from that subsequence extract one
for the second cylinder, and continue. Choose the \(k\)-th diagonal index beyond the \(k\)-th
regulator stage. The resulting diagonal subsequence is cofinal and converges on every cylinder. In
the general directed presentation, compactness of the product of the local state spaces gives the
same conclusion with a cofinal subnet: unresolved early coordinates may be filled by arbitrary
states because every fixed coordinate is genuinely resolved on a cofinal tail. For
\(q\preceq r\), weak-* continuity of precomposition
by \(\iota_{qr}\), together with \textup{(i)}, gives
\[
\overline\omega_r\circ\iota_{qr}
=\lim_\alpha\omega_{s_\alpha\downarrow r}\circ\iota_{qr}
=\lim_\alpha\omega_{s_\alpha\downarrow q}
=\overline\omega_q.
\]
This proves \textup{(ii)}.

If \(a\in\mathcal A_r^{G,\mathrm{sv}}\) represents an element \([a]_r\) of the algebraic
inductive limit, set
\[
\omega_\infty([a]_r):=\overline\omega_r(a).
\]
Projectivity makes this independent of the representative. Positivity and normalization hold at
the finite stage containing any given algebraic element. Moreover, for every \(t\succeq r\),
\[
|\overline\omega_r(a)|
=|\overline\omega_t(\iota_{rt}(a))|
\le\|\iota_{rt}(a)\|.
\]
Taking the infimum along the directed tail gives the \(C^*\)-inductive-limit norm bound, including
when the maps are noninjective. Hence the state extends uniquely to the completion. The
same construction region by region proves isotony and density, giving \textup{(iii)}.

By the Riesz representation theorem, a commutative local limiting state is integration against a
Radon probability measure \(\mu_O\). Its null ideal consists precisely of the continuous functions
vanishing on the measure support, so the quotient is canonically \(C(\operatorname{supp}\mu_O)\)
and the induced state is faithful. If \(O\subseteq O'\) and \(\iota_{OO'}\) is the local
inclusion, state compatibility gives
\[
a\in\mathcal N_\omega(O)
\quad\Longleftrightarrow\quad
\iota_{OO'}(a)\in\mathcal N_\omega(O').
\]
Thus the local inclusions descend to injective maps of the support quotients, which therefore form
an isotone faithful local net. For \(r\preceq t\), projectivity makes
\[
V_{rt}:K_{\overline\omega_r}\longrightarrow K_{\overline\omega_t},
\qquad
V_{rt}[a]_r=[\iota_{rt}(a)]_t
\]
well defined and isometric, because
\[
\|V_{rt}[a]_r\|^2
=\overline\omega_t(\iota_{rt}(a^*a))
=\overline\omega_r(a^*a).
\]
The maps compose, preserve \(\mathbf 1\), and intertwine left multiplication. Their Hilbert
direct limit is therefore the GNS completion of the algebraic cylinder union and has dense local
images. This proves \textup{(iv)}. Finally, suppressing the \(d=4\) superscript, the finite
fiber-sum identity gives
\[
Z_s=\sum_{x\in X_r}\sum_{x':p_{sr}(x')=x}m_s(x')e^{-S_s(x')}
=\alpha_{sr}Z_r,
\]
and hence
\[
(p_{sr})_\#\mu_s(x)
=\frac{\alpha_{sr}m_r(x)e^{-S_r(x)}}{\alpha_{sr}Z_r}
=\mu_r(x).
\]
This is equivalent to \(\omega_s^{(4)}\circ\iota_{rs}^{(4)}=\omega_r^{(4)}\); the commuting
time-zero square gives the corresponding identity for \(d=0\).
\end{proof}

\begin{remark}[Two different quotients]
\label{rem:compact-gauge-two-quotients}
The overlap-trivial presentation ideal in
Definition~\ref{def:finite-compact-gauge-cylinder-system} is not the GNS null ideal
\(\mathcal N_\omega(O)\). The former removes data that no support-visible readout can distinguish
before a state is selected; the latter removes directions that have zero norm in the extracted
state. Faithful finite-stage states can have a nonfaithful weak-* limit, so quotienting only the
overlap-trivial ideal would not prove faithfulness of the limiting pair.
\end{remark}

\begin{assumption}[Renormalized four-dimensional Yang--Mills identification receipt]
\label{ass:compact-gauge-ym-identification}
On the selected four-dimensional cluster family, compatible renormalized holonomy cylinders obey
uniform local Cauchy and regularity bounds. Their infinitesimal rectangle tests converge, in the
declared distributional sense, to a connection/curvature pair
\[
U_{\mu\nu}(\varepsilon,x)
=\mathbf 1+\varepsilon^2F_{\mu\nu}(x)+O(\varepsilon^3),
\qquad
F=dA+A\wedge A.
\]
The renormalized local actions converge to the unique reflection-even positive
dimension-four pure-gauge density on this branch, while the declared irrelevant remainders vanish.
This is the regularity/universality receipt that identifies the projective generalized-holonomy
state with the four-dimensional Yang--Mills cylinder state. The notation
\(e^{-S_E[A]}DA/G\) below abbreviates that cylinder family; it is not a literal
infinite-dimensional Lebesgue measure.
\end{assumption}

\begin{theorem}[Conditional OPH four-dimensional Euclidean Yang--Mills form]
\label{thm:oph-4d-euclidean-yang-mills-form}
Under Assumptions~\ref{ass:oph-yang-mills-branch} and
\ref{ass:compact-gauge-ym-identification}, on an extracted cylinder family from
Proposition~\ref{prop:compact-gauge-extraction-yang-mills} that lies on the declared local
four-dimensional scaling branch, the continuum gauge-sector Euclidean action is
\[
S_E[A]=\frac{1}{4g^2}\int_{\mathbb R^4}
\langle F_{\mu\nu},F_{\mu\nu}\rangle\,d^4x,
\qquad
F=dA+A\wedge A,
\]
with compact simple structure group \(G\). The extracted gauge-quotient cylinder family is denoted
\[
d\mu_{\mathrm{YM}}(A)=Z^{-1}e^{-S_E[A]}\,D A/G
\]
in the OPH support-visible GNS representation. When
Assumption~\ref{ass:compact-gauge-transfer-receipt} also holds, its support-visible continuum
transfer semigroup is the corresponding Euclidean Yang--Mills semigroup.
\end{theorem}

\begin{proof}
The proof spine is included here to make the branch target explicit.
The present Yang--Mills branch takes compact simple \(G\) as branch data. When \(G\) is imported
from OPH reconstruction, that import is conditional on the compact-gauge refinement receipt; on
that tail the zero-obstruction transportable bosonic sector category and its faithful forgetful
fiber functor reconstruct \(G\). At fixed cutoff, the finite
gauge-register / quantum-link presentation gives support-visible link holonomies and plaquette
holonomies. In the refinement limit, the zero-obstruction gluing law makes infinitesimal
rectangle holonomies multiplicative and path-local. The regularity and Cauchy bounds in
Assumption~\ref{ass:compact-gauge-ym-identification} upgrade this generalized-holonomy limit to a
local connection \(A\) on the four-dimensional scaling chart, with infinitesimal plaquette defect
\[
U_{\mu\nu}(\varepsilon,x)
=
\mathbf 1+\varepsilon^2F_{\mu\nu}(x)+O(\varepsilon^3),
\qquad
F=dA+A\wedge A.
\]
The Euclideanized MaxEnt/local-Gibbs branch supplies a local finite-range action density built
from support-visible gauge-invariant collar data. Gauge quotienting permits only class functions
of the curvature and its covariant derivatives. Four-dimensional scaling, Euclidean rotation
invariance, locality, and reflection positivity leave one relevant dimension-four positive
quadratic invariant in the pure gauge sector:
\[
\langle F_{\mu\nu},F_{\mu\nu}\rangle.
\]
The possible topological density \(\langle F\wedge F\rangle\) is reflection odd and belongs to a
separate topological-angle sector; it is absent on the ordinary reflection-positive
zero-obstruction vacuum branch used here. Higher curvature powers and covariant-derivative terms
are irrelevant under the declared continuum scaling; their disappearance in the extracted state
is the remainder bound in Assumption~\ref{ass:compact-gauge-ym-identification}. Normalizing the
unique positive quadratic invariant defines the coupling \(g\).
Definition~\ref{def:finite-compact-gauge-cylinder-system} identifies the finite-stage sources of
the gauge cylinders, and Proposition~\ref{prop:compact-gauge-extraction-yang-mills} proves their
projective weak-\(*\) / GNS extraction. Identification of its transfer generator is the separate
dynamic statement in Theorem~\ref{thm:continuum-transfer-identification}; it is not a consequence
of weak-* compactness alone.
\end{proof}

\paragraph{Prize-facing proof separation.}
The proof has two separate claims. Theorem~\ref{thm:oph-4d-euclidean-yang-mills-form}
conditionally identifies the four-dimensional Euclidean Yang--Mills form on the certified
support-visible compact-gauge branch. The
repair-dynamics theorem proves a spectral gap for that Hamiltonian.

\paragraph{Standing compact-gauge setup.}
Fix a compact simple gauge group \(G\) carried by an OPH compact-gauge zero-obstruction vacuum
branch on a cofinal tail satisfying Definition~\ref{def:compact-gauge-refinement-receipt}, realized
at fixed cutoff by the declared compact-gauge patch-carrier architecture. For
each regulator \(r\), let
\[
(\mathcal H_r,\Omega_r,H_r),\qquad T_r(t)=e^{-tH_r},
\]
be the physical Euclidean Hilbert space, vacuum, Hamiltonian, and transfer semigroup. Let
\(X_r:=X_r^{(0)}\) be the support-visible time-zero compact-gauge quotient configuration space,
and let \(\pi_r\) be the stationary time-zero measure from
Proposition~\ref{prop:compact-gauge-extraction-yang-mills}, and set
\[
K_r:=L^2(X_r,\pi_r).
\]
Write \(\omega_r(a):=\int_{X_r}a\,d\pi_r\) for its state functional. All statements in \(K_r\)
are automatically made after the finite \(\pi_r\)-null support reduction.
Let \(\mathcal C_r\) be the finite family of active repair collars. For each
\(C\in\mathcal C_r\), use the complete repaired visible datum
\(\rho_C:=\rho_{C,r}:X_r\to Y_{C,r}\), and let
\[
E_C:K_r\to K_r
\]
be conditional expectation onto the \(\rho_C\)-measurable functions. This subsection stays on the
ordinary or central zero-obstruction vacuum branch where the compact-gauge reconstruction ladder is
carried by the explicit refinement receipt used in the compact paper.

\begin{proposition}[Local exact repair equals conditional expectation]
\label{prop:sv-repair-expectation}
For each active collar \(C\), the exact-Markov repair map on the support-visible quotient is the
\(\pi_r\)-preserving conditional expectation \(E_C\).
\end{proposition}

\begin{proof}
On the exact-Markov branch, repair preserves exactly the repaired visible datum \(\rho_C\), changes
only complementary invisible fiber data, and acts on the quotient-first physical algebra rather
than on representatives. Let \(\Phi_C\) be the Heisenberg repair map and let \(\mathcal N_C\) be
the repaired local fixed algebra. Exact repair semantics require
\(\mathcal N_C\) to be exactly the \(\rho_C\)-measurable subalgebra. Then
\[
\Phi_C(a)=a\quad(a\in\mathcal N_C),\qquad
\Phi_C(\mathcal A_r^{G,\mathrm{sv}})\subseteq\mathcal N_C,\qquad
\omega_r\circ\Phi_C=\omega_r,
\]
and \(\Phi_C\) is \(\mathcal N_C\)-bimodular. Hence, for
\(a\in\mathcal N_C\) and \(x\in\mathcal A_r^{G,\mathrm{sv}}\),
\[
\omega_r\!\left(a^*\Phi_C(x)\right)=\omega_r(a^*x).
\]
Since \(\Phi_C(x)\in\mathcal N_C\), this characterizes its class in \(K_r\) as the orthogonal
projection of \(x\) onto the \(\rho_C\)-measurable subspace, uniquely modulo \(\pi_r\)-null
functions. That projection is the \(\pi_r\)-preserving conditional expectation \(E_C\).
\end{proof}

\begin{lemma}[Fiber-homogeneous orbit condition]
\label{lem:ym-fiber-symmetry}
Fix an active collar \(C\) and a repaired value \(y\in Y_{C,r}\). Let
\(F_C(y)=\rho_{C,r}^{-1}(y)\), with conditional law \(\nu_{C,y}\). Assume this is either a finite
uniform probability space or a standard atomless probability space, and that the primitive collar
relaxation is invariant under every \(\nu_{C,y}\)-preserving automorphism. Then the complete
conditional fiber, including every holonomy coordinate actually resampled by repair, is
homogeneous for the local repair receipt.
\end{lemma}

\begin{proof}
This is the complete-fiber homogeneity receipt. Quotienting removes declared implementation
labels, but the proof must also check that no remaining source constraint or relaxation rate
distinguishes points in the conditional fiber. Under that check, the conditioned state and
primitive relaxation carry the stated full measure-preserving symmetry.
\end{proof}

\begin{lemma}[Scalar relaxation on a homogeneous conditional fiber]
\label{lem:ym-scalar-relaxation}
Let \((F,\nu)\) be either a finite uniform probability space or a standard atomless probability
space. Let \(E_F\) be expectation onto constants, and let \(D_F\) be a bounded positive
self-adjoint Markov relaxation generator with
\[
\ker D_F=\operatorname{Ran}(E_F)
\]
that commutes with every measure-preserving automorphism of \((F,\nu)\). Then
\(D_F=c_F(I-E_F)\) for a scalar \(c_F>0\).
\end{lemma}

\begin{proof}
For a finite uniform fiber this is the symmetric-group argument. For a standard atomless fiber,
restrict first to step functions on a partition into \(n\) equal-measure pieces. Automorphisms
within pieces and permutations of pieces force every bounded operator in the commutant to be
scalar on the mean-zero step functions. Compatibility under equal-measure refinements gives one
scalar, and such step functions are dense in \(L^2_0(F,\nu)\). Thus the commutant on
\(L^2_0\) is scalar. Positivity and the stated kernel make that scalar strictly positive.
\end{proof}

\begin{assumption}[Finite ground-state-transform and cross-fiber receipt]
\label{ass:finite-euclidean-repair-receipt}
For each regulator, the reflection-positive finite transfer matrix supplies a unitary
\(U_r:\mathcal H_r\to K_r\), with \(U_r\Omega_r=\mathbf 1_r\), whose ground-state-transformed
generator decomposes as
\[
U_rH_rU_r^{-1}=\sum_{C\in\mathcal C_r}D_C.
\]
Each \(D_C\) is the bounded positive self-adjoint detailed-balance Markov generator acting on the
complete complementary conditional fiber of collar \(C\), including every record or holonomy
coordinate changed by repair, with fixed algebra exactly the
\(\rho_{C,r}\)-measurable algebra. If the fiberwise scalar supplied by
Lemma~\ref{lem:ym-scalar-relaxation} over repaired value \(y\) is \(c_C(y)\), the finite receipt
also verifies the cross-fiber equality \(c_C(y)=c_C\) on the support of \(\pi_r\). A Gibbs state
alone does not imply this transfer-matrix/decomposition receipt.
\end{assumption}

\begin{theorem}[Exact Euclidean-consensus law under homogeneous fibers]
\label{thm:euclidean-consensus-law}
Under the fiber-homogeneous orbit condition for every active collar and
Assumption~\ref{ass:finite-euclidean-repair-receipt}, there are positive constants
\(c_C>0\) such that the ground-state transformed physical Euclidean
generator is exactly
\[
L_r^{\mathrm{EC}}=\sum_{C\in\mathcal C_r} c_C(I-E_C),
\]
and therefore
\[
U_r e^{-tH_r}U_r^{-1}=e^{-tL_r^{\mathrm{EC}}}\qquad(t\ge 0),
\]
for a unitary \(U_r:\mathcal H_r\to K_r\) with \(U_r\Omega_r=\mathbf 1_r\).
\end{theorem}

\begin{proof}
The finite receipt supplies the ground-state transform and a decomposition into primitive local
pieces \(D_C\). Each such piece is supported on collar \(C\), preserves the repaired visible datum
\(\rho_{C,r}\), and relaxes the complete complementary conditional fiber. Thus
\[
\ker D_C=\operatorname{Ran}(E_C).
\]
Lemma~\ref{lem:ym-fiber-symmetry} gives full hidden-fiber permutation symmetry. Applying
Lemma~\ref{lem:ym-scalar-relaxation} fiberwise gives
\(D_{C,y}=c_C(y)(I-E_{C,y})\). The cross-fiber part of the finite receipt makes
\(c_C(y)=c_C\), so
\[
D_C=c_C(I-E_C)
\]
for a collar-type constant \(c_C>0\). Summing over the active collars gives the displayed
generator. Positivity and self-adjointness give the transfer-semigroup identity.
\end{proof}

\begin{lemma}[Uniform active-collar rate floor]
\label{lem:repair-rate-floor}
Assume finite local combinatorial type, a branch-homogeneous local constraint family, and
refinement-stable exact repair semantics. Then the local Euclidean repair rate depends only on
active collar type, the active collar-type set is finite across the cofinal refinement family, and
there is \(c_*>0\), independent of \(r\), such that
\[
c_C\ge c_*
\qquad\text{for every active collar }C\in\mathcal C_r.
\]
\end{lemma}

\begin{proof}
Active collars are exactly the collars on which complementary invisible fiber data are genuinely
relaxed, so \(D_C\neq0\) on \(\ker(E_C)\) and \(c_C>0\). Finite local combinatorial type gives a
finite list of bounded collar patterns, including visible interfaces, hidden fiber cardinalities,
constraint templates, and repair maps. Branch homogeneity makes the conditioned MaxEnt relaxation
scalar a function of this finite type data. Refinement stability replaces collars by copies of the
same bounded type templates with the same normalized local Euclidean repair semantics. Taking the
minimum over the finite active type list gives \(c_*>0\).
\end{proof}

\begin{proposition}[Special commuting-color finite-stage repair gap]
\label{prop:finite-stage-repair-gap}
Assume the active collars admit a bounded-color decomposition
\[
\mathcal C_r=\bigsqcup_{a=1}^{q}\mathcal C_{r,a},
\qquad q<\infty,
\]
independent of \(r\), and that exact quotient-local gluing makes the corresponding color
expectations commute. Let \(P_{0,r}\) project onto constants in \(K_r\). Then
\[
L_r^{\mathrm{EC}}\ge c_*(I-P_{0,r}),
\qquad
\Delta_{\mathrm{rep},r}\ge c_*>0.
\]
\end{proposition}

\begin{proof}
For each color \(a\), define the parallel color expectation
\[
E_{r,a}:=\prod_{C\in\mathcal C_{r,a}}E_C.
\]
Same-color collars are disjoint, so the factors commute, and exact quotient-local gluing makes
the family \(\{E_{r,a}\}_{a=1}^q\) a commuting family of orthogonal projections on the vacuum
branch. Repair completeness says that the only support-visible observables fixed by every local
repair are constants:
\[
\bigcap_{a=1}^{q}\operatorname{Ran}(E_{r,a})=\mathbb C\,\mathbf 1_r.
\]
Set
\[
\widetilde L_r:=\sum_{a=1}^{q} c_*(I-E_{r,a}).
\]
For commuting projections, \(I-\prod E_C\le\sum_C(I-E_C)\), so
\(\widetilde L_r\le L_r^{\mathrm{EC}}\). Since the \(E_{r,a}\) commute, they are simultaneously
diagonalizable. On every nonconstant joint eigenspace at least one color eigenvalue is zero.
Thus \(\widetilde L_r\ge c_*(I-P_{0,r})\), and the same lower bound holds for
\(L_r^{\mathrm{EC}}\).
\end{proof}

\begin{remark}[Generic repair-gap certificate]
The commuting-color proposition is a special certificate, not the generic repair-generator route.
For overlapping collars one must instead compute
\[
\kappa_r=\inf_{f\perp 1}
\frac{\sum_C\|(I-E_C)f\|^2}{\|f\|^2}.
\]
If local fiber rates have a lower bound \(\gamma_*>0\), then
\[
L_r^{\mathrm{EC}}\ge \gamma_*\kappa_r(I-P_{0,r}).
\]
Finite repair completeness gives \(\kappa_r>0\) at fixed regulator; a uniform refinement lower
bound is a separate receipt.
\end{remark}

\begin{assumption}[Finite transfer and vacuum compatibility receipt]
\label{ass:compact-gauge-transfer-receipt}
On the cofinal family selected in
Proposition~\ref{prop:compact-gauge-extraction-yang-mills}, suppose the following finite-stage
identities are certified.
\begin{enumerate}[label=\textup{(T\arabic*)},leftmargin=2em]
\item {\emergencystretch=8em\relax The quotient ensembles obey the finite fiber-sum identity, or its continuous
pushforward/disintegration analogue, so
\((p_{sr}^{(4)})_\#\mu_s^{(4)}=\mu_r^{(4)}\) and, by time-zero restriction,
\((p_{sr}^{(0)})_\#\pi_s=\pi_r\). Hence pullback gives coherent isometries
\[
J^K_{rs}:K_r\longrightarrow K_s,
\qquad
J^K_{rs}f=f\circ p_{sr}^{(0)}.
\]\par}
\item There are coherent physical refinement isometries
\(J^{\mathcal H}_{rs}:\mathcal H_r\to\mathcal H_s\) satisfying
\[
J^K_{rs}\mathbf 1_r=\mathbf 1_s,
\qquad
J^{\mathcal H}_{rs}\Omega_r=\Omega_s,
\qquad
U_sJ^{\mathcal H}_{rs}=J^K_{rs}U_r.
\]
\item With one refinement-independent physical Euclidean-time normalization, the finite
semigroups are coherent:
\[
J^K_{rs}e^{-tL_r^{\mathrm{EC}}}
=e^{-tL_s^{\mathrm{EC}}}J^K_{rs},
\qquad
J^{\mathcal H}_{rs}e^{-tH_r}
=e^{-tH_s}J^{\mathcal H}_{rs}
\quad(t\ge0).
\]
\item Let \(\iota_{0,r}\) pull a time-zero observable into the four-dimensional cylinder algebra
and let \(\tau_t^{(r)}\) be finite Euclidean time translation. The finite time-zero
Markov/transfer identity holds on the cylinder core:
\[
\omega_r^{(4)}\!\left(
(\iota_{0,r}f)^*\tau_t^{(r)}(\iota_{0,r}g)
\right)
=\langle f,e^{-tL_r^{\mathrm{EC}}}g\rangle_{K_r}
=\langle U_r^{-1}f,e^{-tH_r}U_r^{-1}g\rangle_{\mathcal H_r}.
\]
The reflection-positive finite OS time-zero quotient is therefore the same finite
\((\mathcal H_r,\Omega_r,H_r)\), through \(U_r\), rather than an unrelated Hilbert space.
\end{enumerate}
These are finite commuting-diagram receipts. They are not consequences of the sector-category
refinement functors or of weak-* state compactness.
\end{assumption}

\begin{theorem}[Continuum exact transfer identification]
\label{thm:continuum-transfer-identification}
Under Assumption~\ref{ass:compact-gauge-transfer-receipt}, the finite repair and physical Hilbert
spaces have Hilbert direct limits \(K\) and \(\mathcal H\). Their semigroups induce strongly
continuous self-adjoint contraction semigroups with nonnegative generators
\(L^{\mathrm{rep}}\) and \(H\), and the finite unitaries induce a unitary
\(U:\mathcal H\to K\) such that
\[
U e^{-tH}U^{-1}=e^{-tL^{\mathrm{rep}}}\qquad(t\ge 0),
\]
and hence
\[
UHU^{-1}=L^{\mathrm{rep}}.
\]
The constant vectors and physical vacua define limit vectors
\(\mathbf 1\in K\) and \(\Omega\in\mathcal H\), with
\[
U\Omega=\mathbf 1,
\qquad
P_0^K=|\mathbf 1\rangle\langle\mathbf 1|,
\qquad
P_0^{\mathcal H}=|\Omega\rangle\langle\Omega|,
\qquad
UP_0^{\mathcal H}U^{-1}=P_0^K.
\]
If \(L_r^{\mathrm{EC}}\ge c_*(I-P_{0,r})\) for one \(c_*>0\), then
\[
L^{\mathrm{rep}}\ge c_*(I-P_0^K),
\qquad
H\ge c_*(I-P_0^{\mathcal H}).
\]
\end{theorem}

\begin{proof}
The fiber-sum identity makes \(J^K_{rs}\) isometric, since
\[
\|f\circ p_{sr}^{(0)}\|_{K_s}^2
=\int_{X_r}|f|^2\,d(p_{sr}^{(0)})_\#\pi_s
=\|f\|_{K_r}^2.
\]
It also makes \(\overline\omega_r^{(0)}=\omega_r^{(0)}\), so these \(J^K_{rs}\) are exactly the
time-zero GNS isometries \(V_{rs}^{(0)}\) in
Proposition~\ref{prop:compact-gauge-extraction-yang-mills}. Thus their
Hilbert direct limit is canonically the support-visible GNS space \(K\) constructed there, not a
second continuum repair space.
Take the Hilbert direct limits under \(J^K_{rs}\) and \(J^{\mathcal H}_{rs}\). On the dense
finite-stage images define
\[
S^K(t)J_r^Kf:=J_r^Ke^{-tL_r^{\mathrm{EC}}}f,
\qquad
S^{\mathcal H}(t)J_r^{\mathcal H}\psi
:=J_r^{\mathcal H}e^{-tH_r}\psi.
\]
The finite coherence identities make these definitions independent of the representative. They
are contraction semigroups. Strong continuity holds on every finite-stage image and therefore,
by density and uniform contractivity, on the whole direct limits. For each fixed \(t\), the
finite-stage inner-product identity makes the bounded extension symmetric on a dense union and
hence symmetric everywhere; a bounded everywhere-defined symmetric operator is self-adjoint.
Positivity also passes from the finite semigroups. Thus the spectral theorem gives nonnegative
self-adjoint generators \(L^{\mathrm{rep}}\) and \(H\).

Define \(UJ_r^{\mathcal H}\psi:=J_r^KU_r\psi\). The finite unitary square makes this well defined
and isometric; the same construction with \(U_r^{-1}\) shows that its range is dense and closed,
so it is unitary. The finite transfer identity of
Theorem~\ref{thm:euclidean-consensus-law} gives
\(US^{\mathcal H}(t)U^{-1}=S^K(t)\) on a dense union and hence everywhere. Uniqueness of
self-adjoint semigroup generators gives \(UHU^{-1}=L^{\mathrm{rep}}\).

Unitality and the physical refinement identity make the constant and vacuum vectors coherent.
For \(f\in K_r\),
\[
P_{0,s}J^K_{rs}f
=\langle\mathbf 1_s,J^K_{rs}f\rangle\mathbf 1_s
=J^K_{rs}P_{0,r}f,
\]
so the rank-one vacuum projections induce the displayed limit projections; the same holds on the
physical side and the unitary identifies them.

The finite operator inequality implies
\[
\|e^{-tL_r^{\mathrm{EC}}}(I-P_{0,r})\|\le e^{-c_*t}.
\]
Passing this norm bound through the direct-limit definition gives
\(\|e^{-tL^{\mathrm{rep}}}(I-P_0^K)\|\le e^{-c_*t}\). The spectral theorem is equivalent to
\(L^{\mathrm{rep}}\ge c_*(I-P_0^K)\), and conjugation by \(U^{-1}\) gives the physical bound.
\end{proof}

\begin{remark}[Asymptotic alternative]
\label{rem:compact-gauge-mosco-alternative}
If the exact semigroup identities in Assumption~\ref{ass:compact-gauge-transfer-receipt} are not
available, the valid replacement is generalized Mosco convergence of both finite transfer forms,
strong cylinder-core convergence of \(U_r\) and \(U_r^{-1}\), and strong convergence of the
vacuum projections. The Mosco theorem then supplies the two limit semigroups and the same
intertwining conclusion. Weak-* convergence of cylinder states by itself supplies none of those
dynamic statements.
\end{remark}

\begin{assumption}[OS regularity and noncollapse receipt]
\label{ass:compact-gauge-os-noncollapse}
The selected finite cylinder family carries reflection-compatible refinement maps and exact finite
reflection positivity. Its renormalized local Schwinger functions have uniform bounds sufficient
to pass Euclidean covariance, locality, OS regularity, and clustering to the extracted family.
Moreover, there are gauge-invariant local cylinders \(A_r\), transported from one fixed cylinder
test, such that
\[
\inf_r\operatorname{Var}_{\pi_r}(A_r)>0,
\qquad
\sup_r\langle A_r\mathbf 1_r,L_r^{\mathrm{EC}}A_r\mathbf 1_r\rangle<\infty.
\]
The centered vectors \(A_r\mathbf 1_r-\omega_r(A_r)\mathbf 1_r\) converge under the same
cylinder/Hilbert identifications used in the extraction and transfer receipts.
This is the separate OS/nontriviality receipt. It is not part of the weak-* extraction theorem.
\end{assumption}

\begin{theorem}[Osterwalder--Schrader reconstruction on the compact-gauge branch]
\label{thm:compact-gauge-os-reconstruction}
Under Assumptions~\ref{ass:oph-yang-mills-branch},
\ref{ass:compact-gauge-ym-identification},
\ref{ass:compact-gauge-transfer-receipt}, and
\ref{ass:compact-gauge-os-noncollapse}, with the extraction of
Proposition~\ref{prop:compact-gauge-extraction-yang-mills}, the continuum support-visible
compact-gauge cylinder family is Euclidean invariant, reflection positive, regular on
gauge-invariant local cylinder observables, and cyclic for the vacuum sector. Thus
Osterwalder--Schrader reconstruction gives a four-dimensional quantum Yang--Mills theory
\((\mathcal H,\Omega,H,\mathcal A_{\mathrm{loc}}^G)\) on the support-visible gauge-invariant local
algebra, with \(H\ge0\) and \(e^{-tH}\) equal to the Euclidean transfer semigroup of
Theorem~\ref{thm:oph-4d-euclidean-yang-mills-form}.
\end{theorem}

\begin{proof}
For every finite list of positive-time cylinders, finite reflection positivity says that the
associated reflected Gram matrix is positive semidefinite. Its entries converge along the
extraction subnet, and the cone of positive semidefinite matrices is closed, so reflection
positivity passes to the limit. Euclidean covariance, locality, regularity, and clustering pass by
the compatible transformation maps and uniform bounds in
Assumption~\ref{ass:compact-gauge-os-noncollapse}; weak-* compactness alone would not supply those
bounds. The vacuum vector is cyclic for the GNS closure of the gauge-invariant local cylinder
algebra. The finite time-zero identity (T4) passes to the limit on the dense cylinder core:
the left side converges by four-dimensional cylinder extraction and the right side by the coherent
semigroup limit. Consequently the OS time-zero inner product and translation semigroup are
unitarily identical to the direct-limit \((\mathcal H,\Omega,e^{-tH})\) of
Theorem~\ref{thm:continuum-transfer-identification}; the notation does not identify two unrelated
Hamiltonians. The
Osterwalder--Schrader reconstruction theorem then produces the Hilbert space, vacuum, local
algebra, positive Hamiltonian, and Euclidean transfer semigroup~\cite{osterwalderSchrader73,
osterwalderSchrader75}.
\end{proof}

\begin{proposition}[Nontriviality of the support-visible compact-gauge theory]
\label{prop:compact-gauge-nontriviality-yang-mills}
Under Assumptions~\ref{ass:compact-gauge-transfer-receipt} and
\ref{ass:compact-gauge-os-noncollapse},
The support-visible compact-gauge local algebra on the zero-obstruction vacuum branch strictly
contains the vacuum scalars and admits a non-vacuum finite-energy local excitation.
\end{proposition}

\begin{proof}
The compact-gauge witness and physical-UV landing theorem supplies finite support-visible
gauge-invariant local observables, for example nonconstant Wilson/plaquette cylinders. The uniform
positive variance in Assumption~\ref{ass:compact-gauge-os-noncollapse} says that the chosen
centered cylinder does not enter the GNS null ideal in the limit, so it gives a nonzero vector
orthogonal to the vacuum. The uniform form bound and lower-semicontinuity of the certified
transfer-form limit give this vector finite continuum energy. Thus the support quotient has not
erased the excitation used to prove nontriviality.
\end{proof}

\begin{theorem}[Conditional positive compact-gauge Yang--Mills mass gap from OPH repair dynamics]
\label{thm:oph-yang-mills-gap}
Let \(G\) be a compact simple gauge group carried by a support-visible compact-gauge OPH vacuum
branch satisfying the standing setup, Assumptions~\ref{ass:compact-gauge-transfer-receipt} and
\ref{ass:compact-gauge-os-noncollapse}, the renormalized Yang--Mills identification receipt
of Assumption~\ref{ass:compact-gauge-ym-identification}, the finite ground-state-transform and cross-fiber receipt
of Assumption~\ref{ass:finite-euclidean-repair-receipt}, and all hypotheses of
Theorem~\ref{thm:euclidean-consensus-law},
Lemma~\ref{lem:repair-rate-floor}, and
Proposition~\ref{prop:finite-stage-repair-gap}. The theory reconstructed in
Theorem~\ref{thm:compact-gauge-os-reconstruction} is nontrivial by
Proposition~\ref{prop:compact-gauge-nontriviality-yang-mills}, and its continuum support-visible
Hamiltonian \(H\)
satisfies
\[
H\ge c_*(I-P_0^{\mathcal H}),
\]
where \(P_0^{\mathcal H}\) projects onto the physical vacuum. Therefore
\[
\operatorname{Spec}(H)\cap(0,c_*)=\varnothing,
\qquad
\Delta_{\mathrm{YM}}\ge c_*>0.
\]
Moreover the Yang--Mills gap is the repair gap:
\[
\Delta_{\mathrm{YM}}=\Delta_{\mathrm{rep}}.
\]
\end{theorem}

\begin{proof}
Proposition~\ref{prop:finite-stage-repair-gap} gives
\[
L_r^{\mathrm{EC}}\ge c_*(I-P_{0,r})
\]
at every finite stage. Theorem~\ref{thm:continuum-transfer-identification}, using the explicit
finite transfer/vacuum receipt, transports the bound to the support-visible continuum:
\[
L^{\mathrm{rep}}\ge c_*(I-P_0^K).
\]
Using \(UHU^{-1}=L^{\mathrm{rep}}\), conjugation by \(U^{-1}\) gives the Hamiltonian lower bound.
The spectral-gap statement follows immediately. Since \(U\) is unitary and maps the vacuum to the
constant sector, it preserves the nonzero spectrum, so the Yang--Mills gap and repair gap are
equal.
\end{proof}

\paragraph{Exact gap accounting.}
The theorem gives an identity stronger than a phenomenological estimate:
\[
\operatorname{Spec}(H)\setminus\{0\}
=
\operatorname{Spec}(L^{\mathrm{rep}})\setminus\{0\}.
\]
Thus
\[
\Delta_{\mathrm{YM}}
=
\inf\bigl(\operatorname{Spec}(H)\setminus\{0\}\bigr)
=
\inf\bigl(\operatorname{Spec}(L^{\mathrm{rep}})\setminus\{0\}\bigr)
=
\Delta_{\mathrm{rep}}.
\]
The finite-stage projection argument proves positivity of that same quantity.

\paragraph{Relation to the Clay/Jaffe--Witten statement.}
The Clay problem asks for a nontrivial quantum Yang--Mills theory on \(\mathbb R^4\), for each
compact simple \(G\), satisfying axiomatic properties at least as strong as the stated Wightman or
Osterwalder--Schrader references and possessing a positive mass gap~\cite{jaffeWittenYM,clayYM}.
Theorem~\ref{thm:oph-4d-euclidean-yang-mills-form} supplies the four-dimensional Euclidean
Yang--Mills form on the OPH support-visible compact-gauge branch, and
Theorem~\ref{thm:compact-gauge-os-reconstruction} supplies the support-visible OS reconstruction
on the gauge-invariant local algebra. Proposition~\ref{prop:compact-gauge-nontriviality-yang-mills}
supplies nontriviality. 
Theorem~\ref{thm:oph-yang-mills-gap} supplies the exact spectral gap accounting on that same
branch. Proposition~\ref{prop:compact-gauge-extraction-yang-mills} proves the algebra/state/GNS
extraction only. Full Clay admissibility additionally requires the finite transfer/vacuum and
OS/noncollapse receipts in Assumptions~\ref{ass:compact-gauge-transfer-receipt} and
\ref{ass:compact-gauge-os-noncollapse}, together with the renormalized Yang--Mills identification,
finite ground-state-transform/cross-fiber, and uniform-gap receipts; weak-* compactness is not a
substitute for those inputs.
The standalone Clay note is only a focused presentation of this same theorem surface; it does not
enlarge the branch beyond the data stated here.
