\section{Fixed-Cutoff Realization, Quotient Repair, and Edge Centers}
\label{app:consensus-fixed-cutoff-port}

This appendix carries the fixed-cutoff realization and edge-center items for the consensus paper.
They sharpen the
quotient-first repair interpretation used throughout the consensus paper and make the collar
boundary data explicit at the same finite patch-net level. On the declared fixed-cutoff collar
branch, the local repair step is read from exact Markov splice or a declared Petz/Fawzi--Renner
recovery move on that same collar data; the recovery move gives a recovered comparison state, while
exact splice requires exact Markovity or a controlled fixed-collar replacement modulus. Representative
repair maps are only lifts of the resulting quotient-local update.

\subsection{Quotient Repair and UV Underdetermination}

At fixed cutoff, each regulator cell \(x\) carries a finite-dimensional factor
\(\mathfrak h_x\), patch algebras are finite type-I algebras, and gauge-as-gluing is realized as
a compact boundary redundancy action on cut data. The physical repair law therefore belongs on the
overlap-invariant quotient rather than on hidden representatives. If \(q:\Sigma\to\Sigma/\Gamma\)
is the quotient by boundary redundancy and \(\overline T_i\) is the physical quotient update, a
representative-level map \(T_i\) is only required to be a lift satisfying
\[
q\circ T_i=\overline T_i\circ q.
\]
Hence
\[
q(T_i(\gamma\cdot s))=q(T_i(s))
\]
for gauge-equivalent inputs. Quotient descent is therefore structural, while strict
representative-level covariance is only implementation bookkeeping. The burden is to prove that
the accepted recovery-derived local moves satisfy the stated repair-completeness, support-local
disjoint-commutation, nested-collar
restriction-compatibility, and Petz-domain control clauses on the declared branch. The
touched-overlap acceptance contract yields finite Lyapunov descent and derived
termination for accepted moves, while the fixed-cutoff gluing package carries the
parenthesization-invariant union-collar state used for the local diamond.

\begin{proposition}[Ancilla-stable UV underdetermination]
Let a fixed-cutoff OPH realization be stabilized by finite ancillary factors \(K_P\) in a fixed
product state, with observable patch algebras embedded as
\(\mathcal A(P)\otimes \mathbf 1_{K_P}\) and repair dynamics acting trivially on the ancillas.
Then observable expectations on the physical subalgebras, overlap data, the local-Gibbs branch,
the collar conditional mutual information \(I(A:D\mid B)\), the Fawzi--Renner remainder, the
collar Markov modulus, and the quotient normal form are unchanged. Thus the fixed-cutoff theorem
package determines the UV branch only modulo such ancillary stabilization together with gauge or
implementation hiding, not a unique microscopic presentation.
\end{proposition}

\begin{proof}
Product ancillas leave physical observables unchanged, cancel additively inside conditional mutual
information, and are inert under the repair maps. Hence every invariant listed above is unchanged.
\end{proof}

\subsection{Derived Boundary Data and Ordinary EC}

\begin{proposition}[Derived boundary gluing datum]
Choose a finite regulator chart for the patches meeting along a connected cut \(\Sigma\). Because
the local overlap algebras are finite-dimensional matrix algebras, any overlap-consistent
recharting is an inner automorphism and is implemented by a unitary on the cut Hilbert space. The
compact closure of the subgroup generated by these recharting unitaries is a compact boundary
redundancy group \(K_\Sigma\). If triple-overlap defects are central, the projective composition
law lifts to a compact central extension \(\widehat K_\Sigma\); on the ordinary branch one simply
sets \(\widehat K_\Sigma = K_\Sigma\). A genuinely noncentral \(2\)-group defect is the only
obstruction to reducing the overlap transition system to an ordinary compact group action.
\end{proposition}

\begin{theorem}[Derived EC decomposition]
Under the fixed-cutoff regulator realization above, and on the ordinary or central-defect branch,
the collar Hilbert space is
\[
\mathcal H_{B_\delta}
=
(\tilde{\mathcal H}_{B_L}\otimes \tilde{\mathcal H}_{B_R})^{\widehat K_\Sigma}
\cong
\bigoplus_{\alpha}
\left(\mathcal H_{b_L^\alpha}\otimes \mathcal H_{b_R^\alpha}\right),
\]
and the center of the collar algebra is generated by the block projectors:
\[
Z(\mathcal A(B_\delta))
=
\bigoplus_\alpha \mathbb C\cdot \mathbf 1_\alpha.
\]
The right half-collar carries the contragredient representation because it sees inverse transport
across the same cut.
\end{theorem}

\begin{remark}
This is the finite-patch-net origin of the collar center used by the later Markov, record, and
observer packages. Exact Markovity is an additional state hypothesis; EC provides the
kinematic block structure.
\end{remark}

\subsection{Higher-Gauge Replacement on the Genuinely Noncentral Branch}

\begin{proposition}[Derived higher-gauge cut datum]
On the genuinely noncentral branch, weak overlap gluing on a connected cut \(\Sigma\) is encoded
by a compact crossed module
\[
\mathbb K_\Sigma=(H_\Sigma\xrightarrow{\partial_\Sigma}G_\Sigma,\triangleright)
\]
with defect class
\[
q_\Sigma\in \check H^2(N_\Sigma,H_\Sigma\to G_\Sigma),
\]
and compact higher-gauge change system
\[
\mathcal T_\Sigma=C^1(N_\Sigma,H_\Sigma)\rtimes C^0(N_\Sigma,G_\Sigma).
\]
\end{proposition}

\begin{theorem}[Higher-gauge EC decomposition and defect transport]
On the genuinely noncentral branch,
\[
\mathcal H_{B_\delta}^{2g}
=
(\tilde{\mathcal H}_{B_L}\otimes \tilde{\mathcal H}_{B_R})^{\mathcal T_\Sigma}
\cong
\bigoplus_\lambda
(\mathcal H_{b_L^\lambda}\otimes \mathcal H_{b_R^\lambda}),
\]
and
\[
Z(\mathcal A_{2g}(B_\delta))
=
\bigoplus_\lambda \mathbb C\cdot \mathbf 1_\lambda.
\]
Moreover the full crossed-module orbit \(q_\Sigma\) is invariant under local rechartings and
classifies fixed-cutoff genuinely noncentral gluing data. The higher associator is removable iff
\(q_\Sigma\) lies in the image of
\[
\check H^1(N_\Sigma,G_\Sigma)longrightarrow
\check H^2(N_\Sigma,H_\Sigma\to G_\Sigma),
\qquad [g]\longmapsto[(g,1)].
\]
That map need not be injective. Strict endpoint-only ordinary transport additionally requires at
least one allowed strict representative with trivial represented loop holonomy.
\end{theorem}

\begin{corollary}[Exact Markov plus split alignment adds the state factorization]
On either the ordinary/central branch of the previous theorem or the genuinely noncentral
higher-gauge branch, if in addition
\[
I_\omega(A_\delta:D_\delta\mid B_\delta)=0
\]
\emph{and} the state satisfies the Markov-split alignment hypothesis (its HJPW decomposition of
\(\mathcal H_{B_\delta}\) can be chosen to be the EC decomposition itself; see the main-text
Section 2.3 and the compact paper's alignment definition), or one passes to the explicitly stated
idealized recoverability limit that supplies both conditions, then
\[
\rho_{A_\delta B_\delta D_\delta}
=
\bigoplus_\alpha p_\alpha
\left(\rho_{A_\delta b_L^\alpha}\otimes \rho_{b_R^\alpha D_\delta}\right).
\]
EC therefore gives the kinematic block decomposition, while exact Markovity plus split alignment
is the extra state input that gives the EC-aligned HJPW normal form. Exact Markovity alone yields
the normal form only over a state-dependent HJPW split, which a Bell-pair example (main text,
Section 2.3) shows can be transposed relative to the EC factors.
\end{corollary}

\begin{proposition}[Parenthesization-invariant union-collar gluing]\label{prop:assocglue}
Fix a finite union collar \(U\) built from two overlapping local repair collars on the declared
fixed-cutoff branch. On the ordinary or central-defect branch, the physical glued state on \(U\)
determined by the exterior marginals and sector data is independent of how the local gluings are
parenthesized, up to the boundary-redundancy action. On the genuinely noncentral branch, the same
statement holds up to the crossed-module change system \(\mathcal T_\Sigma\). Hence the physical
quotient-local glued state on \(U\) is well defined independently of parenthesization.
\end{proposition}

\begin{proof}
On the ordinary or central-defect branch, the preceding edge-center decomposition writes the
collar algebra as a direct sum of sector blocks generated by central projectors. Reparenthesizing
two overlapping local gluings changes only the representative by the central boundary action and
cannot move the state between those block projectors, so the quotient-local glued state is
unchanged. On the genuinely noncentral branch, the failure of strict composition is recorded by
the crossed-module associator, and the higher-gauge theorem above identifies rechartings exactly
with the \(\mathcal T_\Sigma\)-coboundary action. Reparenthesization therefore changes only the
representative inside one \(\mathcal T_\Sigma\)-orbit. In either case the physical quotient state
is parenthesization-independent.
\end{proof}

\begin{remark}
Approximate recoverability gives controlled deviations from this normal form; it is not implied by
EC alone. This is the fixed-cutoff topological package behind the consensus paper's quotient and
record-language surface.
\end{remark}

\begin{corollary}[Physical observables are invariant on one quotient-local glued state]\label{cor:obsglue}
Let \(U\) be a finite union collar on the declared fixed-cutoff branch, and let
\(\omega_U,\omega'_U\) be two microscopic representatives of the same quotient-local glued state
from Proposition~\ref{prop:assocglue}. Then every physical observable \(X\) on the collar
fixed-point / quotient-local algebra has the same expectation in both representatives:
\[
\operatorname{Tr}(X\omega_U)=\operatorname{Tr}(X\omega'_U).
\]
In particular the same holds for the central sector projectors and for any observer-accessible
record observable generated from them on that same declared surface.
\end{corollary}

\begin{proof}
On the ordinary or central-defect branch, Proposition~\ref{prop:assocglue} says the two
representatives differ only by the boundary-redundancy action inside one fixed sector block. The
fixed-point collar algebra and its central block projectors are invariant under that action, so
their expectation values agree. On the genuinely noncentral branch, the same proposition says the
two representatives differ only inside one \(\mathcal T_\Sigma\)-orbit, and the quotient-local
physical algebra \(\mathcal A_{\mathrm{phys}}(U)\) of Definition~\ref{def:physobs} is defined
precisely on that orbit space. Therefore the induced physical state and all expectations of
physical observables agree there as well.
\end{proof}
