\section{Candidate Microphysics Reference Architecture}

The synthesis paper keeps the observer-facing theorem package in the main text, but the concrete
finite screen architecture belongs in an appendix. The theorem-bearing fixed-cutoff
source surface for the edge heat-kernel / Casimir leaf is the microphysics companion paper; the
appendix records only the synthesis-level restatement imported from that surface. The reference
architecture used here is a finite cellulation of the horizon screen with boundary-fixed patch
algebras, boundary-fixed overlap algebras on collars, declared shared readout packets, local
repair instruments, and record registers exposed on the observer-facing interface.

\paragraph{Theorem (Regulated patch-net embedding).}
On a fixed finite cellulation and finite patch cover, the regulated microphysics construction realizes an
explicit finite patch-net layer: patch vertices are genuine screen patches, overlap edges are
genuine collars, packet fields are actual readouts of declared overlap observables, and allowed
repair branches are concrete local channels on the same finite regulator.

\paragraph{Proof sketch.}
All patch and overlap algebras are finite-dimensional at fixed cutoff, and the declared packet
fields are readouts of explicit overlap observables in those algebras. The candidate repair menu
is implemented by local finite-support channels on the same neighborhoods. Therefore the abstract
finite patch-net syntax is embedded into an explicit regulator object rather than introduced as a
separate formal layer.

\paragraph{Theorem (Fixed-cutoff edge heat-kernel branch).}
On the thermalized overlap branch of the same regulated architecture, the stationary sector law is
\[
\pi_\beta(\alpha)\propto d_\alpha e^{-\beta C_2(\alpha)},
\]
and along refinement ladders converging to a compact-group Peter--Weyl decomposition~\cite{peterWeyl27} the same
weights converge cylinderwise to the heat-kernel/Casimir law used in the OPH edge-sector branch.

\paragraph{Proof sketch.}
The regulated proposal kernel is chosen so that the weighted proposal symmetry
\(d_\alpha q_{\alpha\beta}=d_\beta q_{\beta\alpha}\) holds. Detailed balance with the Casimir
acceptance rule then fixes the stationary distribution in finite dimension, and the compact-group
heat-kernel law is the corresponding refinement lift.

\paragraph{Extended derivation.}
The full fixed-cutoff architecture, validation package, and theorem stacks are developed in
\emph{Screen Microphysics, Patches, and Observer Synchronization in OPH}~\cite{ophmicrophysics}.

\section{Interpretive Epilogue: State-and-Law Habitat}

This appendix records the OPH state-and-law habitat available inside the
framework and leaves any strange-loop closure theorem explicitly open.

The OPH inputs used here are:
\begin{enumerate}
\item the patch net \(P\mapsto A(P)\) of von Neumann algebras together with isotony and overlap
restriction maps;
\item the global state on the inductive-limit algebra, whose restrictions witness a nonempty
overlap-consistent local sector;
\item the finite Axiom-3 MaxEnt/refinement branch, which supplies a common finite family of
gauge-invariant local constraint observables across cutoffs;
\item on the fixed-cutoff branch, the derived finite type-I presentations and compact boundary
gluing groups used elsewhere in the OPH package.
\end{enumerate}

The law slot is encoded by the finite expectation-value coordinates of the retained Axiom-3
constraint family. That choice furnishes a compact convex state-and-law habitat for the framework.

\paragraph{Theorem (Internal state-and-law habitat theorem).}
Fix finitely many screen patches \(P_1,\dots,P_N\) in the standard OPH setup. For each \(i\), let
\[
M_i:=A(P_i),
\qquad
M_{ij}:=A(P_i\cap P_j),
\]
where \(M_i\) is the patch von Neumann algebra and \(M_{ij}\subset M_i,M_j\) is the overlap
algebra. Let
\[
S_i:=S(M_i)\subset M_i^*
\]
be the full state space of \(M_i\), endowed with the weak* topology \(\sigma(M_i^*,M_i)\).

Choose a finite family of self-adjoint gauge-invariant local constraint observables
\[
\mathcal O=\{O_1,\dots,O_m\}
\]
from the Axiom-3 MaxEnt branch, with each \(O_a\) supported in one of the chosen patches; write
\(i(a)\) for an index such that \(O_a\in M_{i(a)}\).

Define the overlap-consistent state sector
\[
X_{\mathrm{ov}}
:=
\left\{
(\omega_1,\dots,\omega_N)\in \prod_{i=1}^N S_i:
\omega_i|_{M_{ij}}=\omega_j|_{M_{ij}}\ \text{for all }i,j
\right\}.
\]
Define the OPH law-coordinate map
\[
c:X_{\mathrm{ov}}\to \mathbb R^m,
\qquad
c(\omega_1,\dots,\omega_N)
:=
\bigl(\omega_{i(1)}(O_1),\dots,\omega_{i(m)}(O_m)\bigr).
\]
Let
\[
X_{\mathcal O}
:=
\left\{
(\omega_1,\dots,\omega_N,\ell)\in
\left(\prod_{i=1}^N S_i\right)\times \mathbb R^m:
(\omega_1,\dots,\omega_N)\in X_{\mathrm{ov}},
\ \ell=c(\omega_1,\dots,\omega_N)
\right\}.
\]
Then:
\begin{enumerate}
\item the ambient product
\[
E:=
\left(\prod_{i=1}^N M_i^*\right)\times \mathbb R^m
\]
is a Banach space for any product norm;
\item \(X_{\mathcal O}\) is nonempty and convex;
\item \(X_{\mathcal O}\) is norm-closed in \(E\);
\item \(X_{\mathcal O}\) is compact in the product topology
\[
\tau
:=
\left(\prod_{i=1}^N \sigma(M_i^*,M_i)\right)\times
\text{Euclidean topology on }\mathbb R^m;
\]
\end{enumerate}

\begin{proof}
Each \(M_i\) is a von Neumann algebra in the OPH patch net, hence a Banach space, so each dual
\(M_i^*\) is Banach. A finite product of Banach spaces is Banach, hence so is \(E\).

For each \(i\), the state space
\[
S_i=\{\omega\in M_i^*:\omega\ge 0,\ \omega(1)=1\}
\]
is convex and weak* compact by Banach--Alaoglu, because it is a weak* closed subset of the dual
unit ball. For every pair \((i,j)\), restriction along \(M_{ij}\subset M_i\) and
\(M_{ij}\subset M_j\) defines affine weak* continuous maps
\[
r_{ij}:S_i\to S(M_{ij}),
\qquad
r_{ji}:S_j\to S(M_{ij}).
\]
Hence \(X_{\mathrm{ov}}\) is an intersection of affine equalizer sets, so it is convex and
\(\tau\)-closed inside \(\prod_i S_i\). Since \(\prod_i S_i\) is compact and convex in the
product weak* topology, \(X_{\mathrm{ov}}\) is compact and convex as well.

Nonemptiness comes from the OPH global state on the inductive-limit algebra: its restrictions
\[
\bigl(\omega|_{M_1},\dots,\omega|_{M_N}\bigr)
\]
belong to \(X_{\mathrm{ov}}\) because the restrictions agree on every overlap by construction.

Each coordinate \(\omega_{i(a)}\mapsto \omega_{i(a)}(O_a)\) is affine and weak* continuous, since
evaluation at a fixed algebra element is weak* continuous. Thus \(c\) is affine and
\(\tau\)-continuous. The graph map
\[
G:X_{\mathrm{ov}}\to E,
\qquad
G(x):=(x,c(x)),
\]
is affine and continuous, so its image \(X_{\mathcal O}=G(X_{\mathrm{ov}})\) is convex and
\(\tau\)-compact.

To see norm-closedness in \(E\), let \((x_n,c(x_n))\to (x,\ell)\) in norm. Norm convergence
implies weak* convergence on each coordinate, so \(x\in X_{\mathrm{ov}}\) because
\(X_{\mathrm{ov}}\) is weak* closed. Since \(c\) is weak* continuous, \(c(x_n)\to c(x)\), while
norm convergence in \(\mathbb R^m\) also gives \(c(x_n)\to \ell\). Hence \(\ell=c(x)\), so
\((x,\ell)\in X_{\mathcal O}\).

Finally, \(X_{\mathcal O}\) is a compact convex subset of the locally convex topological vector
space \(E\) equipped with \(\tau\).
\end{proof}

The additional inputs needed for a strange-loop closure theorem are:
\begin{enumerate}
\item a closure map \(T\) built from internal operations such as overlap repair,
Axiom-3 MaxEnt reprojection, collar recoverability, and record-sector coarse-graining;
\item a proof that the stronger ``observer-supporting'' or ``selected-world'' criteria carve out a
nonempty \(T\)-invariant observer-supporting subset of \(X_{\mathcal O}\);
\item any uniqueness, contraction, or Lyapunov-type stability estimate for that closure map.
\end{enumerate}

The habitat theorem supplies only the ambient Banach/compact-convex setting. It does not define a
canonical internal self-map, it does not identify any nonempty invariant observer-supporting subset,
and it does not prove uniqueness or stability. In particular, nonemptiness and compact-convexity
of the ambient habitat do not by themselves imply the existence of a nonempty invariant
observer-supporting sector. This does not erase the exact finite packet branch proved on the
consensus surface: there the quotient normal-form map already pushes forward to a continuous
affine idempotent self-map of the finite packet simplex, with fixed points exactly the packets
supported on quotient normal forms. Any further strange-loop reading of the ambient habitat as a
closure story for existence is interpretive only and is not part of the recovered theorem package.

\subsection{Additional Problem Closures}

Using the phase split of Section~\ref{16-summary-complete-axiom-set}, the broader closure claims
read as follows. The ledger also records appendix-tier closure stories so they cannot float
outside the official status ledger. In this table, ``Proved corollary of earlier theorems'' means
proved under the dependencies named in the row, including declared branch premises and cited
companion-paper theorem surfaces.

\begin{center}
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}p{0.22\textwidth}>{\raggedright\arraybackslash}p{0.48\textwidth}@{}}
\toprule
Claim & Status & Boundary \\
\midrule
Quantum gravity consistency & Proved corollary of earlier theorems & Conditional Lorentz and Jacobson-type Einstein branches follow once the stated scaling-limit, null-bridge, and fixed-cap premises are imported. \\
UV completion / microscopic uniqueness & Explicit future program & Fixed-cutoff theorem packages exist, but a unique microscopic representative, the continuum BW lift on the extracted geometric subnet, and the refinement-limit transportable compact-gauge lift remain open. \\
Measurement problem & Explicit future program & Ref.~\cite{ophmicrophysics} closes the fixed-cutoff central-record / Born-L\"uders interface, but a full philosophical or continuum-level measurement closure is not derived here. \\
Cosmological principle and horizon homogeneity & Explicit future program & MaxEnt symmetry inheritance is suggestive only; an independent derivation of cosmological isotropy and homogeneity remains outside the recovered-core theorems. \\
Observer-relative modular time & Proved corollary of earlier theorems & On the BW\(_{S^2}\) geometric branch, observer-relative time is read from the cap modular automorphism parameter of the observer's accessible algebra/state pair. This is the D3 reading only. \\
Global / operational problem of time & Explicit future program & OPH does not prove a separate operational-clock theorem or a global solution of the problem of time. \\
Black-hole information paradox & Explicit future program & Edge-center sectorization and recoverability motivate an internal resolution template, but the full black-hole-information branch remains outside Phase I. \\
D6 cosmological-capacity closure under declared screen-capacity premise & Proved corollary of earlier theorems & Once the external input \(N_{\mathrm{scr}}\) and the D6 identification \(N_{\mathrm{scr}}=S_{\mathrm{dS}}\) are declared, the same Einstein branch fixes \(\Lambda=3\pi/(G N_{\mathrm{scr}})\) and the static-patch readout. \\
Bare cosmological-constant problem from local null data & Explicit future program & The local null-data route determines the Einstein branch only modulo \(\Lambda g_{ab}\) and does not derive the screen-capacity identification from bare OPH axioms. \\
Magnetic monopole expectation from simple GUT groups & Proved corollary of earlier theorems & The realized product-group branch \(\SU(3)\times\SU(2)\times\U(1)/\mathbb Z_6\) removes the standard simple-GUT symmetry-breaking monopole channel. \\
Proton stability against gauge-mediated decay & Proved corollary of earlier theorems & The realized product-group branch removes the standard simple-GUT gauge-mediated proton-decay channel. \\
Proton spin fraction & Explicit future program & Closing the proton-spin claim still requires nonperturbative QCD completion beyond Phase I. \\
Dark matter phenomenology & Explicit future program & Modular-anomaly response laws remain conjectural beyond the recovered gravity chain. \\
Baryon asymmetry scale & Explicit future program & Suppression-counting estimates are not a substitute for a derived out-of-equilibrium mechanism. \\
Three generations & Proved corollary of earlier theorems & \(N_g=3\) is recovered on the realized MAR-admissible branch. \\
Downstream flavor structure, Koide, and charged-lepton fits & Explicit future program & Later flavor constructions require extra ans\"atze and remain outside the recovered core. \\
Edge-to-2D-YM / controlled large-\(N_{\mathrm{edge}}\) worldsheet branch & Proved corollary of earlier theorems & On the stated overlap-gauge, local-Gibbs/MaxEnt, compact-group, and large-\(N_{\mathrm{edge}}\) premises, the edge-sector heat-kernel bridge and controlled Gross--Taylor worldsheet effective description are theorem-level. \\
Critical superstring / worldsheet CFT lift & Explicit future program & Critical-superstring claims, worldsheet CFT closure, anomaly cancellation, and full massless-spectrum matching require extra ingredients outside the recovered core. \\
Why anything exists / strange-loop closure & Explicit future program & Appendix B provides only the habitat theorem and fixed-point setting. The OPH closure map, invariant observer-supporting sector, and uniqueness/stability proofs remain open. \\
Fixed-cutoff checkpoint/restoration/backup & Proved corollary of earlier theorems & Ref.~\cite{ophmicrophysics} proves same-interface checkpoint/restoration and backup for observer-accessible event algebras with explicit future-law error control. \\
Substrate-transfer / stronger observer continuation & Explicit future program & Stronger substrate-selection, redesigned-environment continuation, strange-loop closure, uniqueness, and stability claims remain open. \\
\bottomrule
\end{tabular}
\end{center}

\section{Observer Continuation and Backup}

This appendix uses the fixed-cutoff checkpoint/restoration/error/identity theorem package proved
in Ref.~\cite{ophmicrophysics} and summarizes its algebraic interface in observer language. It
does not define a strange-loop closure map on an invariant observer-supporting sector or establish
uniqueness and stability for such a map. Nor does it upgrade the fixed-cutoff theorem stack to
continuation across redesigned environments: the proved package is same-interface restoration on
observer-accessible event algebras with explicit error control.

\subsection{Observer as Algebraic Pattern}

Here, an observer is represented by
\[
O=(P,\mathcal{A}(P),\rho,R),
\]
where \(P\) is a screen patch, \(\mathcal{A}(P)\) is its local algebra, \(\rho\) is the local
state, and \(R\) is the record algebra. Records are carried exactly by central record projectors
and, on practical readout surfaces, by approximately commuting projectors in overlap centers, so
they are shareable without violating no-cloning constraints for generic quantum states.

Ref.~\cite{ophmicrophysics} proves a fixed-cutoff observer-facing measurement interface: a
finite central record algebra, Born probabilities for its event projectors, and L\"uders
conditioning on that same commuting record algebra. This appendix uses that fixed-cutoff
measurement package in observer language. If a practical readout uses projectors that are
\(\delta_{\mathrm{rec}}\)-close in operator norm to that central reference algebra and the
accessible state is perturbed by at most \(\varepsilon\) in trace norm, each declared elementary
record-event probability shifts by at most \(\varepsilon+\delta_{\mathrm{rec}}\).

\subsection{Markov Collar Factorization}

For a collar tripartition \(A\)-\(B\)-\(D\) with conditional mutual information
\(I(A:D|B)\le\varepsilon\), the exact Markov limit gives
\[
\rho_{ABD}
=\bigoplus_{\alpha} p_{\alpha}\,
\rho^{(\alpha)}_{A b_L^{\alpha}}
\otimes
\rho^{(\alpha)}_{b_R^{\alpha} D}.
\]
The sector label \(\alpha\) is classical center data. This decomposition is the mathematical
basis for extracting an interior observer state with a controlled boundary interface.

\subsection{Checkpoint and Restoration Map}

A checkpoint is the tuple
\[
\mathcal{C}=\bigl(R,\alpha,\rho_{\mathrm{int}}^{(\alpha)}\bigr),
\]
with \(\rho_{\mathrm{int}}^{(\alpha)}\) the interior conditional state. Given a compatible target
environment state \(\sigma_{\mathrm{env}}^{(\alpha)}\), a restored state is
\[
\rho_{\mathrm{new}}^{(\alpha)}
=
\rho_{\mathrm{int}}^{(\alpha)}
\otimes
\sigma_{\mathrm{env}}^{(\alpha)}.
\]
For approximate Markov collars, recovery is controlled by the standard bound
\[
\left\|
\rho_{ABD}
-
(\mathrm{id}_A\otimes\mathcal{R}_{B\to BD})(\rho_{AB})
\right\|_1
\le
2\sqrt{\ln 2\,\varepsilon}.
\]
This gives quantitative trace-distance control on the recovered state under finite conditional
mutual information (finite collar error). Interpreting that control as observer continuation
requires additional modeling assumptions beyond the bound itself.

The fixed-cutoff microphysics claim is stronger than the bare recoverability estimate written
above. In Ref.~\cite{ophmicrophysics}, exact checkpoint restoration preserves the full future
law of observer-accessible events, while an \(\varepsilon\)-accurate restoration changes that
future law by at most \(\varepsilon\) in total variation. The stronger strange-loop / substrate-transfer closure story
is open.

\subsection{Physical Meaning}

At fixed cutoff, Ref.~\cite{ophmicrophysics} proves a checkpoint/restoration theorem and backup
corollary for observer-accessible event algebras. The proved package stops at same-interface
backup/restoration with explicit future-law error control; stronger continuation and
substrate-selection claims are outside it. This appendix states the observer-facing meaning
of that theorem and its algebraic prerequisites. Open items are the stronger substrate-selection,
strange-loop closure, uniqueness, and stability package.

\input{tex_fragments/OBSERVERS_TECHNICAL_SUPPLEMENT_PORT.tex}
