\section{Consensus, Defects, and Implementation Hiding}

The fixed-cutoff consensus package admits an equivalent finite patch-net formulation. Local patch descriptions agree on
overlaps, local recovery-derived repair rules remove mismatches, and the physical output is the
schedule-independent quotient normal form together with the induced terminal expectation
functionals on the declared physical observable algebras. This section records the fixed-point,
defect, and gauge-quotient statements in that language.

The consensus lane also carries a simple finite-candidate law-selection model: once one equips
candidate repair rules with a fitness functional, replicator dynamics gives a clean toy picture in
which more successful reconciliation laws dominate a competing pool. That selection picture is
useful for the overall synthesis picture, but in the consensus paper it is a finite-candidate
monotonicity result, not part of the recovered-core gravity/gauge theorem surface, not a
universality claim, and not a literal cosmological dynamics claim.

On its declared fixed-cutoff branch, \emph{Reality as a Consensus Protocol: The Fixed-Point
Computation That Implements Physics}~\cite{ophconsensus} imports four core D1 surfaces into this
synthesis surface:
\begin{enumerate}[leftmargin=2em]
\item \textbf{Constraint-code firewall.} A bare finite overlap net is a finite constraint code:
its codewords are exactly the globally consistent states \(C=\Phi^{-1}(0)\). It is not
automatically a QECC/topological code, and its graph min-cut does not determine code distance.
Distance/min-cut, Knill--Laflamme resilience, spectral convergence, BFT liveness, and hardware
speedup enter only through separate certificates.
\item \textbf{Asynchronous confluence.} For the declared accepted repair law, the local-fit
contract makes \(\Phi\) a Lyapunov functional, hence gives termination on the finite patch net.
The fixed-cutoff union-collar gluing package supplies the local diamond on the physical quotient,
and only that confluence condition together with repair completeness yields a unique
schedule-independent normal form from a fixed initial quotient state. Same-boundary uniqueness
requires the additional unique consistent extension condition in the preserved boundary/sector
fiber.
\item \textbf{Cycle obstruction and higher-gauge defects.} On the abelian branch, global
consistency holds exactly when cycle holonomy vanishes; on the genuinely noncentral branch, the
crossed-module gluing orbit
\[
q_\Sigma \in \check H^2(N_\Sigma,H_\Sigma \to G_\Sigma)
\]
labels the full fixed-cutoff gluing orbit. It can admit multiple strict representatives related by
\(H_\Sigma\)-valued edge changes and need not determine one ordinary \(G_\Sigma\)-valued
\(1\)-cocycle class. Associator strictifiability is the separate condition that this orbit admit a
representative \((g^{\mathrm{str}},1)\); strict endpoint-only transport additionally requires at
least one allowed strict representative with trivial represented loop holonomy.
\item \textbf{Gauge quotient and observable-level confluence.} The repair law descends to the
overlap-invariant quotient, and the induced terminal state on the declared physical observable
algebras is unique there even when microscopic representatives differ by gauge or sector
relabelings inside one quotient-local glued state.
\item \textbf{Record algebra and stability.} On the declared fixed-cutoff observer-accessible
operator surface, central record projectors carry the Born/L\"uders rules directly, while
approximate record projectors inherit explicit \((\varepsilon,\delta_{\mathrm{rec}})\) stability
bounds on that same event surface. This is a theorem about the stated algebraic record interface,
not a requirement that OPH first rebuild every mathematical ingredient from operational records alone.
\end{enumerate}

The consensus paper is equally explicit about the imported repair-law data and what sits
outside the fixed-cutoff theorem stack. The declared repair step includes the
touched-overlap local-fit contract and the union-collar gluing package on the physical quotient;
the branch conditions above that step are repair completeness and, on the Petz branch, the stated
support/CPTP clause. On that same fixed-cutoff surface, exact normal-form computation is
finite-state and decidable, automatic approximate stability is only collar-local through the
splice and record estimates, and long-run noisy approximate consensus is theorem-grade only after
a fair-block contraction certificate is supplied for the chosen exported patch-net family. That
certificate boundary is not a dependency for the support-visible BW theorem, local Einstein
branch, receipt-conditional compact-gauge reconstruction, or realized Standard Model branch.

\section{Particle-Spectrum Branch}

The particle branch follows the same logical order as
\emph{Deriving the Particle Zoo from Observer Consistency}~\cite{ophparticles}.
One first fixes the compact-gauge classification basis, applies Minimal Admissible
Realization (MAR) to the realized one-Higgs branch to identify the Standard Model quotient, and only then asks how transport-stable overlap data organize the
observed particle families.

\paragraph{Structural carrier and particle-gate package.}
On the realized compact-gauge branch, the structural carrier roles are fixed by the compact
gauge and MAR-admissibility chain:
\[
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6},
\qquad
N_c=3,
\qquad
N_g=3.
\]
This does not determine quantum-particle masses. The compact paper separately proves that explicit
Maxwell, perturbative pure-Yang--Mills, and pure-Einstein quadratic actions have transverse or TT
classical massless modes on their stated backgrounds and phases. Photon, gluon, or graviton
particle language additionally requires a positive-energy physical quantization, positive-residue
two-point pole, and the appropriate asymptotic/deconfinement receipt.

\paragraph{Proof route.}
The proof route is the one developed in
\emph{Recovering Relativity and the Standard Model from Observer Overlap Consistency}~\cite{ophcompact}
and
\emph{Deriving the Particle Zoo from Observer Consistency}~\cite{ophparticles}.
Under the explicit compact-gauge refinement receipt, coherent bosonic pullback ladder, symmetry,
and forgetful-fiber conditions of the compact paper, the surviving transportable edge-sector category reconstructs a compact internal
symmetry group. MAR then selects the realized admissible branch, anomaly freedom
fixes the hypercharge lattice, the minimal coupled carrier fixes \(N_c=3\), and the same
one-Higgs quark branch fixes \(N_g=3\). The particle branch builds on that structural skeleton and does not bypass
it.

\scriptsize
\setlength{\tabcolsep}{2pt}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.175\textwidth}>{\raggedright\arraybackslash}p{0.165\textwidth}>{\raggedright\arraybackslash}p{0.225\textwidth}>{\raggedright\arraybackslash}p{0.325\textwidth}@{}}
\toprule
Sector & Claim tier & What is fixed here & Boundary to stronger claim \\
\midrule
\endfirsthead
\toprule
Sector & Claim tier & What is fixed here & Boundary to stronger claim \\
\midrule
\endhead
\bottomrule
\endfoot
Carrier roles and classical modes & structural group/content theorem plus conditional quadratic-action theorem & realized quotient, \(N_c=3\), \(N_g=3\); two Maxwell transverse modes, \(2\dim G\) perturbative Yang--Mills modes, and two Einstein TT modes on stated branches & no zero-GeV particle row until the physical Hilbert-space, pole-residue, and phase gates pass \\
Electroweak bosons & validation branch + exact sidecar & target-free continuation rows plus the exact frozen-repair pair \(M_W=80.377~\mathrm{GeV}\), \(M_Z=91.18797809193725~\mathrm{GeV}\) & claim ledger records the validation scope \\
Fine-structure endpoint & comparison coordinate + source audit trunk & measured endpoint \(\alpha^{-1}(0)=137.035999177(21)\) with CODATA-derived comparison pixel \(P_C=1.6309682094\ldots\); source/root value \(\alpha_{\mathrm{root}}^{-1}=136.9948351646\ldots\); mixed-provenance no-hadron diagnostic \(A_{\alpha_U}^{\mathrm{fp}}=137.0359595008\ldots\); bookkeeping factor \(C_{24,Q}=1.00096478597323262538\ldots\) & source-only promotion requires a no-target-leak OPH-QCD spectral payload and same-scheme integrated endpoint certificate; neither the comparison pixel nor the residual supplies that source map \\
Higgs/top stage & exact source-only D11 split theorem on the declared D10/D11 running, matching, and threshold surface + compare-only exact sidecar & shared scalar \(\rho_{HT}\), source-only split selectors, and the declared D11 Jacobian together with an exact Higgs/top inverse pair & the split theorem is closed on the declared quantitative surface; the inverse pair is compare-only; the auxiliary direct-top PDG codomain is compare-only and is closed as a corpus-limited no-go \\
Quark family & selected-class theorem + exact supporting surfaces & exact running quark sextet together with explicit exact forward Yukawas on the public physical quark frame class \(f_P\) & selected-class closure on \(f_P\); supporting exact surfaces and the separate mass bridge are carried by Ref.~\cite{ophparticles}; global classification of all public quark frame classes is closed as a corpus-limited no-go; this surface does not derive the physical strong-CP invariant or prove its vanishing \\
Charged leptons & continuation branch + exact witness & exact same-family charged triple together with exact same-carrier centered readback on a target-anchored witness & same-family-only on the exact witness; theorem lane carries the closed common-shift no-go, and the determinant-line lift applies only on theorem-grade physical charged data; the theorem-grade uncentered trace lift is not emitted \\
Neutrinos & rejected target-informed weighted-cycle candidate + diagnostic sidecars & frozen comparison coordinates only; source-level PMNS, physical ordering, Majorana phases, and absolute masses are unformed & the candidate fails the NuFIT 6.1 correlated profile; its family kernel is a template, its charged basis is open and nearly degenerate, and its historical shared-basis recovery is tautological \\
Hadrons & backend-gated nonperturbative continuation & stable-channel and readout architecture are defined & source-only masses require one production backend export bundle, then executed unquenching, runtime receipt, and production systematics \\
\end{longtable}
\normalsize

\paragraph{Claim-tier boundary.}
Structural carrier roles and the realized Standard Model branch are theorem-bearing outputs;
classical propagation is conditional on the displayed action/background/phase receipts, and
quantum-particle interpretation is a stronger open gate.
The electroweak D10 branch, the Higgs/top stage, quark rows, charged-lepton rows, neutrino rows, and
hadron rows sit on their stated quantitative-closure, continuation, or nonperturbative claim tiers.
On the target-free electroweak D10 lane, the logical order is forward: the outer/inner closure relation fixes \(P\), and then \(P\) fixes \(\alpha_U(P)\),
equivalently \(t_U(P)\) and \(t_{\mathrm{tr}}(P)\), then the downstream scale data and public
electroweak rows. Measured electroweak quantities are compare-only validation targets and do
not feed back into the transmutation solve. Source payloads, same-scheme remainders, interval
certificates, and empirical hadron records document public validation and endpoint bookkeeping;
they document the fine-structure endpoint bridge but do not source-close the Ward-projected
hadronic spectral transport needed to promote the public endpoint to a source-only theorem.

\paragraph{The \(\alpha_U(P)\) source proof record.}
The electroweak hierarchy used by the clock-scale branch depends first on a source readout of the
unified diffusion coupling
\[
\alpha_U(P_\star).
\]
For a trial pixel \(P\), define
\[
M_U(P)=E_\star e^{-2\pi}P^{1/6},
\qquad
E_{\mathrm{cell}}(P)=\frac{E_\star}{\sqrt P}.
\]
On the realized color branch,
\[
N_c=3,
\qquad
\beta_{\mathrm{EW}}:=N_c+1=4,
\]
and the transmutation scale for a candidate coupling \(a\) is
\[
v(P,a)
=
E_{\mathrm{cell}}(P)
\exp\!\left[
-\frac{2\pi}{\beta_{\mathrm{EW}}a}
\right].
\]
The source running family is
\[
\alpha_i^{-1}(\mu;P,a)
=
a^{-1}
+
\frac{b_i}{2\pi}
\log\!\left(\frac{M_U(P)}{\mu}\right),
\qquad i=1,2,3.
\]
The beta-coefficient packet \((b_1,b_2,b_3)\), matching convention, threshold packet, and
renormalization convention are part of the source proof record. They are declared before any
comparison with measured electroweak or gravitational data.

The hypercharge coupling is
\[
\alpha_Y(\mu;P,a)=\frac35\alpha_1(\mu;P,a).
\]
The source \(Z\)-scale is a fixed point of the source equations, not an inserted measured mass:
\[
\mu_Z(P,a)
=
\frac{v(P,a)}{2}
\sqrt{
4\pi\alpha_2(\mu_Z;P,a)
+
4\pi\alpha_Y(\mu_Z;P,a)
}.
\]
For \(G=\mathrm{SU}(2),\mathrm{SU}(3)\), define the finite representation heat-kernel sums
\[
Z_G(t)=\sum_R d_R e^{-tC_2(R)},
\qquad
\bar\ell_G(t)
=
\frac{1}{Z_G(t)}
\sum_R d_R e^{-tC_2(R)}\log d_R.
\]
The source heat-kernel parameters are
\[
t_2(P,a)=4\pi^2\alpha_2(\mu_Z(P,a);P,a),
\qquad
t_3(P,a)=4\pi^2\alpha_3(\mu_Z(P,a);P,a).
\]
The unified-coupling residual is
\[
\Phi_U(P,a)
:=
\bar\ell_{\mathrm{SU}(2)}(t_2(P,a))
+
\bar\ell_{\mathrm{SU}(3)}(t_3(P,a))
-
\frac{P}{4}.
\]
The source value is the zero
\[
\Phi_U(P,\alpha_U(P))=0.
\]

\begin{definition}[No-hidden-free-variable admissibility]\label{def:no-hidden-free-variable-u}
The unified-coupling proof record is admissible only when the representation cutoffs, beta packet,
matching prescription, threshold packet, and renormalization convention are frozen before
comparison with measured electroweak or gravitational data:
\[
N_2,\quad N_3,\quad (b_1,b_2,b_3),\quad
\hbox{matching prescription},\quad
\hbox{threshold packet},\quad
\hbox{renormalization convention}.
\]
None of these may be selected by minimizing the error against
\[
M_W,\quad M_Z,\quad \alpha_s(M_Z),\quad \sin^2\theta_W,\quad v_{\mathrm{exp}},
\quad G_{\mathrm{exp}}.
\]
Tuning any of these objects after comparison with observed electroweak or gravitational data
makes the hierarchy row a calibration.
\end{definition}

\begin{theorem}[No-measured-input unified-coupling proof record]\label{thm:no-input-alpha-u}
Let
\[
\mathcal R_U
=
\bigl(
P_\star,
N_2,N_3,
I_U,
\Phi_U,
K_U,
a_U^{(0)},
r_U,
m_U,
\mathrm{DAG}_U
\bigr)
\]
be an admissible unified-coupling proof record. Here \(N_2,N_3\) are the finite
representation cutoffs for \(\mathrm{SU}(2)\) and \(\mathrm{SU}(3)\), \(I_U\subset\mathbb R_+\)
is the declared physical interval for \(\alpha_U\), \(\Phi_U\) is the heat-kernel closure
residual, \(K_U\) is an interval-Newton or Krawczyk operator, \(a_U^{(0)}\) is the displayed
candidate, \(r_U\) is the residual bound, \(m_U\) is a lower derivative bound, and
\(\mathrm{DAG}_U\) is the dependency graph.

Assume
\[
K_U(I_U)\subset \operatorname{int}(I_U),
\]
\[
|\Phi_U(P_\star,a_U^{(0)})|\le r_U,
\]
\[
|\partial_a\Phi_U(P_\star,a)|\ge m_U>0
\qquad
(a\in I_U),
\]
and assume that \(\mathrm{DAG}_U\) contains no directed path from measured electroweak masses,
measured low-energy gauge couplings, measured \(G\), Planck area, Planck mass, measured
\(\Lambda\), or any equivalent gravity-calibrated or electroweak-calibrated scale. Then there is
a unique source value
\[
\alpha_U(P_\star)\in I_U
\]
such that
\[
\Phi_U(P_\star,\alpha_U(P_\star))=0,
\]
and
\[
|\alpha_U(P_\star)-a_U^{(0)}|
\le
\frac{r_U}{m_U}.
\]
Consequently, the electroweak hierarchy
\[
\frac{v}{E_\star}
=
P_\star^{-1/2}
\exp\!\left[
-\frac{2\pi}{(N_c+1)\alpha_U(P_\star)}
\right]
\]
is no-measured-input on this proof record.
\end{theorem}

\begin{proof}
The residual \(\Phi_U(P_\star,a)\) is built from the source-side pixel \(P_\star\), declared
representation cutoffs, source transmutation law, source running law, and source \(Z\)-scale
fixed-point equation. The dependency condition excludes measured electroweak data and all
gravity-calibrated scales. The interval-Newton/Krawczyk inclusion proves existence and uniqueness
of a zero of \(\Phi_U(P_\star,a)\) inside \(I_U\). The residual estimate and derivative lower
bound give
\[
|\alpha_U(P_\star)-a_U^{(0)}|
\le
\frac{|\Phi_U(P_\star,a_U^{(0)})|}{m_U}
\le
\frac{r_U}{m_U}.
\]
Substitution into the declared transmutation law gives the displayed hierarchy. The dependency
graph contains no measured \(G\), Planck unit, measured \(M_Z\), measured \(M_W\), measured
\(\alpha_s(M_Z)\), or measured low-energy electroweak coupling ancestor, so the emitted hierarchy
is source-side on \(\mathcal R_U\).
\end{proof}

\begin{lemma}[Exponential sensitivity of the hierarchy row]\label{lem:alpha-u-sensitivity}
On the transmutation branch
\[
\frac{v}{E_\star}
=
P_\star^{-1/2}
\exp\!\left[
-\frac{2\pi}{4\alpha_U}
\right],
\]
and on a clock row whose dominant scale dependence is inherited from \(v/E_\star\), the induced
gravity readout satisfies approximately
\[
\frac{\partial\ln G}{\partial \alpha_U}
=
\frac{\pi}{\alpha_U^2}.
\]
At \(\alpha_U\simeq0.0411\),
\[
\frac{\partial\ln G}{\partial \alpha_U}
\simeq
1.86\times10^3.
\]
Therefore a certified relative gravity precision \(\eta_G\) requires
\[
|\delta\alpha_U|
\lesssim
\frac{\eta_G}{1.86\times10^3}.
\]
\end{lemma}

\begin{proof}
For \(\beta_{\mathrm{EW}}=4\),
\[
\ln(v/E_\star)
=
-\frac12\ln P_\star
-
\frac{2\pi}{4\alpha_U}.
\]
Thus
\[
\frac{\partial\ln(v/E_\star)}{\partial\alpha_U}
=
\frac{2\pi}{4\alpha_U^2}
=
\frac{\pi}{2\alpha_U^2}.
\]
Since the gravity row is quadratic in the clock scale,
\[
G\propto \varepsilon_{\mathrm{Cs}}^2,
\]
and the clock scale inherits this dominant factor, one obtains
\[
\frac{\partial\ln G}{\partial\alpha_U}
=
2\cdot\frac{\pi}{2\alpha_U^2}
=
\frac{\pi}{\alpha_U^2}.
\]
\end{proof}

\begin{remark}[Digits policy]\label{rem:gravity-digits-policy}
The exponential branch allows precision only to the extent that the source proof records carry
interval bounds. The number of printed digits in \(G_{\mathrm{SI}}\) may not exceed the precision
certified by \(\mathcal R_U\), \(\mathcal R_{\mathrm{QCD}}\), \(\mathcal R_{\mathrm{flav}}\), and
\(\mathcal R_{\mathrm{Cs}}\). A display such as
\[
\varepsilon_{\mathrm{Cs}}
=
2\pi\nu_{\mathrm{Cs}}\sqrt{\hbar G_{\mathrm{ref}}/c^5}
\]
is a calibration checksum unless the full source stack emits the same interval with a no-\(G\)
dependency graph.
\end{remark}

\paragraph{No-\(G\) clock hierarchy for the gravity scale.}
The numerical gravity row uses the dimensionless cesium clock gap
\[
\varepsilon_{\mathrm{Cs}}
:=
\frac{\hbar\omega_{\mathrm{Cs}}}{E_\star},
\qquad
E_\star:=\frac{\hbar c}{\ell_\star},
\qquad
\omega_{\mathrm{Cs}}=2\pi\nu_{\mathrm{Cs}}.
\]
The size of this gap is a hierarchy problem for the OPH scale branch. The gap is represented as a
factorized source-side readout. The source-only scale branch is accepted as no-\(G\) only when the
gap factorizes through source-side dimensionless physics:
\[
\mathcal R_\gamma
=
\mathcal R_U
+
\mathcal R_\alpha
+
\mathcal R_{e}^{\mathrm{abs}}
+
\mathcal R_{\mathrm{QCD/nuc}}^{133\mathrm{Cs}}
+
\mathcal R_{\mathrm{atom}}^{133\mathrm{Cs}}.
\]
Here \(\mathcal R_U\) emits \(\alpha_U(P_\star)\) and the electroweak scale,
\(\mathcal R_\alpha\) emits the electromagnetic coupling used by the atomic Hamiltonian,
\(\mathcal R_e^{\mathrm{abs}}\) emits the electron absolute mass ratio,
\(\mathcal R_{\mathrm{QCD/nuc}}^{133\mathrm{Cs}}\) emits the cesium nuclear source packet, and
\(\mathcal R_{\mathrm{atom}}^{133\mathrm{Cs}}\) emits the hyperfine spectral gap from those
dimensionless data.

At leading OPH source level, the electroweak hierarchy is generated by the branch-fixed
transmutation law
\[
\frac{v}{E_\star}
=
P_\star^{-1/2}
\exp\!\left[
-\frac{2\pi}{(N_c+1)\alpha_U(P_\star)}
\right],
\qquad
N_c=3.
\]
Thus the weak-to-UV ratio is generated from the dimensionless source data
\(P_\star\), \(N_c\), and \(\alpha_U(P_\star)\). The cesium gap then has the schematic
source form
\[
\varepsilon_{\mathrm{Cs}}
=
\mathcal H_{\mathrm{Cs}}
\left(
\alpha_\star,
\frac{v}{E_\star},
\frac{\Lambda_{\mathrm{QCD}}}{E_\star},
y_e,
y_q,
\hbox{nuclear data},
\hbox{atomic corrections}
\right),
\]
where all arguments are dimensionless source outputs on the declared branch. In leading
hyperfine scaling this contains the familiar structure
\[
\varepsilon_{\mathrm{Cs}}
\sim
\mathcal C_{\mathrm{Cs}}\,
\alpha_\star^4
\frac{m_e^2}{m_pE_\star},
\]
with relativistic, many-body, recoil, QED, finite-nuclear-size, and nuclear-moment corrections
absorbed into \(\mathcal C_{\mathrm{Cs}}\).

\begin{definition}[Cesium source packet]\label{def:cs-source-packet}
A source-only cesium packet is
\[
\mathcal D_{\mathrm{Cs}}^{\mathrm{src}}
=
\left(
\alpha_\star,\,
\frac{m_e}{E_\star},\,
\frac{\Lambda_{\mathrm{QCD}}}{E_\star},\,
\{y_q\},\,
\mathcal N_{133},\,
\mathcal B_{\mathrm{atom}}^{\mathrm{Cs}}
\right).
\]
\(\mathcal N_{133}\) contains the source-side nuclear data for \({}^{133}\mathrm{Cs}\), including
nuclear spin, magnetic moment, magnetization distribution, charge radius, recoil data, and
finite-size data. \(\mathcal B_{\mathrm{atom}}^{\mathrm{Cs}}\) contains the atomic many-body,
relativistic, QED, recoil, and finite-nucleus correction package. Every object in
\(\mathcal D_{\mathrm{Cs}}^{\mathrm{src}}\) is dimensionless and has no dependency path from
measured \(G\), Planck area, Planck mass, Planck time, measured \(\Lambda\), or an algebraically
equivalent gravity-calibrated scale.
\end{definition}

\begin{definition}[OPH cesium Hamiltonian]\label{def:oph-cs-hamiltonian}
Given \(\mathcal D_{\mathrm{Cs}}^{\mathrm{src}}\), define the dimensionless cesium Hamiltonian
\[
\widehat H_{\mathrm{Cs}}^{\mathrm{OPH}}
=
\widehat H_{\mathrm{DC}}
+
\widehat H_{\mathrm{Breit}}
+
\widehat H_{\mathrm{QED}}
+
\widehat H_{\mathrm{recoil}}
+
\widehat H_{\mathrm{nuc}}
+
\widehat H_{\mathrm{manybody}}.
\]
The hats indicate that every term is measured in units of \(E_\star\), not in SI units and not in
Planck units inferred from measured \(G\).
\end{definition}

\begin{theorem}[No-\(G\) OPH clock-hierarchy theorem]\label{thm:no-g-clock-hierarchy}
Assume the local pixel proof selects \(P_\star\). Assume the unified-coupling proof record
\(\mathcal R_U\) of Theorem~\ref{thm:no-input-alpha-u} emits \(\alpha_U(P_\star)\) and
\[
\frac{v}{E_\star}
=
P_\star^{-1/2}
\exp\!\left[
-\frac{2\pi}{(N_c+1)\alpha_U(P_\star)}
\right].
\]
Assume the electromagnetic endpoint branch \(\mathcal R_\alpha\) emits \(\alpha_\star\), the
charged-lepton absolute-scale branch \(\mathcal R_e^{\mathrm{abs}}\) emits
\[
\frac{m_e}{E_\star}
=
\frac{y_e}{\sqrt2}\frac{v}{E_\star},
\]
the QCD/nuclear branch \(\mathcal R_{\mathrm{QCD/nuc}}^{133\mathrm{Cs}}\) emits
\(\mathcal N_{133}\), and the atomic branch
\(\mathcal R_{\mathrm{atom}}^{133\mathrm{Cs}}\) supplies isolated spectral enclosures
\[
J_{F=3},\qquad J_{F=4}
\]
for the source-only Hamiltonian
\[
\widehat H_{\mathrm{Cs}}^{\mathrm{OPH}}
=
\widehat H_{\mathrm{DC}}
+
\widehat H_{\mathrm{Breit}}
+
\widehat H_{\mathrm{QED}}
+
\widehat H_{\mathrm{recoil}}
+
\widehat H_{\mathrm{nuc}}
+
\widehat H_{\mathrm{manybody}}
\]
with disjoint intervals and certified hyperfine gap
\[
\varepsilon_{\mathrm{Cs}}
=
\lambda_{F=4}(\widehat H_{\mathrm{Cs}}^{\mathrm{OPH}})
-
\lambda_{F=3}(\widehat H_{\mathrm{Cs}}^{\mathrm{OPH}}).
\]
Assume further that the combined dependency graph
\[
\mathrm{DAG}_{\mathrm{Cs}}
=
\mathrm{DAG}
\left(
\mathcal R_U,
\mathcal R_\alpha,
\mathcal R_e^{\mathrm{abs}},
\mathcal R_{\mathrm{QCD/nuc}}^{133\mathrm{Cs}},
\mathcal R_{\mathrm{atom}}^{133\mathrm{Cs}}
\right)
\]
contains no directed path from
\[
G_{\mathrm{exp}},
\qquad
\ell_P^2=\frac{\hbar G}{c^3},
\qquad
m_P=\sqrt{\frac{\hbar c}{G}},
\qquad
t_P=\sqrt{\frac{\hbar G}{c^5}},
\qquad
\Lambda_{\mathrm{exp}},
\qquad
\frac{3\pi c^3}{\hbar G},
\]
or from any algebraically equivalent gravity-calibrated scale. Then
\(\varepsilon_{\mathrm{Cs}}\) is a no-\(G\) hierarchy readout. Consequently
\[
\gamma_\star
=
\frac{\ell_\star\nu_{\mathrm{Cs}}}{c}
=
\frac{\varepsilon_{\mathrm{Cs}}}{2\pi}
\]
is non-circular, and
\[
G_{\mathrm{SI}}
=
\frac{c^5}{4\pi^2\hbar\nu_{\mathrm{Cs}}^2}
\varepsilon_{\mathrm{Cs}}^2
\]
has no measured-\(G\) ancestor.
\end{theorem}

\begin{proof}
\(\mathcal R_U\) emits the small weak ratio from \(P_\star\), \(N_c\), and
\(\alpha_U(P_\star)\), all of which are dimensionless branch data. \(\mathcal R_\alpha\) emits
the electromagnetic coupling used by the atomic Hamiltonian. \(\mathcal R_e^{\mathrm{abs}}\)
emits the electron mass ratio. \(\mathcal R_{\mathrm{QCD/nuc}}^{133\mathrm{Cs}}\) emits the
cesium nuclear source packet. Therefore every coefficient of
\(\widehat H_{\mathrm{Cs}}^{\mathrm{OPH}}\) has no measured-\(G\) ancestor. The atomic branch
gives isolated spectral enclosures for the two hyperfine levels, so the gap
\[
\varepsilon_{\mathrm{Cs}}
=
\lambda_{F=4}(\widehat H_{\mathrm{Cs}}^{\mathrm{OPH}})
-
\lambda_{F=3}(\widehat H_{\mathrm{Cs}}^{\mathrm{OPH}})
\]
is well-defined and inherits the no-\(G\) dependency condition of the Hamiltonian.

Finally,
\[
\varepsilon_{\mathrm{Cs}}
=
\frac{\hbar(2\pi\nu_{\mathrm{Cs}})}{\hbar c/\ell_\star}
=
\frac{2\pi\nu_{\mathrm{Cs}}\ell_\star}{c},
\]
so
\[
\gamma_\star=\frac{\ell_\star\nu_{\mathrm{Cs}}}{c}
=
\frac{\varepsilon_{\mathrm{Cs}}}{2\pi}.
\]
Substitution into \(G_{\mathrm{SI}}=c^3\ell_\star^2/\hbar\) gives the displayed expression
for \(G_{\mathrm{SI}}\). The only non-display parent of the expression is the source-side
\(\varepsilon_{\mathrm{Cs}}\) readout, so the gravity row is non-circular under the stated
hypotheses.
\end{proof}

\begin{remark}[Clock-certificate boundary]\label{rem:cs-clock-boundary}
The theorem above is not discharged by printing
\[
\varepsilon_{\mathrm{Cs}}
=
3.1139305134\ldots\times10^{-33}.
\]
That decimal is source-predictive only if it is emitted by
\[
\mathcal R_U
+
\mathcal R_\alpha
+
\mathcal R_e^{\mathrm{abs}}
+
\mathcal R_{\mathrm{QCD/nuc}}^{133\mathrm{Cs}}
+
\mathcal R_{\mathrm{atom}}^{133\mathrm{Cs}}.
\]
If instead it is computed as
\[
\varepsilon_{\mathrm{Cs}}^{\mathrm{cal}}
=
2\pi\nu_{\mathrm{Cs}}
\sqrt{\frac{\hbar G_{\mathrm{exp}}}{c^5}},
\]
then it is a gravity-side calibration checksum, not a source-side clock prediction. The paper
surface supplies the algebraic certificate shape and the \(\mathcal R_U\) numerical witness.
The full source-only \(\mathcal R_{\mathrm{Cs}}\) branch requires the source-only
electromagnetic endpoint, charged-lepton absolute-scale gate, source-side cesium nuclear packet,
and atomic spectral enclosure.
\end{remark}

\begin{remark}[Hadronic and nuclear certificate boundary]\label{rem:hadronic-clock-boundary}
The unresolved load-bearing pieces of the no-\(G\) SI gravity row are the hadronic/same-scheme
endpoint payload in \(\mathcal R_\alpha\) and the source-side cesium QCD/nuclear packet in
\(\mathcal R_{\mathrm{QCD/nuc}}^{133\mathrm{Cs}}\).  The displayed endpoint and
\(\varepsilon_{\mathrm{Cs}}\) rows therefore fix those payloads for checksum and comparison
purposes.  They are not counted as source-only OPH emissions.

The source-only completion route is a Ward-projected QCD/nuclear spectral certificate from a
dedicated OPH optical-compute backend, or an equivalent nonperturbative backend with manifest
provenance and systematics.  Ordinary CPU/GPU runs in this paper are not the declared source
certificate for that hadronic payload.
\end{remark}

\paragraph{Screen-normalized self-consistency for total capacity.}\label{sec:n-closure}
The global counterpart to the local \(P\)-closure is the cosmic record-closure capacity,
\[
N_{\mathrm{CRC}},
\]
the active horizon capacity at which the universe can contain observers who read back the same
boundary capacity that supports them. This synthesis paper records the derivation here, next to the
pixel derivation and the selected no-\(G\) scale certificate, because the three roles must stay
distinct. The local equation for \(P\) says that one screen cell has the same outside geometric
reading and inside electromagnetic reading. The global equation for \(N_{\mathrm{CRC}}\) says that
the whole horizon has the same outside supplied capacity and inside observer-readable cosmic record
capacity. The selected scale certificate supplies
\(\gamma_\star=\ell_\star\nu_{\mathrm{Cs}}/c\), equivalently
\(B_\star=3\pi/\ell_\star^2\), on its own observed branch.

The operational use of observation is reverse engineering, not fitting. Because OPH treats the
realized universe as a closed mathematical fixed structure, approximate measurements can identify
which basin or branch interval internal observers inhabit. The quantitative claim then requires the
OPH map on that interval to be a self-map with a contraction, derivative-sign, strict-concavity, or
equivalent uniqueness proof. The observational readout supplies \(x_0\) or the interval; the
fixed-point theorem supplies \(x_\star\). The exact \(P_\star\) and \(N_{\mathrm{CRC}}\) values must
be computed as closure endpoints.

What \(P_\star\) and \(N_\star\) determine by themselves is the dimensionless geometry. With
\[
N_\star=\frac{3\pi}{\Lambda_\star\ell_\star^2},
\qquad
P_\star=\frac{a_{\mathrm{cell}}}{\ell_\star^2},
\]
one obtains
\[
\Lambda_\star\ell_\star^2=\frac{3\pi}{N_\star},
\qquad
\Lambda_\star a_{\mathrm{cell}}=\frac{3\pi P_\star}{N_\star}.
\]
If \(\mathcal B_\ell:=\Lambda_\star N_\star\), then
\[
\mathcal B_\ell\ell_\star^2=3\pi,
\qquad
\mathcal B_\ell a_{\mathrm{cell}}=3\pi P_\star.
\]
Under the length rescaling \(L\mapsto\lambda L\), both \(P_\star\) and \(N_\star\) stay fixed while
\(\mathcal B_\ell\mapsto\lambda^{-2}\mathcal B_\ell\). Thus the two closures do not determine an
SI value for \(\mathcal B_\ell\), \(\ell_\star^2\), or \(G_{\mathrm{SI}}\) without the selected
scale certificate.
When the selected no-\(G\) scale certificate supplies \(\gamma_\star\), equivalently
\(B_\star\), the SI display is
\[
\gamma_\star=\frac{\ell_\star\nu_{\mathrm{Cs}}}{c},
\qquad
B_\star=\mathcal B_\ell=\Lambda_\star N_\star,
\qquad
\ell_\star^2=\frac{3\pi}{B_\star}.
\]
The branch certificate used by the SI gravity row is
\[
B_\star=
3.60787391468\ldots
\times10^{70}\,\mathrm{m^{-2}},
\]
which gives
\[
\ell_\star^2=
2.61228030237\ldots
\times10^{-70}\,\mathrm{m^2}.
\]
The rounded \(N_{\mathrm{scr}}\simeq3.31\times10^{122}\) display is only a capacity-scale label;
the exact \(G\) row uses the fixed-point value and the selected scale certificate. With the
Planck-2018 curvature benchmark, using only the rounded capacity would shift the Newton row at the
\(8.4\times10^{-4}\) level.

For a trial entropy capacity \(N\), the outside global readout is the de Sitter curvature term
\[
\Lambda_{\mathrm{out}}(N)=\frac{3\pi}{G N}.
\]
The \(G\) used in this capacity branch is the selected scale certificate
\(G_{\mathrm{SI}}=c^3\ell_\star^2/\hbar\), carried in geometric units as
\(G_{\mathrm{geom}}=\ell_\star^2\).
That trial value defines a candidate OPH universe: horizon size, accessible records, dilution rate,
checkpoint continuation, observer-supporting capacity, and late-time de Sitter boundary. Observers
inside that candidate universe do not see an external parameter \(N\) directly. They infer boundary
capacity from internal geometry, causal accessibility, stable records, and self-read closure. The
corresponding capacity readback map is
\[
F(N):=N_{\mathrm{read}}(N),
\]
where \(F(N)\) is the active cosmic record capacity read back by observers inside the universe
supplied with capacity \(N\). The global closure equation is
\[
\boxed{N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}}).}
\]
In words, \(N_{\mathrm{CRC}}\) is the only global capacity at which the universe can read back its
own boundary without deficit or slack.

At fixed cutoff \(r\), the finite OPH machinery makes this map explicit. Let \(\mathfrak U_{r,N}\)
be the finite OPH universe candidate with supplied active boundary capacity \(N\). The consensus
branch supplies a quotient normal-form map \(\operatorname{nf}_{r,N}\) on the declared
terminating/confluent repair surface. Let \(\operatorname{Obs}\) select the stable self-reading
observer sector, and let \(\operatorname{Cap}_{\mathrm{read}}\) return the capacity reconstructed
by that sector. Then the finite readback map has the schematic form
\[
F_r(N)=
\operatorname{Cap}_{\mathrm{read}}
\left(
\operatorname{Obs}\left(\operatorname{nf}_{r,N}(\mathfrak U_{r,N})\right)
\right).
\]
The refinement-limit map \(F\) is the cofinal limit of this finite readback construction when that
limit exists on the admissible capacity interval.

The uniqueness proof is the direct global analogue of the local \(P\)-fixed-point proof. Let
\(I\) be the admissible interval of active horizon capacities. If the OPH-derived readback map
\(F:I\to I\) satisfies
\[
0\le F'(N)\le \kappa<1
\qquad (N\in I)
\]
and the observed branch satisfies \(F(N_{\mathrm{obs}})=N_{\mathrm{obs}}\), then
\(N_{\mathrm{obs}}\) is the unique stable fixed point. Indeed, if \(N_1\) and \(N_2\) are two fixed
points, then
\[
|N_1-N_2|
=|F(N_1)-F(N_2)|
\le \kappa |N_1-N_2|.
\]
Since \(\kappa<1\), this implies \(N_1=N_2\). Banach iteration \(N_{k+1}=F(N_k)\) also converges
to the same fixed point from any starting value in \(I\).

The physical meaning of the contraction condition is that changing supplied raw capacity changes
observer-readable active capacity by less than one-for-one. Extra Hilbert-space room does not
automatically become public record capacity. It must be reachable, recordable, self-readable,
stable under repair, coupled to observer continuation, and visible on the quotient. Capacity is
physical capacity only insofar as the universe can read it.

The existing self-closing normal-form count is the finite-count representation of the same closure target. For
a candidate entropy capacity \(N\), let \(\mathcal H_{\partial,N}\) be the observer-facing horizon
record Hilbert space with \(\log\dim\mathcal H_{\partial,N}=N\), and let
\(\Omega^{\mathrm{sc}}_{r,N}\) be the terminal normal forms that are repair-closed,
observer/checkpoint-supporting, locally recovered-core closed, and whose own horizon record surface
reads back capacity \(N\). Define
\[
A_r(N):=|\Omega^{\mathrm{sc}}_{r,N}|,
\qquad
\Pi_r(N):=\frac{A_r(N)}{\dim\mathcal H_{\partial,N}}=A_r(N)e^{-N}.
\]
The subtraction by \(N\) in
\[
\log\Pi_r(N)=\log|\Omega^{\mathrm{sc}}_{r,N}|-N
\]
is not a tunable penalty; it is exactly division by the full screen Hilbert-space size \(e^N\).
Thus the count-density selector is
\[
N_{r,\star}
=
\operatorname{MAR}\arg\max_N
\left[\log|\Omega^{\mathrm{sc}}_{r,N}|-N\right].
\]
In the refinement limit this becomes
\[
N_\star
=
\operatorname{MAR}\arg\max_N
\left[\log|\Omega^{\mathrm{sc}}_N|-N\right].
\]
When the limiting pressure
\[
\ell(N):=\log|\Omega^{\mathrm{sc}}_N|-N
\]
is differentiable, the count-density proof can also be written as the stationarity fixed point
\[
T_\eta(N):=N+\eta\ell'(N),
\qquad
T_\eta(N)=N\Longleftrightarrow \ell'(N)=0.
\]
The proof certificate is the derivative-sign certificate for
\[
H_N(N):=\ell'(N),
\]
namely \(H_N(N_0)=0\) and \(H_N'(N)<0\) on the admissible interval, or the stronger concavity bound
\[
-M\le\ell''(N)\le -m<0.
\]
This certificate is another way to express uniqueness of the global self-read closure. A numerical
solver may locate a candidate root, but uniqueness and stability come from the OPH-derived
readback or pressure certificate. Software checks, when used, check the finite grammar or
transfer-function certificate; they are not a brute-force enumeration of cosmological normal
forms and are not the proof by themselves.

The observed de Sitter read-off is
\[
N_{\mathrm{obs}}
=S_{\mathrm{dS}}
=\frac{A_{\mathrm{dS}}}{4\ell_P^2}
=\frac{3\pi}{\Lambda\ell_P^2}
\simeq3.31\times10^{122}.
\]
On the observed branch,
\[
N_{\mathrm{CRC}}=N_\star=N_{\mathrm{obs}},
\qquad
\Lambda_{\mathrm{CRC}}\ell_\star^2=\frac{3\pi}{N_{\mathrm{CRC}}},
\qquad
\Lambda_{\mathrm{CRC}}=\frac{3\pi}{G N_{\mathrm{CRC}}}.
\]
The last equality is the scale-certified display. The fixed-point certificate makes this value the unique stable capacity of the self-reading
solution we inhabit, not a freely tunable creator-set parameter. Informally, \(N_{\mathrm{CRC}}\)
is the single horizon capacity at which the outside total horizon capacity and the inside
observer-accessible public record agree.

\paragraph{Outer/inner self-consistency for the pixel ratio.}\label{sec:p-closure}
This synthesis paper is the canonical place where the local pixel ratio \(P\) is defined, so the
compact and particle papers can cite one derivation rather than duplicate it. The construction has
six steps.
\begin{enumerate}[leftmargin=2em]
\item \textbf{Outer pixel ratio.} The outer-side local screen datum is the dimensionless area
ratio
\[
P:=\frac{a_{\mathrm{cell}}}{\ell_\star^2}.
\]
Here \(\ell_\star^2=3\pi/B_\star\) is supplied by the selected scale certificate. After that scale
is emitted, it is displayed in SI language as the Planck area.
\item \textbf{Exact equilibrium benchmark.} The total/bulk/edge hierarchy has one exact
self-similar balance point. Writing
\[
x(C):=\frac{S_{\mathrm{gen}}(C)}{S_{\mathrm{bulk}}(C)}
=
1+\frac{\langle L_C\rangle}{S_{\mathrm{bulk}}(C)},
\]
the self-similar balance condition
\[
\frac{S_{\mathrm{gen}}(C)}{S_{\mathrm{bulk}}(C)}
=
\frac{S_{\mathrm{bulk}}(C)}{\langle L_C\rangle}
\]
gives \(x^2-x-1=0\) and hence \(x=\varphi=(1+\sqrt5)/2\). The realized branch must sit near, but
not exactly at, this point because exact equilibrium is too symmetric to support durable records,
structure, and dynamics.
\item \textbf{Outer detuning variable.} On the declared Phase-II closure surface we parametrize
the outer-side detuning by
\[
\alpha_{\mathrm{ext}}(P):=\frac{P-\varphi}{\sqrt{\pi}},
\qquad\text{equivalently}\qquad
P=\varphi+\alpha_{\mathrm{ext}}(P)\sqrt{\pi}.
\]
\item \textbf{Source-only D10 anchor from the same pixel.} Let \(I\subset\mathbb R_+\) be the
physical pixel interval and let
\[
F_{D10}:I\longrightarrow\mathcal D_{D10}
\]
denote the declared D10 source map. For any trial \(P\in I\), the forward D10 lane emits
\[
P\longmapsto \alpha_U(P)\longmapsto (t_U(P),t_{\mathrm{tr}}(P))
\longmapsto (t_2(P),t_3(P),v(P))
\longmapsto A_Z(P)=\alpha_{\mathrm{em}}^{-1}(m_Z^2;P).
\]
\item \textbf{Ward-projected Thomson transport.} Let \(T_Q\) be the declared Ward-projected
\(\U(1)_Q\) transport operator from the \(m_Z\)-anchor to the Thomson limit. This is the endpoint
functional that reads the fixed point as \(\alpha^{-1}(0)=137.035999177(21)\). Define
\[
A_T(P):=
T_Q\bigl(A_Z(P),F_{D10}(P)\bigr)
=
\alpha_{\mathrm{Th}}^{-1}(P).
\]
The inner coupling used in the outer/inner closure is the coupling, not the inverse coupling:
\[
\alpha_{\mathrm{in}}(P):=\frac{1}{A_T(P)}.
\]
\item \textbf{Closure.} The realized pixel ratio is the fixed point for which the outer detuning
equals the inner observation coupling:
\[
\alpha_{\mathrm{ext}}(P)=\alpha_{\mathrm{in}}(P).
\]
Equivalently,
\[
H(P):=P-\varphi-\frac{\sqrt{\pi}}{A_T(P)}=0,
\qquad\text{or}\qquad
P=\varphi+\frac{\sqrt{\pi}}{A_T(P)}=\varphi+\alpha_{\mathrm{in}}(P)\sqrt{\pi}.
\]
\end{enumerate}
Writing
\[
G(P):=\varphi+\frac{\sqrt{\pi}}{A_T(P)},
\]
the closure problem is the fixed-point condition \(G(P)=P\).
On any physical interval where this induced map is a self-map and a contraction, the closure root
is locally unique.
Equivalently, the solver can use
\[
H(P):=P-\varphi-\frac{\sqrt{\pi}}{A_T(P)}
\]
and accept the unique zero of \(H\) on the declared branch interval. Observer-facing data may
localize that interval. The measured endpoint cannot replace the closure solve.

The closure interpretation assigns one screen cell two coupled roles. On the outer side it is one
cell of the screen whose displacement above the exact self-similar equilibrium \(\varphi\) sets
the geometric detuning. On the inner side the same cell emits the smallest electromagnetic
observation step available on the particle branch. The pixel ratio \(P\) is the size of that cell
in units of the scale-certificate area \(\ell_\star^2\), and the realized \(P\) is the value at which those
outer and inner readings agree. The fixed-point equation is the mathematical form of that
consistency condition. The public
root is
\[
P_\star\simeq1.6309682094,\qquad
\alpha^{-1}(0)=137.035999177(21).
\]
The value is forced on the declared branch because the same screen cell must be
one object with two compatible descriptions. The geometric detuning fixes the
outer side, the Ward-projected Thomson endpoint fixes the inner electromagnetic
side, and the fixed point is the sole shared value. The source/root audit value is
\(136.994835\ldots\). Combining it with \(\alpha_U(P_C)\), evaluated at the
CODATA-derived comparison pixel, gives the mixed-provenance no-hadron diagnostic
\(A_{\alpha_U}^{\mathrm{fp}}=137.0359595008\ldots\); it is not a source-only
prediction. A zero-momentum laboratory
measurement sees the dressed \(\U(1)_Q\) current after charged-lepton vacuum
polarization, confined-quark/hadron spectral transport, and same-scheme endpoint
matching.
The claim table records the source-audit trunk, endpoint residual, and interval-certificate
disclosures. Once the fixed point \(P_\star\) is selected, every downstream
quantity is propagated forward from that same \(P_\star\).
A separate hardware note reports an optical-cavity check of the same fixed-point geometry;
this is treated as corroborating engineering evidence.
The same closure surface also admits an inverse observational use case in which observers infer
\(P\) and total screen capacity from inside the world.

One clean refinement studies the same closure directly at zero momentum. That route would close the
electromagnetic row without transporting from the \(m_Z\) anchor. The present paper keeps the
fixed-point idea itself simple and treats that zero-momentum promotion as a separate quantitative
task.

\paragraph{Non-hadron output surface.}
For quick orientation, the non-hadron output surface consists of receipt-gated classical carrier
modes with no promoted quantum mass rows, the electroweak exact sidecar, the Higgs/top exact
sidecar, a same-family charged witness, and the
selected-class quark theorem with exact forward Yukawas on \(f_P\). The rejected weighted-cycle
neutrino candidate is retained as a comparison and falsification record, outside the exact-output
surface. This synthesis paper uses those facts as lane markers. Ref.~\cite{ophparticles}
carries the exact values, supporting surfaces, diagnostic sidecars, and per-sector caveats.

\paragraph{Extended derivation.}
The structural-to-family route and the full per-sector claim-tier audit are developed in
\emph{Deriving the Particle Zoo from Observer Consistency}~\cite{ophparticles}.

\section{Screen Microphysics, Records, and Observer Continuation}

The screen-microphysics lane is the engineering side of the paper corpus. It asks
whether some microscopic model might exist in principle and gives one explicit regulated
carrier architecture: a federation of finite observer patches with echosahedral multi-port
interfaces, recurrent toroidal subchannels, exposed overlap data, records, repair instruments,
and observer-facing interfaces all made concrete at fixed cutoff. A spherical screen is used
there only as an observer-facing regulator chart for support-visible cuts, not as a claim that
the universe is a literal spherical quantum computer.

This lane has five theorem-bearing components. First, the reference architecture itself is
explicit. Second, the regulated patch-net embedding theorem is closed on its fixed-cutoff
object/local-interface surface, and the edge-sector thermal/Casimir branch carries an explicit
fixed-cutoff law with one compact lift above that theorem surface.
Third, the fixed-cutoff measurement/Born-rule package is closed on its declared operator and
record-event surface. Fourth, the fixed-cutoff
Bell/CHSH package is closed on the declared two-wing surface. Fifth, the
checkpoint/restoration observer package is closed. The downstream boundaries on this lane are
packet-level quotient closure where one wants an autonomous exported dynamics,
compact-group/Peter--Weyl bookkeeping on the D10/compact surfaces, fair-block contraction
certificates for long-run noisy approximate consensus on exported packet nets, and model-family
universality. The
support-visible BW / geometric-modular / local-Einstein closure lives on the companion recovered-core
papers rather than on this fixed-cutoff engineering lane. A reconstruction of Hilbert, \(C^*\)- or von Neumann algebra
structure, Born probabilities, trace structure, and entropy from operational records alone remains
a separate question outside this synthesis lane.

\paragraph{Reference-architecture takeaway.}
The synthesis-level point is that the regulated screen-side architecture supplies a concrete
habitat in which local observables, overlap observables, record registers, and synchronization
maps can all be written without pretending to identify a unique final UV completion. Hardware
evidence is not imported by this synthesis theorem surface unless it appears in a public,
hash-stable OPH evidence bundle. The OPH-FPE simulator repository is the corresponding finite-run
software surface for emitted receipts and replayable OPH experiment bundles~\cite{ophfpe}.

\paragraph{Imported theorem from Ref.~\cite{ophmicrophysics} (Fixed-cutoff record algebra and Born-L\"uders package).}
For each completed compare/write/verify slice of the regulated microphysics, the declared pointer
and overlap-sector projectors generate a finite commutative central record algebra
\[
\mathcal Z_{\mathrm{rec}}.
\]
Every observer-accessible event \(E\) in that algebra has probability
\[
\mathbb P(E)=\operatorname{Tr}(\rho P_E),
\]
and conditioning on \(E\) gives the operational post-measurement state
\[
\rho\!\mid_E = \frac{P_E \rho P_E}{\operatorname{Tr}(\rho P_E)}.
\]
If a practical readout instead uses projectors \(Q_a\) with commuting central reference
projectors \(\widehat Q_a\) on the same declared slots and
\[
\delta_{\mathrm{rec}}=\max_a \|Q_a-\widehat Q_a\|,
\]
then
\[
\|[Q_a,Q_b]\|\le 4\,\delta_{\mathrm{rec}},
\]
and any accessible-state perturbation \(\|\widetilde\rho-\rho\|_1\le\varepsilon\) changes each
declared elementary record-event probability by at most \(\varepsilon+\delta_{\mathrm{rec}}\).

\paragraph{Imported theorem from Ref.~\cite{ophmicrophysics} (Fixed-cutoff Bell / CHSH package).}
On the declared fixed-cutoff physical observable algebra, fix commuting left/right wing
subalgebras, central binary setting registers, binary projective readouts on each wing, and a
physical source state on the joint wing algebra. Then the compare slice carries the joint law
\[
p(a,b\mid x,y)
=
\operatorname{Tr}\!\bigl(\rho_{LR}\,P_{a|x}^{(L)}P_{b|y}^{(R)}\bigr),
\]
the local marginals are independent of the remote setting, the Bell correlators satisfy
\[
E(x,y)=\operatorname{Tr}\!\bigl(\rho_{LR}\,A_xB_y\bigr),
\]
and the CHSH combination obeys
\[
\bigl|E(0,0)+E(0,1)+E(1,0)-E(1,1)\bigr|
\le
2\sqrt2.
\]
If the source family contains an explicit two-qubit branch with the stated Pauli readouts, the
same fixed-cutoff surface saturates \(2\sqrt2\) exactly on that branch. The source-state input
is explicit: the theorem derives the Bell law and the Tsirelson bound from the stated
fixed-cutoff operator surface, while Bell-pair preparation and two-qubit factor structure are
stated branch conditions.

\paragraph{Imported theorem from Ref.~\cite{ophmicrophysics} (Checkpoint/restoration and observer backup).}
For an observer patch \(P_O\), let the checkpoint data consist of the observer-facing record
algebra, the accessible local state, the future update schedule, and the externally visible
overlap interface data. Exact restoration reproduces the full future law of observer-accessible
events, while an \(\varepsilon\)-accurate restoration changes that future law by at most
\(\varepsilon\) in total variation.

\paragraph{Observer-facing conclusion.}
The theorem-level content is modest but sharp: the paper corpus supplies a fixed-cutoff measurement interface,
a fixed-cutoff checkpoint/restoration package, and an operational observer-identity criterion on
observer-accessible event algebras. Stronger substrate-selection or strange-loop closure claims
are outside the recovered theorem package.

\paragraph{Extended derivation.}
The fixed-cutoff edge-law, measurement, Born-rule, Bell/CHSH, and checkpoint/restoration packages are developed in
\emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer Synchronization in OPH}~\cite{ophmicrophysics}.

\section{Worldsheet/String Branch}

The synthesis paper carries the string/worldsheet branch on the same theorem boundary used across
the paper corpus: a genuine theorem-level bridge from the edge-sector theorem surface to
the two-dimensional Yang--Mills partition function, followed by a controlled large-\(N_{\mathrm{edge}}\)
effective-description theorem on the stated branch. This two-dimensional heat-kernel partition
statement and declared-branch large-edge effective description sit beside the compact paper's
conditional support-visible compact-gauge four-dimensional Yang--Mills form and repair-gap
theorems, whose continuum identification and gap transport require the separately named receipts.

\paragraph{Imported theorem (Heat-kernel edge-sector bridge).}
Import the fixed-cutoff same-overlap edge-law package from
\emph{Federated Echosahedral Screen Microphysics}~\cite{ophmicrophysics}.
Under the same overlap-gauge realization and local-Gibbs/MaxEnt edge branch, the edge-sector
weights satisfy
\[
p_R(t)\propto d_R e^{-t C_2(R)}.
\]
Consequently the edge partition function matches the standard two-dimensional Yang-Mills
heat-kernel form. The compact paper carries OS/Wightman-strength continuum reconstruction for the
four-dimensional Euclidean Yang--Mills form and the OPH mass-gap claim separately on the
support-visible compact-gauge branch.

\paragraph{Imported proof route.}
The microphysics source surface carries the fixed-cutoff thermal/Casimir law on the declared
overlap interface. Peter--Weyl decomposition~\cite{peterWeyl27}
then identifies the resulting sum with the standard heat-kernel expression for
two-dimensional Yang-Mills on the compact-group refinement lift.

\paragraph{Compact-carrier theorem.}
Writing the closed edge partition function as
\[
Z_{\mathrm{edge}}(t)=\sum_R d_R^2 e^{-tC_2(R)},
\]
the compact carrier states the exact bridge itself as a named theorem: Peter--Weyl identifies it with the compact-group heat kernel at the identity,
\[
Z_{\mathrm{edge}}(t)=K_t(1).
\]
The Chapman--Kolmogorov gluing law for \(K_t\) is the precise sense in which collar sewing
matches the two-dimensional Yang--Mills heat-kernel surface before any large-\(N_{\mathrm{edge}}\)
continuation is invoked.
The compact carrier is a partition-identity theorem on its stated branch. The four-dimensional OPH
claim identifies the compact-gauge branch with the Euclidean Yang--Mills form and applies the
repair-dynamics theorem on that same support-visible branch.

\paragraph{Controlled large-\(N_{\mathrm{edge}}\) branch.}
Fix a distinct large-\(N_{\mathrm{edge}}\) realization, with \(N_{\mathrm{edge}}\neq N_c=3\), and
the fixed-\(\tau\) variable
\[
\tau=tN_{\mathrm{edge}}
\]
on a compact window \(I\). If the resulting edge free energy satisfies the compact paper's
large-\(N_{\mathrm{edge}}\) criterion, with remainder control on \(I\), then the Gross-Taylor
rewriting~\cite{grossTaylor93} is a controlled theorem-level worldsheet effective description of
the edge dynamics on that branch. Critical-superstring claims, worldsheet CFT closure, anomaly
cancellation, and full massless-spectrum matching are outside the recovered core theorem package.

\paragraph{Higher-gauge continuation slot.}
The genuinely noncentral crossed-module gluing data on cuts provide the natural continuation-level
slot for \(B\)-field / gerbe data in any string-style reorganization of the OPH edge sector. This
is a structural analogy only; it is not an open/closed-string boundary formalism or a
critical-string theorem.

\section{Cross-Lane Theorem Boundary and Continuation Directions}

The paper corpus has the following theorem boundary:

\begin{enumerate}[leftmargin=2em]
\item The fixed-cutoff collar, higher-gauge, consensus, record, Bell/CHSH, checkpoint, and
restoration packages are theorem-bearing on their stated finite-regulator surfaces.
\item Physical UV uniqueness is quotient-level and stable under inert ancillas. OPH fixes terminal
values on declared physical observables, not a unique microscopic representative.
\item The Lorentz/null-modular/Einstein chain is closed on the support-visible refinement/scaling
branch by the finite cap-normal BW scaling theorem on the prime geometric subnet: fixed-collar
Markov replacement with carried \(r_{\mathrm{FR}}\), \(\delta^{\mathrm M}\), and regularized
modular remainders, support-readable modular covariance, support-order faithfulness, BW framing,
held-out oriented cross-ratio rigidity, and independently normalized geometric \(2\pi\)-KMS
convergence make the cap modular automorphism geometric. The compact cap-normal theorem then
identifies \(S^2\) with projective future null rays \(q(\Omega)=(1,\Omega)\), represents
oriented round caps by \(n_C=(\cot\alpha,\csc\alpha\,\mathbf c)\), proves the signed incidence
formula, and obtains \(n_{gC}=\Lambda_gn_C\) and
\(H^3\simeq\mathrm{SO}^+(3,1)/\mathrm{SO}(3)\). This is not a finite-cell
Lorentz-invariance claim, a one-shot upgrade from small CMI to exact Markov geometry, a proof
that bare finite consensus produces the cap-normal certificate, or a populated/neutral-bulk
claim.
\item Record-populated observer-facing \(H^3\) is a separate conditional theorem: calibrated
record-conditioned modular cap responses localize a quotient-visible token only when they factor
through one point-local \(H^3\) source on a compact domain and the finite cap frame has
\(\alpha>0\). Exact data identify one point; finite noisy data produce a localization ball, and a
unique finite point requires a positive residual gap \(\Delta_{\mathrm{loc}}\). This does not
derive particle species, stress-energy, or chart-blind neutral bulk.
\item The cosmological constant branch uses the cosmic record-closure fixed point
\(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})\) and fixes the dimensionless relation
\(\Lambda_{\mathrm{CRC}}\ell_\star^2=3\pi/N_{\mathrm{CRC}}\) on the same Einstein branch. Once the
selected scale certificate supplies \(G_{\mathrm{geom}}=\ell_\star^2\), this is the familiar display
\(\Lambda_{\mathrm{CRC}}=3\pi/(G_{\mathrm{geom}}N_{\mathrm{CRC}})\). Its count-density
representation is
\(N_\star=\operatorname{MAR}\arg\max_N(\log|\Omega^{\mathrm{sc}}_N|-N)\). On the observed branch
this readback fixed point is the de Sitter entropy capacity.
\item Compact gauge reconstruction uses the theorem-produced combined transportability criterion and fixed-cutoff tensor-generated bosonic sector category. On a cofinal tail carrying the explicit compact-gauge refinement receipt, the bosonic refinement ladder and compatible forgetful fibers reconstruct a compact group from sectors with strictifiable central or higher-associator defects and at least one allowed trivial-holonomy strict representative. That is the classification stage. The receipt-certified MAR-admissible witness data plus the explicit one-Higgs matter package then select the realized Standard Model quotient, exact hypercharge, \(N_c=3\), and \(N_g=3\).
\item The particle branch is sector-split: electroweak \(W/Z\) is a validation pair, Higgs/top is exact on its declared quantitative surface, selected-class quarks close on their declared public frame class, the weighted-cycle neutrino candidate is rejected and has no theorem surface, the physical strong-CP invariant is not emitted by this surface, charged-lepton source landing from \(P\) to physical charged data is a corpus-limited no-go boundary, the auxiliary direct-top PDG row is compare-only, and source-only hadron masses require a production OPH backend.
\item The string/worldsheet branch is a controlled heat-kernel continuation branch. The critical-string selector is a separate gate on top of that edge-language branch.
\end{enumerate}

\paragraph{Local unification boundary.}
At the synthesis level, one local unification surface is explicit and one uniform theorem tier for
\(c\), \(G\), \(W\), \(Z\), and \(H\) is absent. The declared local input \(P\) governs the
electroweak/Higgs trunk and fixes the matching between cell area and edge entropy. The gravity
normalization is emitted by the selected scale certificate, while the invariant
causal speed \(c\) is structural from the Lorentz branch and gains its SI label only on the local
readout package.

{\centering
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.11\textwidth}>{\raggedright\arraybackslash}p{0.25\textwidth}>{\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}p{0.31\textwidth}@{}}
\toprule
Quantity & Best value on the paper surface & Common paper-surface chain & Caveat \\
\midrule
\(c_\star\) & \(299792458~\mathrm{m/s}\) by SI definition & structural Lorentz/BW branch \(\rightarrow\) common invariant null cone/speed \(\rightarrow\) SI unit convention & the common cone and dimensionless speed equality are structural; the decimal magnitude is not predicted \\
\(G\) & \(6.674299995910528\times10^{-11}~\mathrm{m^3\,kg^{-1}\,s^{-2}}\) on the stated local extension surface & \(\gamma_\star=\ell_\star\nu_{\mathrm{Cs}}/c\), \(B_\star=3\pi/\ell_\star^2\), \(a_{\mathrm{cell}}=P\ell_\star^2\), \(\ellbar_{\mathrm{shared}}=P/4\), \(G_{\mathrm{SI}}=c^3\ell_\star^2/\hbar\) & the pixel fixes the shared cell/edge identity and cancels in the Newton area law; the strict classical-regime clause is explicit \\
\(M_W\) & target-free continuation row \(80.37700001539531~\mathrm{GeV}\); exact compare-only sidecar \(80.377~\mathrm{GeV}\) & \(P \rightarrow \alpha_U(P) \rightarrow (t_U(P),t_{\mathrm{tr}}(P)) \rightarrow v(P) \rightarrow\) target-free electroweak repair chart \(\rightarrow M_W\) & compare-only validation sidecar; public validation records are the certified \(P\) root, source spectral measure payload, same-scheme remainder, and interval certificate \\
\(M_Z\) & target-free continuation row \(91.18797807794321~\mathrm{GeV}\); exact compare-only sidecar \(91.18797809193725~\mathrm{GeV}\) & same target-free electroweak trunk & same compare-only validation caveat \\
\(M_H\) & exact D11 split-theorem pair \(M_H=125.1995304097179~\mathrm{GeV}\), \(m_t=172.3523553288312~\mathrm{GeV}\) & same \(P\)-driven electroweak core \(\rightarrow\) D10 repair chart \(\rightarrow\) \(\rho_{HT}\) and source-only split selectors \(\rightarrow\) D11 Jacobian & Higgs row is exact on the declared running, matching, and threshold surface; the inverse sidecar is compare-only; the auxiliary direct-top PDG row is a compare-only codomain with a corpus-limited no-go boundary \\
\bottomrule
\end{tabular}
\par}

The exact-release package on that surface is local and finite: the strict classical-regime clause
and the target-free electroweak chart identity for \(W/Z\).
The familiar-unit display split on that same surface is
\[
L_{\mathrm{loc}}=\sqrt{a_{\mathrm{cell}}}\,\widehat L(P),\qquad
t_{\mathrm{loc}}=\frac{\sqrt{a_{\mathrm{cell}}}}{c}\,\widehat T(P),
\]
\[
E_{\mathrm{loc}}=\frac{\hbar c}{\sqrt{a_{\mathrm{cell}}}}\,\widehat E(P),\qquad
\Theta_{\mathrm{loc}}=\frac{\hbar c}{k_B\sqrt{a_{\mathrm{cell}}}}\,\widehat\Theta(P),
\]
with dimensionless \(\widehat L,\widehat T,\widehat E,\widehat\Theta\). The gravity-side
shared-edge identity fixes the cancellation of \(P\), while the local SI readout comes from
\(\ell_\star^2\). Meters, seconds, GeV, and Kelvin are downstream display conventions built from
the structural \(c\) row and the familiar constants \(\hbar\), \(k_B\).

\paragraph{Companion papers.}
Detailed derivations appear in Refs.~\cite{ophcompact,ophconsensus,ophmicrophysics,ophparticles,ophyangmills,ophstringselector}.

\section{Conclusion}

This paper presents the full framework on one synthesis surface. The five-axiom basis, the
derived gravity and gauge branches, the consensus formulation, the particle-spectrum branch,
the regulated screen-microphysics lane, the fixed-cutoff measurement and observer package, and the
controlled large-\(N_{\mathrm{edge}}\) worldsheet effective-description branch appear on one
common synthesis surface.

The corpus is uneven but concrete. It has a sharp
fixed-cutoff local picture, a derived recovered core for relativity and Standard-Model
structure, real particle-side quantitative outputs, and a usable microscopic engineering lane. The
scope boundaries are equally explicit: the E0 bounded-interval kernel in the null-stress
branch, the cosmic record-capacity fixed point for the global branch constant, microscopic
representative uniqueness, public validation artifacts for the D10 electroweak rows, strong CP,
full flavor/CKM closure, charged-lepton source landing from \(P_\star\), and source-only hadron masses
without a production OPH backend.
Refs.~\cite{ophcompact,ophconsensus,ophmicrophysics,ophparticles} are the depth surfaces for
sector-by-sector proofs, quantitative details, and continuation-level material. The local
cross-lane numerical surface is explicit enough to summarize concisely: the fixed point \(P_\star\)
organizes the bosonic mass trunk and the gravity-side shared edge-entropy identity beneath the
emitted local \(G\) row, while the same familiar-unit package reads meters and seconds from the
single ruler \(\sqrt{a_{\mathrm{cell}}}\) together with the structural invariant speed \(c\), and
reads GeV and Kelvin from the inverse local ruler through \(\hbar\) and \(k_B\).
