\begin{thebibliography}{99}

\bibitem{observableNormalForms}
B.~M\"uller, D.~Matscheko, and J.~Hill,
\emph{Observation-Determined Normal Forms: Stability, Obstructions, and Refinement in Constraint
and Rewrite Systems},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/observable_normal_forms.pdf}.

\bibitem{ophcompact}
B.~M\"uller, A.~Osika, M.~Poneder, K.~Xue, P.~Nguyen, M.~A.~Visser, and D.~Matscheko,
\emph{Recovering Relativity and the Standard Model from Observer Overlap Consistency},
2026.
Available at \href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.pdf}{GitHub PDF}.

\bibitem{ophconsensus}
B.~M\"uller, K.~Xue, K.~A.~Anirudha, D.~Matscheko, and J.~Hill,
\emph{Reality as a Consensus Protocol: The Fixed-Point Computation That Implements Physics},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/reality_as_consensus_protocol.pdf}.

\bibitem{ophmicrophysics}
B.~M\"uller, A.~Osika, K.~Xue, B.~Cassie, M.~A.~Visser, and D.~Matscheko,
\emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer Synchronization in OPH},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/screen_microphysics_and_observer_synchronization.pdf}.

\bibitem{ophparticles}
B.~M\"uller, A.~Osika, M.~Poneder, K.~Xue, M.~A.~Visser, and D.~Matscheko,
\emph{Deriving the Particle Zoo from Observer Consistency},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/deriving_the_particle_zoo_from_observer_consistency.pdf}.

\bibitem{ophchinu}
B.~M\"uller, A.~Osika, and D.~Matscheko,
\emph{Theoretical Bounds on \(\chi_\nu\) in Observer-Patch Holography},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/chi_nu_susceptibility_bounds.pdf}.

\bibitem{ophdarkmatter}
B.~M\"uller and D.~Matscheko,
\emph{Observer-Patch Holography and the Dark Matter Phenomenon},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/cosmology/oph_dark_matter_paper.pdf}.

\bibitem{ophyangmills}
B.~M\"uller,
\emph{Explaining the Yang--Mills Mass Gap with Observer-Patch Repair Dynamics},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/yang_mills_gap_clay_problem.pdf}.

\bibitem{ophstringselector}
B.~M\"uller,
\emph{Observer-Patch Holography as a String-Vacuum Selector: Observers, Clocks, Edge Strings, and the Bouchard-Donagi Witness},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/observer_patch_holography_as_string_vacuum_selector.pdf}.

\bibitem{ophfpe}
B.~M\"uller,
\emph{OPH-FPE: finite simulator and receipt engine for Observer-Patch Holography physics experiments},
2026.
Available at \url{https://github.com/muellerberndt/oph-physics-sim}.

\bibitem{nufit61}
I.~Esteban, M.~C.~Gonzalez-Garcia, M.~Maltoni, I.~Martinez-Soler, J.~P.~Pinheiro, and T.~Schwetz,
\emph{NuFit-6.0: Updated global analysis of three-flavor neutrino oscillations},
JHEP \textbf{12} (2024) 216, arXiv:2410.05380,
with the NuFIT 6.1 (2025) profile-table release at
\url{https://www.nu-fit.org/?q=node/309}.

\input{tex_fragments/FOUNDATIONAL_REFERENCES.tex}

\end{thebibliography}
