\section{Cosmology, Horizons, and Modular-Anomaly Continuations}
\label{app:observers-cosmology-port}

This appendix carries the cosmology- and continuation-facing technical statements for the
synthesis paper. They do not enlarge the recovered core; they make the structural continuation
boundary explicit on the synthesis surface.

\subsection{Observer Registry and Clock-Naturality Certificate Contract}
\label{app:observer-registry-clock-contract}

For finite exported observer systems, a theorem-faithful evidence bundle separates executor
metadata from observer semantics. It contains:
\begin{enumerate}[label=(\roman*),leftmargin=2em]
\item a semantic history DAG or labeled poset \(\mathsf H_O=(E_O,\preceq_O,\ell_O)\), with event
keys computed from semantic payload, observer token, visible footprint, and semantic parents;
\item a provenance envelope containing worker ID, repair iteration, retry count, queue position,
timestamp, and packet latency, none of which may enter the semantic event key unless declared as
physical input;
\item local observer registry groupoids with disjoint patch-observer, cap-observer, and
future-observer namespaces, explicit birth-event classes, continuation arrows, split/merge lineage
arrows, and overlap functors preserving those data;
\item a global registry descent certificate: cocycle agreement, trivial monodromy, no duplicate
global observer identifiers, no mixed patch/cap/future namespace collisions, and no reuse of local
anchor-patch identifiers as local observer indices;
\item observer-algebra extraction data
\[
\mathsf{ObsAlg}(\widehat q_{\mathrm{nf}})
=
(\mathcal A_O,\omega_O,\mathcal R_O,\ldots)
\]
whose outputs are state-preserving isomorphic for history-equivalent or implementation-equivalent
terminal augmented normal forms;
\item a support-cap chart map \(J_O\) natural with those observer-algebra isomorphisms; and
\item a clock instrument \(\Theta_O\) with affine reparameterization and residual bound for state,
calibration, and record-readout errors.
\end{enumerate}

\begin{theorem}[Finite observer-clock certificate soundness]\label{thm:finite-observer-clock-certificate}
On a finite exported model, suppose the augmented repair relation on
\(\widehat Q=\{(q,[\mathsf H])\}\) terminates, terminal states are exactly the consistent physical
states with completed semantic records, every augmented critical pair has a history-coherent join,
implementation steps are linearizable to semantic commits or stutters, registry descent passes the
groupoid cocycle and monodromy checks, and the observer-algebra/chart/clock maps satisfy the
state-preserving and affine-residual certificates above. Then worker count, queue order, retry
delivery, scheduler counters, and packet latency that is not declared physical input do not change
the observer-readable history class, registry class, or clock law beyond the declared affine clock
residual.
\end{theorem}

\begin{proof}
Termination plus the augmented local diamond gives confluence by Newman's lemma for terminal
history classes rather than only physical quotient states. Linearizability says every
implementation execution projects to the same semantic relation up to stutters, so executor
metadata cannot create new semantic events. Registry descent identifies the same global observer
groupoid across local presentations. State-preserving observer-algebra extraction and natural
support-cap charts transport the modular flow along the same observer identity, while the clock
instrument certificate bounds the operational readout after the declared affine reparameterization.
\end{proof}

\begin{remark}[Falsifiers]\label{rem:observer-clock-falsifiers}
The certificate fails if semantic event identifiers depend on worker IDs, timestamps, queue
positions, repair iteration counters, or retries; if duplicate retry delivery creates two visible
record commits; if two namespaces collide in the global registry; if registry cocycles or lineage
arrows fail on overlaps; if histories from two executors are not labeled-poset isomorphic; or if
clock residuals exceed the declared bound. These are public evidence-bundle failures that exceed
field-name mismatches.
\end{remark}

\subsection{Cosmological Principle}

\paragraph{\textbf{Lemma 4.1 (MaxEnt symmetry inheritance).}}
Let \(G\) act on the screen by automorphisms \(\alpha_g\). If the constraint set is
\(G\)-invariant and von Neumann entropy is \(G\)-invariant, then the MaxEnt optimizer \(\omega\)
can be taken \(G\)-invariant. If the optimizer is unique, it is automatically \(G\)-invariant.

\paragraph{\textbf{Theorem 4.2 (Isotropy from SO(3)-invariant constraints).}}
Under SO(3)-invariant constraints and MaxEnt uniqueness, the reference state satisfies
\[
\omega\circ\alpha_g=\omega
\qquad
\forall g\in \mathrm{SO}(3).
\]
The corresponding stress tensor has perfect-fluid form:
\[
\langle T_{ab}\rangle=\rho\,u_au_b+p(g_{ab}+u_au_b).
\]

\paragraph{\textbf{Theorem 4.3 (Schur-type homogeneity).}}
Let \((\Sigma,h_{ij})\) be a three-dimensional Riemannian manifold. If at every point
\(p\in\Sigma\), the curvature tensor is SO(3)-invariant, then
\[
R_{ijkl}(p)=K(p)(h_{ik}h_{jl}-h_{il}h_{jk}),
\]
and the second Bianchi identity forces \(\nabla_m K=0\), so \(K\) is constant.

\paragraph{\textbf{Corollary 4.4.}}
If OPH supplies isotropy for all observers, spatial geometry is a constant-curvature space form:
\(S^3\), \(\mathbb R^3\), or \(H^3\).

\paragraph{\textbf{Theorem 4.5 (FLRW emergence).}}
With the semiclassical Einstein equation from recoverable generalized entropy / entanglement
equilibrium, a perfect-fluid stress tensor from SO(3)-invariant MaxEnt, and positive \(\Lambda\)
from finite screen capacity, the emergent geometry is FLRW:
\[
ds^2=-dt^2+a(t)^2\left(\frac{dr^2}{1-kr^2}+r^2d\Omega^2\right),
\]
with Friedmann equations
\[
H^2+\frac{k}{a^2}=\frac{8\pi G}{3}\rho+\frac{\Lambda}{3},
\qquad
\dot H-\frac{k}{a^2}=-4\pi G(\rho+p).
\]

\subsection{Horizon-Problem Control}

\paragraph{\textbf{Theorem 6.1 (Conditional collar-CMI bound).}}
For a finite-range Gibbs tripartition \(A\)-\(B\)-\(D\) with collar width \(\delta\), assume the
uniform strong conditional matrix-mixing premise of Theorem 2.5. Then
\[
I(A:D\mid B)\le c\cdot |\partial C|_{\mathrm{UV}}\cdot e^{-\delta/\xi},
\]
with the explicit constants stated there. Ordinary two-point clustering does not supply the
premise. On the exact central-interface branch, \(I(A:D\mid B)=0\).

\paragraph{\textbf{Corollary 6.2.}}
For bounded observable \(O\) with \(\|O\|\sim1\),
\[
|\Delta\langle O\rangle|\le 2\sqrt{1-e^{-\varepsilon}}\le2\sqrt{\varepsilon}
\]
when \(\varepsilon\) is CMI in nats.
On the CMB anisotropy target \(\delta T/T\lesssim 10^{-5}\), this gives the familiar
\(\varepsilon\)-scale bound used in the horizon-problem bookkeeping:
\[
\varepsilon\lesssim 2.5\times 10^{-11}\ \text{nats},
\qquad
\frac{\delta}{\xi}\gtrsim
\ln\!\left(\frac{c\cdot |\partial C|_{\mathrm{UV}}}{\varepsilon_{\max}}\right)
\approx 24.4+\ln\!\bigl(c|\partial C|_{\mathrm{UV}}\bigr).
\]
The number \(24.4\) is only the unit-prefactor value. The boundary count cannot be dropped. With
\(\xi\approx \sqrt{P}\,\ell_\star\approx 1.28\,\ell_\star\), where \(\ell_\star\) is displayed as the usual Planck length after the selected scale certificate, the corresponding collar
condition is
\[
\delta_{\mathrm{CMB}}
\gtrsim1.28\,\ell_\star
\left[24.4+\ln\!\bigl(c|\partial C|_{\mathrm{UV}}\bigr)\right].
\]
This is a state-recovery benchmark for a bounded observable, not a derivation of CMB anisotropy.
On a continuum family the separate rate condition
\(\delta/\xi-\log|\partial C|_{\mathrm{UV}}\to+\infty\) is required.

\paragraph{\textbf{Theorem 6.3 (Homogeneity as the MaxEnt default).}}
If MaxEnt constraints are uniform across UV cells with no marked points, the MaxEnt state is
invariant under triangulation automorphisms. In the continuum limit this gives SO(3) invariance.

\paragraph{\textbf{Reading rule.}}
The cosmological-principle and horizon-homogeneity package is a branch-local theorem package on the
realized symmetric MaxEnt branch. The exact theorem-level content is:
\begin{enumerate}[leftmargin=2em]
\item SO(3)-invariant constraint data plus MaxEnt uniqueness force an isotropic reference state and
      a perfect-fluid stress tensor.
\item If the same isotropy condition holds for all observers, the Schur/Bianchi argument forces
      constant-curvature spatial slices.
\item Combined with the semiclassical Einstein branch and positive \(\Lambda\) from finite screen
      capacity, the metric takes FLRW form.
\item Markov control supplies an explicit patch-overlap anisotropy bound and the collar benchmark
      used in the CMB homogeneity bookkeeping.
\end{enumerate}
The package does not prove from the bare OPH axioms alone that the realized cosmological branch
must satisfy SO(3)-invariant constraint data, that MaxEnt uniqueness holds in every cosmological
sector, or that the observed universe saturates the displayed CMB benchmark.

\subsection{Conditional Screen-Spectrum Continuation}

\paragraph{\textbf{Theorem 6.4 (Conditional OPH screen spectrum).}}
Let \((\mathcal S_r)\) be a cofinal finite spherical OPH screen system with a schedule-independent
quotient-normal-form scalar \(q_r\), removal of the background and dipole sector, and a target-free
positive quadratic repair operator \(K_r\). If \(K_r\to K\), the finite scalar release energy
satisfies \(E_r/d_r\to A_q\), and local MaxEnt is imposed at fixed expected quadratic release
energy, then \(q_r\) converges in finite harmonic distributions to the centered Gaussian screen
field with covariance \(A_qK^{-1}\). Exact per-sample release energy would instead give a
microcanonical ellipsoid. If the certified repair-scale measure is
\(t^{\theta/2}\,dt/\Gamma(1+\theta/2)\), then
\[
K_{\rm asy}=(-\Delta_{S^2})^{1+\theta/2},
\qquad
C_{\ell,{\rm asy}}^q=A_q[\ell(\ell+1)]^{-1-\theta/2},
\]
as the large-\(\ell\) asymptotic model.  The theorem-grade finite-\(\ell\) conformal-shell family
uses the normalized gamma-ratio precision
\[
\kappa_\ell(\theta)=
\frac{\Gamma(\ell+2+\theta/2)}{\Gamma(\ell-\theta/2)},
\]
with
\[
C_\ell^q=A_q\frac{\Gamma(\ell-\theta/2)}{\Gamma(\ell+2+\theta/2)}.
\]
If \(q\) is additionally certified as the thin-shell pullback of a homogeneous curvature field with
\(\Delta_\zeta^2(k)=A_\zeta(k/k_\star)^{-\theta}\), this same operator supplies the exact
finite-\(\ell\) lift; the pure fractional Laplacian is only the asymptotic scaffold.

\paragraph{\textbf{Receipt boundary.}}
The screen theorem is a Phase III conditional continuation. It requires independent receipts for
the quotient-normal-form scalar readout, the positive repair operator, the operator tilt, and the
fixed expected quadratic scalar release energy. Fawzi--Renner/Markov-collar observable control supplies upper bounds on
release observables; it is not an amplitude equality and does not by itself determine
\(A_\zeta\). A primordial curvature spectrum additionally needs a screen-to-radial lift certificate
with the exact Bessel kernel, radial prior/null-space report, and forward-projection residual. No
physical TT/TE/EE claim follows without independent Boltzmann transfer and likelihood closure.

\subsection{Cosmological-Constant / Screen-Capacity Closure}

\paragraph{\textbf{Theorem 6.5 (D5--D6 local/global closure stack).}}
On the gravity lane, assume the local Einstein branch has been recovered only modulo
\(\Lambda g_{ab}\), the cosmic record-capacity fixed point
\[
N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}}),
\]
its observed-branch de Sitter entropy readout
\[
N_{\mathrm{CRC}}=S_{\mathrm{dS}},
\]
\noindent the standard de Sitter entropy relation
\[
S_{\mathrm{dS}}=\frac{A_{\mathrm{dS}}}{4G}=\frac{3\pi}{G\Lambda},
\]
and the standard de Sitter static-patch formulas
\[
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c}.
\]
Then:
\begin{enumerate}[leftmargin=2em]
\item local null data determine the Einstein branch only modulo \(\Lambda g_{ab}\);
\item with the selected scale certificate, the same branch has the global display
\[
G_{ab}+\frac{3\pi}{G N_{\mathrm{CRC}}}\,g_{ab}=8\pi G\,\langle T_{ab}\rangle;
\]
\item the same D6 closure fixes the entropy and dimensionless capacity relations
\[
S_{\mathrm{dS}}=N_{\mathrm{CRC}},
\qquad
A_{\mathrm{dS}}=4G N_{\mathrm{CRC}},
\qquad
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c};
\]
\item the observed cosmic age is a downstream FLRW benchmark rather than an additional theorem output.
\end{enumerate}
So the cosmological-constant package is one local/global theorem stack rather than a split local
argument plus an unrelated global readout.

\paragraph{\textbf{Scope boundary.}}
The D6 hypotheses are the local Einstein branch, the cosmic record-capacity fixed point
\(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})\), its observed-branch de Sitter entropy readout, the de
Sitter entropy relation, and the standard static-patch formulas. The local null-data route does not
by itself determine the global capacity; that value is fixed by the readback closure. The capacity
closure fixes \(\Lambda_{\mathrm{CRC}}\ell_\star^2=3\pi/N_{\mathrm{CRC}}\); the SI static-patch
scale additionally requires the selected scale certificate.

\paragraph{\textbf{Input-free capacity closure.}}
The zero-input global capacity is the cosmic record-closure fixed point. For candidate capacity
\(N\), let \(F(N)\) be the active horizon capacity read back by
stable observers inside the OPH universe supplied with capacity \(N\):
\[
F(N)=
\operatorname{Cap}_{\mathrm{read}}
\bigl(\operatorname{Obs}(\operatorname{nf}(\mathfrak U_N))\bigr).
\]
The target is
\[
N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}}),
\qquad
\Lambda_{\mathrm{CRC}}=\frac{3\pi}{G N_{\mathrm{CRC}}}.
\]
Equivalently, before the selected scale certificate is applied, the target fixes
\(\Lambda_{\mathrm{CRC}}\ell_\star^2=3\pi/N_{\mathrm{CRC}}\).
The screen-normalized density of terminal self-closing observer normal forms is the count
representation of the same target. Let \(\Omega^{\mathrm{sc}}_N\) be the terminal OPH normal forms
that are repair-closed, observer- and checkpoint-supporting, carry the recovered local package, and
whose own horizon record surface reads back capacity \(N\). Since
\(\log\dim\mathcal H_{\partial,N}=N\), define
\[
\Pi(N):=\frac{|\Omega^{\mathrm{sc}}_N|}{\dim\mathcal H_{\partial,N}}
=|\Omega^{\mathrm{sc}}_N|e^{-N}.
\]
The corresponding Minimal Admissible Realization selector is
\[
N_\star=\operatorname{MAR}\arg\max_N\left[\log|\Omega^{\mathrm{sc}}_N|-N\right].
\]
Equivalently, with \(\ell(N)=\log|\Omega^{\mathrm{sc}}_N|-N\), the OPH-derived stationarity map
\[
T_\eta(N)=N+\eta\ell'(N)
\]
has a unique stable fixed point under the derivative-sign certificate stated in the synthesis
section. Informally, this is the single balance point where the universe reads back its own
boundary without deficit or slack. On the observed branch,
\[
N_{\mathrm{CRC}}=N_\star\simeq3.31\times10^{122}.
\]
This rounded display locates the capacity scale; precision rows use the fixed-point value together
with the selected scale certificate.

\paragraph{\textbf{Capacity normalization.}}
The branch uses \(N_{\mathrm{scr}}\) as the de Sitter entropy capacity. The bare horizon ratio is
\[
N_{\mathrm{patch}}=\left(\frac{r_{\mathrm{dS}}}{\ell_P}\right)^2,
\]
so
\[
N_{\mathrm{scr}}=\pi N_{\mathrm{patch}}
=\frac{3\pi}{\Lambda\ell_P^2}.
\]
For the observed late-time scale, \(N_{\mathrm{patch}}\simeq1.05\times10^{122}\) and
\(N_{\mathrm{scr}}\simeq3.31\times10^{122}\).
These are benchmark displays, not high-precision inputs for the Newton row.

\subsection{Black-Hole Structural Package and Continuation Boundary}

The AMPS-style information trilemma assumes:
\begin{enumerate}[leftmargin=2em]
\item an outgoing mode \(B\) entangled with an interior partner \(A\) (smooth horizon),
\item late radiation \(B\) entangled with early radiation \(R\) (unitarity), and
\item monogamy of entanglement.
\end{enumerate}
The false assumption in this setting is the naive tensor factorization
\[
\mathcal H \stackrel{?}{=}
\mathcal H_{\mathrm{inside}}\otimes
\mathcal H_{\mathrm{outside}}\otimes
\mathcal H_{\mathrm{radiation}}.
\]

\paragraph{\textbf{Theorem 7.1 (Edge-center black-hole decomposition).}}
On the fixed-cutoff edge-center collar branch, assume the black-hole collar state lies in the
exact Markov class or in the idealized exact-recoverability limit used elsewhere in the paper
stack. Then the collar decomposition gives
\[
\rho_{A_\delta B_\delta D_\delta}
=
\bigoplus_\alpha p_\alpha
\left(\rho_{A_\delta b_L^\alpha}\otimes \rho_{b_R^\alpha D_\delta}\right).
\]
The glue between inside and outside is the edge-sector label \(\alpha\) in the center.
Given \(\alpha\), inside and outside factorize.

\paragraph{\textbf{Theorem 7.2 (Hawking/KMS normalization).}}
On the geometric modular branch where the horizon generator carries the standard \(2\pi\) KMS
normalization, the outside algebra is in a KMS state at inverse temperature
\[
\beta=\frac{2\pi}{\kappa}
\]
with respect to the horizon Killing generator.

\paragraph{\textbf{Corollary 7.3 (Recoverability-style interior encoding).}}
On the same fixed-cutoff collar carrier, when
\(I(A_\delta:D_\delta\mid B_\delta)\le\varepsilon\), there exists a recovery channel
\(\mathcal R_{B_\delta\to A_\delta B_\delta}\) such that
\[
\left\|
\rho_{A_\delta B_\delta D_\delta}
-
(\mathcal R_{B_\delta\to A_\delta B_\delta}\otimes \mathrm{id}_{D_\delta})(\rho_{B_\delta D_\delta})
\right\|_1
\le
2\sqrt{1-e^{-\varepsilon}}
\le2\sqrt{\varepsilon}.
\]
Here \(\varepsilon\) is in nats.
So the interior collar data are encoded in the exterior collar together with the shared cut data,
rather than supplied by an independent tensor factor.

\paragraph{\textbf{Corollary 7.4 (Discrete area spectrum and Schwarzschild transition identity).}}
The same edge-center package carries a discrete area operator
\[
L_C=\sum_\alpha (\log d_\alpha)P_\alpha,
\qquad
A_\alpha=4G_{\mathrm{geom}}\log d_\alpha=4\ell_\star^2\ln d_\alpha,
\]
and for a Schwarzschild sector transition \(d\to d'\) one has
\[
\Delta(Mc^2)=k_B T_H\ln(d'/d).
\]
On the emission branch \(d'=d/k\) with \(k>1\), the emitted line energy magnitude is
\[
E_{\mathrm{emit}}=k_B T_H\ln k.
\]

\paragraph{\textbf{Scope boundary.}}
The retained structural theorem package is exactly Theorem 7.1, Theorem 7.2, Corollary 7.3, and
Corollary 7.4. Integer-transition combs, QNM selectors, Page-type linewidth estimates, PBH burst
templates, Kerr/LIGO horizon spectroscopy templates, and any Page-curve or island closure are
outside that structural core. Those items require continuation inputs such as an integer-transition
selection rule, a semiclassical evaporation-power model, a QNM/transition identification, greybody
matching, or an explicit island prescription.

The same no-relabeling rule applies here. A finite capacity register is not an
exterior mass, an archive record is not Hawking radiation, a finite repair
spectrum is not a GR quasinormal-mode spectrum, and an exact finite recovery
threshold is not a Page time unless the corresponding independent physical
bridge supplies source-separated readout, calibration, residuals, controls, and
frozen validation targets.

\subsection{Modular-Anomaly Continuation}

\paragraph{\textbf{Theorem 9.1 (Modular additivity defect).}}
Define the collar modular additivity defect by
\[
\Delta K_\delta:=K_{ABD}-K_{AB}-K_{BD}+K_B.
\]
Then
\[
\langle \Delta K_\delta\rangle_\omega=-I(A:D\mid B)_\omega.
\]
This is a scalar recovery identity. It can enter the modular-anomaly
dark-sector continuation only after a separate matching theorem or hypothesis
identifies it with an anomalous local modular-energy source. By itself it
constructs neither a rank-two tensor nor a dark-matter theorem.

The continuation therefore reserves an anomalous tensor slot only for a finite
covariant source packet that supplies source localization,
CMI-to-modular-source matching when that route is used, rank-two
reconstruction, conservation, normalization, and universal coupling. Once
those receipts pass, the modified Einstein equation is
\[
G_{ab}+\Lambda g_{ab}
=
8\pi G\left(\langle T_{ab}\rangle+\langle T_{ab}^{\mathrm{anom}}\rangle\right),
\]
with rest-frame normalization
\[
\langle T_{00}^{\mathrm{anom}}\rangle
:=
\frac{15}{8\pi^2}\,
\frac{\delta\langle K_C^{\mathrm{anom}}\rangle}{\ell^4}.
\]
On that receipt-certified continuation surface the tensor gravitates and is
covariantly conserved. Calling it dark additionally requires the
no-electromagnetic-coupling receipt. Central or recoverability data alone do
not establish any of these properties.

If one tentatively identifies the imported D6 static-patch radius \(r_{\mathrm{dS}}\) as the
unique IR scale available to the continuation, the natural benchmark acceleration is
\[
a_0^{(\mathrm{OPH})}
:=
\frac{15}{8\pi^2}c^2\sqrt{\frac{\Lambda}{3}}
=
\frac{15}{8\pi^2}\frac{c^2}{r_{\mathrm{dS}}}
\approx
1.03\times 10^{-10}\ \mathrm{m/s^2},
\]
close to the empirical MOND scale. That numerical proximity is only a benchmark unless a separate
source/response law and a controlled galaxy-scale limit are derived. An illustrative MOND/RAR-style response would read
\[
g_{\mathrm{obs}}\approx g_b+\sqrt{a_0 g_b},
\]
but that functional form is not derived from the OPH axioms.

\paragraph{\textbf{Reading rule.}}
The scalar modular-additivity identity remains a recovery theorem. The
anomalous tensor gravitates, is conserved, and is dark only after the source,
matching, tensor, conservation, coupling, and electromagnetic-decoupling
receipts above pass. Even then, the synthesis surface keeps the entire
dark-sector package on the D12 continuation tier rather than promoting any
MOND/RAR-style law, galaxy-rotation template, or cluster phenomenology to
theorem claim tier. The imported D6 static-patch scale fixes only the benchmark
normalization. The missing inputs are the controlled nonrelativistic limit,
derived sign and closure control for the effective anomaly contribution, a
derived source/response law, proof of the relevant dominant galaxy-scale
source, lensing and cluster phenomenology, cosmological abundance and
structure-formation checks, and environment/stability bounds. Those are
continuation-level branches above the identity written here.
