\subsubsection{Source-only primordial bridge theorem}\label{subsec:primordial-bridge-theorems}

The finite screen covariance theorem is a screen theorem.  To read it as a
source-only primordial curvature spectrum one must add the following bridge
objects and receipts.  The dependency chain is
\[
\boxed{
\begin{gathered}
\operatorname{nf}(\mathcal Q_r)
\to
(\chi_r,u_r,h_r)
\to
\mathsf{BackgroundCurvatureStatus}_r
\to
(g,T_I)
\to
q_\zeta=\zeta_\rho\\
\to
\text{single clock}
\to
\text{freeze-out}
\to
\text{coherent growing mode}
\to
\Delta_\zeta^2(k).
\end{gathered}
}
\]
No successful fit of a screen \(C_\ell\) or a TT spectrum may replace one of
these hypotheses.

\textbf{Definition (background curvature branch label).}\label{def:background-curvature-branch-label}
The primordial bridge carries a finite record
\[
\mathsf{BackgroundCurvatureStatus}_r
=
(\mathsf{BranchType},\kappa,I_K,I_{\Omega_K},\mathsf{Basis},\mathsf{Top})
\]
where
\[
\mathsf{BranchType}\in
\{\textsc{FlatExact},\textsc{FlatAssumed},\textsc{OpenCurved},\textsc{ClosedCurved},\textsc{Unresolved}\}.
\]
\textsc{FlatExact} is allowed only after a direct theorem or conditional CMH receipt.  \textsc{FlatAssumed}
may run flat kernels but its outputs remain assumption-conditioned.  \textsc{Unresolved} blocks
physical promotion.  The \(H^3\) observer-facing atlas is not this record; this record comes from
the clocked FLRW slice and its spatial Levi--Civita holonomy or declared branch input.

\textbf{Definition (source stress readout).}\label{def:oph-source-stress}
On a reconstructed branch with relational metric \(g_{ab}\), let
\[
S_{\rm src}=\sum_I S_I[g,\Psi_I],
\qquad
T^I_{ab}=-\frac{2}{\sqrt{-g}}\frac{\delta S_I}{\delta g^{ab}},
\qquad
T^{\rm tot}_{ab}=\sum_I T^I_{ab},
\]
where \(I\) ranges over every active sector, including ordinary matter,
radiation, neutrinos, OPH anomaly or repair sectors, and any auxiliary source
kept in the run.  At finite regulator this is a quotient-visible map
\[
\mathsf{StressRead}_r:
\operatorname{nf}(\mathcal Q_r)\longrightarrow \{T^I_{r,ab}\}_I .
\]
All source stress components must be read from the same global normal form as
the collar scalar.

\textbf{Source-stress closure theorem.}\label{thm:oph-source-stress-closure}
Assume each \(S_I\) is relationally diffeomorphism invariant, the source
equations hold, sector exchanges satisfy
\[
\nabla_aT_I^{ab}=Q_I^b,\qquad \sum_I Q_I^b=0,
\]
and \(\mathsf{StressRead}_r\) descends to the physical quotient and converges.
Then
\[
\nabla_aT_{\rm tot}^{ab}=0.
\]
On the recovered Einstein branch,
\[
G_{ab}+\Lambda g_{ab}=8\pi G\,T^{\rm tot}_{ab}.
\]
The evidence bundle must also report the non-circular comparison
\[
E_T^{ab}=
T_{\rm src}^{ab}
-
\frac{G^{ab}+\Lambda g^{ab}}{8\pi G};
\]
using the geometric right-hand side alone is a geometry diagnostic, not a
source-only primordial receipt.

\textbf{Total-energy frame and curvature covector.}
When \(T^a{}_b\) has a unique future timelike unit eigenvector \(u^a\), define
\[
T^a{}_bu^b=-\rho u^a,\qquad
h_{ab}=g_{ab}+u_au_b,
\]
and decompose
\[
T^{ab}=\rho u^au^b+p h^{ab}+\pi^{ab},
\qquad
u_a\pi^{ab}=0,\qquad \pi^a{}_a=0.
\]
Let \(\Theta=\nabla_a u^a\) and let \(\sigma_{ab}\) be the shear.  Total
energy conservation gives
\[
\dot\rho+\Theta(\rho+p)+\sigma_{ab}\pi^{ab}=0,
\qquad
\dot f:=u^a\nabla_a f.
\]
On an expanding branch, define
\[
p_{\rm eff}=p+\frac{\sigma_{ab}\pi^{ab}}{\Theta};
\]
then \(\dot\rho+\Theta(\rho+p_{\rm eff})=0\).

\textbf{Theorem (exact total-curvature evolution).}\label{thm:oph-total-curvature-evolution}
Let
\[
\dot\alpha=\Theta/3,\qquad
\zeta_a=\nabla_a\alpha-\frac{\dot\alpha}{\dot\rho}\nabla_a\rho,
\]
and
\[
\Gamma^{\rm eff}_a=
\nabla_a p_{\rm eff}
-
\frac{\dot p_{\rm eff}}{\dot\rho}\nabla_a\rho .
\]
Then, exactly and without a long-wavelength approximation,
\[
\mathcal L_u\zeta_a
=
-\frac{\Theta}{3(\rho+p_{\rm eff})}\Gamma^{\rm eff}_a .
\]
Hence a barotropic effective source, \(p_{\rm eff}=p_{\rm eff}(\rho)\),
conserves \(\zeta_a\).

\textbf{Collar scalar corollary.}\label{cor:oph-collar-curvature}
For relational rods Lie-dragged by the total-energy flow, the collar-volume
Jacobian satisfies
\[
J_X=\lambda\sqrt{\det\sigma_{AB}},
\qquad
\frac{d}{d\tau}\frac13\log J_X=\frac{\Theta}{3}.
\]
Relative to a frozen background,
\[
q_\zeta=\frac13\log\frac{J_X}{\bar J_X}.
\]
On the uniform-total-density cut,
\[
q_\zeta=\zeta_\rho+\hbox{constant}.
\]
After removing the monopole and dipole,
\[
q=\Pi_{\ell\ge2}q_\zeta=\Pi_{\ell\ge2}\zeta_\rho,
\qquad
Z_q=1.
\]
This is the source-only quotient scalar on the OPH screen; by itself it has type
\textsc{ScreenCurvature}, not \textsc{PrimordialCurvature}.

\textbf{Definition (rank-one single-clock branch).}\label{def:oph-single-clock}
Let
\[
\mathcal F(x)=
(\rho,p_{\rm eff},\{\rho_I,p_I,Q_I\}_{I=1}^N)
\]
be the scalar source map on the source moduli space.  A branch is rank-one
single-clock when \(\operatorname{rank}d\mathcal F=1\), \(d\rho\ne0\), every
level set of \(\rho\) is connected, all sector velocities agree with \(u^a\),
and orthogonal momentum transfer vanishes or is interval-bounded.  At finite
cutoff this requires a quotient-visible clock \(\chi_r\) and a factorization
\[
\mathcal F_r=\widehat{\mathcal F}_r\circ\chi_r .
\]

\textbf{Theorem (single-clock adiabaticity).}\label{thm:oph-single-clock-adiabaticity}
On a rank-one single-clock branch,
\[
p_{\rm eff}=p_{\rm eff}(\rho),\qquad
S_a^{IJ}=3(\zeta_a^I-\zeta_a^J)=0,
\]
and the intrinsic nonadiabatic pressure and transfer covectors obey
\[
\Gamma_a^I=0,\qquad \Xi_a^I=0 .
\]
Therefore \(\mathcal L_u\zeta_a=0\).  The proof is the chain rule through the
single clock: every source scalar is a function of the same \(\chi\), and
connected \(\rho\)-fibers remove residual branch labels.

\textbf{Theorem (entropy repair gap).}\label{thm:oph-entropy-repair-gap}
Let the linearized scalar repair/evolution block be
\[
\delta Y_{n+1}=L_r\delta Y_n+\eta_n,
\]
and let \(P_\perp\) project away gauge directions, constrained zero modes, and
the adiabatic growing direction.  If there is a positive metric \(H_r\) such
that
\[
\|P_\perp L_rP_\perp\|_{H_r}\le e^{-\gamma_r}<1,
\]
then
\[
\|P_\perp\delta Y_n\|_{H_r}
\le
e^{-n\gamma_r}\|P_\perp\delta Y_0\|_{H_r}
+
\sum_{j=0}^{n-1}e^{-(n-1-j)\gamma_r}\|P_\perp\eta_j\|_{H_r}.
\]
In the unforced case the orthogonal entropy, decaying, and repair scalar
modes vanish.  Eigenvalues alone do not certify this theorem for nonnormal
repair matrices; a norm bound or a discrete Lyapunov inequality
\[
L_\perp^{\mathsf T}H L_\perp\preceq e^{-2\gamma}H
\]
is required.

\textbf{Theorem (growing-mode coherence).}\label{thm:oph-growing-mode-coherence}
Let \(X(k)\) collect the scalar initial-condition variables for curvature,
radiation, baryons, CDM/anomaly, neutrinos, and repair-sector scalars, and let
\(v_+(k)\) be the normalized adiabatic growing vector.  If the single-clock
and repair-gap theorems hold through readout and no independent stochastic
source acts afterward, then
\[
X(k)=v_+(k)\zeta(k),
\qquad
\mathcal P_X(k)=\mathcal P_\zeta(k)v_+(k)v_+(k)^\dagger .
\]
Thus \(\operatorname{rank}\mathcal P_X(k)=1\), source-side isocurvature
fractions vanish, and all species share a deterministic growing-mode phase.
Finite runs must report \(\lambda_2/\lambda_1\), \(\beta_{\rm iso}(k)\),
decaying-mode fraction, and phase-convention defects as source diagnostics.

\textbf{Theorem (screen-to-primordial bridge).}\label{thm:oph-screen-to-primordial}
Assume the geometric record and causal-area metric receipts, the collar
identity \(q_\zeta=\zeta_\rho\), source-stress closure, rank-one normal form,
positive repair gap, freeze-out, adiabatic growing-mode, isocurvature, and
phase-coherence receipts all pass.  Also assume the physical scale-bridge theorem: a source embedding with
\texttt{source\_embedding\_hash}, a physical mode basis with
\texttt{physical\_mode\_basis\_id}, a calibrated comoving coordinate \(\chi\),
mode-normalization and density-of-states receipts, and a no-post-hoc-calibration
receipt, and a \(\mathsf{BackgroundCurvatureStatus}_r\) that is not \textsc{Unresolved}.  Then the low-mode-removed OPH screen
scalar is the source-only primordial curvature field restricted to the
declared shell or radial window:
\[
q(\hat n)=
\Pi_{\ell_{\rm src}\ge2}\int d\chi\,W(\chi)\zeta_\star(\chi\hat n).
\]
For a thin shell, \(q(\hat n)=\Pi_{\ell_{\rm src}\ge2}\zeta_\star(R_\star\hat n)\).  The
forward spectrum is exactly
\[
\begin{gathered}
C_\ell^q
=
4\pi\int_0^\infty d\ln k\,
\Delta_\zeta^2(k)|\Psi_\ell^{\mathsf{BranchType}}(k)|^2,\\
\Psi_\ell^{\mathsf{BranchType}}(k)=
\begin{cases}
\int dr\,W(r)j_\ell(kr), & \mathsf{BranchType}=\textsc{FlatExact}\ \hbox{or}\ \textsc{FlatAssumed},\\
\int dr\,W(r)\Phi^{(-)}_{\ell k}(r), & \mathsf{BranchType}=\textsc{OpenCurved},\\
\int dr\,W(r)\Phi^{(+)}_{\ell k}(r), & \mathsf{BranchType}=\textsc{ClosedCurved},
\end{cases}
\end{gathered}
\]
and for a thin shell
\[
C_\ell^q
=
4\pi\int_0^\infty d\ln k\,
\Delta_\zeta^2(k)
\left|\Psi_\ell^{\mathsf{BranchType}}(k;R_\star)\right|^2 .
\]
At finite regulator the continuum integral is represented by the finite
spectral measure
\[
d\nu_r(k)=\sum_j w_{rj}\delta(k-k_{rj}),
\]
so the actual finite evidence receipt is
\[
C_{\ell_{\rm src},r}^q
=4\pi\sum_j w^{\log k}_{rj}\,
\Delta_{\zeta,r}^2(k_{rj})
|\Psi^{\mathsf{BranchType}}_{\ell_{\rm src},r}(k_{rj})|^2.
\]
Every radial node, window, and mode bin is bound to the geometry hash,
source-embedding hash, scale-certificate hash, boundary-condition hash, and
mode-basis identifier, and the evidence bundle must emit
\texttt{RADIAL\_KERNEL\_GEOMETRY\_COMPATIBILITY\_RECEIPT}.  The observed multipole \(L_{\rm CMB}\) is not
\(\ell_{\rm src}\); it is the output index of the line-of-sight transfer solver.
Cap eigenmodes, inverse cap-opening angles, and relabeled unit strings remain
diagnostic by the dimensional, angular, cap-mode, and unit-string no-go propositions.

\textbf{Physical scale dependency.}
The \(k_{rj}\) grid in the preceding equation is not a free producer field.  It is consumed only
after
\[
\texttt{PHYSICAL\_SPATIAL\_K\_RECEIPT}
\]
recomputes the comoving \(k\)-intervals from the physical geometry, scale certificate, scale factor,
finite eigenvalues, normalization, and refinement residuals.  The radial kernel and source-screen
projection additionally require
\[
\texttt{SCREEN\_TO\_PHYSICAL\_K\_ASSOCIATION\_RECEIPT}.
\]
The source covariance is a finite positive operator on the common physical mode projectors:
\[
C_{\zeta,r}\succeq0.
\]
Homogeneity and isotropy on the safe band require
\[
P_I C_{\zeta,r}P_I=\mathcal P_\zeta(k_I)P_I+E_I
\]
with a declared residual bound, together with an off-diagonal leakage report
\[
\sum_{I\ne J}|P_I C_{\zeta,r}P_J|^2.
\]
The same physical projector family is used by primordial covariance and anomaly response:
\[
\texttt{COMMON\_PRIMORDIAL\_ANOMALY\_MODE\_BASIS\_RECEIPT}.
\]
Mode freezeout and common initial surface are separate gates:
\[
\texttt{PHYSICAL\_MODE\_FREEZEOUT\_MAP\_RECEIPT},\qquad
\texttt{PHYSICAL\_FREEZEOUT\_SURFACE\_RECEIPT}.
\]
The latter contains initial data and normal derivatives on one common spacelike surface.

\textbf{Radial prior, null space, and residual receipt.}
The map above is a forward projection, not a free inversion.  With finite
bins \(p_j\) for \(\Delta_\zeta^2\),
\[
A_{\ell j}=4\pi\int_{\hbox{\scriptsize bin }j}d\ln k\,
b_j(k)|\Psi_\ell(k)|^2,
\qquad
C^q=Ap .
\]
The evidence bundle must declare the basis, support, prior \(p_0,Q\), positivity
conditions, singular spectrum of \(AQ^{-1/2}\), effective rank, null basis,
resolution kernels, prior sensitivity, and every forward residual
\[
r_\ell=C_\ell^q-\widehat C_\ell .
\]
Only after the radial prior, null-space report, positivity test, source-only
ancestry proof, finite mode-normalization receipt, common primordial/anomaly
mode-basis receipt, and forward residual pass may the run emit \(A_s\), \(n_s\),
and \(\alpha_s\).  Otherwise the typed output is
\textsc{ScreenCurvature} or \textsc{ConditionalRadialContinuation}.  If the
geometry packet is imported, the strongest possible claim tier is
\texttt{CONDITIONAL\_PHYSICAL}; \texttt{OPH\_NATIVE\_PHYSICAL} requires the
native \(\mathsf{CosmoGeomRead}_r\) theorem.

\[
\begin{array}{ll}
\mbox{\texttt{TOTAL\_STRESS\_CLOSURE\_RECEIPT}} & T_I^{ab},Q_I^a,E_T,\nabla_aT^{ab} \\
\mbox{\texttt{SINGLE\_CLOCK\_NORMAL\_FORM\_RECEIPT}} & \chi_r,\operatorname{rank}d\mathcal F,\hbox{ connected fibers} \\
\mbox{\texttt{ENTROPY\_REPAIR\_GAP\_RECEIPT}} & L_\perp,H,\gamma,\hbox{ forcing/refinement bounds} \\
\mbox{\texttt{CURVATURE\_EVOLUTION\_RECEIPT}} & \zeta_a,\Gamma_a^{\rm eff},\hbox{ evolution residual, freeze bound} \\
\mbox{\texttt{ADIABATIC\_MODE\_RECEIPT}} & S_{IJ},\Gamma_I,\Xi_I,\hbox{ growing-mode projection} \\
\mbox{\texttt{ISOCURVATURE\_BOUND\_REPORT}} & \beta_{\rm iso}(k)\hbox{ and source covariance} \\
\mbox{\texttt{PRIMORDIAL\_PHASE\_COHERENCE\_RECEIPT}} & \lambda_2/\lambda_1,\hbox{ phase and decaying-mode defects} \\
\mbox{\texttt{SCREEN\_TO\_RADIAL\_LIFT\_RECEIPT}} & W(r),R_\star,\Psi_\ell(k),\hbox{ source hashes} \\
\mbox{\texttt{RADIAL\_NULL\_SPACE\_REPORT\_RECEIPT}} & \hbox{singular values, null basis, resolution kernels} \\
\mbox{\texttt{FORWARD\_PROJECTION\_RESIDUAL\_RECEIPT}} & r_\ell,\hbox{ aggregate norms, quadrature and solver errors}.
\end{array}
\]

\textbf{Source-provenance and pooled-reducer firewall.}\label{par:source-provenance-firewall}
Let the source artifact DAG have parent-to-child edges and let \(M\) be the set
of measurement, residual, likelihood, posterior, fitted-parameter, or
measurement-calibrated nodes.  Define
\[
\tau(v)=\mathbf 1_{v\in M}\lor
\bigvee_{p\in\operatorname{Parents}(v)}\tau(p).
\]
Then \(\tau(v)=1\) exactly when \(v\) has a forbidden measurement ancestor.  The
proof is induction over a topological ordering of the DAG.  Every promoted
source node for \(\eta_R,\Gamma_{\rm rec},A_\zeta,q_{\rm IR},\ell_{\rm IR}\),
\(B_A(k,a)\), \(\rho_A(a)\), and \(N_{\rm CRC}\) must have \(\tau=0\).
Unknown source metadata fails closed.

For nonlinear estimates, shards may not average nonlinear quantities.
Each row must emit additive sufficient statistics in a commutative monoid
\((\mathcal M,\oplus)\), for example
\[
\sum w_i,\qquad \sum w_ix_i,\qquad \sum w_ix_ix_i^{\mathsf T}
\]
or, for weighted response regression,
\[
X^{\mathsf T}WX,\qquad X^{\mathsf T}Wy,\qquad y^{\mathsf T}Wy .
\]
Associativity, commutativity, complete coverage, and duplicate removal make the
pooled statistic partition-invariant; the deterministic estimator is then
evaluated only after pooling.

\textbf{Three-dimensional homogeneous lift.}\label{par:three-d-lift}
A rotationally invariant screen covariance about one observer is not a
statistically homogeneous three-dimensional primordial field by itself.  A frozen lift
\[
\mathcal L_r:V_r^{\rm screen}\to\mathcal H_r^{(3)}
\]
must define
\[
\Sigma_r^{(3)}=\mathcal L_r\Sigma_r^{\rm screen}\mathcal L_r^\ast
\]
and certify positivity, refinement convergence, rotation covariance,
translation covariance or an equivalent multicenter consistency theorem, and
explicit null-space treatment.  If the limiting covariance commutes with
translations and rotations, Fourier diagonalization gives
\[
\langle \zeta_a(\mathbf k)\zeta_b^\ast(\mathbf k')\rangle
=(2\pi)^3\delta^{(3)}(\mathbf k-\mathbf k')P_{ab}(|\mathbf k|),
\]
with \(P_{ab}(k)\) positive semidefinite.

\textbf{Transfer-ready initial data.}\label{par:transfer-ready-initial-data}
The source-to-transfer map must emit a complete initial state
\[
Y(k,\eta_i)=\mathcal M_{\rm init}(k;\mathfrak B_{\rm src})\xi(k),
\]
including metric, photon, polarization, baryon, neutrino, anomaly, recipient,
and auxiliary response variables.  Near a singular early-time point, regular
Frobenius modes solve
\[
Y'=\left(\frac{M_{-1}}{\eta}+M_0+O(\eta)\right)Y,\qquad
Y=\eta^s(v_0+v_1\eta+\cdots),\quad M_{-1}v_0=sv_0.
\]
The branch must classify regular adiabatic growing modes, allowed isocurvature
modes, decaying modes, gauge modes, and singular interaction modes.  On the
adiabatic branch,
\[
S_{IJ}=3(\zeta_I-\zeta_J)=0
\]
for all active sectors.  The finite evidence receipt must bound the initial
Hamiltonian and momentum constraints and the propagated residual
\[
\epsilon_{\rm constraint}=\sup_{k,\eta}\|\mathcal C(k,\eta)Y(k,\eta)\|.
\]
