\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\makeatletter
\renewcommand*\l@subsection{\@dottedtocline{2}{1.5em}{3.2em}}
\makeatother

\newcommand{\OPH}{\mathrm{OPH}}
\newcommand{\LCDM}{\Lambda\mathrm{CDM}}
\newcommand{\MOND}{\mathrm{MOND}}
\newcommand{\Msun}{M_{\odot}}
\newcommand{\aoph}{a_{0,\mathrm{OPH}}}
\newcommand{\aeff}{a_{0,\mathrm{eff}}}
\newcommand{\lambdac}{\lambda_{\mathrm{collar}}}
\newcommand{\Zsix}{\mathbb Z_6}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\claimlabel}[1]{\textsf{#1}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{target}[theorem]{Target}
\newtheorem{definition}[theorem]{Definition}

\title{Observer-Patch Holography and the Dark Matter Phenomenon}
\author{Bernhard Mueller \and David Matscheko}
\date{\OPHPaperReleaseDate}
\input{../paper/release_info}

\begin{document}
\maketitle
\begin{center}
\small\textbf{Paper release:} \OPHPaperReleaseID\quad
\textbf{Released:} \OPHPaperReleaseDate
\end{center}

\begin{abstract}
In OPH, stable gravity is the bookkeeping of agreement between finite observer
patches. Imperfect agreement leaves a record-repair remainder on overlap
collars. On the declared continuation packet, a localized modular-energy
remainder with rank-two reconstruction, conservation, normalization, and
coupling receipts contributes to the gravitational stress seen by the
effective geometry. Raw scalar collar CMI remains a recovery diagnostic and
is not that stress.

This paper develops that conditional idea as a dark-sector continuation. In
old, settled, low-acceleration galaxies the declared response ansatz gives a
MOND-like galaxy law and the baryonic Tully-Fisher scaling. In clusters and
cosmology the candidate source has to move as transported stress, with its own
relaxation, lensing, growth, and likelihood tests.  The first audited public
comparisons find the fixed conditional \(\mathbb Z_6\) scale essentially on the
aggregate RAR optimum and the slope-four BTFR limit compatible with the
error-aware public fit, while the fixed BTFR normalization remains under
systematic-sensitive pressure.  Universal Solar-System extrapolation of the
same static equation is strongly excluded by Cassini, making a source-derived
applicability theorem an explicit requirement of the settled-galaxy branch.
\end{abstract}

\section*{What This Paper Contributes}

The dark matter evidence is not one observation. Galaxy rotation curves, the baryonic
Tully-Fisher relation, the radial acceleration relation, cluster lensing, CMB peaks, BAO, growth,
and \(S_8\) all ask for a gravitating sector that ordinary luminous matter does not supply. This
paper treats the MOND-like galaxy law as a clue about equilibrium response and the \(\Lambda\)CDM
evidence as a clue about transported stress.

The OPH move is to test whether that stress can have an observer-patch origin.
Imperfect record repair leaves a collar remainder. A remainder enters the
effective stress bookkeeping only after the source-localization, matching,
tensor, conservation, normalization, and coupling receipts declared below; raw
CMI alone does not gravitate. On the continuation branch the source has no
luminous charge, and the settled-galaxy response ansatz is RAR-shaped. In
clusters and cosmology the candidate becomes a transported component with its
own relaxation and likelihood contracts. The paper is a continuation surface;
the source packet and joint fit are decisive gates.

In the forcing chain of \texttt{../docs/CONSISTENCY\_STACK.md}, this continuation
sits at the junction of C1 and C5. C1 (self-reading) requires internal
record-keeping with a repair mechanism; C5 (entropic-gravitational
consistency) recovers the Einstein branch from patchwise horizon
thermodynamics of the record surfaces. Imperfect repair is the residue of the
consistency requirement that keeps records readable across the gravitational
carrier: a repair remainder that carries stress enters the same bookkeeping
that C5 makes gravitational, subject to the receipts declared below. The
dark/anomaly stress candidate of this paper is that residue.

\tableofcontents

\section{Plain Picture}

A galaxy does two jobs in this model.  Its baryons source the ordinary weak
field, and its finite observer-overlap collars carry a record-repair load.  The
load is a recovery diagnostic until the declared source packet turns localized
modular-energy readings into a conserved, coupled tensor. On that conditional
branch it is dark to electromagnetic probes because ordinary luminous charges
are absent, and it enters the effective stress bookkeeping. Scalar CMI by
itself does neither.

The RAR shape has a simple origin.  The relevant repair opportunities live on
cuts, so their broad count scales like \(r_M/r=\sqrt{g_b/\aoph}\).  Independent
local opportunity counts give a Poisson zero-count law.  The active fraction is
\(1-\exp[-\lambdac\sqrt{g_b/\aoph}]\).  The conservative field equation
promotes that scalar response into a potential equation.  The simple algebraic
acceleration law is exact only when symmetry removes the curl term.

\section{Three Claim Layers}

The first layer is the static galaxy law.  It contains the RAR shape, the
BTFR limit, the effective dark density, the no-slip lensing rule, and the
\(\Zsix\)/Poisson coefficient.

The second layer is the dynamic dark component.  It treats the anomaly as a
transported stress that relaxes toward the static equilibrium over
\(\tau_{\mathrm{rec}}\).  Cluster offsets use this layer.

The third layer is cosmological dark matter.  It uses the same stress in
linear perturbation theory, with a background abundance, a relaxation rate,
and an equilibrium kernel.  CMB, BAO, lensing, growth, and \(S_8\) test this
layer.

\section{Finite Covariant Parent Contract}

The cosmology layer needs more than scalar rows.  The object consumed by a
Boltzmann solver must be a finite covariant parent from which stress, exchange,
response, and perturbation variables are calculated.  At regulator \(r\), write
\[
\mathfrak P_r=
(\mathcal X_r,g_r,e_r,\Pi_r,Z_r,f_r,\mathsf T_r,\mathsf C_r,\mathsf M_r,\mathsf R_r).
\]
Here \(\mathcal X_r\) is a finite spacetime or cell complex, \(g_r\) the
regulated metric, \(e_r\) tetrads, \(\Pi_r\) parallel transport between adjacent
cells, \(Z_r=Z_{A,r}\sqcup Z_{R,r}\) anomaly and recipient packet states,
\(f_{I,z}\ge0\) packet occupation, \(\mathsf T_r\) finite covariant transport,
\(\mathsf C_r\) reaction or repair, \(\mathsf M_r\) the moment map to currents
and stress, and \(\mathsf R_r\) the reconstruction/refinement comparison map. A
packet \(z=(I,x,p,\lambda)\) must satisfy
\[
g_{\mu\nu}(x)p^\mu p^\nu=-m_I^2,\qquad p^0>0,
\]
with declared finite invariant phase-space weights \(w_z\). For anomaly packets
the Standard Model currents vanish:
\[
  q_z^{\mathrm{EM}}=q_z^{\mathrm{color}}=q_z^{\mathrm{weak}}=0,
\]
or a separate neutral-commutant theorem must prove that the anomaly algebra
induces no Standard Model current.

The finite moments are
\[
J_{I,r}^{\mu}(x)=
\frac{1}{V_x}\sum_{z:x_z=x} w_z f_{I,z}p_z^\mu,
\qquad
T_{I,r}^{\mu\nu}(x)=
\frac{1}{V_x}\sum_{z:x_z=x}w_z f_{I,z}p_z^\mu p_z^\nu .
\]
If the anomaly stress cannot be represented by positive on-shell packets, the
parent must declare an internal packet stress \(\Sigma_z^{\mu\nu}\) and replace
\(p^\mu p^\nu\) by \(p^\mu p^\nu+\Sigma_z^{\mu\nu}\).  Thus the paper allows
three parent branches: positive kinetic parent, kinetic parent with internal
stress, or covariant action parent.  It does not assume every desired effective
stress is pressureless positive dust.

On the positive kinetic branch, \(w_zf_{I,z}\ge0\) and future causal momenta
imply \(T_{ab}t^at^b\ge0\) for every future timelike \(t^a\). This is the
packet-parent source of weak-energy positivity; it must not be manufactured by
taking absolute values of scalar source rows.

\paragraph{Finite total-stress closure.}
Assume finite covariant summation by parts, equal-and-opposite face fluxes after
parallel transport, reaction-channel four-momentum conservation
\[
\sum_{I,z}\nu_{\alpha,I,z}p_z^\mu=0,
\]
and moment-map compatibility with the discrete connection.  Multiplying the
finite kinetic equation by \(w_zp_z^\nu\) and summing gives
\[
\operatorname{Div}_rT_{I,r}^{\mu\nu}=Q_{I,r}^{\nu},
\qquad
Q_{I,r}^{\nu}(x)=
\frac{1}{V_x}\sum_{z:x_z=x} w_zp_z^\nu \mathsf C_{I,r,z}[f].
\]
Summing over sectors cancels all reaction channels, so
\[
\operatorname{Div}_r\sum_I T_{I,r}^{\mu\nu}=0.
\]
Continuum promotion additionally requires
\[
\left\|
\mathsf R_r(\operatorname{Div}_rT_r)
-
\nabla_\mu\mathsf R_r(T_r)^{\mu\nu}
\right\|_{\mathcal W}
\le\epsilon_{\mathrm{div}}(r),
\qquad
\epsilon_{\mathrm{div}}(r)\to0.
\]

\paragraph{FLRW reduction and exchange.}
If the homogeneous packet distribution is invariant under a spatial group with
no invariant vector and no invariant traceless symmetric rank-two tensor, then
\[
\bar q_A^\mu=0,\qquad \bar\pi_A^{\mu\nu}=0,\qquad
\bar T_A{}^\mu{}_\nu=\operatorname{diag}(-\bar\rho_A,\bar p_A,\bar p_A,\bar p_A).
\]
Reserve \(Q_A^\mu\) for exchange four-current:
\[
Q_A^\mu=Q_Au^\mu+F_A^\mu,\qquad u_\mu F_A^\mu=0,\qquad \sum_IQ_I^\mu=0.
\]
The conserved homogeneous anomaly load should be denoted separately, for
example \(\mathcal N_A=a^3\bar\rho_A V_{\mathrm{com}}\).

\paragraph{Retarded response.}
Linearizing the parent around the FLRW background gives
\[
\delta x'=A(k,\eta)\delta x+B(k,\eta)\delta n_b^{(A)},\qquad
\delta y_A=C(k,\eta)\delta x+D(k,\eta)\delta n_b^{(A)} ,
\]
where \(n_b^{(A)}=-u_{A\mu}J_b^\mu\).  With
\(\partial_\eta U(\eta,\eta')=A(\eta)U(\eta,\eta')\),
\[
K_A(\eta,\eta')=C(\eta)U(\eta,\eta')B(\eta')+
D(\eta)\delta(\eta-\eta')
\]
is the actual retarded response kernel.  A scalar \(B_A(k,a)\) and a scalar
\(\Gamma_{\mathrm{rec}}(k,a)\) are controlled reductions of this realization,
not primitive inputs.  If there exists \(H>0\) and \(\gamma>0\) with
\[
HA+A^\dagger H\preceq -2\gamma H,
\]
then \(\|U(\eta,\eta')\|_H\le e^{-\gamma(\eta-\eta')}\).  A one-pole
relaxation rate is valid only when
\(\|K_A-K_A^{(1)}\|_{\mathcal W}\le\epsilon_{\mathrm{one\ pole}}\) in a
predeclared norm.

\paragraph{Abundance selector boundary.}
The conservation equation
\[
\bar\rho_A'+3\mathcal H\bar\rho_A=0
\]
implies \(\bar\rho_A=C_Aa^{-3}\), but it does not determine \(C_A\).  The
source-only OPH abundance requires the finite selector
\[
\mathcal E_{A,r}=
F_{A,r}(\text{quotient ensemble},P_\star,N_{\mathrm{CRC}},
\text{release state},\mathfrak P_r),
\qquad
\bar\rho_{A,r}(a)=\frac{\mathcal E_{A,r}}{a^3V_{\mathrm{com}}},
\]
with refinement compatibility.  Section~\ref{sec:source-only-anomaly-abundance-selector}
defines this selector.  Promotion to a source-only abundance requires
\texttt{ANOMALY\_ABUNDANCE\_SOURCE\_RECEIPT}; without that receipt, cosmological
abundance is a conditional source state rather than a source-only OPH prediction.

\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
Receipt & Claim label \\
\midrule
\texttt{PACKET\_MASS\_SHELL\_RECEIPT} & finite-parent evidence gate \\
\texttt{TOTAL\_STRESS\_CLOSURE\_RECEIPT} & finite-parent evidence gate \\
\texttt{RETARDED\_RESPONSE\_RECEIPT} & response-realization gate \\
\texttt{B\_A\_KERNEL\_RECEIPT} & conditional on response and mode calibration \\
\texttt{ANOMALY\_ABUNDANCE\_SOURCE\_RECEIPT} & source-side finite selector gate \\
\bottomrule
\end{tabular}
\end{center}

\input{../paper/tex_fragments/FINITE_COVARIANT_PARENT_THEOREMS.tex}

\section{Source Ontology, Units, and Matching}

This paper uses metric signature \((-+++)\). Entropies are in nats unless a
receipt explicitly declares bits and multiplies by \(\ln2\). The radius
\(\ell\) in the local source formula is the proper geodesic radius of a small
four-dimensional causal diamond or ball read in the local tetrad, with scale
hierarchy
\[
  \ell_{\mathrm{UV}}\ll \delta_{\mathrm{collar}}\ll \ell
  \ll L_{\mathrm{curvature}},L_{\mathrm{gradient}} .
\]
Natural units may set \(\hbar=c=1\). In SI units a dimensionless entropy
source \(R\) has energy-density normalization
\[
  \rho_Ac^2=\frac{15\hbar c}{8\pi^2\ell^4}R .
\]

\subsection{Three Source Objects}

The dark continuation distinguishes
\[
  R_C^{\mathrm{info}}:=I_\rho(A:D|B),\qquad
  \mathcal M_C^{\mathrm{anom}},\qquad
  T_A^{ab}.
\]
The first is raw finite conditional mutual information. The second is a
source variable proved, or explicitly hypothesized on the continuation branch,
to equal the anomalous local modular energy entering the BW ball calculation.
The third is a tensor stress reconstructed from all-frame source readings and
a finite packet parent. The paper does not identify these three objects by
notation alone.

\paragraph{Exact finite modular-nonadditivity identity.}
For a faithful finite-dimensional state \(\rho_{ABD}\), define support
modular Hamiltonians \(K_X=-\log\rho_X\), embedded in the full algebra, and
\[
  \Delta K_\rho=K_{AB}+K_{BD}-K_B-K_{ABD}.
\]
Then
\[
  \operatorname{Tr}\rho_{ABD}\Delta K_\rho
  =S(AB)+S(BD)-S(B)-S(ABD)
  =I_\rho(A:D|B).
\]
This is an expectation identity. It does not make \(\Delta K_\rho\) a positive
operator, a state-independent geometric generator, or a local collar stress.

\paragraph{First-variation obstruction.}
If \(\sigma\) is full rank with \(I_\sigma(A:D|B)=0\) and
\(\rho(t)=\sigma+tX+O(t^2)\), then
\[
  \left.\frac{\dd}{\dd t}I_{\rho(t)}(A:D|B)\right|_{t=0}=0
\]
because the nonnegative CMI functional has a local minimum on the exact Markov
set. A fixed-reference modular-energy variation
\(\delta\langle K_\sigma\rangle=t\,\operatorname{Tr}(XK_\sigma)+O(t^2)\) is
generically linear. Therefore raw CMI is not generically the same object as
the anomalous local modular energy on a perturbative Markov branch.

\subsection{Declared Source Route}

A source artifact must declare exactly one route:
\[
\texttt{source\_route}\in
\{\texttt{FIXED\_REFERENCE\_MODULAR\_ENERGY},
\texttt{NONLINEAR\_CMI\_STRESS}\}.
\]
There is no automatic mixed mode. On the fixed-reference route the source is
\[
  R_C^{\mathrm{src}}=\mathcal M_C^{\mathrm{anom}}
  =\delta\langle K_C^{(\mathrm{anom})}[\sigma]\rangle,
\]
and CMI is a recovery/localization diagnostic. On the nonlinear-CMI route the
source is \(R_C^{\mathrm{src}}=R_C^{\mathrm{info}}\) only after a named
CMI-to-modular-source matching theorem or explicit continuation hypothesis
with residual ledger.

\begin{target}[CMI-to-modular-source matching]
The nonlinear-CMI route must prove or declare a versioned hypothesis that, for
each small ball \(B_\ell(x,u)\),
\[
  R^{\mathrm{info}}_{x,u,\ell}
  =
  \frac{2\pi}{\hbar c}
  \int_{B_\ell}
  \frac{\ell^2-r^2}{2\ell}\,
  T^A_{ab}u^au^b\,\dd V
  +\varepsilon_{\mathrm{match}},
\]
with refinement-stable matching residual. Strong subadditivity alone does not
prove this statement. With a subtracted background value, positivity requires a
separate packet-parent or branch-restriction certificate.
\end{target}

\begin{theorem}[Conditional local BW source normalization]
Assume the scale hierarchy above, a declared source route, the matching/local
modular representation
\[
  R^{\mathrm{src}}_{x,u,\ell}
  =
  \frac{2\pi}{\hbar c}
  \int_{B_\ell}
  \frac{\ell^2-r^2}{2\ell}\,
  T^A_{ab}u^au^b\,\dd V
  +\varepsilon_{\mathrm{match}},
\]
and smooth \(\varepsilon_A(x,u)=T^A_{ab}(x)u^au^b\) on the ball. Then
\[
R^{\mathrm{src}}_{x,u,\ell}
=
\frac{8\pi^2\ell^4}{15\hbar c}
\left[
\varepsilon_A(x,u)
+\frac{\ell^2}{14}D_\perp^2\varepsilon_A(x,u)
+O\!\left(\frac{\ell^4}{L_{\mathrm{gradient}}^4}
+\frac{\ell^2}{L_{\mathrm{curvature}}^2}\right)
\right]
+\varepsilon_{\mathrm{match}}.
\]
Hence, on the controlled local branch,
\[
  \varepsilon_A(x,u)
  =
  \frac{15\hbar c}{8\pi^2}
  \lim\frac{R^{\mathrm{src}}_{x,u,\ell}}{\ell^4}
\]
with the stated finite-ball, curvature, and matching corrections.
\end{theorem}

\begin{proof}
The BW ball weight is \(w_\ell(r)=(\ell^2-r^2)/(2\ell)\). In flat
Riemann-normal coordinates
\[
  \int_{B_\ell}w_\ell(r)\,\dd^3x
  =4\pi\int_0^\ell r^2\frac{\ell^2-r^2}{2\ell}\,\dd r
  =\frac{4\pi\ell^4}{15}.
\]
Multiplying by \(2\pi/(\hbar c)\) gives \(8\pi^2\ell^4/(15\hbar c)\). The
next term follows from angular averaging
\(\varepsilon_A(y)=\varepsilon_A(x)+r^2D_\perp^2\varepsilon_A(x)/6+\cdots\)
and
\(\int_{B_\ell}w_\ell(r)r^2\dd^3x=4\pi\ell^6/35\), whose ratio to the
constant term gives \(\ell^2/14\). Curvature corrections are the usual
Riemann-normal-coordinate corrections to the volume form and kernel.
\end{proof}

\subsection{Localization, Covers, and Tomography}

Let \(E_{B,\mathrm{phys}}\) be the conditional expectation onto the
quotient-visible physical collar algebra. A finite source receipt must bound
\[
  \left|
  R_C^{\mathrm{src}}-
  \langle E_{B,\mathrm{phys}}(\Delta K)\rangle
  \right|
  \le \varepsilon_{\mathrm{loc}}
\]
with hidden-carrier, port-relabeling, repair-schedule, and refinement
invariance. Cover independence is a separate requirement: admissible collar
covers must converge to the same weak source measure, or a
Möbius/inclusion-exclusion valuation must prove that overlapping collars do
not double count the same information defect.

A scalar reading for one observer gives only \(T_A^{ab}u_au_b\). To reconstruct
a symmetric tensor, the source must be read on enough timelike directions.
For \(e_x(u)=\lim(15\hbar c/8\pi^2)R^{\mathrm{src}}_{x,u,\ell}/\ell^4\), define
the homogeneous extension
\[
  Q_x(v)=[-g(v,v)]e_x\!\left(v/\sqrt{-g(v,v)}\right).
\]
If \(Q_x\) extends quadratically and satisfies the parallelogram identity,
there is a unique symmetric \(T^A_{ab}\) recovered by polarization. The finite
simulator version needs at least ten linearly independent timelike probes and
held-out quadraticity tests; a single \(u^\mu=(1,0,0,0)\) row is not a stress
theorem.

\section{The Dark Matter Challenge}

In Newtonian gravity and in the weak-field limit of general relativity, a
test particle in a circular orbit satisfies
\begin{equation}
  \frac{v^2(r)}{r}=g(r)=\frac{G M(<r)}{r^2}.
\end{equation}
If almost all gravitating matter is visible baryonic matter, then outside the
bright disk the enclosed mass should stop growing quickly and the rotation
speed should fall as \(v(r)\propto r^{-1/2}\).  Disk galaxies do not behave
that way.  Their outer rotation curves often remain flat, so the inferred
dynamical mass grows approximately linearly with radius:
\begin{equation}
  M_{\mathrm{dyn}}(<r)=\frac{v^2 r}{G}.
\end{equation}

The galaxy problem is only one part of the evidence.  Clusters need more
gravity than the observed gas and galaxies provide.  Weak lensing maps in
merging systems such as the Bullet Cluster show gravitational potential peaks
separated from the X-ray gas \cite{clowe2006}.  The CMB and large-scale
structure prefer a gravitating component that is mostly non-baryonic, close to
pressureless, and present before galaxies settle \cite{planck2018}.  Planck's
base \(\LCDM\) parameter set gives
\(\Omega_c h^2=0.120\pm0.001\) and
\(\Omega_b h^2=0.0224\pm0.0001\), so most matter is not baryonic in that
model \cite{planck2018}.

The challenge includes more than ``flat rotation curves''.  A good theory has
to explain:
\begin{itemize}
\item galaxy rotation curves and the baryonic Tully-Fisher relation;
\item the tight radial acceleration relation, abbreviated RAR;
\item galaxy and cluster lensing;
\item cluster offsets in mergers;
\item CMB acoustic peaks, BAO, matter power, weak lensing, and \(S_8\).
\end{itemize}

\section{Standard Routes}

\subsection{Cold Dark Matter}

The standard route adds a new non-baryonic matter component.  In its simplest
form it is cold, effectively collisionless, and pressureless on cosmological
scales.  \(\LCDM\) uses the same component for CMB peaks, large-scale
structure, clusters, lensing, and galaxy halos.

The particle identity is absent.  Direct detection has produced no confirmed
dark matter particle.  Galaxy data show a tight
connection between baryonic acceleration and observed acceleration, much
tighter than a naive halo-plus-disk picture suggests.  Halo fitting also
introduces galaxy-level nuisance freedom, while the RAR looks like a law.

\subsection{MOND}

MOND should be treated as a clue, not as a failure.  Its basic phenomenology
starts from a critical acceleration \(a_0\), and in the deep low-acceleration
regime it gives
\begin{equation}
  g \simeq \sqrt{a_0 g_b}.
\end{equation}
For a point baryonic mass this implies
\begin{equation}
  v^4 = G M_b a_0,
\end{equation}
which is exactly the baryonic Tully-Fisher scaling \cite{milgrom1983}.  This
is MOND's great success: it goes straight at the galaxy regularity.

The pressure points start when the same static acceleration rule is asked to
do more jobs than a galaxy equilibrium law can naturally do:
\begin{itemize}
\item \emph{Relativistic completion and lensing.}  A nonrelativistic force law
does not by itself say which metric photons follow, or how the modified field
contributes to the stress side of Einstein's equations.  Relativistic
completions such as TeVeS exist \cite{bekenstein2004}, but the lensing sector
then depends on extra fields and closure assumptions.
\item \emph{Clusters.}  MOND reduces the cluster mass discrepancy but does not
remove the need for additional gravitating stress in clusters.  Merging systems
are especially sharp: if the anomaly is an instantaneous function of the local
baryonic acceleration, the lensing peak wants to remain too tightly tied to the
visible baryonic source.
\item \emph{The early universe.}  The CMB acoustic peaks, BAO, matter growth,
CMB lensing, and weak-lensing amplitudes need a homogeneous and perturbative
gravitating component before settled galaxies exist.  A static RAR law does
not by itself define that background abundance or its linear response.
\item \emph{Non-spherical and time-dependent systems.}  The algebraic
relation \(g\simeq\sqrt{a_0g_b}\) is clean in high-symmetry systems.  In real
three-dimensional fields, curl terms, environmental dependence, transport, and
relaxation can matter.
\end{itemize}

OPH does not treat the static RAR formula as the master law.  It approximates
MOND in the regime where the OPH stress sector has relaxed onto the old,
settled, low-acceleration galaxy branch.  It need not approximate MOND in
mergers, clusters, or the early universe, because those systems are not static
one-dimensional galaxy equilibria.  The underlying object is an effective
stress sector carried by finite overlap repair.  In old relaxed disks it
projects to a baryon-linked acceleration law.  In lensing it enters the
metric-potential bookkeeping.  In cluster mergers it is transported and
relaxes over a finite repair time.  In FLRW and perturbation theory it has to
be specified as a homogeneous charge, load current, and response kernel.

This is the sense in which the MOND pressure points dissolve in OPH.  OPH
treats those failures as wrong-regime extrapolations, without making the same
algebraic law more complicated.  The static galaxy formula is allowed to be a
very good equilibrium approximation, while lensing, clusters, and cosmology are
handled by the corresponding OPH stress, transport, and perturbation equations.
Those equations must pass their own falsifiers.  The claim is structural
separation, with no immunity from data.

\section{The OPH Route}

Observer-Patch Holography starts from finite observer patches and the demand
that neighboring patches agree on overlap data.  The relevant OPH inputs for
the dark branch are:

\begin{itemize}
\item finite overlap collars and fixed-cutoff collar algebras;
\item edge and cut registers on those collars;
\item read, compare, repair, commit, and refresh operations;
\item a finite carried modular remainder on the collar;
\item the recovered Einstein branch with a screen-capacity de Sitter scale.
\end{itemize}

The dark-sector proposal is:
\begin{quote}
The dark source is a transported modular/collar information-defect remainder.  It
gravitates because it contributes to the effective stress bookkeeping.  It is
electromagnetically dark because it is a record-repair remainder, not an
ordinary luminous matter species.
\end{quote}
No new particle species is postulated.  The effective dark stress is the
gravitating part of finite-observer information repair.
\begin{equation}
  G_{ab}+\Lambda g_{ab}
  =
  8\pi G
  \left(
    T_{ab}^{\mathrm{SM}}
    +T_{ab}^{\mathcal I}
    +T_{ab}^{\mathrm{repair}}
  \right).
  \label{eq:informationstresssurface}
\end{equation}
The symbol \(A\) in formulas below denotes this anomaly or information-defect
component.  It is an effective stress sector, with no literal particle species
claim.

This differs from particle dark matter and MOND in a useful way.  It is
stress-first like dark matter, so lensing and cosmology have a natural slot.
It is baryon-linked like MOND only on the settled galaxy branch, because that
equilibrium response is activated by collar/cut repair opportunities sourced by
baryonic acceleration.  The important contrast with MOND is not the
square-root galaxy law; OPH intentionally reproduces that approximation where
the equilibrium assumptions apply.  The contrast is where the law lives.  In
MOND, the galaxy formula is often treated as the modification itself.  In OPH
it is the equilibrium projection of a transported stress component.  That is
why lensing, clusters, and cosmology can have their own equations without
giving up the galaxy regularity.

\section{Static Galaxy Derivation}

\subsection{Source From The Carried Collar Remainder}

On the support-visible BW branch the primary theorem is the cap automorphism identity. In the
special type-I or effective local representation where the geometric generator may be written
inside the cap algebra, the OPH modular decomposition has the local form
\begin{equation}
  K_C = 2\pi B_C + K_C^{(\mathrm{anom})}+\mathrm{const}.
\end{equation}
At finite regulator stage, the nonadditive modular part is carried on an
overlap collar.  The dark branch may use the raw finite diagnostic
\[
  R_C^{\mathrm{info}}=I_\omega(A:D|B)\ge0,
\]
but the physical density formula uses the routed source variable
\(R_C^{\mathrm{src}}\).  On the fixed-reference route this is the anomalous
modular-energy variation.  On the nonlinear-CMI route it is raw CMI only after
the explicit CMI-to-modular-source matching theorem or hypothesis and its
localization, cover, and tomography receipts pass. With those receipts, the
effective rest-energy density is written
\begin{equation}
  \rho_A c^2
    = \frac{15\hbar c}{8\pi^2\ell^4} R_C^{\mathrm{src}},
  \qquad
  \rho_A
    = \frac{15\hbar}{8\pi^2 c\,\ell^4} R_C^{\mathrm{src}}.
  \label{eq:rhoA}
\end{equation}
Here \(\ell\) is the proper geodesic radius of the local four-dimensional
small ball.  It is not a cap angle, a screen spacing, a collar thickness, a
coordinate radius, or a fitted galaxy scale.  If the simulator records CMI in
bits, the value must be multiplied by \(\ln2\) before using
\eqref{eq:rhoA}.
The weak-field Poisson equation becomes
\begin{equation}
  \nabla^2 \Phi = 4\pi G(\rho_b+\rho_A).
  \label{eq:poisson}
\end{equation}

\paragraph{Conditional theorem 1, attractive sign.}
If the routed source \(R_C^{\mathrm{src}}\) is nonnegative on the declared
branch, then the anomaly is attractive in the Newtonian weak-field equation.
For the nonlinear-CMI route this nonnegativity is inherited from raw CMI only
when no background subtraction has been introduced; otherwise it must be
certified by the packet parent or branch restriction.

\paragraph{Proof.}
The premise and \eqref{eq:rhoA} give \(\rho_A\ge0\).  Equation
\eqref{eq:poisson} then shows that the anomaly enters with the same attractive
sign as baryonic mass.
\(\square\)

\paragraph{Finite-source receipt boundary.}
The exact CMI modular identity, first-variation obstruction, declared route,
matching theorem or hypothesis, collar localization, BW normalization,
\(\ell^4\) plateau, cover independence, and timelike tomography receipts are
the source-side content of Issue~\#319. Without them, \(R_C^{\mathrm{info}}\)
is a recoverability/readback diagnostic and not a physical density source.
After them, a finite positive packet parent must supply \(T_A^{ab}\),
its Standard-Model-neutral charge condition, and the conserved anomaly plus
recipient stress closure.

\subsection{The Acceleration Variable}

Define the baryonic acceleration ratio
\begin{equation}
  x := \frac{g_b}{\aoph}.
\end{equation}
For a point baryonic source,
\begin{equation}
  g_b(r)=\frac{G M_b}{r^2},
  \qquad
  r_M := \sqrt{\frac{G M_b}{\aoph}},
\end{equation}
so
\begin{equation}
  x=\left(\frac{r_M}{r}\right)^2,
  \qquad
  \sqrt{x}=\frac{r_M}{r}.
  \label{eq:sqrtx}
\end{equation}

The OPH support assumption is that settled-galaxy repair opportunities live
on codimension-one collar/cut support.  A screen-area count would scale as
\(x\).  A cut-count scales as \(\sqrt{x}\), as in \eqref{eq:sqrtx}.

\subsection{Poisson Activation}

Let the mean number of independent local repair opportunities be
\begin{equation}
  \mu(x)=\lambdac\sqrt{x}.
\end{equation}
The Poisson law does not follow from fixing this mean alone.
Fixed mean alone would select a geometric distribution on nonnegative
integers.  The OPH claim needs the stronger collar-count premise: independent
increments on disjoint collar intervals, rare local repair events, and
refinement stability.  Partition an interval \(I\) with mean \(\mu(I)\) into
\(m\) equal subintervals.  If each subinterval has one activation opportunity
with probability \(\mu(I)/m+O(m^{-2})\), and the probability of two or more
events in one subinterval is \(O(m^{-2})\), then for every fixed \(n\),
\begin{equation}
  \Pr[N(I)=n]
  =
  \lim_{m\to\infty}
  {m\choose n}
  \left(\frac{\mu(I)}{m}\right)^n
  \left(1-\frac{\mu(I)}{m}\right)^{m-n}
  =
  e^{-\mu(I)}\frac{\mu(I)^n}{n!}.
  \label{eq:poissonlaw}
\end{equation}
In particular, the zero-count probability is
\begin{equation}
  \Pr[N(I)=0]
  =
  \lim_{m\to\infty}
  \left(1-\frac{\mu(I)}{m}\right)^m
  =
  e^{-\mu(I)}.
\end{equation}
The probability that at least one repair opportunity is active is
\begin{equation}
  p(x)=1-\Pr[N=0]
      =1-\exp[-\lambdac\sqrt{x}].
  \label{eq:activation}
\end{equation}

The activation count is only the counting part of the static law.  The source
closure says that active scalar repair opportunities recover baryonic flux in
the settled one-dimensional branch:
\begin{equation}
  g_b = p(x) g_{\mathrm{obs}}.
  \label{eq:fluxrecovery}
\end{equation}
Thus
\begin{equation}
  g_{\mathrm{obs}}
    = \nu_{\OPH}(x) g_b,
  \qquad
  \nu_{\OPH}(x)
    = \frac{1}{1-\exp[-\lambdac\sqrt{x}]}.
  \label{eq:ophrar}
\end{equation}
At \(\lambdac=1\) this is the McGaugh--Lelli--Schombert empirical
interpolating function fitted to SPARC \cite{mcgaugh2016}; SPARC comparisons
of \eqref{eq:ophrar} are therefore non-held-out.  The universal extrapolation
of this static law to a Solar source in the Galactic external field is
excluded by Cassini at \(19.22\sigma\) (\(18.01\sigma\) on the unit branch;
see the Cassini Applicability Stress subsection).  The surviving claim is the
declared old-settled-galaxy scope, pending a source-derived applicability
theorem.

\paragraph{Conditional theorem 2, activation law.}
Assume codimension-one collar/cut support, independent increments on disjoint
collar intervals, rare local repair events, refinement stability, and the
settled scalar flux-recovery closure \eqref{eq:fluxrecovery}.  Then the
settled one-dimensional galaxy response is \eqref{eq:ophrar}.

\paragraph{Proof.}
Codimension-one support gives a mean count proportional to \(\sqrt{x}\).
The scalar coefficient is \(\lambdac\).  Independent increments and rare-event
refinement give the Poisson law \eqref{eq:poissonlaw}.  The active probability is
the complement of the zero-count event, which is \eqref{eq:activation}.
Solving \(g_b=p(x)g_{\mathrm{obs}}\) in one-dimensional symmetry gives
\eqref{eq:ophrar}. \(\square\)

\subsection{Conservative Potential Equation}

For general disks and three-dimensional baryonic profiles, the algebraic vector
rule
\begin{equation}
  \mathbf g_{\mathrm{alg}}
  =
  \nu_{\OPH}(|\mathbf g_b|/\aoph)\mathbf g_b
\end{equation}
need not be curl-free because
\begin{equation}
  \nabla\times\mathbf g_{\mathrm{alg}}
  =
  \nabla\nu_{\OPH}\times\mathbf g_b.
\end{equation}
A gravitational acceleration must be derived from a potential.  The primary
static OPH equation is therefore
\begin{equation}
  \nabla^2\Phi
  =
  \nabla\cdot
  \left[
    \nu_{\OPH}\!\left(\frac{|\nabla\Phi_b|}{\aoph}\right)
    \nabla\Phi_b
  \right],
  \qquad
  \mathbf g_{\mathrm{obs}}=-\nabla\Phi,
  \label{eq:ophpotential}
\end{equation}
with
\begin{equation}
  \nabla^2\Phi_b=4\pi G\rho_b.
\end{equation}
In one-dimensional symmetry, \eqref{eq:ophpotential} integrates to
\begin{equation}
  g_{\mathrm{obs}}
  =
  \nu_{\OPH}(g_b/\aoph)g_b+C.
\end{equation}
The boundary condition \(g_{\mathrm{obs}}\to0\) when the enclosed baryonic
flux vanishes sets \(C=0\), so \eqref{eq:ophrar} is exact for spherical,
planar, or one-dimensional symmetry.  The SPARC tables in this note use the
algebraic diagnostic; a full disk-potential solver is required for
publication-grade rotation and lensing claims.  Equation
\eqref{eq:ophpotential} holds only on the declared old-settled-galaxy branch:
its universal extension is excluded by the Cassini quadrupole bound at
\(19.22\sigma\), and no source-derived applicability theorem yet selects the
branch.

\subsection{Newtonian And Deep-IR Limits}

For \(x\gg1\), \(p(x)\to1\), hence
\begin{equation}
  g_{\mathrm{obs}}\to g_b.
\end{equation}
For \(x\ll1\),
\begin{equation}
  p(x)=\lambdac\sqrt{x}+O(x),
\end{equation}
so
\begin{equation}
  g_{\mathrm{obs}}
  \simeq \frac{g_b}{\lambdac\sqrt{g_b/\aoph}}
  = \sqrt{\frac{\aoph}{\lambdac^2}g_b}
  = \sqrt{\aeff g_b},
\end{equation}
where
\begin{equation}
  \aeff = \frac{\aoph}{\lambdac^2}.
  \label{eq:aeff}
\end{equation}
For a point source,
\begin{equation}
  v^4 = G M_b \aeff.
  \label{eq:btfr}
\end{equation}

\paragraph{Theorem 3, BTFR.}
The OPH activation law implies the baryonic Tully-Fisher scaling in the
deep-IR limit.

\paragraph{Proof.}
For a circular orbit, \(v^2/r=g_{\mathrm{obs}}\).  In the deep-IR limit,
\(g_{\mathrm{obs}}=\sqrt{\aeff G M_b/r^2}\).  Multiplying by \(r\) gives
\(v^2=\sqrt{G M_b\aeff}\), hence \eqref{eq:btfr}. \(\square\)

\subsection{Effective Dark Density}

The anomaly can be represented as an equilibrium effective density:
\begin{equation}
  \mathbf g_A=(\nu_{\OPH}-1)\mathbf g_b,
  \qquad
  \rho_{A,\mathrm{eq}}
   =-\frac{1}{4\pi G}\nabla\cdot[(\nu_{\OPH}-1)\mathbf g_b].
  \label{eq:rhoaeq}
\end{equation}
For a spherical system,
\begin{equation}
  M_{\mathrm{dyn}}(r)=\nu_{\OPH}(x) M_b(r),
  \qquad
  M_A(r)=[\nu_{\OPH}(x)-1]M_b(r).
\end{equation}
In the deep-IR point-source limit, \(M_{\mathrm{dyn}}(r)\propto r\), which is
the effective mass profile behind flat rotation curves.

For a point baryonic source, the exact equilibrium expression is
\begin{equation}
  M_A(r)
  =
  \frac{M_b}{\exp(\lambdac r_M/r)-1},
\end{equation}
and
\begin{equation}
  \rho_A(r)
  =
  \frac{
    M_b\lambdac r_M\exp(\lambdac r_M/r)
  }{
    4\pi r^4[\exp(\lambdac r_M/r)-1]^2
  }.
\end{equation}
For an extended spherical baryonic profile, positivity of the settled
effective density is the monotonicity condition
\begin{equation}
  \frac{\dd}{\dd r}
  \left(
    [\nu_{\OPH}(x(r))-1]M_b(r)
  \right)
  \ge 0.
\end{equation}
Profiles that violate this condition need finite pressure, shear, or transport
terms instead of the settled dust equilibrium alone.

\paragraph{RAR/source matching target.}
The local modular-source normalization and the settled-galaxy RAR activation
law are separate claims. The RAR density
\[
  \rho_A^{\mathrm{RAR}}
  =
  \frac{1}{4\pi G}
  \nabla\cdot\left[(\nu_{\OPH}-1)\nabla U_b\right]
\]
is matched to the collar source only after a branch theorem proves
\[
  \frac{15\hbar c}{8\pi^2\ell^4}\,
  \bar R_\ell[\rho_b]
  =
  c^2\rho_A^{\mathrm{RAR}}[\rho_b]
\]
with no refit. Until that receipt passes, the RAR law is a settled-equilibrium
continuation law, while the BW normalization is the local source theorem.

\section{The Finite-Collar Coefficient}

\subsection{Unit Branch}

The default branch is
\begin{equation}
  \lambdac=1,
  \qquad
  \aeff=\aoph.
\end{equation}
This branch sets the finite-collar opportunity density to one.

\subsection{\(\Zsix\) Reserve Branch}

The OPH gauge structure contains the realized quotient
\begin{equation}
  G_{\mathrm{phys}}
    = \frac{SU(3)\times SU(2)\times U(1)}{\Zsix}.
\end{equation}
The protected shared-edge reserve has mean
\begin{equation}
  \epsilon_{\Zsix}
    = \frac{\bar\ell_{\mathrm{shared}}}{|\Zsix|}
    = \frac{P/4}{6}
    = \frac{P}{24}.
\end{equation}
Using
\begin{equation}
  P=1.630968209403959,
\end{equation}
gives
\begin{equation}
  \epsilon_{\Zsix}=0.06795700872516496.
\end{equation}

\paragraph{Trace convention.}
The exponent mean is the normalized quotient expectation:
\[
\tau_q(Z_{6,r,C})=\epsilon_{\Zsix}=\frac{P}{24}.
\]
The reciprocal reserve-depth trace is
\[
\operatorname{Tr}^{\#}_q(Z_{6,r,C})=\frac{24}{P}.
\]
The Poisson factor is
\[
e^{-\tau_q(Z_{6,r,C})}=e^{-P/24},
\]
not \(e^{-\operatorname{Tr}^{\#}_q(Z_{6,r,C})}\).

\paragraph{Conditional bridge 4, quotient-edge co-registration.}
Galaxy scalar repair opportunities are quotient-edge cut-register events on
the same edge-center resolution that carries the protected \(\Zsix\) reserve.
The \(\Zsix\) reserve therefore co-registers with the scalar activation count.

\paragraph{Conditional argument.}
The scalar source is a quotient-local recoverability defect, so pure
\(\Zsix\) center motion changes no realized matter or Higgs state and is
inactive for scalar sourcing.  If the scalar count and the protected reserve
are forced onto the same center-projector resolution, the reserve removes
active scalar opportunities from that same layer. \(\square\)

\paragraph{Imported scalar-slot closure.}
This bridge is discharged, on the quotient-edge scalar branch, by the quotient-edge
collar theorem stack of the screen-microphysics paper~\cite{ophmicro}. That
paper defines
\[
\mathsf{Scal}_{r,C}=\mathcal E_{r,C}
\]
on the edge-center scalar-completeness branch and proves the imported
statements labeled
\[
\texttt{thm:scalar-activation-edge-center},\quad
\texttt{thm:scalar-z6-same-register-commute},\quad
\texttt{thm:scalar-channel-exhaustion},\quad
\texttt{thm:no-separate-scalar-carrier},\quad
\texttt{thm:coherent-matter-same-channel-forcing},\quad
\texttt{thm:unique-scalar-linear-response}.
\]
Thus
\[
\Pi^{\rm scal}_{r,C}\in\mathcal E_{r,C},
\qquad
Z_{6,r,C}\in\mathcal E_{r,C},
\qquad
[\Pi^{\rm scal}_{r,C},Z_{6,r,C}]=0,
\]
and the scalar activation channel has no independent scalar bulk, screen-area,
or noncentral collar carrier unless the scalar-completeness or
scalar-activation-channel completeness branch fails. For a nondegenerate
OPH-coherent material subfederation, the imported source readout is
\[
S_{\mathrm{coh}}^{\mathrm{can}}
=\mathbf 1_{\rm self-read}\,\mathsf R_U\,\mathsf P_U\,\mathsf C_U>0
\]
and coherent-matter same-channel forcing places this source in
\(\mathcal E_{r,C}\). This is a scalar-channel identity theorem. It supplies no
finite covariant dark-stress parent, no abundance prediction, and no
Boltzmann-likelihood closure.
The scalar source route is
\[
R_C^{\mathrm{src}}
\longmapsto
\mathcal N_{\nu,r,C}
\longmapsto
\nu_{\OPH}.
\]
The exact \(\Zsix\) coefficient additionally requires the imported gate
\texttt{UNIFORM\_PRODUCT\_THICKENING\_EXACT}; co-registration alone is not the
same as scalar-reserve unbiasedness.

\paragraph{Finite channel bridge.}
The same-channel statement can be represented by one finite channel object:
one indexed family \(E\) carries both the record panel
\((p_e(q),a_e,q\mapsto q\oplus e)\) used by the scalar opportunity count and
the collar panel \((w_e,\epsilon_e)\) used by the reserve survival factor.
Then the record slots and collar slices are definitionally the same finite
family, and the composite law reads
\[
\lambda_{\mathrm{collar}}\,
(\mathcal L^{\mathrm{coh}}\mathcal N_{\nu})(q)
=
e^{-P/24}\,S_{\mathrm{coh}}^{\mathrm{can}}(q)\,A(q)
\]
on the uniform product-thickening branch. This bridge removes the bookkeeping
ambiguity in the phrase ``the same counter.'' It does not close the physical
residues: nature must instantiate the one-channel structure, and the numerical
record-\(\Delta S\) to gravity-\(\Delta S\) calibration remains a separate G9
obligation.

\paragraph{Conditional bridge 5, local Poisson reserve survival.}
If the reserve occupancy in a co-registered local scalar slot at transverse
collar coordinate \(y\) is Poisson with mean \(\epsilon_{\Zsix}(y)\), then the
local scalar survival factor is
\begin{equation}
  \lambda_{\mathrm{slot}}(y)
  =
  \Pr[N_{\Zsix}(y)=0]
  =
  \exp[-\epsilon_{\Zsix}(y)].
  \label{eq:z6localsurvival}
\end{equation}

\paragraph{Proof.}
A Poisson variable with mean \(\epsilon_{\Zsix}\) has zero-count probability
\(\exp(-\epsilon_{\Zsix})\).  A scalar opportunity survives only when its
co-registered reserve count is zero.  This proves the local survival factor.
\(\square\)

\subsection{Finite Thickness}

Let \(y\) be the transverse collar coordinate and \(w(y)\) the normalized
activation weight:
\begin{equation}
  \int \dd y\,w(y)=1.
\end{equation}
The finite-thickness branch gives
\begin{equation}
  \lambdac
   =\int \dd y\, w(y)\exp[-\epsilon_{\Zsix}(y)].
  \label{eq:thick}
\end{equation}

\paragraph{Scalar-conditioned reserve mean.}
The unconditioned reserve mean
\[
\tau_q(Z_{6,r,C})=P/24
\]
does not automatically imply
\[
\frac{\tau_q(\Pi^{\rm scal}_{r,C}Z_{6,r,C})}
{\tau_q(\Pi^{\rm scal}_{r,C})}
=
P/24.
\]
The finite-thickness branch uses the scalar-weighted reserve profile
\[
\epsilon_{\Zsix}(y)
=
\frac{\tau(\Pi^{\rm scal}Z_6p_y)}
{\tau(\Pi^{\rm scal}p_y)}.
\]
Thus the mean condition entering Jensen is
\[
\int \dd y\,w(y)\epsilon_{\Zsix}(y)=P/24.
\]
This is a scalar-weighted mean receipt. It follows on the uniform
product-thickening branch, but not from co-registration alone.

If
\begin{equation}
  \int \dd y\,w(y)\epsilon_{\Zsix}(y)=P/24,
\end{equation}
then Jensen's inequality gives
\begin{equation}
  \lambdac \ge \exp(-P/24).
\end{equation}
Equality holds when \(\epsilon_{\Zsix}(y)\) is constant on the weighted
collar.

\paragraph{Conditional bridge 6, exact finite-thickness coefficient.}
The exact finite-thickness coefficient requires the uniform product-thickening
branch of the screen-microphysics paper:
\[
\mathcal A^{\rm thick}_{r,C}
\cong
\mathcal E_{r,C}\otimes\mathcal T_r(Y),
\]
\[
\tau^{\rm thick}_{q,r,C}
=
\tau^{\mathcal E}_{q,r,C}\otimes\tau^Y_r,
\]
\[
Z^{\rm thick}_{6,r,C}=Z_{6,r,C}\otimes1_Y,
\]
and, essentially,
\[
\frac{
\tau^{\mathcal E}_{q,r,C}
\!\left(\Pi^{\rm scal}_{r,C}(y)Z_{6,r,C}\right)
}{
\tau^{\mathcal E}_{q,r,C}
\!\left(\Pi^{\rm scal}_{r,C}(y)\right)
}
=
\frac{P}{24}
\]
for every scalar-active transverse slice \(y\). Product trace alone is not
enough. The scalar-active sampler must be reserve-unbiased.

\paragraph{Conditional argument.}
With local Poisson reserve survival and the uniform product-thickening branch,
the imported theorem labeled
\texttt{thm:exact-uniform-product-thickening-coefficient} gives
\begin{equation}
  \lambdac
  =
  \exp(-P/24)
  =
  0.9343006394893864\ldots .
\end{equation}
Without the uniform branch, the theorem-grade coefficient is
\[
\lambdac
=
\int \dd y\,w(y)e^{-\epsilon_{\Zsix}(y)}.
\]
If the scalar-weighted protected reserve mean is \(P/24\), Jensen gives only
\[
e^{-P/24}\le\lambdac\le1.
\]

On that exact branch,
\begin{equation}
  \lambdac=\exp(-P/24)=0.934300639489386\ldots
  \label{eq:z6lambda}
\end{equation}
and by \eqref{eq:aeff}
\begin{equation}
  \aeff=1.179018696\times10^{-10}\,\mathrm{m\,s^{-2}}.
\end{equation}

\paragraph{Failure consequence.}
Without finite-thickness uniformity, the coefficient is the integral
\eqref{eq:thick}.  Exact \(\exp(-P/24)\) is not available as a theorem-grade
number.

\section{Lensing And Relativistic Stress}

A density source by itself fixes the Newtonian Poisson equation.  Lensing also
depends on the spatial stress.  The OPH no-slip claim uses the transported
record-number stress and its spatial moments.

The conditional OPH stress closure is a kinetic record measure.  At each
coarse-grained event, the finite collar packet emits a positive measure
\(\dd\mathcal E_x(v)\) on the future unit timelike shell.  Define
\begin{equation}
  J_{\mathcal I}^a(x)=\int v^a\,\dd\mathcal E_x(v),
  \qquad
  T_{\mathcal I}^{ab}(x)=\int v^a v^b\,\dd\mathcal E_x(v).
  \label{eq:kineticstress}
\end{equation}
This stress is symmetric and future-positive.  Relative to an observer
\(u^a\), it decomposes as
\begin{equation}
  T_{\mathcal I}^{ab}
  =
  \epsilon_{\mathcal I}u^a u^b
  +P_{\mathcal I}h^{ab}
  +2u^{(a}q_{\mathcal I}^{b)}
  +\pi_{\mathcal I}^{ab}.
  \label{eq:stressdecomposition}
\end{equation}
The settled branch should not be modelled as an exactly static extended
monokinetic dust halo. Separately conserved dust follows geodesics and cannot
generically remain static in a nonconstant gravitational potential. The
settled no-slip branch is instead a cold-isotropic kinetic branch
\[
  f_A(x,\mathbf p)=F(x,|\mathbf p|)
\]
in the local rest frame, or a stationary \(F(E)\) branch when an energy
integral exists. Angular symmetry gives \(q_{\mathcal I}^a=0\) and
\(\pi_{\mathcal I}^{ab}=0\), while a small pressure or velocity dispersion may
support the halo. The cold condition is
\[
  0\le\frac{P_{\mathcal I}}{\epsilon_{\mathcal I}}\le\epsilon_{\mathrm{cold}}\ll1,
\]
with a Jeans or stationary-Vlasov residual such as
\[
  |\nabla_iP_{\mathcal I}+\rho_{\mathcal I}\nabla_iU|
  \le\tau_{\mathrm{Jeans}}
\]
in the Newtonian regime.
In Newtonian gauge,
\begin{equation}
  \dd s^2
  =a^2[-(1+2\Psi)\dd\eta^2+(1-2\Phi)\dd x^2].
\end{equation}
The off-diagonal spatial Einstein equation gives
\begin{equation}
  k^2(\Phi-\Psi)
  =12\pi G a^2\sum_i(\rho_i+P_i)\sigma_i.
\end{equation}
The \(\mathcal I\)-sector intrinsic contribution to the right-hand side
vanishes whenever the transported packet distribution is rotationally
invariant in the local rest frame, so \(q_{\mathcal I}^a=0\) and
\(\pi_{\mathcal I}^{ab}=0\). A velocity-spread or imperfectly isotropic branch
must instead emit
\[
  \epsilon_\pi=\frac{|\pi_A|}{\epsilon_A+P_A}
\]
and an \(O(\epsilon_\pi)\) slip bound.
If baryonic, neutrino, radiation, and repair-recipient anisotropic stresses are
absent or handled separately, if there is one metric source, and if boundary
conditions do not add an unmodelled transverse exchange, then
\begin{equation}
  \Phi=\Psi.
\end{equation}
The lensing potential is therefore the same potential that controls dynamics:
\begin{equation}
  \Phi_{\mathrm{lens}}=\frac{\Phi+\Psi}{2}=\Phi.
\end{equation}
In weak-field physical units, with \(U=c^2\Phi=c^2\Psi\) on this no-intrinsic
slip branch,
\[
  \nabla^2U=4\pi G(\rho_b+\rho_A)
  +\mathcal E_{\mathrm{PN}}+\mathcal E_P+\mathcal E_{\mathrm{match}}
  +\mathcal E_{\mathrm{finite,ball}},
\]
and geometric-optics lensing uses
\[
  \boldsymbol\alpha=\frac2{c^2}\int\nabla_\perp U\,\dd z .
\]
A simulator that fits separate dynamical and lensing potentials has not passed
the common-metric receipt.

This is where OPH behaves differently from a force-only MOND law.  The
correction is attached to stress bookkeeping, so the same potential controls
slow matter and lensing on settled no-slip galaxy states.  Cluster mergers and
cosmological perturbations use the full decomposition
\eqref{eq:stressdecomposition}; a velocity-spread branch can carry pressure,
heat flux, or anisotropic stress.

\section{Clusters And Transport}

The static galaxy law is an equilibrium law.  Merging clusters need a
transported information-defect state.  In the cold transported branch, the
kinetic stress \eqref{eq:kineticstress} reduces to a density and velocity
field:
\begin{align}
  \partial_t\rho_{\mathcal I}
    +\nabla\cdot(\rho_{\mathcal I}\mathbf v_{\mathcal I})
    &=-\frac{\rho_{\mathcal I}
      -\rho_{\mathcal I,\mathrm{eq}}[\rho_b]}{\tau_{\mathrm{rec}}},
    \label{eq:transport1}\\
  \partial_t\mathbf v_{\mathcal I}
    +(\mathbf v_{\mathcal I}\cdot\nabla)\mathbf v_{\mathcal I}
    &=-\nabla\Phi,
    \label{eq:transport2}\\
  \nabla^2\Phi&=4\pi G(\rho_b+\rho_{\mathcal I}).
    \label{eq:transport3}
\end{align}
Velocity-spread branches use the moment equations of
\eqref{eq:stressdecomposition} instead of \eqref{eq:transport1}.

The repair-commit theorem gives the form of the relaxation term.  A transition
matrix has a dimensionless step eigenvalue.  Physical relaxation uses its
logarithmic decay together with the physical commit time.  Let \(r_\star\) be
the largest nonstationary step eigenvalue in modulus,
\(g_{\mathrm{step}}=1-r_\star\), and
\(\gamma_{\log}=-\log |r_\star|\).  With physical commit time
\(t_{\mathrm{commit}}\),
\begin{equation}
  \Gamma_{\mathrm{rec}}
   =\frac{\gamma_{\log}}{t_{\mathrm{commit}}},
  \qquad
  \tau_{\mathrm{rec}}
   =\frac{t_{\mathrm{commit}}}{\gamma_{\log}}.
\end{equation}
The small-gap approximation is
\(\Gamma_{\mathrm{rec}}=g_{\mathrm{step}}/t_{\mathrm{commit}}
 +O(g_{\mathrm{step}}^2)\).  The symbols \(r_\star\),
\(g_{\mathrm{step}}\), \(\gamma_{\log}\), and \(\Gamma_{\mathrm{rec}}\)
denote different artifact types.

Bianchi consistency requires a repair-exchange stress:
\begin{equation}
  \nabla_a(T_b^{ab}+T_{\mathcal I}^{ab}+T_R^{ab}+\cdots)=0.
\end{equation}
In quasi-covariant notation,
\begin{equation}
  \nabla_a T_{\mathcal I}^{ab}
  =
  -\Gamma_{\mathrm{rec}}
  (\rho_{\mathcal I}-\rho_{\mathcal I,\mathrm{eq}})
  u_{\mathcal I}^b,
\end{equation}
and \(T_R^{ab}\) carries the opposite exchange flux.

An OPH-side no-fit clock candidate is the Jacobi mismatch rate.  Let
\(E_{ij}=C_{0i0j}\) be the electric Weyl tidal tensor measured in the local
free-fall frame, equivalently the trace-free Newtonian Hessian in the weak
field.  The homogeneous FLRW Ricci focusing term is subtracted, because it
does not create a local overlap-visible cluster offset.  The scalar rate
\begin{equation}
  \Gamma_J
  =
  \left(\frac{E_{ij}E^{ij}}{6}\right)^{1/4},
  \qquad
  \tau_J=\Gamma_J^{-1}
  \label{eq:jacobiclock}
\end{equation}
is invariant under local rotations and has the right units.  For a Newtonian
point source,
\begin{equation}
  E_{ij}E^{ij}=6\left(\frac{GM}{r^3}\right)^2,
  \qquad
  \tau_J=\sqrt{\frac{r^3}{GM}}.
\end{equation}
The numerical scale is:
\begin{center}
\begin{tabular}{@{}lrrr@{}}
\toprule
Scale & \(M/\Msun\) & \(r\) in kpc & \(\tau_J\) in Gyr \\
\midrule
Inner spiral disk & \(6.0\times10^{10}\) & \(10\) & \(0.0608673\) \\
Outer spiral disk & \(6.0\times10^{10}\) & \(30\) & \(0.316276\) \\
Dwarf scale & \(1.0\times10^9\) & \(5\) & \(0.166692\) \\
Cluster core & \(1.0\times10^{14}\) & \(300\) & \(0.244986\) \\
Massive cluster aperture & \(1.0\times10^{15}\) & \(1000\) & \(0.471476\) \\
\bottomrule
\end{tabular}
\end{center}
For \(d_0=200\,\mathrm{kpc}\) and \(t=0.2\,\mathrm{Gyr}\), the massive-cluster
aperture row gives \(d(t)=130.859\,\mathrm{kpc}\).

The conditional physical-time conversion is
\begin{equation}
  \Gamma_{\mathrm{rec}}(x,t)=\Gamma_J(x,t),
  \qquad
  t_{\mathrm{commit}}(x,t)
  =\frac{\gamma_{\log}(x,t)}{\Gamma_J(x,t)} .
\end{equation}
The static RAR law does not determine this clock.  Any positive relaxation
rate leaves the same equilibrium density.  The Jacobi clock requires the
premise that repair timing is set by the overlap-visible tidal mismatch rate
of transported information-defect records.  The theorem-grade packet clock
must derive this premise without using cluster offsets as selectors.

For a one-mode merger offset,
\begin{equation}
  d(t)=d_0\exp(-t/\tau_{\mathrm{rec}}),
  \qquad
  \tau_{\mathrm{rec}}=\frac{t}{\ln(d_0/d(t))}.
\end{equation}
With \(d_0=200\,\mathrm{kpc}\) and \(t=0.2\,\mathrm{Gyr}\):
\begin{center}
\begin{tabular}{@{}rr@{}}
\toprule
Retained offset & Required \(\tau_{\mathrm{rec}}\) \\
\midrule
\(50\,\mathrm{kpc}\) & \(0.144\,\mathrm{Gyr}\) \\
\(100\,\mathrm{kpc}\) & \(0.288\,\mathrm{Gyr}\) \\
\(134\,\mathrm{kpc}\) & \(0.500\,\mathrm{Gyr}\) \\
\(150\,\mathrm{kpc}\) & \(0.696\,\mathrm{Gyr}\) \\
\(164\,\mathrm{kpc}\) & \(1.000\,\mathrm{Gyr}\) \\
\bottomrule
\end{tabular}
\end{center}
Settled galaxies impose
\begin{equation}
  \tau_{\mathrm{rec}}<\frac{T_{\mathrm{set}}}{\ln(1/\epsilon)}
\end{equation}
if the allowed tracking error after settling time \(T_{\mathrm{set}}\) is
\(\epsilon\).  For \(T_{\mathrm{set}}=5\,\mathrm{Gyr}\), the bounds are
\(2.17\,\mathrm{Gyr}\), \(1.67\,\mathrm{Gyr}\), and \(1.09\,\mathrm{Gyr}\)
for \(10\%\), \(5\%\), and \(1\%\) tracking error.

\section{CMB, BAO, Growth, And \(S_8\)}

The linear cosmology contract has two distinct branches.  A conserved
homogeneous information-defect branch obeys
\begin{equation}
  \rho_A' + 3\mathcal H\rho_A=0,
  \qquad
  \rho_A(a)=\rho_{A0}a^{-3},
  \label{eq:conservedbranch}
\end{equation}
where primes denote conformal time and \(\mathcal H=a'/a\).  This branch
behaves like a cold stress component if its kinetic measure is monokinetic and
its homogeneous charge \(Q_A=a^3\rho_A V_{\mathrm{com}}\) is transported by an
anomaly-current conservation receipt and selected by the source-only anomaly
abundance receipt of Section~\ref{sec:source-only-anomaly-abundance-selector}.
A source-localized CMI value without those receipts does not imply the
\(a^{-3}\) scaling or the homogeneous amplitude.

\paragraph{No-go boundary for scalar parents.}
A scalar parent that emits only
\(\rho_A(a)\), \(\rho_{A,\mathrm{eq}}(a)\), and \(B_A(k,a)\) is a source
candidate, not a physical Boltzmann closure.  It does not determine
\[
  w_A(a),\quad c_{s,A}^2(k,a),\quad \sigma_A(k,a),\quad Q_A^\mu,\quad
  \Gamma_{\mathrm{rec}}(k,a),
\]
and it does not by itself fix gauge-independent perturbations or the recipient
stress needed when repair transfers energy-momentum.  In the physical source
contract \(B_A\) is built from the anomaly-frame baryon density
\[
  n_b^{(A)}=-u_{A\mu}J_b^\mu ,
\]
not from a gauge-fixed coordinate density.  The physical object is a
finite covariant collar-packet parent
\[
  \mathcal P_r[X,g]=(C_r,Z_r,A_r,R_r,G_r,\pi_r[X],L_r[X],Q_r,D_r),
\]
where \(Z_r\) is a finite packet-state set split into anomaly and recipient
channels, \(\pi_r\) is the convex equilibrium packet functional, \(L_r\) is the
repair generator, \(Q_r\) records reaction channels, and \(D_r\) records any
causal auxiliary response.  The parent must emit the stress moments and source
projections consumed by the Boltzmann solver; otherwise CMB/BAO/growth rows
remain diagnostics.

\paragraph{Finite covariant parent object.}
The theorem-grade parent is not a parent-shaped JSON object.  At regulator \(r\)
it is a quotient-visible finite kinetic package
\[
\mathcal P_r[X,g]=
(\mathcal C_r,g_r,e_r,U_r,Z_r,\omega_r,p_r,f_r,\Phi_r,
\mathcal R_r,\mathcal G_r,\pi_r,\mathsf{Read}_r),
\]
with finite causal complex \(\mathcal C_r\), local tetrads \(e_r\), finite
parallel transports \(U_r\), packet sectors
\[
Z_r=\bigsqcup_s Z_{s,r},
\]
positive quadrature weights, occupations \(f_{c,z}\ge0\), and momenta obeying
the declared \((-+++)\) mass shell
\[
g_{ab}p_z^ap_z^b=-m_z^2,\qquad p_z^0>0.
\]
The quotient \(\mathcal G_r\) includes hidden carrier coordinates, equivalent
packet labels, port relabelings, local-frame presentations, and accepted
repair-schedule presentations.  The readout
\[
\mathsf{Read}_r=(\mathsf{StressRead}_r,\mathsf{ExchangeRead}_r,
\mathsf{ScalarSourceMap}_r,\mathsf{ClockRead}_r,\mathsf{RepairTangent}_r)
\]
must factor through that quotient.

\paragraph{Exact finite closure receipt.}
For each sector define
\[
J_{s,c}^a=\frac1{V_c}\sum_{z\in Z_s}W_{c,z}p_z^a,\qquad
T_{s,c}^{ab}=\frac1{V_c}\sum_{z\in Z_s}W_{c,z}p_z^ap_z^b .
\]
The simulator must reconstruct these moments from packet rows and emit
residual ledgers
\[
R_{s,c}^a=(D_rT_s)^a-Q_{s,c}^a,\qquad
R_{{\rm total},c}^a=D_rT_{\rm total}^a,
\]
including internal-face cancellation, boundary flux, geometry/redshift work,
external work, reaction four-momentum, and conserved charges.  Producer
booleans, zero-density labels, invented recipient rows, or scalar residuals
are not stress closure.
Promoting \(\rho_A(a)\), \(B_A(k,a)\), a certified
\(\Gamma_{\mathrm{rec}}(k,a)\), or any associated primordial scalar input also
requires a source-provenance DAG and a pooled-reducer receipt.  A transition
spectral number remains \(\gamma_{\mathrm{repair\ step}}\) until active-fiber,
physical-clock, and common-parent response receipts pass.  Contradictory
no-data-use metadata fails closed, and nonlinear quantities such as amplitudes,
ranks, condition numbers, and isocurvature leakage are computed only after
additive sufficient statistics are pooled globally.

For the source-only primordial bridge, this closed branch has the stricter
contract
\begin{equation}
  \nabla_aJ_A^a=0,\qquad
  T_A^{ab}=\epsilon_Au^au^b,\qquad
  Q_A^a=0 .
  \label{eq:closed-anomaly-primordial-contract}
\end{equation}
It may enter the rank-one primordial theorem only when \(\rho_A\) is a
function of the same source clock as the rest of the total stress.  Transport
of a supplied \(Q_A\) is not an OPH derivation of the homogeneous abundance.

A repair-exchange branch instead relaxes toward a finite-collar equilibrium
source:
\begin{equation}
  \rho_A' + 3\mathcal H\rho_A
  = -a\Gamma_{\mathrm{rec}}(\rho_A-\rho_{A,\mathrm{eq}}).
  \label{eq:repairbackground}
\end{equation}
The factor \(a\Gamma_{\mathrm{rec}}\) is the conformal-time rate associated
with the physical repair rate.  Define
\begin{equation}
  q_A=\frac{\rho_{A,\mathrm{eq}}}{\rho_A},
  \qquad
  \delta_{A,\mathrm{eq}}(k,a)=B_A(k,a)\delta_b(k,a).
\end{equation}
For a pressureless no-slip repair branch with energy exchange parallel to
the anomaly four-velocity, the Newtonian-gauge perturbations reduce to
\begin{align}
  \delta_A'
    &=-\theta_A+3\Phi'
      -a\Gamma_{\mathrm{rec}}q_A
       (\delta_A-\delta_{A,\mathrm{eq}}),
       \label{eq:deltaA}\\
  \theta_A'
    &=-\mathcal H\theta_A+k^2\Psi.
       \label{eq:thetaA}
\end{align}
The no-slip statement here concerns the information-defect sector.  The total
metric slip depends on baryons, radiation, neutrinos, repair stress, and any
anisotropic stress in a velocity-spread branch.

For the same primordial bridge, the repair-exchange branch is admissible only
with an explicit transfer receipt:
\begin{equation}
  \nabla_aT_A^{ab}=Q_A^b,\qquad
  \Xi_a^A=0,\qquad
  h^a{}_bQ_A^b=0
  \label{eq:repair-anomaly-primordial-contract}
\end{equation}
or with interval bounds on the two defects.  The dark-sector continuation in this
paper separates transport of a supplied homogeneous load from source selection
of that load.  Transport alone has label
\[
  \texttt{PHYSICAL\_PARENT\_WITH\_CONDITIONAL\_ABUNDANCE}.
\]
A source-only homogeneous abundance requires
\[
  \texttt{RHO\_A\_SOURCE\_RECEIPT}
  =
  \texttt{RHO\_A\_TRANSPORT\_RECEIPT}
  \wedge
  \texttt{ANOMALY\_ABUNDANCE\_SOURCE\_RECEIPT}.
\]
For primordial certification without that receipt, use
\[
  \texttt{dark\_continuation = OFF}.
\]
A supplied dark abundance may be used only as
\[
  \texttt{dark\_continuation = CONDITIONAL\_SOURCE\_STATE},
\]
not as a derived OPH primordial prediction.

If the exchange branch is nonzero, the recipient sector is not optional.  The
finite parent must expose a recipient stress \(T_R^{ab}\), a reaction channel,
and equal-and-opposite exchange currents such that
\[
  \nabla_a(T_A^{ab}+T_R^{ab}+T_{\mathrm{other}}^{ab})=0 .
\]
Without that explicit stress and current closure, a repair sink/source can
mimic a scalar damping term but cannot be promoted to an Einstein-source
prediction.

The finite scalar-load repair diagnostic gives
\[
  \gamma_{\mathrm{repair\ step}}=0.050717471.
\]
It maps a cluster-scale relaxation window to the following commit times:
\begin{center}
\begin{tabular}{@{}rr@{}}
\toprule
\(\tau_{\mathrm{rec}}\) & \(t_{\mathrm{commit}}\) \\
\midrule
\(0.3\,\mathrm{Gyr}\) & \(15.2152\,\mathrm{Myr}\) \\
\(0.5\,\mathrm{Gyr}\) & \(25.3587\,\mathrm{Myr}\) \\
\(1.0\,\mathrm{Gyr}\) & \(50.7175\,\mathrm{Myr}\) \\
\bottomrule
\end{tabular}
\end{center}
For the same relaxation window, a simple background timing diagnostic gives:
\begin{center}
\begin{tabular}{@{}rrrr@{}}
\toprule
\(\tau_{\mathrm{rec}}\) & \(z=0\) & \(z=10\) & \(z=1100\) \\
\midrule
\(0.3\,\mathrm{Gyr}\) & \(48.4092\) & \(2.36213\) & \(0.00205644\) \\
\(0.5\,\mathrm{Gyr}\) & \(29.0455\) & \(1.41728\) & \(0.00123387\) \\
\(1.0\,\mathrm{Gyr}\) & \(14.5228\) & \(0.708639\) & \(0.000616933\) \\
\bottomrule
\end{tabular}
\end{center}
For a hybrid branch, repair relaxation is tiny during acoustic physics and
large in low-Hubble settled environments.  A cosmology claim requires a
finite covariant source artifact, Boltzmann implementation, frozen likelihood
hashes, and likelihood tests against CMB TT/TE/EE, CMB lensing, BAO, weak
lensing, redshift-space distortions, and \(S_8\).

\section{Abundance And Kernel Targets}

The static galaxy law fixes a settled response around resolved baryonic
inhomogeneity.  A cosmological dark-matter branch needs OPH source outputs:
\begin{equation}
  \rho_A(a),
  \qquad
  B_A(k,a),
  \qquad
  \Gamma_{\mathrm{rec}}(k,a),
  \qquad
  w_A,\ c_{s,A}^2,\ \sigma_A,\ Q_A^\mu .
\end{equation}
The first is the homogeneous anomaly abundance.  The second is the linear
equilibrium-source kernel in
\begin{equation}
  \delta_{A,\mathrm{eq}}(k,a)=B_A(k,a)\delta_b(k,a).
\end{equation}
The remaining entries close the stress tensor and exchange law.

\subsection{Static FLRW Boundary}

The nonlinear galaxy law cannot be inserted directly into FLRW perturbation
theory.  In an exactly homogeneous background there is no preferred baryonic
acceleration vector.  If one tries to Taylor-expand the static RAR law at
\(\mathbf g_b=0\), the susceptibility is singular because
\(\nu_{\OPH}(x)\sim(\lambdac\sqrt{x})^{-1}\).  The static RAR branch therefore
does not select a homogeneous anomaly density or a universal CMB kernel.

This is a useful boundary.  It prevents a hidden fit from being smuggled into
the galaxy law.  The CMB branch has to declare its background anomaly charge
and its perturbation kernel from OPH state selection or finite-collar
microphysics.

\subsection{Capacity-Saturated State Selection}

One clean homogeneous benchmark is flat capacity saturation.  More generally, the de Sitter screen
capacity fixes \(H_{\mathrm{dS}}\); the capacity itself is the SL-4 estimate
read from measured \(\Lambda\) with the scale bridge
(\texttt{../docs/STRANGE\_LOOP\_PRINCIPLES.md}), so \(H_{\mathrm{dS}}\) is an input-carrying quantity
rather than an OPH output.  The object that would promote this capacity lane
is generator G2 of \texttt{../docs/CONSISTENCY\_STACK.md}: constructing the
readback map \(F\) and its contraction certificate.  The Friedmann closure at \(a=1\) gives only the degenerate
combination
\begin{equation}
  \Omega_{A0}+\Omega_{K0}
  =
  1-\Omega_{\Lambda,\OPH}-\Omega_{b0}-\Omega_{\nu0}-\Omega_{r0},
  \qquad
  \Omega_{\Lambda,\OPH}
  =
  \left(\frac{H_{\mathrm{dS}}}{H_0}\right)^2.
  \label{eq:flatresidual}
\end{equation}
The displayed number becomes an \(\Omega_{A0}\) value only after an independent curvature readout or
an explicit flat-branch assumption \(\Omega_{K0}=0\).  It cannot be used to prove flatness.
The transported homogeneous dust branch is
\begin{equation}
  \rho_A(a)=\rho_{A0}a^{-3}.
\end{equation}
The legacy plumbing run used \(H_0=67.4\,\mathrm{km\,s^{-1}\,Mpc^{-1}}\),
\(\Omega_b h^2=0.02237\), \(\Omega_r=9.17\times10^{-5}\), and the
target-informed weighted-cycle comparison value
\(\sum m_\nu=0.0900119296\,\mathrm{eV}\).  That neutrino value is now rejected
and has no OPH prediction status.  The resulting historical residual was:
\begin{center}
\begin{tabular}{@{}lr@{}}
\toprule
Quantity & Legacy diagnostic value \\
\midrule
\(H_{\mathrm{dS}}\) & \(55.759940256\,\mathrm{km\,s^{-1}\,Mpc^{-1}}\) \\
\(\Omega_{\Lambda,\OPH}\) & \(0.684423332\) \\
\(\Omega_b\) & \(0.049243191\) \\
\(\Omega_\nu\) & \(0.002127375\) \\
\(\Omega_r\) & \(0.000091700\) \\
\(\Omega_A+\Omega_K\) & \(0.264114401\) \\
\(\Omega_m\) & \(0.315484968\) \\
\(\rho_{A0}\) & \(2.253649933\times10^{-27}\,\mathrm{kg\,m^{-3}}\) \\
\bottomrule
\end{tabular}
\end{center}
The \(\Omega_m=0.315484968\) here is the Friedmann closure sum
\(\Omega_A+\Omega_K+\Omega_b+\Omega_\nu\); the CAMB tables later in the paper
print the solver output \(0.315905207\) from the same inputs, and the quoted
Planck pull uses the latter.
This legacy number matches the Planck-like cold-matter budget at the
compressed-parameter level only on the explicit flat benchmark.  It is
invalidated as a current quantitative OPH row because its supplied neutrino
input came from the rejected weighted-cycle candidate.  A current run must
declare an external neutrino scenario and recompute the residual.  Even then,
the number is a closure residual,
not an independent anomaly abundance and not a flatness proof.  The static galaxy RAR law
does not determine it.  The OPH theorem that would make \(\Omega_{A0}\) standalone is a
finite-screen additive-load selector for the conserved homogeneous anomaly charge together with an
independent curvature label.

Finite exports must therefore label
\[
\Omega_{A,\mathrm{source}}\in
\{\textsc{IndependentOPH},\textsc{External},\textsc{ResidualDefinition},\textsc{Unknown}\}
\]
and separately label the curvature source.  A residual-defined \(\Omega_A\) cannot pass a
Friedmann-curvature independence audit.

The closed transported branch does give a theorem-grade current and charge.
Let \(u_A^a\) be the branch four-velocity and let \(\rho_A\) be the
coarse-grained information-defect load density.  The load current is
\begin{equation}
  J_A^a=\rho_A u_A^a .
\end{equation}
On the closed branch,
\begin{equation}
  \nabla_aJ_A^a=0,
  \qquad
  Q_A[\Sigma]=\int_{\Sigma} J_A^a n_a\,\dd\Sigma
\end{equation}
is independent of the homogeneous slice.  In FLRW this gives
\begin{equation}
  Q_A=a^3\rho_A V_{\mathrm{com}},
  \qquad
  \rho_A(a)=\frac{Q_A}{a^3V_{\mathrm{com}}}.
\end{equation}
This proves transport of a supplied homogeneous load.  It does not fix the
amplitude \(Q_A\).  The source-only selector is the quotient expectation of the
parent-emitted anomaly load on a release hypersurface,
\begin{equation}
  \mathcal E_{A,r}
  =
  F_{A,r}\!\left(
    Q^{\rm rel}_{A,r},\mu^{\rm rel}_{A,r},P_\star,N_{\rm CRC},
    \mathfrak R^{\rm rel}_{A,r},\mathcal P_r
  \right),
  \qquad
  \rho_A(a)=\frac{\mathcal E_{A,r}}{a^3V_{\mathrm{com},r}} .
\end{equation}
Section~\ref{sec:source-only-anomaly-abundance-selector} gives the finite
selector and receipt.  Without that source selector receipt, the abundance is
cosmological state data or the flat capacity-saturated residual
\eqref{eq:flatresidual}.

\subsection{Environmental Kernel}

Around a nonzero local background field
\(\bar{\mathbf g}_b\), write
\begin{equation}
  x=\frac{|\bar{\mathbf g}_b|}{\aoph},
  \qquad
  \mathbf n=\frac{\bar{\mathbf g}_b}{|\bar{\mathbf g}_b|}.
\end{equation}
Linearizing the anomaly field
\((\nu_{\OPH}-1)\mathbf g_b\) gives the susceptibility
\begin{equation}
  A_{ij}
  =
  [\nu_{\OPH}(x)-1]\delta_{ij}
  +x\nu_{\OPH}'(x)n_i n_j,
\end{equation}
where
\begin{equation}
  \nu_{\OPH}'(x)
  =
  -\frac{
    \lambdac\exp[-\lambdac\sqrt{x}]
  }{
    2\sqrt{x}[1-\exp(-\lambdac\sqrt{x})]^2
  }.
\end{equation}
For a Fourier mode whose direction has cosine \(\mu\) against \(\mathbf n\),
the density-response multiplier is
\begin{equation}
  K_A^{(\rho)}(x,\mu)
  =
  \nu_{\OPH}(x)-1+x\nu_{\OPH}'(x)\mu^2.
  \label{eq:environmentalkernel}
\end{equation}
An isotropic environmental average gives
\begin{equation}
  \langle K_A^{(\rho)}\rangle
  =
  \nu_{\OPH}(x)-1+\frac{x}{3}\nu_{\OPH}'(x).
\end{equation}
The contrast kernel used in perturbation equations is normalized by the
equilibrium-background density ratio only after the response is diagonal in the calibrated physical mode basis:
\begin{equation}
  B_A(k,a)
  =
  \frac{\bar\rho_b(a)}{\bar\rho_{A,\mathrm{eq}}(a)}K_A^{(\rho)}(k,a).
\end{equation}
Using \(\bar\rho_A\) in the denominator would define the different variable
\(\delta\rho_{A,\mathrm{eq}}/\bar\rho_A\) and would require rederiving the
external \(q_A=\bar\rho_{A,\mathrm{eq}}/\bar\rho_A\) factor in the perturbation
equations.  This paper uses the equilibrium-contrast convention globally.
At finite regulator the primary object is the response operator
\begin{equation}
  (B_{A,r})_{jj'}(a)
  =
  \frac{\bar\rho_b(a)}{\bar\rho_{A,\mathrm{eq}}(a)}
  \left\langle
  v_{rj},
  D\rho_{A,\mathrm{eq}}[\bar\rho_b]\,
  v_{rj'}
  \right\rangle ,
\end{equation}
where \(v_{rj}\) are the same calibrated comoving scalar modes used by the
primordial source and transfer handoff.  A scalar table \(B_A(k_j,a)\) is
promoted only if
\[
\|[B_{A,r},\Delta_{\mathrm{com},r}]\|\le\varepsilon_{\rm comm},\qquad
\sum_{j'\ne j}|(B_{A,r})_{jj'}|^2\le\varepsilon_{\rm off}^2
\]
on the resolved band.  Otherwise the physical input is the mode-coupling matrix,
not a diagonal function of \(k\).
In a realistic cosmological calculation, this local expression has to be
integrated against the distribution of environmental fields,
\begin{equation}
  K_A^{(\rho)}(k,a)
  =
  \int\dd x\,\dd\mu\,
  \Pi(x,\mu|k,a)
  [\nu_{\OPH}(x)-1+x\nu_{\OPH}'(x)\mu^2].
\end{equation}
This average is finite only under an explicit small-field support condition,
for example
\begin{equation}
  \int_0^\epsilon \dd x\,\dd\mu\,
  \Pi(x,\mu|k,a)\,x^{-1/2}<\infty
  \qquad
  \text{for some }\epsilon>0.
\end{equation}
If \(\Pi\) has an exact atom at \(x=0\), the local nonzero-field kernel is not
the correct FLRW response.
The distribution \(\Pi\) is an OPH finite-collar output or an explicitly
declared environmental closure.  Exact FLRW has \(x=0\), so
\eqref{eq:environmentalkernel} does not provide a regular universal CMB
density-response kernel by itself.

The implementation contract uses one parent finite-collar functional:
\begin{equation}
  \rho_{A,\mathrm{eq}}[X]c^2
  =
  \frac{15}{8\pi^2\ell(X)^4}
  \int_{\mathcal C_X}\dd\mu_C\,
  R_C^{\mathrm{src}}[\omega_C].
  \label{eq:parentfunctional}
\end{equation}
For finite samples \(s\) with weights \(w_s\), define
\begin{align}
  R(X)&=\frac{\sum_s w_s R_s^{\mathrm{src}}}{\sum_s w_s},\\
  K_A^{(\rho)}(k,a)
  &=\frac{1}{\bar\rho_b}
    \frac{\partial \rho_{A,\mathrm{eq}}}{\partial \delta_b(k,a)},\\
  B_A(k,a)
  &=\frac{\bar\rho_b(a)}{\bar\rho_{A,\mathrm{eq}}(a)}K_A^{(\rho)}(k,a).
\end{align}
The same evaluator emits the homogeneous equilibrium density, the linear
density-response kernel, the settled galaxy source, and the cluster
equilibrium source.  A theorem-grade prediction requires the OPH collar
measure \(\dd\mu_C\), the finite-screen ensemble, and the small-field support
condition.  Fitting \(\Pi\) to CMB, weak-lensing, SPARC, or cluster data is
excluded.

\subsection{Physical Source And Kernel Promotion}

The scalar tables used by Boltzmann codes are the last stage of a finite
source construction.  Let \(Q_{r,a}\) be the finite quotient state space at
regulator \(r\) and background scale factor \(a\).  A physical anomaly source
is a quotient-visible \(C^1\) functional
\begin{equation}
  \mathcal E_{A,r}:Q_{r,a}\times\mathcal A\longrightarrow\mathbb R
\end{equation}
such that
\begin{equation}
  \bar\rho_{A,\mathrm{eq},r}(a)
  =
  \mathcal E_{A,r}(q_{0,r}(a),a),
  \qquad
  D\mathcal E_{A,r}|_{q_0}
  \ \hbox{is the anomaly response used in }B_{A,r}.
\end{equation}
For the fixed-reference modular-energy route one may write, on each frozen
reference patch,
\begin{equation}
  \mathcal E_{A,r}(q,a)
  =
  \rho_{A,\mathrm{eq},r}^{(0)}(a)
  +\mathcal N_{r,a}\,
  \operatorname{Tr}\!\left[
    \bigl(\rho_r(q)-\sigma_{r,a}\bigr)
    K^{\rm anom}_{\sigma,r,a}
  \right]
  +\mathcal R_{2,r}(q,a),
\end{equation}
with \(\mathcal R_{2,r}(q_0,a)=0\) and
\(D\mathcal R_{2,r}|_{q_0}=0\).  Then
\[
  D\mathcal E_{A,r}|_{q_0}[v]
  =
  \mathcal N_{r,a}
  \operatorname{Tr}\!\left[D\rho_r|_{q_0}[v]\,K^{\rm anom}_{\sigma,r,a}\right].
\]
The shift \(K^{\rm anom}_{\sigma,r,a}\mapsto
K^{\rm anom}_{\sigma,r,a}+cI\) leaves this tangent term invariant because
\(\operatorname{Tr} D\rho_r[v]=0\).  The baseline
\(\rho_{A,\mathrm{eq},r}^{(0)}\) is separate finite source data; a modular
variation alone gives a response, not an absolute positive abundance.
For a nonlinear-CMI route at an exact Markov reference, the first variation
vanishes and the leading object is the Hessian.  A nonzero linear response
from CMI therefore requires a declared non-Markov background and its residual.

Let finite packet occupations satisfy
\[
  \mathcal M_{r,a}
  =
  \{f\in\mathbb R_{\ge0}^{N_r}:A_{r,a}f=b_{r,a}\},
  \qquad
  Q_{r,a}=\mathcal M_{r,a}/\mathcal G_{r,a}.
\]
At an interior background \(f_0>0\),
\begin{equation}
  T_{[f_0]}Q_{r,a}
  =
  \ker A_{r,a}/T_{f_0}(\mathcal G_{r,a}\cdot f_0).
\end{equation}
Boundary backgrounds use the corresponding tangent cone.  A symmetric
\(\pm\epsilon\) finite difference is admissible only when both perturbed
states stay in the same admissible support.  For a retraction
\(\mathcal R_{q_0}(0)=q_0\), \(D\mathcal R_{q_0}(0)=I\), and a \(C^3\)
readout \(E_r\),
\[
  \frac{
  E_r(\mathcal R_{q_0}(\epsilon v))
  -E_r(\mathcal R_{q_0}(-\epsilon v))
  }{2\epsilon}
  =
  DE_r[v]+O(\epsilon^2).
\]
If the third directional derivative is bounded by \(M_v\), the truncation
error is at most \(M_v\epsilon^2/6\).

Let \(S_r:Q_{r,a}\to U_r\) be the delivered baryon-source map and
\(E_r:Q_{r,a}\to Y_r\) the anomaly source map.  A physical response depending
only on the delivered source exists exactly when
\begin{equation}
  \ker DS_r|_{q_0}\subseteq\ker DE_r|_{q_0}.
\end{equation}
Then there is a unique linear operator
\[
  B_{A,r}:\operatorname{im}DS_r|_{q_0}\to Y_r
\]
such that \(DE_r|_{q_0}=B_{A,r}DS_r|_{q_0}\).  This is the
lift-independence condition: perturbing a collar width, packet occupation, or
port current gives the same kernel only if those microscopic lifts deliver the
same physical source tangent.

The delivered source should initially be the vector
\[
  \mathcal S_b=
  \bigl(
    \Delta_b^{(A)},\Theta_b^{(A)},\delta T_b^{[\tau]},
    \delta x_e^{[\tau]},\Phi_{\rm GI},\Psi_{\rm GI},\ldots
  \bigr),
\]
and the anomaly output the vector
\[
  \mathcal Y_A=
  \bigl(
    \delta\rho_A,\delta p_A,q_A,\pi_A,\delta Q_A,F_A,\ldots
  \bigr).
\]
A scalar \(B_A(k,a)\) is licensed only when non-density columns are below the
declared frozen residual threshold.  If geometry feedback is present, the
Boltzmann handoff normally receives the bare partial derivatives
\((E_b,E_g)\), while the dressed static gain is
\[
  B_{\rm dressed}=(I-E_gG_A)^{-1}(E_b+E_gG_b).
\]
Passing the dressed gain into a solver that separately evolves metric
feedback would count gravity twice.

The physical repair rate has the same source discipline.  An equilibrium
sampler kernel does not determine physical time.  The finite parent must
provide native rates \(q_u(x,y)\) and a physical clock,
\[
  (L_uf)(x)=\sum_{y\ne x}q_u(x,y)[f(y)-f(x)].
\]
The generator descends to the quotient iff, for any two representatives
\(\pi(x)=\pi(x')\),
\[
  \sum_{y:\pi(y)=q'}q_u(x,y)
  =
  \sum_{y:\pi(y)=q'}q_u(x',y)
  \quad\hbox{for every quotient state }q'.
\]
Only this native generator, together with quotient lumpability and physical
rate units, can promote \(\Gamma_{\rm rec}\).  Static settled-state response,
step response, and the integrated retarded kernel must agree in the common
parent model before a one-pole reduction is emitted.

The physical kernel receipts are therefore
\begin{center}
\begin{tabular}{@{}l@{}}
\texttt{COMMON\_SOURCE\_FUNCTIONAL\_RECEIPT}\\
\texttt{ADMISSIBLE\_SOURCE\_TANGENT\_RECEIPT}\\
\texttt{CONSTRAINT\_PRESERVING\_RETRACTION\_RECEIPT}\\
\texttt{SOURCE\_VECTOR\_SUFFICIENCY\_RECEIPT}\\
\texttt{B\_A\_SOURCE\_LIFT\_INDEPENDENCE\_RECEIPT}\\
\texttt{SOURCE\_DESIGN\_IDENTIFIABILITY\_RECEIPT}\\
\texttt{FINITE\_DIFFERENCE\_ORDER\_RECEIPT}\\
\texttt{C1\_REFINEMENT\_RECEIPT}\\
\texttt{ORDER\_OF\_LIMITS\_RECEIPT}\\
\texttt{NATIVE\_REPAIR\_GENERATOR\_RECEIPT}\\
\texttt{PHYSICAL\_RATE\_UNIT\_RECEIPT}\\
\texttt{QUOTIENT\_LUMPABILITY\_RECEIPT}\\
\texttt{STATIC\_DYNAMIC\_RESPONSE\_CONSISTENCY\_RECEIPT}
\end{tabular}
\end{center}
The simulator may emit diagnostic candidates before these receipts pass, but
those candidates are not physical \(B_A\), \(\rho_{A,\mathrm{eq}}\), or
\(\Gamma_{\rm rec}\) kernels.

\subsection{Compressed CMB, BAO, Growth, And \(S_8\) Diagnostic}

The checked-in legacy Boltzmann plumbing test passes the anomaly as a cold
pressureless component with the flat-benchmark diagnostic parent-grid ratio
\(\rho_A/\rho_b=5.363470441\).  It uses CAMB \(1.6.6\), the rejected
weighted-cycle comparison value \(\sum m_\nu=0.0900119296\,\mathrm{eV}\), and
diagonal Gaussian compressed rows.  The neutrino input is a compare-only
historical coordinate, not an OPH prediction:
\begin{center}
\begin{tabular}{@{}lrrr@{}}
\toprule
Quantity & Legacy diagnostic & Target & Pull \\
\midrule
Planck \(\Omega_m\) & \(0.315905207\) & \(0.315\pm0.007\) & \(+0.129\) \\
Planck \(\sigma_8\) & \(0.807787208\) & \(0.811\pm0.006\) & \(-0.535\) \\
Planck \(S_8\) & \(0.828924043\) & \(0.831027707\pm0.0111\) & \(-0.190\) \\
DESI DR1 BAO \(\Omega_m\) & \(0.315905207\) & \(0.295\pm0.015\) & \(+1.394\) \\
DESI DR1 BAO/BBN/\(\theta_\ast\) \(H_0\) & \(67.4\) & \(68.52\pm0.62\) & \(-1.806\) \\
Weak-lensing \(S_8\) & \(0.828924043\) & \(0.790\pm0.016\) & \(+2.433\) \\
\bottomrule
\end{tabular}
\end{center}
The Planck rows are in-loop consistency rows, not predictions: the
flat-benchmark \(\Omega_A\) is a Friedmann residual built from measured
inputs on a Planck-like budget, fed to CAMB, and scored against Planck.  The
weak-lensing \(S_8\) row is the one discriminating row in this table; at
\(+2.433\sigma\) it currently disfavors the benchmark.
The historical diagonal compressed value is \(\chi^2=11.463\) for six rows.
Because the run inherited the rejected neutrino input, it is invalidated as a
current OPH score and is retained only as a reproducibility record.  Even after
regeneration with an explicitly declared external neutrino scenario, this is a
plumbing check and does not replace Planck, DESI, or weak-lensing likelihoods.
A publication-grade calculation needs the OPH \(B_A(k,a)\) kernel in a custom
Boltzmann module and the full experimental covariances.

\section{Likelihood Contracts}

\subsection{SPARC Disk-Potential Contract}

The publication-grade SPARC test must solve the conservative disk equation
\begin{equation}
  \nabla^2\Phi
  =
  \nabla\cdot
  \left[
    \nu_\lambda\!\left(\frac{|\nabla\Phi_b|}{\aoph}\right)
    \nabla\Phi_b
  \right]
\end{equation}
on an axisymmetric baryonic disk model.  The hierarchy must marginalize or
profile distance, inclination, disk and bulge mass-to-light ratios, gas scale,
intrinsic scatter, velocity covariance, quality cuts, and grid convergence.
The unit branch and the \(\Zsix\)/Poisson branch are fixed before this test;
SPARC is used as a comparison, not as the selector for \(\lambdac\).  The
equation is scoped to old settled galaxies: its universal extension is
excluded by Cassini at \(19.22\sigma\), and the contract inherits that scope
restriction until a source-derived applicability theorem exists.

\subsection{Cluster Map Contract}

The cluster forward model uses gas hydrodynamics, stellar and galaxy tracers,
transported defect stress, the repair source
\(\rho_{A,\mathrm{eq}}\), lensing projection, X-ray emissivity, SZ pressure,
and covariance-aware map likelihoods.  Merging clusters test whether the
transported stress lags collisional gas.  Relaxed clusters test whether the
same stress law returns to the static equilibrium source.  The static-only
failure mode is part of the likelihood contract.

\subsection{Boltzmann Contract}

The Boltzmann module exposes
\[
  \bar\rho_A(a),\quad
  \bar\rho_{A,\mathrm{eq}}(a),\quad
  w_A(a),\quad
  c_{s,A}^2(k,a),\quad
  \sigma_A(k,a),\quad
  Q_A^\mu,\quad
  B_A(k,a),\quad
  \Gamma_{\mathrm{rec}}(k,a),
\]
with an explicitly declared external neutrino-mass scenario in the same run.
The rejected weighted-cycle tuple may appear only as a labeled compare-only
scenario; it may not be a default, a source input, or a promotion path.  Every
dark-sector entry must be derived
from a frozen finite covariant parent artifact with no CMB, BAO, lensing,
SPARC, or cluster fit in that source step.  It must recover the \(\LCDM\)
cold-component limit when the exchange and stress corrections are turned off,
reproduce the compressed diagnostic rows only as a plumbing check, and then run
the full CMB TT/TE/EE, CMB lensing, BAO, supernova, weak-lensing, RSD, and
\(S_8\) likelihoods under the same nuisance model used for \(\LCDM\) and
\(w_0w_a\).  The physical likelihood run is frozen by immutable hashes for the
source artifact, Boltzmann solver, and likelihood configuration before the data
comparison.  The same run must expose official likelihood and CDM-limit
reductions at global scope. Shard-local \(\texttt{any()}\) rollups do not
promote the source artifact.

\section{Numerical Galaxy Comparison}

The OPH capacity benchmark used here is
\begin{equation}
  \aoph = 1.029186271\times10^{-10}\,\mathrm{m\,s^{-2}}.
\end{equation}
The value of \(\aoph\) is built from the measured \(H_0\) and \(\Lambda\)
through the capacity de Sitter branch and the SI clock bridge.  Under the
strange-loop principle set these are SL-4/SL-5 inputs
(\texttt{../docs/STRANGE\_LOOP\_PRINCIPLES.md}), so \(\aoph\) inherits two measured cosmological
quantities.  Every comparison of \(\aoph\) or \(\aeff\) against the empirical
acceleration scale in this section is therefore a consistency display between
measured inputs, not an OPH prediction.
The common empirical reference is
\begin{equation}
  a_0^{\mathrm{emp}}=1.2\times10^{-10}\,\mathrm{m\,s^{-2}}.
\end{equation}
The \(\Zsix\)/Poisson branch gives
\begin{equation}
  \lambdac=0.934300639,
  \qquad
  \aeff=1.179018696\times10^{-10}\,\mathrm{m\,s^{-2}}.
\end{equation}

\begin{center}
\begin{tabular}{@{}lrr@{}}
\toprule
Quantity & Value & Comparison \\
\midrule
\(\aoph\) &
\(1.029186271\times10^{-10}\) &
\(-8.070\%\) versus best same-function RAR \\
\(\aoph\) &
\(1.029186271\times10^{-10}\) &
\(-14.234\%\) versus empirical reference \\
\(\aeff\), \(\Zsix\)/Poisson &
\(1.179018696\times10^{-10}\) &
\(+5.314\%\) versus best same-function RAR \\
\(\aeff\), \(\Zsix\)/Poisson &
\(1.179018696\times10^{-10}\) &
\(-1.748\%\) versus empirical reference \\
\bottomrule
\end{tabular}
\end{center}
These rows are consistency displays: \(\aoph\) carries measured \(H_0\) and
\(\Lambda\), and an exact hit on the common empirical \(a_0\) would require
about \(13\%\) more protected inactive reserve than the \(P/24\) behind
\(\lambdac=e^{-P/24}\) (see the Correction Audit).

\subsection{SPARC RAR}

At \(\lambdac=1\) the response function \(\nu_{\OPH}(x)\) of
\eqref{eq:ophrar} coincides with the McGaugh--Lelli--Schombert empirical
interpolating function, which was fitted to the SPARC radial acceleration
relation \cite{mcgaugh2016}.  The SPARC comparisons below therefore score a
SPARC-fitted functional form against SPARC itself: they are not held-out
tests, and per the sensitivity audit they mostly test normalization rather
than shape.  Using the public SPARC RAR data \cite{sparcpage,mcgaugh2016},
the local diagnostic gives:
\begin{center}
\begin{tabular}{@{}lrrr@{}}
\toprule
Scenario & \(a_0\) in \(\mathrm{m\,s^{-2}}\) & RMS dex & Binned RMS dex \\
\midrule
OPH unit & \(1.029186271\times10^{-10}\) & \(0.134208\) & \(0.026169\) \\
\(\Zsix\)/Poisson & \(1.179018696\times10^{-10}\) & \(0.132834\) & \(0.015760\) \\
Empirical reference & \(1.200000000\times10^{-10}\) & \(0.132913\) & \(0.016164\) \\
Best same-function & \(1.119530397\times10^{-10}\) & \(0.132947\) & \(0.017428\) \\
\bottomrule
\end{tabular}
\end{center}
All rows share the SPARC-fitted functional form and are non-held-out; the
comparison mostly tests normalization.  An exact hit on the common empirical
\(a_0\) would require about \(13\%\) more protected reserve than \(P/24\).

\subsection{Rotation Diagnostics}

The fixed stellar mass-to-light diagnostic and the first nuisance-profiled
diagnostic give:
\begin{center}
\begin{tabular}{@{}lrrr@{}}
\toprule
Scenario & Fixed-M/L RMS & Profiled-M/L \(\chi^2/\mathrm{pt}\) & Profiled RMS \\
\midrule
OPH unit & \(23.366208\) & \(1.341948\) & \(12.420181\) \\
\(\Zsix\)/Poisson & \(22.868866\) & \(1.390941\) & \(12.590203\) \\
Empirical reference & \(22.842145\) & \(1.400930\) & \(12.624079\) \\
\bottomrule
\end{tabular}
\end{center}
Units for the RMS columns are \(\mathrm{km\,s^{-1}}\).  These rows inherit
the SPARC-fitted functional form and the measured-input \(\aoph\); they are
non-held-out consistency displays that mostly test normalization.

\subsection{Systematic Likelihood Scaffold}

A stronger local scaffold profiles stellar M/L, distance, inclination, and gas
scale per galaxy using the SPARC sample table \cite{lelli2016,sparcpage}.  It
uses \(Q\le2\), inclination at least \(30^\circ\), and 3168 rotation-curve
rows.
\begin{center}
\begin{tabular}{@{}lrrrr@{}}
\toprule
Scenario & \(\chi^2/\mathrm{pt}\) & \(\chi^2/\mathrm{dof}\) & RMS & Median disk M/L \\
\midrule
OPH unit & \(1.016589\) & \(1.275672\) & \(11.249541\) & \(0.519102\) \\
\(\Zsix\)/Poisson & \(1.021093\) & \(1.281324\) & \(11.276832\) & \(0.497435\) \\
Empirical reference & \(1.023261\) & \(1.284045\) & \(11.285518\) & \(0.493865\) \\
\bottomrule
\end{tabular}
\end{center}
The systematic scaffold mildly favors the unit branch.  The \(\Zsix\)/Poisson
branch remains the better acceleration-scale and fixed-M/L RAR match.  The
fixed-M/L improvement alone is weak evidence for the \(\Zsix\) bridge theorem.
This table shares the non-held-out SPARC provenance and the
mostly-normalization sensitivity caveat of the RAR rows above, and the
\(13\%\) reserve mismatch against the common empirical \(a_0\) applies to
its acceleration scales unchanged.

\subsection{Audited Fixed-Branch RAR And BTFR Results}

The aggregate RAR calculation above is now also evaluated explicitly as a
fixed-branch test.  Without refitting either OPH branch to the 2,693 public RAR
rows from 153 galaxies, the conditional \(\Zsix\) scale gives
\(0.1328335\) dex RMS, while the unit endpoint gives \(0.1342082\) dex.  The
effective scale that minimizes the same table's diagonal chi-square proxy has
RMS \(0.1329467\) dex.  The near equality is an encouraging retrospective
check of the fixed formula and scale.  It is not a blind prediction:
\(\aoph\) is a capacity/cosmology benchmark, exact
\(\lambdac=e^{-P/24}\) is conditional, and the aggregate rows share distance,
inclination, and stellar-population systematics.  A full nuisance-aware SPARC
analysis independently reports
\[
a_0=(1.19\pm0.04_{\rm stat}\pm0.09_{\rm sys})\times10^{-10}
\,\mathrm{m\,s^{-2}},
\]
placing the conditional \(\Zsix\) value near its central result
\cite{desmond2023}.

The BTFR audit corrects an earlier statistics error.  Unweighted ordinary
least squares discarded the published errors in both \(M_b\) and \(V_f\), and
the earlier \(0.9469\)-dex headline compared unequal-slope intercepts at
\(V_f=1\,\mathrm{km\,s^{-1}}\), far outside the sample.  Orthogonal maximum
likelihood with both-axis errors and intrinsic perpendicular scatter gives
\[
s_{\rm BTFR}=3.845654\pm0.085817,
\]
reproducing the published \(3.85\pm0.09\) result \cite{lelli2019}.  The OPH
deep-limit slope \(4\) is \(1.80\sigma\) high and lies within the published
systematic range \(3.5\)--\(4.0\).  At the declared
\(100\,\mathrm{km\,s^{-1}}\) pivot, however, the fixed-slope fit gives
\(\log_{10}(M_b/M_\odot)=9.670792\pm0.020827\), whereas the conditional
\(\Zsix\) normalization predicts \(9.805555\).  The data-minus-model offset is
therefore \(-0.134763\) dex, or \(-6.47\sigma\) using only the fit's statistical
normalization error.  That pull does not yet marginalize a global stellar
mass-to-light shift, distances, inclinations, sample selection, or whether
every reported \(V_f\) has reached the asymptotic regime.  The 123-galaxy BTFR
table is drawn from SPARC, so it is a separate observable on an overlapping
sample rather than an independent galaxy population.

These aggregate checks evaluate the algebraic RAR proxy.  They do not replace
the conservative disk solve of the likelihood contract.  In non-spherical
geometry \(\nabla\nu\times\mathbf g_b\) need not vanish, so a
publication-grade OPH test must expose the curl-field residual pattern rather
than assume the pointwise algebraic relation.

\subsection{Cassini Applicability Stress}

If the conservative settled-galaxy equation is extrapolated universally to a
Solar source embedded in the measured Galactic external field, it predicts an
external-field quadrupole.  The audited angular integral reproduces the
published spherical benchmark and gives
\[
Q_2^{\Zsix}=3.62018\times10^{-26}\,\mathrm{s^{-2}},\qquad
Q_2^{\lambda=1}=3.40219\times10^{-26}\,\mathrm{s^{-2}}.
\]
Against the Cassini summary
\(Q_2=(1.6\pm1.8)\times10^{-27}\,\mathrm{s^{-2}}\), these are fixed-input
residuals of \(19.22\sigma\) and \(18.01\sigma\), respectively
\cite{park2026}.  Adding only the linearized Gaia uncertainty on the Galactic
acceleration reduces the \(\Zsix\) pull to about \(10.71\sigma\), still
strongly negative \cite{gaia2021}.  No sign, unit, angular-integration, or
branch-mapping error has been found.

This falsifies the natural universal/full-source extension of the displayed
static equation.  It does not, by itself, falsify the recovered OPH core or
the equation's declared old-settled-galaxy scope.  The branch now owes a
quantitative source-derived applicability, coarse-graining, screening, or
transport theorem that preserves the galaxy result while suppressing the
Solar-System quadrupole.  A free switch introduced after reading Cassini would
be a fitted continuation, not that theorem.

\subsection{Empirical Implementation Scorecard}

The executable empirical pass combines four diagnostic layers: public SPARC
tables, the flat-benchmark capacity-saturated homogeneous anomaly state, the finite
repair matrix with a cluster timing gate, and the compressed CAMB rows.  The
checked-in single-pass output below predates the neutrino audit and used the
rejected weighted-cycle mass sum.  It is an invalidated legacy diagnostic, not
a current OPH number surface:
\begin{center}
\small
\begin{tabularx}{\textwidth}{@{}p{0.39\textwidth}p{0.24\textwidth}X@{}}
\toprule
Quantity & Stored legacy diagnostic & Measurement comparison \\
\midrule
\(\Omega_A\) & \(0.264114401\) & Planck-like matter budget under \(\Omega_K=0\) benchmark \\
\(\Omega_{\Lambda,\OPH}\) & \(0.684423332\) & capacity de Sitter branch \\
\(\rho_A/\rho_b\) & \(5.363470441\) & flat-benchmark residual ratio \\
\(\gamma_{\mathrm{repair\ step}}\) & \(0.050717471\) & finite repair matrix step-gap diagnostic \\
\(\aoph\) & \(1.029186271\times10^{-10}\) & \(8.070\%\) low versus best RAR \\
\(\aeff\), \(\Zsix\)/Poisson & \(1.179018696\times10^{-10}\) & \(1.748\%\) low versus common empirical \(a_0\) \\
SPARC systematic \(\chi^2/\mathrm{pt}\), unit & \(1.016589\) & best scaffold row \\
SPARC systematic \(\chi^2/\mathrm{pt}\), \(\Zsix\) & \(1.021093\) & close scaffold row \\
CAMB \(\Omega_m\) & \(0.315905206\) & \(+0.129\sigma\) versus Planck \\
CAMB \(\sigma_8\) & \(0.807787204\) & \(-0.535\sigma\) versus Planck \\
CAMB \(S_8\) & \(0.828924037\) & \(+2.433\sigma\) versus weak lensing \\
\bottomrule
\end{tabularx}
\end{center}
Row labels: the CAMB \(\Omega_m\) and \(\sigma_8\) rows scored against Planck
are in-loop consistency rows, since the flat-benchmark \(\Omega_A\) residual
consumed Planck-like measured inputs before CAMB ran.  The weak-lensing
\(S_8\) row is the discriminating out-of-loop row and currently disfavors the
benchmark at \(+2.433\sigma\).  The \(\aoph\) and \(\aeff\) rows carry
measured \(H_0\) and \(\Lambda\) inside \(\aoph\), the non-held-out SPARC
provenance of \(\nu_{\OPH}\), and the \(13\%\) reserve mismatch against the
common empirical \(a_0\); the SPARC \(\chi^2\) rows mostly test
normalization.

The stored legacy CMB/BAO/growth score is
\[
  \chi^2_{\mathrm{diag}}=11.463
  \qquad \hbox{for six compressed rows.}
\]
Within that invalidated run, the pressure point was weak-lensing \(S_8\).  The stored value is
\(0.828924037\).  The DES/KiDS compressed row is \(0.790\pm0.016\).

For the cluster timing gate, take a \(200\,\mathrm{kpc}\) initial anomaly
separation, a \(0.2\,\mathrm{Gyr}\) time after passage, and an example measured
offset \(150\pm50\,\mathrm{kpc}\).  The repair matrix gives:
\begin{center}
\begin{tabular}{@{}rrrrr@{}}
\toprule
\(\tau_{\mathrm{rec}}\) in Gyr & \(t_{\mathrm{commit}}\) in Myr &
Retained fraction & Offset in kpc & \(\chi^2\) \\
\midrule
\(0.3\) & \(15.2152\) & \(0.513417\) & \(102.683\) & \(0.896\) \\
\(0.5\) & \(25.3587\) & \(0.670320\) & \(134.064\) & \(0.102\) \\
\(1.0\) & \(50.7175\) & \(0.818731\) & \(163.746\) & \(0.076\) \\
\bottomrule
\end{tabular}
\end{center}
This row is a timing gate.  Map likelihoods need observed lensing maps, gas
maps, stellar maps, merger-age priors, and covariance.

\subsection{Implementation Work Packages}

The code required for paper-grade empirical tests consists of the following
modules:
\begin{enumerate}
\item An axisymmetric conservative disk-potential solver for
\[
  \nabla^2\Phi
  =
  \nabla\cdot[\nu(|\nabla\Phi_b|/\aoph)\nabla\Phi_b],
\]
with grid-convergence tests and lensing-potential output.
\item A hierarchical SPARC likelihood that samples or profiles distance,
inclination, disk M/L, bulge M/L, gas scale, intrinsic scatter, velocity
covariance, and selection cuts under one nuisance model.
\item A finite-collar parent evaluator for \(\rho_A(a)\),
\(K_A^{(\rho)}(k,a)\), \(B_A(k,a)\), and
\(\rho_{A,\mathrm{eq}}[X]\), using OPH collar samples as input.  The
scalar-load diagnostic grid is plumbing only.
\item A CAMB or CLASS anomaly module exposing the background density, stress
variables, exchange current, relaxation kernel, environmental response
kernel, and an explicitly declared external neutrino-mass scenario in one run.
The rejected weighted-cycle tuple may be retained only as a named compare-only
scenario and must fail every promotion gate.
\item A cluster forward model with gas hydrodynamics, galaxy and stellar
tracers, transported anomaly stress, lensing projection, X-ray and SZ
observables, merger-age priors, and map covariance.
\item A likelihood runner for Planck or ACT spectra, CMB lensing, BAO,
supernovae, weak lensing, RSD, SPARC, and cluster maps, with model comparison
against \(\LCDM\), empirical MOND functions, halo models, and \(w_0w_a\)
extensions.
\item A reproducibility harness with fixed data hashes, fixed random seeds,
unit checks, and independent numerical replication of the scorecard rows.
\end{enumerate}

\subsection{Executable Dark-Sector Simulation Ladder}

The simulator counterpart is organized as a promotion ladder, not as a single
dark-matter model run.  The integration command is
\begin{verbatim}
python3 -m oph_fpe.cli dark-sector-simulation-plan --run-dir runs/<run_id> \
  --out runs/<run_id>/dark_sector_simulation_plan
\end{verbatim}
and emits \texttt{DARK\_SECTOR\_SIMULATION\_PLAN\_RECEIPT}.  The report reads
the static galaxy, finite covariant parent, finite-collar Boltzmann bundle,
Boltzmann-input, CMB-anomaly, and frozen-likelihood reports, records the first
blocked gate, and names the next simulator command.  It is a receipt-audit and
work-queue object.  It is not a physical dark-sector prediction, not a fitted
likelihood, and not a substitute for source-generation receipts.

The gate order is:
\begin{enumerate}
\item Static galaxy diagnostic:
\texttt{run-galaxy-static} must emit
\texttt{STATIC\_GALAXY\_RAR\_BTFR\_RECEIPT}.  This checks only the settled
RAR/BTFR bridge.
\item Finite covariant parent:
\texttt{finite-covariant-collar-parent} must emit
\texttt{FINITE\_COVARIANT\_COLLAR\_PACKET\_PARENT\_RECEIPT}.  This is the
covariant source artifact required before physical stress and exchange-current
claims can be promoted.
\item Finite-collar Boltzmann source bundle:
\texttt{finite-collar-boltzmann-bundle} must emit the diagnostic source-bundle
receipt and, for physical promotion,
\texttt{PHYSICAL\_BOLTZMANN\_EXPORT\_CERTIFICATE}.
\item Boltzmann input bridge:
\texttt{oph-boltzmann-inputs} must expose the CDM-limit solver row and keep
diagnostic repair-exchange rows separate from physical inputs.
\item Frozen transfer and likelihood closure:
\texttt{frozen-transfer-likelihood} must certify source freeze, solver pins,
CDM-limit regression, Standard-Model-off controls, blinded setup, and official
likelihood execution before the dark branch can claim a likelihood-evaluated
physical prediction.
\end{enumerate}

The planner also records optional \texttt{cmb-anomaly-report} output.  That
diagnostic can guide anomaly studies.  The physical dark-matter promotion gate
uses it only with passing finite-parent, Boltzmann, and likelihood receipts.

\subsection{Correction Audit}

The comparison mostly tests normalization because the OPH static law uses the
same acceleration-family shape as the empirical RAR fit.  If \(\aoph\) is held
fixed, different targets imply different \(\lambdac\) values:

\begin{center}
\begin{tabular}{@{}lrrr@{}}
\toprule
Target & Required \(\lambdac\) & Reserve \(-\ln\lambdac\) & Ratio to \(P/24\) \\
\midrule
Best same-function RAR & \(0.958802256\) & \(0.042070424\) & \(0.619074\) \\
Binned RAR & \(0.936737944\) & \(0.065351711\) & \(0.961663\) \\
Common empirical \(a_0\) & \(0.926096769\) & \(0.076776547\) & \(1.129781\) \\
Fixed-M/L rotation & \(0.926654674\) & \(0.076174302\) & \(1.120919\) \\
OPH \(\Zsix\)/Poisson & \(0.934300639\) & \(0.067957009\) & \(1.000000\) \\
\bottomrule
\end{tabular}
\end{center}

This rules out several tempting shortcuts.  In the normalization-profiled
all-point objective, a generalized activation exponent near \(0.503420\)
appears.  With fixed \(\aoph\), direct RAR objectives give exponents near
\(0.516\) all-point and \(0.519\) weighted-bin.  These shifts are
objective-dependent, and flat deep-IR rotation requires \(0.5\).  Moving the
exponent would buy little and would damage the BTFR theorem.

Finite-thickness nonuniformity can raise \(\lambdac\) above \(\exp(-P/24)\),
which moves the coefficient toward the binned RAR value.  It cannot lower
\(\lambdac\) toward the common empirical or fixed-M/L values while the mean
reserve remains \(P/24\) and Poisson counting is retained.  An exact hit to
the common empirical acceleration would require about \(13\%\) more protected
inactive reserve than \(P/24\), or a different microscopic selector.  That
extra reserve needs an OPH theorem before use.

\section{Claim Boundaries}

\begin{longtable}{@{}p{0.30\textwidth}p{0.46\textwidth}p{0.16\textwidth}@{}}
\toprule
Pressure point & OPH route & Status \\
\midrule
\endhead
Unknown particle & Dark source is a carried modular/collar information-defect
stress. & Conditional source target. \\
Galaxy RAR and BTFR & Collar/cut activation gives the square-root transition
and Poisson activation law under independent-increment repair counting;
universal extension excluded by Cassini at \(19.22\sigma\). &
Conditional static theorem, old-settled-galaxy scope only. \\
Acceleration scale & Capacity scale gives \(\aoph\) from measured
\(H_0\)/\(\Lambda\) (SL-4/SL-5 inputs); \(\Zsix\)/Poisson reserve gives
\(\aeff\) close to the empirical scale, \(13\%\) short in reserve of an exact
hit. & Conditional coefficient theorem; in-loop consistency display. \\
Galaxy lensing & No-slip branch gives \(\Phi=\Psi\) if the information-defect
stress is dust on settled galaxies. & Conditional stress theorem. \\
Cluster offsets & Transported anomaly can lag collisional gas; the Jacobi
clock gives a no-fit scale under the tidal-mismatch premise. & Forward
likelihood contract. \\
CMB and growth & Flat capacity state selection gives a CDM-like homogeneous
residual; the closed branch has a conserved load current; environmental
kernels describe nonzero-field response. & Amplitude selector and real
Boltzmann likelihood are not emitted by this paper. \\
\bottomrule
\end{longtable}

The supported claim is:
\begin{quote}
OPH defines an imperfect-information correction to the recovered Einstein
branch.  Under explicit bridge premises, the static galaxy equation reproduces
the RAR/BTFR functional form from collar/cut repair statistics and yields an
acceleration scale close to SPARC as an in-loop consistency display, since
\(\aoph\) carries measured \(H_0\) and \(\Lambda\) as SL-4/SL-5 inputs.  The
unit branch is low in normalization.
The \(\Zsix\)/Poisson branch lands within \(1.748\%\) of the common empirical
acceleration reference.  Profiled stellar, distance, inclination, and gas
nuisances mildly favor the unit branch.  The Jacobi clock gives a no-fit
cluster-offset scale under its tidal-mismatch premise.  Flat capacity state
selection gives a Planck-like homogeneous information-defect residual, while
closed-branch transport gives a conserved load current.  Cluster and
CMB/growth likelihoods require measured cluster covariances, a finite-screen
amplitude selector, a finite covariant source parent, recipient stress and
exchange-current closure for any nonzero repair exchange, physical-clock
receipts for any promoted \(\Gamma_{\mathrm{rec}}\), and a frozen
Boltzmann/likelihood implementation.
\end{quote}

Claim outside this paper:
\begin{quote}
OPH has fully derived dark matter and solved MOND's cluster and CMB problems.
\end{quote}
That stronger statement requires SPARC publication likelihoods, cluster
likelihoods, a finite covariant parent for the cosmological source functions,
and frozen Boltzmann likelihoods.

\section{Proof Ledger}

\begin{center}
\begin{tabularx}{\textwidth}{@{}p{0.25\textwidth}Xp{0.22\textwidth}@{}}
\toprule
Target & OPH closure & Numerical state \\
\midrule
Galaxy source & Minimal scalar recoverability defect
\(R_C=I(A:D|B)\). & Conditional source target. \\
Quotient-edge locality & Scalar repair opportunities are edge-center
cut-register events on the physical quotient. & Conditional bridge. \\
Coherent material source lift & A nondegenerate OPH-coherent material source
\(S_{\mathrm{coh}}^{\mathrm{can}}\) descends to the quotient and is forced into
the same edge-center scalar channel by Scalar Edge-Center Exhaustion. &
Theorem-grade scalar-channel identity in the screen microphysics and
\(\chi_\nu\) papers; finite stress-parent, abundance, and Boltzmann gates are
separate obligations. \\
Finite channel bridge & One finite channel carries both the scalar-slot
record panel and the collar-slice reserve panel, so the source generator and
collar survival factor are composed on the same indexed family. &
Bookkeeping bridge; nature-instantiation and G9 numerical calibration remain
open physical obligations. \\
Finite thickness & Uniform product-thickening plus slice-wise
scalar-reserve unbiasedness licenses the exact coefficient; otherwise the
profile integral and, when scalar-weighted mean passes, Jensen band apply. &
Conditional imported theorem. \\
No-slip stress & Positive kinetic collar measure; settled monokinetic branch
has dust stress and vanishing information-sector anisotropic stress. &
Conditional stress theorem. \\
Repair relaxation & Fixed repair-commit chain gives
\(\tau_{\mathrm{rec}}=t_{\mathrm{commit}}/\gamma_{\log}\). &
Conditional packet theorem and clock candidate. \\
CMB and growth & Nonzero-environment kernel is explicit; exact FLRW static
RAR kernel is blocked by a no-go theorem. &
Finite-parent Boltzmann contract. \\
Abundance history & Flat capacity state selection gives a CDM-like residual;
the closed transported branch has a conserved load current and charge. &
Amplitude selector not emitted by this paper. \\
Linear transfer & The perturbation equation has a relaxation transfer
solution between CDM-like and tracking limits. & Requires evaluated
\(B_A(k,a)\), recipient stress and exchange-current closure for nonzero
exchange, physical-clock receipts for any promoted \(\Gamma_{\mathrm{rec}}\),
and frozen hashes. \\
Parent functional & The finite collar expectation of the positive repair
defect emits \(\rho_{A,\mathrm{eq}}\) and \(B_A\) if its FLRW limit is
regular. & Scalar source target, not full stress closure. \\
Repair matrix & A reversible Metropolis kernel on packet states gives a
concrete \(K\). & Conditional on declared packet schema. \\
Jacobi clock & The tidal scalar \((E_{ij}E^{ij}/6)^{1/4}\) gives a no-fit
dynamic repair scale under the Jacobi mismatch premise. & Conditional clock. \\
\bottomrule
\end{tabularx}
\end{center}

\subsection{Positive Galaxy Source}

\paragraph{Theorem target 0A.}
The scalar carried charge is fixed by the exact modular-defect identity, not by
a separate uniqueness principle.  For a faithful finite collar state
\(\omega_{ABD}\),
\[
  -\langle K_{ABD}-K_{AB}-K_{BD}+K_B\rangle_\omega
  =I_\omega(A:D|B).
\]
After reference subtraction on an exact Markov collar, this defines the
canonical carried modular charge \(M_C=I_\omega(A:D|B)\) in nats.  A
quotient-invariant collar allocation may sum these charges over a proper
small-ball cover only when it passes the source-localization saturation receipt
connecting the same carried operator to the finite-cutoff Einstein remainder.

\paragraph{Explicit premise.}
The galaxy-scale finite-stage modular nonadditivity is the carried modular
charge appearing in the fixed-cap small-ball remainder, with hidden carrier
duplicates, port relabelings, repair schedules, and refinement-equivalent
covers quotiented out.

\paragraph{Conditional argument.}
Conditional mutual information is nonnegative, so the source-localized carried
charge is nonnegative.  Equation~\eqref{eq:rhoA} then gives a nonnegative
rest-mass density after the source-localization receipt passes.  The scalar
charge alone does not determine \(T_A^{ab}\); packet factorization, causal
directions, allocation, rest frame, and transport law are required to lift it
to a stress tensor. \(\square\)

\paragraph{Proof obligation.}
Prove the operator-level source-localization relation between the finite-stage
small-ball modular remainder and the quotient-invariant collar charge, then
prove the positive packet allocation and covariant causal packet lift.

\paragraph{Failure consequence.}
Without source localization, \(I(A:D|B)\) is only a recoverability and
collar-diagnostic number.  Without the packet lift, it cannot support lensing,
CMB, growth, or conservation claims as a physical stress source.

\subsection{Quotient-Edge Scalar Opportunity}

\paragraph{Imported theorem.}
The fixed-cutoff uniqueness statement is discharged in the microphysics paper
by
\[
\mathsf{Scal}_{r,C}=\mathcal E_{r,C}
\]
on the edge-center scalar-completeness branch, and by the following
imports:
\[
\Pi^{\rm scal}_{r,C}\in\mathcal E_{r,C},
\qquad
Z_{6,r,C}\in\mathcal E_{r,C},
\qquad
[\Pi^{\rm scal}_{r,C},Z_{6,r,C}]=0.
\]
The relevant theorem labels in the microphysics paper are
\[
\texttt{thm:scalar-activation-edge-center},\quad
\texttt{thm:scalar-z6-same-register-commute},\quad
\texttt{thm:scalar-channel-exhaustion},\quad
\texttt{thm:no-separate-scalar-carrier},\quad
\texttt{thm:coherent-matter-same-channel-forcing},\quad
\texttt{thm:unique-scalar-linear-response}.
\]
For coherent material support the imported source is
\[
S_{\mathrm{coh}}^{\mathrm{can}}
=\mathbf 1_{\rm self-read}\,\mathsf R_U\,\mathsf P_U\,\mathsf C_U
\in\mathcal E_{r,C}
\]
on the nondegenerate branch. This import fixes the scalar channel used by the
\(\chi_\nu\) coefficient and does not supply a finite covariant dark-stress
parent.

\paragraph{Branch boundary.}
The import is conditional on the microphysics assumptions labeled
\texttt{ass:edge-center-scalar-completeness} and
\texttt{ass:scalar-activation-channel-completeness}. If either fails, then
scalar activation may require an additional quotient-visible scalar carrier,
and the \(\Zsix\) reserve cannot determine \(\lambdac\) without a new
co-registration theorem.

\subsection{Uniform Finite-Thickness Reserve}

\paragraph{Correct exact-value premise.}
The exact finite-thickness coefficient requires the uniform product-thickening
branch of the microphysics paper:
\[
\mathcal A^{\rm thick}_{r,C}
\cong
\mathcal E_{r,C}\otimes\mathcal T_r(Y),
\]
\[
\tau^{\rm thick}_{q,r,C}
=
\tau^{\mathcal E}_{q,r,C}\otimes\tau^Y_r,
\]
\[
Z^{\rm thick}_{6,r,C}=Z_{6,r,C}\otimes1_Y,
\]
and, essentially,
\[
\frac{
\tau^{\mathcal E}_{q,r,C}
\!\left(\Pi^{\rm scal}_{r,C}(y)Z_{6,r,C}\right)
}{
\tau^{\mathcal E}_{q,r,C}
\!\left(\Pi^{\rm scal}_{r,C}(y)\right)
}
=
\frac{P}{24}
\]
for every scalar-active transverse slice \(y\). Product trace alone is not
enough. The scalar-active sampler must be reserve-unbiased.

\paragraph{Imported theorem.}
With local Poisson reserve survival and the uniform product-thickening branch,
the microphysics theorem labeled
\texttt{thm:exact-uniform-product-thickening-coefficient} gives
\[
\lambdac=e^{-P/24}
=
0.9343006394893864\ldots .
\]
Without the uniform branch, the theorem-grade coefficient is
\[
\lambdac
=
\int \dd y\,w(y)e^{-\epsilon_{\Zsix}(y)}.
\]
If the scalar-weighted protected reserve mean is \(P/24\), Jensen gives only
\[
e^{-P/24}\le\lambdac\le1.
\]

\subsection{No-Slip Settled Stress}

\paragraph{Theorem target 0D.}
Let the information-defect stress be the second moment of a positive
finite-collar kinetic measure \(\dd\mathcal E_x(v)\) on the future unit
timelike shell:
\begin{equation}
  T_{\mathcal I}^{ab}=\int v^a v^b\,\dd\mathcal E_x(v).
\end{equation}
If the settled galaxy branch is monokinetic in its rest frame, then
\begin{equation}
  T_{\mathcal I}^{ab}
  =
  \rho_{\mathcal I}u_{\mathcal I}^a u_{\mathcal I}^b,
  \qquad
  P_{\mathcal I}=0,
  \qquad
  q_{\mathcal I}^a=0,
  \qquad
  \pi_{\mathcal I}^{ab}=0.
\end{equation}
For negligible or separately modeled anisotropic stress in all other sectors,
\(\Phi=\Psi\).

\paragraph{Explicit premise.}
The finite collar packet state emits the positive kinetic measure, and the
settled galaxy branch is monokinetic at the coarse scale used for lensing.

\paragraph{Conditional argument.}
A positive measure on future timelike velocities has a symmetric
future-positive second moment.  In the monokinetic branch the measure is
concentrated at one four-velocity, so the second moment is
\(\rho_{\mathcal I}u_{\mathcal I}^a u_{\mathcal I}^b\).  Its pressure, heat
flux, and anisotropic stress vanish in that rest frame.  The off-diagonal
spatial Einstein equation then gives \(\Phi=\Psi\) when the other sectors
carry no uncompensated anisotropic stress. \(\square\)

\paragraph{Proof obligation.}
Derive \(\dd\mathcal E_x(v)\) from the finite OPH collar packet state or from
an equivalent covariant parent action.

\paragraph{Failure consequence.}
If pressure or anisotropic stress survives coarse graining, the lensing slip
equation must include those terms and no-slip is regime-dependent.

\subsection{Repair Relaxation Scale}

\paragraph{Theorem 0E.}
Let \(K\) be the fixed-cutoff repair-commit transition matrix for one local
coarse cell at fixed baryonic source.  If \(K\) is finite, irreducible, and
aperiodic, with largest nonstationary eigenvalue \(r_\star\) in modulus, then
\begin{equation}
  \tau_{\mathrm{rec}}
  =\frac{t_{\mathrm{commit}}}{-\log |r_\star|}.
\end{equation}
If every allowed repair move has probability at least \(q_{\min}>0\) and the
comparison chain has conductance \(\Phi_K\), then
\begin{equation}
  1-|r_\star|\ge \frac12 q_{\min}\Phi_K^2.
\end{equation}

\paragraph{Proof.}
A finite irreducible aperiodic chain has a unique stationary state.  Every
nonstationary mode decays as \(|r_j|^n\) in repair-step time.  One physical
commit step takes \(t_{\mathrm{commit}}\), so physical relaxation has rate
\(-\log |r_\star|/t_{\mathrm{commit}}\).  The conductance bound follows
from the standard Cheeger comparison for the reversible comparison chain and
the lower move probability \(q_{\min}\). \(\square\)

\paragraph{Theorem 0E'.}
Equilibrium data do not select physical repair kinetics.  Let \(P\) be an
irreducible finite transition matrix with stationary law \(\pi P=\pi\).
For any \(0<\alpha\le1\), define
\[
  P_\alpha=(1-\alpha)I+\alpha P.
\]
Then \(\pi P_\alpha=\pi\).  If \(r_j\) is an eigenvalue of \(P\), the
corresponding eigenvalue of \(P_\alpha\) is
\[
  r_j(\alpha)=1-\alpha+\alpha r_j,
\]
and the physical decay rate at commit time \(\Delta t_{\mathrm{physical}}\) is
\[
  \Gamma_j(\alpha)
  =
  -\frac{\log |1-\alpha+\alpha r_j|}{\Delta t_{\mathrm{physical}}}.
\]
Thus the same equilibrium law, \(\rho_{A,\mathrm{eq}}\), \(B_A\), and detailed
balance can support different kinetics.  A sampler built from an equilibrium
functional is a valid equilibrium evaluator only after its proposal law,
attempt frequency, causal neighborhood, active fiber, and physical clock are
declared as part of the OPH repair generator. \(\square\)

\subsection{Environmental Kernel Around A Nonzero Field}

\paragraph{Conditional theorem 0F.}
Let the settled anomaly field be
\begin{equation}
  \mathbf g_A=(\nu_{\OPH}-1)\mathbf g_b.
\end{equation}
Linearize around a nonzero background field
\(\bar{\mathbf g}_b\).  With
\[
  x=|\bar{\mathbf g}_b|/\aoph,
  \qquad
  n_i=\bar g_{b,i}/|\bar{\mathbf g}_b|,
\]
the Fourier density response to a baryonic density mode is
\begin{equation}
  K_A^{(\rho)}(x,\mu)
  =
  \nu_{\OPH}(x)-1+x\nu_{\OPH}'(x)\mu^2,
\end{equation}
where \(\mu\) is the cosine between the mode direction and \(\mathbf n\).
The contrast kernel is
\begin{equation}
  B_A(k,a)
  =
  \frac{\bar\rho_b(a)}{\bar\rho_{A,\mathrm{eq}}(a)}K_A^{(\rho)}(k,a).
\end{equation}

\paragraph{Proof.}
The first variation is
\begin{equation}
  \delta g_{A,i}
  =
  \left(
    [\nu_{\OPH}(x)-1]\delta_{ij}
    +x\nu_{\OPH}'(x)n_i n_j
  \right)\delta g_{b,j}.
\end{equation}
Taking the divergence and using the Fourier-space Poisson relation for
\(\delta\mathbf g_b\) gives the displayed scalar multiplier.  The derivative
of
\[
  \nu_{\OPH}(x)=[1-\exp(-\lambdac\sqrt{x})]^{-1}
\]
is
\[
  \nu_{\OPH}'(x)
  =
  -\frac{\lambdac\exp[-\lambdac\sqrt{x}]}
  {2\sqrt{x}[1-\exp(-\lambdac\sqrt{x})]^2}.
\]
\(\square\)

\subsection{Background Abundance Green Function}

\paragraph{Theorem 0G.}
Let the background anomaly density obey
\begin{equation}
  \rho_A' + 3\mathcal H\rho_A
  = -a\Gamma_{\mathrm{rec}}(\rho_A-\rho_{A,\mathrm{eq}}).
\end{equation}
Define the comoving densities
\begin{equation}
  R_A=a^3\rho_A,
  \qquad
  R_{A,\mathrm{eq}}=a^3\rho_{A,\mathrm{eq}}.
\end{equation}
Then
\begin{equation}
  R_A(\eta)=
  W(\eta,\eta_i)R_A(\eta_i)
  +\int_{\eta_i}^{\eta}\dd\eta'\,
    W(\eta,\eta')a(\eta')\Gamma_{\mathrm{rec}}(\eta')
    R_{A,\mathrm{eq}}(\eta'),
\end{equation}
where
\begin{equation}
  W(\eta,\eta')
  =
  \exp\!\left[
    -\int_{\eta'}^{\eta}\dd\tilde\eta\,
      a(\tilde\eta)\Gamma_{\mathrm{rec}}(\tilde\eta)
  \right].
\end{equation}

\paragraph{Proof.}
Multiplying the background equation by \(a^3\) gives
\begin{equation}
  R_A'
  =
  -a\Gamma_{\mathrm{rec}}(R_A-R_{A,\mathrm{eq}}).
\end{equation}
This is a first-order linear equation.  Multiplication by the integrating
factor
\begin{equation}
  \exp\!\left[
    \int_{\eta_i}^{\eta}\dd\eta'\,
      a(\eta')\Gamma_{\mathrm{rec}}(\eta')
  \right]
\end{equation}
and integration gives the stated expression. \(\square\)

The theorem shows exactly where abundance information enters: the initial
comoving anomaly load, the equilibrium source, and the repair rate.  These are
OPH microphysical outputs, not SPARC parameters.

\subsection{Linear Relaxation Transfer}

\paragraph{Theorem 0H.}
For fixed \(k\), assume the no-slip anomaly perturbation equation
\begin{equation}
  \delta_A'
    =-\theta_A+3\Phi'
      -a\Gamma_{\mathrm{rec}}q_A
       (\delta_A-B_A\delta_b).
\end{equation}
Define
\begin{equation}
  \Xi_A=a\Gamma_{\mathrm{rec}}q_A.
\end{equation}
Then
\begin{equation}
\begin{aligned}
  \delta_A(\eta,k)
  &=W_A(\eta,\eta_i)\delta_A(\eta_i,k)\\
  &\quad
  +\int_{\eta_i}^{\eta}\dd\eta'\,
    W_A(\eta,\eta')
    \left[
      -\theta_A+3\Phi'
      +\Xi_A B_A\delta_b
    \right]_{\eta',k},
\end{aligned}
\end{equation}
with
\begin{equation}
  W_A(\eta,\eta')
  =
  \exp\!\left[
    -\int_{\eta'}^{\eta}\dd\tilde\eta\,\Xi_A(\tilde\eta,k)
  \right].
\end{equation}

\paragraph{Proof.}
Move the damping term to the left:
\begin{equation}
  \delta_A' + \Xi_A\delta_A
  =
  -\theta_A+3\Phi' + \Xi_A B_A\delta_b.
\end{equation}
The integrating-factor solution is the displayed expression. \(\square\)

This formula makes the two useful limits explicit.  If
\(\Xi_A/\mathcal H\ll1\), the anomaly evolves like pressureless free-falling
matter.  If \(\Xi_A/\mathcal H\gg1\), it tracks the OPH equilibrium source up
to derivative corrections.  Cluster offsets and settled galaxies require the
same relaxation operator to sit between those limits.

\subsection{Static-To-Linear Separation}

\paragraph{Theorem 0I.}
The nonlinear static RAR law
\begin{equation}
  g_{\mathrm{obs}}
  =
  \frac{g_b}{1-\exp[-\lambdac\sqrt{g_b/\aoph}]}
\end{equation}
does not define the FLRW anomaly abundance or the linear CMB kernel by itself.

\paragraph{Proof.}
The RAR law is written for a static weak-field acceleration vector sourced by a
resolved baryonic inhomogeneity.  An exactly homogeneous FLRW background has no
preferred spatial acceleration vector.  Its scalar data are background
densities and perturbation kernels, with no radial acceleration profile.  In
addition, the RAR map contains \(\sqrt{g_b}\), so its first derivative is
singular at \(g_b=0\) if treated as a homogeneous-background Taylor series.
Therefore the static law cannot be linearized into CMB equations without an
OPH parent functional.  A scalar parent functional must emit
\(\rho_A(a)\) and \(B_A(k,a)\), which belongs to the source-candidate layer.
Physical Boltzmann promotion requires the finite covariant packet parent above,
its source-provenance certificate, and pooled global reducers. \(\square\)

\subsection{Parent Collar Functional}

\paragraph{Scalar source target 0J.}
Let \(\mathcal C_x(a)\) be the finite collar family contributing to a coarse
FLRW cell \(x\) at scale factor \(a\).  Assume this finite-collar state
selection has a regular FLRW limit.  Let \(\omega[\rho_b]\) be the OPH collar
state selected by the baryonic source, and let \(R_C^{\mathrm{src}}\) be the
typed source routed by the source-route theorem:
\begin{equation}
  R_C^{\mathrm{src}}[\omega]
  =
  \begin{cases}
  \delta\langle K_C^{\mathrm{anom}}[\sigma]\rangle,
  & \texttt{FIXED\_REFERENCE\_MODULAR\_ENERGY},\\
  I_\omega(A:D|B),
  & \texttt{NONLINEAR\_CMI\_STRESS}\text{ with matching receipt}.
  \end{cases}
\end{equation}
Define
\begin{equation}
  \rho_{A,\mathrm{eq}}(x,a)c^2
  =
  \frac{15}{8\pi^2\ell(a)^4}
  \int_{\mathcal C_x(a)}\dd\mu_C\,
  R_C^{\mathrm{src}}[\omega[\rho_b]].
  \label{eq:parentcollar}
\end{equation}
Then \eqref{eq:parentcollar} is a scalar parent collar functional that emits a
background equilibrium source and a linear response operator:
\begin{equation}
  \bar\rho_{A,\mathrm{eq}}(a)=
  \rho_{A,\mathrm{eq}}[\bar\rho_b](a),
\end{equation}
\begin{equation}
  (K_{A,r}^{(\rho)})_{jj'}(a)=
  \left\langle
  v_{rj},
  \left.
  \frac{\delta\rho_{A,\mathrm{eq}}(x,a)}
       {\delta\rho_b(x',a)}
  \right|_{\bar\rho_b}
  v_{rj'}
  \right\rangle,
  \qquad
  (B_{A,r})_{jj'}(a)
  =\frac{\rho_b(a)}{\rho_{A,\mathrm{eq}}(a)}(K_{A,r}^{(\rho)})_{jj'}(a).
\end{equation}

\paragraph{Conditional argument.}
The collar measure, the conditional mutual information, and the selected
collar state are quotient-local scalar data.  The integral is therefore a
scalar density on the coarse FLRW cell.  Evaluating the functional on a
homogeneous baryonic density gives the background equilibrium source.  Taking
the first functional derivative around that homogeneous state gives a
translation-invariant and rotation-invariant linear response kernel.  Its
finite mode-basis matrix is \(K_{A,r}^{(\rho)}(a)\), and division by the equilibrium background density gives
\(B_{A,r}(a)\).  The scalar \(B_A(k,a)\) is the diagonal, mode-decoupled special case after the
commutator and off-diagonal leakage receipts pass. \(\square\)

The scalar reduction is accepted only on the physical projectors supplied by the scale bridge.  In
projector notation,
\[
  K_{A,r;IJ}^{(\rho)}(a)=P_{r,I}\mathcal K_{A,r}^{(\rho)}(a)P_{r,J},
  \qquad
  B_{A,r;IJ}(a)=
  \frac{\bar\rho_b(a)}{\bar\rho_{A,\mathrm{eq}}(a)}K_{A,r;IJ}^{(\rho)}(a).
\]
Reporting a scalar \(B_A(k,a)\) requires
\[
  \epsilon_{\mathrm{off}}(a)
  =
  \frac{
    \left(\sum_{I\ne J}|P_{r,I}\mathcal K_A P_{r,J}|^2\right)^{1/2}
  }{
    |\mathcal K_A|+\epsilon_0
  }
  \le \bar\epsilon_{\mathrm{off}}
\]
and, inside every degenerate projector,
\[
  P_{r,I}\mathcal K_A P_{r,I}=b_I(a)P_{r,I}+E_I,\qquad
  \frac{|E_I|}{|b_I|+\epsilon_0}\le\bar\epsilon_{\mathrm{iso}}.
\]
The evidence bundle records \(\texttt{mode\_basis\_hash}\),
\(\texttt{background\_hash}\), \(\texttt{clock\_hash}\), and
\(\texttt{scale\_bridge\_hash}\).  \(\rho_A(a)\), \(B_A(k,a)\), and
\(\Gamma_{\mathrm{rec}}(k,a)\) must share one frozen geometry and clock generation.  A transition
matrix eigenvalue per repair cycle is a diagnostic until a physical interval \(\Delta\tau_r\), an
active response block, and either a spectral-radius formula or a Lyapunov/semigroup bound are
certified.  A scalar \(B_A(k,a)\) fails when off-diagonal mode mixing exceeds its frozen tolerance
or when the result depends on unitary rotations inside a degenerate physical projector.

The finite-collar evaluation of \eqref{eq:parentcollar} is the mathematical
target for replacing a fitted dark-matter abundance, but it does not determine
the full fluid closure.  The scalar parent leaves open \(w_A\), \(c_{s,A}^2\),
\(\sigma_A\), \(Q_A^\mu\), exchange-current closure, a certified
\(\Gamma_{\mathrm{rec}}\), recipient stress, local-frame/quotient covariance,
gauge-invariant perturbations, and causal response.  Those data must come from
the finite covariant packet parent before the scalar tables can feed a physical
Boltzmann module.

\paragraph{Proof obligation.}
Evaluate the collar measure and selected state from finite OPH screen/collar
data in the homogeneous, perturbative, galaxy, and cluster regimes; lift the
result to a finite covariant packet parent; prove exact stress-energy closure,
gauge independence of \(B_{A,r}\), common mode-basis compatibility with the primordial source,
physical-time calibration for \(\Gamma_{\mathrm{rec}}\), recipient stress for nonzero exchange,
exchange-current closure, local-frame and carrier-quotient invariance,
causal/stable response, refinement convergence,
and CDM-limit recovery.

\subsection{Finite Repair Matrix}

\paragraph{Theorem 0K.}
Let \(\mathsf S\) be the finite packet-state space declared by one
fixed-cutoff overlap interface.  Let \(\pi_{\mathrm{eq}}(s|\rho_b)\) be the
equilibrium packet distribution emitted by the parent collar functional.  Let
\(q(s,s')\) be an inverse-closed local proposal rule generated by the declared
repair menu, with \(q(s,s')>0\) iff \(q(s',s)>0\).  Define, for \(s\ne s'\),
\begin{equation}
  K(s,s')
  =
  q(s,s')
  \min\!\left(
    1,
    \frac{\pi_{\mathrm{eq}}(s'|\rho_b)q(s',s)}
         {\pi_{\mathrm{eq}}(s|\rho_b)q(s,s')}
  \right),
\end{equation}
and
\begin{equation}
  K(s,s)=1-\sum_{s'\ne s}K(s,s').
\end{equation}
Then \(K\) is a finite stochastic repair transition matrix with stationary
distribution \(\pi_{\mathrm{eq}}\).  If the proposal graph is connected and
some rejection or hold probability is nonzero, \(K\) is irreducible and
aperiodic.

\paragraph{Proof.}
Each row sums to one by construction, so \(K\) is stochastic.  For
\(s\ne s'\), inverse-closed proposals make both directions available.  Hence
\begin{equation}
  \pi_{\mathrm{eq}}(s)K(s,s')
  =
  \min\!\left(
    \pi_{\mathrm{eq}}(s)q(s,s'),
    \pi_{\mathrm{eq}}(s')q(s',s)
  \right)
  =
  \pi_{\mathrm{eq}}(s')K(s',s).
\end{equation}
Detailed balance proves stationarity.  Connected proposal support gives
irreducibility, and a nonzero hold probability gives aperiodicity. \(\square\)

This construction declares \(K\) from OPH data: packet states, local proposals,
and the parent equilibrium distribution.

\paragraph{Scalar-load diagnostic.}
The executable packet diagnostic takes
\[
  \mathsf S=\{0,1,\ldots,40\},
  \qquad
  \pi_{\mathrm{eq}}(n)=
  \mathrm{Pois}\!\left(n;5.363470441\right)
\]
with truncation at \(40\), nearest-neighbor inverse-closed proposals, and
hold probability \(0.25\).  The resulting matrix has row-sum error
\(1.110\times10^{-16}\), detailed-balance error \(6.939\times10^{-18}\), and
\[
  \gamma_{\mathrm{repair\ step}}=0.050717471.
\]
This diagnostic is a finite packet schema.  The OPH task is to derive that
schema, or its replacement, from the finite collar states and then attach the
stress, recipient, response, convergence, and frozen-likelihood receipts needed
for physical transfer.

\subsection{Finite Repair-Graph Gap}

\paragraph{Theorem 0L.}
For a declared fixed-cutoff repair graph with transition matrix \(K\), the
relaxation time used by clusters and perturbations is computable from the
second eigenvalue.  If \(K\) is reversible with stationary distribution
\(\pi_{\mathrm{eq}}\), then
\begin{equation}
  r_\star=\max_{\lambda_j\ne 1}|\lambda_j(K)|,\qquad
  g_{\mathrm{abs}}=1-r_\star
\end{equation}
in discrete repair-step units.  If the commit interval is
\(\Delta t_{\mathrm{commit}}\), the exact physical e-folding rate is
\begin{equation}
  \Gamma_{\mathrm{phys}}
  =
  -\frac{\log r_\star}{\Delta t_{\mathrm{commit}}},
  \qquad
  \tau_{\mathrm{phys}}
  =
  \frac{\Delta t_{\mathrm{commit}}}{-\log r_\star}.
\end{equation}
The expression \(\Delta t_{\mathrm{commit}}/(1-r_\star)\) is only the
small-gap approximation.  For continuous-time generator \(L\), the rate is the
smallest positive eigenvalue of \(-L\) on the mean-zero subspace.  On a
nonequilibrium nonnormal branch, eigenvalues alone are not enough; the parent
must instead provide a Lyapunov, singular-value, or logarithmic-norm bound that
excludes transient amplification.

\paragraph{Proof.}
Reversibility makes \(K\) self-adjoint in
\(L^2(\pi_{\mathrm{eq}})\).  The stationary vector has eigenvalue one.  Every
mean-zero mode decomposes into eigenvectors and decays by its eigenvalue per
repair step.  The slowest decaying nonstationary mode is therefore the largest
nontrivial absolute eigenvalue \(r_\star\).  After \(n=t/\Delta t_{\mathrm{commit}}\)
commits, its amplitude is \(r_\star^n=\exp[-t(-\log r_\star)/\Delta t_{\mathrm{commit}}]\),
which gives the stated physical rate.  The continuous-time statement follows by
exponentiating the generator. \(\square\)

This is an exact finite-matrix target for the repair/commit microphysics.  A
cluster timescale is a prediction only after this matrix or its OPH state
functional is supplied.

\subsection{Jacobi Repair Clock}

\paragraph{Theorem target 0M.}
Assume repair timing is set by the overlap-visible Jacobi mismatch rate of
transported information-defect records.  Let \(E_{ij}=C_{0i0j}\) be the
electric Weyl tensor in the local free-fall frame, equivalently the trace-free
Newtonian tidal tensor in the weak-field limit.  Homogeneous FLRW Ricci
focusing is excluded from this local cluster-offset clock.  The scalar repair
rate is
\begin{equation}
  \Gamma_J
  =
  \left(\frac{E_{ij}E^{ij}}{6}\right)^{1/4}.
\end{equation}
For a Newtonian point source this gives
\begin{equation}
  \Gamma_J=\sqrt{\frac{GM}{r^3}},
  \qquad
  \tau_J=\sqrt{\frac{r^3}{GM}}.
\end{equation}

\paragraph{Explicit premise.}
The repair-cycle clock is controlled by overlap-visible geodesic-deviation
mismatch of transported information-defect records.

\paragraph{Conditional argument.}
The relative acceleration of neighboring transported records is controlled by
the Jacobi operator.  The local cluster-offset part is the trace-free Weyl
electric tensor \(E_{ij}\); the homogeneous FLRW Ricci term changes the
background expansion and is excluded from the local offset between collisional
gas and transported record stress.  A scalar clock made from \(E_{ij}\), with no
chosen direction and no extra dimensional constant, must be a power of
\(E_{ij}E^{ij}\).  The fourth root has units of inverse time.  For a point
Newtonian source the eigenvalues of \(E_{ij}\) are
\(-2GM/r^3,GM/r^3,GM/r^3\) up to sign convention, hence
\(E_{ij}E^{ij}=6(GM/r^3)^2\).  The normalization in the theorem makes the
point-source result exact. \(\square\)

\paragraph{Proof obligation.}
Derive from OPH packet microphysics that the commit clock is the
overlap-visible Weyl-Jacobi mismatch clock, while pixel, de Sitter,
entropy-production, local-acceleration, and Ricci-curvature clocks are
excluded.  The
self-consistent prediction evaluates \(E_{ij}\) from the total weak-field
potential determined by baryons plus information-defect stress.

\paragraph{Failure consequence.}
Without that derivation, \(\Gamma_J\) is a no-fit dynamic diagnostic rather
than a repair-clock theorem.

\paragraph{Static-clock boundary.}
The static equilibrium equation contains \(\rho_{A,\mathrm{eq}}\) but no
relaxation rate.  Replacing \(\Gamma_{\mathrm{rec}}\) by any positive function
leaves the same settled solution.  The Jacobi clock is therefore a dynamic
OPH premise and has no theorem claim inside the static RAR law.

\subsection{Homogeneous Anomaly State Selection}

\paragraph{Theorem target 0N.}
Under capacity-saturated FLRW state selection, the homogeneous closure relation is
\begin{equation}
  \Omega_{A0}+\Omega_{K0}
  =
  1-\Omega_{\Lambda,\OPH}
   -\Omega_{b0}-\Omega_{\nu0}-\Omega_{r0},
  \qquad
  \Omega_{\Lambda,\OPH}
  =
  \left(\frac{H_{\mathrm{dS}}}{H_0}\right)^2.
\end{equation}
If \(\Omega_{K0}=0\) is separately selected or explicitly assumed, this reduces to the flat
benchmark value for \(\Omega_{A0}\).  Otherwise it is only a sum rule.
If the homogeneous anomaly charge is transported as dust with no homogeneous
repair exchange, then
\begin{equation}
  \rho_A(a)=\rho_{A0}a^{-3}.
\end{equation}

\paragraph{Explicit premise.}
The homogeneous state is capacity-saturated.  The flat version additionally assumes or derives
\(\Omega_{K0}=0\).  A residual Friedmann constraint after \(H_0\), baryons, neutrinos, and radiation
are supplied does not by itself select either the curvature sector or the anomaly abundance.

\paragraph{Conditional argument.}
The flat Friedmann equation at \(a=1\) is
\begin{equation}
  1
  =
  \Omega_{\Lambda,\OPH}
  +\Omega_{b0}+\Omega_{\nu0}+\Omega_{r0}+\Omega_{A0}+\Omega_{K0}.
\end{equation}
Solving gives only \(\Omega_{A0}+\Omega_{K0}\).  Pressureless
homogeneous transport with zero homogeneous exchange obeys
\[
  \rho_A'+3\mathcal H\rho_A=0,
\]
whose solution is \(\rho_A(a)=\rho_{A0}a^{-3}\). \(\square\)

\paragraph{Proof obligation.}
Derive the conserved homogeneous information-defect charge \(Q_A\) by the
source-only anomaly abundance selector of
Section~\ref{sec:source-only-anomaly-abundance-selector} and supply an
independent curvature label, or declare the abundance as cosmological state
data.

\paragraph{Failure consequence.}
The CMB dark abundance is conditional when \(Q_A\) lacks
\texttt{RHO\_A\_SOURCE\_RECEIPT}.  A nonzero exchange branch is also
conditional unless the same finite parent exposes the recipient stress and
equal-and-opposite exchange current that balances the exchange.

\paragraph{Capacity boundary.}
The screen capacity fixes the dimensionless de Sitter capacity relation; the
capacity is the SL-4 estimate read from measured \(\Lambda\)
(\texttt{../docs/STRANGE\_LOOP\_PRINCIPLES.md}), and the
SI de Sitter scale additionally uses the selected OPH scale certificate.  After
\(H_0\) and that scale display are supplied, it fixes \(\Omega_{\Lambda,\OPH}\);
\(\Lambda\) itself is on no OPH output list.
It does not by itself fix the baryon density, the neutrino density, the radiation density, the
curvature sector, or a conserved homogeneous
anomaly charge.  A standalone OPH cosmology needs a theorem of the form
\[
  Q_A
  \equiv
  \mathcal E_{A,r}
  =
  F_{A,r}(Q^{\rm rel}_{A,r},\mu^{\rm rel}_{A,r},P_\star,N_{\rm CRC},
  \mathfrak R^{\rm rel}_{A,r},\mathcal P_r)
\]
or an explicitly declared state-selection premise such as a flat benchmark using
\eqref{eq:flatresidual}.

\subsection{Source-Only Anomaly Abundance Selector}
\label{sec:source-only-anomaly-abundance-selector}

\begin{definition}[C.52. Anomaly release state]
\label{def:anomaly-release-state}
An anomaly release state at regulator \(r\) is
\[
\mathfrak R^{\rm rel}_{A,r}
=
(
\Sigma^{\rm rel}_r,
n^a_r,
a_{\rm rel,r},
V_{{\rm com},r},
\Pi^{(0)}_r,
\mathfrak B^{\rm rel}_r,
h_{\rm rel},
\mathfrak L_{\rm no\,data}
).
\]
Here \(\Sigma^{\rm rel}_r\) is the finite release hypersurface; \(n^a_r\) is
its future unit normal in the parent tetrad; \(a_{\rm rel,r}\) is the release
scale factor; \(V_{{\rm com},r}\) is the declared comoving volume;
\(\Pi^{(0)}_r\) is the homogeneous FLRW zero-mode projector; and
\(\mathfrak B^{\rm rel}_r\) is the release-branch boundary and sector data,
including declared \(P_\star\), \(N_{\rm CRC}\), compact-gauge branch,
ordinary-sector branch, and exchange branch.  The hash \(h_{\rm rel}\) freezes
the generation.  The ledger \(\mathfrak L_{\rm no\,data}\) records the source
dependency graph.

The release state is source-admissible only if all of its fields are fixed
before CMB, BAO, supernova, weak-lensing, RSD, SPARC, cluster, and other
likelihood comparisons.
\end{definition}

\begin{definition}[C.53. Finite anomaly load observable]
\label{def:finite-anomaly-load-observable}
Let
\[
\mathcal P_r[X,g]
\]
be the finite covariant collar-packet parent, or its source-side pre-load parent
before total homogeneous amplitude selection.  For a quotient state
\(q\in Q^{\rm rel}_{A,r}\), define the local anomaly energy density on the
release hypersurface by
\[
\varepsilon_{A,r}(c;q):=T^{ab}_{A,r}(c;q)n_an_b .
\]
On the BW source route this readout has the form
\[
\varepsilon_{A,r}(c;q)
=
\frac{15\hbar c}{8\pi^2}
\frac{R^{\rm src}_{A,r}(c,n,\ell;q)}{\ell^4}
+
\Delta^{\rm BW}_{A,r}(c;q),
\]
where \(\Delta^{\rm BW}_{A,r}\) is the finite-ball, curvature, gradient,
localization, tomography, and variational/moment residual package required by
the finite parent receipt.

The finite anomaly load observable is
\[
\boxed{
\mathsf L_{A,r}(q)
:=
\Pi^{(0)}_r
\sum_{c\subset\Sigma^{\rm rel}_r(q)}
V^{\rm phys}_{c,r}(q)\,
\varepsilon_{A,r}(c;q).
}
\]
It has units of energy.  It is defined on the physical quotient.  Hidden
representatives are not valid selector inputs.

The abundance selector is circular and invalid if \(\mathsf L_{A,r}\) is
computed from a parent occupation field whose normalization was set by an
externally supplied \(\Omega_A\), \(\rho_{A0}\), Planck residual, SPARC fit,
cluster fit, Boltzmann residual, or likelihood comparison.
\end{definition}

\begin{definition}[C.54. Source-only anomaly abundance selector]
\label{def:source-only-anomaly-abundance-selector}
Let \(Q^{\rm rel}_{A,r}\) be the release quotient state space and let
\(\mu^{\rm rel}_{A,r}\) be the declared OPH release law on that quotient.  The
source-only anomaly abundance selector is the deterministic functional
\[
\boxed{
F_{A,r}
(
Q^{\rm rel}_{A,r},
\mu^{\rm rel}_{A,r},
P_\star,
N_{\rm CRC},
\mathfrak R^{\rm rel}_{A,r},
\mathcal P_r
)
:=
\mathbb E_{\mu^{\rm rel}_{A,r}}
[
\mathsf L_{A,r}
].
}
\]
Equivalently,
\[
\boxed{
\mathcal E_{A,r}
=
\sum_{q\in Q^{\rm rel}_{A,r}}
\mu^{\rm rel}_{A,r}(q)\,
\mathsf L_{A,r}(q).
}
\]
The emitted homogeneous anomaly density is
\[
\boxed{
\bar\rho_{A,r}(a)
=
\frac{\mathcal E_{A,r}}{a^3V_{{\rm com},r}}
}
\]
on the conserved dust branch.
\end{definition}

\begin{definition}[C.55. Source MaxEnt release law]
\label{def:source-maxent-release-law}
The release law \(\mu^{\rm rel}_{A,r}\) is source-admissible if it is either
\[
\mu^{\rm rel}_{A,r}=\mu_r\vert_{Q^{\rm rel}_{A,r}}
\]
renormalized on the release branch, where \(\mu_r\) is a certified OPH quotient
law, or the finite MaxEnt law
\[
\mu^{\rm rel}_{A,r}(q)
=
\frac{
m^{\rm rel}_{A,r}(q)
\exp[-S^{\rm rel}_{A,r}(q)-\sum_j\theta_jF^{\rm rel}_{j,r}(q)]
}{
Z^{\rm rel}_{A,r}
}
\]
on \(Q^{\rm rel}_{A,r}\), where every constraint \(F^{\rm rel}_{j,r}\), target
\(c_{j,r}\), unit, support, zero-mode treatment, sector convention, and
refinement map is declared in the source constraint ledger.

No simulator output, Boltzmann residual, likelihood value, observational target,
or tuned visual diagnostic may appear in \(m^{\rm rel}_{A,r}\),
\(S^{\rm rel}_{A,r}\), \(F^{\rm rel}_{j,r}\), \(c_{j,r}\), or the
branch-selection ledger.
\end{definition}

\begin{theorem}[C.56. Source-only anomaly abundance selection]
\label{thm:source-only-anomaly-abundance-selection}
Assume:
\begin{enumerate}
\item \(Q^{\rm rel}_{A,r}\), \(\mu^{\rm rel}_{A,r}\), \(P_\star\),
\(N_{\rm CRC}\), \(\mathfrak R^{\rm rel}_{A,r}\), and \(\mathcal P_r\) are
source-only artifacts.
\item \(\mathsf L_{A,r}\) factors through the physical quotient.
\item The local BW/source route, tomography, finite parent, stress closure,
gauge, and refinement receipts required by the parent pass.
\item \(\mu^{\rm rel}_{A,r}\) is a certified OPH quotient law or a source
MaxEnt law.
\item The no-data-use ledger excludes all observational likelihoods and all
diagnostic solver outputs used to evaluate the prediction.
\end{enumerate}
Then
\[
\mathcal E_{A,r}
=
F_{A,r}
(
Q^{\rm rel}_{A,r},
\mu^{\rm rel}_{A,r},
P_\star,
N_{\rm CRC},
\mathfrak R^{\rm rel}_{A,r},
\mathcal P_r
)
\]
is a source-only OPH anomaly abundance artifact.  If the conserved dust branch
holds, then
\[
\bar\rho_{A,r}(a)
=
\frac{\mathcal E_{A,r}}{a^3V_{{\rm com},r}}
\]
is a source-only homogeneous anomaly density.
\end{theorem}

\begin{proof}
The load observable \(\mathsf L_{A,r}\) is constructed from the parent-emitted
anomaly stress or from the BW-normalized source route followed by stress
tomography.  By assumption it factors through \(Q^{\rm rel}_{A,r}\), so hidden
carrier coordinates, port labels, repair schedules, gauge representatives, and
worker metadata do not change it.

The release law \(\mu^{\rm rel}_{A,r}\) is either a certified OPH quotient law
or the finite MaxEnt law determined by source constraints.  Hence the
expectation
\[
\mathbb E_{\mu^{\rm rel}_{A,r}}[\mathsf L_{A,r}]
\]
is a deterministic finite functional of source artifacts.

No observational likelihood or diagnostic solver output enters the source DAG
by assumption.  Therefore the artifact is source-only.  On the conserved dust
branch, the background parent equation gives
\[
(a^3\bar\rho_A V_{\rm com})'=0,
\]
so the selected release load transports as
\[
\bar\rho_A(a)=\mathcal E_{A,r}/(a^3V_{\rm com}).
\]
\end{proof}

\begin{theorem}[C.57. No-data-use proof for \(F_{A,r}\)]
\label{thm:abundance-selector-no-data-use}
Let \(G_A^{\rm load}\) be the source DAG whose terminal node is
\(\mathcal E_{A,r}\).  Suppose every node verifier recomputes its predicate
from committed artifacts, theorem witnesses, parent predicates, dependency
manifests, and error envelopes, and suppose every root node is one of
\[
Q^{\rm rel}_{A,r},\quad
m^{\rm rel}_{A,r},\quad
S^{\rm rel}_{A,r},\quad
F^{\rm rel}_{j,r},\quad
c_{j,r},\quad
P_\star,\quad
N_{\rm CRC},\quad
\mathfrak R^{\rm rel}_{A,r},\quad
\mathcal P_r
\]
or a standard non-CMB physical constant allowed by the cosmology contract.

If the dependency ledger contains no CMB, BAO, supernova, weak-lensing, RSD,
SPARC, cluster, likelihood, posterior, nuisance-fit, simulator residual, or
diagnostic visual-comparison input, then
\[
\texttt{ANOMALY\_ABUNDANCE\_SOURCE\_RECEIPT}
\]
passes.
\end{theorem}

\begin{proof}
Topologically order \(G_A^{\rm load}\).  Root nodes are source-only by
hypothesis.  For a non-root node, the verifier accepts only if every parent has
passed and the node value is recomputed from its declared parents and theorem
witness.  Induction over the DAG proves that the terminal value
\(\mathcal E_{A,r}\) is a deterministic function of source-only inputs.  Since
the ledger excludes every observational or likelihood target used for
evaluation, no target-leakage path exists.  A producer Boolean is not a proof
because it is not a recomputation from the committed artifacts.
\end{proof}

\begin{theorem}[C.58. Exact refinement compatibility of the abundance selector]
\label{thm:abundance-selector-exact-refinement}
Let \(s\succeq r\) and let
\[
c_{sr}:Q^{\rm rel}_{A,s}\to Q^{\rm rel}_{A,r}
\]
be the physical coarse map.  Suppose:
\begin{enumerate}
\item the release laws are exactly compatible:
\[
(c_{sr})_\#\mu^{\rm rel}_{A,s}
=
\mu^{\rm rel}_{A,r};
\]
\item the load observable is exactly natural:
\[
\mathsf L_{A,s}(q_s)
=
\mathsf L_{A,r}(c_{sr}q_s)
\qquad
\forall q_s\in Q^{\rm rel}_{A,s};
\]
\item the release volume and homogeneous projector commute with refinement.
\end{enumerate}
Then
\[
\boxed{
\mathcal E_{A,s}
=
\mathcal E_{A,r}.
}
\]
\end{theorem}

\begin{proof}
By definition,
\[
\mathcal E_{A,s}
=
\sum_{q_s}
\mu^{\rm rel}_{A,s}(q_s)\mathsf L_{A,s}(q_s).
\]
Using load naturality,
\[
\mathcal E_{A,s}
=
\sum_{q_s}
\mu^{\rm rel}_{A,s}(q_s)\mathsf L_{A,r}(c_{sr}q_s).
\]
Push the fine law forward along \(c_{sr}\).  Exact law compatibility gives
\[
\sum_{q_s:c_{sr}q_s=q_r}\mu^{\rm rel}_{A,s}(q_s)
=
\mu^{\rm rel}_{A,r}(q_r).
\]
Therefore
\[
\mathcal E_{A,s}
=
\sum_{q_r}
\mu^{\rm rel}_{A,r}(q_r)\mathsf L_{A,r}(q_r)
=
\mathcal E_{A,r}.
\]
\end{proof}

\begin{theorem}[C.59. Approximate refinement bound for the abundance selector]
\label{thm:abundance-selector-approx-refinement}
Let \(s\succeq r\).  Suppose
\[
\left\|(c_{sr})_\#\mu^{\rm rel}_{A,s}
-
\mu^{\rm rel}_{A,r}
\right\|_{\rm TV}
\le
\delta^\mu_{sr},
\]
and
\[
\sup_{q_s}
\left|
\mathsf L_{A,s}(q_s)
-
\mathsf L_{A,r}(c_{sr}q_s)
\right|
\le
\delta^L_{sr}.
\]
Let
\[
L_{\max,r}:=\|\mathsf L_{A,r}\|_\infty.
\]
Then
\[
\boxed{
|\mathcal E_{A,s}-\mathcal E_{A,r}|
\le
\delta^L_{sr}
+
2L_{\max,r}\delta^\mu_{sr}.
}
\]
For a refinement chain \(r=r_0\preceq r_1\preceq\cdots\preceq r_n=s\),
\[
|\mathcal E_{A,s}-\mathcal E_{A,r}|
\le
\sum_{k=0}^{n-1}
\left(
\delta^L_{r_{k+1}r_k}
+
2L_{\max,r_k}\delta^\mu_{r_{k+1}r_k}
\right).
\]
If the right-hand side tends to zero along a cofinal family, the selected
anomaly load has a regulator-independent limit.
\end{theorem}

\begin{proof}
Insert and subtract the coarse load pulled back to the fine law:
\[
\begin{aligned}
|\mathcal E_{A,s}-\mathcal E_{A,r}|
&\le
\left|
\mathbb E_{\mu_s}[
\mathsf L_{A,s}
-
\mathsf L_{A,r}\circ c_{sr}
]
\right|
\\
&\quad+
\left|
\mathbb E_{\mu_s}[\mathsf L_{A,r}\circ c_{sr}]
-
\mathbb E_{\mu_r}[\mathsf L_{A,r}]
\right|.
\end{aligned}
\]
The first term is at most \(\delta^L_{sr}\).  The second term is bounded by the
total-variation estimate
\[
2\|\mathsf L_{A,r}\|_\infty\delta^\mu_{sr}.
\]
Summing the one-step bounds gives the chain estimate.  Cofinal convergence
follows immediately.
\end{proof}

\begin{theorem}[C.60. Source-only \(\rho_A\) promotion]
\label{thm:source-only-rhoA-promotion}
The receipt
\[
\texttt{RHO\_A\_SOURCE\_RECEIPT}
\]
passes iff
\[
\texttt{RHO\_A\_TRANSPORT\_RECEIPT}
\wedge
\texttt{ANOMALY\_ABUNDANCE\_SOURCE\_RECEIPT}
\]
passes under the same frozen generation, unit ledger, release state, and parent
generation.  When this receipt passes, \(\bar\rho_A(a)\) may be labelled
\[
\texttt{SOURCE\_ONLY\_ANOMALY\_ABUNDANCE}.
\]
If only the transport receipt passes, the label is
\[
\texttt{PHYSICAL\_PARENT\_WITH\_CONDITIONAL\_ABUNDANCE}.
\]
\end{theorem}

\begin{proof}
The transport receipt proves that the finite parent evolves a homogeneous
anomaly load consistently once that load is supplied.  The abundance source
receipt proves that the load itself is selected by the OPH source functional
\(F_{A,r}\), without target leakage and with refinement compatibility.  Their
conjunction is exactly the statement that \(\rho_A\) is both physically
transported and source-selected.  Without the selector, the amplitude is
external state data.
\end{proof}

The closed paper-side abundance receipt is
\[
\begin{aligned}
\texttt{ANOMALY\_ABUNDANCE\_SOURCE\_RECEIPT}
= {}&
\texttt{ANOMALY\_RELEASE\_STATE\_RECEIPT}
\wedge
\texttt{ANOMALY\_LOAD\_OBSERVABLE\_RECEIPT}
\\
&\wedge
\texttt{SOURCE\_MAXENT\_RELEASE\_LAW\_RECEIPT}
\wedge
\texttt{LOAD\_QUOTIENT\_INVARIANCE\_RECEIPT}
\\
&\wedge
\texttt{LOAD\_NO\_CIRCULARITY\_RECEIPT}
\wedge
\texttt{LOAD\_NO\_DATA\_USE\_RECEIPT}
\\
&\wedge
\texttt{LOAD\_REFINEMENT\_COMPATIBILITY\_RECEIPT}.
\end{aligned}
\]
Then
\[
\texttt{RHO\_A\_SOURCE\_RECEIPT}
=
\texttt{RHO\_A\_TRANSPORT\_RECEIPT}
\wedge
\texttt{ANOMALY\_ABUNDANCE\_SOURCE\_RECEIPT}.
\]
The source-ready dark Boltzmann handoff is
\[
\begin{aligned}
\texttt{DARK\_PHYSICAL\_BOLTZMANN\_SOURCE\_RECEIPT}
= {}&
\texttt{FINITE\_COVARIANT\_PARENT\_RECEIPT\_V2}
\wedge
\texttt{PHYSICAL\_ANOMALY\_KERNEL\_RECEIPT\_V2}
\\
&\wedge
\texttt{RHO\_A\_TRANSPORT\_RECEIPT}
\wedge
\texttt{FROZEN\_GENERATION\_MANIFEST\_RECEIPT}
\\
&\wedge
\texttt{BOLTZMANN\_INITIAL\_CONSTRAINT\_RECEIPT}
\wedge
\texttt{BOLTZMANN\_ADAPTER\_WELLPOSEDNESS\_RECEIPT}
\\
&\wedge
\texttt{CDM\_LIMIT\_RECOVERY\_RECEIPT}.
\end{aligned}
\]
For a source-only dark abundance claim,
\[
\texttt{SOURCE\_ONLY\_ANOMALY\_ABUNDANCE}
\Longleftrightarrow
\texttt{RHO\_A\_SOURCE\_RECEIPT}.
\]

Equivalently, the selector computes
\[
\boxed{
F_{A,r}
=
\mathbb E_{\mu^{\rm rel}_{A,r}}
\left[
\Pi^{(0)}_r
\sum_{c\subset\Sigma^{\rm rel}_r}
V^{\rm phys}_{c,r}\,
T^{ab}_{A,r}(c)n_an_b
\right].
}
\]
On the BW source branch,
\[
\boxed{
F_{A,r}
=
\mathbb E_{\mu^{\rm rel}_{A,r}}
\left[
\Pi^{(0)}_r
\sum_{c\subset\Sigma^{\rm rel}_r}
V^{\rm phys}_{c,r}
\left(
\frac{15\hbar c}{8\pi^2}
\frac{R^{\rm src}_{A,r}(c,n,\ell)}{\ell^4}
+
\Delta^{\rm BW}_{A,r}(c)
\right)
\right].
}
\]
The selector integrates the finite source stress over the release hypersurface
and averages it over the declared source quotient ensemble.  It does not read a
Friedmann residual, a Planck fit, a SPARC fit, a cluster fit, or a Boltzmann
likelihood.

\section{Falsifiers}

The OPH dark branch fails if any of the following happens:
\begin{enumerate}
\item OPH collar/cut microphysics cannot derive the activation law
\(p(x)=1-\exp[-\lambdac\sqrt{x}]\), or a replacement law that passes the same
galaxy tests.
\item The carried galaxy defect is not positive or not attractive.
\item The settled anomaly stress cannot give \(\Phi=\Psi\).
\item A full SPARC likelihood rejects both the unit branch and every
independently derived coefficient branch under the same nuisance treatment used
for comparison models.
\item Cluster lensing offsets require a relaxation law incompatible with old
settled-galaxy RAR.
\item CMB peaks, CMB lensing, BAO, weak lensing, or growth reject every frozen
finite covariant parent whose certified \(\Gamma_{\mathrm{rec}}\), \(B_A(k,a)\),
\(\rho_A(a)\), stress closure, recipient/exchange-current channel, physical
clock, and CDM-limit recovery are compatible with the galaxy branch.
\end{enumerate}

\section{Reproducibility}

The numerical tables were produced in the OPH cosmology workspace by:
\begin{verbatim}
python3 code/dark_matter/scripts/dark_sector_measurement_ledger.py
python3 code/dark_matter/scripts/dark_empirical_scorecard.py --quiet
python3 code/dark_matter/scripts/sparc_systematic_likelihood.py
python3 code/dark_matter/scripts/dark_perturbation_parameters.py
python3 code/dark_matter/scripts/dark_repair_transition_matrix.py
python3 code/dark_matter/scripts/dark_cluster_boltzmann_prelikelihood.py
python3 code/dark_matter/scripts/dark_jacobi_repair_clock.py
python3 code/dark_matter/scripts/dark_homogeneous_state_selection.py
python3 code/dark_matter/scripts/dark_parent_collar_grid.py --diagnostic-scalar-load \
  --mu-eq 5.363470440729118 \
  --out code/dark_matter/outputs/dark_parent_flat_capacity_state_selection.json
python3 code/dark_matter/scripts/dark_cmb_bao_growth_s8_likelihood.py \
  --parent-grid code/dark_matter/outputs/dark_parent_flat_capacity_state_selection.json
python3 code/dark_matter/scripts/camb_fixed_neutrino_compare.py
python3 -m oph_fpe.cli dark-sector-simulation-plan --run-dir runs/<run_id> \
  --out runs/<run_id>/dark_sector_simulation_plan
\end{verbatim}
The SPARC data files used are public measurement tables from the SPARC page
\cite{sparcpage}.

\begin{thebibliography}{99}

\bibitem{ophcompact}
B. Mueller, A. Osika, M. Poneder, K. Xue, P. Nguyen, M. A. Visser, and D. Matscheko,
\emph{Recovering Relativity and the Standard Model from Observer Overlap Consistency},
OPH compact paper, GitHub main PDF.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.pdf}

\bibitem{ophsynthesis}
B. Mueller, A. Osika, M. Poneder, K. Xue, B. Cassie, P. Nguyen, M. A. Visser, K. A. Anirudha, D. Matscheko, and J. Hill,
\emph{Observers Are All You Need}, OPH synthesis paper, GitHub main PDF.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/observers_are_all_you_need.pdf}

\bibitem{ophmicro}
B. Mueller, A. Osika, K. Xue, B. Cassie, M. A. Visser, and D. Matscheko,
\emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer Synchronization in OPH},
OPH microphysics paper, GitHub main PDF.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/screen_microphysics_and_observer_synchronization.pdf}

\bibitem{ophparticles}
B. Mueller, A. Osika, M. Poneder, K. Xue, M. A. Visser, and D. Matscheko,
\emph{Deriving the Particle Zoo from Observer Consistency},
OPH particle paper, GitHub main PDF.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/deriving_the_particle_zoo_from_observer_consistency.pdf}

\bibitem{planck2018}
Planck Collaboration,
\emph{Planck 2018 results. VI. Cosmological parameters},
arXiv:1807.06209.
\url{https://arxiv.org/abs/1807.06209}

\bibitem{lelli2016}
F. Lelli, S. S. McGaugh, and J. M. Schombert,
\emph{SPARC: Mass Models for 175 Disk Galaxies with Spitzer Photometry and Accurate Rotation Curves},
Astron. J. 152, 157, 2016, arXiv:1606.09251.
\url{https://arxiv.org/abs/1606.09251}

\bibitem{sparcpage}
F. Lelli, S. S. McGaugh, and J. M. Schombert,
SPARC public data page.
\url{https://astroweb.cwru.edu/SPARC/}

\bibitem{mcgaugh2016}
S. S. McGaugh, F. Lelli, and J. M. Schombert,
\emph{The Radial Acceleration Relation in Rotationally Supported Galaxies},
Phys. Rev. Lett. 117, 201101, 2016, arXiv:1609.05917.
\url{https://arxiv.org/abs/1609.05917}

\bibitem{lelli2019}
F. Lelli, S. S. McGaugh, and J. M. Schombert,
\emph{The Small Scatter of the Baryonic Tully--Fisher Relation},
Mon. Not. R. Astron. Soc. 484, 3267--3278, 2019, arXiv:1901.05966.
\url{https://arxiv.org/abs/1901.05966}

\bibitem{desmond2023}
H. Desmond,
\emph{The underlying radial acceleration relation},
Mon. Not. R. Astron. Soc. 526, 3342--3356, 2023, arXiv:2303.11314.
\url{https://arxiv.org/abs/2303.11314}

\bibitem{park2026}
R. S. Park et al.,
\emph{Cassini spacecraft navigation data constrain modified gravity in the Solar System},
2026, arXiv:2602.17884.
\url{https://arxiv.org/abs/2602.17884}

\bibitem{gaia2021}
Gaia Collaboration,
\emph{Gaia Early Data Release 3: Acceleration of the Solar System from Gaia astrometry},
Astron. Astrophys. 649, A9, 2021, arXiv:2012.02036.
\url{https://arxiv.org/abs/2012.02036}

\bibitem{li2018}
P. Li, F. Lelli, S. S. McGaugh, and J. M. Schombert,
\emph{Fitting the radial acceleration relation to individual SPARC galaxies},
Astron. Astrophys. 615, A3, 2018, arXiv:1803.00022.
\url{https://arxiv.org/abs/1803.00022}

\bibitem{milgrom1983}
M. Milgrom,
\emph{A modification of the Newtonian dynamics as a possible alternative to the hidden mass hypothesis},
Astrophys. J. 270, 365, 1983.
\url{https://ui.adsabs.harvard.edu/abs/1983ApJ...270..365M/abstract}

\bibitem{bekenstein2004}
J. D. Bekenstein,
\emph{Relativistic gravitation theory for the modified Newtonian dynamics paradigm},
Phys. Rev. D 70, 083509, 2004.
\url{https://doi.org/10.1103/PhysRevD.70.083509}

\bibitem{clowe2006}
D. Clowe, M. Bradac, A. H. Gonzalez, M. Markevitch, S. W. Randall,
C. Jones, and D. Zaritsky,
\emph{A direct empirical proof of the existence of dark matter},
Astrophys. J. Lett. 648, L109, 2006, arXiv:astro-ph/0608407.
\url{https://arxiv.org/abs/astro-ph/0608407}

\end{thebibliography}

\end{document}
