\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,array,longtable}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xurl}

\IfFileExists{../paper/release_info.tex}{
  \input{../paper/release_info.tex}
}{
  \newcommand{\OPHPaperReleaseDate}{\today}
  \newcommand{\OPHPaperReleaseBanner}{Draft}
  \newcommand{\OPHPaperReleaseID}{local-cosmology-staging}
}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.08}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{target}[theorem]{Target}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\theoremstyle{plain}

\newcommand{\OPH}{\mathrm{OPH}}
\newcommand{\Conf}{\mathrm{Conf}}
\newcommand{\LCDM}{\Lambda\mathrm{CDM}}
\newcommand{\Zsix}{\mathbb Z_6}
\newcommand{\dd}{\,\mathrm d}
\newcommand{\rhoA}{\bar\rho_A}
\newcommand{\GammaRec}{\Gamma_{\rm rec}}
\newcommand{\Azeta}{A_\zeta}
\newcommand{\Bkernel}{B_A}
\newcommand{\NCRC}{N_{\rm CRC}}
\newcommand{\rhoAeq}{\bar\rho_{A,\mathrm{eq}}}
\newcommand{\csA}{c_{s,A}^2}
\newcommand{\sigmaA}{\sigma_A}
\newcommand{\QA}{Q_A^\mu}
\newcommand{\pathref}[1]{\nolinkurl{#1}}
\newcommand{\SimSourceRepo}{\url{https://github.com/muellerberndt/oph-physics-sim}}
\newcommand{\SimSourceCommit}{\texttt{aeea9e502491a277b5e21a80bb89df6d089a074d}}
\newcommand{\SimSourceCommitURL}{\url{https://github.com/muellerberndt/oph-physics-sim/commit/aeea9e502491a277b5e21a80bb89df6d089a074d}}

\title{OPH Cosmology as a Finite-Source Prediction Program:\\
Observer-Screen Synchronization, Dark Stress, and the Physical CMB Gate}
\author{B.\ M\"uller}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{abstract}
OPH cosmology assigns the jobs usually given to inflation to finite
observer-screen synchronization. Flatness comes from the selected spatial
branch, horizon coherence from shared boundary repair, the near scale-invariant
pattern from screen geometry and source release, and acoustic peaks from
ordinary Boltzmann transfer.

Simulator runs give useful CMB-shaped diagnostics. A physical CMB prediction
needs source data fixed before comparison, a physical scale bridge, a covariant
dark-stress parent, Boltzmann transfer, and a frozen likelihood comparison.
\end{abstract}

\section*{What This Paper Contributes}

The OPH core papers recover local observer-facing geometry, records, modular flow, gauge/matter
structure, and finite screen microphysics. The cosmology work asks a different question: which
large-scale data can be predicted once the finite observer-screen state is released into an
Einstein-Boltzmann cosmology?

The program paper has four jobs.
\begin{enumerate}[leftmargin=2em]
\item It states the inflation-free OPH cosmology branch as a technical companion outside the
release bundle.
\item It separates diagnostic simulator outputs from physical predictions. A good visual or
measurement-facing CMB overlay is not a physical CMB prediction unless its inputs are source-only
finite OPH artifacts fixed before likelihood comparison.
\item It names the finite objects required for physical promotion of simulation outputs in CMB,
vacuum, or cosmological uses of the dark sector: source provenance, physical mode calibration,
freezeout, covariant stress, anomaly kernels, transfer, likelihood, and quotient ensemble receipts.
The dark-sector derivations themselves are owned by the released cosmology paper
\pathref{cosmology/oph_dark_matter_paper.tex}.
\item It gives the conditional cosmology branch one theorem surface for the finite-source and likelihood
claim gates.
\end{enumerate}

\tableofcontents
\newpage

\section{Claim Boundary}

This technical companion sits outside the release bundle and sets the shared
cosmology contract for paper and simulator work.

The branch claim is:
\[
\boxed{
\begin{gathered}
\text{OPH can replace the logical jobs of inflation on a finite-source branch:}\\
\text{flatness by direct/CMH spatial-holonomy selection, horizon coherence by same-boundary repair,}\\
\text{near scale invariance by the geometric screen spectrum, hot initial data by MaxEnt release,}\\
\text{and acoustic peaks by Boltzmann transfer from source-only OPH artifacts.}
\end{gathered}}
\]

Here ``can'' means ``can on the declared finite-source branch with the listed
source, stress, lift, transfer, and likelihood gates closed.'' The recovered
Phase I SM/GR core excludes inflation replacement, CMB spectra, and dark-sector
cosmology.

The branch supplies claim boundaries and measurement-facing diagnostic evidence.
Physical CMB prediction, completed Planck/ACT likelihood runs, OPH-native
quantum vacuum, full cosmological dark-matter likelihood, and production
particle-formation simulation require the gates below.

\begin{remark}[No simulator shortcut]
The paper-side theorem gates mark the difference between a simulation that
resembles CMB data and a prediction whose input artifacts were fixed without
using CMB data. Physical CMB promotion requires those gates as mathematical
statements and deterministic checks.
\end{remark}

\section{Finite Quotient Ensembles and Claim Tiers}

\input{../paper/tex_fragments/FINITE_QUOTIENT_ENSEMBLE_THEOREMS.tex}

\input{../paper/tex_fragments/SCREEN_SPECTRUM_THEOREMS.tex}

\input{../paper/tex_fragments/PHYSICAL_SCALE_BRIDGE_THEOREMS.tex}

\section{Compatibility With the Core Stack}

The compatibility table fixes how the inflation-free draft is read against the core papers.

\begin{longtable}{@{}p{0.28\textwidth}p{0.62\textwidth}@{}}
\toprule
Imported draft idea & Core-compatible reading\\
\midrule
\endhead
\bottomrule
\endfoot
Inflation-free replacement &
Phase III conditional branch. The compact paper's recovered core covers the
SM/GR package; inflation replacement, physical CMB likelihood, the \(H_0/S_8\)
branch, and dark-sector cosmology sit outside that core.\\
Finite normal form &
Use quotient-level fixed-cutoff normal forms on the declared branch, unique only modulo boundary
redundancy, implementation hiding, inert ancillary stabilization, and any required same-boundary
unique-extension condition. Do not read the old draft as selecting a unique microscopic
representative.\\
Screen spectrum and \(n_s=1-P/48\) &
Screen-level theorem only after geometric \(q_r\), normalized \(K_r\), source release energy,
refinement tilt, and angular-spectrum receipts pass. The special \(P/48\) tilt is theorem-grade
only after the edge-center reserve, half-collar projection, and reserve-to-RG receipts pass.
Physical \(A_s\), \(n_s\), running, isocurvature, phase coherence, and TT/TE/EE spectra require the
separate source-stress, single-clock, radial-prior, null-space, forward-residual, transfer, and
likelihood receipts.\\
Dark/anomaly slot &
Imported from \pathref{cosmology/oph_dark_matter_paper.tex}. For a source-only primordial certification run, the dark
continuation is \texttt{OFF} unless a supplied abundance is explicitly typed
\texttt{CONDITIONAL\_SOURCE\_STATE}; transported \(Q_A\) is not by itself an OPH derivation of the
homogeneous anomaly abundance.\\
Scalar anomaly rows &
Rows for \(\rhoA\), \(\rhoAeq\), and \(\Bkernel\) are diagnostics unless the finite covariant
parent also emits \(w_A\), \(\csA\), \(\sigmaA\), \(\QA\), exchange-current closure, recipient
stress for nonzero exchange, gauge-independent variables, CDM-limit recovery, and refinement
convergence. A transition-matrix number is \(\gamma_{\mathrm{repair\ step}}\) until promoted to
\(\GammaRec\) by the physical clock, active-fiber, and common-parent response receipts.\\
Boltzmann and likelihood comparison &
Physical promotion requires immutable source, solver, and likelihood hashes, official likelihood
execution, and global CDM-limit reductions. Shard-local \texttt{any()} rollups or nonlinear
averages before global pooling do not satisfy the contract.\\
Vacuum language &
Finite reference states and free-field/lattice baselines remain reference ensembles. OPH-native
vacuum promotion requires the quotient-ensemble selector plus source Euclidean slab data and a
transfer/reflection-positive reconstruction gate from the compact/screen-microphysics theorem
surface.\\
Simulator receipts &
Any physical-promotion receipt cited here must carry exact source/config/solver/likelihood hashes. The 256k run
used for diagnostics records \texttt{git\_commit=unknown}, so it is not used as exact replay
provenance.\\
\end{longtable}

\section{Source Corpus}

This paper consolidates these active surfaces.
\begin{longtable}{@{}p{0.28\textwidth}p{0.62\textwidth}@{}}
\toprule
Surface & Imported role\\
\midrule
\endhead
\bottomrule
\endfoot
\pathref{cosmology/oph_inflation_without_inflaton_observer_screen_synchronization.tex} &
Main inflation-free branch: finite screen federation, flatness, horizon coherence, geometric screen
spectrum, screen amplitude, radial lift, MaxEnt release, anomaly slot, transfer, and likelihood gates.\\
\pathref{cosmology/physical_cmb_theorem_program.md} &
Theorem-contract file identifying the physical CMB source, scale, stress, kernel,
transfer, and likelihood contracts.\\
\pathref{paper/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.tex} &
Compact recovered-core claim boundary and the first surface for later propagation.\\
\pathref{paper/tex_fragments/PAPER.tex} &
Main technical paper surface for global OPH theorem language.\\
\pathref{paper/tex_fragments/PRIMORDIAL_BRIDGE_THEOREMS.tex} &
Primordial bridge theorem boundary and screen-to-primordial finite-source conditions.\\
\pathref{paper/screen_microphysics_and_observer_synchronization.tex} &
Finite observer-screen carriers, records, patch ports, evidence bundles, and implementation
invariance.\\
\pathref{cosmology/oph_dark_matter_paper.tex} &
Collar-remainder dark/anomaly stress, galaxy equilibrium, dynamic stress, and cosmological kernel
contracts. This paper imports those contracts by reference; it does not duplicate the dark-sector
derivations.\\
\pathref{oph-physics-sim/runs/gcp_large_vis_256k_modkernel_20260623} &
256k-patch simulator evidence: strong CMB diagnostics, physical-prediction receipt with failed
gates, and full visualizer export data. The run manifest records \texttt{git\_commit=unknown};
the canonical simulator repository is \SimSourceRepo, and the public source reference available for
this consolidation is \SimSourceCommit.\\
\end{longtable}

\begin{remark}[Simulator receipt provenance]
Whenever this paper mentions simulator receipts, the receipt artifacts should be traced to the
responsible commit in the canonical simulator repository, \SimSourceRepo. For the 256k run used here, the local artifact
\pathref{runs/gcp_large_vis_256k_modkernel_20260623/manifest.json} reports
\texttt{git\_commit=unknown}. Therefore the numerical run is cited as diagnostic evidence with
incomplete commit provenance. The available public source context for this consolidation is
\SimSourceCommitURL, but that link is not asserted to be an exact run-replay hash for the 256k
artifacts. Physical-promotion receipts require exact source, config, solver, and likelihood hashes.
\end{remark}

\begin{remark}[Ownership boundary for the dark-matter paper]
The released dark-matter paper \pathref{cosmology/oph_dark_matter_paper.tex} keeps ownership of
the dark-sector theory: collar-remainder stress, galaxy equilibrium, dynamic repair-stress
transport, cluster behavior, and the detailed perturbation-kernel derivations. This cosmology
program paper only records the interface that paper must expose to the physical
CMB/large-scale-structure pipeline. When it names
\(\rhoA(a)\), \(\Bkernel(k,a)\), stress closure, repair-stress transport, or a certified
\(\GammaRec(k,a)\), it is naming imported source functions and receipts, not rederiving the dark
sector here.
\end{remark}

\section{Imported Theorem Map}

The inflation-free draft contains many theorem statements. The table gives them a public-core
landing surface and keeps their dependency roles visible.

\begin{longtable}{@{}p{0.30\textwidth}p{0.60\textwidth}@{}}
\toprule
Imported theorem family & Role in this paper\\
\midrule
\endhead
\bottomrule
\endfoot
Finite synchronization normal form &
Defines the early observer-facing quotient state whose repair normal form replaces an assumed
smooth primordial substrate, with uniqueness read modulo the compact-paper quotient
equivalences.\\
Clocked FLRW curvature holonomy, flat-sector selection, and curvature bounds &
Owns the flatness branch: zero clock-slice spatial Levi--Civita holonomy identifies
\(\kappa=0\); exact selection requires a direct theorem, conditional CMH selector, or explicit
flat-branch assumption. Curvature damping supplies only \(|K|\) or \(|\Omega_K|\) bounds.\\
Diffusive horizon no-go, same-boundary coherence, and low-\(k\) repair gap &
Separates a failed purely local diffusion story from the allowed same-boundary or uniform low-\(k\)
synchronization mechanisms.\\
Geometric screen scalar, precision operator, MaxEnt screen covariance, Mellin lift,
edge-center scalar opportunities, \(\Zsix\) reserve, and half-collar sampling &
Owns the screen-level near-scale-invariant covariance. The red tilt \(P/48\) is theorem-grade only
after the reserve-to-RG receipts pass; physical primordial promotion waits for the source-only radial
bridge receipts.\\
Finite release collar state, scalar release code, and scalar amplitude theorem &
Owns \(\Azeta\) as a finite source artifact rather than a fitted amplitude.\\
MaxEnt release, entropy transport, BBN-safe release, recombination inheritance, and adiabaticity &
Connects the synchronized finite screen/collar state to a hot radiation branch with ordinary
low-energy thermal history.\\
Freezeout, scalar quotient record, gauge-invariant \(\zeta\), isocurvature decay, and
superhorizon conservation &
Imported only through the stricter primordial bridge: total stress closure, single clock, repair
gap, freezeout, growing mode, isocurvature, phase coherence, radial prior, null-space, and forward
residual.\\
Finite homogeneous anomaly charge, no double counting, packet moments, cold anomaly, Bianchi
exchange, no-slip lensing, and linear anomaly transfer &
Imported from \pathref{cosmology/oph_dark_matter_paper.tex}; this paper only records the CMB/LSS
handoff interface and receipt gates.\\
Universe Simulation certificate bundle, no-data-use theorem, finite-certificate branch, Boltzmann
stability, likelihood promotion, and CMB admissibility &
Owns the promotion rule: source-only finite artifacts first, frozen transfer and likelihood second,
physical CMB claim last.\\
Tensor repair gap and finite-collar non-Gaussianity &
Records secondary predictions to be tested only after the primary scalar/source/stress gates close.\\
\end{longtable}

\section{Extended Cosmology Agenda}

The local cosmology notes identify several OPH-native prediction surfaces beyond the immediate CMB
gate. They are program tracks, not independent claims.

\begin{enumerate}[leftmargin=2em]
\item \textbf{CMB as observer-consensus fossil.} The highest-value target is the CMB: largest
observable scales should carry relics of finite observer synchronization rather than a fitted
inflationary initial spectrum.
\item \textbf{\(\Lambda\) from observer capacity.} The screen-capacity branch relates the de Sitter
scale to finite horizon capacity. A full cosmology paper should derive the equation of state,
possible time evolution, and any deviation from \(w=-1\).
\item \textbf{Full cosmological dark sector.} The dark paper's galaxy layer is not enough. CMB,
BAO, weak lensing, growth, and \(S_8\) need the transported repair-stress perturbation branch.
\item \textbf{\(H_0\) and \(S_8\) predictions.} With the scale bridge and anomaly kernels fixed,
the branch should emit blind values or intervals for \(H_0\) and \(S_8\), without tuning toward
observed tensions.
\item \textbf{Large-scale topology.} Finite observer-accessible screens make global topology and
matching-circle style signatures natural tests.
\item \textbf{Consensus hierarchy of structure.} Galaxy, cluster, and supercluster formation should
be investigated as a hierarchy of stable consensus attractors, with density perturbation growth in a
fixed background as one layer of the story.
\item \textbf{Cosmological arrow of time.} OPH has native records, checkpoints, and continuation
laws; these should be used to formulate the low-entropy past condition as a finite-record boundary
condition.
\item \textbf{Cosmological neutrino background.} The particle/mass branch should eventually feed
neutrino background and free-streaming predictions into the same frozen likelihood contract.
\end{enumerate}

\section{Finite Cosmological State}

\begin{definition}[Early OPH screen federation]
An early OPH cosmological state at regulator \(r\) is a finite patch federation
\[
\mathcal F_r=
\left(
V_r,E_r,\{\mathcal A_i,\rho_i,\mathcal R_i\}_{i\in V_r},
\{\mathcal I_e,\pi_{i,e}\}_{e\in E_r},
\mathcal U_r,\mathrm{Chk}_r
\right),
\]
with finite accessible algebras, record algebras, visible overlap interfaces, repair instruments,
and checkpoint data. Its physical content is the quotient under hidden carrier coordinates that do
not affect visible interface records, repair maps, or checkpoint continuation.
\end{definition}

\begin{definition}[Source-only finite artifact]
A finite artifact \(X\) is source-only for cosmology if it is a deterministic functional of declared
OPH source data, release-branch constants, and standard non-CMB physical constants, and if its
dependency manifest excludes CMB, BAO, supernova, weak-lensing, RSD, SPARC, cluster, or other
observational likelihood values used to evaluate the prediction.
\end{definition}

\begin{definition}[Physical CMB promotion]
An OPH CMB run is physically promoted only when the primordial source, scale bridge, dark/anomaly
stress kernels, Boltzmann solver input files, solver version/tolerances, and likelihood code/data
hashes are all frozen before likelihood evaluation, and all source functions are source-only finite
artifacts.
\end{definition}

\begin{definition}[Cosmology artifact promotion ladder]
Cosmology artifacts first carry the three claim tiers of
Definition~\ref{def:cosmology-claim-tiers}.  Within a tier, source artifacts also carry an explicit
semantic type
\[
\textsc{DiagnosticProxy}
\prec
\textsc{FiniteScreenSource}
\prec
\textsc{FinitePrimordialSource}
\prec
\textsc{PhysicalBoltzmannSource}
\prec
\textsc{PhysicalCMBPrediction}.
\]
No receipt may skip a boundary in this order.  A close TT curve, a scalar CMI row, a cap-angle
mode number, a repair-clock eigenvalue, or a visual freezeout surface is therefore
\texttt{DIAGNOSTIC\_PROXY} until the required source, physical-scale, stress, transfer, and
likelihood receipts promote it step by step.  Imported FLRW geometry can promote downstream labels
only to \texttt{CONDITIONAL\_PHYSICAL}; \texttt{OPH\_NATIVE\_PHYSICAL} additionally requires
Target~\ref{target:cosmo-geometry-extraction}.
\end{definition}

\begin{definition}[Proof-carrying source artifact]
A promotable artifact is a record
\[
\mathfrak A_v=
(id_v,\tau_v,x_v,\mathcal X_v,\mathcal U_v,\mathrm{Par}(v),
\mathcal D_v,\mathcal E_v,h_v^{\rm theorem},h_v^{\rm witness},
h_v^{\rm build},h_v^{\rm artifact}),
\]
where \(\tau_v\) is the semantic type, \(x_v\) is the value or tensor/function,
\(\mathcal X_v\) records axes, domain, grid, and support, \(\mathcal U_v\)
records units, gauge, frame, pivot, and conventions, \(\mathrm{Par}(v)\) is the
complete parent set, \(\mathcal D_v\) is the data-class ledger,
\(\mathcal E_v\) is the numerical and theorem error envelope, and the hashes
commit to theorem version, witness, build environment, and artifact payload.
\end{definition}

\begin{theorem}[Sound promotion by source DAG induction]
Let \(G=(V,E)\) be a finite acyclic artifact graph.  For each node \(v\), let
\(P_v(\mathfrak A_v)\) be the mathematical predicate claimed by the artifact
and let \(V_v(\mathfrak A_v,w_v)\) be a sound verifier, so
\[
V_v(\mathfrak A_v,w_v)=1\Longrightarrow P_v(\mathfrak A_v).
\]
Define
\[
\operatorname{Pass}(v)
=V_v(\mathfrak A_v,w_v)
\wedge\bigwedge_{p\in\operatorname{Par}(v)}\operatorname{Pass}(p)
\wedge\operatorname{SourceOnly}(v).
\]
Then \(\operatorname{Pass}(v)=1\) implies \(P_v(\mathfrak A_v)\), and every
required parent predicate holds.
\end{theorem}

\begin{proof}
Order the finite DAG topologically. Root nodes satisfy their predicates by
local verifier soundness. If every parent of \(v\) has passed, then the local
verifier proves \(P_v\) and the parent hypotheses are available. The
claim follows by induction.
\end{proof}

\begin{target}[Source ancestry and freeze receipts]
Physical promotion requires
\[
\texttt{TRANSITIVE\_SOURCE\_ANCESTRY\_RECEIPT},\quad
\texttt{HERMETIC\_READ\_SET\_RECEIPT},\quad
\texttt{SOURCE\_MODEL\_FREEZE\_RECEIPT}.
\]
The first receipt walks every ancestor of every promoted quantity and rejects any CMB, BAO,
supernova, weak-lensing, growth, cluster, or similar evaluation-data dependency.  The second
requires an intercepted, content-addressed read set for files, network, environment, command-line
configuration, caches, randomness, code, dependencies, and human-selected branch identifiers.  The
third freezes branch, model family, basis, pivot, cutoff, packetization, smoothing, thresholds,
freezeout tolerances, and hyperparameter ranges before comparison.
\end{target}

\section{Inflation-Free Branch}

The inflation-free branch replaces inflation's jobs rather than reproducing an inflaton. Its
load-bearing theorem stack is:
\begin{enumerate}[leftmargin=2em]
\item quotient-level observer-facing normal form for the early screen/collar federation, with the
compact-paper quotient equivalences;
\item zero clock-slice spatial Levi--Civita holonomy to identify the flat branch, plus a direct
flatness theorem, conditional CMH selector, or explicit flat-branch assumption to select it;
\item same-boundary scalar normal form or a low-\(k\) repair gap for horizon coherence;
\item geometric screen spectrum for near scale invariance;
\item protected \(\Zsix\) half-collar reserve for the red spectral exponent;
\item finite scalar release code for \(\Azeta\);
\item MaxEnt release and common release clock for a hot adiabatic start;
\item imported dark/anomaly stress variables for the pre-recombination CDM-like slot, when the
\pathref{cosmology/oph_dark_matter_paper.tex} source contract permits them;
\item Boltzmann transfer and frozen likelihood for observational comparison.
\end{enumerate}

\begin{theorem}[Conditional OPH replacement of inflation]
Assume a cofinal family of finite early OPH screen federations has a quotient-level
observer-facing normal-form projection on a declared branch, with uniqueness understood modulo
boundary redundancy, implementation hiding, inert ancillary stabilization, and any same-boundary
unique-extension condition required by the branch. Assume the clocked FLRW continuation boundary
\(B_{\cos,r}\) supplies \(u_a=-N\nabla_a\chi\), \(h_{ab}=g_{ab}+u_au_b\),
\(K(\tau)=\kappa/a^2\), and topology policy, and that one of the exact flat-sector gates is
present: \textsc{DirectTheorem}, \textsc{ConditionalCMH}, or \textsc{ExplicitAssumption}. Assume
every CMB-scale scalar mode shares the same boundary normal
form or satisfies a uniform low-\(k\) repair gap, the finite screen-spectrum receipts derive a
geometric \(q_r\), normalized \(K_r\), source release energy \(A_q\), and refinement tilt, the
source-only radial bridge receipts pass, and the imported dark/anomaly sector supplies a permitted CDM-like source
state through recombination. Then the branch supplies flatness, horizon coherence, near scale
invariance, hot adiabatic initial data, and acoustic-transfer input without an inflaton degree of
freedom.
\end{theorem}

\begin{proof}
The proof is a dependency composition. The quotient normal-form projection gives a finite
observer-facing early state on the declared branch, not a unique hidden representative. The spatial
Levi--Civita holonomy theorem identifies the \(\kappa=0\) branch; the direct, CMH, or
explicit-assumption gate selects it. Curvature damping is not used as a selector. Same-boundary
repair or a low-\(k\) gap gives
coherence on the observed CMB band. The screen-spectrum theorem package first gives
\[
C_\ell^q
=A_q\frac{\Gamma(\ell-\theta/2)}{\Gamma(\ell+2+\theta/2)}.
\]
The value \(\theta=P_\star/48\) follows only if the edge-center reserve, half-collar scalar projection,
and reserve-to-RG receipts pass; otherwise \(\theta\) is measured from the actual scalar refinement
operator or kept as a diagnostic hypothesis. The source-only bridge receipts then type that screen
scalar as a primordial curvature source and convert \(A_q\) to \(\Azeta\) only after the exact
thin-shell or finite-window radial lift, null-space, and forward-residual receipts pass. Without
them it remains a screen theorem.
MaxEnt release gives a hot radiation state and the common clock gives adiabatic leading
perturbations. If the imported anomaly stress branch is an admissible source state through
recombination, the acoustic peaks are computed by ordinary Einstein-Boltzmann transfer from those
finite inputs.
\end{proof}

\begin{proposition}[Curvature suppression is not sector selection]
On a fixed clocked FLRW sector,
\[
K(\tau)=\kappa/a(\tau)^2,\qquad \dot K=-2HK .
\]
Any repair or expansion estimate that proves a finite bound on \(|K|\) or \(|\Omega_K|\) is an
\textsc{ApproximateBound}. It does not change \(\kappa\), does not distinguish globally inequivalent
flat topologies, and may not be reported as \textsc{DirectTheorem} or \textsc{ConditionalCMH}.
\end{proposition}

\begin{remark}[Theorem boundary]
The theorem is conditional at the CMB-prediction tier unless the finite source package, physical
scale bridge, stress parent, Boltzmann transfer, and frozen likelihood receipts all pass for the
same generation. Imported frozen geometry can support the \texttt{CONDITIONAL\_PHYSICAL} route.
\texttt{OPH\_NATIVE\_PHYSICAL} also requires the quotient-derived
\(\mathsf{CosmoGeomRead}_r\) and source embedding theorem.
\end{remark}

\section{Physical CMB Finite-Source Contract}

The physical CMB source contract requires theorem-grade finite artifacts:
\[
\Azeta,\qquad q_{\rm IR},\qquad \ell_{\rm IR},\qquad
\rhoA(a),\qquad \rhoAeq(a),\qquad \Bkernel(k,a),\qquad
\gamma_{\mathrm{repair\ step}}(k,a)\ \hbox{or certified}\ \GammaRec(k,a),
\]
plus full stress variables, freezeout, physical mode calibration, and \(\NCRC\) provenance.

\begin{definition}[Finite primordial source package]
At regulator \(r\), a physical primordial-source claim is carried by
\[
\mathfrak S_r^{\rm prim}=
(\mathcal Q_r,n_r,\mu_r,q_r,J_r,\Pi_r,K_r,M_r,\Xi_r,\Sigma_r,E_r^{\rm rel},
A_{q,r},\theta_r,q_{{\rm IR},r},t_{{\rm IR},r},\Sigma_{\star,r},W_r,
\Delta_{\zeta,r}^2,\mathcal P_{IJ,r},\mathcal E_r).
\]
Here \(\mathcal Q_r\) is the physical quotient state space, \(n_r\) the
normal-form map, \(\mu_r\) the source probability law, \(q_r\) the
quotient-visible scalar source, \(J_r\) the finite carrier-to-harmonic readout,
\(\Pi_r\) the gauge/monopole/dipole projector, \(K_r\) the positive scalar
precision operator, \(M_r\) the mobility or repair-response operator,
\(\Xi_r\) the stochastic forcing covariance,
\(\Sigma_r=\operatorname{Cov}_{\mu_r}(q_r)\), \(E_r^{\rm rel}\) the source
release-energy artifact, \(A_{q,r}\) the finite screen amplitude, \(\theta_r\)
the spatial/RG spectral exponent, \(q_{{\rm IR},r}\) the IR suppression depth,
\(t_{{\rm IR},r}\) the IR semigroup time, \(\Sigma_{\star,r}\) the freezeout
cut, \(W_r\) the radial window, \(\Delta_{\zeta,r}^2\) the lifted primordial
spectrum, \(\mathcal P_{IJ,r}\) the species-level initial covariance, and
\(\mathcal E_r\) the complete error and refinement envelope.
\end{definition}

\begin{target}[Finite-source input contract]
The paper stack must define pass/fail receipts for:
\begin{enumerate}[leftmargin=2em]
\item a source-provenance dependency DAG for all CMB source inputs;
\item globally pooled sufficient-statistic reducers before nonlinear source estimates;
\item the role of \(\NCRC\) as a consensus invariant, additive capacity, or theorem-side constant;
\item finite derivations of \(\Azeta\), \(q_{\rm IR}\), and \(\ell_{\rm IR}\);
\item total stress closure, single-clock normal form, entropy repair gap, curvature evolution,
adiabatic growing mode, isocurvature bound, phase coherence, screen-to-radial lift, radial null-space,
forward residual, and finite freezeout receipts;
\item \(\texttt{physical\_k\_units\_calibrated}\), derived exactly from
\(\texttt{PHYSICAL\_SPATIAL\_K\_RECEIPT}\);
\item \(\texttt{screen\_to\_physical\_k\_association\_calibrated}\), derived from
\(\texttt{SCREEN\_TO\_PHYSICAL\_K\_ASSOCIATION\_RECEIPT}\);
\item \(\texttt{source\_angular\_sector\_calibrated}\), derived from
\(\texttt{SOURCE\_ANGULAR\_SECTOR\_RECEIPT}\), with
\(\ell_{\rm src}\) kept distinct from \(L_{\rm CMB}\);
\item \(\texttt{calibrated\_a\_evolution}\), derived from
\(\texttt{CALIBRATED\_A\_EVOLUTION\_RECEIPT}\);
\item \(\texttt{physical\_mode\_freezeout\_map\_calibrated}\), derived from
\(\texttt{PHYSICAL\_MODE\_FREEZEOUT\_MAP\_RECEIPT}\);
\item \(\texttt{common\_primordial\_initial\_surface\_calibrated}\), derived from
\(\texttt{PHYSICAL\_FREEZEOUT\_SURFACE\_RECEIPT}\);
\item a nonempty cross-receipt manifest with matching regulator-family, generation, geometry,
background, clock, scale-certificate, source-embedding, mode-basis, mode-lineage, boundary,
solver-convention, freezeout-surface, and source-DAG hashes;
\item source-only imported dark-sector functions \(\rhoA(a)\), \(\rhoAeq(a)\), \(w_A(a)\),
\(\csA(k,a)\), \(\sigmaA(k,a)\), \(\QA\), \(\Bkernel(k,a)\), and the
\(\gamma_{\mathrm{repair\ step}}\) diagnostic or certified \(\GammaRec(k,a)\), where the chosen
dark-continuation mode permits them.
\end{enumerate}
A mode-dependent freezeout map does not satisfy
\(\texttt{PHYSICAL\_FREEZEOUT\_SURFACE\_RECEIPT}\); the receipt denotes a common spacelike initial
surface with initial data and normal derivatives in one frozen generation.
\end{target}

\begin{target}[Scalar, harmonic, and IR source receipts]
The scalar-source branch must supply
\[
\texttt{SCALAR\_SOURCE\_MAP\_RECEIPT},\quad
\texttt{A5\_TO\_SO3\_INTERTWINER\_RECEIPT},\quad
\texttt{SPHERICAL\_QUADRATURE\_RECEIPT},\quad
\texttt{LOW\_MODE\_PROJECTOR\_RECEIPT}.
\]
The map \(\mathsf{ScalarSourceMap}_r:\operatorname{nf}(\mathcal Q_r)\to
V_r^{\rm scalar}\) must be quotient-invariant, refinement-natural, and
normalized without per-run standardization.  Harmonic reconstruction uses a
weighted Gram matrix \(G_L=Y_L^\dagger W Y_L\) and the low-mode projector
\[
\Pi_{\ge2}=I-Y_{01}(Y_{01}^\dagger W Y_{01})^{-1}Y_{01}^\dagger W.
\]
The IR kernel is parameterized by the semigroup time
\[
S_{\rm IR}=I-q_{\rm IR}e^{-t_{\rm IR}L},\qquad
F_{\rm IR}(\ell)=1-q_{\rm IR}e^{-t_{\rm IR}\ell(\ell+1)}.
\]
The validator must enforce \(0\le q_{\rm IR}\le1\), \(t_{\rm IR}\ge0\), and
derive the display scale
\[
\ell_{\rm IR}=\frac{-1+\sqrt{1+4/t_{\rm IR}}}{2}
\]
when \(t_{\rm IR}>0\).  The old dimension count \(12+20+1=33\Rightarrow
\ell_{\rm IR}=32\) is not a source theorem.
\end{target}

\begin{target}[Fluctuation covariance and tilt receipts]
Deterministic settling does not choose a fluctuation ensemble.  The finite
quotient ensemble must supply \(\mu_r(q)=m_r(q)e^{-S_r(q)}/Z_r\) with
projective compatibility, sampler correctness, and implementation invariance.
Repair drift does not determine covariance: \(D\Sigma+\Sigma D^{\mathsf T}=\Xi\)
requires the noise covariance \(\Xi\).  A fluctuation-dissipation branch may
use \(D=M_rK_r\), \(\Xi=2A_rM_r\), and \(\Sigma_r=A_rK_r^{-1}\) when it also supplies
\[
\texttt{QUOTIENT\_ENSEMBLE\_RECEIPT},\quad
\texttt{LYAPUNOV\_COVARIANCE\_RECEIPT},\quad
\texttt{FLUCTUATION\_DISSIPATION\_RECEIPT},\quad
\texttt{MODE\_RESOLVED\_PRECISION\_OPERATOR\_RECEIPT}.
\]
The temporal repair gap, spatial RG exponent, primordial tilt, and physical
exchange-rate kernel are distinct types:
\[
\texttt{TEMPORAL\_REPAIR\_GAP},\quad
\texttt{SPATIAL\_RG\_EIGENEXPONENT},\quad
\texttt{PRIMORDIAL\_SPECTRAL\_TILT},\quad
\texttt{PHYSICAL\_EXCHANGE\_RATE\_KERNEL}.
\]
Only after the radial theorem identifies
\(\Delta_\zeta^2(k)\propto k^{-\theta}\) may the branch write
\(n_s=1-\theta\).
\end{target}

\begin{proposition}[Why the 256k CMB curve is diagnostic]
The 256k OPH-FPE run has measurement-facing diagnostic status only. Its
promotion report marks the finite-source input contract false and lists missing
source provenance, missing pooled reducers, missing \(\NCRC\) invariant role, non-finite
\(\Azeta\), missing screen-to-primordial lift, non-finite \(q_{\rm IR}\) and \(\ell_{\rm IR}\),
non-finite \(\rhoA\) and \(\Bkernel\), missing finite covariant parent receipt, missing stress
closure, missing full fluid/exchange variables, missing gauge/causal/refinement certificates,
missing freezeout, missing official likelihood and CDM-limit reductions, and missing frozen solver
and likelihood hashes.
\end{proposition}

\section{Physical Scale Bridge}

Section~\ref{sec:physical-scale-bridge} owns the bridge definitions, no-go propositions, and
conditional physical-scale theorem.  The practical rule is:
\[
\texttt{inverse\_cap\_opening\_angle\_proxy},\quad
\texttt{repair\_cycle},\quad
\texttt{graph\_mode\_index}
\]
are nonpromotable diagnostic labels unless the structured receipt conjunctions in
Target~\ref{target:physical-scale-receipts} pass.  A frozen imported FLRW geometry packet can
exercise the complete spectral/clock/freezeout/transfer pipeline at tier
\texttt{CONDITIONAL\_PHYSICAL}.  The \texttt{OPH\_NATIVE\_PHYSICAL} tier additionally requires a
quotient-derived \(\mathsf{CosmoGeomRead}_r\) and source embedding theorem with the same downstream
interfaces.

\section{Dark/Anomaly Interface Imported from the Dark-Matter Paper}

The dark/anomaly slot is the largest cosmology-facing bridge between the OPH dark-matter paper and
the CMB program. The released dark-matter paper \pathref{cosmology/oph_dark_matter_paper.tex}
owns the derivation: collar remainder stress, settled galaxy response, dynamic transport, cluster
behavior, and perturbation kernels. This paper only states the interface the CMB program requires
from that paper. Cosmology needs the
imported dark sector to expose a transported stress component with background density,
perturbations, exchange terms, gauge-invariant variables, and the CDM-limit switch-off check.

\begin{definition}[Imported finite covariant collar-packet parent interface]
For the purpose of this cosmology program, the finite covariant collar-packet parent is an imported
\pathref{cosmology/oph_dark_matter_paper.tex}-owned finite artifact interface
\[
\mathcal P_A=
(\mathcal C_r,Z_r,A_r,R_r,G_r,\pi_r,L_r,Q_r,D_r)
\]
where \(Z_r\) splits anomaly and recipient packet states, \(\pi_r\) is the finite equilibrium
packet functional, \(L_r\) is the repair generator, \(Q_r\) records energy-momentum reaction
channels, and \(D_r\) records any causal auxiliary response. The interface emits packet stress
moments
\[
\rho_A,\quad P_A,\quad q_A,\quad \pi_A,
\]
and source variables
\[
\rhoA(a),\quad \rhoAeq(a),\quad w_A(a),\quad \csA(k,a),\quad
\sigmaA(k,a),\quad \QA,\quad \Bkernel(k,a),\quad
\gamma_{\mathrm{repair\ step}}(k,a)\ \hbox{or certified}\ \GammaRec(k,a),
\]
with explicit conservation or exchange equations, recipient stress for nonzero exchange, gauge
projection, causal response, regulator-refinement convergence, and \(B_A\) built from the
anomaly-frame baryon density \(n_b^{(A)}=-u_{A\mu}J_b^\mu\).
\end{definition}

\begin{definition}[Issue \#319 conditional source receipt]
The imported dark-sector parent first has to pass
\[
\texttt{ISSUE\_319\_CONDITIONAL\_SOURCE\_RECEIPT}.
\]
This receipt is a conjunction of source-side receipts, not a scalar CMI row. It requires exactly
one declared route,
\[
\texttt{SOURCE\_ROUTE\_RECEIPT},
\]
unit metadata
\[
\texttt{ENTROPY\_UNIT\_RECEIPT},
\]
the exact carried modular identity
\[
  \langle K_{AB}+K_{BD}-K_B-K_{ABD}\rangle=I(A:D|B),
\]
and the first-variation classification that prevents raw CMI from being silently identified with a
linear fixed-reference modular-energy variation. The source route is either
\texttt{FIXED\_REFERENCE\_MODULAR\_ENERGY} or \texttt{NONLINEAR\_CMI\_STRESS}. The second route also
requires
\[
\texttt{CMI\_TO\_MODULAR\_SOURCE\_MATCHING\_RECEIPT}.
\]
Both routes require collar-localization, BW normalization, physical diamond scale, \(\ell^4\)
scaling, cover-independence, and stress-tomography receipts before the proper-radius normalization
\[
  T_A^{ab}u_a u_b
  =
  \frac{15\hbar c}{8\pi^2\ell^4}R^{\rm src}_{r,\ell}
\]
may be imported. Classical diagonal CMI rows, cap-angle proxies, duplicated collar counts, or
absolute-value rectified density rows do not satisfy this receipt by themselves.
\end{definition}

\begin{target}[Imported stress-parent receipt]
The simulator receipt
\[
\texttt{FINITE\_COVARIANT\_PARENT\_RECEIPT}
\]
must fail unless the owning dark-sector paper and its evidence bundle certify all of the following:
\begin{enumerate}[leftmargin=2em]
\item \(\texttt{ISSUE\_319\_CONDITIONAL\_SOURCE\_RECEIPT}\);
\item \(\texttt{CMI\_TO\_MODULAR\_SOURCE\_MATCHING\_RECEIPT}\) on the nonlinear-CMI route, or
\(\texttt{FIXED\_REFERENCE\_MODULAR\_ENERGY\_RECEIPT}\) on the fixed-reference route;
\item \(\texttt{STRESS\_TOMOGRAPHY\_RECEIPT}\) and \(\texttt{SM\_CURRENT\_NULL\_RECEIPT}\);
\item exact finite stress-energy closure for anomaly plus recipient stresses;
\item explicit recipient stress and equal-and-opposite exchange current whenever the exchange
branch is nonzero;
\item detailed balance or a declared nonequilibrium exchange law;
\item gauge independence of the emitted perturbation variables, including the anomaly-frame
baryon-density definition of \(B_A\);
\item causal response with subluminal finite characteristics;
\item convergence under regulator refinement;
\item recovery of the CDM branch when exchange, pressure, sound speed, and anisotropic stress are
switched off.
\end{enumerate}
The finite parent receipt is source-side.  It does not include official CMB likelihood execution.
The later
\(\texttt{PHYSICAL\_CMB\_PROMOTION\_RECEIPT}\) additionally requires the physical scale bridge,
physical \(\rho_A\), \(B_A\), and \(\Gamma_{\rm rec}\) kernels, Boltzmann transfer, frozen
source/solver/likelihood hashes, and the official likelihood run.
\end{target}

\begin{remark}[Dark continuation modes]
For a source-only primordial certification run, the dark-sector paper recommends
\texttt{dark\_continuation = OFF}. A supplied dark abundance may enter only as
\texttt{dark\_continuation = CONDITIONAL\_SOURCE\_STATE} until the dark-matter theorem surface
derives the homogeneous anomaly abundance and finite kinetic stress construction. The physical
cosmology branch may set \texttt{dark\_continuation = PHYSICAL\_PARENT} only after the finite
covariant parent receipt, physical scale bridge, response/kernel receipts, and CDM-limit recovery
all pass for the same frozen generation.
\end{remark}

\section{Physical Kernel Interface}

The physical kernels are not scalar rows in a table. They are imported finite functionals with
units, gauge-invariant definitions, paired controls, and refinement margins. Their derivation stays
in \pathref{cosmology/oph_dark_matter_paper.tex}; this paper only states what the CMB/LSS pipeline must receive.

\begin{target}[Physical anomaly kernel interface]
The released dark-matter paper must define deterministic receipts
\begin{center}
\begin{tabular}{@{}l@{}}
\texttt{RHO\_A\_SOURCE\_RECEIPT}\\
\texttt{RHO\_A\_EQ\_SOURCE\_RECEIPT}\\
\texttt{B\_A\_KERNEL\_RECEIPT}\\
\texttt{GAMMA\_REC\_SOURCE\_RECEIPT}
\end{tabular}
\end{center}
These receipts pass only when \(\rhoA(a)\), \(\Bkernel(k,a)\), and \(\GammaRec(k,a)\) are emitted
as certified physical functions with \(\rhoAeq(a)\), \(w_A(a)\), \(\csA(k,a)\), \(\sigmaA(k,a)\),
and \(\QA\) from the finite parent, physical scale calibration, gauge consistency, paired
perturbation controls, active-fiber/physical-clock response receipts, CDM-limit recovery, and
refinement convergence. The cosmology program consumes the emitted functions but does
not redefine the dark-sector source law.

The physical kernel receipt imports these inner receipts from the dark/anomaly paper:
\begin{center}
\begin{tabular}{@{}l@{}}
\texttt{COMMON\_SOURCE\_FUNCTIONAL\_RECEIPT}\\
\texttt{ADMISSIBLE\_SOURCE\_TANGENT\_RECEIPT}\\
\texttt{CONSTRAINT\_PRESERVING\_RETRACTION\_RECEIPT}\\
\texttt{SOURCE\_VECTOR\_SUFFICIENCY\_RECEIPT}\\
\texttt{B\_A\_SOURCE\_LIFT\_INDEPENDENCE\_RECEIPT}\\
\texttt{SOURCE\_DESIGN\_IDENTIFIABILITY\_RECEIPT}\\
\texttt{FINITE\_DIFFERENCE\_ORDER\_RECEIPT}\\
\texttt{C1\_REFINEMENT\_RECEIPT}\\
\texttt{ORDER\_OF\_LIMITS\_RECEIPT}\\
\texttt{NATIVE\_REPAIR\_GENERATOR\_RECEIPT}\\
\texttt{PHYSICAL\_RATE\_UNIT\_RECEIPT}\\
\texttt{QUOTIENT\_LUMPABILITY\_RECEIPT}\\
\texttt{STATIC\_DYNAMIC\_RESPONSE\_CONSISTENCY\_RECEIPT}
\end{tabular}
\end{center}
A diagnostic candidate may contain paired finite differences, controls, and
refinement rows.  The physical receipt is false unless the source functional,
delivered source tangent, source-vector sufficiency, lift-independence,
native generator, and static-dynamic consistency receipts pass in the same
frozen generation.
\end{target}

Diagnostic rows remain useful for debugging. They should be plotted, stress-tested, and compared to
controls. They should not be accepted by the physical CMB contract unless they are promoted by the
kernel receipts above. Until the physical clock, active fiber, conserved-sector decomposition, and
common-parent response pole are certified, the simulator should emit the transition number as
\(\gamma_{\mathrm{repair\ step}}\), not as \(\Gamma_{\rm rec}\). Likewise finite rows for
\(\rho_A\), \(\rho_{A,\mathrm{eq}}\), and \(B_A\) have label
\texttt{DIAGNOSTIC\_SCALAR\_RESPONSE} until promoted by the parent and kernel receipts.

\begin{target}[Finite covariant parent import]
The imported dark-sector parent is not a readiness boolean.  The receipt consumed by this paper is
the conjunction of primitive parent receipts owned by
\pathref{cosmology/oph_dark_matter_paper.tex}:
\[
\begin{gathered}
\texttt{SOURCE\_ROUTE\_RECEIPT},\quad
\texttt{ENTROPY\_UNIT\_RECEIPT},\quad
\texttt{MODULAR\_NONADDITIVITY\_IDENTITY\_RECEIPT},\\
\texttt{CMI\_FIRST\_VARIATION\_CLASSIFICATION\_RECEIPT},\quad
\texttt{SOURCE\_LOCALIZATION\_SATURATION\_RECEIPT},\\
\texttt{BW\_BALL\_NORMALIZATION\_RECEIPT},\\
\texttt{PHYSICAL\_DIAMOND\_SCALE\_RECEIPT},\\
\texttt{ELL4\_SCALING\_PLATEAU\_RECEIPT},\\
\texttt{COVER\_INDEPENDENCE\_RECEIPT},\quad
\texttt{STRESS\_TOMOGRAPHY\_RECEIPT},\\
\texttt{FINITE\_PACKET\_KINEMATICS\_RECEIPT},\\
\texttt{PACKET\_MASS\_SHELL\_RECEIPT},\\
\texttt{TRANSPORT\_COVARIANCE\_RECEIPT},\\
\texttt{CHANNEL\_FOUR\_MOMENTUM\_RECEIPT},\\
\texttt{FINITE\_PACKET\_STRESS\_READOUT\_RECEIPT},\\
\texttt{VARIATIONAL\_MOMENT\_STRESS\_AGREEMENT\_RECEIPT},\\
\texttt{LOCAL\_FRAME\_COVARIANCE\_RECEIPT},\\
\texttt{CARRIER\_QUOTIENT\_INVARIANCE\_RECEIPT},\\
\texttt{TOTAL\_STRESS\_CLOSURE\_RECEIPT},\\
\texttt{EXPLICIT\_RECIPIENT\_STRESS\_RECEIPT},\\
\texttt{EXCHANGE\_CURRENT\_CLOSURE\_RECEIPT},\\
\texttt{SM\_CURRENT\_NULL\_RECEIPT},\\
\texttt{COSMOLOGICAL\_GAUGE\_INVARIANCE\_RECEIPT},\\
\texttt{FINITE\_DOMAIN\_OF\_DEPENDENCE\_RECEIPT},\\
\texttt{SUBLUMINAL\_CHARACTERISTICS\_RECEIPT},\\
\texttt{RETARDED\_RESPONSE\_RECEIPT},\quad
\texttt{RESPONSE\_STABILITY\_RECEIPT},\\
\texttt{REFINEMENT\_CONVERGENCE\_RECEIPT},\quad
\texttt{CDM\_LIMIT\_RECOVERY\_RECEIPT}.
\end{gathered}
\]
The source parent does not contain solver or likelihood hashes.  Those belong to the frozen
generation and likelihood layer below.
\end{target}

\section{Boltzmann Transfer and Frozen Likelihood}

For finite physical source functions, the transfer problem is ordinary cosmology. OPH does not need
a special CMB plotting rule. It needs a frozen handoff to CAMB, CLASS, or a declared independent
Einstein-Boltzmann solver.

\begin{target}[Frozen transfer and likelihood protocol]
A physical OPH CMB prediction requires:
\begin{enumerate}[leftmargin=2em]
\item immutable hashes for source artifacts;
\item immutable hashes for solver source, version, tolerances, and input files;
\item immutable hashes for likelihood code, datasets, covariances, masks, and nuisance priors;
\item a no-data-use manifest showing that observational likelihood values did not enter source
artifact generation;
\item global pooled reducers for nonlinear source estimates and global CDM-limit checks;
\item official likelihood execution readiness beyond a diagnostic binned-table comparison;
\item a falsification rule fixed before the likelihood run.
\end{enumerate}
\end{target}

\begin{definition}[Model generation]\label{def:model-generation}
A cosmology prediction generation is
\[
G_n=(H_{\rm source},H_{\rm scale},H_{\rm parent},H_{\rm kernel},H_{\rm init},
H_{\rm solver},H_{\rm build},H_{\rm config},H_{\rm likelihood},H_{\rm data},
H_{\rm priors},\mathcal A_n),
\]
where \(\mathcal A_n\) is the registry of observational datasets, residuals, posterior summaries,
and diagnostic plots exposed during source development.  Hashing the final artifact is not enough:
if a Planck residual influenced source or model selection, the generation is calibrated on Planck
even when the final bytes are frozen.
\end{definition}

\begin{theorem}[Physical OPH cosmology promotion]\label{thm:physical-oph-cosmology-promotion}
Let \(R_{\rm src}\) be source-only provenance and pooled-reducer receipt,
\(R_{\rm scale}\) the physical mode/clock/lift receipt, \(R_{\rm parent}\) the finite covariant
parent receipt, \(R_{\rm kernel}\) the physical response/kernel receipt, \(R_{\rm init}\) the
regular initial-mode and Einstein-constraint receipt, \(R_{\rm transfer}\) the Boltzmann
well-posedness and numerical-convergence receipt, \(R_{\rm freeze}\) the model-generation freeze
receipt, and \(R_{\rm like}\) the official likelihood execution receipt.  Define
\[
R_{\rm spectrum}=
R_{\rm src}\wedge R_{\rm scale}\wedge R_{\rm parent}\wedge R_{\rm kernel}
\wedge R_{\rm init}\wedge R_{\rm transfer}\wedge R_{\rm freeze},
\]
and for an observational dataset family \(D\),
\[
R_{\rm tested}^{(D)}=R_{\rm spectrum}\wedge R_{\rm like}^{(D)}.
\]
If every receipt in \(R_{\rm spectrum}\) is labelled \(\texttt{PASS}\), then the resulting
TT/TE/EE, lensing, matter power, growth, BAO, or RSD spectra are
\(\texttt{FROZEN\_PHYSICAL\_SPECTRUM}\) outputs of generation \(G_n\).  If \(R_{\rm tested}^{(D)}\)
also passes for a frozen dataset and likelihood family \(D\), the output is a
\(\texttt{LIKELIHOOD\_EVALUATED\_PHYSICAL\_PREDICTION}\).  If any receipt is
\(\texttt{FAIL}\), \(\texttt{OPEN\_GATE}\), \(\texttt{INCOMPLETE}\), or
\(\texttt{INVALIDATED}\), the spectra remain diagnostic or conditional according to the parameter
ledger.
\end{theorem}

\begin{proof}
Each receipt states a typed premise needed by the next map: source fields, physical coordinates,
parent stress, response kernels, initial state, transfer evolution, freeze integrity, and likelihood
execution.  Composition through \(R_{\rm spectrum}\) gives a frozen physical spectrum.  Composing
that frozen spectrum with \(R_{\rm like}^{(D)}\) evaluates it against \(D\).  A failed or open
receipt removes at least one premise, so downstream software cannot promote the output.
\end{proof}

\begin{target}[Outcome and prediction-class ledger]
Likelihood outcomes are
\[
\begin{gathered}
\texttt{INVALIDATED},\quad
\texttt{NUMERICALLY\_INCONCLUSIVE},\quad
\texttt{FALSIFIED\_ON\_DECLARED\_TEST},\\
\texttt{PASSED\_DECLARED\_TEST}.
\end{gathered}
\]
\texttt{INVALIDATED} is used when provenance or freeze integrity fails; it is not a physical
falsification.  Inputs are typed as
\[
\begin{gathered}
\texttt{OPH\_DERIVED},\quad
\texttt{EXTERNAL\_FIXED},\quad
\texttt{CONDITIONAL\_COSMOLOGY},\quad
\texttt{NUISANCE},\\
\texttt{MEASUREMENT\_CALIBRATED},
\end{gathered}
\]
and outputs as
\[
\begin{gathered}
\texttt{SOURCE\_ONLY\_OPH\_PREDICTION},\quad
\texttt{CONDITIONAL\_OPH\_PREDICTION},\\
\texttt{FITTED\_OPH\_MODEL},\quad
\texttt{DIAGNOSTIC\_BASELINE}.
\end{gathered}
\]
The 256k curve has label \(\texttt{CMB0\_LCDM\_DIAGNOSTIC\_BASELINE}\).
\end{target}

\begin{remark}[Global reducers only]
Shard-local nonlinear averages and shard-local \texttt{any()} rollups are not promotion rules. The
source artifact must pool additive sufficient statistics globally, with validated units, coordinate
grids, coverage, duplicate policy, interpolation policy, and covariance, before any nonlinear
quantity such as amplitude, rank, condition number, isocurvature leakage, \(\Bkernel\), \(\rhoA\),
or \(\GammaRec\) is evaluated; a transition diagnostic is recorded separately as
\(\gamma_{\mathrm{repair\ step}}\).
\end{remark}

\begin{remark}[Comparison versus prediction]
The best OPH diagnostic model in the 256k run is scientifically useful because it is close: shape
correlation \(0.9951542364\), normalized RMSE \(0.0984455548\), amplitude-fit
\(\chi^2/{\rm bin}=41.6684770597\), zero mean peak-location error, and mean peak-height fractional
error about \(0.0704905\). Those numbers justify fixing the theorem gates. They do not replace the
gates.
\end{remark}

\section{Vacuum and Quantum-Fluctuation Boundary}

The same finite-source discipline applies to vacuum claims. Seed noise, repair jitter, and
reference free-field baselines are not an OPH-native quantum vacuum.

\begin{target}[OPH-native vacuum gate]
An OPH-native vacuum simulation needs a quotient ensemble measure or density operator on the
observable quotient algebra, refinement compatibility, implementation invariance, a sampler
correctness proof, and source Euclidean slab data \((Q_r,m_r^0,J_r,V_r,a_{t,r})\) whose transfer
operator is derived independently of the target law and sampler. Without this gate, vacuum-like
fields in the simulator are reference baselines or diagnostics.
\end{target}

\section{Claim-Gate Summary}

The paper-side gates are quotient ensemble measure, OPH-native vacuum promotion, Boltzmann transfer,
frozen likelihood closure, finite-source CMB contract hardening, physical scale bridge, finite
covariant collar-packet stress parent, physical anomaly kernels, flat-sector selection,
screen-spectrum derivation, conditional collar source routing, repair-stress transport, and linear
repair-stress perturbations. GitHub issues carry the mutable ownership, dependency, and completion
state for those gates.

\section{Physical Promotion Rule}

Physical promotion requires exact receipt semantics for the objects the simulator is being asked to
produce:
\begin{enumerate}[leftmargin=2em]
\item implement the finite-source dependency DAG and no-data-use firewall;
\item implement global pooled reducers for all nonlinear source estimates;
\item implement the \texttt{CONDITIONAL\_PHYSICAL} imported-FLRW reference backend for the
spectral, clock, freezeout, and transfer pipeline;
\item implement the structured physical scale bridge and freezeout certificates from
Target~\ref{target:physical-scale-receipts};
\item implement the imported finite covariant parent and stress-closure receipts from the
\pathref{cosmology/oph_dark_matter_paper.tex} dark-sector theory;
\item implement physical \(\rhoA\), \(\Bkernel\), and \(\GammaRec\) kernel receipts as imported
dark-sector source functions;
\item freeze source, solver, and likelihood hashes;
\item run official likelihood comparisons and global CDM-limit reductions;
\item label the result \texttt{CONDITIONAL\_PHYSICAL} when all imported-geometry physical receipts
pass, or \texttt{OPH\_NATIVE\_PHYSICAL} when Target~\ref{target:cosmo-geometry-extraction} also
passes.
\end{enumerate}

The simulator may run diagnostics before physical promotion: visualization payloads, CMB overlays,
vacuum baselines, defect worldlines, observer cameras, and H3 readouts. Those outputs carry
diagnostic labels until the relevant receipt passes.

\section{Conclusion}

The 256k simulator almost-fits are not random noise. They expose stable structure close enough to
justify the theorem gates, and they show why those gates are necessary. A physical cosmology
prediction needs finite source-only objects, physical scale calibration, covariant stress closure,
physical anomaly kernels, and frozen likelihoods. This paper is the staging surface for that work and
the simulator contract for physical promotion.

\begin{thebibliography}{99}

\bibitem{ophcompact}
B.~M\"uller, A.~Osika, K.~Xue, and P.~Nguyen,
\emph{Recovering Relativity and the Standard Model from Observer Overlap Consistency},
OPH compact paper, release \OPHPaperReleaseID, 2026.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.pdf}

\bibitem{ophsynthesis}
B.~M\"uller, A.~Osika, M.~Poneder, K.~Xue, B.~Cassie, P.~Nguyen, M.~A.~Visser, K.~A.~Anirudha, and J.~Hill,
\emph{Observers Are All You Need},
OPH synthesis paper, release \OPHPaperReleaseID, 2026.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/observers_are_all_you_need.pdf}

\bibitem{ophconsensus}
B.~M\"uller, K.~Xue, K.~A.~Anirudha, and J.~Hill,
\emph{Reality as a Consensus Protocol},
OPH consensus paper, release \OPHPaperReleaseID, 2026.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/reality_as_consensus_protocol.pdf}

\bibitem{ophmicro}
B.~M\"uller and K.~Xue,
\emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer Synchronization in OPH},
OPH microphysics paper, release \OPHPaperReleaseID, 2026.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/screen_microphysics_and_observer_synchronization.pdf}

\bibitem{ophdark}
B.~M\"uller,
\emph{Observer-Patch Holography and the Dark Matter Phenomenon},
OPH cosmology paper, 2026.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/cosmology/oph_dark_matter_paper.pdf}

\bibitem{ophinflationdraft}
B.~M\"uller,
\emph{Inflation Without an Inflaton: Observer-Screen Synchronization as an OPH Cosmology Branch},
workspace cosmology draft, 2026.

\bibitem{ophsim}
B.~M\"uller,
\emph{OPH-FPE finite screen-consensus and cosmology diagnostics}.
\url{https://github.com/muellerberndt/oph-physics-sim}

\bibitem{planck2018}
Planck Collaboration,
\emph{Planck 2018 results. VI. Cosmological parameters},
Astron.\ Astrophys.\ 641, A6, 2020, arXiv:1807.06209.
\url{https://arxiv.org/abs/1807.06209}

\bibitem{camb}
A.~Lewis, A.~Challinor, and A.~Lasenby,
\emph{Efficient computation of CMB anisotropies in closed FRW models},
Astrophys.\ J.\ 538, 473--476, 2000, arXiv:astro-ph/9911177.
\url{https://arxiv.org/abs/astro-ph/9911177}

\bibitem{class}
D.~Blas, J.~Lesgourgues, and T.~Tram,
\emph{The Cosmic Linear Anisotropy Solving System (CLASS). Part II: Approximation schemes},
JCAP 07, 034, 2011, arXiv:1104.2933.
\url{https://arxiv.org/abs/1104.2933}

\end{thebibliography}

\end{document}
