\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,array,longtable}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xurl}

\IfFileExists{paper/release_info.tex}{
  \input{paper/release_info.tex}
}{
  \IfFileExists{../paper/release_info.tex}{
    \input{../paper/release_info.tex}
  }{
    \newcommand{\OPHPaperReleaseID}{r1518}
    \newcommand{\OPHPaperReleaseDate}{July 7, 2026}
    \newcommand{\OPHPaperReleaseBanner}{%
      \begin{center}
      \small\textbf{Paper release:} \texttt{\OPHPaperReleaseID}\quad\textbf{Released:} \OPHPaperReleaseDate
      \end{center}}
  }
}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.08}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{target}[theorem]{Target}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\theoremstyle{plain}

\newcommand{\pathref}[1]{\nolinkurl{#1}}
\newcommand{\SimSourceRepo}{\url{https://github.com/muellerberndt/oph-physics-sim}}

\title{OPH Cosmology Data and Likelihood Contracts:\\
Frozen Sources, No-Data-Use Receipts, and Comparable Predictions}
\author{B.\ M\"uller}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{abstract}
OPH cosmology can be compared with the sky only after its inputs are fixed. This
paper states the comparison contract for CMB, BAO, supernova, weak-lensing,
growth, and large-scale-structure data.

A close visual overlay or a good binned curve is a diagnostic. A prediction
requires source data fixed before the comparison, declared solver settings, a
frozen likelihood run, pooled statistics, and a falsification rule. The point is
to keep a simulator resemblance from being promoted into a sky prediction by
name alone.  Applying that contract to the first audited RAR, BTFR, Cassini,
and scalar-tilt comparisons yields encouraging conditional checks, one excluded
universal static extension, one negative finite-clock diagnostic, and no frozen
physical-prediction receipts.
\end{abstract}

\section{Scope}

This is a technical companion outside the release bundle. It sets the data and
likelihood boundary for CMB/CAMB comparisons, other cosmological data products,
and visualizer payload provenance emitted by the OPH-FPE simulator.

\section{Shared Finite Quotient and Claim Tiers}

\input{../paper/tex_fragments/FINITE_QUOTIENT_ENSEMBLE_THEOREMS.tex}

\section{E5 Prediction Contract}

An observable cosmological prediction requires all source artifacts to be fixed before likelihood
comparison.  The minimum contract is:
\begin{enumerate}[leftmargin=2em]
\item immutable hashes for OPH source artifacts, schema versions, and regulator manifests;
\item immutable scale-bridge hashes for the generation, geometry, background, clock, scale
certificate, source embedding, mode basis, mode lineage, boundary condition, solver convention,
freezeout surface, and source DAG;
\item immutable hashes for Boltzmann solver source, version, tolerances, inputs, and build
environment;
\item immutable hashes for likelihood code, datasets, masks, covariances, and nuisance-prior
definitions;
\item a no-data-use manifest showing that likelihood values did not enter source artifact
generation;
\item global pooled reducers for nonlinear source estimates;
\item a fixed falsification rule and reporting template before executing the likelihood.
\end{enumerate}
A source-only anomaly abundance belongs to the source-artifact layer.  It must be
frozen before the Boltzmann run and before likelihood comparison.

\begin{definition}[proof-carrying data artifact]
A data-facing artifact is not represented by a value plus a receipt Boolean.  It is a typed object
\[
  \mathfrak A_v=(id_v,\tau_v,x_v,\mathcal X_v,\mathcal U_v,Par(v),
  \mathcal D_v,\mathcal E_v,h_v^{\rm thm},h_v^{\rm wit},
  h_v^{\rm build},h_v^{\rm art}),
\]
where \(\tau_v\) is the semantic type, \(\mathcal X_v\) records axes, domain, grid, and support,
\(\mathcal U_v\) records units, gauge, frame, pivots, and conventions, \(Par(v)\) is the complete
parent set, \(\mathcal D_v\) is the data-class ledger, \(\mathcal E_v\) is the error envelope, and
the four hashes commit to the theorem version, witness, build environment, and artifact payload.
All hashes are content-addressed commitments, not display labels.
\end{definition}

\begin{definition}[scale-bridge cross-receipt manifest]
The physical scale bridge supplies a nonempty cross-receipt manifest.  Every child receipt repeats
the same regulator-family id, generation id, geometry hash, background hash, clock hash,
scale-certificate hash, source-embedding hash, mode-basis hash, mode-lineage hash,
boundary-condition hash, solver-convention hash, freezeout-surface hash, and source-DAG hash.
An empty manifest or a missing identity field fails before likelihood execution.
\end{definition}

\begin{theorem}[no receipt-Boolean promotion]
Let \(G\) be the finite acyclic graph of data-facing artifacts.  If every node verifier recomputes
its predicate from its artifact, witness, complete parent set, data ledger, and error envelope, then
a passed \textsc{PhysicalCMBPrediction} node implies that every required source, solver, likelihood,
and no-data-use parent predicate also holds.  In particular, caller-supplied receipt Booleans cannot
promote an artifact across a semantic type boundary.
\end{theorem}

\begin{proof}
Topologically order \(G\).  A root passes only when its verifier recomputes the corresponding
predicate from the committed artifact and witness.  A non-root node additionally requires every
parent to pass.  Induction gives all parent predicates and the local predicate at each passing node.
A Boolean supplied by the producer is merely input data unless it is itself recomputed by such a
verifier.
\end{proof}

The promotion order used by this paper is
\[
  \begin{aligned}
  \textsc{DiagnosticProxy}
  &\prec \textsc{FiniteScreenSource}
  \prec \textsc{FinitePrimordialSource}\\
  &\prec \textsc{PhysicalBoltzmannSource}
  \prec \textsc{PhysicalCMBPrediction}.
  \end{aligned}
\]
No simulator export may jump over an intermediate node by relabelling a diagnostic scalar as a
physical function.

The coherent-matter same-channel theorem fixes a local scalar-channel identity:
\[
S_{\rm coh}^{\rm can}
=\mathbf 1_{\rm self\mbox{-}read}R_UP_UC_U\in\mathcal E_{r,C}
\]
for nondegenerate OPH-coherent material sources under Scalar Edge-Center
Exhaustion. That identity is insufficient for a physical dark/anomaly row in a
likelihood contract. Physical promotion also requires the finite covariant
parent to emit \(w_A\), \(c_{s,A}^2\), \(\sigma_A\), \(Q_A^\mu\),
exchange-current closure, recipient stress, gauge-independent variables,
CDM-limit recovery, and refinement convergence.

\section{Finite Primordial Source Artifact}

The CMB-facing source object is
\[
\mathfrak S_r^{\rm prim}=
(\mathcal Q_r,n_r,\mu_r,q_r,J_r,\Pi_r,K_r,M_r,\Xi_r,\Sigma_r,
E_r^{\rm rel},A_{q,r},\theta_r,q_{{\rm IR},r},t_{{\rm IR},r},
\Sigma_{\star,r},W_r,\Delta_{\zeta,r}^2,\mathcal P_{IJ,r},\mathcal E_r).
\]
Here \(\mathcal Q_r\) is the quotient state space, \(n_r\) the normal-form map, \(\mu_r\) the
source law, \(q_r\) the quotient-visible scalar source, \(J_r\) the weighted carrier-to-harmonic
readout, \(\Pi_r\) the projector removing gauge, monopole, and dipole directions, \(K_r\) a
positive precision operator, \(M_r\) a mobility or repair-response operator, \(\Xi_r\) the
stochastic forcing covariance, and \(\Sigma_r=\operatorname{Cov}_{\mu_r}(q_r)\).  The remaining
entries record release energy, amplitude, spectral exponent, infrared suppression, freezeout cut,
radial window, lifted primordial spectrum, species covariance, and errors.

The old shorthand ``screen count plus fitted scalar curve'' is therefore only a diagnostic proxy.
It does not determine amplitude, tilt, infrared suppression, species covariance, or physical
Boltzmann inputs without the source artifact above.

\section{Comparable Data Lanes}

\begin{longtable}{@{}p{0.25\textwidth}p{0.30\textwidth}p{0.35\textwidth}@{}}
\toprule
Lane & Allowed diagnostic output & E5 promotion blocker\\
\midrule
\endhead
\bottomrule
\endfoot
CMB TT/TE/EE/lensing & Binned overlays, CAMB/CLASS scaffolds, peak metrics & Missing frozen
source, Boltzmann, official likelihood, or no-data-use receipt.\\
BAO/SN/\(H_0\) & Distance-ladder and background-expansion diagnostics & Missing physical scale
bridge and frozen background source functions.\\
Weak lensing and growth & Diagnostic \(S_8\), growth, and lensing comparisons & Missing global
stress closure, dark/anomaly kernels, and covariance-ready likelihood.\\
Large-scale structure & Prototype transfer/growth tables & Missing source-only primordial and
growth-seed receipts.\\
Visualizer payloads & Observer cameras, screen fields, object/worldline diagnostics & Missing claim
receipts; visual rendering is not a likelihood.\\
\end{longtable}

\section{Round-One Audited Comparison Ledger}

The first cross-domain audit applies the claim tiers above to the public
comparison surfaces already executable without a new observer simulation.  It
does not define a cross-domain score and reports zero frozen physical-prediction
receipts.  The ledger discipline instantiates rules 2 and 7 of
\pathref{../docs/STRANGE\_LOOP\_PRINCIPLES.md}: closure residuals are recorded exactly, and executed
verdicts are permanent.

\begin{longtable}{@{}p{0.19\textwidth}p{0.20\textwidth}p{0.25\textwidth}p{0.27\textwidth}@{}}
\toprule
Surface & Evidence class & Audited result & Interpretation \\
\midrule
\endhead
\bottomrule
\endfoot
Analytic \(P_\star/48\) tilt & Conditional analytic diagnostic &
\(n_s=0.9660214956\), \(+0.267\sigma\) from the Planck summary; CAMB with one
profiled amplitude gives \(\chi^2/N_{\rm bin}=0.954498\), baseline \(0.944496\),
and total diagonal \(\Delta\chi^2=+0.8302\) over 83 PR3 TT bins &
Analytic candidate, not lattice-derived, \(\kappa_{\mathrm{rep}}\) certificate
pending; two candidate tilt formulas are on record with the selection
uncounted, so the \(0.267\sigma\) comparison is a basin location, not a hit.
Not an official likelihood or a physical-prediction receipt;
the source theorem, amplitude, radial lift, and background inputs remain open
or imported.\\
Simulation-clock TT & Diagnostic proxy &
\(\chi^2/N_{\rm bin}=1.41749\), baseline \(0.94450\), total diagonal
\(\Delta\chi^2=+39.26\) &
Negative for the uncertified \(n_s=0.9789308\) finite-clock diagnostic.  This is
not the analytic \(1-P_\star/48\) branch.\\
Fixed \(\mathbb Z_6\) RAR & Retrospective fixed-formula comparison &
Aggregate RMS \(0.1328335\) dex; unit branch \(0.1342082\) dex; same-data
effective-scale optimum \(0.1329467\) dex on 2,693 rows from 153 galaxies &
Positive formula/scale check.  The response function is the
McGaugh--Lelli--Schombert empirical fit trained on SPARC, so the comparison is
non-held-out; the coefficient provenance is
benchmark-derived and conditional, and the aggregate rows do not support a
formal nuisance-marginalized significance.\\
BTFR slope and normalization & Overlapping-sample external table &
Error-aware slope \(3.845654\pm0.085817\); slope \(4\) differs by \(1.80\sigma\).
At \(100\,\mathrm{km\,s^{-1}}\), the fixed \(\mathbb Z_6\) normalization is
\(0.134763\) dex high, or \(6.47\sigma\) statistical-only &
Positive slope check and unresolved normalization pressure.  The old
unweighted slope \(3.4863\) and \(0.9469\)-dex intercept mismatch are
superseded because they discarded both-axis errors and compared unequal-slope
intercepts at \(1\,\mathrm{km\,s^{-1}}\).\\
Cassini external-field quadrupole & Conditional external-domain falsifier &
\(Q_2=3.62018\times10^{-26}\,\mathrm{s^{-2}}\) for the conditional
\(\mathbb Z_6\) branch, a \(19.22\sigma\) fixed-input residual; \(10.71\sigma\)
after adding only the linearized Gaia external-field uncertainty &
Strong exclusion of universal/full-source application of the static galaxy
equation.  The settled-galaxy paper scope lacks a Solar-System applicability
receipt, so the result is a hard missing gate rather than a recovered-core
falsification.\\
Compressed cosmology & Invalidated &
Archived diagonal values \(11.4633\), \(9.5504\), and \(6.2852\) &
Hard-coded constants, no attached covariance, correlated compressed variables,
and a rejected neutrino input; excluded from evidence.\\
\end{longtable}

The ledger establishes a useful asymmetry.  A larger observer run can refine
the finite source and clock receipts, but it cannot retroactively promote the
fixed RAR/BTFR comparisons or repair the Cassini applicability gap.  Those need
new source mathematics, a disk or lensing forward model, and frozen nuisance
likelihoods.  Conversely, the analytic \(P_\star/48\) check can be advanced to
official Planck and ACT likelihoods without another observer simulation, while
retaining its conditional source status.

\section{Simulator Contract}

Every data-facing export should carry:
\begin{itemize}[leftmargin=2em]
\item \pathref{NO_DATA_USE_RECEIPT}
\item \pathref{SOURCE_PROVENANCE_RECEIPT}
\item \pathref{POOLED_SOURCE_REDUCER_RECEIPT}
\item \pathref{BOLTZMANN_TRANSFER_RECEIPT}
\item \pathref{FROZEN_LIKELIHOOD_RECEIPT}
\item \pathref{PHYSICAL_CMB_PREDICTION_RECEIPT}
\end{itemize}
The receipt may be false.  False is preferable to silently promoting a diagnostic curve.

\section{Adversarial Contract Rejections}

A conforming simulator contract must fail closed on the following cases.
\begin{enumerate}[leftmargin=2em]
\item negative or out-of-domain source parameters such as \(q_{\rm IR}<0\), missing freezeout
surfaces, one-character hashes, and \(1\times1\) zero kernels;
\item child artifacts declaring \pathref{source_only=true} while any transitive parent is
measurement-fit, likelihood-fit, hand-tuned after looking at data, or outside the hermetic read set;
\item local shard averages used as nonlinear global reducers;
\item defaulting a single source row to a global pooled reducer when no pooled reducer receipt was
constructed;
\item accepting arbitrary labels such as ``anomaly'' or ``recipient'' as physical stress rows
without a finite covariant parent and stress/exchange closure receipt;
\item promoting temporal repair gaps, spatial refinement exponents, primordial tilt, and physical
exchange rates as if they were the same semantic type.
\item accepting a source-only \(\rho_A\) or \(\Omega_A\) claim unless
\texttt{RHO\_A\_SOURCE\_RECEIPT} passes;
\item accepting a \texttt{RHO\_A\_SOURCE\_RECEIPT} whose receipt decomposition is anything other
than
\texttt{RHO\_A\_TRANSPORT\_RECEIPT} plus
\texttt{ANOMALY\_ABUNDANCE\_SOURCE\_RECEIPT};
\item accepting an \texttt{ANOMALY\_ABUNDANCE\_SOURCE\_RECEIPT} whose load observable is
computed from an amplitude-loaded parent occupation field normalized by an external \(\Omega_A\),
Planck residual, SPARC fit, cluster fit, Boltzmann residual, or likelihood comparison;
\item accepting an anomaly abundance selector whose source DAG reads CMB, BAO, supernova,
weak-lensing, RSD, SPARC, cluster, posterior, likelihood, nuisance-fit, or diagnostic residual
data;
\item accepting a selector whose release law lacks a quotient-intrinsic ensemble law or source
MaxEnt constraint ledger;
\item accepting a selector whose refinement defect exceeds the declared
\texttt{LOAD\_REFINEMENT\_COMPATIBILITY} tolerance;
\item accepting a selector whose hidden carrier coordinates, port labels, repair schedules, or
worker metadata change \(\mathsf L_A\).
\end{enumerate}

The no-data-use verifier must traverse the complete parent graph, including file reads, network
reads, environment variables, configuration values, caches, random seeds, dependency versions, and
human-selected branch identifiers.  A missing channel is a blocker.

\section{Unclosed Claim Boundaries}

\begin{enumerate}[leftmargin=2em]
\item Implement the finite primordial source artifact schema and verifier in the simulator.
\item Specify official likelihood readiness for Planck, ACT, BAO, SN, weak lensing, and growth
lanes.
\item Make pooled reducers the only allowed source of nonlinear global quantities.
\item Define the falsification thresholds before running any public comparison.
\end{enumerate}

\end{document}
