\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,array,longtable}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xurl}

\IfFileExists{paper/release_info.tex}{
  \input{paper/release_info.tex}
}{
  \IfFileExists{../paper/release_info.tex}{
    \input{../paper/release_info.tex}
  }{
    \newcommand{\OPHPaperReleaseID}{r1518}
    \newcommand{\OPHPaperReleaseDate}{July 7, 2026}
    \newcommand{\OPHPaperReleaseBanner}{%
      \begin{center}
      \small\textbf{Paper release:} \texttt{\OPHPaperReleaseID}\quad\textbf{Released:} \OPHPaperReleaseDate
      \end{center}}
  }
}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.08}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{target}[theorem]{Target}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\theoremstyle{plain}

\newcommand{\OPH}{\mathrm{OPH}}
\newcommand{\LCDM}{\Lambda\mathrm{CDM}}
\newcommand{\Zsix}{\mathbb Z_6}
\newcommand{\pathref}[1]{\nolinkurl{#1}}
\newcommand{\SimSourceRepo}{\url{https://github.com/muellerberndt/oph-physics-sim}}

\title{Inflation Without an Inflaton:\\
Observer-Screen Synchronization as an OPH Cosmology Branch}
\author{B.\ M\"uller}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{abstract}
OPH cosmology replaces the inflaton with finite observer-screen
synchronization. Flatness, horizon coherence, near scale invariance, hot source
release, and acoustic-transfer inputs are treated as jobs for the finite screen
state rather than for a new scalar field.

The branch is conditional. Screen spectra, repair gaps, release amplitudes, and
dark-sector inputs become physical cosmological inputs only after the source
law, radial lift, transfer calculation, and likelihood comparison are fixed.
Without that chain, simulator outputs are diagnostics.
\end{abstract}

\section{Scope}

This is a technical companion outside the release bundle. It states the
inflation-free branch against the compact, screen-microphysics, dark-sector,
and finite-source CMB papers.

\section{Finite Quotient and Claim-Tier Firewall}

\input{../paper/tex_fragments/FINITE_QUOTIENT_ENSEMBLE_THEOREMS.tex}

\input{../paper/tex_fragments/SCREEN_SPECTRUM_THEOREMS.tex}

\section{Branch Thesis}

The branch claim is:
\[
\boxed{
\begin{gathered}
\text{On a finite-source branch, OPH may replace the logical jobs of}\\
\text{inflation by direct/CMH spatial-holonomy selection, same-boundary or low-}k\text{ repair coherence,}\\
\text{a geometric screen spectrum, MaxEnt release, and ordinary Boltzmann transfer.}
\end{gathered}}
\]
This claim is not part of the recovered SM/GR core.  It becomes predictive only when the source
objects are fixed before observational comparison.
Screen synchronization instantiates C3 of the project consistency stack:
modular self-consistency, with internal time generated by the state--algebra
pair rather than by an external clock.

Coherent-matter same-channel forcing supplies a local scalar-channel identity for
nondegenerate OPH-coherent material sources under Scalar Edge-Center Exhaustion.
It does not supply the finite covariant dark-stress parent needed for
cosmological \(w_A\), \(c_{s,A}^2\), \(\sigma_A\), \(Q_A^\mu\),
recipient-stress, gauge-variable, CDM-limit, and refinement-convergence
receipts.

The anomaly abundance selector is owned by
\pathref{cosmology/oph_dark_matter_paper.tex}.  The finite-source branch may
use a source-only \(\bar\rho_A(a)\) only when
\[
\texttt{ANOMALY\_ABUNDANCE\_SOURCE\_RECEIPT}
\]
passes.  Otherwise the dark continuation is either \(\texttt{OFF}\) or
\(\texttt{CONDITIONAL\_SOURCE\_STATE}\).

\section{Paper Targets}

\begin{longtable}{@{}p{0.28\textwidth}p{0.62\textwidth}@{}}
\toprule
Target & Required theorem or receipt\\
\midrule
\endhead
\bottomrule
\endfoot
Finite early state & Quotient normal-form branch with declared base measure and implementation
invariance.\\
Flatness & Zero clock-slice spatial Levi--Civita holonomy identifies \(\kappa=0\). Exact selection
requires \textsc{DirectTheorem}, \textsc{ConditionalCMH}, or \textsc{ExplicitAssumption}; damping
is only an approximate \(|K|\) or \(|\Omega_K|\) bound.\\
Horizon coherence & Same-boundary unique-extension theorem or a uniform low-\(k\) repair gap.\\
Near scale invariance & Geometric screen scalar, normalized scalar precision, source release
energy, refinement tilt, and angular screen-spectrum receipts.\\
Amplitude & Source release-energy certificate for \(A_q\), followed by a separate radial lift for
\(A_\zeta\); neither may be fitted from CMB data.\\
Hot start & MaxEnt release into the realized radiation branch with a common release clock.\\
Acoustic transfer & Declared source functions and Boltzmann transfer owned by the finite-source CMB
and data-contract papers.\\
\end{longtable}

\section{Simulator Contract}

The simulator reference is \SimSourceRepo.  For this paper the simulator may emit diagnostic
screen spectra, observer-screen synchronization receipts, and release-amplitude candidates.  It
must not label them inflation replacement, OPH primordial field, or physical CMB prediction unless
the E4 and E5 receipts in the shared theorem fragment pass in the concrete run bundle.

\section{Flatness Boundary}

The flatness branch is split into identification and selection.  On a clocked FLRW continuation
with \(u_a=-N\nabla_a\chi\), \(h_{ab}=g_{ab}+u_au_b\), and
\(K(\tau)=\kappa/a(\tau)^2\), the area-normalized small-loop holonomy of the spatial
Levi--Civita connection identifies \(K=0\) and hence \(\kappa=0\).  It does not select that sector
from the raw FLRW fiber.  The simulator must therefore report one of
\(\textsc{DirectTheorem}\), \(\textsc{ConditionalCMH}\), \(\textsc{ExplicitAssumption}\), or
\(\textsc{OpenTheorem}\).  S3 screen/collar defect decay is a repair diagnostic, not a spatial
curvature holonomy.  Curvature damping can certify only an \(\textsc{ApproximateBound}\) on
\(|K|\) or \(|\Omega_K|\).

\section{Screen-Spectrum Branch}

The load-bearing screen result is the angular screen covariance, not a CMB spectrum:
\[
  C_\ell^q
  =
  A_q\frac{\Gamma(\ell-\theta/2)}{\Gamma(\ell+2+\theta/2)}.
\]
This statement requires the geometric \(q_r\) of Definition~\ref{def:oph-screen-scalar}, a
normalized positive precision operator \(K_r\), a source-only release ensemble and
\(E^{\rm src}_{q,r}\), the MaxEnt covariance theorem, and a finite-to-continuum refinement error
budget.  The value \(\theta=P_\star/48\) is theorem-grade only if the edge-center reserve,
half-collar scalar projection, and reserve-to-RG Ward identity in
Target~\ref{target:oph-p-over-48-tilt} pass.  Otherwise \(P_\star/48\) and
\(e(P_\star-\varphi)\) are distinct diagnostic hypotheses.  Canonical status
for the resulting tilt \(n_s=1-\theta\): analytic candidate, not
lattice-derived, \(\kappa_{\mathrm{rep}}\) contraction certificate pending;
two candidate formulas are on record and the selection between them is
uncounted, so the \(0.27\sigma\) Planck comparison of the \(P_\star/48\)
branch is a basin location, not a hit.

The primordial power law
\[
  \Delta_\zeta^2(k)=A_\zeta\left(\frac{k}{k_\star}\right)^{-\theta}
\]
enters this paper only after the thin-shell or finite-window lift fixes \(R_\star\), \(Z_\star\),
the radial window, the null-space report, the forward-projection residual, and the amplitude
conversion from \(A_q\) to \(A_\zeta\).  A screen theorem by itself does not prove TT, TE, EE,
lensing, acoustic peaks, or an official likelihood result.

\section{Unclosed Claim Boundaries}

\begin{enumerate}[leftmargin=2em]
\item Prove the same-boundary or low-\(k\) coherence branch in quotient language.
\item Replace diagnostic feature-weight scalar readouts with the geometric collar-volume
\(q_r=\Pi_{\ge2,r}(1/3)\log(J_{X,r}/\bar J_{X,r})\).
\item Specify the source-release-energy certificate for \(A_q\) without CMB data use.
\item Prove or bound the refinement source of \(\theta\), including the separate \(P_\star/48\)
edge-center reserve lemmas if that branch is retained.
\item Connect the synchronized release state to the source-only primordial bridge.
\item Hand the resulting source inputs to the CMB and likelihood-contract papers.
\end{enumerate}

\end{document}
