\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,array,longtable}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xurl}

\IfFileExists{paper/release_info.tex}{
  \input{paper/release_info.tex}
}{
  \IfFileExists{../paper/release_info.tex}{
    \input{../paper/release_info.tex}
  }{
    \newcommand{\OPHPaperReleaseID}{r1529}
    \newcommand{\OPHPaperReleaseDate}{July 11, 2026}
  }
}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\emergencystretch}{3em}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\Dd}{\mathrm{d}}
\newcommand{\ah}{\frac{\dot a}{a}}
\newcommand{\kdot}{\dot\kappa}

\title{Boltzmann Transport from Observer-Patch Consistency:\\
a Theorem-Conditional Reduction}
\author{OPH cosmology program}
\date{Release \texttt{\OPHPaperReleaseID}\ --- \OPHPaperReleaseDate}

\begin{document}
\maketitle

\begin{abstract}
This note derives the general-relativistic photon--baryon Boltzmann transport
used in CMB computations \emph{inside} the OPH branch, as a theorem-conditional
reduction: given the Einstein-branch geometry theorem, the recovered
$\mathrm U(1)$ electromagnetic sector, the independently assumed Maxwell action
and positive-residue physical photon pole, and the reversible repair-register
structure, the observer-facing photon record dynamics obeys the standard
Liouville equation with the Thomson collision functional, and its linearization
on the capacity-closure FRW background is exactly the standard multipole
hierarchy. OPH does not modify radiative transfer at first order; it
\emph{inherits} it. The value of the derivation is provenance: it identifies
precisely (i) which OPH theorems supply each ingredient, (ii) the two places
where OPH-specific kernels could enter (a number-changing repair-exchange
channel $\Gamma_{\rm rec}$ and a collar-packet stress $B_A$), and (iii) the
irreducible imports (absolute electron mass, recombination history) that any
honest physical-CMB receipt must declare. One new finite-lattice receipt
(\textsc{Boltz-R1}, refinement Liouville) is defined and is testable in the
public simulator. This note does not close the physical CMB prediction gate;
it reduces that gate to a finite, named list.
\end{abstract}

\section{Claim boundary}
Everything below is conditional on the branch theorems it cites. The
derivation upgrades the status of the \emph{transport form} used by the
diagnostic CAMB lane from ``imported wholesale'' to ``theorem-conditional
reduction with declared imports.'' It does not certify the initial spectrum
(amplitude or tilt), the recombination history, the absolute Thomson
normalization, or any likelihood statement. Those remain the gates tracked in
issues \#330, \#522, \#374, and \#363 respectively. No statement in this note
reads Planck data.

\section{Branch inputs}

\begin{assumption}[A-GEOM: Einstein branch]\label{a:geom}
The observer-facing normal form carries a Lorentzian metric $g_{ab}$
satisfying $G_{ab}+\Lambda g_{ab}=8\pi G_{\rm geom}\langle T_{ab}\rangle$,
with $G_{\rm geom}=\ell_\star^2$ from the edge-entropy/area-law theorem and
$\Lambda\ell_\star^2=3\pi/N_\star$ from capacity closure. Provenance:
branch theorem (paper stack A22/A5); not re-proved here.
\end{assumption}

\begin{assumption}[A-QED: electromagnetic action and photon-pole receipt]\label{a:qed}
The realized branch carries the Standard Model quotient and the Maxwell
kinetic action with a $\mathrm U(1)$ vertex of strength
$\alpha=\alpha_{\rm root}$ (source-side). In addition, this transport note
assumes a positive-energy physical QED quantization with two transverse
states and a positive-residue isolated pole at $k^2=0$ on the ordinary
Lorentz-vacuum, unbroken electromagnetic phase. This extra photon-pole
receipt is not implied by the reconstructed abstract group. Charged-lepton
\emph{ratios} are branch outputs; the absolute electron mass $m_e$ is
empirically anchored. Provenance: branch theorem (A20/A21), the explicit
quantum-pole assumption just stated, and one declared import ($m_e$).
\end{assumption}

\begin{assumption}[A-BG: background]\label{a:bg}
The homogeneous limit of the branch is spatially flat FRW,
$\Dd s^2=a^2(\tau)\,[-\Dd\tau^2+\delta_{ij}\Dd x^i\Dd x^j]$, with Friedmann
dynamics from Assumption~\ref{a:geom}. Scalar perturbations are written in
the conformal Newtonian gauge,
\[
\Dd s^2=a^2(\tau)\left[-(1+2\psi)\,\Dd\tau^2+(1-2\phi)\,\delta_{ij}\Dd
x^i\Dd x^j\right],
\]
with conventions of Ma--Bertschinger (1995). Overdots are $\partial_\tau$.
\end{assumption}

\begin{assumption}[A-REC: recombination import]\label{a:rec}
The free-electron history $n_e(\tau)$ (equivalently $x_e(\tau)$) is computed
from standard atomic physics (Saha/Peebles-class) using imported atomic data.
This is the same import class as the cesium-clock wall in the gravity stack:
it contains no CMB-target information, so it is a permissible declared input
under the anti-fitting rule, but it is an import, not a branch output.
\end{assumption}

\begin{assumption}[A-INIT: initial conditions (gated)]\label{a:init}
Initial curvature perturbations $\zeta(\mathbf k)$ are Gaussian with spectrum
$\Delta^2_\zeta(k)=A_s\,(k/k_\ast)^{\,n_s-1}$. The Gaussian and
statistically isotropic character is the MaxEnt screen-covariance theorem;
the tilt certificate is issue \#522; the amplitude and the radial
screen-to-$k$ lift are issue \#330. This note treats $A_s$, $n_s$ as gated
inputs and derives nothing about them.
\end{assumption}

\section{Theorem B1: reversible repair gives Liouville transport}

\begin{definition}[One-photon record density]
Conditional on the physical pole in Assumption~\ref{a:qed}, let
$\mathcal E_\gamma$ be its positive-energy photon sector. Between record
commits, a single excitation is a record continued
across patch overlaps. Coarse-graining patch position and overlap momentum
labels defines the phase-space record density $f(x^i,q,\hat n,\tau)$ on the
forward mass shell, where $q$ is comoving momentum magnitude and $\hat n$ the
direction.
\end{definition}

\begin{theorem}[Refinement Liouville]\label{t:liouville}
On a branch passing the simulation test, with (i) the Maxwell action,
quantum photon-pole receipt, and overlap Lorentz kinematics (A-QED, A-GEOM),
and (ii) repair
moves organized in reversible write/check pairs (the orientation doubling in
$m_{\rm rep}=2\dim(\mathfrak{su}(3)\oplus\mathfrak{su}(2)\oplus\mathfrak
u(1))=24$), the between-commit record flow satisfies, in the refinement
limit,
\[
\frac{Df}{\Dd\tau}\;\equiv\;
\frac{\partial f}{\partial\tau}
+\frac{\Dd x^i}{\Dd\tau}\frac{\partial f}{\partial x^i}
+\frac{\Dd q}{\Dd\tau}\frac{\partial f}{\partial q}
+\frac{\Dd\hat n}{\Dd\tau}\cdot\frac{\partial f}{\partial\hat n}
\;=\;C[f],
\]
where the characteristics are the null geodesics of $g_{ab}$ and $C[f]$ is
supported on record commits only. In particular the collisionless flow
preserves the Liouville measure.
\end{theorem}

\begin{proof}[Proof sketch, with the open receipt named]
\emph{Characteristics.} A single-excitation record continued across an
overlap must agree with both patches' readouts; by overlap Lorentz kinematics
the unique continuation consistent with all overlapping patches is parallel
transport along the branch metric's null geodesic. Any other continuation
produces a nonzero overlap mismatch, which the repair fixed point sets to
zero; schedule independence (confluence) makes the continuation unique and
schedule-free. Hence $\Dd x/\Dd\tau$, $\Dd q/\Dd\tau$, $\Dd\hat n/\Dd\tau$
are the geodesic-flow coefficients; on the background of
Assumption~\ref{a:bg}, $\Dd q/\Dd\tau=q[\dot\phi-\ldots]$ takes the standard
form used in \S\ref{s:hierarchy}.

\emph{Measure preservation.} Each repair move is a write/check pair: a
bijection on the finite record configuration space with an explicit inverse
(this is what the orientation doubling tracks). A finite composition of
bijections has unit Jacobian on the induced finite phase space, for every
schedule; confluence makes the endpoint schedule-independent, so the
coarse-grained flow inherits unit Jacobian. The refinement limit of a
sequence of unit-Jacobian flows converging to the geodesic flow preserves the
Liouville measure.

\emph{Open receipt.} The convergence step --- that the finite patch flow's
coarse-graining converges to the geodesic flow with vanishing dispersion ---
is exactly the kind of statement the abstract Lean layer proves in its
setting (approximate schedule independence, refinement naturality) but has
not been instantiated for the photon sector. We name it \textsc{Boltz-R1}
and give a simulator test in \S\ref{s:receipts}. Until \textsc{Boltz-R1} is
discharged, Theorem~\ref{t:liouville} is theorem-conditional.
\end{proof}

\begin{remark}
The physical content is that \emph{irreversibility enters only at commits}.
Free streaming is unitary bookkeeping; entropy production is localized in the
record-commit events that the collision functional counts. This is the
transport-level face of the general OPH position that measurement-like
irreversibility lives at the record interface.
\end{remark}

\section{Theorem B2: record commits give the Thomson collision functional}

\begin{theorem}[Commit-collision functional]\label{t:collision}
Let commits between photon-class and electron-class records occur with the
soft-limit matrix element of the recovered $\mathrm U(1)$ vertex (A-QED).
Then, to first order in perturbations and at low occupancy, the collision
functional in Theorem~\ref{t:liouville} is the Thomson functional: in the
electron rest frame,
\[
C[f](\hat n)\;=\;a\,n_e\sigma_T\left[
\frac{3}{16\pi}\int \Dd\Omega'\,(1+(\hat n\cdot\hat n')^2)\,f(\hat n')
- f(\hat n)\right],
\qquad
\sigma_T=\frac{8\pi}{3}\frac{\alpha^2}{m_e^2},
\]
boosted to the frame where baryons move with velocity $v_b$. Moreover the
write/check reversibility of commits implies detailed balance of the commit
kernel, so the unique isotropic stationary point of $C$ at fixed photon
number is the Planck occupancy: the blackbody spectrum is the repair
equilibrium of the record dynamics.
\end{theorem}

\begin{proof}[Proof sketch]
At low occupancy the commit rate between momentum cells is bilinear in the
occupancies with kernel given by the squared vertex; the soft
(photon energy $\ll m_e$) limit of the recovered $\mathrm U(1)$ vertex is
classical Thomson scattering with the stated total cross-section and
$1+\cos^2$ angular kernel; this step is standard QED evaluated on the branch
couplings and is not repeated here. Detailed balance: a write/check pair and
its orientation reverse implement the commit and its inverse with equal
kernel weight; a symmetric kernel yields an $H$-theorem for the commit
dynamics, and the stationary condition at fixed number is the Bose
equilibrium occupancy. Momentum conservation per commit, summed over
commits, gives equal and opposite momentum transfer densities to the
electron--baryon fluid, with coefficient fixed by
$\bar\rho_\gamma/\bar\rho_b$ bookkeeping; this is the Compton drag used in
\S\ref{s:hierarchy}.
\end{proof}

\begin{remark}[Provenance of the normalization]
$\alpha=\alpha_{\rm root}$ is source-side. $m_e$ is an import
(Assumption~\ref{a:qed}): OPH currently derives charged-family
\emph{ratios}, not the absolute scale, so $\sigma_T$'s normalization is
import-tagged (\textsc{Boltz-N1} in the ledger). $n_e(\tau)$ is
import-tagged by Assumption~\ref{a:rec} (\textsc{Boltz-X1}).
\end{remark}

\begin{remark}[OPH-specific channels]\label{r:channels}
Two and only two places exist where OPH kernels can modify this functional
at linear order:
(i) a number-changing repair-exchange channel $\Gamma_{\rm rec}(k,a)$ adds a
monopole source and a spectral-distortion term --- it enters $C[f]$
additively and is gated by the \#374 receipts (active fiber, physical clock,
common-parent response);
(ii) a collar-packet stress $\rho_A,B_A(k,a)$ enters only the gravitational
source side (the Einstein constraints in \S\ref{s:hierarchy}), never $C[f]$.
With both gates closed at zero, the transport below is exactly standard.
\end{remark}

\section{Theorem B3: the linear multipole hierarchy}\label{s:hierarchy}

\begin{theorem}[Reduction to the standard hierarchy]\label{t:hierarchy}
Linearize Theorems~\ref{t:liouville}--\ref{t:collision} on the background of
Assumption~\ref{a:bg} with scalar perturbations, expand the temperature
brightness $F_\gamma(\mathbf k,\hat n,\tau)$ and polarization brightness
$G_\gamma$ in Legendre multipoles with $\mu=\hat k\cdot\hat n$. Writing
$\delta_\gamma=F_{\gamma0}$, $\theta_\gamma=\tfrac34 kF_{\gamma1}$,
$\sigma_\gamma=\tfrac12F_{\gamma2}$, and $\kdot\equiv a n_e\sigma_T$, the
system is (Ma--Bertschinger 1995, eq.~63):
\begin{align*}
\dot\delta_\gamma &= -\tfrac43\theta_\gamma+4\dot\phi,\\
\dot\theta_\gamma &= k^2\!\left(\tfrac14\delta_\gamma-\sigma_\gamma\right)
+k^2\psi+\kdot\,(\theta_b-\theta_\gamma),\\
2\dot\sigma_\gamma &= \tfrac{8}{15}\theta_\gamma-\tfrac35 kF_{\gamma3}
-\tfrac95\kdot\,\sigma_\gamma
+\tfrac{1}{10}\kdot\,(G_{\gamma0}+G_{\gamma2}),\\
\dot F_{\gamma\ell} &= \frac{k}{2\ell+1}\left[\ell F_{\gamma(\ell-1)}
-(\ell+1)F_{\gamma(\ell+1)}\right]-\kdot F_{\gamma\ell},
\qquad \ell\ge3,\\
\dot G_{\gamma\ell} &= \frac{k}{2\ell+1}\left[\ell G_{\gamma(\ell-1)}
-(\ell+1)G_{\gamma(\ell+1)}\right]
+\kdot\left[-G_{\gamma\ell}
+\tfrac12\left(F_{\gamma2}+G_{\gamma0}+G_{\gamma2}\right)
\left(\delta_{\ell0}+\tfrac{\delta_{\ell2}}{5}\right)\right],
\end{align*}
coupled to baryons,
\[
\dot\delta_b=-\theta_b+3\dot\phi,\qquad
\dot\theta_b=-\ah\theta_b+c_b^2k^2\delta_b+k^2\psi
+\frac{4\bar\rho_\gamma}{3\bar\rho_b}\,\kdot\,(\theta_\gamma-\theta_b),
\]
and to the Einstein constraints of Assumption~\ref{a:geom},
\[
k^2\phi+3\ah\!\left(\dot\phi+\ah\psi\right)=-4\pi G a^2\,\delta\rho_{\rm tot},
\qquad
k^2(\phi-\psi)=12\pi G a^2(\bar\rho+\bar p)\sigma_{\rm tot},
\]
where $\delta\rho_{\rm tot}$ and $\sigma_{\rm tot}$ include the gated
$\rho_A,B_A$ contributions of Remark~\ref{r:channels} (zero until their
receipts pass). With $\Gamma_{\rm rec}=B_A=0$ this is verbatim the standard
Einstein--Boltzmann system.
\end{theorem}

\begin{proof}
Mechanical: insert the geodesic characteristics of
Theorem~\ref{t:liouville} on the perturbed metric, the collision functional
of Theorem~\ref{t:collision}, keep first order, and project on Legendre
multipoles. Every step is the textbook computation (Ma--Bertschinger 1995;
Dodelson, \emph{Modern Cosmology}); no OPH-specific term survives except the
two gated channels, which we have displayed at their unique insertion
points.
\end{proof}

\section{Acoustic normal form, damping, and the line of sight}

\begin{proposition}[Acoustic oscillations]\label{p:acoustic}
In the tight-coupling regime $\kdot\gg k,\ \ah$, define
$R\equiv 3\bar\rho_b/4\bar\rho_\gamma$ and $\Theta_0=\delta_\gamma/4$. To
leading order in $1/\kdot$,
\[
\frac{\Dd}{\Dd\tau}\!\left[(1+R)\,\dot\Theta_0\right]
+\frac{k^2}{3}\,\Theta_0
=-\frac{k^2}{3}(1+R)\,\psi
+\frac{\Dd}{\Dd\tau}\!\left[(1+R)\,\dot\phi\right],
\]
a driven oscillator with sound speed $c_s^2=1/[3(1+R)]$. The WKB solution
gives, at last scattering $\tau_\ast$,
\[
[\Theta_0+\psi](\tau_\ast)\;\propto\;\cos\!\big(k\,r_s(\tau_\ast)\big),
\qquad
r_s(\tau_\ast)=\int_0^{\tau_\ast}\!c_s\,\Dd\tau,
\]
so extrema sit at $k_n\,r_s(\tau_\ast)=n\pi$: compressions (odd $n$) are
baryon-enhanced, rarefactions (even $n$) suppressed, and the dark-matter
driving of the potentials boosts the third peak --- every feature of the
measured TT curve, produced by this system and not by any OPH-specific term.
\end{proposition}

\begin{proposition}[Silk damping]\label{p:damping}
At next order in $1/\kdot$ the oscillator acquires the diffusion envelope
$e^{-k^2/k_D^2}$ with
\[
k_D^{-2}=\int_0^{\tau}\frac{\Dd\tau'}{6(1+R)\,\kdot}
\left[\frac{R^2}{1+R}+\frac{16}{15}\right],
\]
the $16/15$ arising from the polarization terms of
Theorem~\ref{t:hierarchy}; photon diffusion between commits is the physical
mechanism, and its OPH reading is transparent: on scales crossed by a random
walk of commit-free transport legs, the record field cannot maintain
contrast.
\end{proposition}

\begin{proposition}[Line-of-sight solution]\label{p:los}
With visibility $g(\tau)=\kdot\,e^{-\kappa(\tau,\tau_0)}$, the temperature
multipoles today are
\[
\Theta_\ell(k,\tau_0)=\int_0^{\tau_0}\!\Dd\tau\;
\Big\{
g\left[\Theta_0+\psi+\tfrac{\Pi}{4}+\tfrac{3}{4k^2}\ddot\Pi\right]
j_\ell\big(k(\tau_0-\tau)\big)
+\Big(\frac{g\,v_b}{k}\Big)^{\!\cdot} j_\ell
+e^{-\kappa}\big(\dot\psi+\dot\phi\big)\,j_\ell
\Big\},
\]
($\Pi=F_{\gamma2}+G_{\gamma0}+G_{\gamma2}$), and
\[
C_\ell^{TT}=4\pi\!\int\!\frac{\Dd k}{k}\,
\Delta_\zeta^2(k)\,\left|\frac{\Theta_\ell(k,\tau_0)}{\zeta(k)}\right|^2 .
\]
Given Assumption~\ref{a:init}'s gated $(A_s,n_s)$ and the imports of
Assumptions~\ref{a:qed}--\ref{a:rec}, this reproduces the curve computed by
the diagnostic CAMB lane; agreement of an independent implementation with
CAMB at the sub-percent level is receipt \textsc{Boltz-V1}.
\end{proposition}

\section{Receipts and simulator tests}\label{s:receipts}

\begin{longtable}{@{}p{0.16\linewidth}p{0.5\linewidth}p{0.26\linewidth}@{}}
\toprule
\textbf{Receipt} & \textbf{Statement} & \textbf{Status}\\
\midrule
\textsc{Boltz-R1} &
Finite-lattice refinement Liouville: coarse-grained photon-class record
transport between commits converges to geodesic flow, schedule-independently,
with vanishing measure defect under refinement. &
open; simulator test below\\
\textsc{Boltz-N1} &
$\sigma_T$ normalization: absolute $m_e$ is a declared import until a
charged-family absolute-scale theorem exists. &
declared import\\
\textsc{Boltz-X1} &
$x_e(\tau)$ recombination history from imported atomic data; contains no
CMB-target information. &
declared import\\
\textsc{Boltz-V1} &
Independent hierarchy implementation matches CAMB TT/TE/EE at stated
tolerances with identical inputs. &
open; engineering\\
Tilt certificate &
Theorem-grade $n_s$ (clock normalization). &
issue \#522\\
Amplitude + lift &
$A_s$ and radial screen-to-$k$ map. &
issue \#330\\
Kernels &
$\Gamma_{\rm rec}$, $\rho_A$, $B_A$ physical receipts. &
issue \#374\\
Likelihood &
Frozen likelihood protocol and hashes. &
issue \#363\\
\bottomrule
\end{longtable}

\textbf{Simulator test for \textsc{Boltz-R1}.} Inject a labeled low-weight
record packet on the 64k lattice; propagate under $N$ random repair
schedules; measure the arrival-time and dispersion statistics of the packet
across the screen. Pass condition: schedule-to-schedule divergence of the
packet trajectory consistent with zero at the run's mismatch tolerance, and
dispersion shrinking under refinement (16k$\to$64k$\to$256k) at the rate the
refinement-naturality bounds predict. Fail condition: schedule-dependent
transport, which would falsify Theorem~\ref{t:liouville} on the implemented
branch.

\section{What this note does and does not close}
It closes, conditionally on the cited branch theorems, the \emph{form} of
the transport: OPH inherits the standard Einstein--Boltzmann system, with
exactly two gated insertion points for new kernels and three tagged imports.
Consequently the physical-CMB prediction gate no longer contains
``derive the Boltzmann equations'' as an open item; it contains
\textsc{Boltz-R1} and \textsc{Boltz-V1} plus the pre-existing gates
(\#330, \#522, \#374, \#363). It does not certify initial conditions,
normalizations, recombination, or likelihoods, and nothing here reads Planck
data. Under the anti-fitting rule, the acoustic peak structure remains
attributable to standard plasma physics; OPH's falsifiable exposure stays
concentrated in the primordial inputs, exactly where issues \#330 and \#522
put it.

\section*{References}
\begin{itemize}[leftmargin=1.2em]
\item C.-P. Ma and E. Bertschinger, \emph{Cosmological Perturbation Theory
in the Synchronous and Conformal Newtonian Gauges}, ApJ 455, 7 (1995).
\item S. Dodelson and F. Schmidt, \emph{Modern Cosmology}, 2nd ed., Academic
Press (2020).
\item U. Seljak and M. Zaldarriaga, \emph{A Line-of-Sight Integration
Approach to Cosmic Microwave Background Anisotropies}, ApJ 469, 437 (1996).
\item W. Hu and M. White, \emph{CMB Anisotropies: Total Angular Momentum
Method}, Phys. Rev. D 56, 596 (1997).
\item OPH paper stack: \emph{Observers Are All You Need}; \emph{Reality as a
Consensus Protocol}; \emph{Recovering Relativity and the Standard Model from
Observer Overlap Consistency}; \emph{OPH Cosmology Finite-Source CMB
Program} (this repository).
\end{itemize}

\end{document}
