\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,array,longtable}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xurl}

\IfFileExists{../paper/release_info.tex}{
  \input{../paper/release_info.tex}
}{
  \newcommand{\OPHPaperReleaseDate}{\today}
  \newcommand{\OPHPaperReleaseBanner}{Draft}
  \newcommand{\OPHPaperReleaseID}{local-cosmology-staging}
}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.08}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{target}[theorem]{Target}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\theoremstyle{plain}

\newcommand{\pathref}[1]{\nolinkurl{#1}}
\newcommand{\SimSourceRepo}{\url{https://github.com/muellerberndt/oph-physics-sim}}

\title{OPH Cosmological Vacuum and Structure Formation:\\
Finite Transfer Gates, Fluctuation Ensembles, and Proto-Object Receipts}
\author{B.\ M\"uller}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{abstract}
OPH cosmology needs a sharp distinction between a field that looks noisy and a
field that deserves to be called a physical vacuum. This paper sets that
boundary. A settled simulator state, a repair relaxation, or a plausible visual
fluctuation is only a diagnostic unless it comes from OPH source data with a
proper transfer construction and refinement check.

The same boundary organizes structure formation. Vacuum-like fields, primordial
seeds, and observable sky predictions are different claims. The paper keeps
those layers separate so a useful simulation cannot be mistaken for a completed
cosmological prediction.
\end{abstract}

\section{Scope}

This is a technical companion outside the release bundle. It coordinates the
vacuum and fluctuation boundary for finite-source cosmology, screen
microphysics, the compact theorem stack, and OPH-FPE simulator outputs.

\section{Shared Finite Quotient Theorem Surface}

\input{../paper/tex_fragments/FINITE_QUOTIENT_ENSEMBLE_THEOREMS.tex}

\section{Vacuum Claim Boundary}

The strongest allowed simulator labels are:
\[
E0:\hbox{ seed noise or repair jitter},\qquad
E1:\hbox{ conventional reference ensemble}.
\]
An OPH-native vacuum label requires an E3 receipt.  The source data must include
\[
\mathfrak S_r^E=(Q_r,m_r^0,J_r,V_r,a_{t,r})
\]
with \(J_r\), \(V_r\), and \(a_{t,r}\) derived from OPH source structure rather than from a target
law or a desired visual spectrum.  Accepted repair moves are generally directed and cannot simply
be reused as reversible Euclidean conductances.

\section{Structure-Formation Targets}

\begin{longtable}{@{}p{0.28\textwidth}p{0.62\textwidth}@{}}
\toprule
Object & Required source-side label\\
\midrule
\endhead
\bottomrule
\endfoot
Fluctuating screen field & E0 or E1 unless an E2 quotient ensemble receipt passes.\\
OPH vacuum field & E3 only after source Euclidean slab, ground-state, Doob, reflection-positivity,
and transfer-refinement receipts.\\
Proto-object worldlines & Diagnostic until production matter/particle and observer-facing object
population receipts pass.\\
Growth seeds & E4 only after the primordial bridge, radial lift, null-space, positivity, and
forward-projection receipts pass.\\
LSS comparison & E5 only after frozen likelihood/data contracts pass in the data-contract paper.\\
\end{longtable}

\section{Simulator Contract}

The simulator should emit the following receipt names even when they fail:
\begin{itemize}[leftmargin=2em]
\item \pathref{TRACIALLY_POINTED_QUOTIENT_RECEIPT}
\item \pathref{SOURCE_EUCLIDEAN_SLAB_RECEIPT}
\item \pathref{TRANSFER_REFINEMENT_RECEIPT}
\item \pathref{STATIONARY_LAW_SCHEDULE_INVARIANCE_RECEIPT}
\item \pathref{PATHWISE_PARTITION_INVARIANCE_RECEIPT}
\end{itemize}
False receipts are part of the scientific result.  They prevent a reference baseline or rendering
field from being mislabeled as an OPH vacuum.

\section{Unclosed Claim Boundaries}

\begin{enumerate}[leftmargin=2em]
\item Derive the reversible source conductances \(J_r\), potential \(V_r\), and slab thickness
\(a_{t,r}\) from finite OPH source data.
\item Prove reflection positivity or an equivalent reconstruction theorem on the selected branch.
\item Relate passed E3 vacuum receipts to E4 primordial growth seeds without using CMB or LSS data.
\item Specify proto-object/worldline receipts that remain distinct from production particle claims.
\end{enumerate}

\end{document}
