\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{longtable,booktabs,array,multirow}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{framed}
\usepackage{fancyvrb}
\usepackage{ragged2e}
\usepackage{hyperref}
\usepackage{xurl}
\input{release_info.tex}

% Springer/pdflatex compatibility: provide fallbacks for Unicode math/text glyphs.
\newcounter{none}
\providecommand{\theHnone}{\arabic{none}}
\providecommand{\textsubscript}[1]{$_{\mathrm{#1}}$}
\newcommand{\ellbar}{\bar{\ell}}
\newcommand{\ophid}[1]{\path{#1}}
\ifdefined\DeclareUnicodeCharacter
\DeclareUnicodeCharacter{00B1}{\ensuremath{\pm}}
\DeclareUnicodeCharacter{00B2}{\textsuperscript{2}}
\DeclareUnicodeCharacter{00B3}{\textsuperscript{3}}
\DeclareUnicodeCharacter{00B7}{\ensuremath{\cdot}}
\DeclareUnicodeCharacter{00B9}{\textsuperscript{1}}
\DeclareUnicodeCharacter{00D7}{\ensuremath{\times}}
\DeclareUnicodeCharacter{02B8}{\textsuperscript{y}}
\DeclareUnicodeCharacter{0393}{\ensuremath{\Gamma}}
\DeclareUnicodeCharacter{0394}{\ensuremath{\Delta}}
\DeclareUnicodeCharacter{039B}{\ensuremath{\Lambda}}
\DeclareUnicodeCharacter{03A3}{\ensuremath{\Sigma}}
\DeclareUnicodeCharacter{03A6}{\ensuremath{\Phi}}
\DeclareUnicodeCharacter{03A9}{\ensuremath{\Omega}}
\DeclareUnicodeCharacter{03B1}{\ensuremath{\alpha}}
\DeclareUnicodeCharacter{03B2}{\ensuremath{\beta}}
\DeclareUnicodeCharacter{03B3}{\ensuremath{\gamma}}
\DeclareUnicodeCharacter{03B4}{\ensuremath{\delta}}
\DeclareUnicodeCharacter{03B5}{\ensuremath{\varepsilon}}
\DeclareUnicodeCharacter{03B7}{\ensuremath{\eta}}
\DeclareUnicodeCharacter{03B8}{\ensuremath{\theta}}
\DeclareUnicodeCharacter{03BA}{\ensuremath{\kappa}}
\DeclareUnicodeCharacter{03BB}{\ensuremath{\lambda}}
\DeclareUnicodeCharacter{03BC}{\ensuremath{\mu}}
\DeclareUnicodeCharacter{03BD}{\ensuremath{\nu}}
\DeclareUnicodeCharacter{03BE}{\ensuremath{\xi}}
\DeclareUnicodeCharacter{03C0}{\ensuremath{\pi}}
\DeclareUnicodeCharacter{03C1}{\ensuremath{\rho}}
\DeclareUnicodeCharacter{03C3}{\ensuremath{\sigma}}
\DeclareUnicodeCharacter{03C4}{\ensuremath{\tau}}
\DeclareUnicodeCharacter{03C6}{\ensuremath{\phi}}
\DeclareUnicodeCharacter{03C7}{\ensuremath{\chi}}
\DeclareUnicodeCharacter{03C8}{\ensuremath{\psi}}
\DeclareUnicodeCharacter{03C9}{\ensuremath{\omega}}
\DeclareUnicodeCharacter{1D9C}{\textsuperscript{c}}
\DeclareUnicodeCharacter{2020}{\ensuremath{\dagger}}
\DeclareUnicodeCharacter{2070}{\textsuperscript{0}}
\DeclareUnicodeCharacter{2074}{\textsuperscript{4}}
\DeclareUnicodeCharacter{2075}{\textsuperscript{5}}
\DeclareUnicodeCharacter{2076}{\textsuperscript{6}}
\DeclareUnicodeCharacter{2077}{\textsuperscript{7}}
\DeclareUnicodeCharacter{2078}{\textsuperscript{8}}
\DeclareUnicodeCharacter{2079}{\textsuperscript{9}}
\DeclareUnicodeCharacter{207A}{\textsuperscript{+}}
\DeclareUnicodeCharacter{207B}{\textsuperscript{-}}
\DeclareUnicodeCharacter{207D}{\textsuperscript{(}}
\DeclareUnicodeCharacter{207E}{\textsuperscript{)}}
\DeclareUnicodeCharacter{207F}{\textsuperscript{n}}
\DeclareUnicodeCharacter{2080}{\textsubscript{0}}
\DeclareUnicodeCharacter{2081}{\textsubscript{1}}
\DeclareUnicodeCharacter{2082}{\textsubscript{2}}
\DeclareUnicodeCharacter{2083}{\textsubscript{3}}
\DeclareUnicodeCharacter{2085}{\textsubscript{5}}
\DeclareUnicodeCharacter{2086}{\textsubscript{6}}
\DeclareUnicodeCharacter{2087}{\textsubscript{7}}
\DeclareUnicodeCharacter{2088}{\textsubscript{8}}
\DeclareUnicodeCharacter{208B}{\textsubscript{-}}
\DeclareUnicodeCharacter{2102}{\ensuremath{\mathbb{C}}}
\DeclareUnicodeCharacter{210B}{\ensuremath{\mathcal{H}}}
\DeclareUnicodeCharacter{2113}{\ensuremath{\ell}}
\DeclareUnicodeCharacter{2124}{\ensuremath{\mathbb{Z}}}
\DeclareUnicodeCharacter{2192}{\ensuremath{\to}}
\DeclareUnicodeCharacter{2193}{\ensuremath{\downarrow}}
\DeclareUnicodeCharacter{2194}{\ensuremath{\leftrightarrow}}
\DeclareUnicodeCharacter{21D2}{\ensuremath{\Rightarrow}}
\DeclareUnicodeCharacter{2202}{\ensuremath{\partial}}
\DeclareUnicodeCharacter{2208}{\ensuremath{\in}}
\DeclareUnicodeCharacter{220F}{\ensuremath{\prod}}
\DeclareUnicodeCharacter{2212}{\ensuremath{-}}
\DeclareUnicodeCharacter{221A}{\ensuremath{\surd}}
\DeclareUnicodeCharacter{221D}{\ensuremath{\propto}}
\DeclareUnicodeCharacter{221E}{\ensuremath{\infty}}
\DeclareUnicodeCharacter{2229}{\ensuremath{\cap}}
\DeclareUnicodeCharacter{222B}{\ensuremath{\int}}
\DeclareUnicodeCharacter{223C}{\ensuremath{\sim}}
\DeclareUnicodeCharacter{2245}{\ensuremath{\cong}}
\DeclareUnicodeCharacter{2248}{\ensuremath{\approx}}
\DeclareUnicodeCharacter{2261}{\ensuremath{\equiv}}
\DeclareUnicodeCharacter{2264}{\ensuremath{\leq}}
\DeclareUnicodeCharacter{2265}{\ensuremath{\geq}}
\DeclareUnicodeCharacter{226A}{\ensuremath{\ll}}
\DeclareUnicodeCharacter{2272}{\ensuremath{\lesssim}}
\DeclareUnicodeCharacter{2295}{\ensuremath{\oplus}}
\DeclareUnicodeCharacter{2297}{\ensuremath{\otimes}}
\DeclareUnicodeCharacter{2609}{\ensuremath{\odot}}
\DeclareUnicodeCharacter{2713}{\ensuremath{\checkmark}}
\DeclareUnicodeCharacter{27E8}{\ensuremath{\langle}}
\DeclareUnicodeCharacter{27E9}{\ensuremath{\rangle}}
\DeclareUnicodeCharacter{27F9}{\ensuremath{\Longrightarrow}}
\fi

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setcounter{tocdepth}{2}
\setcounter{secnumdepth}{3}
\setlength{\LTleft}{0pt}
% Stretchable right margin lets longtable rows sit at natural width instead of
% forcing rigid full-width rows, which emitted badness-10000 alignment warnings.
\setlength{\LTright}{0pt plus 1fill}
\setlength{\tabcolsep}{1.2pt}
\setlength{\emergencystretch}{3em}
\renewcommand{\arraystretch}{1.05}

\providecommand{\tightlist}{%
 \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CommentTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\AttributeTok}[1]{#1}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\U}{\mathrm{U}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}[theorem]{Remark}

\title{Observers Are All You Need}
\author{Bernhard Mueller\textsuperscript{1}\thanks{\protect\raggedright Corresponding authors: Bernhard Mueller,
\href{mailto:bernhard@floatingpragma.ai}{\texttt{bernhard@floatingpragma.ai}};
Alexander Osika, \href{mailto:alex@snrgystudios.com}{\texttt{alex@snrgystudios.com}}.}
\and Alexander Osika\textsuperscript{2} \and Mario Poneder \and Kai Xue \and Ben Cassie \and Peter Nguyen
\and Maarten Antonie Visser \and Kale Arnav Anirudha \and David Matscheko \and Jonathan Hill}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{center}
\small\textbf{Author af\kern0pt f\kern0pt iliations:} \textsuperscript{1}Pragma Inc., Washington, USA; \textsuperscript{2}SNRGY Inc., Gothenburg, Sweden.
\end{center}

\begin{abstract}
Observer-Patch Holography (OPH) is an observer-consistency framework in which
public physics is the stable result of finite observers comparing and repairing
the records visible on overlapping screen patches. Time, geometry, matter, and
history are treated as readouts of the settled observer-facing structure
produced by finite record overlap and repair.

Each observer has access only to local patch data, and overlapping patches must
agree on the records both sides can check. Public structure is therefore the
quotient normal form of bounded systems with
local state, ports or boundaries, readback, records, feedback or repair moves,
and public evidence bundles.

The paper gives the program in one pass. Overlap repair produces public records
and normal forms. A separate geometric-readout branch then adds modular screen
geometry, the three-dimensional spatial chart, Lorentz kinematics, and the
Einstein branch with its Newton limit.
Receipt-conditional compact sector reconstruction yields the Standard Model charge structure, three
colors, and three generations. Every one of these reconstructions is conditional
on the declared branch certificates, and realized-branch nonemptiness is open.
The same stack carries the record interface,
Maxwell and Yang--Mills branches, action-level classical carrier modes with a separate quantum-particle gate, cosmic
capacity closure, and the hierarchy/naturality result.
The framework's starting point is the strange-loop principle set;
under two of those principles the quantitative coordinates
\(P\) and \(N\) are estimates from measured \(\alpha\) and \(\Lambda\) and enter
as inputs, and the status of the quantitative program is carried by the project
closure ledger. The review surface
separates theorem claims, branch assumptions, quantitative fixed-point
continuations, implementation evidence, and named falsifiers.
\end{abstract}

\begin{center}
\begin{minipage}{0.88\textwidth}
\centering
\bfseries
The paper's thesis is that public physical structure is the fixed point of
finite observer records, overlap comparison, and repair; spacetime and matter
are then recovered as observer-facing readouts of that settled structure.
\end{minipage}
\end{center}

\noindent\textbf{Keywords:} observer patch holography; quantum foundations; emergent spacetime;
fixed-point consensus; Standard Model structure; quantum gravity

\section*{What This Paper Contributes}

The framework occupies a distinct epistemic position, and this paper states it with the labels
attached. OPH carries zero continuous dials: every constant it addresses is defined by a closure
equation, each declared pixel map carries a machine-certified interval proof that it has exactly
one fixed point on its stated numerical domain, and the conditional capacity fixed point is
certified to relative width \(1.6\times10^{-25}\). The formalized subset comprises 111 sorry-free
Lean theorems covering the consensus core and the capacity-coupling algebra. A standing
falsification program maintains frozen, externally timestamped targets with a permanent executed
record. A hostile adversarial third-party audit of forty-two findings reproduced the certified
interval arithmetic and identified no false theorem in the recovered mathematical core; the two
implementation defects it exposed were repaired behind fail-closed gates with adversarial
regression tests. The epistemic statuses printed throughout this paper carry those corrections.

The strongest quantitative surfaces carry their labels directly. The self-consistent gauge-width
map has certified fixed point \(\alpha^{-1}=137.035660136947\), at \(2.5\times10^{-6}\) relative
from the measured \(137.035999177(21)\), and the source map has certified fixed point
\(136.994835177413\), at \(3.0\times10^{-4}\); each is a certified fixed point of its declared
map, and the Ward-projected hadronic transport is open. The source-audit electroweak law emits
the \(W\) chart coordinate \(80.330~\mathrm{GeV}\), \(0.5\) propagated experimental standard
deviations from the converted PDG 2026 complex pole \(80.3340~\mathrm{GeV}\); this is a
convention diagnostic with the derived readout contract open, and the \(Z\) analogue sits at
about \(17\) standard deviations. The conditional capacity fixed point is certified at
\(3.5321315434\times10^{122}\), with central value about \(2.5\) one-dimensional Planck standard
deviations from the \(\Lambda\)-located capacity, conditional on the readback map \(F\) and
premises CP-1 to CP-3, with posterior propagation open. Dimensional transmutation of the source
strong coupling gives \(\alpha_s(M_Z)=0.11834\) against the measured \(0.1179(9)\) and
\(\Lambda_{\mathrm{QCD}}^{(3)}=334.8~\mathrm{MeV}\) against \(338(12)~\mathrm{MeV}\), and the
published lattice ratio, labeled as an external theory input, places the nucleon mass within one
percent of measurement. The retrospective tilt candidate \(n_s=0.9660215\) carries its declared
trial count, and the conditional galaxy branch holds its BTFR exponent at \(1.80\sigma\) from the
error-aware fit.

OPH uses familiar mathematics without disguising it. Finite algebras, quantum channels, modular
flow, recovery maps, Jacobson's entropy-to-gravity route, Doplicher--Roberts/Tannaka
reconstruction, anomaly algebra, and fixed-point analysis all have lives before this paper. The
distinct move is to put them under one operational constraint: finite observers compare only the
records visible on overlaps, repair mismatches by declared recovery moves, and accept as public only
the normal form that survives those comparisons.

The finite observer-facing patch is the primitive object. The consensus paper proves when patch
repair has a unique quotient normal form from a fixed initial quotient state and where global
agreement fails. The substrate-neutral analysis in Ref.~\cite{observableNormalForms} proves that
the stronger comparison of endpoints from different same-boundary sources is equivalent, under
observation preservation and completeness, to injectivity of the boundary map on the consistent
quotient. It keeps that cross-source criterion separate from same-source confluence, weak
normalization, and all-schedule liveness; it does not itself establish injectivity for every
physical OPH boundary map. By itself the finite consensus theorem does not prove Lorentzian
geometry or Einstein dynamics. The compact SM/GR paper
carries the declared geometric-readout branch, controlled Bisognano--Wichmann (BW) modular flow, the null-stress bridge,
bounded-interval transport, fixed-cap generalized-entropy stationarity, small-ball area variation,
remainder control, and timelike coverage into a Jacobson-type Einstein equation. The same compact
paper reconstructs compact gauge structure on a cofinal tail carrying its explicit refinement
receipt and selects the realized Standard Model quotient on the declared Minimal Admissible
Realization (MAR) branch. The particle paper carries the branch into
the declared pixel map, the conditional capacity-electroweak bridge, and the selected-branch hierarchy and
Higgs-naturality result. The dark-sector, Yang--Mills, string, and consciousness papers use the
same machinery with narrower support boundaries and their own gates.

The technical novelty lies in the coupling. OPH adds a finite observer-facing patch tuple with
visible interface algebras and repair instruments; a recovery-derived repair relation with a
quotient normal form; a controlled modular-geometric extraction from screen caps; a
minimal-admissibility selector that acts after compact gauge reconstruction; and two dimensionless
closure coordinates, the incomplete declared-map output \(P_\star\) and the conditional
cosmic record-closure capacity candidate \(N_{\mathrm{CRC}}\), with stated uniqueness tests for their mathematical maps. Broad
slogans about information, entropy, or emergence carry no proof load here. The proof load sits on
the maps, branch hypotheses, uniqueness certificates, and falsifiers named in the paper stack.
The ontological sentence below the abstract is an interpretive conclusion from that reconstruction
chain. It is not an additional axiom used to derive the physics rows.

On that geometric branch, OPH recovers the three-dimensional observer-facing spatial chart, Lorentz kinematics, the Einstein branch, the de Sitter
capacity relation for dark energy, the Standard Model quotient, exact charge quantization, three
colors, three generations, Maxwell and Yang--Mills equations on their stated branches, and the
conditional classical Maxwell, perturbative pure-Yang--Mills, and pure-Einstein carrier modes.
Quantum photon/gluon/graviton poles require the separate receipt stated in the compact and shared
derivation papers. On the quantitative side it uses one dimensionless declared-map output,
\(P_\star\), one conditional capacity candidate, \(N_{\mathrm{CRC}}\), and a selected no-\(G\) scale certificate.
Those coordinates feed the fine-structure, hierarchy, particle, and cosmology rows.

The round-one cosmology audit separates favorable comparisons from an
excluded extrapolation.  The conditional fixed-$\mathbb Z_6$ galaxy response
has aggregate RAR scatter $0.132834$ dex, its BTFR exponent $4$ is
$1.80\sigma$ from an error-aware fit, and the conditional analytic candidate
$n_s=1-P_\star/48=0.9660215$ is $0.27\sigma$ from the Planck summary, with
its trial count declared \cite{planck18,ophdarkmatter}.  These are retrospective or conditional
comparison receipts, not frozen predictions.  Applying the same static dark
response universally to the Milky-Way--Sun system is excluded by the Cassini
quadrupole comparison at about $19.22\sigma$ on the fixed branch.  The scoped
old-settled-galaxy continuation therefore owes a source-derived applicability
rule expressed in the observer system's local state, boundary ports, readback
records, feedback, and repair moves.  The current cosmology ledger contains no
frozen physical-prediction receipt.

For gravity, Jacobson supplies the comparison target: Einstein gravity follows from entropy
equilibrium or a Clausius relation under local assumptions. OPH uses that target with a different
upstream and downstream structure. Upstream, the relevant regions are observer-visible screen caps
and collars; their modular flow is extracted from the controlled cap branch. The stationarity
statement is fixed-cap generalized entropy stationarity on declared MaxEnt variations, with the
collar recovery remainder, bounded-interval kernel, fixed-volume small-ball area identity, and
null-stress bridge supplied on the recovered-core geometric branch. Downstream,
timelike-direction completeness upgrades the rest-frame scalar relation to a tensor equation,
while local null data leave the metric term open. A constructed cosmic record-capacity readback
map with the required physical premises would close that term; the paper stack has not constructed
that map. A
counterexample to any of these branch steps defeats the OPH gravity claim while leaving Jacobson's
original comparison result untouched.

The boundaries matter as much as the outputs. A theorem, a scaling branch, a fixed-point
certificate, a phenomenological continuation, and an ontology reading are different kinds of
claim. OPH fails as stated if a load-bearing theorem has a counterexample under its assumptions,
if the controlled modular branch cannot be physically instantiated, if MAR admits a smaller
realized package, if a quantitative closure is nonunique or target-leaking, or if a carrier
implementation changes the observable quotient after visible records and repair maps are held
fixed.

\section*{Canonical Observer Language}

An abstract observer patch is the algebraic object
\[
\mathsf O_i=
\left(
\mathcal A_i,\rho_i,\mathcal R_i,
\{(\mathcal I_e,\pi_{i,e})\}_{e\ni i},
\mathcal U_i,\mathrm{Chk}_i
\right).
\]
Here \(\mathcal A_i\) is the finite or regulated accessible algebra, \(\rho_i\) the accessible
state, \(\mathcal R_i\) the exact or approximate record algebra, \(\mathcal I_e\) the overlap-visible
interface algebra, \(\pi_{i,e}\) the visible restriction, \(\mathcal U_i\) the allowed update and
repair instruments, and \(\mathrm{Chk}_i\) the checkpoint data used for continuation.

A support patch, such as a cap \(P_i\subset S^2\) or a causal diamond, is a geometric chart of the
abstract patch on a geometric branch. A carrier patch is a physical or digital implementation that
realizes the same visible interface and record statistics within a declared error. Echosahedral
hardware is therefore a reference carrier architecture for a fixed-cutoff implementation surface.
The physical claim lives at the quotient of visible records, interface statistics, repair maps, and
checkpoint continuation.

The observer patch is therefore the formal access structure used by the proof. A human observer, a
horizon cap, and a hardware module can realize or chart it, but none of those examples is the
definition. Physical predictions attach to quotient data: visible interface statistics, record
readout, repair maps, and checkpoint continuation. A carrier implementation is admissible only when
those data remain invariant within its declared error model.

\begin{definition}[Semantic observer history]\label{def:semantic-observer-history}
For an observer token \(O\), the observer-readable history is a labeled causal poset
\[
\mathsf H_O=(E_O,\preceq_O,\ell_O).
\]
The elements of \(E_O\) are semantic record events, \(\preceq_O\) is physical or informational
dependence, and \(\ell_O\) is the observer-visible event label. Event identity is derived from the
canonical semantic payload, observer token, visible footprint, and semantic causal parents. It is
not derived from worker ID, repair iteration, queue position, retry counter, timestamp, or packet
latency metadata. Latency is execution gauge only when it does not alter semantic causality,
delivered data, timeout-sensitive operations, or operational clock records.
\end{definition}

\begin{definition}[Observer registry groupoid and namespaces]\label{def:observer-registry-groupoid}
Observer identities live in a registry groupoid, not in a flat UUID table. Objects are observer
tokens
\[
\mathrm{RID}(O)=\bigl(\mathrm{kind}(O),[\mathrm{birth}(O)]_{\mathsf H},\mathrm{lineage}(O)\bigr),
\]
where \(\mathrm{kind}(O)\) lies in the disjoint namespace
\[
\{\text{patch observer},\ \text{cap observer},\ \text{future observer}\}.
\]
The birth event is a semantic event class in \(\mathsf H\), and lineage is carried by explicit
continuation, split, and merge arrows. Local registries on overlapping presentations must preserve
observer kind, birth event, lineage arrows, visible observer structure, and checkpoint cuts. The
global registry is the descent groupoid or colimit of those local registries when the cocycle and
trivial-monodromy checks pass. A split creates child tokens with parent links; it does not silently
assign one identity to multiple descendants.
\end{definition}

\begin{definition}[Operational observer clock]\label{def:operational-observer-clock}
The modular parameter of an observer-facing cap pair is not, by itself, an arbitrary operational
clock reading. A clock claim supplies an observer-accessible instrument
\[
\Theta_O:\mathrm{Chk}_O(D)\to\operatorname{Prob}(\mathbb R)
\]
and a declared affine calibration law. For a corresponding observer \(O'\), the required finite
or exact certificate has the form
\[
\Theta_{O'}(\Phi_{O*}\rho)
\approx
(A_{a,b})_*\Theta_O(\rho),
\qquad
A_{a,b}(\tau)=a\tau+b,
\]
with an explicit residual bound from state mismatch, calibration error, and record-readout error.
Execution counters are provenance; observer record order, modular parameter, and clock
uncertainty are separate semantic or operational fields.
\end{definition}

\begin{remark}[Observer-clock naturality gate]\label{rem:observer-clock-naturality-gate}
The present paper proves observer-first quotient and readback claims only where the cited theorem
surface supplies the required data. Scheduler-independent observer history and clock naturality
require a history-augmented quotient relation with history-coherent diamonds, registry descent,
state-preserving observer-algebra extraction, support-cap chart naturality, and the operational
clock instrument above. A public evidence bundle can falsify the claim by showing counter-dependent
semantic event keys, duplicate or namespace-colliding registry identities, broken registry
cocycles, non-isomorphic semantic history DAGs across executors, or clock residuals exceeding the
declared bound. Implementation field names alone are not the proof.
\end{remark}

This definition leaves the primitive observer size open. The axioms require finite or regulated
access at fixed cutoff and permit connected support regions with different finite or regulated
algebras. A primitive observer may therefore be a variable finite federation of screen cells. The
stronger claim that elementary carriers are isomorphic fixed-capacity cells would require a separate
branch: homogeneous UV cellulation, isomorphic local cell algebras, equivariant overlap maps,
refinement preservation of the cell type, and a proof identifying one cell or a fixed block of cells
with the primitive carrier.

\section*{Failure Tests}

OPH is wrong as stated if a load-bearing theorem admits a counterexample under its declared
assumptions, if the controlled modular/Einstein branch cannot be instantiated under physically
realizable conditions, if MAR fails to select the stated realized package on the declared
admissible class, if a quantitative closure is nonunique or target-leaking, or if a physical
implementation shows branch-essential dependence on hidden carrier presentation after visible
quotient data are held fixed. Concrete falsifiers include failure of a displayed Maxwell,
pure-Yang--Mills, or pure-Einstein quadratic kernel to have its stated transverse or transverse-traceless (TT) classical
mode under all of that theorem's action/background/phase hypotheses; failure of a claimed quantum
pole after its full quantization and spectral receipt is supplied; gauge-mediated proton decay on
the realized Standard Model branch; a fourth
light matter generation in the realized low-energy branch; a smaller admissible one-Higgs Standard
Model package; nonunique \(P_\star\) or \(N_{\mathrm{CRC}}\) closure; a failed fixed-cap
entropy-to-Einstein tensor upgrade; or carrier-dependent observables after the visible interface is
held fixed. A failed continuation does not erase the recovered core unless that continuation is one
of the stated parents of the core claim.
	
\tableofcontents
\newpage

\section{Introduction}

Observer-Patch Holography asks how much of physics is forced once the world is described from the
inside. No observer has access to a view from nowhere. In the idealized description there is a
shared screen net, often charted by \(S^2\), but each finite observer has access only to a local
patch \(P_O\) of that net. The observer carries records inside that patch and can compare only the
observables shared with neighboring patches. OPH takes that comparison rule literally: where
descriptions overlap, they must agree. Thus an "observer screen" is an operational access cut, not a
private physical sphere assigned to the observer.

The formalism used here is deliberately quantum-algebraic. Patches carry algebras and states,
record events use the trace/Born rule on their declared operator surface, and the gravity branch
uses generalized entropy. OPH's theory-of-everything claim is that the observed effective universe
can be recovered from this axiom set and its stated branch conditions if the framework is correct.
The reconstruction may use declared standard mathematics and branch hypotheses without treating
those ingredients as hidden empirical constants.

The computational interpretation has a sharp boundary. A conventional simulation evolves surrogate
universe states,
\[
U_t\longrightarrow U_{t+1}\longrightarrow U_{t+2}\longrightarrow\cdots .
\]
OPH uses a fixed-point computation, but the equation alone is not the definition of
simulation. In the fundamental description there is no global timeline on which the contents
of spacetime are updated. The readback-and-repair operator acts on observer-readable world
candidates and selects a stable solution
\[
\mathcal T(W)=W .
\]
The companion consensus paper~\cite{ophconsensus}, Definition
\texttt{def:oph-simulation}, requires five independent clauses: recovery-derived endogenous
update, nontrivial quotient-readable records, strict overlap-repair descent with a
schedule-independent normal form, elimination of a proper candidate basin in the selected
boundary/sector fiber, and implementation/clock closure. Its Theorem
\texttt{thm:oph-simulation} proves that the selected finite OPH packet meets those clauses
under the stated boundary and record hypotheses and then derives the fixed-point equation.
The same theorem gives an identity-map/constant-functional counterexample, so an ordinary
equilibrium is insufficient as a simulation.

The local readout of the selected normal form supplies history for observers who subjectively
experience time. Time is therefore internal record order instead of an external update
parameter. In OPH, ``simulation'' means this certified observer-facing self-consistency
structure, not a bare fixed point and not a frame renderer. The executable OPH-FPE simulator
and its finite-run receipt bundles are a separate public evidence surface for finite OPH
experiments~\cite{ophfpe}; they do not replace the theorem-level definition above.

That certified consistency demand is strong enough to organize the familiar world. The effective bulk is reconstructed
from compatible screen data. Locality comes from the way collars control recovery across patch
boundaries. Gauge freedom is the freedom to change the local description without changing any shared
observable. Records are the stable parts of a patch that can be checked by other patches. Matter is
the stable charge and excitation content that survives transport, fusion, and minimal admissible
realization.

The first major result is spacetime kinematics. Modular flow on screen caps becomes geometric,
and the compact cap-normal theorem identifies a sky direction with \(q(\Omega)=(1,\Omega)\),
represents an oriented round cap by \(n_C=(\cot\alpha,\csc\alpha\,\mathbf c)\), proves
\(\eta(n_C,q(\Omega))=0\) exactly on the cap boundary with the interior/exterior sign rule, and
gives \(n_{gC}=\Lambda_g n_C\). Future unit observer frames then form
\(H^3\simeq\mathrm{SO}^+(3,1)/\mathrm{SO}(3)\), exactly three-dimensional. A cap determines an
\(H^3\) plane/half-space, not a preferred observer point or populated bulk. On the conditional
record-population branch, quotient-visible record tokens whose calibrated modular cap responses
factor through point-local \(H^3\) sources are uniquely identifiable in exact data and stably
localized in finite noisy data. The finite localization radius is
\(R_H[(L/\alpha)\varepsilon+(2/\alpha)\sigma]\) for exact net minimization, with a positive
residual gap required before a unique finite point is reported. Generalized entropy
at fixed cap then gives the Einstein relation in the large-scale regime. The proposed cosmological
capacity relation is
\[
\Lambda_{\mathrm{CRC}}=\frac{3\pi}{G N_{\mathrm{CRC}}}.
\]
The Gibbons--Hawking entropy and the Planck-2018 late-time de Sitter benchmark give a concrete normalization~\cite{gibbonsHawking77,planck18}. With
\(R_{\mathrm{dS}}\simeq1.66\times10^{26}\,\mathrm m\) and
\(\ell_P\simeq1.616\times10^{-35}\,\mathrm m\), the bare horizon ratio is
\[
N_{\mathrm{patch}}=\left(\frac{R_{\mathrm{dS}}}{\ell_P}\right)^2\simeq1.05\times10^{122}.
\]
The entropy capacity is
\[
N_{\mathrm{scr}}=S_{\mathrm{dS}}=\frac{A_{\mathrm{dS}}}{4\ell_P^2}
=\pi N_{\mathrm{patch}}\simeq3.31\times10^{122},
\]
so \(\Lambda\ell_P^2\simeq2.85\times10^{-122}\). OPH uses \(N_{\mathrm{scr}}\) for the
Gibbons--Hawking entropy capacity and \(N_{\mathrm{patch}}\) for the bare horizon area ratio.
The proposed input-free closure would define an OPH readback map \(F(N)\) as the active cosmic
record capacity reconstructed by stable observers inside the universe supplied with capacity
\(N\). The cosmic record-closure capacity satisfies
\[
N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}}).
\]
The paper stack has not constructed this physical map \(F\). The electroweak bridge supplies a
mathematical candidate of about \(3.532\times10^{122}\) only if premises CP-1 to CP-3 identify
that bridge with \(F\). The Planck-\(\Lambda\) central read-off is about
\(3.313\times10^{122}\), which is about \(6.6\) percent below the bridge candidate. The joint
Planck posterior, propagated through the \(\Lambda\)-to-\(N\) map across three degeneracy routes,
places the gap at \(2.4\) to \(2.5\) one-dimensional standard deviations under the consumed
likelihood combination and \(3.8\) to \(3.9\) under Planck+BAO, so the combination freeze is part
of any future test registration; a final statement requires the closed premises. Thus neither
the physical fixed-point identity nor the cosmological display
\(\Lambda_{\mathrm{CRC}}=3\pi/(G N_{\mathrm{CRC}})\) is established by the bridge calculation.

The second result is the Standard Model structure. On a cofinal tail carrying the explicit
compact-gauge refinement receipt (including coherent surjective charge pullbacks, finite block
embeddings, tensor realizations, \(3+1\)D symmetry, and compatible forgetful fibers), edge sectors reconstruct the
bosonic compact-gauge branch. On the realized low-energy branch with the explicit
one-generation/one-Higgs matter package, minimal admissible realization then selects the
compact gauge quotient
\[
\SU(3)\times\SU(2)\times\U(1)/\mathbb Z_6.
\]
The realized low-energy branch then fixes exact hypercharge, three generations, three colors,
integer charge for color singlets, and the absence of gauge-mediated proton decay. On separately
stated Maxwell, perturbative/deconfined Yang--Mills, and pure-Einstein action/phase branches, the
quadratic reductions have the corresponding classical null carrier modes. Photon, gluon, or
graviton particle claims require the additional physical-Hilbert-space and spectral-pole receipts.

The third result is quantitative and sits outside the recovered core. OPH's constants program
has an incomplete declared pixel map, a proposed global cosmic record-closure map, and a selected
no-\(G\) scale proof record. Its rule is reverse
engineering followed by fixed-point closure: observations are allowed to locate the relevant basin,
because the OPH universe is treated as a closed mathematical structure whose branch coordinates are
displayed to its internal observers; the published OPH value is then the fixed point picked
out by a declared map and uniqueness proof.

This reading order is the native shape of a test inside a strange loop, and the loop's geometry
forces it. A self-reading universe owns no outside vantage from which its constants could be
predicted ahead of any measurement; inside the loop, measurement and substrate readback are one
act performed from two ends. The test of such a structure has two stages. First the measured
world locates the basin: the observed \(\alpha\), the observed \(\Lambda\), and the observed gauge
structure say where each fixed point must sit if the loop closes. Locating a basin consumes a
measurement, so a located basin can never score as a hit, and the claim rules price every located
basin as an input, permanently. Second, the closure equations either contract into the located
basin or miss it. A certified contraction into a basin the map was never tuned to is the one
event the program scores, and a certified miss kills the formulation. Every quantitative row in
this paper is accordingly one of three objects: a basin location, which is an input; an audit of
arithmetic, which is a consistency check; or a conditional coordinate waiting on its closure term.
The scoreboard stays empty until blind contractions land, and the loop's own structure says this
is the only shape a test of a self-reading universe can take.

The numerical root reported for \(P_\star\) is an
endpoint of the declared numerical map; its physical endpoint relation has not been derived. The
physical readback map needed for \(N_{\mathrm{CRC}}\) has likewise not been constructed. The
Planck-\(\Lambda\) central capacity is \(N_{\mathrm{scr}}\simeq3.313\times10^{122}\), whereas the
conditional electroweak bridge gives about \(3.532\times10^{122}\).

The equation that would force the measured capacity is not known at current standing. The
conditional bridge \(N=\pi\exp[6\pi/(P\,\alpha_U)]\) is the only closed form on the table: it
lands about seven percent above the \(\Lambda\)-located value, its balance premise CP-1 is a
declared input rather than a theorem, and the candidate one-term corrections that would land
it inside the Planck basin are work in progress, none of them derived. Read through
\(\Lambda_\star\ell_\star^2=3\pi/N\), the bridge is a zero-dial relation between the two
constants that frame physics, \(\Lambda\ell_P^2=3\exp[-6\pi/(P\,\alpha_U(P))]\) up to the
correction term: the \(122\) orders of magnitude that the naive vacuum-energy estimate misses
appear as \(e^{-281}\), with the same exponent that runs the weak hierarchy, and since
\(\alpha_U\) is a function of \(P\) alone and \(P\) is located from \(\alpha\), the theory
side holds no continuous freedom once \(\alpha\) is measured. The working capacity
is therefore located by the basin method: \(N_\Lambda=3\pi/(\Lambda\ell_\star^2)\) reads the
capacity off the measured cosmological constant, and every surface that consumes \(N\)
consumes this located value as an input under the direction-of-inference rule.

This is the expected standing for a strange loop, and it costs the program little. Basin
location is the first stage of the loop's native test, and Planck locates the capacity basin
to \(2.7\) percent; what stays open is the second stage, the contraction. The borrow is one
number tied to one named generator and priced in the closure ledger; it is not a parameter family.
None of the structural results consume the closed form of \(N\): the kinematics, the gauge
quotient, the Einstein branch, and the hierarchy law stand without it. The missing object is
also sharply bounded: a derived balance must land within one part in \(10^4\) of the bridge
exponent, against a three-candidate correction set with a declared menu price, so the open
item is one small counting theorem, and a wrong derivation falsifies the lane rather than
hiding inside it. The three candidates are in addition nearly degenerate with one another,
spanning a band of relative width \(9\times10^{-4}\) in \(N\), a point prediction
\(\Lambda\ell_P^2\in[2.84618,\,2.84878]\times10^{-122}\) sitting \(0.03\sigma\) from the
measured value: a future \(\Lambda\) determination at one percent precision separates that
band from the uncorrected bridge at \(6.5\sigma\), and at \(0.3\) percent tests the band
itself, so the capacity lane carries a drafted forward registration whichever way the
derivation lands.

The local
pixel ratio is
\[
P:=\frac{a_{\mathrm{cell}}}{\ell_\star^2},
\qquad
\gamma_\star=\frac{\ell_\star\nu_{\mathrm{Cs}}}{c},
\qquad
B_\star=\frac{3\pi}{\ell_\star^2}.
\]
If the two declared-map outputs acquire their missing physical identifications,
\(P_\star\) and \(N_{\mathrm{CRC}}\) fix
\(\Lambda_\star\ell_\star^2=3\pi/N_{\mathrm{CRC}}\) and
\(\Lambda_\star a_{\mathrm{cell}}=3\pi P_\star/N_{\mathrm{CRC}}\). They fix the dimensionless
geometry. The selected scale certificate supplies the SI scale product
\(B_\star=\Lambda_\star N_{\mathrm{CRC}}=3\pi/\ell_\star^2\).
The selected scale certificate does not construct the cosmic readback map or remove the
\(6.6\)-percent central-value mismatch.
Under those same identifications, the pixel \(P_\star\) together with the \(\Lambda\)-located
working capacity \(N_\Lambda=3.31\times10^{122}\) fixes a canonical geometric pixel area and a
total geometric cell count on an equal-area screen chart,
\[
K_{\mathrm{cell}}
=\frac{A_{\mathrm{screen}}}{a_{\mathrm{cell}}}
=\frac{4N_\Lambda}{P_\star}
\simeq 8.12\times10^{122}.
\]
The capacity in this count is the measured-side working value, a permanent input under the claim
rules; at the conditional bridge capacity the same chart count reads \(8.66\times10^{122}\).
The result supplies a geometric chart count. It does not choose a primitive observer capacity. The
quantity \(P_\star/4\simeq0.408\) nats, or about \(0.588\) bits, should not be read as
\(\log\dim\mathcal H_{\mathrm{cell}}\) for an autonomous tensor factor. OPH capacity lives on
shared cuts, edge centers, and constrained overlap data; adjacent geometric pixels are not assumed
to factor into independent Hilbert components. No fixed primitive observer algebra follows from
\(P_\star\) and \(N_{\mathrm{CRC}}\) alone.
The no-\(G\) burden of the scale proof record is the clock hierarchy. The first load-bearing object
must be a strict source-root proof for \(\alpha_U(P_\star)\); the present source-audit
branch is only a witness. After that, the cesium gap
\(\varepsilon_{\mathrm{Cs}}\sim10^{-33}\) must be emitted by source-side electroweak
transmutation, QCD/hadronic data, flavor and nuclear data, and a cesium hyperfine spectral
readout, with no dependency path from measured gravity or any calibrated electroweak or
gravity scale.
The public \(\alpha_U\) record is a one-dimensional comparison-branch fixed-point certificate:
\[
\begin{aligned}
\alpha_U(P_\star)&=0.041124336195630495,\\
\frac{v}{E_\star}&=2.0199803239725553\times10^{-17},
\end{aligned}
\]
and the Krawczyk image of
\([0.041123336195630494,\;0.041125336195630496]\) lies strictly inside that interval. A
source-side diagnostic branch records
\(P_{\mathrm{cand}}=1.630972095694329\ldots\),
\(\alpha_U(P_{\mathrm{cand}})=0.04112424744557487\), and
\(v(P_{\mathrm{cand}})/E_\star=2.0198114150099223\times10^{-17}\), with the public Thomson
endpoint excluded upstream. A converged precision-100 rerun supersedes this printed
\(P_{\mathrm{cand}}\) tail beyond digit 10; the certified forward pixel is
\(P_{\mathrm{fwd}}=1.630972095858897\ldots\) (CL-6, closed).
That source branch is a witness, not a full endpoint proof; it still
needs the strict interval root for the Ward-projected self-map. The dimensionless formula is the
strongest clean hierarchy statement. It does not supply an independently physical \(E_\star\), a mass
in GeV, or a complex propagator pole. The full SI gravity row requires the full set of
cesium-clock source records.
The QCD and hadronic weakpoint is narrow. The low-energy Thomson endpoint and the cesium-clock
display require confined-quark and nuclear source payloads that the first-principles trunk in this
paper does not emit. For a source-only Thomson endpoint, the missing object is the OPH-QCD
hadronic backend: source QCD parameters, a quotient ensemble, finite Euclidean vacuum transfer,
Ward-normalized electromagnetic currents, the two-current spectral marginal, same-scheme
remainder, systematics, and no-target-leak receipts.

Four fine-structure coordinates must be kept separate. The source/root audit records the
undressed declared-map witness
\(\alpha_{\mathrm{root}}^{-1}=136.9948351646\ldots\). A converged precision-100 rerun
supersedes this printed tail beyond digit 9; the certified value is
\(\alpha_{\mathrm{root}}^{-1}=136.994835177413\ldots\) (interval-certified unique fixed
point of that numerical map, enclosure width \(7.2\times10^{-24}\); CL-6, closed).
The declared map is incomplete: no derivation identifies this root with a physical
fine-structure endpoint. Adding the finite-screen unified
gauge-width contribution at the CODATA-derived comparison pixel gives the mixed-provenance,
no-hadron diagnostic
\[
A_{\alpha_U}^{\mathrm{fp}}=137.0359595008\ldots.
\]
The certified self-consistent gauge-width fixed point is
\(\alpha^{-1}=137.035660136946577\ldots\) (CL-2). The displayed \(137.0359595008\ldots\)
mixes the inner value evaluated at \(P_{\mathrm{fwd}}\) with \(\alpha_U\) evaluated at the
SL-3 pixel, is not a fixed point of any single declared map, and stays on record as a
display packet only.
An executed empirical closure, using external
\(e^+e^-\to\mathrm{hadrons}\) spectral data, records
\[
\Delta\alpha_{\mathrm{had}}^{(5)}(M_Z)
=0.0267591200\pm0.0007524955,
\qquad
\alpha_{\mathrm{emp}}^{-1}(0)=136.2636589431
\]
with interval \([136.1583832834,136.3690975240]\). The measured endpoint is
\(\alpha^{-1}(0)=137.035999177(21)\), outside that interval. The resulting same-scheme
anchor correction is \([0.6485541111,0.8547920666]\) inverse-alpha units. This empirical payload
tests the endpoint map and exposes the missing contribution; it does not supply a source-only OPH
hadron law. The two-current spectral measure covers the running-\(\alpha\)/HVP marginal. HLbL and
rare-decay rows require higher-point and transition spectral sectors from the same source law.
For that reason the compact quantitative stress test is the hierarchy row above: it avoids the
public Thomson endpoint, \(G\), \(\Lambda\), \(W/Z\), Higgs mass, hadronic payloads, and the
cesium clock.

The same hierarchy exponent has a local/global capacity form:
\[
\frac{v}{E_{\mathrm{cell}}}
=
\left(\frac{N_{\mathrm{CRC}}^{\mathrm{EW}}}{\pi}\right)^{-P_\star/12},
\qquad
N_{\mathrm{CRC}}^{\mathrm{EW}}
=
\pi\exp\!\left[\frac{6\pi}{P_\star\alpha_U(P_\star)}\right].
\]
This is the electroweak bridge capacity, about
\(3.53235\times10^{122}\) on the declared comparison branch. Identifying it with the cosmic
capacity requires the unconstructed readback map \(F\) and premises CP-1 to CP-3. The
Planck-\(\Lambda\) central capacity, about \(3.313\times10^{122}\), is lower by about \(6.6\)
percent. The screen-sieve theorem gives the geometric reading of the factor
\(12\): on the triangulated \(S^2\) screen,
\(\sum_v(6-\deg v)=12\); MaxEnt/refinement stability spreads that curvature
charge into twelve unit fivefold defects; edge-center collars make them
central ports; \(A_5\) symmetry places them on the icosahedral vertex orbit.
Including reversible write/check orientation gives a 24-slot oriented repair
register. The hierarchy exponent uses this 24-fold repair normalization.
The twelve-port result selects an exposed interface architecture. The internal dimension of a
primitive observer algebra belongs to a separate carrier theorem, possibly with MAR acting on the
port, record, and repair structure.

The compact proof packages this quantitative surface as a source-certified
compression test. A row counts in the accidental-hit estimate only when its
declared source map has no dependency path from the measured target or a
calibrated proxy. If \(p_i\) bounds the conditional accidental-hit probability
for row \(i\) after the preceding accepted rows, then
\[
P_{\rm acc}\le\prod_i p_i .
\]
The closure ledger records the qualifying rows, including the structural
gauge-boson zeros and the clause-conditional hypercharge lattice. Any compression claim cites
those declared settings and landed basins.
The proof load remains the fixed-point maps, uniqueness certificates, source
records, and falsifiers.

The declared map for \(P\) gives the same screen cell two readings. From outside, the cell
sits a little above the exact self-similar
entropy balance point \(\varphi=(1+\sqrt5)/2\). From inside, the same cell appears as the smallest
electromagnetic observation step available in the encoded world. Under SL-3 the measured
fine-structure constant locates the comparison coordinate. The interval certificate proves a
unique root of the numerical map, while the physical relation between that root and the
electromagnetic endpoint remains unconstructed.

The named \(P\) branches organize the electroweak carrier chart, the low-energy electromagnetic
endpoint, the conditional Higgs/top surface, the rejected reciprocal-ray quark candidate and its
six-coordinate physical interface, a target-informed weighted-cycle neutrino comparison candidate, and the local cell/edge
consistency used by the gravity readout. The hierarchy theorem fixes \(v/E_\star\). An independent
physical \(E_\star\) and the separate pole receipt govern any mass in GeV. The gravity
normalization itself comes from \(\ell_\star^2\), and \(P\) cancels in the Newton area-law readout.
The support table records the distinct electroweak chart, conditional law, and inverse target adapter,
the frozen charged-lepton continuation, the NuFIT 6.1 rejection of the neutrino candidate, its
tautological historical basis transport and open charged-basis gate, and the open hadron
construction~\cite{nufit61}.

The fourth result is implementation. The screen-microphysics construction makes patches,
overlaps, edge observables, records, repair maps, and observer checkpoints explicit at finite
cutoff through a federated patch-carrier architecture. OPH has a regulated observer-and-record surface on which the basic consistency
machinery can be written directly.

\paragraph{Axioms in words.}
The theory uses five axioms. A screen net assigns algebras to connected screen patches. Overlap
consistency requires agreement on shared observables. Local MaxEnt selects the least biased local
state compatible with the finite constraint data and keeps the realized construction stable under
refinement. Recoverable generalized entropy supplies the collar-recovery and focusing structure
used by the gravity lane. Minimal admissible realization selects the simplest low-energy sector
compatible with the consistency constraints. These axioms define a quantum-algebraic
starting point. Quantum mechanics and quantum field theory are treated as effective descriptions
carried by the deeper observer-patch architecture, not as structures whose use here depends on
first deriving every mathematical ingredient from operational records alone.

\paragraph{The selection chain.}
The argument, end to end, is the forcing chain C1--C10 of the project consistency
stack. Rows C1--C6 (self-reading, overlap consensus, modular
self-consistency, transportable-charge consistency, entropic-gravitational consistency, record
existence) remove, on their declared branches and receipts, every structural freedom except a
two-real-parameter family \((P,N)\) together with the declared discrete selections counted in
the closure ledger. Row C7 identifies the two parameters with the SL-3/SL-4
estimates from measured \(\alpha\) and \(\Lambda\), rows C8--C9 are then two equations on that
two-parameter family, and C10 confines unit conventions to bookkeeping. The endpoint is
conditional and sharp: if both closure equations hold and their fixed points are unique, the stack
admits exactly one universe on the declared branches, and whether that universe is ours is the
closure ledger reading zero. Uniqueness lemma L1 (one \(P\)) is discharged globally: the interval
contraction certificate
gives existence and uniqueness on its certified interval, and the domain-global certificate
bounds \(\sup|g'|<1\) on every piece of a 256-piece subdivision of the declared numerical domain
(\(\alpha^{-1}\in[100,200]\), both readout maps, empty exceptional set), so each declared readout
map has exactly one fixed point on that domain. This certificate does not derive a physical
endpoint relation for the incomplete declared map. Lemma L2 (one
\(N_{\mathrm{CRC}}\)) rests on the coupling theorem G2-GAP-1, a conditional theorem: the
putative capacity readback fixed point equals the electroweak bridge capacity
\(N=\pi\exp[6\pi/(P\,\alpha_U)]\), proven modulo three declared premises, CP-1 the balance
condition \(\Pi_{\mathrm{EW}}=\beta_{\mathrm{EW}}P\) (the genuinely physical premise), CP-2 the
port-load inversion form, and CP-3 the averaging carrier (dispensable for the fixed-point
location); the tick-projection identity \(\Pi_{\mathrm{EW}}=24\pi/(\alpha_U X)\) and the readback
seed \(N_0=\pi\) are discharged theorems, and the conditional fixed point is certified by
interval arithmetic at \(3.5321315434\times10^{122}\) with relative width \(1.6\times10^{-25}\)
(closure ledger row CL-7). This interval certifies the bridge formula, not the unconstructed
physical map \(F\). Its value is about \(6.6\) percent above the Planck-\(\Lambda\) central
capacity \(3.313\times10^{122}\). The decisive C9 computation is a future
target-blind hadronic completion under a detached successor coordinate
contract (rows CL-1/CL-2). The historical externally timestamped v2 target
conflated total and residual coordinates and cannot score that computation;
corrective v3 is a permanently inactive post-target-access erratum scaffold.
A successor must bind a complete method frozen before genuinely withheld data,
or use an audited clean-room producer, before execution.

The synthesis surface gives the operational picture first, then places the technical proof machinery
after the reader has the construction in hand.

\section{Main Results}

The OPH papers support the following unified picture.

\begin{enumerate}[leftmargin=2em]
\item \textbf{Observers and records become physical objects.} Finite patches, shared overlaps,
record algebras, repair maps, and observer checkpoints are represented on the screen as part of the
construction.
\item \textbf{Spacetime is reconstructed.} On the controlled Einstein-branch geometry readout,
the finite cap-normal BW certificate (support-order faithfulness, regularized mixed-GNS modular
transport, BW framing, held-out oriented cross-ratio rigidity, and independently normalized
geometric \(2\pi\)-KMS (Kubo--Martin--Schwinger) convergence) makes the support-visible cap modular automorphism geometric
and supplies Lorentz kinematics. Recoverable
generalized entropy together with the null modular bridge, bounded-interval transport, fixed-volume
small-ball area variation, admissible fixed-cap stationarity, and timelike tensor upgrade then
		supplies the Einstein relation. Bare finite consensus supplies only the upstream quotient-normal-form input. The screen-capacity branch proposes the dimensionless
		cosmological-constant relation below. The identification of its cosmic record-closure value with
		the electroweak bridge is conditional on CP-1 to CP-3, and the physical readback map \(F\) has
		not been constructed:
\[
N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}}),
\qquad
\Lambda_{\mathrm{CRC}}\ell_\star^2=\frac{3\pi}{N_{\mathrm{CRC}}},
\qquad
\Lambda_{\mathrm{CRC}}=\frac{3\pi}{G N_{\mathrm{CRC}}}.
\]
The last display uses the selected scale certificate \(G_{\mathrm{geom}}=\ell_\star^2\).
	The bridge formula has a certified mathematical value near \(3.532\times10^{122}\); the
	Planck-\(\Lambda\) central value near \(3.313\times10^{122}\) is lower by about \(6.6\) percent.
	A uniqueness certificate for the bridge formula does not establish uniqueness or stability of
	the missing physical map \(F\).
\item \textbf{The Standard Model quotient is selected by MAR.} Under the stated coherent transportable-sector
refinement conditions, edge sectors reconstruct a bosonic compact-gauge branch. The overlap/holonomy calculus classifies transportable sectors; it does not by itself choose the Standard Model. The realized low-energy branch
with the explicit one-generation/one-Higgs matter package and MAR then selects the compact gauge quotient, exact hypercharge,
three generations, three colors, and the structural absence of
gauge-mediated proton decay. On the ordinary electromagnetic branch, the unbroken
\(\U(1)_Q\) factor reduces the compact-gauge curvature to \(F_Q=dA_Q\); after separately
assuming the low-energy Maxwell action and its nonzero kinetic term, variation gives
\(dF_Q=0\) and \(d{*}F_Q=g_Q^2{*}J_Q\), i.e. Maxwell's equations after
canonical electromagnetic normalization.
\item \textbf{SL-3 supplies a comparison coordinate; physical loop closure is open.} The
comparison pixel
\(P_C\simeq1.6309682094\) is located from the measured fine-structure constant under SL-3:
\(\alpha^{-1}(0)=137.035999177(21)\),
\(\alpha(0)\simeq0.00729735256433\). The forward model with
the source anchor and Ward-projected electromagnetic transport measures the
loop-closure residual: \(3.0\times10^{-4}\) relative on the source chain (closure ledger row
CL-1) and \(2.5\times10^{-6}\) relative for the certified numerical gauge-width
fixed point \(\alpha^{-1}=137.035660136946577\ldots\) (CL-2), a certified fixed point of the
declared map with the Ward-projected hadronic transport open. The mixed-provenance display
packet \(137.0359595008\ldots\) is a fixed point of no single declared map and stays on record
as a display packet only. The separate root \(136.994835177413\ldots\) is an interval-certified
output of an incomplete declared map; no derivation relates it to the physical fine-structure
endpoint.
The claim table
records the source-side diagnostic trunk and endpoint residual.
\item \textbf{The framework has a regulated implementation surface.} The microphysics paper turns
the observer language into explicit finite patch carriers, edge observables, records, and repair
cycles.
\item \textbf{Edge sectors also admit two-dimensional Yang--Mills and worldsheet-style effective descriptions.} The heat-kernel
edge partition function reorganizes the same boundary data into the two-dimensional
Yang--Mills form, and on the declared large-edge branch this yields a controlled worldsheet
effective description. This 2D bridge sits beside the compact paper's controlled
compact-gauge repair-gap theorem. The string-vacuum selector uses this bridge only as the
effective edge-language input; critical worldsheet closure, Bouchard-Donagi cohomology,
operator-safety realization, threshold matching, and moduli locking remain separate gates.
\item \textbf{The compact-gauge branch carries the 4D Euclidean Yang--Mills form and isolates the
gap theorem.} On the declared controlled compact-gauge branch, with the four-dimensional
scaling chart, reflection-positive ordinary vacuum, no additional gauge-invariant relevant
dimension-four pure-gauge operator on that branch besides curvature squared, repair completeness,
and the compact paper's explicit finite cylinder system in force, OPH proves projective weak-* /
GNS extraction of a support-visible cylinder cluster family. Identification of that family with
the Euclidean Yang--Mills action additionally uses the renormalized four-dimensional
regularity/universality receipt. Weighted observation-fiber resampling is the finite
conditional-expectation projector, with the noncircular matrix-recognition criterion of
Ref.~\cite{observableNormalForms}. A concrete active repair law is identified with that projector
only after its independently extracted transition matrix passes the support, equal-fiber-row, and
weighted detailed-balance receipt. Identification of Euclidean transfer with the repair generator,
vacuum persistence, and passage of a uniform finite-stage gap use the separate finite
ground-state-transform, transfer/vacuum, OS-regularity/noncollapse, and uniform-gap receipts.
Only on that certified branch is
\(\Delta_{\mathrm{YM}}=\Delta_{\mathrm{rep}}\). Weak-* extraction alone is not the
Clay-facing axiomatic construction.
\end{enumerate}

\section{Physical Implementation and \(A_5\)/\(E_8\) Significance}

The implementation question is what must exist below the observer-level axioms so they have a
physical carrier. OPH's answer is a fixed-cutoff federation of finite patch carriers. Each carrier
exposes overlap ports, record registers, repair maps, and checkpoint interfaces. The screen is the
observer-facing geometry chart. It is not the carrier itself in the sense of one literal smooth ball.
The implementation is the finite algebraic machinery that makes compare, write, repair, and re-read
operations available.

The term ``sphere folding'' has a restricted technical meaning in this stack. It is the
observer-facing spherical presentation of the repaired quotient normal form:
\[
\operatorname{Fold}_{S,r}(s)=\chi_{S,r}\!\left(n_r(\pi_r(s))\right).
\]
The quotient map removes hidden carrier presentation, the normal-form map performs accepted
repair, and the spherical chart displays caps, collars, cuts, edge sectors, and boundary records.
Folding is therefore the geometric face of overlap repair on the screen chart.
On the consensus surface this repair is defined first as the quotient operator
\(\operatorname{Rep}_\lambda:Q\to Q\), with representative-level maps only serving as lifts, so
hidden carrier labels do not become additional physical data.

Spherical geometry carries several pieces of the construction at once. An observer-accessible cut
has a closed two-dimensional angular chart. Caps and collars on that chart supply the cut data used
by modular flow, entropy variation, and overlap comparison. The orientation-preserving conformal
group of the same \(S^2\) chart is the celestial-sphere realization of
\(\mathrm{SO}^+(3,1)\), so the sphere is the kinematic bridge between finite screen cuts and the
emergent \(3+1\)-dimensional Lorentz branch once the controlled cap-pair theorem is
satisfied. Finite cellulations of the chart provide the regulator surface on which ports, edge
sectors, and local comparison data can be made explicit; they are not by themselves a Lorentz
invariant continuum.

The echosahedral carrier is the concrete local realization of this chart data. Its multi-port
interface supplies discrete boundary directions, face and edge incidence, exposed readout
channels, record slots, and repair channels. Recurrent toroidal subchannels supply local winding
and memory structure. The smooth spherical chart describes the observer-facing cut; the
echosahedral carrier supplies the fixed-cutoff local machine whose quotient data can present that
cut.

The \(A_5\) and \(E_8\) labels mark different roles in that machinery. \(A_5\)-icosahedral symmetry
is the local finite-screen language used when a patch carrier is made concrete: it organizes ports,
faces, and overlap data with enough discrete symmetry to stabilize observer-facing cuts.
\(E_8\)-type language is the exceptional closure language used by the high-symmetry branch. It names
the root-lattice and affine exceptional structure in which the icosahedral data can sit. The term
is representation-closure language for the branches that call for it.

One finite certificate lives on the \(E_8\)-side of that split. The
\(E_8/\mathrm{Spin}(8)\) triality sidecar gives exact matrices for an \(A_8\) root subsystem inside
\(E_8\), the subgroup \(\mathrm{Alt}(9)\subset W(A_8)\cong\mathrm{Sym}(9)\), its nonsplit
\(2\!\cdot\!\mathrm{Alt}(9)\) lift in \(\mathrm{Spin}(8)\), and a positive half-spin image
preserving an \(E_8\) lattice. The vector and half-spin presentations have distinct
\(E_8/2E_8\) orbit fingerprints, \(\{9,36,84,126\}\) and \(\{120,135\}\), before Spin(8)
triality fuses them. This is a finite exceptional representation-closure receipt. It is not a
recovered-core theorem, a new particle or force, a heterotic edge-CFT proof, or hardware evidence.

This distinction matters for the synthesis paper. The physical claim lives at the observer-visible
quotient: finite patches must expose the same records and shared observables after allowed
implementation-hiding changes. The microphysics paper gives the concrete reference architecture for
that quotient surface, including the federated patch-carrier model, fixed-cutoff edge
heat-kernel/Casimir law, central-record/Born--L\"uders measurement interface, Bell/CHSH event
surface, and checkpoint/restoration package. See Ref.~\cite{ophmicrophysics}, available as the
numbered GitHub reference in the bibliography.

\subsection*{Famous equations and structural outputs recovered}

The table below maps headline formulas by logical role. Some rows are core theorem results, some
are short corollaries of recovered actions, and some are standard limits once the parent OPH
branch is established.

\begingroup
\footnotesize
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}p{0.18\textwidth}>{\raggedright\arraybackslash}p{0.30\textwidth}>{\raggedright\arraybackslash}p{0.20\textwidth}@{}}
\toprule
Recovered result & OPH role & Famous display & Support boundary \\
\midrule
\endhead
\bottomrule
\endfoot
Three-dimensional observer-frame chart, Lorentz kinematics, and invariant light cone & core theorem & \(q(\Omega)=(1,\Omega)\), \(n_C=(\cot\alpha,\csc\alpha\,\mathbf c)\), \(n_{gC}=\Lambda_gn_C\), \(H^3\simeq\mathrm{SO}^+(3,1)/\mathrm{SO}(3)\) & scaling-limit prime geometric subnet; chart population and neutral bulk are separate gates \\
Record-populated observer-facing \(H^3\) & conditional theorem & \(R_i(C,t,O)\to F(X_i)+e\), \(\alpha\bar d\le |F(X)-F(Y)|_W\), \(S_i(t)=B_H(\widehat X_i,r_i)\) & point-local calibrated cap responses, compact source domain, bounded error, quantitative cap frame, and positive gap for unique finite output \\
Einstein equation & core theorem & \(G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle\) & full Einstein-branch theorem stack; dependency discharge in Theorem E0; \(\Lambda\) fixed by the capacity branch \\
Newton-Poisson gravity & inherited weak-field limit & \(\nabla^2\Phi=4\pi G\rho\), \(\ddot{\mathbf x}=-\nabla\Phi\) & weak field and slow motion \\
Maxwell equations & electromagnetic corollary & \(dF_Q=0,\quad d{*}F_Q=g_Q^2{*}J_Q\) & ordinary \(\mathrm U(1)_Q\) branch plus explicit Maxwell action/current hypothesis \\
Yang--Mills equations & compact-gauge corollary & \(DF=0,\quad D{*}F=g^2{*}J\) & compact-gauge connection branch plus explicit Yang--Mills action/current hypothesis \\
Bekenstein--Hawking / de Sitter area law & global capacity branch & \(N_{\mathrm{scr}}=A/(4\ell_P^2)=3\pi/(G\Lambda)\) & screen-capacity closure \\
Born rule and L\"uders update & fixed-cutoff theorem & \(\mathbb P(E)=\operatorname{Tr}(\rho P_E)\), \(\rho|_E=P_E\rho P_E/\operatorname{Tr}(\rho P_E)\) & central record algebra \\
Tsirelson bound & fixed-cutoff theorem & \(|S_{\mathrm{CHSH}}|\le2\sqrt2\) & Bell event surface \\
Charge quantization & core theorem & \(Q=T_3+Y\), color singlets have \(Q\in\mathbb Z\) & quarks are confined fractional-charge fields \\
Classical carrier-mode poles & conditional action theorem & \(K_X^{\mathrm{phys}}\propto(\omega^2-c_\star^2|\mathbf k|^2)\Pi_X\) & Maxwell, perturbative pure-Yang--Mills, or pure-Einstein action/phase receipt; quantum particle gate separate \\
Coherent-matter scalar susceptibility & conditional scalar theorem & \(\chi_\nu^{\rm can}=1-P_\chi/24=0.9320429912748350\ldots\) & nondegenerate OPH-coherent material source, Scalar Edge-Center Exhaustion, and protected-reserve collar closure under the presence reading of the reserve profile; device force and covariant dark stress are separate gates \\
\end{longtable}
\endgroup

\subsection*{Particle Support Status}

The particle paper treats the closure matrix explicitly. The non-hadron
bundle has the following support levels:

Full \(W/Z\) promotion requires a strict source root, an independently physical
\(E_\star\), the finite quotient-transport certificate, a frozen RG/matching/scheme
packet, branch rigidity, prospective provenance, and complex-pole and
uncertainty receipts.

\begin{table}[h]
\centering
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}p{0.26\textwidth}>{\raggedright\arraybackslash}p{0.18\textwidth}@{}}
\toprule
Lane & Output & Role & Support boundary \\
\midrule
Carrier modes & two transverse Maxwell modes; \(2\dim G\) perturbative Yang--Mills modes; two Einstein TT modes & symmetry-protected massless classical kernels on the stated action branches & no quantum zero-mass particle row until the physical Hilbert-space, pole-residue, and phase gates pass \\
\(W/Z\) & no nonzero source-only physical mass emitted & strict source-audit zero-selector branch; exact selected-carrier chart; conditional quotient-transport implication; frozen inverse target adapter & the coordinate pairs have different provenance. The finite-carrier certificate and the source-law selection principle deciding the discrete two-law choice are not emitted, and no physical complex-pole pair is promoted \\
Fine structure & four distinct coordinates & source witness, mixed diagnostic, empirical closure, and measurement & the empirical interval misses the measured endpoint. Source-only promotion requires the OPH-QCD backend \\
Higgs/top & no nonzero source-only physical mass emitted & double-criticality family from the gauge sector; frozen boundary-scale candidate; declared-surface calibration fit kept separate & promotion inherits the boundary-scale selection theorem plus the source-root, physical-scale, running, matching, rigidity, provenance, uncertainty, and complex-pole gates \\
Charged leptons & no nonzero source-only physical mass emitted & target-anchored postdiction, exact \(A_5/C_3\) face-carrier lemma, and conditional nature/pole transport & the affine map and engineered record model remain authored. The nature bridge assumes the physical Yukawa response identity, while the pole bridge assumes the face-quotient Dyson singularity readout; its explicit zero-self-energy kernel is only a free witness. Physical source selection, attachment, interacting kernel, infrared completion, coherent branch, and cofinal refinement remain open \\
Quarks & no nonzero source-only physical mass emitted & common-scale reciprocal-ray falsification; exact six-scalar interface; restricted source-spread lower bound & the candidate fails across the audited common scales. Its old sub-percent residuals belong to a mixed-convention retrospective chart. The simulator contains no Yukawa coupling and no Yukawa information, while generation-blind flavor singlets supply no physical flavor-orbit selector \\
Neutrinos & no nonzero source-only physical mass emitted & rejected target-informed template candidate & the correlated profile rejects the candidate; the shared-basis recovery was tautological, the charged basis is open, and no source-only PMNS or absolute-mass row is emitted~\cite{nufit61} \\
Hadrons & no first-principles prediction emitted; empirical electromagnetic closure executed separately & OPH-QCD backend absent; external spectral payload integrated & source-only rows require source QCD parameters, quotient ensemble, Ward current ledger, higher-point and transition spectral exports, same-scheme remainder, and no-target-leak receipts \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Conditional and audit coordinates.}
The source-audit zero-selector law outputs the running/chart coordinates
\((80.330,91.119)~\mathrm{GeV}\), with a residual freedom of one discrete
two-law choice (\(9.3\)~MeV on the \(W\) coordinate and \(5.1\)~MeV on the \(Z\)
coordinate). These values are not commensurate with the PDG mass-dependent-width
Breit--Wigner masses or with complex-pole masses, so their numerical proximity supplies no
physical mass evidence. The selected
carrier, conditional value law, and frozen inverse target adapter give the
downstream audit coordinates
\[
\begin{array}{rcl}
\text{selected carrier} && (80.3862916924,91.1829044467)~\mathrm{GeV},\\
\text{conditional value law} && (80.3770000154,91.1879780779)~\mathrm{GeV},\\
\text{frozen inverse target adapter} && (80.3625,91.1879)~\mathrm{GeV}.
\end{array}
\]
The two-loop audit returned \((79.115335,89.802735)~\mathrm{GeV}\) in its designated primary
cell. Its prescription adds an SM two-loop increment to an MSSM one-loop baseline, making it an
inconsistent MSSM-1L+SM-2L hybrid prescription test rather than a consistent two-loop
calculation. The pole audit returned approximately
\((79.53284,89.71232)~\mathrm{GeV}\) under a partial PRTS/Feynman-gauge prescription. The
definition of \(v\), tadpole treatment, field-content and threshold matching, scale selection,
and higher-order terms remain open. These audits establish neither a unique scheme conversion
nor a unique \(1\)--\(2\%\) defect, and they do not exhaust the physical prescription family.
As a stated diagnostic under the complex-pole conversion of the PDG-2026 reference values, the
chart \(W\) coordinate differs from the converted \(W\) pole \(80.3340~\mathrm{GeV}\) by \(0.5\)
propagated experimental standard deviations, and the chart \(Z\) coordinate from its converted
pole by about \(17\); both figures carry no OPH theory covariance and acquire physical meaning
only when the physical readout contract closes.
The Higgs/top pair is read on the double-criticality branch, a
zero-continuous-parameter family whose frozen post-exposure boundary-scale
candidate \(E_\star e^{-\pi}P^{-1/6}\) gives
\((m_H,m_t)=(125.77,172.63)~\mathrm{GeV}\) at two loops, with
\(m_H=125.72~\mathrm{GeV}\) on the fit-free curve at the measured top. The
declared calibration surface \((125.1995304097,172.3523553288)~\mathrm{GeV}\)
is a target-anchored fit that validates the formula stack and never predicts.
For the quark audit at \(M_Z\),
\[
(\rho_u,\rho_d)=(1.1108888543,0.7519410008),
\qquad \rho_u\rho_d=0.8353228768,
\]
where the reciprocal ray requires one. Granting four endpoints leaves a
\(21.556\%\) held-out minimax error. The generic exact interface is
\[
(\mu_u,\sigma_u,\rho_u,\mu_d,\sigma_d,\rho_d).
\]
The
\(0.2946\%\) and \(0.29436\%\) retrospective residuals use mixed conventions,
and a lower-order ablation fits that chart better. These conditional and audit
coordinates are excluded from the particle-output ledger. Ref.~\cite{ophparticles}
contains the detailed receipt audit.

\subsection*{Stack-Wide Claim Boundary}

The paper stack uses one no-relabeling rule throughout. A finite diagnostic or
calibration field does not become a physical observable merely because it is
renamed. Capacity bookkeeping needs an independent energy readout before it can
count as mass; an archive needs a physical source, propagation, and detector
channel before it can count as radiation; a finite repair spectrum needs a
continuum operator/readout bridge before it can count as a physical spectrum;
and a finite reconstruction threshold needs physical entropy and clock data
before it can count as a Page-time claim. The compact paper records this as the
source-separation rule behind the support-level table.
The \(\chi_\nu\) scalar-channel identity is theorem-grade for nondegenerate
OPH-coherent material sources once Scalar Edge-Center Exhaustion is imported.
Device-scale force, cosmological abundance, and finite covariant dark stress
require their own receipt packages.

\paragraph{Remaining program and evidence status.}
The closure ledger groups its open rows under four generating objects and one selector. This is a
work plan, not a proof that the underlying prescription families are exhaustive. G1 is the
Ward-projected hadronic transport for CL-1 and CL-2. Its broad V1 internal-mass bracket
\(S_{\mathrm{hadronic}}\in[0.5578,1.0543]\) contains the zero-EW CL-1 point diagnostic 0.8954,
but it spans about \(1.16\times10^8\) widths of v2's historical invalid tolerance; v3
registers no active decision threshold. The value is present only in the compare-only
payload, and the evaluation pixel is not the comparison pixel. The bracket therefore carries no
promotion. G2 requires construction of the physical capacity readback map \(F\). The interval
certificate at \(3.5321315434\times10^{122}\) applies to the conditional electroweak bridge under
CP-1 to CP-3; it does not construct \(F\), and it differs from the Planck-\(\Lambda\) central
capacity by about \(6.6\) percent. G3 carries the forward electroweak chain. Its preregistered
96-entry one-loop sweep excludes entries inside that frozen menu only; higher-order, matching,
threshold, tadpole, scale, and field-content prescriptions remain open. G4 supplies numerical
solver hygiene for the declared map. Twelve preregistered flavor candidates were also excluded,
which excludes those candidates rather than the broader selector family.

A full adversarial third-party audit reproduced the certified interval arithmetic
across its forty-two findings and identified no false theorem in the recovered mathematical
core; the two implementation defects it exposed, a hadronic target-coordinate algebra error and
a finite transition-clock eligibility predicate, were repaired behind fail-closed
gates with adversarial regression tests, and the epistemic statuses printed in this paper carry
those corrections.
The evidence ledger contains zero discriminating frozen-prospective hits. The electroweak checks
freeze analysis choices against known targets, so they are audits rather than prospective
predictions. Other positive rows have theorem, conditional, retrospective, or non-discriminating
status; this accounting does not classify every positive row as retrodictive.

\subsection*{Companion Papers}

The detailed depth surfaces used throughout this synthesis are:
\begin{enumerate}[leftmargin=2em]
\item \emph{Observation-Determined Normal Forms: Stability, Obstructions, and Refinement in Constraint and Rewrite Systems}~\cite{observableNormalForms}, which gives the substrate-neutral same-source/cross-source quantifier split, endpoint and refinement bounds, collar-repair obstructions, and the finite conditional-resampling receipt used by the repair papers.
\item \emph{Recovering Relativity and the Standard Model from Observer Overlap Consistency}~\cite{ophcompact}, which gives the compact technical core for relativity, gravity, receipt-conditional combined-zero-obstruction compact-gauge reconstruction (central or higher-associator strictification plus an allowed trivial-holonomy strict representative), and MAR-selected Standard Model structure.
\item \emph{Reality as a Consensus Protocol: The Fixed-Point Computation That Implements Physics}~\cite{ophconsensus}, which carries the finite patch-net fixed-point, defect, quotient, and operator-record consensus package, with the default overlap code treated as a finite constraint code, termination separated from the local-diamond and repair-completeness conditions needed for confluence, and QECC/min-cut, spectral, BFT, and hardware-speedup claims gated by separate certificates.
\item \emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer Synchronization in OPH}~\cite{ophmicrophysics}, which carries the regulated federated patch-carrier architecture, the fixed-cutoff edge heat-kernel / Casimir theorem, and the measurement and observer checkpoint/restoration packages.
\item \emph{Deriving the Particle Zoo from Observer Consistency}~\cite{ophparticles}, which carries the particle derivations, masses, couplings, and sector calculations.
\item \emph{Theoretical Bounds on \(\chi_\nu\) in Observer-Patch Holography} and \emph{Observer-Patch Holography and Dark Matter}~\cite{ophchinu,ophdarkmatter}, which carry the coherent-matter same-channel theorem, the protected-reserve susceptibility coefficient, and the separate finite dark-stress proof obligations.
\item \emph{Explaining the Yang--Mills Mass Gap with Observer-Patch Repair Dynamics}~\cite{ophyangmills}, which isolates the controlled compact-gauge repair mechanism and states the continuum certificate needed before the finite repair gap becomes a Clay-facing four-dimensional Yang--Mills gap.
\item \emph{Observer-Patch Holography as a String-Vacuum Selector}~\cite{ophstringselector}, which treats string theory as an effective edge language and applies OPH gates to critical-string candidates, with the Bouchard-Donagi witness conditional on its open certificates.
\end{enumerate}

The sections that follow give the synthesis view. Detailed proof burdens sit with the companion
papers and with the late dependency checklist in this paper.

\def\OPHSkipEmbeddedReferences{1}
\input{tex_fragments/PAPER.tex}
\input{tex_fragments/OBSERVERS_SYNTHESIS_SECTIONS.tex}

\appendix
\input{tex_fragments/OBSERVERS_APPENDICES.tex}
\input{tex_fragments/OBSERVERS_REFERENCES.tex}

\section*{Statements and Declarations}

\noindent\textbf{Funding declaration:} The authors declare that no external grants or dedicated
third-party research funding were received for the preparation of this manuscript.

\noindent\textbf{Author af\kern0pt f\kern0pt iliations declaration:} Bernhard Mueller is af\kern0pt f\kern0pt iliated with
Pragma Inc., Washington, USA. Alexander Osika is af\kern0pt f\kern0pt iliated with SNRGY Inc.,
Gothenburg, Sweden. No institutional af\kern0pt f\kern0pt iliations were declared for Mario Poneder, Kai
Xue, Ben Cassie, Peter Nguyen, Maarten Antonie Visser, Kale Arnav Anirudha, David Matscheko, or
Jonathan Hill in this submission.
Correspondence email addresses are provided in the correspondence declaration.

\noindent\textbf{Consent to Participate declaration:} not applicable.

\noindent\textbf{Consent to Publish declaration:} not applicable.

\noindent\textbf{Author Contribution declaration:} Bernhard Mueller developed the OPH concept,
mathematical formulation, paper-stack synthesis, main manuscript text, release integration, and
submission package. Alexander Osika contributed to the OPH/Karma and OMEGA hardware path,
experimental prototype framing, hardware evidence boundary, and submission review. Mario Poneder
contributed proof and validation work on the hierarchy certificates, the edge-entropy area-law
route to the Einstein/Newton coupling, coupling normalization, particle and neutrino certificate
surfaces, and manuscript/book consistency surfaces. Kai Xue contributed broad paper-stack work,
including audit passes, consistency checks, implementation-surface review, simulator and OPH
Universe evidence-surface feedback, receipt and visualization data-surface review, and prototype
engineering boundary review. Ben Cassie contributed audit work across the hardware evidence
surface, implementation claims, receipt boundary, experimental-prototype framing, and submission
package. Peter Nguyen contributed proof-surface hardening, branch-boundary audits, claim-tier
alignment across the paper and book stack, Yang-Mills and compact-gauge status surfaces, finite
packet-quotient closure, fine-structure certification surfaces, and manuscript consistency passes.
Maarten Antonie Visser contributed to the P/N=24 repair-resonance material, consensus-protocol
consistency review, and physics feedback on the foundations and emergent-spacetime framing. Kale
Arnav Anirudha contributed consensus-paper material, formal review of the consensus-protocol
surface, QBFT assumptions, FLP citation handling, repair-map definitions, QECC notation,
asynchronous bound wording, and the BFT/QECC appendix material. David Matscheko provided the
OPHProofChain Lean 4 formalization and audit campaign for the consensus repair, Rule-90
boundary-reconstruction, Route-A assembly, finite modular-flow, Einstein-algebra,
hypercharge/\(Z_6\), scalar-channel/collar/channel-bridge, dark-sector, energy-cage, and
run-matrix theorem surfaces; he also provided audit material for the dark-sector and
coherent-matter susceptibility surfaces and contributed to the anti-gravity experiment path. All
authors reviewed and approved the manuscript.

\noindent\textbf{Correspondence declaration:} Correspondence should be addressed to Bernhard
Mueller, \href{mailto:bernhard@floatingpragma.ai}{\texttt{bernhard@floatingpragma.ai}}, and
Alexander Osika, \href{mailto:alex@snrgystudios.com}{\texttt{alex@snrgystudios.com}}.

\noindent\textbf{Data Availability declaration:} The paper stack, source manuscripts, public
release PDFs, simulation code, and implementation notes are available through the OPH project
repository and linked public release surfaces. Some hardware and prototype evidence requires a
sanitized ancillary audit bundle before external release because raw logs may include device
configuration, operational metadata, or private infrastructure details. The intended audit bundle
contains source hashes, simulator configs, finite-receipt JSON, verifier code, hardware acceptance
records, calibration logs, and selected run traces sufficient to replay the stated implementation
claims.

\noindent\textbf{Code Availability declaration:} The OPH simulator, finite-consensus harnesses,
visualization payload schemas, and public paper build sources are maintained in the OPH project
repositories. Submission artifacts include a standalone source file and a source bundle so that the
manuscript can be rebuilt without relying on private local paths.

\noindent\textbf{Ethics declaration:} not applicable.

\noindent\textbf{Competing Interests declaration:} The authors participate in OPH-related research
and implementation programs, including prototype hardware and simulator development. The authors
declare no external competing financial interests for this manuscript.

\noindent\textbf{Use of AI-assisted tools declaration:} AI-assisted tools were used for language
editing, drafting assistance, formatting support, and submission-package preparation. The authors
reviewed and remain responsible for all scientific content, claims, references, and declarations.
\end{document}
