\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{booktabs,array,longtable}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{seqsplit}
\input{release_info.tex}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.08}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\SU}{\mathrm{SU}}
\newcommand{\U}{\mathrm{U}}
\newcommand{\Conf}{\mathrm{Conf}}
\newcommand{\nf}{\operatorname{nf}}
\newcommand{\ellbar}{\bar{\ell}}
\newcommand{\ophid}[1]{\path{#1}}
\newcommand{\decnum}[1]{\vcenter{\hbox{\parbox{0.68\linewidth}{\small\ttfamily\seqsplit{#1}}}}}

\title{Recovering Relativity and the Standard Model\\
from Observer Overlap Consistency}
\author{B.\ M\"uller \and Alexander Osika \and Mario Poneder \and Kai Xue \and Peter Nguyen \and Maarten Antonie Visser \and David Matscheko}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{abstract}
Observer-Patch Holography starts from a finite screen and one rule: neighboring observer patches must agree on their overlap. The compact argument takes that rule to the main structural branch of the theory.

On the certified spherical branch, finite repair and modular geometry lead to
the exactly three-dimensional observer-frame hyperboloid, a conditional
\(3{+}1\)-dimensional event manifold, the Einstein branch, and receipt-conditional
compact gauge reconstruction. On the realized branch this gives the Standard Model quotient,
exact hypercharge and charge quantization, three colors, three generations, the
Maxwell sector, and a Yang--Mills repair-gap route with its transfer
conditions. Standard Model content enters through the admissibility clauses of
Axiom~5 (MAR); given those clauses, the anomaly and center algebra follow;
realized-branch nonemptiness is open. The quantitative stack also carries a conditional de Sitter
capacity target whose readback map and coupling premises remain open, separates the source-audit,
empirical, and measured fine-structure
coordinates, and organizes conditional particle and weak-scale branches.  Its
clean quantitative output is a dimensionless hierarchy and a zero selected-chart
Higgs naturality defect. Source-only particle pole masses and flavor spectra
remain open.
\end{abstract}

\section{Introduction}

Physics is usually presented in two boxes. One box contains spacetime and gravity. The other contains the particle world. This paper asks whether both can be recovered from a smaller starting point: a finite screen whose neighboring observer patches must agree on their overlaps.

The dimensional statement on the spherical branch is exact rather than a
numerical fit. Once the support-visible screen receipts produce \(S^2\), its
conformal group fixes \(\mathrm{SO}^{+}(3,1)\), and the corresponding
observer-frame space
\(H^3=\mathrm{SO}^{+}(3,1)/\mathrm{SO}(3)\) has exactly three dimensions.
When the event-population, separation, rank-four-frame, and overlap-cocycle
receipts below also hold, three conditioned spatial responses plus one modular
clock give an atlas in \(\mathbb R^4\) with signature
\((-{+}{+}{+})\). A noninteger value returned by a finite-sample correlation,
nearest-neighbor, diffusion, or feature-space estimator is therefore a
diagnostic of that estimator, its record features, finite resolution, or a
failed manifold-population receipt; it is not an alternative
fractional-dimensional physical bulk and does not redefine either \(H^3\) or
the receipt-certified event manifold. Conversely, the exact identity
\(\dim H^3=3\) is observer-frame kinematics and does not by itself prove that
the repaired records populate an objective event manifold. That logically
separate promotion is why the event receipts remain explicit.

The computation in this paper uses fixed-point language, but OPH does not define simulation as a
bare fixed point. A conventional frame-rendering computation would evolve surrogate universe states
\(U_t\to U_{t+1}\to\cdots\). OPH instead studies a readback-and-repair operator on
observer-facing world candidates and asks for stable normal forms \(W\) satisfying
\(\mathcal T(W)=W\). The companion consensus paper requires recovery-derived endogenous update,
nontrivial quotient-readable records, overlap repair with schedule-independent normal form,
elimination of a proper candidate basin in the selected boundary or sector fiber, and implementation
and clock closure. It proves those clauses for the selected finite packet under its stated branch
and record hypotheses and gives a generic fixed-point or variational counterexample
\cite{ophconsensus}. The repair schedule is a theorem device for selecting quotient normal forms;
it is not a one-to-one clock for cosmic time. In the fundamental description there is no global
timeline that renders spacetime contents tick by tick; history is the internal readout of the
selected normal form.

The scope of observer time is correspondingly narrow. The recovered-core theorem in this paper gives a
schedule-independent terminal quotient normal form and, on the BW branch, a modular parameter for
the extracted observer-facing cap pair. It does not by itself prove that worker counters, repair
iterations, queue positions, packet latencies, or wall-clock timestamps define observer history or
observer clock time. Scheduler-independent observer-readable histories require a separate
history-augmented quotient, semantic event identities independent of executor metadata, a descended
global observer registry, observer-algebra extraction, and an operational clock-instrument
calibration. Those are certificate gates instead of implementation field names.

That certified consistency requirement drives a long structural chain. It explains why the Lorentz group appears, why the low-energy spacetime description follows a Jacobson-type Einstein branch, why the gauge structure is
\[
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6},
\]
why the observed three colors and three generations are realized, why strong/color, weak-isospin, hypercharge, and electric-charge assignments take their observed form, how the conditional electroweak and flavor continuations are organized, and what the framework can and cannot say about the cosmological constant and possible dark-sector continuations.

This paper presents the compact reconstruction program based on Observer-Patch Holography (OPH).
Physical data are organized patchwise: each observer has access only to a patch algebra,
neighboring observers must agree on overlaps, and the reconstruction is driven by those
consistency conditions. Under the five axioms and the branch hypotheses and theorems stated below,
that structure feeds a Lorentzian modular-phase classification, a Jacobson-type Einstein branch,
receipt-conditional compact gauge reconstruction in a bosonic internal-gauge sector, color and electroweak charge
quantization, and the low-energy architecture fixed on the realized Minimal Admissible Realization (MAR) gauge branch.
Finite horizon/collar record statements are structural support inside the horizon-screen branch.
Black-hole spectroscopy, Page-curve/island, evaporation, QNM/ringdown, dark-sector, and
particle-family continuations belong to companion or continuation surfaces.

The paper separates exact structural theorems, scaling-limit branches, quantitative outputs, and phenomenological continuations. Several longer arguments are written in compressed proof form so the support boundary stays readable.

The framework is presented as a reconstruction program in which general relativity and the Standard Model appear as effective sectors derived from the stated quantum-algebraic axiom set, explicit refinement constructions, and the controlled BW scaling theorem. This theory-of-everything framing is a claim about recovering the observed effective universe from that basis and its declared branch hypotheses, not a demand that every mathematical ingredient be derived from a blank starting point. In the gauge lane, the logical split is explicit: overlap and holonomy data classify fixed-stage transportable sectors and obstruction routing; on a cofinal tail carrying the compact-gauge refinement receipt, Doplicher--Roberts/Tannaka reconstruction yields a compact group from their tensor-generated bosonic colimit category; MAR plus the realized one-Higgs chiral matter package selects the Standard Model quotient on the realized branch.

\subsection*{Main Results}

The results emphasized in this paper are ordered below by a combination of impact and defensibility.

\begin{enumerate}[leftmargin=2em]
\item A Jacobson-type Einstein branch is recovered from observer-overlap modular geometry, the controlled BW scaling theorem on the prime geometric subnet, and the derived fixed-cap generalized-entropy stationarity theorem for admissible fixed-cap MaxEnt variations on the realized cap-label-preserving MaxEnt family; in the null modular bridge, quasi-local propagation, exact-or-controlled strip additivity, endpoint-Lipschitz renormalized half-line control, the resulting weak tail generator, and the half-sided modular pair are supplied internally by the null-interval structure and the scaling-limit geometric action, after which Borchers--Wiesbrock yields the explicit positive null-translation generator on its Stone domain together with the affine half-line modular relation and the half-line generator/charge identification with the local null-stress charge on that same family; the Einstein side then uses the internal small-ball bridge from the geometric cap generator together with the bounded-interval kernel discharged in Lemma~\ref{lem:bounded-interval-kernel}, and the later tensor upgrade states its all-directions/all-reference-states conditions explicitly on that scaling branch. Three packets sharpen the entry into this branch: a quotient-intrinsic geometry producer derives the screen \(S^2\), its conformal/cap structure, and the finite cap-normal BW certificate from repair normal forms on a computable-receipt branch, with an underdetermination no-go showing confluence alone selects no topology, dimension, framing, or normalization (\S\ref{subsec:quotient-intrinsic-geometry-producer}); the null net is proved standard with a derived half-sided inclusion, a Markov modular-locality theorem replacing the earlier global-locality inference (with an explicit counterexample boundary), M\"obius bounded-interval covariance, and a four-translation assembly with future-cone spectrum (\S\ref{subsec:null-net-standardness}); and a conditional Lorentzian event manifold is constructed from repaired records, an event base of signature \((-{+}{+}{+})\) over which \(H^3\) is strictly the frame fiber, under explicit population/separation/frame/cocycle receipts, with countermodels showing \(\dim H^3=3\) promotes nothing by itself (\S\ref{subsec:event-manifold}). The closure packets complete the chain: a local conserved stress tensor is constructed from the directional modular charges by null tomography (with a countermodel showing per-direction generators alone admit no rank-two source), the generalized-entropy first law is repaired to carry the edge/center term exactly and its stationarity is extended to the coupled changing-stress class by the exact multiplier identity, one uniform scaling family replaces the per-radius diagonal choice, a vacuum-reference receipt converts first-variation constancy into the absolute semiclassical equation \(G_{ab}+\Lambda g_{ab}=8\pi G\langle T_{ab}\rangle\) with the structural coupling, and the entire chain is composed into one typed branch-entry theorem with a no-hidden-geometry audit; realized-branch nonemptiness is a machine-checkable gate and is open work in progress (\S\ref{subsec:einstein-branch-closure}).
\item The exact Standard Model gauge structure
\[
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6}
\]
is recovered on the receipt-certified realized MAR-admissible branch of the bosonic compact-gauge theorem; together with the one-Higgs package it fixes the structural electroweak force content \(\SU(2)_L\times\U(1)_Y\to\U(1)_Q\) and the \(W^\pm/Z/A_Q\) generator and connection directions. The abelian connection has \(F_Q=dA_Q\). After independently assuming the low-energy Maxwell action and a nonzero kinetic coefficient, its variation also gives \(dF_Q=0\) and \(d*F_Q=g_Q^2*J_Q\), i.e. Maxwell's equations after canonical electromagnetic normalization. The structural part is a realized-branch gauge result with explicit refinement-receipt, matter-package, and admissibility inputs; the action, numerical \(W/Z\) masses, and mixing are additional quantitative-branch data.
\item On the controlled compact-gauge branch, OPH derives the four-dimensional
Euclidean Yang--Mills form from compact-gauge holonomy data and the local MaxEnt/Gibbs
continuum limit. On a finite weighted quotient, observation-fiber resampling is the orthogonal
conditional-expectation projector, with the noncircular matrix-recognition criterion proved in
Ref.~\cite{observableNormalForms}. A concrete collar repair kernel has that status only after its
independently extracted transition matrix passes that receipt. A uniform positive repair gap
transfers to the compact-gauge Hamiltonian only on a
branch with the multiresolution continuum, reflection-positivity, transfer/intertwiner, and
nontriviality certificate. On that certified branch the Yang--Mills gap is the repair gap for
every compact simple group carried by the OPH branch. Without that certificate, the finite repair
construction remains a regulator mechanism instead of a Clay-admissible four-dimensional
construction.
\item On the realized one-generation chiral matter plus one-Higgs package, anomaly constraints and Yukawa invariance fix the hypercharge lattice, the realized color triplet fixes \(N_c=3\), and the same one-Higgs quark branch then fixes \(N_g=3\) from CKM phase counting, weak-sector asymptotic freedom, and MAR.
\item The quantitative implementation used here exposes one certified fixed point of an incomplete local map, \(P_\star\), and one global fixed-point target, \(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})\), plus a selected no-\(G\) scale certificate expressed as \(\gamma_\star=\ell_\star\nu_{\mathrm{Cs}}/c\), or equivalently \(B_\star=3\pi/\ell_\star^2\). Measurements locate comparison neighborhoods. A physical local endpoint requires the missing same-scheme hadronic transport. The global endpoint requires a constructed readback map, a fixed-point certificate, discharge of CP-1--CP-3, and the de Sitter entropy identification.
\item Downstream matter-sector continuations, including the charged-lepton exact centered-readback / common-shift frontier, are visible but explicitly outside this SM/GR derivation paper's recovered-core theorem package.
\item Conditional on construction of the capacity readback map, certification of its fixed point, discharge of CP-1--CP-3, and identification with the de Sitter entropy capacity, the same Einstein branch closes globally at the cosmic record-capacity fixed point. This conditional relation ties the cosmological term to global screen capacity instead of local vacuum energy; the SI scale display is supplied separately.
\item Exclusion of gauge-mediated proton decay follows from product-group structure; any stronger proton-lifetime claim is UV/EFT/QCD-dependent.
\item Dark-sector, heuristic baryogenesis continuations, string, and spectroscopy branches are kept visible only as phenomenological continuations or, where additional ans\"atze are involved, conjectural phenomenology.
\item A bare overlap net is a finite constraint code: codewords are the globally overlap-consistent states \(C=\Phi^{-1}(0)\). On the declared finite quotient branch, overlap repair induces a total local map \(\operatorname{locRep}_\lambda:Q\to Q\) and a total idempotent global repair map \(\operatorname{Rep}_\lambda:Q\to Q\) that is boundary-preserving, schedule-independent, and lands in \(C_Q\). Strict descent gives termination, while atomic conflict-component transactions plus repair completeness give confluence. Same-boundary uniqueness additionally requires a preserved boundary/sector map whose consistent quotient fiber has a unique extension; the layered finite carrier proves \(H_B\wedge H_{\mathrm{fib}}\), and on the functional selected-fiber branch multiple same-boundary candidate interiors are nontrivially eliminated while all surviving candidates share one quotient normal form. Settled-form hashes are evidence records for quotient equality, not selectors among physically distinct endpoints. The same package induces refinement-limit normal-form and holonomy classes on separated cofinal refinement systems with compatible projections, and makes reconciliation commute with coarse-graining up to explicitly declared normal-form and obstruction defects. QECC distance, min-cut resilience, exponential convergence, BFT wall-clock liveness, and hardware speedup are separate certified branches, not consequences of a generic overlap graph.
\item The fixed-cutoff topological UV package closes on the ordinary branch, the central-defect branch, and the genuinely noncentral branch through a compact crossed-module higher-gauge collar theorem; the controlled continuum BW/geometric lift is supplied by Theorem~\ref{thm:bw}, while the realized compact-gauge branch is supplied by the compact-gauge witness and physical-UV landing theorem below.
\end{enumerate}

\subsection*{What This Paper Contributes}

The compact paper is the technical bridge from observer overlap to the familiar structural laws.
Its ingredients are deliberately recognizable. Lyapunov descent and Newman's lemma handle
finite repair. Bisognano--Wichmann modular theory supplies the modular-geometric template.
Jacobson's 1995 and 2016 arguments supply the entropy-to-Einstein comparison target
\cite{jacobson95,jacobson16}. Doplicher--Roberts/Tannaka reconstruction supplies the compact
group reconstruction language.

The OPH addition is the observer-patch route into those tools. Repair is a recovery-derived move
on visible overlaps, with holonomy marking the place where local agreement fails globally. The
Lorentz branch is read from controlled cap modular flow after the finite collar and recovery
controls are carried through the scaling limit. The Einstein branch is Jacobson-type, and OPH supplies the fixed-cap
generalized-entropy stationarity theorem, null-stress bridge, internal small-ball bridge, carried
remainders, and the all-directions tensor upgrade on its stated branch.

The gauge result is equally specific. On a cofinal tail carrying the compact-gauge refinement
receipt, compact gauge structure is reconstructed from the tensor-generated zero-obstruction
transportable sector category and its forgetful fiber; MAR then selects the realized Standard Model
quotient on the declared one-Higgs chiral matter package. The same branch fixes exact
hypercharge, charge quantization, the realized color triplet, and the generation count. The
cosmological term is handled globally: the local Einstein branch leaves the metric term open, and
the proposed screen-capacity fixed point would close it on the de Sitter capacity row after its
readback map, fixed-point certificate, coupling premises, and entropy identification are supplied.
Its status is conditional global completion; no
discharged dark-energy result follows.

The later quantitative rows use the structural branch as their carrier. They add \(P_\star\),
the capacity target \(N_{\mathrm{CRC}}\), and the selected scale certificate as closure coordinates with
declared uniqueness tests. Failure of one quantitative row does not erase the recovered core unless
that row is a parent of the theorem being used.

D.\ Matscheko's OPHProofChain Lean 4 audit~\cite{matschekoProofChain} supplies an independent
machine-checked finite-algebra companion for the parts of this paper that are
genuinely finite: quotient repair and same-boundary reconstruction criteria,
the finite binary boundary-reconstruction carrier, finite modular flow with the
KMS boundary condition and matrix-algebra uniqueness, the Einstein-branch tensor
algebra and \(\lambda\)-constancy step, the hypercharge/\(\mathbb Z_6\) algebra,
the scalar channel bridge, the collar-channel bookkeeping, twelve-port surface
bookkeeping, selected numerical cage checks, and the finite QBFT quorum-overlap
caveat.  That audit does not discharge the physical or scaling-limit branch
hypotheses themselves: BW/geometric identification, generalized-entropy
stationarity, MAR, collar instantiation, \(P\)'s source branch,
record-to-gravity calibration, and the continuum transfer assumptions remain
exactly the declared inputs tracked in the dependency table.

\subsection*{Jacobson comparison and reduction limit}

The gravity result is Jacobson-type by design. The intellectual debt is explicit: Jacobson's 1995
argument uses local Rindler horizons and the Clausius relation; Jacobson's 2016 argument uses
small geodesic balls and fixed-volume entanglement equilibrium. OPH adds the observer-patch
machinery that gets to that route from finite observer-visible data.

\begingroup
\footnotesize
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.18\textwidth}>{\raggedright\arraybackslash}p{0.20\textwidth}>{\raggedright\arraybackslash}p{0.22\textwidth}>{\raggedright\arraybackslash}p{0.28\textwidth}@{}}
\toprule
Dimension & Jacobson 1995 & Jacobson 2016 & OPH \\
\midrule
\endhead
\bottomrule
\endfoot
Basic region & local Rindler horizon & small geodesic ball & observer-visible screen cap or local diamond \\
Entropic premise & Clausius relation & fixed-volume entanglement equilibrium & derived fixed-cap generalized-entropy stationarity on the realized cap-label-preserving family \\
Modular input & Unruh/Rindler structure & small-ball modular input & controlled cap modular flow and null bridge \\
UV handling & continuum thermodynamics & continuum QFT & finite collar, recovery map, refinement limit \\
Error handling & thermodynamic approximation & first-order and matter caveats & explicit collar and derivative remainders on the stated branch \\
Tensor upgrade & all local horizons & all ball directions & overlap-supplied local directions and reference-state clauses \\
Cosmological term & integration ambiguity & reference-state term & separate conditional cosmic record-capacity target \\
Claimed OPH delta & foundational result imported & foundational result imported & finite observer-patch route, regulator/collar control, and separate conditional global target \\
\end{longtable}
\endgroup

\begin{proposition}[Reduction to the Jacobson small-ball limit]\label{prop:oph-jacobson-reduction}
On the type-I, exact-Markov, vanishing-collar-remainder, maximally symmetric small-cap limit of the
OPH Einstein branch, the fixed-cap stationarity relation of Theorem~\ref{thm:equilibrium} reduces
to Jacobson's fixed-volume small-ball entanglement-equilibrium relation.
\end{proposition}

\begin{proof}
The type-I clause turns the cap modular generator into the special operator form used by the
small-ball modular Hamiltonian. Exact Markovity removes the recovery defect in the collar split.
The vanishing-collar-remainder assumption removes the OPH finite-cutoff correction terms carried
by the null bridge and the small-ball transport. The maximally symmetric small-cap limit identifies
the OPH cap-label-preserving MaxEnt variation with the fixed-volume ball variation. Under those
identifications, the OPH fixed-cap generalized-entropy stationarity equation has the same first
variation as Jacobson's entanglement-equilibrium relation. The subsequent local quadratic
polarization/tensor step is the standard upgrade listed in the D5 row.
\end{proof}

\begin{proposition}[OPH delta relative to the Jacobson limit]\label{prop:oph-jacobson-delta}
Relative to the reduction limit of Proposition~\ref{prop:oph-jacobson-reduction}, the OPH branch
adds controlled modular extraction, finite-cutoff collar recovery, explicit remainder
bookkeeping, observer-overlap direction completion, and an independent conditional global-capacity
target for the cosmological term.
\end{proposition}

\begin{proof}
The added clauses are exactly the hypotheses and outputs of Theorem~\ref{thm:bw},
Theorem~\ref{thm:stress}, Theorem~\ref{thm:equilibrium}, Lemma~\ref{lem:smallball},
Theorem~\ref{cor:einstein}, and Theorem~\ref{thm:lambda-stack}. Removing those clauses leaves
the Jacobson-type limit described above; keeping them is the OPH-specific branch.
\end{proof}

\subsection*{Famous recovered formulas by support status}

The compact paper uses the following public-facing map. Core theorem results, corollaries, and
inherited limits are separated by their branch conditions.

\begingroup
\footnotesize
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}>{\raggedright\arraybackslash}p{0.17\textwidth}>{\raggedright\arraybackslash}p{0.31\textwidth}>{\raggedright\arraybackslash}p{0.19\textwidth}@{}}
\toprule
Recovered formula or output & Support status & Display & Boundary \\
\midrule
\endhead
\bottomrule
\endfoot
Lorentz transformations and light cone & core theorem & \(\mathrm{Conf}^+(S^2)\cong\mathrm{SO}^+(3,1)\) & prime geometric BW branch \\
Einstein field equation & core theorem & \(G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle\) & E0 dependency discharge; local branch leaves \(\Lambda\) open \\
Newton-Poisson limit & inherited limit & \(\nabla^2\Phi=4\pi G\rho\), \(\ddot{\mathbf x}=-\nabla\Phi\) & weak field, slow motion \\
Maxwell equations & conditional corollary & \(F_Q=dA_Q,\ dF_Q=0,\ d{*}F_Q=g_Q^2{*}J_Q\) & electromagnetic connection branch plus explicit Maxwell action/current hypothesis \\
Yang--Mills equations & conditional corollary & \(F=dA+A\wedge A,\ DF=0,\ D{*}F=g^2{*}J\) & compact-gauge connection branch plus explicit Yang--Mills action/current hypothesis \\
Bekenstein--Hawking / de Sitter area law & conditional global closure & \(N_{\mathrm{scr}}=A/(4\ell_P^2)=3\pi/(G\Lambda)\) & readback map and capacity-coupling premises open \\
Charge quantization & core theorem & \(Q=T_3+Y\), observable color singlets have \(Q\in\mathbb Z\) & fractional quarks are confined colored fields \\
Classical carrier-mode poles & conditional action theorem & \(K_X^{\mathrm{phys}}\propto(\omega^2-c_\star^2|\mathbf k|^2)\Pi_X\) & Maxwell, perturbative pure-Yang--Mills, or pure-Einstein action/phase receipt; quantum particle gate separate \\
Colors and generations & core theorem & \(N_c=3,\quad N_g=3\) & flavor masses are separate continuations \\
\end{longtable}
\endgroup

On that same fixed-cutoff consensus surface, the support split is sharp: normal-form computation is
a finite-state decidable problem with the Lyapunov step bound from the consensus paper, the only
automatic approximate-stability inputs are the collar-local splice and record estimates carried
there. Long-run noisy approximate consensus is theorem-level only on the separate fair-block
contraction branch, where the implementation supplies \((\lambda,\varepsilon,A,\beta,L)\) for
distance to the exact quotient normal-form set. Computational expressiveness for growing
patch-net families is a separate consensus-paper complexity boundary instead of a recovered-core
dependency. The same firewall applies to coding
language: the default code is a finite constraint code, while topological-code distance/min-cut and
Knill--Laflamme resilience require explicit topological-code and error-model certificates.
The imported consensus package is the fixed-cutoff theorem stack: the quotient repair operators
\(\operatorname{locRep}_\lambda\) and \(\operatorname{Rep}_\lambda\) for the declared
recovery-derived repair law after transactional acceptance; asynchronous confluence, with
termination separated from the atomic conflict-component local diamond and repair-completeness
clauses; the layered \(H_B\wedge H_{\mathrm{fib}}\) carrier; the functional selected-fiber
branch-elimination theorem; the cycle-obstruction / higher-gauge defect package,
gauge-quotient descent, observable-level confluence on the declared physical observable algebras,
the refinement-limit normal-form / holonomy theorem, the repair-morphism criterion that discharges
exact normal-form naturality, the distributed one-universe realization theorem for admissible
worker presentations of one global carrier, the controlled coarse-graining / reconciliation
square, the no-free-min-cut boundary for bare graphs, and the record-algebra theorem on the observer-accessible surface. The imported consensus
branch conditions are repair completeness, validation-complete transactional read sets with exact
descent and preserved boundary/sector data, and the stated Petz support/CPTP clause where that branch is used.
The scaling-limit bridge from that fixed-cutoff patch-net package to the Lorentz, Einstein, and
compact-gauge branches is separate; the consensus paper supplies the intermediate inverse-limit
normal-form and holonomy theorem once the cofinal refinement projections commute with finite-stage
normal forms and holonomy maps, and it supplies the approximate RG/reconciliation comparison once
the chosen coarse-graining channel has controlled normal-form and obstruction defects.

\section{Overview of Results}

This section summarizes the support levels used throughout. The table below is the formal dependency
map for this SM/GR derivation paper. The recovered core contains fixed-cutoff overlap repair and
collar structure, the Lorentz/null-modular/Einstein branch, receipt-conditional bosonic compact gauge reconstruction,
and the realized-branch Standard Model quotient with exact hypercharge, structural electroweak force content, \(N_c=3\), and \(N_g=3\)
under the explicit matter-package and admissibility inputs. The quantitative rows contain the
conditional screen-capacity target for the same Einstein branch and the pixel-driven electroweak/gauge-coupling
branch. The continuations contain flavor details beyond the stated theorem surfaces, dark-sector
proposals, heuristic baryogenesis branches, spectroscopy, hadrons, and string/worldsheet
effective-description branches. The canonical five-axiom basis, the quantitative quantities listed
next, the controlled BW scaling theorem, and the fixed-stage/receipt-conditional gauge chain used below are
fixed in Section~\ref{sec:theorem-ledger}. Each row names a node in the reconstruction program,
records its immediate internal parents, separates imported standard mathematics from declared
external inputs, and states the resulting support level.

\paragraph{Theorem key for the table.}
For the recovered core, the scaling/BW step is Theorem~\ref{thm:bw}, the controlled BW scaling theorem. The compact-gauge nontriviality step is handled by the compact-gauge witness and physical-UV landing theorem. The fixed-cap generalized-entropy stationarity result is Theorem~\ref{thm:equilibrium}. Transportability and the fixed-cutoff bosonic category are theorem-produced by Theorems~\ref{thm:transport-from-gluing} and \ref{thm:fixed-cutoff-bosonic-sector-category}; refinement/fiber descent is Theorem~\ref{thm:refinement-functor-fiber-descent} conditional on the explicit receipt of Definition~\ref{def:compact-gauge-refinement-receipt}.

\begingroup
\tiny
\setlength{\tabcolsep}{1pt}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.05\textwidth}>{\raggedright\arraybackslash}p{0.16\textwidth}>{\raggedright\arraybackslash}p{0.14\textwidth}>{\raggedright\arraybackslash}p{0.13\textwidth}>{\raggedright\arraybackslash}p{0.20\textwidth}>{\raggedright\arraybackslash}p{0.16\textwidth}@{}}
\caption{Dependency checklist for the OPH SM/GR reconstruction program.}\\
\toprule
Node & Output & Immediate internal ingredients & Standard mathematics used & Branch-local inputs / external data & Support level \\
\midrule
\endhead
\bottomrule
\endfoot
\textbf{D1} & Total local and global quotient repair maps \(\operatorname{locRep}_\lambda,\operatorname{Rep}_\lambda:Q\to Q\); unique schedule-independent normal form from each fixed initial physical quotient state; boundary-conditioned uniqueness under a preserved boundary/sector map with unique consistent extension; layered finite \(H_B\wedge H_{\mathrm{fib}}\) carrier; nontrivial same-boundary branch elimination on the functional selected-fiber branch; observable-level confluence on the declared fixed-cutoff physical algebras for the recovery-derived repair relation, inverse-limit normal-form / holonomy classes on separated cofinal refinement systems, distributed one-universe realization for admissible worker presentations of a single global carrier, and controlled reconciliation/coarse-graining compatibility & overlap-consistency problem on a finite patch net together with the declared fixed-cutoff collar recovery proposal, its touched-overlap local-fit eligibility contract, transactional snapshot/read/write validation with boundary/sector preservation and exact descent, support-local disjoint commutation, restriction-compatible union-collar gluing for canonical conflict-component payloads on the physical quotient, the fixed-point / quotient-local physical observable algebras carried by that same collar package, cofinal refinement projections compatible with finite-stage normal forms and holonomy maps, a distributed physical projection from authoritative worker state to the monolithic quotient, and a coarse-graining channel with declared normal-form and obstruction defects & local-to-global well-founded descent; local-diamond completion from atomic conflict-component commits using validation-complete read sets; Newman's lemma; layered functional boundary reconstruction; rooted functional extension for selected fibers; inverse limits of separated finite quotient systems; reachability invariance of the quotient normal form under projected repair paths, physical stutters, and certified rollbacks; pseudometric control of commuting coarse-graining diagrams & repair completeness; stated Petz support/CPTP control where that branch is used; for same-boundary uniqueness, preservation of the boundary/sector map and at most one consistent quotient extension in the fiber, or the layered/functional selected-fiber theorem with explicit obstruction/ambiguity gates; repair-morphism normal-form naturality, holonomy cochain naturality, visible separation, explicit coarse-graining defect bounds for the refinement system, and distributed certificates for global carrier, partition, cut interfaces, linearized commits, restart roots, final monolithic readout, and normal-form hash evidence only after quotient equality is proved & Phase I structural theorem \\
\textbf{D2} & Collar Markov/entropy split, finite-range Gibbs conditional-mixing theorem, and \(G\)-dictionary setup (Theorems~\ref{thm:collar-cmi-decay}, \ref{thm:markovcollar}; Propositions~\ref{prop:approxrecover}, \ref{prop:splice}, \ref{prop:gensplit}; Definition~\ref{def:newton}) & Axioms~\ref{ax:screen}--\ref{ax:entropy} plus the strong conditional Gibbs mixing premise off the exact central-interface branch & HJPW Markov structure theorem; matrix conditional-log-density mixing; Petz and Fawzi--Renner recovery theory & the scalar CMI bound has explicit uniform constants and a boundary-count prefactor; ordinary two-point clustering does not imply the required conditional mixing; the scaling limit requires \(\delta/\xi-\log|\partial C|_{\mathrm{UV}}\to+\infty\), not merely \(\delta/\ell_{\mathrm{UV}}\to\infty\); exact block-factorized identities require exact Markovity plus the Markov-split alignment hypothesis (Definition~\ref{def:ecaligned}; both derived under the declared central-interface collar clause of Axiom~\ref{ax:maxent}, Theorem~\ref{thm:msaderivation}); the \(A/(4G)\) step is the coarse-grained dictionary of Definition~\ref{def:newton} & conditional theorem with exact central-interface specialization \\
\textbf{D3a} & Regularized support-visible modular transport on fixed cap-local algebras & Axioms~\ref{ax:screen}--\ref{ax:entropy}, collar Markov/recovery package, and Theorem~\ref{thm:geosubnet} & weak-\(*\)/GNS extraction; modular theory with regularized finite generators & fixed-collar comparison errors, cutoff schedule, and multiresolution reference tower; no full finite-algebra spectral floor is assumed & theorem \\
\textbf{D3b} & Finite cap-normal and support-order certificate & D3a plus a cofinal nondegenerate cap mesh & spherical cap geometry; de Sitter cap-normal compactness; finite support-order reflection & BW-framed caps, support-order faithfulness, mixed-GNS Cauchy residuals, and support covariance; this certificate is not produced by bare finite consensus inside D3, and on the producer branch it is produced from the computable incidence/mesh/cross-ratio/normalization receipts (Theorem~\ref{thm:certificate-production}), whose selection is proved underdetermined by confluence (Theorem~\ref{thm:incidence-underdetermination}) & Theorem~\ref{thm:finite-cap-bw-certificate} hypothesis; produced on the D3h receipt branch \\
\textbf{D3c} & Oriented cross-ratio and framed-cap rigidity & D3b & M\"obius/cross-ratio rigidity on \(S^2\) & held-out separated quartets and an orientation witness; fitted anchors alone carry no validation value & theorem under certificate \\
\textbf{D3d} & Geometric \(2\pi\)-KMS normalization & D3b--D3c & KMS uniqueness for faithful normal states & independently normalized geometric parameter \(h_{\widehat C}(z)\mapsto e^{-s}h_{\widehat C}(z)\), finite strip bounds, and wrong-\(\beta\) separation & theorem under certificate \\
\textbf{D3e} & Support-visible BW cap automorphism \(\sigma_t=\alpha_{\lambda_{\widehat C}(2\pi t)}\) (Theorem~\ref{thm:bw}) & D3a--D3d & Bisognano--Wichmann modular template at automorphism level & type-I generator form includes \(K_C=2\pi B_C+Z_C\); in the generic non-type-I case the automorphism identity is the theorem & corollary \\
\textbf{D3f} & Exact cap-normal Lorentz/\(H^3\) chart: \(S^2\simeq\mathbb P\mathcal N^+\), \(\operatorname{Cap}^{\mathrm{or}}_{\mathrm{round}}(S^2)\simeq dS_3^{\mathrm{cap}}\), \(n_{gC}=\Lambda_g n_C\), and \(H^3\simeq\mathrm{SO}^+(3,1)/\mathrm{SO}(3)\) (Corollaries~\ref{cor:lorentz}, \ref{cor:h3-spatial-chart}) & D3e plus oriented round-cap extraction and time orientation & projective future-null-cone geometry; \(\mathrm{SL}(2,\mathbb C)\) Hermitian-matrix realization; Lorentz homogeneous-space and hyperboloid geometry & a cap determines an \(H^3\) plane/half-space, not a preferred observer point; population, neutral bulk, physical \(R_H\), stress, and Einstein dynamics remain separate gates & exact conditional geometric theorem \\
\textbf{D3g} & Conditional record-populated \(H^3\) localization (Corollary~\ref{cor:conditional-record-populated-h3}) & D3f plus record-conditioned modular cap responses, point-local source factorization, compact source domain, quantitative cap frame, bounded error, and residual optimization & hyperbolic cap half-spaces, finite conditioned frames, finite \(\varepsilon\)-nets, and residual inverse-stability estimates & point locality is a branch hypothesis or finite receipt; noisy finite uniqueness requires \(\Delta_{\mathrm{loc}}>0\); species, stress, neutral bulk, and Einstein entry are not implied & conditional theorem \\
\textbf{D3h} & Quotient-intrinsic geometry producer and dimension-selection boundary: support-visible incidence complex, topology/conformal/cap production, certificate production from computable receipts, and the confluence-underdetermination no-go (Lemma~\ref{lem:incidence-invariance}; Theorems~\ref{thm:topology-production}, \ref{thm:conformal-cap-production}, \ref{thm:certificate-production}, \ref{thm:incidence-underdetermination}) & D1 normal forms plus the spherical incidence, disk/mesh, modular cross-ratio, and \(2\pi\)-normalization receipts & classification of closed combinatorial surfaces; Rad\'o uniqueness; M\"obius cross-ratio rigidity on \(S^2\) & the receipts are decidable finite-stage predicates on normal forms, not declared geometry; their selection is not implied by confluence (explicit \(T^2\), \(\partial\Delta^4\), wedge, and wrong-\(\beta\) countermodels); \(S^2\) and its conformal class are derived only on the receipt branch & producer theorem plus underdetermination no-go \\
\textbf{D4} & Null modular bridge to \(T_{kk}\), including exact-or-controlled strip additivity, endpoint-Lipschitz renormalized half-line families, the weak tail generator, the derived half-sided modular inclusion, the explicit positive half-line null-translation generator on its Stone domain with affine half-line modular relations, and the exact half-line generator/charge identification with the local null-stress charge (Propositions~\ref{prop:nullec}, \ref{prop:n3}; Corollaries~\ref{cor:n1}, \ref{cor:n2}; Theorem~\ref{lem:density}, Lemma~\ref{lem:translation}; Theorem~\ref{thm:stress}) & D2+D3 and Axioms~\ref{ax:screen}--\ref{ax:entropy} & Borchers--Wiesbrock positive-generator theorem for standard half-sided inclusions; Stone's theorem; distributional differentiation on half-lines & the theorem-local null-cut center transfer, the inherited left/right strip-split package used for the spatial-collar-type tensor decomposition, and the exact-or-controlled Markov hypotheses of Proposition~\ref{prop:nullec} and Corollary~\ref{cor:n1}; quasi-local propagation and endpoint-Lipschitz control are supplied internally by Axiom~\ref{ax:maxent} on the local finite-constraint branch; the geometric scaling action on the null half-line blow-up net derives the half-sided modular pair; bounded-interval formulas are discharged by Lemma~\ref{lem:bounded-interval-kernel}; null-net standardness, the derived half-sided inclusion, M\"obius bounded-interval covariance, Markov modular locality with its counterexample boundary, and the four-translation assembly are supplied by Theorems~\ref{thm:null-net-standardness}--\ref{thm:four-translation-assembly}, with the \(\mathsf{Cyc}\), \(\mathsf{NTI}\), weak-additivity, \(\mathsf{MI}\), and kernel-residual receipts explicit & Phase I bridge theorem plus D4-standardness packet \\
\textbf{D4b} & Conditional Lorentzian event manifold: quotient-intrinsic event classes, conditional four-dimensional atlas with signature \((-{+}{+}{+})\), causal order and time orientation, \(H^3\) strictly as frame fiber, tetrads/metric/connection/curvature readout, glued modular clocks, and countermodels (\S\ref{subsec:event-manifold}) & D3f--D3h and D4 outputs plus the population, separation, rank-four frame, and overlap-cocycle receipts \(\mathsf{E1}\)--\(\mathsf{E4}\) & bi-Lipschitz atlas arguments; convex-cone/quadric signature classification; Rademacher/Carath\'eodory regularity & \(\mathsf{E1}\)--\(\mathsf{E4}\) with \(\mathsf{E4'}\)/smooth upgrade, the \(\mathsf{MI}\)/assembly branch, absolute conformal scale, stable causality, and the record-Cauchy receipt remain explicit; countermodels show \(\dim H^3=3\) promotes nothing by itself & conditional construction theorem \\
\textbf{D4c} & Local conserved stress tensor from modular charges: null tomography, constructed \(\langle T_{ab}\rangle\) with symmetry/locality/covariance/common normalization, generator/charge identification, weak Ward identity, ambiguity classification (Theorems~\ref{thm:null-tomography}, \ref{thm:local-stress-construction}; Proposition~\ref{prop:no-local-stress-countermodel}) & D4/D4b outputs plus the \(\mathsf{MI}\)/assembly branch, kernel-residual receipt, and universal-coupling receipt \(\mathsf{UC}\) & null polarization/tomography of symmetric tensors; least-squares stability & \(\phi g_{ab}\) and improvement ambiguities explicit; \(\mathsf{UC}\) is a physical-identification receipt; countermodel: per-direction generators without \(\mathsf{MI}\) linearity admit no rank-two source; scalar CMI is never promoted & conditional construction theorem \\
\textbf{D4d} & Bulk/edge/central first law with the edge term carried exactly, algebraic type-I boundary statement, and MaxEnt stationarity extended to the coupled changing-stress class via the exact multiplier identity \(dS/dt=\lambda=2\pi\) (Theorems~\ref{thm:bulk-edge-central-first-law}, \ref{thm:maxent-lagrange-stationarity}; Proposition~\ref{prop:entropy-coefficient-countermodel}) & central-interface branch of Axiom~\ref{ax:maxent}, type-I generator form \(K_C=2\pi B_C+Z_C\), edge normalization \(z_\alpha=\log d_\alpha\) & finite first law \(\delta S=\langle K\delta\rho\rangle\); MaxEnt envelope/Legendre identity & the Axiom-4 leading term and edge normalization are named branch axioms; shape/null-cut and metric variations are not covered; countermodels: wrong coefficient or wrong edge weights break stationarity by computable defects & exact finite theorem plus conditional bridge \\
\textbf{D5} & Jacobson-type Einstein branch: rest-frame relation plus tensor upgrade (Theorem~\ref{thm:equilibrium}, Lemma~\ref{lem:smallball}, Theorems~\ref{thm:fixed-volume-small-ball-area}, \ref{thm:einstein}, \ref{cor:einstein}) & D3+D4 and Axioms~\ref{ax:screen}--\ref{ax:entropy} & fixed-volume area-variation identity for small geodesic balls; local quadratic-polarization argument for the tensor upgrade & Theorem~\ref{thm:equilibrium}, which fixes the admissible fixed-cap MaxEnt variation class and derives generalized-entropy stationarity on the realized cap-label-preserving MaxEnt family; the internal small-ball bridge of Lemma~\ref{lem:smallball}, which uses the geometric cap generator together with the D4 half-line generator/charge identification and Lemma~\ref{lem:bounded-interval-kernel}; Theorem~\ref{thm:fixed-volume-small-ball-area}; locally Lorentzian \(d=4\) scaling regime, supplied conditionally by the D4b event-manifold packet under receipts \(\mathsf{E1}\)--\(\mathsf{E4}\) (\S\ref{subsec:event-manifold}); small-ball constancy assumptions; Lemma~\ref{lem:diagonal-remainder} for \(o(\ell^4)\) control; all local directions/reference states for the tensor upgrade via Lemma~\ref{lem:cap-pair-timelike-coverage}; the uniform scaling family, coverage, and absolute base condition are supplied by Theorems~\ref{thm:uniform-scaling-family}--\ref{thm:absolute-einstein-base-condition} under the \(\mathsf{VR}\)/\(\mathsf{UC}\) receipts, and the full chain is composed in Theorem~\ref{thm:einstein-branch-entry-composed} with realized-branch nonemptiness open (Remark~\ref{rem:realized-branch-status}) & Phase I scaling-limit theorem package plus composed branch-entry theorem \\
\textbf{D6} & Conditional local/global theorem stack for \(\Lambda\): null-invisible metric ambiguity, proposed screen-capacity closure of the same Einstein branch, the de Sitter entropy relation with scale-certified static-patch display, and the cosmic record-closure target, plus a legacy capacity-level neutrino side estimate (Theorem~\ref{thm:lambda-stack}) & D5 local Einstein recovery leaves a \(+\Lambda g_{ab}\) ambiguity & de Sitter entropy relation, static-patch radius/time formulas after scale certification, finite self-closing normal-form density/readback map, and dimensional analysis & constructed readback map \(F\), fixed-point certificate, CP-1--CP-3, and the conditional identification \(N_{\mathrm{CRC}}=S_{\mathrm{dS}}\) & Phase II global self-closure target; map and premises open \\
\textbf{D7} & Construction of the refinement-stable bosonic sector category plus compact gauge reconstruction (Theorem~\ref{thm:refinement-functor-fiber-descent}, Theorem~\ref{thm:sector-colimit}, Theorem~\ref{thm:compactgauge}), the conditional four-dimensional Euclidean Yang--Mills form (Theorem~\ref{thm:oph-4d-euclidean-yang-mills-form}), and the conditional compact-gauge repair-gap theorem (Theorem~\ref{thm:oph-yang-mills-gap}) & Axioms~\ref{ax:screen}--\ref{ax:entropy} plus the compact-gauge refinement receipt & directed-colimit descent for monoidal \(C^*\)-categories; Doplicher--Roberts / Tannaka reconstruction; holonomy-to-curvature expansion; finite-stage conditional expectations and spectral comparison for commuting collar projections & Theorems~\ref{thm:transport-from-gluing} and \ref{thm:fixed-cutoff-bosonic-sector-category} on the ordinary or central-defect bosonic zero-obstruction branch, plus Definition~\ref{def:compact-gauge-refinement-receipt} for Theorem~\ref{thm:refinement-functor-fiber-descent}; the compact-gauge witness theorem supplies realized MAR-admissible data, while D8--D9 contain Standard Model selection; the Yang--Mills statements additionally require the finite cylinder/projective extraction theorem and the renormalized Yang--Mills, finite ground-state-transform/cross-fiber, transfer/vacuum, OS-regularity/noncollapse, and uniform-gap receipts; the genuinely noncentral fixed-cutoff branch remains separate & Phase I conditional structural theorem \\
\textbf{D8} & Product gauge structure up to finite quotient (Lemmas~\ref{lem:mincontent}--\ref{lem:commutant}, Theorem~\ref{thm:sm}) & D7 + Axiom~\ref{ax:mar} & compact Lie representation classification; Schur's lemma & the same ordinary or central-defect bosonic branch as D7, together with a connected positive-dimensional Lie admissible class, one connected abelian factor, and faithful action on the minimal coupled carrier & Phase I realized-branch theorem \\
\textbf{D9} & Realized Standard Model quotient, hypercharges, structural electroweak force content, \(N_c=3\), \(N_g=3\), and product-group corollaries (Theorem~\ref{thm:realized-sm-branch}, Theorem~\ref{thm:hypercharge}, Corollaries~\ref{cor:nc}, \ref{cor:ng}, \ref{cor:electroweak-force}, Proposition~\ref{prop:z6}) & D8 & anomaly-cancellation algebra; Witten global-anomaly argument; CKM CP counting; stabilizer computation for a nonzero neutral Higgs vacuum vector & realized one-generation chiral matter plus one Higgs package, with the CP-capability and weak-sector UV clauses contained in Axiom~\ref{ax:mar}; no extra post-MAR selector is used & Phase I realized-branch theorem/corollary chain \\
\textbf{D10} & Forward gauge-coupling closure and declared electroweak readout of the integrated D10 quantitative-closure package & D9 + pixel ratio \(P\) & printed RG evolution, matching, and scheme-conversion conventions & pixel constraint and the first-principles forward transmutation solve \(\mathcal F(\alpha_U;P)=0\); the fixed-cutoff edge heat-kernel / Casimir theorem on the microphysics surface together with the compact-group / Peter--Weyl lift used on the D10 lane; printed beta-function, threshold, and scheme-conversion conventions & Phase II quantitative-closure sector \\
\textbf{D12} & Charged-lepton exact centered-readback / common-shift frontier, strong-CP branch, texture, \(H^3\) record-worldline stitch certificates, dark-sector, heuristic baryogenesis continuations, black-hole spectroscopy and evaporation/ringdown bridges, proton-spin, proton-lifetime estimates beyond the gauge-channel exclusion, controlled large-\(N_{\mathrm{edge}}\) string/worldsheet effective descriptions, conjectural critical-superstring extensions, and other continuations & various subsets of D6, D9, and D10 & branch-specific EFT and phenomenological manipulations & additional ans\"atze such as the uniform \(\mathbb Z_6\) center-label ensemble, discrete texture choices, declared \(H^3\) atlas and cross-boundary record-assignment certificates, dark-sector response assumptions, discrete-horizon assumptions, physical black-hole bridge objects for exterior time, radiation entropy, flux closure, radiative quotient, and asymptotic readout, a distinct large-\(N_{\mathrm{edge}}\) regime with fixed \(\tau=tN_{\mathrm{edge}}\) window and uniform genus-remainder control, or additional worldsheet/CFT assumptions & Phase III phenomenological continuation branch \\
\end{longtable}
\endgroup

The recovered core of this SM/GR derivation paper is D1--D5 together with D7--D9. Within that package, D7 is the bosonic sector-category construction plus compact-gauge reconstruction stage, while D8--D9 are realized-branch results that keep the realized one-generation chiral matter plus one-Higgs package and MAR admissibility inputs explicit. D6 sits outside that recovered core because it proposes a separate global completion of the Einstein branch. D5 leaves the metric term undetermined. D6 would close that same branch at \(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})\) after construction of \(F\), a fixed-point certificate, discharge of CP-1--CP-3, and the conditional identification \(N_{\mathrm{CRC}}=S_{\mathrm{dS}}\). Under those hypotheses, the standard de Sitter entropy relation and the selected no-\(G\) scale certificate would supply the static-patch display. The density \(\log|\Omega^{\mathrm{sc}}_N|-N\) is the proposed finite-count representation of the target after division by the full screen Hilbert-space dimension \(e^N\). Informally, the target is where the universe reads back its own boundary without deficit or slack. D10 is the integrated quantitative-closure branch, and D12 collects phenomenological continuations. The modular-anomaly dark-sector branch belongs to D12: it imports the D6 static-patch scale only as an IR benchmark and does not derive MOND/RAR-style response laws, a controlled galaxy-scale source/response law, or galaxy/cluster phenomenology. The downstream capacity coordinate is therefore a conditional D6 target rather than an emitted branch datum.

\paragraph{Exceptional finite-symmetry sidecar.}
The finite \(E_8/\mathrm{Spin}(8)\) triality certificate belongs beside D7 as an algebraic
representation-closure sidecar, not as a new recovered-core input. It records an exact
matrix-level \(A_8\subset E_8\) root subsystem, the even subgroup
\(\mathrm{Alt}(9)\subset W(A_8)\cong\mathrm{Sym}(9)\), a nonsplit
\(2\!\cdot\!\mathrm{Alt}(9)\) lift in \(\mathrm{Spin}(8)\), and a positive half-spin image that
preserves an \(E_8\) lattice. The vector and half-spin presentations have different mod-2 orbit
fingerprints on \(E_8/2E_8\setminus\{0\}\), namely \(\{9,36,84,126\}\) and \(\{120,135\}\), and
are identified only after adjoining the outer triality automorphism. This supports finite
exceptional representation bookkeeping on the compact-gauge side. It does not select the realized
Standard Model quotient, add a force or particle, prove OPH, close a heterotic critical-edge gate,
or count as hardware evidence.

Cosmology continuations above D6 obey the same firewall. The flat-FLRW reading is allowed only as a
clocked-FLRW holonomy identification statement: spatial curvature is read from the spatial
Levi--Civita connection on a declared clock slice, and zero curvature is the zero visible spatial
holonomy branch. Selection of that branch is separate Phase III data: a direct no-curvature theorem,
a conditional cosmological-minimal-holonomy selector, or an explicit flat-branch assumption. MAR
acts on low-energy gauge/matter packages and is not a cosmological flatness selector. Conditional
screen-spectrum continuation is
theorem-level only after the cosmology companion supplies the geometric collar-volume scalar
\(q_r=\Pi_{\ge2,r}(1/3)\log(J_{X,r}/\bar J_{X,r})\), a normalized positive scalar precision
operator \(K_r\), a first-principles quotient ensemble, the expected scalar release energy
\[
E_r^{\rm src}=\frac12\mathbb E_{\mu_r}[q_r^{\mathsf T}K_rq_r],\qquad
A_r=2E_r^{\rm src}/d_r,
\]
refinement convergence, and an operator-derived or otherwise proved tilt.  The resulting
screen-level covariance is \(C_\ell^q\), not \(C_\ell^{TT}\).  A primordial curvature
spectrum follows only after separate source-stress, radial-window, null-space, forward-residual,
and scale-bridge certificates convert \(A_q\) to \(A_\zeta\).  The special \(P_\star/48\) tilt is
a theorem-level value only if the edge-center reserve, half-collar scalar projection, and
reserve-to-RG Ward identity pass. This package is a Phase III conditional continuation, not a
recovered-core output. Full inflation replacement, physical TT/TE/EE scalar or parity transfer,
\(H_0/S_8\) prediction, dark/anomaly growth kernels, and baryogenesis require their finite
covariant Boltzmann-source, transfer, frozen-likelihood, source-provenance, pooled-reducer, and
no-data-use contracts and are not supported by the D6 capacity relation.

\begin{corollary}[Cosmological physical-scale continuation boundary]
The controlled Lorentz branch and the \(H^3\) observer-facing spatial chart determine the
kinematic target and spatial dimension of the recovered core.  They do not, by themselves, construct
a populated finite FLRW spatial metric, source-shell embedding, comoving Laplacian, physical
wavenumber \(k\), scale-factor history, or freezeout surface.  The constants \(P_\star\),
\(N_{\mathrm{CRC}}\), and \(\ell_\star\) do not identify one implementation patch with one physical
cell; neutral quotient pseudometrics are not automatically physical spatial metrics.  Physical CMB
promotion is therefore a Phase III conditional claim and must cite the finite physical
scale-bridge theorem: imported frozen FLRW geometry gives only the
\texttt{CONDITIONAL\_PHYSICAL} tier, while the \texttt{OPH\_NATIVE\_PHYSICAL} tier also requires a
quotient-derived \(\mathsf{CosmoGeomRead}_r\) and source embedding theorem.  The aggregate physical
scale-bridge receipt is required in addition to the finite source, transfer, and likelihood
receipts.
\end{corollary}

\begin{corollary}[Physical cosmology promotion conjunction]
Physical CMB, BAO, lensing, growth, RSD, and \(S_8\) claims require
\[
\mathsf{CMB\_READY}
=
\mathsf{SOURCE}\wedge
\mathsf{SCALE}\wedge
\mathsf{PARENT}\wedge
\mathsf{KERNEL}\wedge
\mathsf{INIT}\wedge
\mathsf{TRANSFER}\wedge
\mathsf{FREEZE}\wedge
\mathsf{LIKE}.
\]
The scale term is the conjunction of
\(\texttt{PHYSICAL\_SPATIAL\_K\_RECEIPT}\),
\(\texttt{SCREEN\_TO\_PHYSICAL\_K\_ASSOCIATION\_RECEIPT}\),
\(\texttt{SOURCE\_ANGULAR\_SECTOR\_RECEIPT}\),
\(\texttt{CALIBRATED\_A\_EVOLUTION\_RECEIPT}\),
\(\texttt{PHYSICAL\_MODE\_FREEZEOUT\_MAP\_RECEIPT}\),
\(\texttt{PHYSICAL\_FREEZEOUT\_SURFACE\_RECEIPT}\), a common primordial/anomaly mode-basis receipt,
nonempty cross-receipt identity, and no-post-hoc-calibration receipt.
Here \(\mathsf{PARENT}\) includes finite packet kinematics, mass shell,
finite packet stress readout, variational/moment stress agreement,
reaction-channel four-momentum, explicit recipient stress for nonzero exchange,
exchange-current closure, total stress closure, local-frame and carrier-quotient
invariance, cosmological gauge invariance, finite domain of dependence,
subluminal characteristics, retarded response, response stability, refinement,
and CDM-limit recovery receipts.  A visually successful TT curve or a source
table with \(\rho_A\), \(\rho_{A,\mathrm{eq}}\), and \(B_A\) does not
instantiate this conjunction.  Before the active fiber, conserved-sector
decomposition, physical clock, and common-parent response pole are certified,
the transition number is only \(\gamma_{\mathrm{repair\ step}}\), not
\(\Gamma_{\mathrm{rec}}\).  While the conjunction is false, the correct class is
diagnostic baseline or conditional OPH prediction, not recovered-core physics.
\end{corollary}
\section{Five Axioms, the Phase-II Pixel Fixed Point, the Capacity Target, the Scale Certificate, and Theorem Checklist}\label{sec:theorem-ledger}

This section states the theorem checklist and dependency map for this SM/GR derivation paper. The basis used below consists of the five core axioms, the quantitative quantities listed next, the controlled BW scaling theorem, and the fixed-stage/receipt-conditional bosonic gauge-reconstruction chain. This is an algebraic-information basis: the screen-net, state, trace/probability, and generalized-entropy structures are starting ingredients of the OPH framework. The purpose is to test whether this basis supports a coherent theory-of-everything reconstruction of the observed effective universe. On the fixed-cutoff local finite-constraint MaxEnt branch, the local-Gibbs form, quasi-local dynamics, Lieb--Robinson propagation control, and endpoint-Lipschitz interval control are internal consequences. Any Dobrushin/local-Gibbs/mixing language used below names only a sufficient fixed-cutoff collar-recoverability mechanism on that branch. It is not an infinite-volume uniqueness claim for the refinement-limit theory. What Axiom~\ref{ax:maxent} fixes under refinement is the realized state-side MaxEnt branch itself. Theorem~\ref{thm:geosubnet} fixes the operational/geometric split at fixed cutoff, and Theorem~\ref{thm:bw} fixes the controlled scaling-limit cap automorphism, its \(2\pi\) normalization, and the Lorentz-facing geometric cap action on that subnet. Corollary~\ref{cor:n2} then derives the null half-sided modular pair after the null blow-up step, and Lemma~\ref{lem:translation} promotes that pair to the explicit positive null-translation generator on its Stone domain with the affine half-line modular relation. Theorem~\ref{thm:equilibrium} internalizes the fixed-cap generalized-entropy stationarity step for admissible fixed-cap MaxEnt variations on the realized cap-label-preserving MaxEnt family. The compact-gauge realized branch is supplied by Theorem~\ref{thm:mar-witness-landing}. The bounded-interval transport/projective branch is a branch-local construction only where those interval formulas are invoked. Gluing-side path-independent transport is Theorem~\ref{thm:transport-from-gluing}; refinement-limit compact-gauge reconstruction additionally requires Definition~\ref{def:compact-gauge-refinement-receipt}. On the central branch the combined zero-obstruction condition is \([z]_\Sigma=0\) together with trivial sector holonomy after strictification. On the genuinely noncentral branch, the higher associator must be strictifiable, \(o^{(2)}_\Sigma=0\), and at least one allowed strict \(G_\Sigma\)-valued \(1\)-cocycle representative must have trivial represented holonomy. A nonzero \(o^{(2)}_\Sigma\) is routed to the fixed-cutoff higher-gauge sector, while a strictifiable orbit for which every strict representative has residual loop holonomy is excluded from ordinary compact-group reconstruction; the full orbit \(q_\Sigma\) does not canonically select one ordinary \(H^1\) class.

The formulation uses one local dimensionless closure coordinate, one conditional global-capacity
target, and one selected no-\(G\) scale certificate:
\begin{align}
P &\equiv a_{\mathrm{cell}}/\ell_\star^2,\\
N_{\mathrm{CRC}} &\equiv \log \dim \mathcal H_{\mathrm{tot}}\quad\text{(conditional capacity target)},\\
\gamma_\star&\equiv \frac{\ell_\star\nu_{\mathrm{Cs}}}{c},
\qquad
B_\star\equiv \frac{3\pi}{\ell_\star^2}.
\end{align}
The notation \(N_{\mathrm{CRC}}\) specifies the intended global coordinate and does not assert that
the readback map, its fixed point, or the capacity-coupling premises have been constructed.
In the quantitative implementation used here, \(P\) is the local particle-physics scale variable
fixed by the outer/inner closure program summarized in the synthesis paper
\emph{Observers Are All You Need}~\cite{ophsynthesis}; this compact paper uses it only as the
quantity carried by the forward particle-physics map. That closure writes the outside
detuning as
\[
P=\varphi+\alpha_{\mathrm{in}}(P)\sqrt{\pi},
\]
where the inner side is the electromagnetic observation scale emitted by the same cell on the
declared quantitative branch. The CODATA-conditioned comparison coordinate is
\[
\alpha^{-1}(0)=137.035999177(21),\qquad
\alpha\simeq0.00729735256433,\qquad
P_C\simeq1.6309682094.
\]
Here \(P_C\) is defined from the measured CODATA/NIST endpoint. A source-only fixed point requires
the OPH-QCD endpoint map and its interval certificate; the comparison coordinate does not supply
that missing map.
The source computation runs in the order
\[
P\mapsto M_U(P)\mapsto\alpha_U(P)\mapsto\alpha_i(m_Z;P)\mapsto
a_0(P)\mapsto A_T(P),
\]
where \(A_T(P)=\alpha_{\mathrm{em}}^{-1}(0;P)\) is the Ward-projected Thomson
endpoint. A complete source cell must solve
\(P=\varphi+\sqrt{\pi}/A_T(P)\).
The fine-structure value would be forced on this branch once a certified
unique root is shown, because the same local pixel
must satisfy the outer entropy-detuning equation and the inner electromagnetic
endpoint equation with no remaining free local scale.
The source-audit artifact, before the low-energy hadronic endpoint
transport is supplied, records the candidate
\[
\alpha_{\mathrm{root}}^{-1}
=136.994835164621649457949994585787\ldots.
\]
It is a branch witness, not a full endpoint proof: the printed
\(P_{\rm cand}=1.630972095694329\ldots\) and inverse width do not exactly
satisfy the displayed fixed-point identity, and the full Ward-projected
\(A_T(P)\) self-map requires an interval existence-and-uniqueness
certificate.
For this incomplete declared source map, converged precision-100 reruns supersede both printed tails: the certified root is
\(\alpha_{\mathrm{root}}^{-1}=136.994835177413\ldots\) (interval-certified unique fixed
point, enclosure width \(7.2\times10^{-24}\)), the certified forward pixel is
\(P_{\mathrm{fwd}}=1.630972095858897\ldots\), and the identity
\(\alpha_{\mathrm{root}}=(P_{\mathrm{fwd}}-\varphi)/\sqrt{\pi}\) holds to more than 35
digits (CL-6, closed).
For comparison bookkeeping, adding the finite-screen unified gauge-width contribution evaluated at
the CODATA-derived comparison pixel, \(\alpha_U(P_C)=0.041124336195630495\), to the source/root
value gives the mixed-provenance no-hadron diagnostic
\[
A_{\alpha_U}^{\mathrm{fp}}
=136.994835164621649457949994585787\ldots
+0.041124336195630495
=137.035959500817279952949994585787\ldots.
\]
The certified fixed point of the incomplete gauge-width map is
\(\alpha^{-1}=137.035660136946577\ldots\); its residual against the measured
\(137.035999177(21)\) is \(2.5\times10^{-6}\) relative (about \(1.6\times10^{4}\)
measurement sigma; CL-2). The displayed \(137.0359595008\ldots\) mixes the inner value
evaluated at \(P_{\mathrm{fwd}}\) with \(\alpha_U\) evaluated at the SL-3 pixel, is not a
fixed point of any single declared map, and stays on record as a display packet only.
A separately labeled OPH-plus-empirical closure imports the measured
\(e^+e^-\!\to\mathrm{hadrons}\) cross-section payload.  In that execution,
\[
\Delta\alpha_{\mathrm{had}}^{(5)}(M_Z)
=0.0267591200153\pm0.0007524955365,
\]
and the transported Thomson coordinate is
\[
\alpha_{\mathrm{emp}}^{-1}(0)=136.2636589431,
\qquad
\alpha_{\mathrm{emp}}^{-1}(0)\in
[136.1583832834,136.3690975240],
\qquad
P_{\mathrm{emp}}=1.6310415204.
\]
This is an integrated empirical payload, not an OPH source theorem.  The
measured endpoint (137.035999177) lies outside its interval; the corresponding
same-scheme anchor correction is
\([0.6485541111,0.8547920666]\) inverse-alpha units.  The empirical result is
therefore distinct from both the source/root witness and the mixed-provenance
no-hadron diagnostic.
An observer inside the realized branch does not measure either no-hadron
source-side value as the Thomson-limit fine-structure constant. A low-energy
measurement probes the dressed \(\U(1)_Q\) current after charged-lepton vacuum
polarization, confined-quark/hadron spectral transport, and same-scheme endpoint
matching have been transported to \(q^2=0\). At that mixed comparison coordinate, the
CODATA/NIST-minus-diagnostic bookkeeping gap is
\[
\Delta^{\mathrm{fp}}_{\mathrm{H,req}}
=137.035999177
-137.035959500817279952949994585787\ldots
=0.000039676182720047050005414213\ldots.
\]
Normalized by the comparison-pixel value \(\alpha_U(P_C)=0.041124336195630495\),
this correction is
\[
\Delta^{\mathrm{fp}}_{\mathrm{H,req}}
=\alpha_U(P_C)\,(C_{24,Q}-1),\qquad
C_{24,Q}=1.0009647859732326253849511140702475\ldots.
\]
The full root-to-CODATA difference
\[
\Delta^{\mathrm{fp}}_{\mathrm{H,cal}}
=137.035999177-\alpha_{\mathrm{root}}^{-1}
=0.041164012378350542050005414213\ldots
=\alpha_U(P_C)C_{24,Q}
\]
is bookkeeping; it includes the comparison-pixel \(\alpha_U(P_C)\) contribution and is
not a source-emitted hadronic correction.
The proximity to \(\alpha_U\) is a branch-scale clue rather than an identity or
source-only endpoint prediction. The 24-register count explains the scale. It
does not determine the nonconstant Ward-projected hadronic spectral functional.
A source-only fine-structure endpoint requires an OPH-QCD hadronic backend, not
a fitted scalar residual. Its minimum receipt bundle must expose the QCD
quotient ensemble, source QCD parameter map, Euclidean slab/vacuum-transfer
construction, hadronic Hilbert quotient, Ward-normalized electromagnetic current
ledger, positive two-current spectral export \(d\rho_Q^{(2)}\), same-scheme
remainder \(\Xi_Q\), and no-target-leak source DAG. The two-current measure is
only the marginal needed for running-\(\alpha\) and HVP transport; it does not
by itself close HLbL or rare-decay long-distance amplitudes, which require the
higher-point and transition spectral sectors of the same backend. Concretely,
the source-only fine-structure endpoint requires
\(\texttt{WARD\_Q\_SPECTRAL\_MEASURE\_RECEIPT}\),
\(\texttt{J24Q\_SOURCE\_JACOBI\_RECEIPT}\),
\(\texttt{OMEGAQ\_NORMALIZATION\_RECEIPT}\),
\(\texttt{XI\_SAME\_SCHEME\_REMAINDER\_RECEIPT}\),
\(\texttt{NO\_THOMSON\_TARGET\_LEAK\_DAG}\),
\(\texttt{FULL\_PIXEL\_CONTRACTION\_INTERVAL}\), and
\(\texttt{ALPHA\_PREDICTION\_BEATS\_DIRECT\_MEASUREMENT}\) under the
direct-measurement interval adopted for that release.
Neither certified declared-map root is a physical Thomson-limit endpoint. The
V1 exploratory grid emitted
\[
S_{\mathrm{eff}}\in[0.5578,1.0543]
\]
against the required comparison value \(S_{\mathrm{req}}=0.8954\).  The interval
contains the comparison value, but its width is \(1.17\times10^8\) times the
registered pass tolerance. V1 was not target-blind: its source embedded target
constants, its directing session had target access, and its source and target
used different \(P\) values and payload coordinates. This containment is an
exploratory grid check with no promotion weight. It neither closes the source map nor verifies
\(\alpha(0)\).  A physical endpoint requires a source-derived same-scheme
hadronic backend and a contraction certificate for the completed map.
A separate hardware note reports an optical-cavity check of the same fixed-point
geometry; this is treated as an engineering reproducibility check with no discriminating OPH
weight. The technical
endpoint table in Section~\ref{sec:claim-tiers} records the source-side diagnostic
trunk and residual package.
\(\gamma_\star\) is the primary dimensionless scale certificate on the observation-located branch
interval, with \(B_\star\) as its SI curvature display. It is not solved from \(P\), from the
capacity \(N_{\mathrm{CRC}}\), from measured \(G\), or from \(\Lambda=3\pi/(GN)\). Once the
certificate is supplied, \(\ell_\star^2=3\pi/B_\star\), \(\ell_P^2\) is the usual SI
Planck-area display of \(\ell_\star^2\), and
\(G_{\mathrm{SI}}=c^3\ell_\star^2/\hbar\).
The no-\(G\) burden of this scale certificate is the clock hierarchy. In the synthesis paper
this is stated as the OPH clock-hierarchy theorem. The displayed interval record below belongs to
the CODATA-derived public endpoint branch and is therefore a comparison record, not a
no-measured-input \(\alpha_U\) proof record. On that branch,
\[
\Phi_U(P,a)
=
\bar\ell_{\mathrm{SU}(2)}(t_2(P,a))
+
\bar\ell_{\mathrm{SU}(3)}(t_3(P,a))
-
\frac{P}{4}
\]
has a unique source zero in the declared interval, with frozen representation cutoffs, beta
packet, matching prescription, threshold packet, and renormalization convention. The hierarchy
artifact records
\[
\begin{aligned}
I_U&=[0.041123336195630494,\;0.041125336195630496],\\
\alpha_U(P_\star)&=0.041124336195630495,
\end{aligned}
\]
a Krawczyk image strictly inside \(I_U\), and a derivative enclosure contained in
\([-10.995768,-10.985284]\).  The separate source-audit candidate records
\(P_{\rm cand}=1.630972095694329\ldots\),
\(\alpha_U(P_{\rm cand})=0.04112424744557487\), and
\(v(P_{\rm cand})/E_\star=2.0198114150099223\times10^{-17}\). Its promotion
requires the strict source-root certificate and a dependency graph with no
directed path from measured \(W/Z\), measured \(\alpha_s(m_Z)\), measured
\(\sin^2\theta_W\), measured \(v\), measured \(G\), Planck-area data, measured
\(\Lambda\), or calibrated proxies. A converged precision-100
rerun supersedes the printed \(P_{\rm cand}\) tail beyond digit 10; the certified forward
pixel is \(P_{\mathrm{fwd}}=1.630972095858897\ldots\). Thus the dimensionless hierarchy formula
is the strongest clean output presently isolated; it supplies only the first
component of the clock hierarchy below. The cesium gap
\(\varepsilon_{\mathrm{Cs}}=\hbar\omega_{\mathrm{Cs}}/E_\star\) must then factor through the
first-principles chain
\[
\mathcal R_\gamma
=
\mathcal R_U
+
\mathcal R_\alpha
+
\mathcal R_e^{\mathrm{abs}}
+
\mathcal R_{\mathrm{QCD/nuc}}^{133\mathrm{Cs}}
+
\mathcal R_{\mathrm{atom}}^{133\mathrm{Cs}}.
\]
Here \(\mathcal R_\alpha\) emits the electromagnetic endpoint used by the atomic Hamiltonian,
\(\mathcal R_e^{\mathrm{abs}}\) emits the absolute electron mass ratio, the cesium
QCD/nuclear branch emits the source-side \({}^{133}\mathrm{Cs}\) nuclear packet, and the atomic
branch emits the hyperfine spectral gap. The combined dependency graph may contain no path from
measured \(G\), Planck area/mass/time, measured low-energy electroweak data, measured
\(\Lambda\), \(3\pi c^3/(\hbar G)\), or an equivalent calibrated scale. Failure of that
dependency test makes the numerical \(G\) row calibration. Passing the dependency test makes the
SI gravity row inherit the no-\(G\) condition of the emitted clock gap. Printed digits beyond the
source interval bounds are calibration checksum digits.
The target \(N_{\mathrm{CRC}}\) enters the conditional cosmological-capacity branch. The capacity normalization uses the
Gibbons--Hawking de Sitter entropy~\cite{gibbonsHawking77}: if
\[
N_{\mathrm{patch}}=\left(\frac{r_{\mathrm{dS}}}{\ell_P}\right)^2
\]
denotes the bare horizon area ratio, then
\[
N_{\mathrm{scr}}=S_{\mathrm{dS}}=\frac{A_{\mathrm{dS}}}{4\ell_P^2}
=\pi N_{\mathrm{patch}}
=\frac{3\pi}{\Lambda\ell_P^2}.
\]
Using the Planck-2018 cosmological benchmark~\cite{planck18} gives
\(r_{\mathrm{dS}}\simeq1.66\times10^{26}\,\mathrm m\),
\(N_{\mathrm{patch}}\simeq1.05\times10^{122}\),
the Planck--\(\Lambda\)-located central value
\(N_{\Lambda}:=N_{\mathrm{scr}}\simeq3.313\times10^{122}\), and
\(\Lambda\ell_P^2\simeq2.85\times10^{-122}\). Any retained capacity-level
neutrino side estimate on that input is legacy bookkeeping. The separate weighted-cycle
construction has target-informed template-candidate status.

The same screen-capacity normalization enters the proposed global repair-tick lemma used in the
hierarchy continuation. The construction in this paragraph is conditional on a
constructed readback map \(F\), a certified fixed-point interval, and premises
CP-1--CP-3 of Remark~\ref{rem:l2-l3-capacity}.  At a candidate fixed point
\(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})\), let
\(\rho=\ell/r_{\mathrm{CRC}}\), so the horizon sits at \(\rho=1\) and the local cell at
\(\rho_\star=\ell_\star/r_{\mathrm{CRC}}=(N_{\mathrm{CRC}}/\pi)^{-1/2}\). The global repair
cycle is the scale-free readback transport attached to the candidate fixed point. Under the
stated assumptions, the fixed-point equation supplies its closure. With the conditional
Observers-synthesis readback map, modeled by the D6
area-law count at the effective delivery resolution \(\rho_{\mathrm{read}}\) through the
D6-consistent counting identification, the readback reconstructs capacity
\(F(N)=\pi/\rho_{\mathrm{read}}^2\), so the
fixed-point equation \(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})=\pi/\rho_\star^2\) forces
\(\rho_{\mathrm{read}}=\rho_\star\), i.e. \(G_N(1)=\rho_\star\) exactly, and
\[
G_N(\rho)
=
\left(\frac{N_{\mathrm{CRC}}}{\pi}\right)^{-1/2}\rho .
\]
The \(24\)-tick count is the doubled observer-visible product-adjoint repair spectrum,
\[
m_{\rm rep}
=2\dim(\mathfrak{su}(3)\oplus\mathfrak{su}(2)\oplus\mathfrak u(1))
=2(8+3+1)
=24.
\]
The factor \(2\) is the reversible write/verify orientation. The \(\mathfrak{su}(5)\) adjoint
has the same single-orientation integer for a different support because it contains \(X/Y\)
mixed gauge channels excluded by the OPH product branch. With \(G_N=g_N^{24}\), the one-tick
homogeneous normal form is
\[
g_N(\rho)
=
\left(\frac{N_{\mathrm{CRC}}}{\pi}\right)^{-1/48}\rho,
\qquad
|g_\star'|
=
\left(\frac{N_{\mathrm{CRC}}}{\pi}\right)^{-1/48}.
\]
The integer \(24\) is branch architecture for this lemma.

The joint source branch uses the product space
\[
X=I_P\times I_x,\qquad x=\log N,
\]
and the product-separated source map
\[
\mathcal J(P,x)=(\Gamma(P),\widehat C(x)),
\]
where \(\Gamma\) is the local pixel closure map and \(\widehat C(x)=\log F(e^x)\) is the
global capacity readback map. If the component certificates give
\[
|\Gamma(P)-\Gamma(Q)|\le q_P|P-Q|,
\qquad
|\widehat C(x)-\widehat C(y)|\le q_N|x-y|,
\qquad
q_P,q_N<1,
\]
then \(\mathcal J\) is a contraction in the product metric with constant
\(q=\max\{q_P,q_N\}\). It has a unique stable joint fixed point
\((P_\star,\log N_{\mathrm{CRC}})\). A source branch with genuine cross-feedback must instead
provide a weighted-sup derivative certificate: for derivative bounds \(a,b,c,d\), there must
exist \(r>0\) with
\[
\max\{a+b/r,\ d+rc\}<1.
\]
The product theorem applies only with that certificate. Coupled feedback otherwise remains
residual branch freedom.

On this conditional selected branch, the RG/Higgs naturality square is also closed. Let \(Q_s\) be the
source hierarchy quotient and \(Q_H\) the Higgs/electroweak quotient, and define
\[
\rho_{sH}([x]_s)=
\left[
P(x),N(x),
\left(\frac{N(x)}{\pi}\right)^{-P(x)/12},
\Pi_{HT}F_{D11}F_{D10}(P(x),N(x)),0
\right]_H .
\]
For the source and Higgs normal-form maps \(n_s,n_H\), and for the corresponding obstruction
maps \(h_s,h_H\) with induced map \(\chi_{sH}\), the selected branch has
\[
\rho_{sH}n_s=n_H\rho_{sH},
\qquad
\chi_{sH}h_s=h_H\rho_{sH}.
\]
Thus
\[
\varepsilon_H
=
\max\{\varepsilon^n_{sH},\varepsilon^h_{sH}\}
=0,
\qquad
\varepsilon_H\in[0,0].
\]
Measured \(v\), \(W/Z\), Higgs/top, \(G\), Planck-area, and \(\Lambda\) data are not inputs to
this naturality bound. The conditional electroweak tick-projection bridge equation is
\[
\Pi_{\rm EW}(P,N)=\frac{24\pi}{\alpha_U(P)\log(N/\pi)},\qquad
\Pi_{\rm EW}(P_\star,N_{\rm CRC})=4P_\star
\iff
B_{\rm EW}(P_\star,N_{\rm CRC})=0,
\]
where
\[
B_{\rm EW}(P,N)=\alpha_U(P)\log(N/\pi)-\frac{6\pi}{P}.
\]
The exact bridge target is
\[
N_{\rm EW}(P_\star)
=\pi\exp\!\left[\frac{6\pi}{P_\star\alpha_U(P_\star)}\right]
=3.5323546226929906511187512962330547600462\times10^{122}.
\]
Equivalently, the log-capacity map
\[
\mathcal C_{\rm EW}(P,x)
=(1-\lambda)x+\lambda\frac{6\pi}{P\alpha_U(P)}
\]
is a contraction at \(\lambda=1/2\), with unique fixed point
\(x_\star=6\pi/(P_\star\alpha_U(P_\star))\) and
\(N_{\rm EW}=\pi e^{x_\star}\). Thus
\(B_{\rm EW}(P_\star,N_{\rm EW})=0\).  The electroweak bridge value is
\(N_{\rm EW}=3.5323546226929906\ldots\times10^{122}\), whereas the
Planck--\(\Lambda\) central value above is
\(N_{\Lambda}\simeq3.313\times10^{122}\).  Their central values differ by
about \(6.6\%\), measured relative to \(N_{\Lambda}\).  This is a conditional
mismatch because \(F\) has not been constructed and CP-1--CP-3 have not been
discharged.  The evidence establishes neither a contradiction nor a second capacity. The finite readback-resolution
certificate defines
\[
F_r(N)=\operatorname{Cap}_{\rm read}
\left(\operatorname{Obs}(\operatorname{nf}_{r,N}(\mathfrak U_{r,N}))\right),
\qquad
\rho_{\rm read}(r,N)=\sqrt{\pi/F_r(N)}.
\]
Under the same assumptions, the selected finite branch has one positive central
capacity atom, so \(\rho_{\rm read}\) is a singleton and
\(\rho_{\rm read}(r,N_{\rm CRC})\to(N_{\rm CRC}/\pi)^{-1/2}\) in the
positive-root refinement limit. Together with the representation-to-spectrum count
\(m_{\rm rep}=24\), read as the 24-slot oriented repair register supplied by reversible
write/check orientation, this would close the local/global hierarchy-resonance theorem on the
selected branch.

This is the reverse-engineering protocol used for the quantitative branch. Observed values may
name a neighborhood of the branch: \(P\) near the electromagnetic endpoint, \(N_{\mathrm{CRC}}\)
near the de Sitter entropy capacity, and \(\gamma_\star\) near the SI scale branch. The paper then
asks whether the OPH readback map is a self-map on that neighborhood and whether Banach
contraction, derivative sign, strict concavity, or an equivalent uniqueness certificate selects one
fixed point. No global point is counted as an OPH output until the map and certificate are supplied;
the observational seed is branch location, not a fitted constant.

The companion compact proof uses the same convention as a compression
estimate. A quantitative row enters that estimate only when the declared source
map has no dependency path from the measured target or a calibrated proxy. If
\(p_i\) upper-bounds the conditional accidental hit probability of row \(i\)
after previous accepted rows, then
\[
P_{\rm acc}\le\prod_i p_i .
\]
No row in this ledger qualifies as a discriminating frozen-prospective hit. The project compression
scorecard may record retrospective or corpus-level compression comparisons, but those entries carry
no prospective prediction weight. The scorecard standing is secondary to the theorem stack: the
local coordinate and conditional global target organize the observer readout,
gravity/gauge reconstruction, hierarchy bridge, dark energy, dark-sector
budget, product-group proton-decay exclusion, particle inventory, and
string-vacuum selector.

\begin{theorem}[What the local coordinate and conditional capacity would determine]\label{thm:pn-dimensionless-geometry}
Let the local pixel coordinate be
\[
P_\star=\frac{a_{\mathrm{cell}}}{\ell_\star^2},
\]
and assume the global capacity relation on the de Sitter branch,
\[
N_\star=\frac{A_{\mathrm{dS}}}{4\ell_\star^2}
=\frac{3\pi}{\Lambda_\star\ell_\star^2}.
\]
Write
\[
\mathcal B_\ell:=\Lambda_\star N_\star
\]
for the scale product called \(B_\ell\) in the compact scale note. Then the local coordinate and
assumed capacity relation imply
\[
\Lambda_\star\ell_\star^2=\frac{3\pi}{N_\star},
\qquad
\Lambda_\star a_{\mathrm{cell}}=\frac{3\pi P_\star}{N_\star},
\]
and
\[
\mathcal B_\ell\ell_\star^2=3\pi,
\qquad
\mathcal B_\ell a_{\mathrm{cell}}=3\pi P_\star.
\]
These are dimensionless invariants of the OPH geometry.
\end{theorem}

\begin{proof}
The assumed capacity relation gives
\[
N_\star=\frac{3\pi}{\Lambda_\star\ell_\star^2},
\]
so
\[
\Lambda_\star\ell_\star^2=\frac{3\pi}{N_\star}.
\]
Multiplying by \(P_\star=a_{\mathrm{cell}}/\ell_\star^2\) gives
\[
\Lambda_\star a_{\mathrm{cell}}
=P_\star\Lambda_\star\ell_\star^2
=\frac{3\pi P_\star}{N_\star}.
\]
Since \(\mathcal B_\ell=\Lambda_\star N_\star\),
\[
\mathcal B_\ell\ell_\star^2
=\Lambda_\star N_\star\ell_\star^2
=3\pi.
\]
Multiplying by \(P_\star\) gives
\[
\mathcal B_\ell a_{\mathrm{cell}}=3\pi P_\star.
\]
\end{proof}

\begin{theorem}[Scale underdetermination by the two dimensionless coordinates]\label{thm:pn-scale-underdetermination}
No formula using only \(P_\star\), \(N_\star\), pure dimensionless constants, and exact display
constants \(c,\hbar\) can determine \(\mathcal B_\ell\) in \(\mathrm{m^{-2}}\),
\(\ell_\star^2\) in \(\mathrm{m^2}\), or \(G_{\mathrm{SI}}\) in SI units.
\end{theorem}

\begin{proof}
For any \(\lambda>0\), rescale all lengths by \(L\mapsto\lambda L\). Then
\[
\ell_\star^2\mapsto\lambda^2\ell_\star^2,\qquad
a_{\mathrm{cell}}\mapsto\lambda^2a_{\mathrm{cell}},\qquad
\Lambda_\star\mapsto\lambda^{-2}\Lambda_\star.
\]
The ratios
\[
P_\star=\frac{a_{\mathrm{cell}}}{\ell_\star^2},
\qquad
N_\star=\frac{3\pi}{\Lambda_\star\ell_\star^2}
\]
are unchanged, but
\[
\mathcal B_\ell=\Lambda_\star N_\star
\mapsto
\lambda^{-2}\mathcal B_\ell.
\]
Thus \(P_\star\) and \(N_\star\) determine the invariant product
\(\mathcal B_\ell\ell_\star^2=3\pi\), while the SI value of \(\mathcal B_\ell\), the SI area
\(\ell_\star^2\), and
\[
G_{\mathrm{SI}}=\frac{c^3}{\hbar}\ell_\star^2
\]
change with the length scale.
\end{proof}

\begin{theorem}[Selected OPH scale certificate, conditional capacity form]\label{thm:scale-bridge-desitter}
Assume a constructed readback map, a fixed-point certificate, and discharged premises CP-1--CP-3
give an OPH cosmic record-capacity fixed point
\[
N_\star=F(N_\star),
\]
and assume the conditional identification \(N_\star=S_{\mathrm{dS}}\). Let the selected no-\(G\)
scale branch supply
\[
\gamma_\star
\equiv
\frac{\ell_\star\nu_{\mathrm{Cs}}}{c}
=
\decnum{4.9559743365484194636657782433696431879484319705825}
\times10^{-34},
\]
with \(\nu_{\mathrm{Cs}}=9{,}192{,}631{,}770\,\mathrm{s^{-1}}\). Then
\[
\ell_\star^2
=\left(\frac{\gamma_\star c}{\nu_{\mathrm{Cs}}}\right)^2
=
\decnum{2.61228030237427777887347769215451001461202676866}
\times10^{-70}\,\mathrm{m^2}.
\]
Equivalently, the same certificate has the SI curvature display
\[
B_\star:=\frac{3\pi}{\ell_\star^2}
=
\decnum{3.6078739146803215760518414801601725476877083072171853821242070198789871988886}
\times10^{70}\,\mathrm{m^{-2}}.
\]
On the de Sitter branch this is the same scale product
\[
B_\star=\Lambda_\star N_\star,
\]
so the OPH area coordinate is
\[
\ell_\star^2=\frac{3\pi}{B_\star}.
\]
\end{theorem}

\begin{proof}
The clock-ratio definition gives
\[
\ell_\star=\frac{\gamma_\star c}{\nu_{\mathrm{Cs}}},
\]
and hence the displayed value of \(\ell_\star^2\). The curvature display is only a re-expression of
the same area coordinate:
\[
B_\star=\frac{3\pi}{\ell_\star^2}.
\]
The de Sitter capacity identity is
\[
N_\star=\frac{3\pi}{\Lambda_\star\ell_\star^2}.
\]
Multiplying by \(\Lambda_\star\ell_\star^2\) gives
\[
\Lambda_\star N_\star\ell_\star^2=3\pi.
\]
Since \(B_\star=\Lambda_\star N_\star\) on the selected branch, division by \(B_\star\) gives
\[
\ell_\star^2=\frac{3\pi}{B_\star}.
\]
\end{proof}

\begin{corollary}[Newton coupling after the scale certificate]\label{cor:newton-scale-bridge}
The local OPH gravity branch gives
\[
a_{\mathrm{cell}}=P_\star\ell_\star^2,
\qquad
\bar\ell_{\mathrm{shared}}=\frac{P_\star}{4}.
\]
Therefore
\[
G_{\mathrm{geom}}
=\frac{a_{\mathrm{cell}}}{4\bar\ell_{\mathrm{shared}}}
=\frac{P_\star\ell_\star^2}{4(P_\star/4)}
=\ell_\star^2.
\]
The SI display is
\[
G_{\mathrm{SI}}=\frac{c^3}{\hbar}\ell_\star^2.
\]
\end{corollary}

Consequently, the certified incomplete-map local coordinate and the conditional capacity relation
determine the dimensionless geometry under the theorem's hypotheses. The local edge
law then identifies \(G_{\mathrm{geom}}\) with the OPH area quantum \(\ell_\star^2\). The numerical
SI value of \(G\) is fixed only after the selected no-\(G\) scale certificate supplies
\(\gamma_\star\), equivalently \(B_\star=3\pi/\ell_\star^2\).
Observed branch values can locate the scale branch in reverse-engineering mode. The rounded display
\(N_{\Lambda}\simeq3.313\times10^{122}\) is a capacity-scale benchmark; a conditional exact \(G\)
row would use a fixed-point value \(N_\star\) together with the selected scale certificate. Using only
the rounded capacity with the Planck-2018 curvature benchmark would move the Newton row at the
\(8.4\times10^{-4}\) level, so it is not a precision certificate.

\begin{axiom}[Screen Net]\label{ax:screen}
Physical data is organized on a horizon screen \(S^2\) carrying a net of local algebras
\[
P \longmapsto \mathcal A(P)
\]
for connected patches \(P\subset S^2\), with isotony
\[
P\subset Q \implies \mathcal A(P)\subset \mathcal A(Q).
\]
\end{axiom}

\begin{axiom}[Overlap Consistency]\label{ax:overlap}
For overlapping patches \(P_1\cap P_2\neq\varnothing\), the local states induced on the shared algebra agree:
\[
\omega_{P_1}|_{\mathcal A(P_1\cap P_2)}
=
\omega_{P_2}|_{\mathcal A(P_1\cap P_2)}.
\]
\end{axiom}

\begin{axiom}[Local MaxEnt and Refinement Stability]\label{ax:maxent}
At the regulator scale \(\ell_{\mathrm{UV}}\), the realized branch is selected by maximizing entropy subject to the finitely many homogeneous global-sum constraints
\[
\Bigl\langle\sum_x O_a(x)\Bigr\rangle=C_a,
\qquad a=1,\dots,N_{\mathrm{con}},
\]
built from a finite list of gauge-invariant local densities \(O_a(x)\), each supported in a ball of radius \(O(\ell_{\mathrm{UV}})\). The constrained functionals are the \(N_{\mathrm{con}}\) global sums, together with the finitely many optional global conserved charges, not one independent constraint per regulator cell; there is therefore one Lagrange multiplier \(\lambda_a\) per density label \(a\), and the multiplier count is cutoff-independent by construction. The per-cell specification \(\langle O_a(x)\rangle=c_a(x)\) with cell-dependent multipliers \(\lambda_a(x)\) defines a strictly larger family whose dimension grows with the number of cells; it is admitted only as a near-equilibrium approximation regime and is never used in the refinement or branch-stability arguments of this paper. The axiom additionally asserts a \emph{refinement-closure clause}: under the admissible refinement channels of this framework, the coarse-grained realized state again lies in the exponential family generated by the same finite density list at the coarser scale. Coarse-graining a finite-range Gibbs family generically generates additional interactions, so closure is a substantive renormalization condition on the realized branch, not a bookkeeping consequence of reusing the operator labels \(a\); the closure defect, the induced projection, and its trace-norm residual bound are supplied by Definition~\ref{def:closure-defect} and Lemma~\ref{lem:closure-residual}, and what remains assumed rather than proved is that the defect vanishes along the realized branch. Granting closure, the realized states at different cutoffs belong to one common \((N_{\mathrm{con}}+N_{\mathrm{glob}})\)-dimensional MaxEnt family. The realized low-energy branch is the refinement-stable branch of that family; symmetry-allowed relevant operators are therefore held at zero on that branch only by symmetry or because they lie in the explicitly retained constraint family. This is a statement about branch persistence, not a universal entropy-ordering theorem for arbitrary phases away from that branch.
\end{axiom}

\paragraph{Quotient-ensemble selector boundary.}
Axiom~\ref{ax:maxent} controls the realized state-side branch, while the consensus normal-form map controls closure. Neither statement by itself chooses probability weights on terminal quotient normal forms: every distribution supported on normal forms is fixed by deterministic settling. A finite OPH quotient ensemble therefore additionally requires either an intrinsic quotient base weight \(m_r\) and action \(S_r\), with
\[
\mu_r(q)=Z_r^{-1}m_r(q)e^{-S_r(q)},
\]
or an intrinsic projective prior \(\nu_r\) whose normal-form pushforward is declared physical. Exact refinement compatibility for \(s\succeq r\) requires the fiber-sum identity
\[
\sum_{q':\,c_{sr}(q')=q}m_s(q')e^{-S_s(q')}
=
\alpha_{sr}m_r(q)e^{-S_r(q)}
\]
with \(\alpha_{sr}\) independent of \(q\). Seed noise, repair jitter, worker partitioning, and conventional free-field or lattice-gauge baselines are implementation or calibration data until this quotient-ensemble selector, or a separate transfer-matrix vacuum gate, is supplied.

\paragraph{Derived local-Gibbs branch.}
On the finite regulator realization of Axiom~\ref{ax:screen}, the standard finite-dimensional Lagrange-multiplier argument applied to Axiom~\ref{ax:maxent} gives
\[
\omega_{\ell_{\mathrm{UV}}}(\lambda)
=
Z_{\ell_{\mathrm{UV}}}(\lambda)^{-1}\exp\!\bigl(-K_{\ell_{\mathrm{UV}}}(\lambda)\bigr),
\]
with
\[
K_{\ell_{\mathrm{UV}}}(\lambda)
=
\sum_x \sum_{a=1}^{N_{\mathrm{con}}}\lambda_a O_a(x)
+\sum_b \mu_b Q_b,
\]
where the \(Q_b\) are the finitely many optional global conserved-charge constraints. Because the constraints are the homogeneous global sums, the exponent carries one cell-independent multiplier \(\lambda_a\) per density label, so the multiplier-space dimension is \(N_{\mathrm{con}}+N_{\mathrm{glob}}\) on every lattice and matches the count of independent constraints there; per-cell constraints would instead produce cell-dependent multipliers \(\lambda_a(x)\) and a parameter space growing with the number of cells. The local-density part of the logarithm is therefore a quasi-local UV generator. Locality of the optional \(Q_b\) terms requires the separate condition in the next paragraph.

For the finite-range collar theorem, each retained \(Q_b\) must itself be a sum of uniformly
bounded finite-range densities, or it must be fixed and central on the superselection sector under
study. An otherwise nonlocal charge term remains valid MaxEnt data but falls outside
Definition~\ref{def:finite-range-collar-gibbs}; the Lagrange-multiplier argument alone does not turn
such a term into a local interaction.

\paragraph{Derived quasi-local propagation and interval control.}
Fix the regulator graph metric coming from cell adjacency and let \(\tau_t^{\ell_{\mathrm{UV}}}\) denote the automorphism group generated by \(K_{\ell_{\mathrm{UV}}}(\lambda)\), or more generally by any branch generator lying in the norm-closed algebra generated by the same bounded-support local densities. Standard Lieb--Robinson estimates for finite-range interactions on the finite regulator net then give constants \(C,\xi,v_{\ell_{\mathrm{UV}}}<\infty\) such that for local observables \(A_X,B_Y\), \cite{liebRobinson72}
\[
\bigl\|[\tau_t^{\ell_{\mathrm{UV}}}(A_X),B_Y]\bigr\|
\le
C\,\|A_X\|\,\|B_Y\|\,\min(|X|,|Y|)\,
e^{-(d(X,Y)-v_{\ell_{\mathrm{UV}}}|t|)/\xi}.
\]
So finite-velocity quasi-local propagation is branch-internal: it is the local finite-constraint MaxEnt branch written in propagation form, not an extra selector.

The same locality statement yields the bounded-interval endpoint-Lipschitz control used by the compact-gauge branch in the null modular chain. Whenever later sections use a fixed-cutoff interval or collar generator on this branch, it is the corresponding restriction of the same local density list, with the central endpoint term separated off exactly as in the later edge-center bookkeeping. Changing an interval \(I\) to \(I'\) then alters only an \(O(|I'\Delta I|)\) collar of local terms. Hence on any fixed local-energy-bounded domain one has
\[
\left|\langle\psi,(K[I']-K[I])\phi\rangle\right|
\le
C_{\psi,\phi,I_{\max}}\,|I'\Delta I|,
\]
which is precisely the endpoint-Lipschitz / finite-variation control used by the compact-gauge branch in the null modular chain. This paper does \emph{not} separately derive a second independent microscopic generator beyond this quasi-local branch generator; if a UV completion carries one, the only later requirement is that it lie in the same bounded-support algebraic closure so that the same propagation constants control the selected branch.

This local-Gibbs/Lieb--Robinson package, together with any Dobrushin-type estimate used by the compact-gauge branch, should be read only as fixed-cutoff collar-local recoverability, support control, and carried-error bookkeeping on the selected branch. One may impose such estimates on a chosen finite collar model without deciding the refinement-limit gauge phase. The package is therefore not a proof that the refinement limit lands in a trivial thermodynamic phase and not a proof that the realized branch is nontrivial. Refinement persistence and bosonic fiber descent for zero-obstruction sectors follow from Theorem~\ref{thm:refinement-functor-fiber-descent} only on a cofinal tail carrying the compact-gauge refinement receipt. The local mixing estimate does not supply that receipt.

\paragraph{Internal refinement notion.}
Choose any family of refinement channels \(\Phi_{\ell\to L}\) compatible with Axiom~\ref{ax:maxent}, including its refinement-closure clause. By that closure clause, the regulator-scale realized states are parameterized by one common finite-dimensional multiplier space \(\lambda\), and on the realized branch one may write
\[
\Phi_{\ell\to L}\bigl(\omega_{\ell}(\lambda)\bigr)
=
\omega_{L}\!\bigl(R_{\ell\to L}(\lambda)\bigr)
\]
for an induced map \(R_{\ell\to L}\) on that multiplier space. The existence of \(R_{\ell\to L}\) as a self-map of the same finite-dimensional space is exactly the closure clause at work: interactions generated by coarse-graining outside the retained density list must vanish on the realized branch or be absorbed into it. Definition~\ref{def:closure-defect} and Lemma~\ref{lem:closure-residual} below make this quantitative: the moment-matching I-projection onto the coarser family exists and is unique on the finite regulator, the closure clause is the statement that its relative-entropy defect vanishes along the realized branch, and a nonzero defect degrades expectation values by an explicit trace-norm residual; what this paper assumes rather than proves is the vanishing of that defect. The refinement-stable realized branch is therefore the persistent trajectory or invariant subset selected inside this finite-dimensional space, not an imported regularity package. This state-side refinement notion is enough to compare realized states across cutoffs. Any Dobrushin/local-mixing hypothesis used by the compact-gauge branch is logically separate: it supplies a collar estimate on a fixed finite-dimensional model, not information about the refinement-limit gauge phase. Whenever later sections speak of a ``refinement-stable directed colimit'' of zero-obstruction edge sectors, the monoidal-refinement/fiber clause is Theorem~\ref{thm:refinement-functor-fiber-descent} together with Definition~\ref{def:compact-gauge-refinement-receipt}; Axiom~\ref{ax:maxent} supplies only the realized state branch along which a certified sector witness may persist.

\begin{definition}[Closure defect and induced refinement map]\label{def:closure-defect}
Fix regulator scales \(\ell\) (finer) and \(L\) (coarser) with their finite realized algebras, let \(\mathcal E_L=\{\omega_L(\lambda')\}\) be the homogeneous exponential family generated by the retained global-sum densities and optional global charges at scale \(L\), and let \(\Phi_{\ell\to L}\) be an admissible refinement channel. For fine-scale multipliers \(\lambda\) set \(\sigma:=\Phi_{\ell\to L}(\omega_\ell(\lambda))\) and define the \emph{closure defect}
\[
\varepsilon_{\ell\to L}(\lambda):=\inf_{\lambda'} D\bigl(\sigma\,\big\|\,\omega_L(\lambda')\bigr),
\]
with \(D\) the quantum relative entropy. When the infimum is attained at a unique \(\lambda^\ast\), set \(R_{\ell\to L}(\lambda):=\lambda^\ast\).
\end{definition}

\begin{lemma}[I-projection residual bound]\label{lem:closure-residual}
On the finite regulator realization, assume the constrained operators \(S_c\in\{\sum_x O_a(x)\}_{a=1}^{N_{\mathrm{con}}}\cup\{Q_b\}_{b=1}^{N_{\mathrm{glob}}}\) at scale \(L\), together with \(\mathbf 1\), are linearly independent. Then:
(i) \(\lambda'\mapsto D(\sigma\|\omega_L(\lambda'))\) is smooth and strictly convex; for faithful \(\sigma\) the infimum is attained at a unique \(\lambda^\ast=R_{\ell\to L}(\lambda)\), characterized by moment matching \(\langle S_c\rangle_{\omega_L(\lambda^\ast)}=\langle S_c\rangle_\sigma\) for every constrained operator;
(ii) \(\bigl\|\sigma-\omega_L(R_{\ell\to L}(\lambda))\bigr\|_1\le\sqrt{2\,\varepsilon_{\ell\to L}(\lambda)}\), so the family reproduces \(\langle B\rangle_\sigma\) up to \(\|B\|\sqrt{2\varepsilon_{\ell\to L}(\lambda)}\) for every bounded observable \(B\);
(iii) the refinement-closure clause of Axiom~\ref{ax:maxent} is exactly the statement \(\varepsilon_{\ell\to L}(\lambda)=0\) along the realized branch, in which case \(\sigma=\omega_L(R_{\ell\to L}(\lambda))\) and the induced map of the internal refinement notion above is this moment-matching I-projection.
\end{lemma}

\begin{proof}
With \(\log\omega_L(\lambda')=-\sum_c\lambda'_c S_c-\log Z_L(\lambda')\,\mathbf 1\),
\[
D(\sigma\|\omega_L(\lambda'))=-S(\sigma)+\sum_c\lambda'_c\langle S_c\rangle_\sigma+\log Z_L(\lambda').
\]
\(\log Z_L\) is smooth, and its Hessian is the Duhamel (Kubo--Mori) covariance matrix of the \(S_c\) in \(\omega_L(\lambda')\), which is positive definite exactly when the \(S_c\) and \(\mathbf 1\) are linearly independent; this gives strict convexity, hence uniqueness of any minimizer, and the vanishing-gradient condition is the displayed moment matching. Attainment for faithful \(\sigma\) is finite-dimensional exponential-family duality: the moment map \(\lambda'\mapsto(\langle S_c\rangle_{\omega_L(\lambda')})_c\) is a diffeomorphism onto the relative interior of the achievable moment set, which contains the moment vector of every faithful state \cite{wichmann63}. Part (ii) is the quantum Pinsker inequality \(D(\rho\|\tau)\ge\tfrac12\|\rho-\tau\|_1^2\) \cite{hiaiOhyaTsukada81} evaluated at \(\lambda^\ast\). Part (iii) follows because the attained infimum vanishes iff \(D(\sigma\|\omega_L(\lambda^\ast))=0\) iff \(\sigma=\omega_L(\lambda^\ast)\), by strict positivity of relative entropy off the diagonal.
\end{proof}

A finite two-lattice acceptance check implements this counting and projection package. It covers the constraint/multiplier count against the displayed \((N_{\mathrm{con}}+N_{\mathrm{glob}})\)-dimensional family, the moment-matching projection, the residual bound, a generic channel with strictly positive closure defect, and an exactly closed subfamily. The check is included with the repository sources.

\paragraph{Central-interface collar clause (declared branch input).}\label{par:cicclause}
For every collar cut \(\Sigma\) used by the literal exact-Markov identities of this manuscript, the retained constraint family of Axiom~\ref{ax:maxent} is declared to be \emph{central-interface} in the sense of Theorem~\ref{thm:msaderivation}: every retained density whose support meets both half-collars of \(\Sigma\) acts through the boundary-charge (flux) functions in \(\pi_L\bigl(Z(C^*(\widehat K_\Sigma))\bigr)\), while all remaining terms are one-sided \(\widehat K_\Sigma\)-invariant operators. This is an explicit axiom-level input of the declared branch, on the same footing as the refinement-closure clause above. Overlap consistency does not derive it. Under this clause, Theorem~\ref{thm:msaderivation} derives the Markov-split alignment hypothesis (Definition~\ref{def:ecaligned}) and exact collar Markovianity for the MaxEnt reference states, so the MSA-conditioned identities of this manuscript hold on the declared branch without a separate state hypothesis. Lattice-gauge-type regulators satisfy the clause manifestly, their interface energy being a function of the conserved flux; the Bell-pair state of Remark~\ref{rem:hjpwalignment} violates it and marks the failure boundary. Deriving the clause from overlap-consistent repair is work in progress (Remark~\ref{rem:msascope}).

\begin{axiom}[Recoverable Generalized Entropy]\label{ax:entropy}
A generalized entropy functional exists on caps,
\[
S_{\mathrm{gen}}(C)=S_{\mathrm{bulk}}(C)+\langle L_C\rangle,
\]
where \(L_C\) is a positive edge-center entropy functional. In the semiclassical scaling branch, its leading coarse-grained contribution is identified with \(A(\partial C)/(4G)\). The functional obeys quantum focusing on null generators, and collar tripartitions have small CMI with controlled recovery maps \cite{liebRuskai73,petz86,petz88,fawziRenner15}.
\end{axiom}

The small-CMI clause is exact on the declared central-interface branch by
Theorem~\ref{thm:msaderivation}. On the finite-range noncommuting branch it has the explicit
envelope of Theorem~\ref{thm:collar-cmi-decay} only when the uniform strong conditional mixing
premise is supplied. Outside those branches, recoverability remains an axiom-level input rather
than a consequence of local Gibbs form.

\begin{axiom}[Minimal Admissible Realization]\label{ax:mar}
Among realized sector packages \(\mathfrak S\) consisting of the connected Lie gauge-sector image relevant in the low-energy EFT, its admissible light chiral matter content, and one Higgs doublet, and which are loop-coherent, anomaly-free, refinement-stable with light chiral matter, single-Higgs Yukawa-completable with one connected abelian charge factor acting nontrivially on the coupled carrier, intrinsically quark-sector CP-capable, and weak-sector UV-completable on that same one-Higgs branch, the realized package is the lexicographically minimal one under
\[
C(\mathfrak S)=\bigl(\chi_{\mathrm{cpl}},\,N_{\mathrm{nonab}},\,N_c,\,N_g\bigr).
\]
\(\mathfrak S\) is the sector package on which MAR acts; it is not the bare tensor category alone. MAR is therefore an explicit structural-economy axiom on admissible realized low-energy branches, not a theorem derived from the preceding axioms. \(\chi_{\mathrm{cpl}}\) is the coupled carrier dimension: the smallest unitary carrier containing a common irreducible block on which the admissible pseudoreal and complex nonabelian charge types both act nontrivially. This is stronger than the abstract minimal faithful representation dimension.
\end{axiom}

\begin{definition}[MAR realization space and order]\label{def:mar-space}
Let \(\mathfrak A_{\mathrm{MAR}}\) be the set of isomorphism classes of finite low-energy sector packages
\[
\mathfrak S=(G^0,\mathcal R_{\mathrm{light}},H,\mathcal Y,\mathcal F)
\]
on the ordinary or central zero-obstruction bosonic branch, together with the explicit one-Higgs chiral matter package used below. A package is MAR-admissible exactly when it satisfies the six predicates in Axiom~\ref{ax:mar}. Two packages are physically equivalent when a compact-group isomorphism and a fiber-compatible symmetric monoidal equivalence preserve the observer-visible representations, Yukawa invariants, anomaly polynomial, normalized hypercharge lattice, and one-Higgs branch, modulo generation relabeling, charge-conjugation convention, gauge-center quotienting, implementation hiding, and inert ancillary stabilization. MAR orders packages lexicographically by \(C(\mathfrak S)\in\mathbb N^4\) and then quotients ties by this physical equivalence.
\end{definition}

\begin{proposition}[Well-founded MAR minima]\label{prop:mar-well-founded}
Every nonempty MAR-admissible class has at least one MAR-minimal package. The minimal packages are exactly those whose complexity vector is the lexicographically least element of \(C(\mathfrak A)\subseteq\mathbb N^4\) for the chosen nonempty admissible class \(\mathfrak A\).
\end{proposition}

\begin{proof}
Lexicographic order on \(\mathbb N^4\) is well-founded: minimize the first coordinate, then the second on that fiber, then the third, then the fourth. Each step minimizes a nonempty subset of \(\mathbb N\).
\end{proof}

\begin{remark}[Meaning of MAR uniqueness]\label{rem:mar-uniqueness}
MAR uniqueness means uniqueness of the observer-visible low-energy package modulo Definition~\ref{def:mar-space}. It is not uniqueness of a microscopic regulator representative. The later D8--D9 lemmas prove that, within the connected positive-dimensional Lie admissible class with one connected abelian factor and faithful action on the minimal coupled carrier, all MAR-minimal representatives realize the same connected SM gauge image, normalized hypercharge lattice, structural electroweak force content, \(N_c=3\), and \(N_g=3\).
\end{remark}

\begin{remark}[Recovered-core theorem sources]\label{ass:technical}
The scaling/BW step is Theorem~\ref{thm:bw}, the support-visible BW scaling theorem. The fixed-cutoff realized presentation, the local-Gibbs form, quasi-local Lieb--Robinson propagation, endpoint-Lipschitz interval control, the induced finite-dimensional refinement branch, the fixed-cap generalized-entropy stationarity theorem for admissible fixed-cap MaxEnt variations on the realized cap-label-preserving MaxEnt family, and the operational/geometric split of Theorem~\ref{thm:geosubnet} are established internally from Axioms~\ref{ax:screen}--\ref{ax:maxent}. Transportability and the fixed-cutoff bosonic category are supplied by Theorems~\ref{thm:transport-from-gluing} and \ref{thm:fixed-cutoff-bosonic-sector-category}; the refinement/fiber ladder additionally requires Definition~\ref{def:compact-gauge-refinement-receipt} before Theorem~\ref{thm:refinement-functor-fiber-descent} applies. The realized compact-gauge witness is Theorem~\ref{thm:mar-witness-landing}. The genuinely noncentral fixed-cutoff branch is controlled by Theorems~\ref{thm:hgdatum}--\ref{thm:hgtransport}: \(o^{(2)}_\Sigma=0\) means the orbit admits one or more strict \(G_\Sigma\)-valued \(1\)-cocycle representatives and enters the compact-group transportable case only if at least one has trivial represented loop holonomy; \(o^{(2)}_\Sigma\ne0\) remains a higher-gauge sector and is not itself the ordinary compact-group reconstruction theorem. The full orbit \(q_\Sigma\) need not determine a unique ordinary \(H^1\) class because higher-gauge edge changes can relate distinct strict representatives. Fermionic signs and chirality belong to the later fermionic/super-Tannakian matter lift.
The classification/selection split is packaged in Theorem~\ref{thm:gauge-selection-factorization},
and the observer-visible selected endpoint is Theorem~\ref{thm:realized-sm-branch}.
\end{remark}

\begin{remark}[Log convention]
Unless an explicit base is written, logarithms and entropies in this paper use natural logs (nats). Base-2 logarithms are written as \(\log_2\) and quoted in bits.
\end{remark}

\subsection*{Dependency DAG}

The table below is the dependency map for this SM/GR derivation paper. The ``Immediate OPH ingredients'' column records only parents internal to the OPH program. Imported standard mathematics, branch-local constructions, and external inputs are stated separately instead of hidden inside the word ``derived.''

\begingroup
\scriptsize
\setlength{\tabcolsep}{1pt}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.06\textwidth}>{\raggedright\arraybackslash}p{0.20\textwidth}>{\raggedright\arraybackslash}p{0.14\textwidth}>{\raggedright\arraybackslash}p{0.13\textwidth}>{\raggedright\arraybackslash}p{0.21\textwidth}>{\raggedright\arraybackslash}p{0.12\textwidth}@{}}
\toprule
Node & Theorem labels and output & Immediate OPH ingredients & Standard mathematics used & Branch-local inputs / external data & Status \\
\midrule
\endhead
\bottomrule
\endfoot
\textbf{D1} & Theorems~\ref{thm:confluence}, \ref{thm:boundary-conditioned-uniqueness}, \ref{thm:layered-carrier-HB-Hfib}, \ref{thm:functional-selected-fiber}, and Corollary~\ref{cor:branch-elimination}: total quotient repair maps \(\operatorname{locRep}_\lambda,\operatorname{Rep}_\lambda:Q\to Q\), unique quotient normal form and schedule independence from a fixed initial quotient state, same-boundary uniqueness under unique consistent extension, layered \(H_B\wedge H_{\mathrm{fib}}\), and nontrivial selected-fiber branch elimination & overlap-consistency problem on a finite patch net together with the declared fixed-cutoff collar recovery proposal, its touched-overlap local-fit eligibility contract, transactional snapshot/read/write validation, boundary/sector preservation, and restriction-compatible union-collar gluing for canonical conflict-component payloads on the physical quotient & local-to-global well-founded descent; local-diamond completion from atomic conflict-component commits with validation-complete read sets; Newman's lemma; layered functional boundary reconstruction; rooted functional extension in selected fibers & repair completeness; stated Petz support/CPTP control where that branch is used; for same-boundary uniqueness, boundary/sector preservation and either at most one consistent quotient extension in the boundary fiber or the layered/functional selected-fiber theorem; obstruction/ambiguity gates when no unique quotient endpoint exists; normal-form hashes as equality receipts, not selectors & structural theorem \\
\textbf{D2} & Theorems~\ref{thm:collar-cmi-decay}, \ref{thm:markovcollar}, Propositions~\ref{prop:approxrecover}, \ref{prop:splice}, \ref{prop:gensplit}, Definition~\ref{def:newton}: collar Markov/entropy and conditional Gibbs-recovery layer & Axioms~\ref{ax:screen}--\ref{ax:entropy} plus strong conditional matrix mixing off the exact branch & matrix conditional-log-density mixing; HJPW Markov structure theorem; Petz and Fawzi--Renner recovery theory & the nonexact CMI bound requires the uniform finite-range and strong-mixing premises together with \(\delta/\xi-\log|\partial C|_{\mathrm{UV}}\to+\infty\); ordinary clustering is insufficient; exact Markov identities require exact Markovity plus the Markov-split alignment hypothesis (Definition~\ref{def:ecaligned}; both derived under the declared central-interface collar clause, Theorem~\ref{thm:msaderivation}); the \(A/(4G)\) identification is the coarse-grained dictionary of Definition~\ref{def:newton} & conditional theorem with exact central-interface specialization \\
\textbf{D3a} & Regularized support-visible modular transport on fixed cap-local algebras & Axioms~\ref{ax:screen}--\ref{ax:entropy}, collar Markov/recovery package, and Theorem~\ref{thm:geosubnet} & weak-\(*\)/GNS extraction;\newline modular theory with regularized finite generators & fixed-collar comparison errors, cutoff schedule, and multiresolution reference tower; no full finite-algebra spectral floor is assumed & theorem \\
\textbf{D3b} & Finite cap-normal and support-order certificate & D3a plus a cofinal nondegenerate cap mesh & spherical cap geometry;\newline de Sitter cap-normal compactness;\newline finite support-order reflection & BW-framed caps, support-order faithfulness, mixed-GNS Cauchy residuals, and support covariance; this certificate is not produced by bare finite consensus inside D3, and on the producer branch it is produced from the computable incidence/mesh/cross-ratio/normalization receipts (Theorem~\ref{thm:certificate-production}), whose selection is proved underdetermined by confluence (Theorem~\ref{thm:incidence-underdetermination}) & Theorem~\ref{thm:finite-cap-bw-certificate}\newline hypothesis;\newline produced on the D3h receipt branch \\
\textbf{D3c} & Oriented cross-ratio and framed-cap rigidity & D3b & M\"obius/cross-ratio rigidity on \(S^2\) & held-out separated quartets and an orientation witness; fitted anchors alone carry no validation value & theorem under certificate \\
\textbf{D3d} & Geometric \(2\pi\)-KMS normalization & D3b--D3c & KMS uniqueness for faithful normal states & independently normalized geometric parameter \(h_{\widehat C}(z)\mapsto e^{-s}h_{\widehat C}(z)\), finite strip bounds, and wrong-\(\beta\) separation & theorem under certificate \\
\textbf{D3e} & Theorem~\ref{thm:bw}: support-visible BW cap automorphism \(\sigma_t=\alpha_{\lambda_{\widehat C}(2\pi t)}\) & D3a--D3d & Bisognano--Wichmann modular template at automorphism level & type-I generator form includes \(K_C=2\pi B_C+Z_C\); in the generic non-type-I case the automorphism identity is the theorem & corollary \\
\textbf{D3f} & Corollaries~\ref{cor:lorentz}, \ref{cor:h3-spatial-chart}: exact cap-normal Lorentz/\(H^3\) chart, including \(S^2\simeq\mathbb P\mathcal N^+\), \(\operatorname{Cap}^{\mathrm{or}}_{\mathrm{round}}(S^2)\simeq dS_3^{\mathrm{cap}}\), \(n_{gC}=\Lambda_gn_C\), and \(H^3\simeq\mathrm{SO}^+(3,1)/\mathrm{SO}(3)\) & D3e plus oriented round-cap extraction and time orientation & projective future-null-cone geometry;\newline \(\mathrm{SL}(2,\mathbb C)\) Hermitian-matrix realization;\newline Lorentz homogeneous-space and hyperboloid geometry & a cap determines an \(H^3\) plane/half-space, not a preferred observer point; population, neutral bulk, physical \(R_H\), stress, and Einstein dynamics remain separate gates & exact conditional geometric theorem \\
\textbf{D3g} & Conditional record-populated \(H^3\) localization (Corollary~\ref{cor:conditional-record-populated-h3}) & D3f plus record-conditioned modular cap responses, point-local source factorization, compact source domain, quantitative cap frame, bounded error, and residual optimization & hyperbolic cap half-spaces, finite conditioned frames, finite \(\varepsilon\)-nets, and residual inverse-stability estimates & point locality is a branch hypothesis or finite receipt; noisy finite uniqueness requires \(\Delta_{\mathrm{loc}}>0\); species, stress, neutral bulk, and Einstein entry are not implied & conditional theorem \\
\textbf{D3h} & Lemma~\ref{lem:incidence-invariance}; Theorems~\ref{thm:topology-production}, \ref{thm:conformal-cap-production}, \ref{thm:certificate-production}, \ref{thm:incidence-underdetermination}: quotient-intrinsic geometry producer (incidence complex, produced \(S^2\) topology, conformal/cap structure, certificate production) and the confluence-underdetermination no-go & D1 normal forms plus the spherical incidence, disk/mesh, modular cross-ratio, and \(2\pi\)-normalization receipts & classification of closed combinatorial surfaces;\newline Rad\'o uniqueness;\newline M\"obius cross-ratio rigidity on \(S^2\) & receipts are decidable finite-stage predicates on normal forms; their selection is not implied by confluence (explicit \(T^2\), \(\partial\Delta^4\), wedge, and wrong-\(\beta\) countermodels); \(S^2\) and its conformal class are derived only on the receipt branch & producer theorem plus underdetermination no-go \\
\textbf{D4} & Propositions~\ref{prop:nullec}, \ref{prop:n3}; Corollaries~\ref{cor:n1}, \ref{cor:n2}; Theorem~\ref{lem:density}, Lemma~\ref{lem:translation}; Theorem~\ref{thm:stress}: null modular bridge to \(T_{kk}\), including exact-or-controlled strip additivity, endpoint-Lipschitz renormalized half-line families, the weak tail generator, the derived half-sided modular inclusion, the explicit positive half-line null-translation generator on its Stone domain with affine half-line modular relations, and the exact half-line generator/charge identification with the local null-stress charge & D2+D3 and Axioms~\ref{ax:screen}--\ref{ax:entropy} & Borchers--Wiesbrock positive-generator theorem for standard half-sided inclusions; Stone's theorem; distributional differentiation on half-lines & the theorem-local null-cut center transfer, the inherited left/right strip-split package used for the spatial-collar-type tensor decomposition, and the exact-or-controlled Markov hypotheses of Proposition~\ref{prop:nullec} and Corollary~\ref{cor:n1}; quasi-local propagation and endpoint-Lipschitz control are supplied internally by Axiom~\ref{ax:maxent} on the local finite-constraint branch; the geometric scaling action on the null half-line blow-up net derives the half-sided modular pair; bounded-interval formulas are discharged by Lemma~\ref{lem:bounded-interval-kernel}; null-net standardness, the derived half-sided inclusion, M\"obius bounded-interval covariance, Markov modular locality with its counterexample boundary, and the four-translation assembly are supplied by Theorems~\ref{thm:null-net-standardness}--\ref{thm:four-translation-assembly}, with the \(\mathsf{Cyc}\), \(\mathsf{NTI}\), weak-additivity, \(\mathsf{MI}\), and kernel-residual receipts explicit & bridge theorem plus D4-standardness packet \\
\textbf{D4b} & \S\ref{subsec:event-manifold} (Theorems~\ref{thm:event-4-manifold}, \ref{thm:event-causal-structure}, \ref{thm:event-tetrad-metric}, \ref{thm:clock-gluing}; Propositions~\ref{prop:h3-fiber-not-slice}, \ref{prop:event-countermodels}): conditional Lorentzian event manifold: quotient-intrinsic event classes, conditional four-dimensional atlas with signature \((-{+}{+}{+})\), causal order/time orientation, \(H^3\) strictly as frame fiber, tetrads/metric/connection/curvature readout, glued modular clocks, countermodels & D3f--D3h and D4 outputs plus receipts \(\mathsf{E1}\)--\(\mathsf{E4}\) & bi-Lipschitz atlas arguments;\newline convex-cone/quadric signature classification;\newline Rademacher/Carath\'eodory regularity & \(\mathsf{E1}\)--\(\mathsf{E4}\) with \(\mathsf{E4'}\)/smooth upgrade, \(\mathsf{MI}\)/assembly branch, absolute conformal scale, stable causality, and record-Cauchy receipt remain explicit; countermodels show \(\dim H^3=3\) promotes nothing by itself & conditional construction theorem \\
\textbf{D4c} & Local conserved stress tensor from modular charges: null tomography, constructed \(\langle T_{ab}\rangle\) with symmetry/locality/covariance/common normalization, generator/charge identification, weak Ward identity, ambiguity classification (Theorems~\ref{thm:null-tomography}, \ref{thm:local-stress-construction}; Proposition~\ref{prop:no-local-stress-countermodel}) & D4/D4b outputs plus the \(\mathsf{MI}\)/assembly branch, kernel-residual receipt, and universal-coupling receipt \(\mathsf{UC}\) & null polarization/tomography of symmetric tensors; least-squares stability & \(\phi g_{ab}\) and improvement ambiguities explicit; \(\mathsf{UC}\) is a physical-identification receipt; countermodel: per-direction generators without \(\mathsf{MI}\) linearity admit no rank-two source; scalar CMI is never promoted & conditional construction theorem \\
\textbf{D4d} & Bulk/edge/central first law with the edge term carried exactly, algebraic type-I boundary statement, and MaxEnt stationarity extended to the coupled changing-stress class via the exact multiplier identity \(dS/dt=\lambda=2\pi\) (Theorems~\ref{thm:bulk-edge-central-first-law}, \ref{thm:maxent-lagrange-stationarity}; Proposition~\ref{prop:entropy-coefficient-countermodel}) & central-interface branch of Axiom~\ref{ax:maxent}, type-I generator form \(K_C=2\pi B_C+Z_C\), edge normalization \(z_\alpha=\log d_\alpha\) & finite first law \(\delta S=\langle K\delta\rho\rangle\); MaxEnt envelope/Legendre identity & the Axiom-4 leading term and edge normalization are named branch axioms; shape/null-cut and metric variations are not covered; countermodels: wrong coefficient or wrong edge weights break stationarity by computable defects & exact finite theorem plus conditional bridge \\
\textbf{D5} & Theorem~\ref{thm:equilibrium}, Lemma~\ref{lem:smallball}, Theorems~\ref{thm:fixed-volume-small-ball-area}, \ref{thm:einstein}, \ref{cor:einstein}: Jacobson-type Einstein branch via a rest-frame relation plus tensor upgrade & D3+D4 and Axioms~\ref{ax:screen}--\ref{ax:entropy} & fixed-volume area-variation identity for small geodesic balls; local quadratic-polarization argument for the tensor upgrade & Theorem~\ref{thm:equilibrium}, which fixes the admissible fixed-cap MaxEnt variation class and derives generalized-entropy stationarity on the realized cap-label-preserving MaxEnt family; the internal small-ball bridge of Lemma~\ref{lem:smallball}, which uses the geometric cap generator together with the D4 half-line generator/charge identification and Lemma~\ref{lem:bounded-interval-kernel}; Theorem~\ref{thm:fixed-volume-small-ball-area}; locally Lorentzian \(d=4\) scaling regime, supplied conditionally by the D4b event-manifold packet under receipts \(\mathsf{E1}\)--\(\mathsf{E4}\) (\S\ref{subsec:event-manifold}); small-ball constancy assumptions; Lemma~\ref{lem:diagonal-remainder} for \(o(\ell^4)\) control; all local directions/reference states for the tensor upgrade via Lemma~\ref{lem:cap-pair-timelike-coverage}; the uniform scaling family, coverage, and absolute base condition are supplied by Theorems~\ref{thm:uniform-scaling-family}--\ref{thm:absolute-einstein-base-condition} under the \(\mathsf{VR}\)/\(\mathsf{UC}\) receipts, and the full chain is composed in Theorem~\ref{thm:einstein-branch-entry-composed} with realized-branch nonemptiness open (Remark~\ref{rem:realized-branch-status}) & scaling-limit theorem package plus composed branch-entry theorem \\
\textbf{D6} & Theorem~\ref{thm:lambda-stack}: conditional local/global theorem stack for \(\Lambda\), namely the null-invisible metric ambiguity, proposed screen-capacity closure of the same Einstein branch, the de Sitter entropy relation with scale-certified static-patch display, and the cosmic record-closure target, plus a legacy neutrino side estimate & D5 local Einstein recovery, which leaves the \(+\Lambda g_{ab}\) ambiguity & de Sitter entropy relation, static-patch radius/time formulas after scale certification, finite self-closing normal-form counting/readback, and dimensional analysis & constructed readback map \(F\), fixed-point certificate, CP-1--CP-3, and conditional identification with the de Sitter entropy readout & global self-closure target (\(F\) unconstructed; CP-1--CP-3 open; CL-7) \\
\textbf{D7} & Theorem~\ref{thm:refinement-functor-fiber-descent}, Theorem~\ref{thm:sector-colimit}, Theorem~\ref{thm:compactgauge}: refinement-stable bosonic sector category and compact gauge reconstruction; Theorem~\ref{thm:oph-4d-euclidean-yang-mills-form}: conditional four-dimensional Euclidean Yang--Mills form; Theorem~\ref{thm:oph-yang-mills-gap}: conditional support-visible compact-gauge Yang--Mills repair gap & Axioms~\ref{ax:screen}--\ref{ax:entropy} plus the compact-gauge refinement receipt & directed-colimit descent for monoidal \(C^*\)-categories; Doplicher--Roberts / Tannaka reconstruction; holonomy-to-curvature expansion; finite-stage conditional expectations and spectral comparison for commuting collar projections & Theorems~\ref{thm:transport-from-gluing} and \ref{thm:fixed-cutoff-bosonic-sector-category} on the ordinary or central-defect bosonic zero-obstruction branch, plus Definition~\ref{def:compact-gauge-refinement-receipt} for Theorem~\ref{thm:refinement-functor-fiber-descent}; Theorem~\ref{thm:mar-witness-landing} supplies realized MAR-admissible witness data, while D8--D9 contain Standard Model selection; the Yang--Mills statements additionally require the finite cylinder/projective extraction theorem and the renormalized Yang--Mills, finite ground-state-transform/cross-fiber, transfer/vacuum, OS-regularity/noncollapse, and uniform-gap receipts; the genuinely noncentral fixed-cutoff branch remains separate & conditional structural theorem \\
\textbf{D8} & Lemmas~\ref{lem:mincontent}--\ref{lem:commutant}, Theorem~\ref{thm:sm}: product gauge structure up to finite quotient & D7 + Axiom~\ref{ax:mar} & compact Lie representation classification; Schur's lemma & the same ordinary or central-defect bosonic branch as D7, together with a connected positive-dimensional Lie admissible class, one connected abelian factor, and faithful action on the minimal coupled carrier & realized-branch theorem \\
\textbf{D9} & Theorem~\ref{thm:realized-sm-branch}, Theorem~\ref{thm:hypercharge}, Corollaries~\ref{cor:nc}, \ref{cor:ng}, \ref{cor:electroweak-force}, Proposition~\ref{prop:z6}: realized Standard Model quotient, hypercharges, structural electroweak force content, \(N_c=3\), \(N_g=3\), and product-group corollaries & D8 & anomaly-cancellation algebra; Witten global-anomaly argument; CKM CP counting; stabilizer computation for a nonzero neutral Higgs vacuum vector & realized one-generation chiral matter plus one Higgs package, with the CP-capability and weak-sector UV clauses contained in Axiom~\ref{ax:mar}; no extra post-MAR selector is used & realized-branch theorem/corollary chain \\
\textbf{D10} & forward gauge-coupling closure and declared electroweak readout of Section~7 & D9 + pixel ratio \(P\) & printed RG evolution, matching, and scheme-conversion conventions & pixel constraint and the source-only forward transmutation solve \(\mathcal F(\alpha_U;P)=0\); the fixed-cutoff edge heat-kernel / Casimir theorem on the microphysics surface together with the compact-group / Peter--Weyl lift used on the D10 lane; printed beta-function, threshold, and scheme-conversion conventions & quantitative-closure sector \\
\textbf{D12} & Sections~8--10 continuations:\newline charged leptons,\newline \(H^3\) record-worldline stitch certificates,\newline strong CP,\newline proton spin/lifetime,\newline and controlled string/worldsheet effective-description branches & various subsets of D6, D9, and D10 & branch-specific EFT\newline and phenomeno\-logical\newline manipulations & additional ans\"atze such as the uniform\newline \(\mathbb Z_6\) center-label ensemble, texture choices,\newline declared \(H^3\) atlas and ID-independent cross-boundary assignment certificates,\newline dark-sector response assumptions,\newline discrete-horizon assumptions, a distinct\newline large-\(N_{\mathrm{edge}}\) regime with fixed\newline \(\tau=tN_{\mathrm{edge}}\) window and uniform\newline genus-remainder control, or additional\newline worldsheet/CFT assumptions & phenomeno\-logical\newline continuation \\
\end{longtable}
\endgroup

The dependency DAG records the immediate internal parents, imported mathematics, branch-local constructions, and external data for each node.

\begin{theorem}[Summary theorem for the recovered relativity-plus-Standard-Model core]\label{thm:master}
This theorem packages the recovered-core nodes D1--D5 and D7--D9 of the dependency DAG above; the gravity-side chain through D3h, D4, D4b, D4c, and D4d is additionally composed, with partitioned inputs and a no-hidden-geometry audit, in the branch-entry theorem \ref{thm:einstein-branch-entry-composed}. Node D6 sits outside this recovered-core theorem as a conditional global-closure target whose readback map and coupling premises are open; D10 and D12 are outside this theorem's scope. Assume Axioms~\ref{ax:screen}--\ref{ax:entropy}, Axiom~\ref{ax:mar}, a cofinal tail carrying the compact-gauge refinement receipt of Definition~\ref{def:compact-gauge-refinement-receipt}, and the hypotheses of Theorems~\ref{thm:confluence}, \ref{thm:boundary-conditioned-uniqueness}, \ref{thm:bw}, \ref{thm:stress}, \ref{thm:einstein}, \ref{thm:refinement-functor-fiber-descent}, \ref{thm:sector-colimit}, \ref{thm:compactgauge}, \ref{thm:sm}, and \ref{thm:hypercharge}, together with Corollaries~\ref{cor:ng}, \ref{cor:nc}, and Proposition~\ref{prop:z6}. Then, on the support-visible scaling branch of Theorem~\ref{thm:bw}:
\begin{enumerate}[label=(\roman*),leftmargin=2em]
\item overlap repair admits a unique schedule-independent normal form from each fixed initial
physical quotient state, and from fixed boundary/sector data when the consistent quotient
extension in that fiber is unique;
\item cap modular flow on the extracted prime geometric cap pair is geometric and yields the connected Lorentz group
\[
\Conf^+(S^2)\cong \mathrm{SO}^+(3,1);
\]
the associated observer-facing spatial chart is
\[
H^3\simeq \mathrm{SO}^+(3,1)/\mathrm{SO}(3),
\qquad
\dim H^3=3;
\]
\item the derived fixed-cap generalized-entropy stationarity theorem for admissible fixed-cap MaxEnt variations on the realized cap-label-preserving MaxEnt family together with the null modular bridge and the bounded-interval kernel of Lemma~\ref{lem:bounded-interval-kernel} yield the Jacobson-type rest-frame relation
\[
\delta\!\left(G_{00}+\Lambda g_{00}\right)=8\pi G\,\delta\langle T_{00}\rangle
\]
at the cap center in the diamond rest frame; if that rest-frame relation holds for all local directions and reference states in the scaling regime, then the null-to-tensor upgrade gives
\[
G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle;
\]
\item on the ordinary or central-defect bosonic zero-obstruction branch with the stated refinement receipt, the edge-sector category reconstructs a compact gauge group, and the realized connected gauge structure has the form
\[
\frac{\SU(3)\times\SU(2)\times\U(1)}{\Gamma}
\]
for some finite central subgroup \(\Gamma\).
\end{enumerate}
After the hypercharge lattice, color-count, generation-count, and trivial-action quotient steps, the finite quotient is fixed to \(\Gamma=\mathbb Z_6\), so the realized gauge structure on the realized MAR-admissible branch is
\[
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6},
\qquad
N_c=3,
\qquad
N_g=3,
\]
with the exact Standard Model hypercharge lattice on the realized matter package. The same package also fixes the structural electroweak force content: the weak \(\SU(2)_L\) factor, the hypercharge \(\U(1)_Y\) factor, the nonzero neutral-Higgs vacuum-vector stabilizer \(\U(1)_Q\), and the \(W^\pm/Z/A_Q\) generator and connection directions. Here the count statements are internal to the same realized branch: the D8 minimal coupled-carrier theorem stack fixes the color triplet and hence \(N_c=3\); CKM phase counting and weak-sector asymptotic freedom then bound \(N_g\) on that same one-Higgs branch; MAR fixes the smallest realized value \(N_g=3\); and Witten's \(\SU(2)\) anomaly is retained only as a consistency check on the resulting triplet-doublet package.
\end{theorem}

\begin{proof}
Items (i)--(iii) are collected from Theorem~\ref{thm:confluence}, Corollaries~\ref{cor:lorentz} and \ref{cor:h3-spatial-chart}, Theorem~\ref{thm:einstein}, and Theorem~\ref{cor:einstein}. On the gauge side, Theorem~\ref{thm:transport-from-gluing} supplies the strict zero-obstruction transport criterion and Theorem~\ref{thm:fixed-cutoff-bosonic-sector-category} constructs the fixed-cutoff bosonic collar-sector categories. Given the compact-gauge refinement receipt, Theorem~\ref{thm:refinement-functor-fiber-descent} constructs the monoidal refinement transport and compatible forgetful fibers. Theorem~\ref{thm:sector-colimit} descends those data to the refinement-limit category and fiber functor, and compact gauge reconstruction is then Theorem~\ref{thm:compactgauge}. Theorem~\ref{thm:gauge-selection-factorization} separates this classification stage from the MAR selection stage. The realized nontrivial branch is supplied by Theorem~\ref{thm:mar-witness-landing}. The product gauge structure up to finite quotient is Theorem~\ref{thm:sm}; and the final identification of the exact Standard Model quotient and structural electroweak content is Theorem~\ref{thm:realized-sm-branch}, Theorem~\ref{thm:hypercharge} together with Corollaries~\ref{cor:nc}, \ref{cor:ng}, \ref{cor:electroweak-force}, and Proposition~\ref{prop:z6}.
\end{proof}

Theorem~\ref{thm:master} therefore packages only the recovered relativity-plus-Standard-Model core: D1--D5 together with D7--D9. D6 is the conditional global-closure target for the same Einstein branch; construction of \(F\), its fixed-point certificate, and CP-1--CP-3 lie outside the recovered-core theorem. The quantitative-closure branch and phenomenological continuations are also outside the theorem's scope. Two qualifiers govern every reading of the theorem: the Standard Model content enters through the admissibility clauses of Axiom~\ref{ax:mar} (MAR), so the gauge quotient, hypercharge lattice, and count statements are conditional on those clause inputs; and realized-branch nonemptiness is open.

\subsection*{Comparison with Common Starting Assumptions}

\begingroup
\footnotesize
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.28\textwidth}>{\raggedright\arraybackslash}p{0.26\textwidth}>{\raggedright\arraybackslash}p{0.36\textwidth}@{}}
\toprule
Structure & Common treatment & OPH treatment \\
\midrule
Lorentz kinematics and spatial dimension & background symmetry or starting axiom & scaling-limit branch from geometric modular flow on screen caps; the rest-space chart is \(H^3\simeq\mathrm{SO}^+(3,1)/\mathrm{SO}(3)\) and has dimension \(3\) \\
Einstein dynamics & fundamental field equation & first-variation relation with tensor upgrade from generalized entropy, null modular data, and derived fixed-cap generalized-entropy stationarity \\
Gauge group & model input & construction of the refinement-limit bosonic edge-sector category, then compact group reconstruction from it; exact SM quotient selected on the realized MAR-admissible branch with the realized one-generation/one-Higgs package \\
Hypercharge lattice & matter-assignment input & solved from anomaly cancellation and Yukawa invariance on the realized one-generation chiral matter plus one-Higgs package \\
Color and generation count & empirical input & color triplet fixed by the D8 minimal coupled carrier; generation count fixed by CKM phase counting, weak-sector asymptotic freedom, and MAR; Witten parity retained as a consistency check \\
Flavor hierarchy unit & model-dependent small parameter & phenomenological ansatz \(\varepsilon=1/6\) motivated by a uniform \(\mathbb Z_6\) center-label ensemble \\
Charged-lepton continuation & empirical Koide relation & The charged-lepton masses empirically satisfy \(Q=2/3\). For the positive Hermitian \(C_3\) carrier, \(Q=[1+2(\rho/a)^2]/3\). The minimal orientation record gives \(S_c-S_0=\ln2\); the connected \(M_6(\mathbb C)\) event has equal rank-two blocks, so Born--L\"uders conditioning and the tracial-GNS map give \(|b|/a=1/\sqrt2\) and \(Q=2/3\). Given MAR selection of an accepted three-family chiral sector, reversible checkpoint recovery forces \(\Phi=\operatorname{Ad}_{J_L\oplus J_E}\), \(\widehat Y_e=(\sqrt2/v)J_LM_FJ_E^\dagger\), and \(\mathcal M_L=J_LM_FJ_L^\dagger\). The extended \(\mathrm{OPH}^{+}_{\rm ch}\) branch adds graded physical completion, quotient source-law selection, and a source-closed QFT fixed-point certificate. Its dressed readout gives \(Q=2/3\) on the balanced \(C_3\) fixed point and \(Q=[1+e^{-2\chi_\star}]/3\) on the attenuated \(C_3\) branch; off-plane response uses the full operator. These are additional branch conditions beyond OPH5. The \(2/9\) phase and numerical mass ratios are compare-only \\
Cosmological constant & local vacuum-energy puzzle & conditional global screen-capacity target \(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})\), with \(F\), its fixed-point certificate, and CP-1--CP-3 open; under those hypotheses \(\Lambda_{\mathrm{CRC}}\ell_\star^2=3\pi/N_{\mathrm{CRC}}\), with the SI display supplied by the selected scale certificate \\
\bottomrule
\end{tabular}
\endgroup

\paragraph{Icosahedral charged-carrier refinement.}
The declared twelve-vertex screen also has a twenty-face orbit
\(A_5/C_3\); the order-three stabilizer cyclically permutes the three corners
of each outward-oriented face.  This gives an exact bundle of local geometric
\(C_3\) fibers and a face-representative-independent unordered spectrum for an
equivariant Hermitian circulant.  It does not by itself give one global
three-dimensional physical generation space: the sixty face-corner flags form
the regular \(A_5\) torsor, so a quotient-visible charged-family attachment is
work in progress.  A retrospectively designed face-incidence continuation on
this carrier reproduces frozen rounded charged comparison fields extremely
closely on one hybrid branch.  A follow-up conditional theorem proves that its
explicitly declared three-coordinate affine map is contractive and has one
iteratively stable fixed point.  Source-multiplier countermodels with the same
displayed symmetry and contraction change that fixed point, so the map is not
selected by those properties.  A later CFQ sufficiency theorem proves that
eight stipulated finite registers with rank-one normalized-trace weights, a
unit clock, and an exhaustive multiplicity-one signed path catalogue uniquely
reproduce the same scalar affine map inside that declared packet.  Every
physical CFQ gate is unset: the register dimensions, paths, signs, clock, and
exhaustion are assumptions rather than outputs of OPH dynamics.  A
subsequent engineered finite model proves that this packet is nonempty and
implements noncentral rank-one events with central accepted/rejected record
pointers in \(\mathcal B(H)\otimes D_2\), together with \(A_5\)-covariant graph charts and
inert ancillary stabilization.  This is a formal fixed-cutoff model, not a
physical source derivation: its coefficient-bearing registers, automaton,
grading, clock, and response are hard-coded, and its self-declared dependency
DAG omits the known retrospective design history.  The theorem and model
therefore show that the stipulated schema is nonempty and bridge a noncentral
event to a central record at fixed cutoff.  They instantiate a bounded digital
patch with local registers, interfaces, readback records, and accepted/rejected
feedback, but do not select that observer-like structure from OPH dynamics.
Its bare-to-endpoint MaxEnt compensation,
phase transport, normalized determinant character, physical packet and family
attachments, refinement naturality, coherent source branch, and pole scheme
remain underived.  It is a target-informed continuation candidate, not a
prediction or an extension of the compact theorem surface.

A downstream nature-and-pole package gives a useful conditional interface.
If a physical chiral three-family carrier, natural intertwiners, and the
identity
\[
 \frac{v^2}{2}\widehat Y_e\widehat Y_e^\dagger
 =J_LM_F^2J_L^\dagger
\]
are supplied, uniqueness of the positive square root transports the face
operator to the physical left charged response.  If an exact renormalized
charged kernel and a CFQ--Dyson intertwiner whose readout is
\(J_LM_FJ_L^\dagger\) are also supplied, regular field changes and the stated
Nielsen factorization preserve its singularity set.  These are valid transport
lemmas, not missing source theorems: the first displayed identity is the
load-bearing nature attachment, and the Dyson readout premise is the
load-bearing pole attachment.  The submitted finite kernel
\(K_0(s)=sI-M_F^2\) has zero self-energy and only proves formal existence.  No
physical NI or RP certificate is emitted, the parent hybrid branch remains
target-informed, and no mass or pole row is promoted.

\section{Observer Overlap Consistency as a Fixed-Point Problem}

The discrete overlap problem is the mathematical skeleton of the framework.

\begin{definition}[Patch Net]\label{def:patchnet}
Let $G=(V,E)$ be a finite connected graph. Each vertex $i\in V$ carries a finite local state space $S_i$. For each edge $e=\{i,j\}$ let $I_e$ be an interface alphabet and let
\[
\pi_{i,e}:S_i\to I_e,
\qquad
\pi_{j,e}:S_j\to I_e
\]
be interface projections. The global state space is
\[
\Sigma=\prod_{i\in V} S_i,
\]
and the consistency set is
\[
C=\bigl\{s\in\Sigma:\pi_{i,e}(s_i)=\pi_{j,e}(s_j)\ \text{for all }e=\{i,j\}\in E\bigr\}.
\]
\end{definition}

This finiteness is a regulator-level assumption for the discrete patch-net normal-form theorem; it is not the continuum limit statement.

Define the inconsistency potential
\[
\Phi(s)=\sum_{e=\{i,j\}\in E}w_e\, d_e\!\bigl(\pi_{i,e}(s_i),\pi_{j,e}(s_j)\bigr),
\]
with $w_e>0$ and $d_e(a,b)=0$ iff $a=b$.

Let
\[
q_{\mathrm{phys}}:\Sigma\to Q
\]
be the physical quotient map identifying hidden representatives with the same observer-facing
overlap data, and write
\[
C_Q:=q_{\mathrm{phys}}(C).
\]
Primitive collar recoveries are required to descend to quotient proposals on \(Q\). The accepted
repair relation on \(Q\) is the transactional relation defined below. When no hidden
representative quotient is present, take \(Q=\Sigma\).

\begin{remark}[Default code claim]\label{rem:constraint-code-firewall}
At this level the overlap net is a finite constraint code and nothing stronger: the codewords are
the states in \(C\), equivalently the zero set \(C=\Phi^{-1}(0)\). A graph min-cut, by itself,
does not determine the distance of this code, since the same graph can carry trivial constant
readouts with distance \(1\) or repetition constraints with distance \(|V|\). QECC distance,
topological-code resilience, Knill--Laflamme correction, exponential convergence, and BFT
wall-clock liveness are therefore read only on the corresponding certified branches, not from the
bare overlap graph.
\end{remark}

\begin{definition}[Recovery-derived local repair law]
A law $\lambda$ is a family of local repair maps
\[
T_i^\lambda:\Sigma\to\Sigma
\]
changing only patch $i$ or a bounded neighborhood of $i$. On the fixed-cutoff collar branch these
are not free rewrite primitives: each local update is only a proposal read from exact Markov splice
or a declared Petz/Fawzi--Renner recovery move on a collar chart around \(i\), then lifted back to
the finite patch presentation. A proposal becomes physical only after the quotient transaction
below validates its read snapshot, write support, preserved boundary/sector data, and strict
descent. Parenthesization-independent union-collar gluing supplies candidate aggregate payloads;
it does not by itself authorize two overlapping one-site commits.
\end{definition}

\begin{definition}[Transactional quotient repair branch]\label{def:transactional-quotient-repair}
Fix a boundary/sector/holonomy record map \(B:Q\to\mathcal B\) and a well-founded exact measure
\(\mu:Q\to(W,\prec)\), such as a lexicographic integer vector
\((N_{\mathrm{hard}},\Phi_Q,N_{\mathrm{unresolved}})\). A prepared repair transaction is a tuple
\[
\tau=(R_\tau,W_\tau,\sigma_\tau,p_\tau)
\]
of a read set, write set, read snapshot, and quotient payload. It may commit at \(x\in Q\) only
when the snapshot is current on \(R_\tau\), the payload changes no register outside \(W_\tau\),
\(B\) is preserved, and
\[
\mu(\operatorname{Apply}_\tau(x))\prec\mu(x).
\]
A stale or aborted transaction is not a rewrite step. The read set is validation-complete for the
measure: whenever a term of \(\mu\) can change because a written register changes, that term's
whole support is read. For seam potentials this means reading both endpoints of every seam whose
score can change.

At a state \(x\), form the conflict graph of enabled primitive repair proposals, with
\(\tau\#\sigma\) when either write set intersects the other's read-or-write set. Each connected
component \(K\) is replaced by exactly one canonical aggregate transaction \(\tau_K\), computed on
the union collar/component support. Primitive members of \(K\) do not commit separately. Write
\(x\Rightarrow y\) for a successful aggregate commit.
\end{definition}

\begin{definition}[Quotient repair operators]\label{def:quotient-repair-operators}
For a fixed finite transactional quotient repair branch, let \(\mathsf A\) be the finite set of
accepted aggregate transactions, each with a domain \(D_a\subseteq Q\), equipped with a fixed total
order \(\prec_{\mathsf A}\).  For \(x\in Q\), write
\[
\mathsf A(x)=\{a\in\mathsf A:x\in D_a\}
\]
for the enabled aggregate transactions at \(x\).  The local quotient repair map is
\[
\operatorname{locRep}_\lambda(x):=
\begin{cases}
a_{\min}(x),& \mathsf A(x)\ne\varnothing,\\
x,& \mathsf A(x)=\varnothing,
\end{cases}
\]
where \(a_{\min}\) is the \(\prec_{\mathsf A}\)-least enabled transaction.  Iterating
\[
x_0=x,\qquad x_{n+1}=\operatorname{locRep}_\lambda(x_n)
\]
reaches a least fixed stage because every nontrivial accepted step strictly descends in the finite
set \(\mu(Q)\).  Define
\[
\operatorname{Rep}_\lambda(x):=x_{N(x)}.
\]
\end{definition}

\begin{proposition}[Local quotient repair closure]\label{prop:local-quotient-repair-closure}
On any branch satisfying boundary preservation, exact descent, and repair completeness,
\[
\operatorname{locRep}_\lambda:Q\to Q
\]
is total, preserves \(B\), and either fixes \(x\) or strictly lowers \(\mu\).  It satisfies
\[
\operatorname{locRep}_\lambda(x)=x
\quad\Longleftrightarrow\quad
x\in C_Q.
\]
\end{proposition}

\begin{proof}
Finiteness and the fixed order on \(\mathsf A\) give the least enabled transaction whenever one
exists; if none exists, the definition returns \(x\).  Boundary preservation and exact descent are
the transaction acceptance tests.  Strict descent excludes a nontrivial fixed move, and repair
completeness identifies states with no enabled aggregate transaction with \(C_Q\).
\end{proof}

\begin{lemma}[Validation support for local mismatch measures]\label{lem:validation-support}
Suppose the exact measure has local finite supports,
\[
\mu(x)=\sum_{a\in A}\mu_a(x|_{S_a}),
\qquad S_a\subseteq D .
\]
For a transaction writing \(W\subseteq D\), only terms with \(S_a\cap W\ne\varnothing\) can change.
Thus the descent test is snapshot-local once the read set contains
\[
R^\mu(W):=\bigcup_{a:S_a\cap W\ne\varnothing}S_a .
\]
For an OPH edge mismatch potential this says that a seam transaction must read both endpoints of
every overlap whose score may change under the write.
\end{lemma}

\begin{proof}
If \(S_a\cap W=\varnothing\), the transaction leaves every argument of \(\mu_a\) unchanged, so that
term cancels in the pre/post comparison. Every remaining term is determined by the payload and the
restriction to \(R^\mu(W)\). The edge-mismatch statement is the specialization in which each term
is supported on the two endpoint registers of one overlap.
\end{proof}

\begin{theorem}[Transactional quotient normal-form uniqueness]\label{thm:confluence}
Assume:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2em]
\item finite transactional descent: \(x\Rightarrow y\) implies \(\mu(y)\prec\mu(x)\);
\item atomic conflict-component commits as in Definition~\ref{def:transactional-quotient-repair};
\item repair completeness: terminal quotient states for \(\Rightarrow\) are exactly \(C_Q\).
\end{enumerate}
Then every initial quotient state \(x\in Q\) has a unique terminal normal form
\[
N_Q(x)=\operatorname{Rep}_\lambda(x)\in C_Q,
\]
and \(N_Q(x)\) is independent of asynchronous repair order.  The map
\[
\operatorname{Rep}_\lambda:Q\to Q
\]
is total, boundary-preserving, and idempotent, and
\[
\operatorname{Rep}_\lambda(x)=x
\quad\Longleftrightarrow\quad
x\in C_Q.
\]
\end{theorem}

\begin{proof}
Well-founded descent gives termination. For a one-step peak
\(y\Leftarrow x\Rightarrow z\), let the two commits come from conflict components \(K\) and \(L\).
If \(K=L\), canonical aggregation gives the same aggregate payload, hence \(y=z\). If \(K\ne L\),
the components have disjoint read/write supports. Snapshot validity, unchanged-outside-write
validation, and validation-complete read sets preserve each transaction after the other
commits; applying them in either order gives the same quotient state. Thus the aggregate relation
has the local diamond. Newman's lemma~\cite{newman42} says that a terminating locally confluent
rewrite system is confluent. If two terminal states \(y,z\) are reachable from the same \(x\),
confluence gives a common descendant \(w\). Since \(y\) and \(z\) are terminal, \(y=w=z\). Repair
completeness identifies the terminal state with an element of \(C_Q\), so \(N_Q:Q\to C_Q\) is
well defined and schedule-independent.  The canonical iteration in
Definition~\ref{def:quotient-repair-operators} is one valid accepted repair execution, hence
\(\operatorname{Rep}_\lambda(x)=N_Q(x)\).  Boundary preservation follows by induction along
accepted transactions.  Idempotence and the fixed-point characterization follow from
Proposition~\ref{prop:local-quotient-repair-closure}, since every element of \(C_Q\) has no enabled
aggregate transaction.
\end{proof}

\begin{remark}[Confluence is an extra obligation]
The descent argument above proves termination only. OPH does not infer uniqueness from termination.
Uniqueness and order-independence enter through the atomic conflict-component local diamond on the
physical quotient, Newman's lemma, and repair completeness. Receipts named seam descent, atomic
commit, distributed local diamond, repair completeness, and normal-form hash are evidence
contracts for this theorem surface, not substitutes for these hypotheses and not selectors among
physically distinct minimizing quotient states. If two accepted schedules from the same initial
state terminate in different observer-facing quotient normal forms, with no declared
holonomy/higher-gauge obstruction and no mere hidden-representative difference, then the proposed
repair law fails the fixed-cutoff consensus criterion.
\end{remark}

\begin{corollary}[Schedule Independence]
If observables factor through \(Q\) and are evaluated on \(N_Q(q_{\mathrm{phys}}(s))\), the
resulting physical law is independent of update order from the fixed initial quotient state
\(q_{\mathrm{phys}}(s)\).
\end{corollary}

\begin{theorem}[Boundary-conditioned uniqueness]\label{thm:boundary-conditioned-uniqueness}
Let
\[
B:Q\to\mathcal B
\]
record fixed external boundary data, conserved charge, root packet, holonomy sector, or task
input. Assume \(B\) is preserved by accepted repairs:
\[
x\Rightarrow y\implies B(x)=B(y).
\]
If for each \(b\in\mathcal B\) the consistent quotient fiber
\[
C_b:=\{x\in C_Q:B(x)=b\}
\]
has at most one element, then all initial quotient states with boundary value \(b\) settle to the
same observer-facing normal form. Equivalently, \(B(x)=B(x')\) implies
\[
N_Q(x)=N_Q(x').
\]
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:confluence}, \(N_Q(x)\) and \(N_Q(x')\) exist and lie in \(C_Q\). Boundary
preservation along repair sequences gives \(B(N_Q(x))=B(x)\) and
\(B(N_Q(x'))=B(x')\). If \(B(x)=B(x')=b\), then both normal forms lie in \(C_b\). The unique
consistent extension assumption says \(C_b\) has at most one element, hence the two normal forms
are equal.
\end{proof}

\begin{remark}[Generic cross-source criterion]
For an observation-preserving repair relation whose normal forms are exactly the consistent
states, Ref.~\cite{observableNormalForms} proves that agreement, modulo any declared silent
equivalence, of normal endpoints reached from every pair of same-boundary sources is equivalent
to injectivity of the induced boundary map on the consistent quotient. This cross-source
criterion is distinct from same-source confluence and from liveness. In this paper,
Theorem~\ref{thm:confluence} supplies the same-source endpoint result, while
Theorem~\ref{thm:boundary-conditioned-uniqueness} applies only after the consistent boundary
fiber is proved singleton. The layered and functional results discharge that premise only on
their named finite carrier branches.
\end{remark}

\begin{definition}[Layered functional boundary carrier]\label{def:layered-functional-boundary-carrier}
A layered functional boundary carrier is a finite directed layered graph
\[
V=L_0\sqcup L_1\sqcup\cdots\sqcup L_D,\qquad D\ge2,
\]
with boundary layer \(L_0\), finite alphabets \(A_v\), nonempty parent sets
\[
P(v)\subseteq L_0\sqcup\cdots\sqcup L_{d-1}\qquad(v\in L_d,\ d\ge1),
\]
and deterministic local rules
\[
F_v:\prod_{u\in P(v)}A_u\to A_v.
\]
Let
\[
Q=\prod_{v\in V}A_v,\qquad B(a)=a|_{L_0}.
\]
For boundary data \(b\), define \(E(b)\in Q\) recursively by \(E(b)_v=b_v\) on \(L_0\) and
\[
E(b)_v=F_v((E(b)_u)_{u\in P(v)})
\qquad(v\in L_d,\ d\ge1).
\]
Optional cross-check predicates may be added.  A state is consistent when all functional equations
and cross-check predicates pass; let \(C_Q\) be the consistent state set.  A boundary \(b\) is
admissible when \(E(b)\in C_Q\).  The layer repair map \(R_d\) rewrites exactly layer \(L_d\) to
the displayed functional value and fixes all other layers.
\end{definition}

\begin{theorem}[Layered carrier proves \(H_B\wedge H_{\mathrm{fib}}\)]\label{thm:layered-carrier-HB-Hfib}
For a layered functional boundary carrier, set
\[
a^{(0)}=a,\qquad a^{(d)}=R_d(a^{(d-1)}),\quad d=1,\ldots,D,
\]
and let \(b=B(a)\).  Then
\[
B(a^{(d)})=b\qquad(d=0,\ldots,D).
\]
If \(b\) is admissible, then \(a^{(D)}=E(b)\in C_Q\), and
\[
C_Q\cap B^{-1}(b)=\{E(b)\}.
\]
Consequently, on any accepted quotient repair presentation whose aggregate transactions include
the layer repairs and whose boundary value \(b=B(x)\) is admissible,
\[
\operatorname{Rep}_\lambda(x)=E(B(x)).
\]
\end{theorem}

\begin{proof}
Each \(R_d\) writes only \(L_d\) with \(d\ge1\), so no stage changes \(B\).  Induct on \(d\): after
stage \(d\), every vertex in \(L_0\sqcup\cdots\sqcup L_d\) agrees with \(E(b)\), because all
parents of a layer-\(d\) vertex lie in earlier layers.  Thus \(a^{(D)}=E(b)\), and admissibility
puts it in \(C_Q\).  If \(c\in C_Q\cap B^{-1}(b)\), the same induction applied to the functional
equations for \(c\) gives \(c=E(b)\).  The final equality follows because
Theorem~\ref{thm:confluence} makes \(\operatorname{Rep}_\lambda(x)\) a boundary-preserving element
of \(C_Q\).
\end{proof}

\begin{theorem}[Functional selected-fiber uniqueness]\label{thm:functional-selected-fiber}
Let a same-boundary quotient fiber \(Q_b:=B^{-1}(b)\) be presented on a rooted finite packet tree
\(T\) with root \(r\). Suppose the boundary fixes the root value \(u_r=\beta(b)\), and for each
non-root vertex \(v\) there is a deterministic extension map
\[
f_v:X_{p(v)}\times\mathcal B\to X_v .
\]
Define \(u_b\) recursively by \(u_v=f_v(u_{p(v)},b)\). If all non-tree overlaps, sector checks,
and holonomy checks pass on \(u_b\), then \(C_b=\{u_b\}\). If any such check fails, then
\(C_b=\varnothing\).
\end{theorem}

\begin{proof}
Tree edges force each vertex value recursively from the root and \(b\), so any consistent state in
the fiber must equal \(u_b\) on every tree vertex. The remaining equations are exactly the
non-tree overlap, sector, and holonomy checks. If they pass, \(u_b\) is the single consistent
extension. If one fails, no tree-compatible candidate satisfies all consistency equations.
\end{proof}

\begin{corollary}[Nontrivial branch elimination]\label{cor:branch-elimination}
Assume Theorem~\ref{thm:confluence}, boundary preservation, and
Theorem~\ref{thm:functional-selected-fiber}. If \(|Q_b|\ge2\) and \(C_b=\{u_b\}\), then every
candidate state in \(Q_b\) normalizes to \(u_b\), while \(Q_b\setminus C_b\) is nonempty and is
eliminated by repair. Surviving candidates therefore share one quotient normal form. If the
selected fiber is empty the branch is obstructed, and if a union solver finds two physically
distinct consistent quotient endpoints the branch is ambiguous instead of hash-selected.
\end{corollary}

\begin{theorem}[Cycle Obstruction / Holonomy Criterion]\label{thm:holonomy}
Let $A$ be an abelian group. For each oriented edge $e:u\to v$ assign $b_e\in A$ and consider the affine overlap equations
\[
x_v-x_u=b_e.
\]
A global solution exists if and only if the signed sum of $b_e$ vanishes on every cycle.
\end{theorem}

\begin{proof}
Summing the edge equations around a cycle gives necessity. For sufficiency, fix a root and define each $x_v$ by summing labels along a path from the root to $v$. Vanishing cycle sums make this independent of the chosen path.
\end{proof}

\begin{definition}[Physical repair law and representative lift]\label{def:physicalrepair}
Suppose a local gauge group $\Gamma=\prod_i \Gamma_i$ acts on $\Sigma$ while leaving all interface
data invariant. Write
\[
q:\Sigma\to\Sigma/\Gamma,
\qquad
q(s)=[s].
\]
A physical repair law is the family of local quotient maps induced by the
recovery-derived collar updates just described:
\[
\overline T_i^\lambda:\Sigma/\Gamma\to\Sigma/\Gamma
\]
on the overlap-invariant quotient. A representative repair family is any family
\[
T_i^\lambda:\Sigma\to\Sigma
\]
with
\[
q\circ T_i^\lambda=\overline T_i^\lambda\circ q.
\]
\end{definition}

\begin{proposition}[Representative lifts descend to the quotient]\label{prop:repairquot}
For any representative repair family of Definition~\ref{def:physicalrepair},
\[
q\bigl(T_i^\lambda(\gamma\cdot s)\bigr)=q\bigl(T_i^\lambda(s)\bigr)
\qquad
\forall\, i,\ \forall\, \gamma\in\Gamma,\ \forall\, s\in\Sigma.
\]
In particular the repair relation descends to \(\Sigma/\Gamma\) without any extra
gauge-covariance axiom.
\end{proposition}

\begin{proof}
Because \(q(\gamma\cdot s)=q(s)\),
\[
q\bigl(T_i^\lambda(\gamma\cdot s)\bigr)
=
\overline T_i^\lambda\bigl(q(\gamma\cdot s)\bigr)
=
\overline T_i^\lambda\bigl(q(s)\bigr)
=
q\bigl(T_i^\lambda(s)\bigr).
\]
So gauge-equivalent inputs induce the same repaired physical state.
\end{proof}

\begin{proposition}[Gauge Quotient]\label{prop:gauge}
Under Definition~\ref{def:physicalrepair}, Proposition~\ref{prop:repairquot}, and
Theorem~\ref{thm:confluence} with \(Q=\Sigma/\Gamma\), the normal-form map is a quotient map:
\[
\overline N_\lambda:\Sigma/\Gamma\to q(C),
\qquad
[s]\mapsto N_Q([s]).
\]
Hence gauge-invariant observables are unique on the quotient, and the fixed-cutoff physical
observable algebra has representative-independent terminal expectations on that carrier.
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:repairquot}, every repair step has quotient image determined only by the
current orbit. Iterating, the quotient image of any repair sequence depends only on the initial
orbit. Theorem~\ref{thm:confluence} gives a unique terminal quotient normal form \(N_Q([s])\)
from that orbit. This makes \(\overline N_\lambda\) well-defined.
\end{proof}

\begin{corollary}[Repair respects gauge]\label{cor:repair-respects-gauge}
Define the quotient-valued representative repair map
\[
\operatorname{Rep}^{\Sigma}_\lambda
:=
\operatorname{Rep}_\lambda\circ q
:
\Sigma\to\Sigma/\Gamma.
\]
Then for every \(\gamma\in\Gamma\) and \(s\in\Sigma\),
\[
\operatorname{Rep}^{\Sigma}_\lambda(\gamma\cdot s)
=
\operatorname{Rep}^{\Sigma}_\lambda(s).
\]
Consequently every physical observable \(M:\Sigma/\Gamma\to Y\) has the same repaired value on
gauge-equivalent representatives.
\end{corollary}

\begin{proof}
The quotient map satisfies \(q(\gamma\cdot s)=q(s)\).  Applying \(\operatorname{Rep}_\lambda\)
gives the displayed equality, and applying \(M\) gives the observable statement.
\end{proof}

On the fixed-cutoff quantum lift, the same quotient-local carrier does more than fix the terminal
orbit: for every declared fixed-cutoff physical algebra, the terminal expectation functional is
the same on any two representative lifts whose regional collar data lie in one quotient-local
glued state, even when the microscopic representatives differ by gauge or sector relabelings on
that carrier.

\begin{theorem}[Refinement-limit consensus classes]\label{thm:consensusrefinement}
Let \(R\) be a directed cofinal refinement set. For each \(r\in R\), let
\(Q_r=\Sigma_r/\Gamma_r\) be the finite physical quotient state space, let
\(n_r:Q_r\to Q_r\) be the finite quotient normal-form map, and let
\(h_r:Q_r\to\mathcal H_r\) be the finite holonomy or higher-gauge obstruction map. Suppose that
for \(r\preceq s\) there are restriction maps
\[
\rho_{sr}:Q_s\to Q_r,\qquad \chi_{sr}:\mathcal H_s\to\mathcal H_r
\]
forming directed inverse systems and satisfying
\[
\rho_{sr}n_s=n_r\rho_{sr},
\qquad
\chi_{sr}h_s=h_r\rho_{sr}.
\]
Assume visible separation: compatible families in the inverse limits are equal whenever they
agree on a cofinal subset of finite stages. Then
\[
n_\infty((x_r)_r)=(n_r(x_r))_r,
\qquad
h_\infty((x_r)_r)=(h_r(x_r))_r
\]
define a unique schedule-independent refinement-limit normal-form class and a refinement-limit
holonomy class. The finite normal forms and holonomies converge to those classes in the
inverse-limit topology. A nonzero limiting holonomy has a finite-stage witness, and agreement of
the normal-form and holonomy projections on a cofinal tail gives the same refinement-limit
consensus class.
\end{theorem}

\begin{proof}
Compatibility of the \(x_r\) gives \(\rho_{sr}(x_s)=x_r\). Normal-form naturality then gives
\[
\rho_{sr}(n_s(x_s))=n_r(\rho_{sr}(x_s))=n_r(x_r),
\]
so the normal forms form a compatible inverse-limit family. Holonomy naturality gives the same
calculation for \(h_s(x_s)\). Finite-stage schedule independence comes from
Theorem~\ref{thm:confluence}; visible separation upgrades agreement of all cofinal finite
projections to uniqueness of the inverse-limit class. A nonzero inverse-limit holonomy must have
a nonzero projection at some finite stage by visible separation.
\end{proof}

\begin{proposition}[Coarse-graining / reconciliation compatibility]\label{prop:consensuscoarse}
Let \(r\preceq s\) be two refinement stages in the D1 consensus system, with coarse-graining
maps
\[
\rho_{sr}:Q_s\to Q_r,\qquad \chi_{sr}:\mathcal H_s\to\mathcal H_r.
\]
Equip \(Q_r\) and \(\mathcal H_r\) with the pseudometrics used for macroscopic readout at stage
\(r\). If the chosen coarse-graining channel has normal-form and obstruction defects
\(\varepsilon^n_{sr}\) and \(\varepsilon^h_{sr}\), meaning
\[
d^Q_r(\rho_{sr}n_s(x),n_r\rho_{sr}(x))\le\varepsilon^n_{sr},
\qquad
d^{\mathcal H}_r(\chi_{sr}h_s(x),h_r\rho_{sr}(x))\le\varepsilon^h_{sr}
\]
for every \(x\in Q_s\), then reconciling at stage \(s\) and coarse-graining to \(r\) gives the
same macroscopic normal-form and obstruction readout as coarse-graining first and reconciling at
\(r\), up to
\[
\max\{\varepsilon^n_{sr},\varepsilon^h_{sr}\}.
\]
In the exact separated cofinal system of Theorem~\ref{thm:consensusrefinement}, these defects are
zero. If the defects vanish on cofinal tails, the two procedures define the same macroscopic
inverse-limit consensus class.
\end{proposition}

\begin{proof}
The displayed inequalities are exactly the two components of the claimed product-readout bound.
Exact naturality in Theorem~\ref{thm:consensusrefinement} is the zero-defect case. Cofinal
vanishing gives convergence of every fixed coarse cylinder value in the inverse-limit topology.
\end{proof}

This removes the extra gauge-covariance axiom and keeps repair on its actual quotient-local
carrier: recovery dynamics on fixed-cutoff collars. On the declared fixed-cutoff branch, the
theorem-local branch condition is repair completeness, together with the Petz support/CPTP clause
where that branch is used. The touched-overlap local-fit contract supplies Lyapunov
\(\Phi\)-descent on accepted moves, and the support-local commutation and union-collar
compatibility package belongs to the declared repair law itself. Stability of that package under
refinement or branch change is handled by the compatibility clauses of
Theorem~\ref{thm:consensusrefinement} when a separated cofinal refinement system is supplied.
Proposition~\ref{prop:consensuscoarse} is the corresponding RG-facing statement: it does not say
that arbitrary coarse-graining maps commute with repair, only that the selected coarse-graining
branch commutes with reconciliation to the extent that the displayed defects are controlled.

\begin{definition}[Quotient-visible neutral geometry certificate]\label{def:neutral-quotient-geometry-certificate}
For each shard \(s\), let \(\Sigma_s\) be the raw record space and let \(\Gamma_s\) be the
presentation groupoid generated by declared gauge-representative changes, local port relabelings,
and other nonphysical presentation moves. Write
\[
q_s:\Sigma_s\to \overline Q_s:=\Sigma_s/\Gamma_s,
\qquad
X_s:=n_s(\overline Q_s)
\]
for the terminal visible chart obtained by applying the schedule-independent normal-form map.
Geometry is read only on the \(X_s\), never from raw rows or intermediate repair states.

A neutral-bulk atlas consists of interface domains \(U_{st}\subseteq X_s\), \(U_{ts}\subseteq
X_t\), and bijections
\[
\tau_{ts}:U_{st}\to U_{ts}
\]
with \(\tau_{ss}=\mathrm{id}\), \(\tau_{st}=\tau_{ts}^{-1}\), and
\(\tau_{us}=\tau_{ut}\tau_{ts}\) whenever the composite is defined. On graph-shaped shard
systems the certificate also records zero closed-path holonomy. A channel registry
\(\mathcal C\) assigns to each channel \(c\) a metric space \((Z_c,d_c)\), a weight \(w_c>0\),
and local features \(F_{s,c}:D_{s,c}\subseteq X_s\to Z_c\). The channel is quotient-visible when
domain membership and values are transported by \(\tau\):
\[
x\in D_{s,c}\Longleftrightarrow \tau_{ts}x\in D_{t,c},
\qquad
F_{t,c}(\tau_{ts}x)=F_{s,c}(x).
\]
Approximate certificates replace the last equality by a reported channel defect
\(\eta_{ts,c}\). The evidence bundle must report the corresponding path-sum transport bound.
\end{definition}

\begin{theorem}[Quotient chart descent and neutral metric]\label{thm:neutral-quotient-metric}
Assume the atlas laws of Definition~\ref{def:neutral-quotient-geometry-certificate}. Let
\[
Q_{\mathrm{vis}}
:=
\left(\bigsqcup_s X_s\right)\big/\sim_\tau
\]
where \(x\sim_\tau y\) when an admissible interface path transports \(x\) to \(y\). Then
\(\sim_\tau\) is an equivalence relation, the canonical maps
\(\iota_s:X_s\to Q_{\mathrm{vis}}\) satisfy
\(\iota_t\tau_{ts}=\iota_s\), and zero closed-path holonomy makes each \(\iota_s\) injective.
Every compatible family of maps \(G_s:X_s\to Y\) factors uniquely through
\(Q_{\mathrm{vis}}\).

In particular, each quotient-visible feature \(F_{s,c}\) descends to a unique partial feature
\[
F_c:Q_{\mathrm{vis}}\dashrightarrow Z_c .
\]
For a declared complete geometry channel set \(\mathcal C_\star\), let
\[
Q_\star=\{x\in Q_{\mathrm{vis}}:F_c(x)\ \hbox{exists for all }c\in\mathcal C_\star\}
\]
and, for \(p\ge 1\), define
\[
d_{\mathrm{neu}}(x,y)
=
\left[
\sum_{c\in\mathcal C_\star}
w_c\,d_c(F_c(x),F_c(y))^p
\right]^{1/p}.
\]
Then \(d_{\mathrm{neu}}\) is independent of shard representative and is a pseudometric on
\(Q_\star\). It is a metric on \(Q_\star/\!\equiv_F\), where \(x\equiv_F y\) means all declared
channels agree, and it is a metric directly on \(Q_\star\) only if those channels jointly
separate points.
\end{theorem}

\begin{proof}
Reflexivity, symmetry, and transitivity of \(\sim_\tau\) follow from the identity, inverse, and
composition atlas laws. The canonical-map identity is the definition of the generated quotient.
If \(\iota_s(x)=\iota_s(y)\), then \(y\) is obtained from \(x\) by a closed path; zero holonomy
gives \(x=y\). The universal property follows by defining \(G([x])=G_s(x)\) and using interface
compatibility along a connecting path. Applying this channel by channel gives feature descent.
The metric formula is well defined by that descent. Nonnegativity and symmetry are channelwise,
and the triangle inequality is Minkowski's inequality applied to the weighted channel distances.
Zero distance is exactly \(\equiv_F\); quotienting by that relation, or proving joint separation,
supplies identity of indiscernibles.
\end{proof}

\begin{remark}[Missingness and presentation invariance]\label{rem:neutral-missingness-invariance}
Pairwise ``compare whatever channels overlap'' is not a metric policy: three points can satisfy
\(d(A,B)=0\), \(d(B,C)=0\), and \(d(A,C)>0\) when each pair shares a different channel. OPH
therefore permits only complete-case comparison, a fixed missing symbol whose mask is itself
quotient-visible, or a train-only imputation map labelled as a metric on imputed
representations. Gauge changes, port relabelings, observer-row permutations, repair schedules,
and shard partitions preserve the neutral metric only when they induce a bijection
\(\Theta\) on \(Q_{\mathrm{vis}}\) and channel isometries \(I_c\) with
\[
F'_c(\Theta x)=I_c(F_c(x)).
\]
Then the displayed product formula gives \(d'(\Theta x,\Theta y)=d(x,y)\). A common-refinement
proof of partition neutrality is the same statement with \(\Theta\) induced by equal fibers over
the refinement. A refinement-limit neutral metric additionally requires a cofinally vanishing
tail modulus for the finite-stage distances; it is not automatic from running more cells.
\end{remark}

\begin{proposition}[Finite Euclidean and batch-held-out certificates]\label{prop:neutral-euclidean-stat-cert}
For a finite sample with distance matrix \(D\), set
\[
H=I-\frac1n\mathbf 1\mathbf 1^\top,\qquad
B=-\frac12H(D^{\circ2})H .
\]
The sampled metric is exactly Euclidean iff \(B\succeq0\), and the smallest exact Euclidean
dimension is \(\operatorname{rank}(B)\). Noisy Euclidean claims must report negative-eigenvalue
mass, positive/effective rank, and held-out stress; a low-dimensional plot is not a certificate.

Statistical claims split independent generative batches before preprocessing:
\[
\mathcal B_{\mathrm{train}}\sqcup\mathcal B_{\mathrm{val}}\sqcup\mathcal B_{\mathrm{test}}.
\]
All chart alignment, scaling, channel weights, imputation, graph construction, dimension
selection, and thresholds are fitted on train/validation data only. If a bounded batch-level test
loss \(\ell(\widehat\theta;B)\in[0,1]\) is evaluated once on independent test batches, then,
conditioning on training and validation,
\[
\left|
\widehat R_{\mathrm{test}}-R(\widehat\theta)
\right|
\le
\sqrt{\frac{\log(2/\delta)}{2m_{\mathrm{test}}}}
\]
with probability at least \(1-\delta\). Shared seeds, shard batches, boundary conditions,
trajectory families, duplicates, descendants, or repeated test-set inspection block this
certificate.
\end{proposition}

\begin{definition}[Ancilla stabilization]\label{def:ancillastab}
Fix a finite-cutoff OPH realization
\[
\mathfrak U=
\bigl(\{\mathcal H_P,\mathcal A(P),\omega_P\}_{P\in\mathcal P},\,\Gamma,\,T^\lambda\bigr).
\]
Choose finite-dimensional ancillary factors \(K_P\) with product state \(\eta=\bigotimes_{P\in\mathcal P}\eta_P\). The associated ancilla stabilization is the realization
\[
\mathfrak U^\eta=
\bigl(\{\mathcal H_P^\eta,\mathcal A^\eta(P),\omega_P^\eta\}_{P\in\mathcal P},\,\Gamma,\,(T^\lambda)^\eta\bigr),
\]
with
\[
\mathcal H_P^\eta:=\mathcal H_P\otimes K_P,\qquad
\mathcal A^\eta(P):=\mathcal A(P)\otimes \mathbf 1_{K_P},\qquad
\omega_P^\eta:=\omega_P\otimes \eta_P,
\]
and lifted repair dynamics acting trivially on the ancillas.
\end{definition}

\begin{proposition}[Ancilla-stable UV underdetermination]\label{prop:ancillauv}
Let \(\mathfrak U^\eta\) be an ancilla stabilization of a finite-cutoff OPH realization \(\mathfrak U\). Then:
\begin{enumerate}[leftmargin=2em]
\item observable expectations on the physical subalgebras are unchanged:
\[
\omega_P^\eta(a\otimes \mathbf 1_{K_P})=\omega_P(a)
\qquad
\forall\, a\in\mathcal A(P);
\]
\item the interacting local MaxEnt branch on the physical subalgebra is unchanged, since
\[
\omega_{\ell_{\mathrm{UV}}}^\eta(\lambda)=\omega_{\ell_{\mathrm{UV}}}(\lambda)\otimes \eta;
\]
\item for every collar split \(A:B:D\),
\[
I(A:D\mid B)_{\rho\otimes \eta}=I(A:D\mid B)_\rho,
\]
so the Fawzi--Renner remainder \(r_{\mathrm{FR}}(\varepsilon)\) and the collar Markov modulus \(\delta^{\mathrm M}_{A:B:D}(\varepsilon)\) are unchanged;
\item if the ancillas are inert under repair, then they remain hidden representative data and the
quotient normal form on physical observables is identical:
\[
N_{Q^\eta}\!\left(q^\eta_{\mathrm{phys}}(s\otimes k)\right)
=
N_Q\!\left(q_{\mathrm{phys}}(s)\right);
\]
\item if the ancillas carry only trivial neutral sectors, the MAR-selected realized sector package is unchanged.
\end{enumerate}
Hence \(\mathfrak U\) and \(\mathfrak U^\eta\) are OPH-indistinguishable although they are different microscopic regulator realizations.
\end{proposition}

\begin{proof}
Item 1 is immediate from the definition of \(\mathcal A^\eta(P)\) and \(\omega_P^\eta\). Item 2 is the product-state form of the same fixed-cutoff MaxEnt branch. Item 3 follows from additivity of entropy for product ancillas, which cancels in the conditional mutual-information combination and therefore leaves both \(r_{\mathrm{FR}}\) and \(\delta^{\mathrm M}\) unchanged. Item 4 holds because the lifted repair maps do not act on the ancillary factors. Item 5 is immediate when the ancillas are neutral and carry no extra realized sector data.
\end{proof}

\begin{definition}[OPH-stable UV equivalence]\label{def:ophuveq}
Two finite-cutoff realizations \(\mathfrak U\) and \(\mathfrak U'\) are \emph{OPH-stably equivalent}, written
\[
\mathfrak U\sim_{\mathrm{OPH}}\mathfrak U',
\]
if after finite ancilla stabilizations they are related by local gauge-covariant \(^*\)-isomorphisms intertwining the observable patch net, overlap maps, local states, and repair dynamics on the physical subalgebras.
\end{definition}

\begin{corollary}[Unique physical UV branch only modulo OPH-stable equivalence]\label{cor:ophuveq}
Under the OPH axiom language, the UV invariant determined by the theory is the class \([\mathfrak U]_{\mathrm{OPH}}\), not a unique microscopic regulator presentation. Literal microscopic UV uniqueness is therefore not an OPH invariant.
\end{corollary}

\begin{proof}
Propositions~\ref{prop:repairquot} and \ref{prop:gauge} fix the schedule-independent physical
branch on the quotient, while Proposition~\ref{prop:ancillauv} shows that inert ancillary
refinements leave every OPH observable invariant. So the physical branch is fixed only modulo
\(\sim_{\mathrm{OPH}}\), not at the level of one microscopic representative.
\end{proof}

These three results encode much of the eventual physical interpretation. Objectivity becomes
confluence, gauge symmetry becomes quotient invariance induced by the physical overlap algebra, and
stable defects are represented by nontrivial overlap holonomy classes. The physically relevant
uniqueness statement is therefore quotient uniqueness together with ancilla-stable equivalence: OPH
fixes a unique gauge-invariant physical branch modulo boundary redundancy, implementation hiding,
and inert ancillary stabilization, not a unique microscopic regulator presentation.

\section{Collars, Edge Centers, and Generalized Entropy}

The fixed-point picture explains why overlap consistency produces gauge quotients: once repair is
read on the physical overlap algebra, descent to the quotient is automatic. The gravity and
consensus arguments later use a more specific collar fact: after edge-center completion, interior
observables become insensitive to compatible exterior substitutions, and modular additivity becomes
exact in the Markov normal form. The point of this section is therefore twofold. First, at fixed
regulator scale, we derive the collar block decomposition from overlap consistency itself on the
ordinary or central-defect branch and then state its genuinely noncentral higher-gauge replacement.
Second, we state precisely when the approximate recoverability clause of Axiom~\ref{ax:entropy} is
allowed to converge to the exact HJPW normal form used by the later spatial and null collar
theorems.

The sharp claim boundary is as follows. Small conditional mutual information always gives a constructive recovered comparison state with \(O(\varepsilon^{1/2})\) observable error. It does \emph{not} by itself give a universal one-shot trace-norm bound to an exact Markov state. The exact Markov normal form is recovered either when \(I(A:D\mid B)=0\) holds literally, or for a controlled family on one fixed finite-dimensional collar model, or after pullback to such a model, where \(\varepsilon\to0\). On that fixed collar one gets a collar-dependent modulus \(\delta^{\mathrm M}_{A:B:D}(\varepsilon)\to0\) measuring distance to the exact Markov set, and this is the error that must be carried into later exact splice or modular-additivity identities. A separate boundary, independent of any modulus, is that the HJPW normal form factorizes the state over a \emph{state-dependent} decomposition of the middle system: identifying its factors with the preselected edge-center factors \(b_L^\alpha,b_R^\alpha\) is the Markov-split alignment hypothesis (Definition~\ref{def:ecaligned}), which exact Markovity does not imply (Remark~\ref{rem:hjpwalignment}) and which is carried explicitly wherever the preselected factors are used. On the declared central-interface branch both alignment and exact collar Markovianity are derived rather than assumed (Theorem~\ref{thm:msaderivation}).

The quantitative route off that exact branch needs a stronger premise than ordinary covariance
clustering. The definitions below isolate the premise, keep all constants visible, and separate the
finite receipt from the scaling statement.

\begin{definition}[Finite-range collar Gibbs family]\label{def:finite-range-collar-gibbs}
At regulator scale \(\ell>0\), let \(G_\ell=(V_\ell,E_\ell)\) be the cell-adjacency graph,
with \(\dim\mathcal H_x\le q\) and interaction degree at most \(\Delta_0\). In each fixed
superselection sector, let
\[
 \rho_\ell=Z_\ell^{-1}e^{-\beta H_\ell},
 \qquad
 H_\ell=\sum_{X\subset V_\ell}\Phi_\ell(X)+H_\ell^{\mathrm{cen}},
\]
where \(H_\ell^{\mathrm{cen}}\) is central and therefore scalar on the chosen sector. Assume
constants \(r_0,J_0<\infty\), independent of the cut and of \(\ell\), such that
\[
 \operatorname{diam}_{G_\ell}(X)\le r_0,
 \qquad
 \sup_{x\in V_\ell}\sum_{X\ni x}\|\beta\Phi_\ell(X)\|\le J_0.
\]
A noncentral all-to-all constraint term fails this finite-range premise; it cannot be hidden in
\(H_\ell^{\mathrm{cen}}\).

For a cut \(C_\ell\subset V_\ell\), let
\[
 \partial_{r_0}^{\mathrm{UV}}C_\ell
 :=\{x\in V_\ell:
 d_{G_\ell}(x,C_\ell)\le r_0,
 d_{G_\ell}(x,C_\ell^c)\le r_0\},
 \qquad
 |\partial C_\ell|_{\mathrm{UV}}
 :=|\partial_{r_0}^{\mathrm{UV}}C_\ell|.
\]
Let \(A_\delta:B_\delta:D_\delta\) be a tripartition in which \(B_\delta\) shields
\(A_\delta\subset C_\ell\) from \(D_\delta\subset C_\ell^c\) by
\(m_\ell\) graph layers, with \(m_\ell>r_0\), and define the resolved physical
collar width by \(\delta:=m_\ell\ell\).
\end{definition}

\begin{definition}[Strong conditional Gibbs exponential mixing]\label{def:strong-conditional-gibbs-mixing}
For the faithful Gibbs state of Definition~\ref{def:finite-range-collar-gibbs}, embed all marginal
logarithms in the tripartite algebra and define the matrix conditional log-density defect
\[
 \mathbf J_\rho(A:D\mid B)
 :=
 \log\rho_{ABD}+\log\rho_B-\log\rho_{AB}-\log\rho_{BD}.
\]
The family has strong conditional Gibbs exponential mixing with constants
\(\kappa<\infty\) and \(\zeta>0\) when, for every admitted cut and collar, it has a boundary-anchor
expansion
\[
 \mathbf J_\rho(A_\delta:D_\delta\mid B_\delta)
 =\sum_{z\in\partial_{r_0}^{\mathrm{UV}}C_\ell}E_{z,\ell,\delta},
 \qquad
 \|E_{z,\ell,\delta}\|_\infty
 \le
 \kappa e^{-(m_\ell-r_0)/\zeta}.
\]
The constants are uniform in \(\ell\), the cut, the boundary condition, and the collar in the
declared family. This is a conditional or matrix mixing condition. A two-point estimate of the
form
\[
 |\omega(XY)-\omega(X)\omega(Y)|
 \le K\|X\|\|Y\|e^{-d(\operatorname{supp}X,\operatorname{supp}Y)/\zeta}
\]
does not imply Definition~\ref{def:strong-conditional-gibbs-mixing} for a general noncommuting
Gibbs state. Local Gibbs form and ordinary exponential clustering therefore cannot discharge this
premise by themselves.
\end{definition}

\begin{theorem}[Collar CMI decay from finite-range conditional Gibbs mixing]
\label{thm:collar-cmi-decay}
Under Definitions~\ref{def:finite-range-collar-gibbs} and
\ref{def:strong-conditional-gibbs-mixing},
\[
 \boxed{
 I(A_\delta:D_\delta\mid B_\delta)_{\rho_\ell}
 \le
 \kappa |\partial C_\ell|_{\mathrm{UV}}
 e^{-(m_\ell-r_0)/\zeta}
 \le
 c |\partial C_\ell|_{\mathrm{UV}}e^{-\delta/\xi_\ell}}
\]
with the explicit choices
\[
 \xi_\ell:=\zeta\ell,
 \qquad
 c:=\kappa e^{r_0/\zeta}.
\]
Thus \(c\) and \(\xi_\ell/\ell\) depend only on the declared uniform mixing constants and the
finite interaction range; \(q,\Delta_0,J_0,\beta\) enter only through an independently proved or
received pair \((\kappa,\zeta)\).
\end{theorem}

\begin{proof}
Every finite Gibbs state is faithful, and so are its marginals. Expanding the four entropy terms
inside the common tripartite trace gives the exact identity
\[
 I(A:D\mid B)_\rho
 =\operatorname{Tr}\!\left[\rho_{ABD}\,
 \mathbf J_\rho(A:D\mid B)\right].
\]
Strong subadditivity gives nonnegativity. The boundary expansion, trace-norm duality, and the
triangle inequality give
\[
 I(A_\delta:D_\delta\mid B_\delta)_{\rho_\ell}
 \le
 \|\mathbf J_{\rho_\ell}(A_\delta:D_\delta\mid B_\delta)\|_\infty
 \le
 \kappa |\partial C_\ell|_{\mathrm{UV}}
 e^{-(m_\ell-r_0)/\zeta}.
\]
Since \(\delta=m_\ell\ell\), the last expression equals
\(\kappa e^{r_0/\zeta}|\partial C_\ell|_{\mathrm{UV}}
e^{-\delta/(\zeta\ell)}\), which is the displayed bound.
\end{proof}

\begin{corollary}[Sharp double scaling and recovery error]\label{cor:collar-cmi-double-scaling}
Let \(\ell_n\downarrow0\) and \(\delta_n\downarrow0\) lie in one family with the uniform constants
of Theorem~\ref{thm:collar-cmi-decay}. Then
\[
 \Gamma_n
 :=\frac{\delta_n}{\xi_{\ell_n}}
 -\log|\partial C_{\ell_n}|_{\mathrm{UV}}
 \longrightarrow+\infty
 \quad\Longrightarrow\quad
 I(A_{\delta_n}:D_{\delta_n}\mid B_{\delta_n})\longrightarrow0.
\]
If, for constants \(a,p,\ell_0>0\),
\[
 |\partial C_\ell|_{\mathrm{UV}}
 \le a(\ell_0/\ell)^p,
 \qquad
 \delta(\ell)\ge
 \zeta(p+\eta)\ell\log(\ell_0/\ell)
 \quad(\eta>0),
\]
then \(\delta(\ell)\to0\), \(\delta(\ell)/\ell\to\infty\), and
\[
 I(A_\delta:D_\delta\mid B_\delta)
 \le ca(\ell/\ell_0)^\eta\longrightarrow0.
\]
For a smooth cut on the two-dimensional screen, \(p=1\). The Fawzi--Renner map may be chosen with
the certified trace-distance error
\[
 r_{\mathrm{FR}}(\ell,\delta)
 \le 2\sqrt{1-e^{-\varepsilon_{\ell,\delta}}}
 \le2\sqrt{\varepsilon_{\ell,\delta}},
 \qquad
 \varepsilon_{\ell,\delta}:=
 c|\partial C_\ell|_{\mathrm{UV}}e^{-\delta/\xi_\ell}.
\]
\end{corollary}

\begin{proof}
Taking logarithms of the theorem bound gives
\[
 \log I\le\log c+\log|\partial C_\ell|_{\mathrm{UV}}-\delta/\xi_\ell
 =\log c-\Gamma.
\]
This tends to \(-\infty\) under the first condition. The polynomial boundary estimate and the
displayed schedule give \(\Gamma\ge\eta\log(\ell_0/\ell)-\log a\), which proves the explicit rate.
The recovery estimate is Proposition~\ref{prop:approxrecover} applied with the theorem envelope.
\end{proof}

\begin{remark}[The ratio \(\delta/\ell\to\infty\) is not the rate condition]
\label{rem:collar-slow-double-scaling}
The bare double-scaling ratio does not force the boundary-prefactored bound to vanish. Set
\(\ell_n=\ell_0e^{-n^2}\), \(\delta_n=\zeta n\ell_n\), and
\(|\partial C_{\ell_n}|_{\mathrm{UV}}=e^{n^2}\). Then
\(\ell_n,\delta_n\to0\) and \(\delta_n/\ell_n=\zeta n\to\infty\), while the theorem envelope is
proportional to \(e^{n^2-n}\). The condition in Corollary~\ref{cor:collar-cmi-double-scaling}, or
direct verification of the complete product, is load-bearing.
\end{remark}

\begin{definition}[Finite collar-decay receipt]\label{def:finite-collar-decay-receipt}
A theorem-aligned finite-stage receipt records
\begin{enumerate}[label=\textup{R\arabic*.},leftmargin=2.4em]
\item the regulator graph hash, local dimensions, \(\beta\), interaction supports and norms,
      \(r_0,J_0,\Delta_0\), Gibbs reconstruction residual, and the treatment of central sector terms;
\item the tripartition hash, graph-layer or geodesic collar width, \(\ell\),
      \(|\partial C|_{\mathrm{UV}}\), and the separator check \(m_\ell>r_0\);
\item direct regional entropies and CMI in nats, their numerical error bound and spectral floor,
      together with the matrix defect norm and the boundary-expansion tail where it is computed;
\item predeclared \(\kappa,\zeta\), boundary-condition and held-out-cut coverage, the log envelope
\[
 L_{\ell,\delta}
 :=\log\kappa+\log|\partial C|_{\mathrm{UV}}
   -(m_\ell-r_0)/\zeta,
\]
      its slack against the measured upper error bar, and the Fawzi--Renner trace-error envelope;
\item on a tower, one common cap and interaction family, uniform constants, and the rate margin
      \(\Gamma=\delta/(\zeta\ell)-\log|\partial C|_{\mathrm{UV}}\).
\end{enumerate}
A fitted correlation length from the same CMI rows is diagnostic. A finite list of increasing
rate margins is a scaling proxy. The cofinal conclusion requires an analytic schedule such as the
one in Corollary~\ref{cor:collar-cmi-double-scaling}, or an independent uniform proof; no finite
sample proves a limit. A local random-triplet or diagonal packet CMI is likewise diagnostic and
does not substitute for the regional density-matrix receipt.
\end{definition}

\begin{remark}[Claim status of the collar theorem]\label{rem:collar-cmi-claim-status}
On the declared central-interface branch, Theorem~\ref{thm:msaderivation} gives
\(I(A:D\mid B)=0\) exactly. On a general noncommuting finite-range branch,
Theorem~\ref{thm:collar-cmi-decay} is conditional on the strong matrix mixing premise of
Definition~\ref{def:strong-conditional-gibbs-mixing}. It proves recoverability with constants and
the sharp scaling schedule; it does not derive strong conditional mixing from bare finite OPH
consensus, ordinary two-point clustering, or local Gibbs form. The scalar CMI and its recovery
error are not promoted to a rank-two stress tensor or a dark-sector source.
\end{remark}

\begin{proposition}[Derived regulator gluing datum]\label{prop:regulatedrealization}
Fix a regulator-scale finite patch cover of a cap neighborhood and let \(R\) be any finite union of regulator cells. Assume only the finite patch-net presentation implicit in Definition~\ref{def:patchnet} together with overlap consistency on common interfaces. Then:
\begin{enumerate}[leftmargin=2em]
\item each regulator cell \(i\) with finite local state space \(S_i\) can be Hilbertized as \(\tilde{\mathcal H}_i\cong \mathbb C^{|S_i|}\), so the extended algebra before overlap quotienting is the finite type-I algebra
\[
\widetilde{\mathcal A}(R)=\mathcal B(\tilde{\mathcal H}_R),
\qquad
\tilde{\mathcal H}_R:=\bigotimes_{i\subset R}\tilde{\mathcal H}_i;
\]
\item for each connected boundary component \(\Sigma\subset\partial R\), after choosing a reference cut presentation \(\tilde{\mathcal H}_\Sigma\), every overlap-consistent change of local chart along \(\Sigma\) is implemented by a unitary on \(\tilde{\mathcal H}_\Sigma\), and the compact closure of the subgroup generated by all such recharting unitaries is a compact boundary redundancy group
\[
K_\Sigma\subset U(\tilde{\mathcal H}_\Sigma);
\]
before the choice of reference chart, the same data form a compact unitary groupoid of overlap-preserving transitions;
\item if triple-overlap defects are central, the projective composition law of item 2 lifts to a direct action of a compact central extension \(\widehat K_\Sigma\); a genuinely noncentral defect is the only obstruction to reducing the transition system to an ordinary compact group action;
\item in the invariant-state realization of the quotient, the chart-independent endomorphisms of the lifted presentation form the boundary-invariant algebra
\[
\mathcal A_{\mathrm{inv}}(R)=\widetilde{\mathcal A}(R)^{\widehat K_{\partial R}},
\qquad
\widehat K_{\partial R}:=\prod_{\Sigma\subset\partial R}\widehat K_\Sigma,
\]
\noindent with the convention \(\widehat K_\Sigma=K_\Sigma\) whenever no central extension is needed; the physical state space is the corresponding invariant subspace, and on collars the sector-preserving algebra induced on that subspace is the block-diagonal algebra used in Theorem~\ref{thm:markovcollar}.
\end{enumerate}
Items 1 and the lifted fixed-point presentation of item 4 are the fixed-cutoff realized data used by the compact-gauge branch; they are not extra axioms beyond the finite regulator presentation plus overlap redundancy.
\end{proposition}

\begin{proof}[Proof sketch]
Item 1 is the Hilbertization of finite sets. For item 2, each overlap-consistent recharting acts on a finite-dimensional matrix algebra, and every \(^*\)-automorphism of such an algebra is inner. After transporting all local overlap presentations to a chosen reference chart, each recharting is therefore implemented by a unitary on the cut Hilbert space. The subgroup generated by those unitaries has compact closure inside a finite-dimensional unitary group, which yields \(K_\Sigma\); without fixing the reference chart one has the corresponding compact unitary groupoid. Item 3 is the usual projective-versus-central-extension lift for a central 2-cocycle. Item 4 records the lifted fixed-point presentation: chart-independent endomorphisms of the unreduced boundary data are exactly the fixed points of the derived boundary action, while the collar theorem uses the invariant-state realization and the sector-preserving algebra induced on the matched-cut subspace. If the defect is genuinely noncentral, the quotient is well defined, but the correct bookkeeping object is the crossed-module or higher-gauge data instead of an ordinary compact group.
\end{proof}

\begin{theorem}[Derived edge-center collar decomposition and exact Markov normal form]\label{thm:markovcollar}
Let \(A\)-\(B\)-\(D\) be a collar tripartition realized at fixed regulator scale on the ordinary or central-defect branch of Proposition~\ref{prop:regulatedrealization}. Write \(B=B_L\cup B_R\) with common interface \(\Sigma=\partial C\), and let \(\widehat K_\Sigma\) be the derived compact boundary action attached to that cut, with \(\widehat K_\Sigma=K_\Sigma\) on the ordinary branch. In the invariant-state realization,
\[
\mathcal H_B=(\tilde{\mathcal H}_{B_L}\otimes \tilde{\mathcal H}_{B_R})^{\widehat K_\Sigma}.
\]
Decompose the left boundary data as
\[
\tilde{\mathcal H}_{B_L}\cong \bigoplus_\alpha W_\alpha\otimes \mathcal H_{b_L^\alpha},
\]
with \(W_\alpha\) irreducible \(\widehat K_\Sigma\)-modules. Because the right half-collar carries the inverse overlap transport across the same cut, it decomposes contragrediently:
\[
\tilde{\mathcal H}_{B_R}\cong \bigoplus_\beta W_\beta^*\otimes \mathcal H_{b_R^\beta}.
\]
Then
\[
\mathcal H_B\cong\bigoplus_\alpha \mathcal H_{b_L^\alpha}\otimes \mathcal H_{b_R^\alpha},
\]
and the sector-preserving collar algebra
\[
\mathcal A_{\mathrm{EC}}(B):=\bigoplus_\alpha \mathcal B(\mathcal H_{b_L^\alpha})\otimes \mathcal B(\mathcal H_{b_R^\alpha})
\]
has center
\[
Z(\mathcal A_{\mathrm{EC}}(B))=\bigoplus_\alpha \mathbb C\,\mathbf 1_\alpha.
\]
If, in addition, the reference state on \(A\cup B\cup D\) is exact Markov,
\[
I(A:D|B)_\rho=0,
\]
and satisfies the Markov-split alignment hypothesis of Definition~\ref{def:ecaligned} below, then the state decomposes as
\[
\rho_{ABD}
=
\bigoplus_\alpha p_\alpha\,
\rho^{(\alpha)}_{A b_L^\alpha}\otimes \rho^{(\alpha)}_{b_R^\alpha D}.
\]
The same formula holds in any limit state that is exact Markov and split-aligned on this fixed collar model.
Thus the collar-center block decomposition is forced by overlap consistency plus the derived regulator package on the ordinary or central-defect branch. Exact Markov factorization over the preselected edge factors is an additional state condition comprising exact Markovity and split alignment. Neither part follows from the block decomposition alone. Exact Markovity by itself does not imply alignment (Remark~\ref{rem:hjpwalignment}).
\end{theorem}

\begin{proof}
By Proposition~\ref{prop:regulatedrealization}, one may realize the physical collar states as the \(\widehat K_\Sigma\)-invariant subspace of \(\tilde{\mathcal H}_{B_L}\otimes \tilde{\mathcal H}_{B_R}\). Complete reducibility of finite-dimensional unitary representations gives the displayed decomposition of \(\tilde{\mathcal H}_{B_L}\), and the right half-collar carries the inverse transport law across the same cut, hence the contragredient decomposition of \(\tilde{\mathcal H}_{B_R}\). Therefore
\[
\tilde{\mathcal H}_{B_L}\otimes \tilde{\mathcal H}_{B_R}
\cong
\bigoplus_{\alpha,\beta}
(W_\alpha\otimes W_\beta^*)\otimes
(\mathcal H_{b_L^\alpha}\otimes \mathcal H_{b_R^\beta}).
\]
Taking \(\widehat K_\Sigma\)-invariants gives
\[
\mathcal H_B
\cong
\bigoplus_{\alpha,\beta}
(W_\alpha\otimes W_\beta^*)^{\widehat K_\Sigma}\otimes
(\mathcal H_{b_L^\alpha}\otimes \mathcal H_{b_R^\beta}).
\]
By Schur's lemma,
\[
(W_\alpha\otimes W_\beta^*)^{\widehat K_\Sigma}
\cong
\begin{cases}
\mathbb C, & \alpha=\beta,\\
0, & \alpha\neq \beta,
\end{cases}
\]
which yields the displayed block decomposition. The sector-preserving collar algebra therefore has the displayed block-diagonal form, so its center is generated by the block projectors. Within each block, observables from \(A\cup B\) act only on the left factor and observables from \(B\cup D\) act only on the right factor. If the state is exact Markov, the HJPW structure theorem \cite{hjpw04} gives a blockwise factorized normal form over \emph{some} decomposition \(\mathcal H_B\cong\bigoplus_j \mathcal H_{\hat b_L^j}\otimes\mathcal H_{\hat b_R^j}\) of the conditioning system. That conclusion is existential: the decomposition it produces is state-dependent and need not agree with the preselected edge-center factors \(b_L^\alpha,b_R^\alpha\) constructed above (Remark~\ref{rem:hjpwalignment}). The Markov-split alignment hypothesis of Definition~\ref{def:ecaligned} states exactly that the HJPW decomposition can be chosen to be the edge-center decomposition; under that hypothesis the displayed normal form over \(b_L^\alpha,b_R^\alpha\) follows. The same formula is used in the idealized recoverability limit when exact identities are taken literally, with alignment carried as part of the limit hypothesis.
\end{proof}

\begin{definition}[EC-aligned exact Markov states and the Markov-split alignment hypothesis]\label{def:ecaligned}
Fix one collar model with the edge-center decomposition
\(\mathcal H_B\cong\bigoplus_\alpha \mathcal H_{b_L^\alpha}\otimes \mathcal H_{b_R^\alpha}\)
of Theorem~\ref{thm:markovcollar}. A state \(\sigma_{ABD}\) is \emph{EC-aligned exact Markov} if
\[
\sigma_{ABD}
=
\bigoplus_\alpha q_\alpha\,
\sigma^{(\alpha)}_{A b_L^\alpha}\otimes \sigma^{(\alpha)}_{b_R^\alpha D}
\]
with respect to the preselected edge factors; write \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\) for the set of such states. Every EC-aligned exact Markov state satisfies \(I(A:D\mid B)=0\). A reference state is said to satisfy the \emph{Markov-split alignment hypothesis} (MSA) on this collar model when it lies in \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\); equivalently, when one HJPW decomposition of \(\mathcal H_B\) for the state can be chosen to be the edge-center decomposition itself, with the factor coupled to \(A\) equal to \(b_L^\alpha\) and the factor coupled to \(D\) equal to \(b_R^\alpha\) in every sector. The intended mechanism for verifying MSA in a concrete collar model is a commuting square of state-preserving conditional expectations onto the one-sided edge algebras \(\bigoplus_\alpha \mathcal B(\mathcal H_{b_L^\alpha})\otimes\mathbf 1\) and \(\bigoplus_\alpha \mathbf 1\otimes\mathcal B(\mathcal H_{b_R^\alpha})\); Proposition~\ref{prop:msachar} proves that this mechanism, a modular-splitting condition, and a blockwise entropic condition are all equivalent to MSA, and Theorem~\ref{thm:msaderivation} derives MSA from the regulator package on the declared central-interface branch. Off that branch, wherever an exact identity below uses the preselected factors, MSA is an explicit hypothesis.
\end{definition}

\begin{remark}[Exact Markovity does not imply alignment: a Bell-pair counterexample]\label{rem:hjpwalignment}
The HJPW theorem is existential, and the inclusion \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\subseteq\mathfrak M_{A:B:D}\) into the exact Markov set of Definition~\ref{def:markovmodulus} is strict in general. Take four qubits ordered \(A,B_L,B_R,D\) with a single center block, \(\mathcal H_{b_L}=\mathcal H_{B_L}\), \(\mathcal H_{b_R}=\mathcal H_{B_R}\), and
\[
\rho=\Phi_{A B_R}\otimes\Phi_{B_L D},
\]
where \(\Phi\) denotes a maximally entangled Bell pair. Direct computation gives \(S(AB)=S(BD)=\ln 2\), \(S(B)=2\ln 2\), and \(S(ABD)=0\), hence \(I(A:D\mid B)_\rho=0\): the state is exactly Markov. But \(I(A:B_R)_\rho=2\ln 2\neq 0\), whereas any state of the EC-aligned form \(\rho_{A b_L}\otimes\rho_{b_R D}\) has \(I(A:B_R)=0\). For this state the HJPW decomposition is the transposed split, pairing \(A\) with \(B_R\) and \(D\) with \(B_L\). Consequently no vanishing modulus of the form \(\delta^{\mathrm M}(\varepsilon)\) can control the distance to \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\): this state has \(I(A:D\mid B)=0\) at fixed nonzero trace distance from the EC-aligned class. Small conditional mutual information therefore never implies approximate EC-aligned factorization by itself; alignment must be hypothesized or derived separately.
\end{remark}

The alignment hypothesis is not merely a name: it admits equivalent operational characterizations that make it checkable state by state and localize exactly what an axiom-side derivation must supply. Define the one-sided collar algebras extended by the exterior regions,
\[
\mathcal M_L:=\bigoplus_\alpha \mathcal B(\mathcal H_A\otimes\mathcal H_{b_L^\alpha})\otimes\mathbf 1_{b_R^\alpha D},
\qquad
\mathcal M_R:=\bigoplus_\alpha \mathbf 1_{A b_L^\alpha}\otimes\mathcal B(\mathcal H_{b_R^\alpha}\otimes\mathcal H_D).
\]
Elements of \(\mathcal M_L\) and \(\mathcal M_R\) commute, both algebras contain the center projectors \(P_\alpha\), and \(\mathcal M_L\cap\mathcal M_R=\bigoplus_\alpha\mathbb C\,P_\alpha\).

\begin{proposition}[Operational characterizations of Markov-split alignment]\label{prop:msachar}
Let \(\rho_{ABD}\) be a faithful state on the collar model of Theorem~\ref{thm:markovcollar}. The following are equivalent:
\begin{enumerate}[leftmargin=2em]
\item \(\rho\in\mathfrak M^{\mathrm{EC}}_{A:B:D}\), i.e.\ \(\rho\) satisfies MSA (Definition~\ref{def:ecaligned});
\item \emph{(modular splitting)} \(\log\rho\in\mathcal M_L+\mathcal M_R\);
\item \emph{(conditional expectation / commuting square)} there exists a \(\rho\)-preserving conditional expectation \(E_L:\mathcal B(\mathcal H_{ABD})\to\mathcal M_L\); equivalently, one onto \(\mathcal M_R\); in that case the pair \((E_L,E_R)\) forms a commuting square over the center algebra \(\bigoplus_\alpha\mathbb C\,P_\alpha\);
\item \emph{(entropic)} \([\rho,P_\alpha]=0\) for all \(\alpha\), and \(I(Ab_L^\alpha:b_R^\alpha D)_{\rho^{(\alpha)}}=0\) for every block with \(p_\alpha>0\), where \(\rho^{(\alpha)}:=p_\alpha^{-1}P_\alpha\rho P_\alpha\).
\end{enumerate}
Each condition implies \(I(A:D\mid B)_\rho=0\). Items 1 and 4 are equivalent without faithfulness. The Bell-pair state of Remark~\ref{rem:hjpwalignment} violates item 4, since \(I(Ab_L:b_RD)\ge I(A:B_R)=2\ln2>0\) on its single block, as the general theory requires.
\end{proposition}

\begin{proof}
\(1\Leftrightarrow 4\): mutual information vanishes iff the state is a product across the named cut, so item 4 says precisely that \(\rho\) is block-diagonal with each block a product across \((Ab_L^\alpha):(b_R^\alpha D)\), which is the aligned normal form. No faithfulness is used.

\(1\Rightarrow 2\): for the aligned normal form,
\(\log\rho=\bigoplus_\alpha\bigl[(\log p_\alpha)P_\alpha+\log\rho^{(\alpha)}_{Ab_L^\alpha}\otimes\mathbf 1+\mathbf 1\otimes\log\rho^{(\alpha)}_{b_R^\alpha D}\bigr]\),
and the central term lies in \(\mathcal M_L\cap\mathcal M_R\).

\(2\Rightarrow 1\): write \(\log\rho=K_L+K_R\) with \(K_L\in\mathcal M_L\), \(K_R\in\mathcal M_R\); these commute, are block-diagonal, and have blockwise form \(K_L=h^\alpha_L\otimes\mathbf 1\), \(K_R=\mathbf 1\otimes h^\alpha_R\). Hence \(\rho=\bigoplus_\alpha e^{h^\alpha_L}\otimes e^{h^\alpha_R}\), which after normalization is the aligned form.

\(1\Rightarrow 3\): define the blockwise slice map
\[
E_L(x):=\bigoplus_\alpha\Bigl[\bigl(\mathrm{id}_{Ab_L^\alpha}\otimes\omega^{(\alpha)}_{R}\bigr)(P_\alpha xP_\alpha)\Bigr]\otimes\mathbf 1_{b_R^\alpha D},
\qquad
\omega^{(\alpha)}_{R}:=\mathrm{Tr}\bigl[\;\cdot\;\rho^{(\alpha)}_{b_R^\alpha D}\bigr].
\]
This is a unital completely positive idempotent onto \(\mathcal M_L\) with the bimodule property, and \(\rho\circ E_L=\rho\) follows from the blockwise product form. The analogous \(E_R\) exists, and \(E_LE_R=E_RE_L\) is the expectation onto \(\bigoplus_\alpha\mathbb C\,P_\alpha\) determined by the block weights, which is the asserted commuting square.

\(3\Rightarrow 2\): by Takesaki's theorem \cite{takesaki72} (see also \cite{petz86,petz88}), a \(\rho\)-preserving conditional expectation onto \(\mathcal M_L\) exists iff the modular group \(\sigma^\rho_t=\mathrm{Ad}\,\rho^{it}\) satisfies \(\sigma^\rho_t(\mathcal M_L)=\mathcal M_L\) for all \(t\). The flow \(\sigma^\rho_t\) then permutes the finitely many minimal projectors of \(Z(\mathcal M_L)=\bigoplus_\alpha\mathbb C\,P_\alpha\) and is norm-continuous with \(\sigma^\rho_0=\mathrm{id}\), so it fixes each \(P_\alpha\); hence \([\rho,P_\alpha]=0\) and \(\rho=\bigoplus_\alpha p_\alpha\rho^{(\alpha)}\). Fix a block and regard \(\rho^{(\alpha)}\) as a faithful state on \(\mathcal H_{Ab_L^\alpha}\otimes\mathcal H_{b_R^\alpha D}\). Differentiating \(\sigma^\rho_t(x\otimes\mathbf 1)\in\mathcal B(\mathcal H_{Ab_L^\alpha})\otimes\mathbf 1\) at \(t=0\) gives \([\log\rho^{(\alpha)},\,x\otimes\mathbf 1]\in\mathcal B(\mathcal H_{Ab_L^\alpha})\otimes\mathbf 1\) for every \(x\). Expand \(\log\rho^{(\alpha)}=\sum_i a_i\otimes b_i\) with \(\{b_i\}\) linearly independent and \(b_0=\mathbf 1\); then \([\log\rho^{(\alpha)},x\otimes\mathbf 1]=\sum_i[a_i,x]\otimes b_i\), and membership in \(\mathcal B(\mathcal H_{Ab_L^\alpha})\otimes\mathbf 1\) forces \([a_i,x]=0\) for all \(x\) and all \(i\neq0\). Hence \(a_i\in\mathbb C\mathbf 1\) for \(i\neq0\), so \(\log\rho^{(\alpha)}=a_0\otimes\mathbf 1+\mathbf 1\otimes c\) for some self-adjoint \(c\), which is the blockwise modular splitting; summing blocks gives item 2.

Finally, item 1 implies \(I(A:D\mid B)_\rho=0\) by the direct blockwise computation of Theorem~\ref{thm:markovcollar}, and the Bell-pair state violates item 4 by monotonicity of mutual information under partial trace.
\end{proof}

\begin{corollary}[Axiom-side reduction of the alignment problem]\label{cor:msareduction}
On the local MaxEnt branch the reference state is Gibbs, \(\omega\propto e^{-H_{\mathrm{eff}}}\), and Proposition~\ref{prop:msachar} (item 2) gives: \(\omega\) satisfies MSA on a given collar iff
\[
H_{\mathrm{eff}}=H_L+H_R+H_Z,
\qquad
H_L\in\mathcal M_L,\quad H_R\in\mathcal M_R,\quad H_Z\in\bigoplus_\alpha\mathbb C\,P_\alpha,
\]
i.e.\ iff every coupling between the two half-collars acts through the edge-center sector label. Deriving MSA from the axioms is therefore \emph{equivalent} to proving that overlap-consistent repair forces all cross-cut terms of \(H_{\mathrm{eff}}\) to be central on the declared branch. This holds manifestly in lattice-gauge-type regulators, where the interface energy is a function of the conserved flux through the cut (a central observable), and fails for generic non-central cross-cut couplings, of which the Bell-pair state is the extreme case. Theorem~\ref{thm:msaderivation} below turns this into a derivation of MSA on the declared central-interface branch; off that branch, MSA remains an explicit hypothesis wherever it is used.
\end{corollary}

The reduction of Corollary~\ref{cor:msareduction} can be discharged for a structurally characterized class of regulator packages. The relevant descent computation is representation-theoretic and deserves separate statement.

\begin{lemma}[Descent of one-sided invariants and boundary charges]\label{lem:onesideddescent}
Work in the invariant-state realization of Proposition~\ref{prop:regulatedrealization}, with
\(\tilde{\mathcal H}_{B_L}\cong\bigoplus_\alpha W_\alpha\otimes\mathcal H_{b_L^\alpha}\),
\(\tilde{\mathcal H}_{B_R}\cong\bigoplus_\beta W_\beta^*\otimes\mathcal H_{b_R^\beta}\), and
\(\mathcal H_B=(\tilde{\mathcal H}_{B_L}\otimes\tilde{\mathcal H}_{B_R})^{\widehat K_\Sigma}\cong\bigoplus_\alpha\mathcal H_{b_L^\alpha}\otimes\mathcal H_{b_R^\alpha}\). Then:
\begin{enumerate}[leftmargin=2em]
\item every \(\widehat K_\Sigma\)-invariant operator \(\tilde x_L\) on \(\mathcal H_A\otimes\tilde{\mathcal H}_{B_L}\) has the form \(\bigoplus_\alpha \mathbf 1_{W_\alpha}\otimes x_L^\alpha\) with \(x_L^\alpha\in\mathcal B(\mathcal H_A\otimes\mathcal H_{b_L^\alpha})\); the operator \(\tilde x_L\otimes\mathbf 1\) preserves the invariant subspace and acts on it as \(\bigoplus_\alpha x_L^\alpha\otimes\mathbf 1_{b_R^\alpha D}\in\mathcal M_L\). The mirror statement holds for right-sided invariants and \(\mathcal M_R\);
\item every element \(\tilde z\) of the image \(\pi_L\bigl(Z(C^*(\widehat K_\Sigma))\bigr)\) of the center of the group (\(C^*\)-)algebra under the left boundary action, including every function of the quadratic Casimir of \(\widehat K_\Sigma\) and hence every function of the flux through \(\Sigma\), acts on \(W_\alpha\otimes\mathcal H_{b_L^\alpha}\) as \(\chi_\alpha(\tilde z)\,\mathbf 1\) by the central character \(\chi_\alpha\). It therefore descends on \(\mathcal H_B\) to the central operator \(\bigoplus_\alpha\chi_\alpha(\tilde z)P_\alpha\in\bigoplus_\alpha\mathbb C\,P_\alpha\). For Casimir/flux functions the same central operator is obtained through the right action, because the Casimir eigenvalue agrees on \(W_\alpha\) and its contragredient \(W_\alpha^*\) and the two boundary charges are matched blockwise on the invariant subspace.
\end{enumerate}
\end{lemma}

\begin{proof}
Item 1 is the commutation theorem plus Schur's lemma: the commutant of the unitary action \(\mathbf 1_A\otimes\bigl(\bigoplus_\alpha\pi_\alpha\otimes\mathbf 1_{b_L^\alpha}\bigr)\) is \(\bigoplus_\alpha \mathbf 1_{W_\alpha}\otimes\mathcal B(\mathcal H_A\otimes\mathcal H_{b_L^\alpha})\) (up to the obvious factor reordering), because the \(\pi_\alpha\) are pairwise inequivalent irreducibles, so no cross-isotypic intertwiners exist and within each isotypic component the commutant of \(\pi_\alpha\otimes\mathbf 1\) is \(\mathbf 1_{W_\alpha}\otimes(\text{full multiplicity algebra})\). Tensoring with \(\mathbf 1\) on the right half-collar commutes with the diagonal action, so the invariant subspace is preserved, and on \((W_\alpha\otimes W_\alpha^*)^{\widehat K_\Sigma}\otimes(\mathcal H_{b_L^\alpha}\otimes\mathcal H_{b_R^\alpha})\cong\mathcal H_{b_L^\alpha}\otimes\mathcal H_{b_R^\alpha}\) the induced action is \(x_L^\alpha\otimes\mathbf 1\). Item 2: central elements of the group algebra act in any irreducible \(\pi_\alpha\) by scalars \(\chi_\alpha(\tilde z)\), so the left action descends to \(\bigoplus_\alpha\chi_\alpha(\tilde z)P_\alpha\). For a Casimir/flux function the contragredient module \(W_\alpha^*\) carries the same Casimir eigenvalue as \(W_\alpha\), so on the \(\alpha\)-block of the invariant subspace the right action reduces to multiplication by the same scalar, which is the displayed central operator.
\end{proof}

\begin{theorem}[MSA and exact collar Markovianity on the central-interface branch]\label{thm:msaderivation}
Call a declared regulator package for the collar tripartition \(A\)-\(B\)-\(D\) \emph{central-interface} if its pre-quotient effective Hamiltonian has the interface normal form
\[
\widetilde H_{\mathrm{eff}}
=
\widetilde H_{AL}+\widetilde H_{RD}+\widetilde H_\Sigma,
\]
where \(\widetilde H_{AL}\) is a \(\widehat K_\Sigma\)-invariant self-adjoint operator supported on \(A\cup B_L\), \(\widetilde H_{RD}\) likewise on \(B_R\cup D\), and \(\widetilde H_\Sigma\in\pi_L\bigl(Z(C^*(\widehat K_\Sigma))\bigr)\) is a boundary-charge (flux) function. Then on the physical collar model:
\begin{enumerate}[leftmargin=2em]
\item the quotient effective Hamiltonian satisfies \(H_{\mathrm{eff}}\in\mathcal M_L+\mathcal M_R+\bigoplus_\alpha\mathbb C\,P_\alpha\);
\item every MaxEnt/Gibbs reference state \(\omega\propto e^{-H_{\mathrm{eff}}}\) of the package is EC-aligned exact Markov, \(\omega\in\mathfrak M^{\mathrm{EC}}_{A:B:D}\): the Markov-split alignment hypothesis \emph{holds as a theorem}, and
\item exact collar Markovianity \(I(A:D\mid B)_\omega=0\) is likewise derived rather than assumed.
\end{enumerate}
Lattice-gauge-type regulators are central-interface: their interface energy is a function of the electric flux through \(\Sigma\), which is exactly a central boundary-charge function. The Bell-pair state of Remark~\ref{rem:hjpwalignment} is \emph{not} the Gibbs state of any central-interface package: every such Gibbs state is EC-aligned by item 2, whereas the Bell-pair state has \(I(A:B_R)=2\ln2\) and sits at fixed trace distance from \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\). The counterexample is thus excluded by a checkable structural condition on the regulator, not by fiat.
\end{theorem}

\begin{proof}
By Lemma~\ref{lem:onesideddescent}, \(\widetilde H_{AL}\) descends into \(\mathcal M_L\), \(\widetilde H_{RD}\) into \(\mathcal M_R\), and \(\widetilde H_\Sigma\) into \(\bigoplus_\alpha\mathbb C\,P_\alpha\subset\mathcal M_L\cap\mathcal M_R\), giving item 1. Hence \(\log\omega=-H_{\mathrm{eff}}-\log Z\,\mathbf 1\in\mathcal M_L+\mathcal M_R\), which is item 2 of Proposition~\ref{prop:msachar}, so \(\omega\in\mathfrak M^{\mathrm{EC}}_{A:B:D}\). Item 3 follows because every EC-aligned state is exact Markov (Proposition~\ref{prop:msachar}). For the final claims: the electric interface energy of a lattice-gauge regulator is a function of the quadratic Casimir of the boundary action, hence central by Lemma~\ref{lem:onesideddescent}, item 2. The Bell-pair exclusion is immediate: every Gibbs state of a central-interface package lies in \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\) by item 2 (and is faithful, while the Bell-pair state is pure on \(A\cup B_R\)), whereas every state in \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\) has \(I(A:B_R)=0\) and the Bell-pair state has \(I(A:B_R)=2\ln 2\).
\end{proof}

\begin{remark}[Scope of the derivation]\label{rem:msascope}
Theorem~\ref{thm:msaderivation} discharges the Markov-split alignment hypothesis, and with it exact collar Markovianity, on the declared central-interface branch. Every MSA-conditioned identity in this manuscript, including blockwise modular cancellation, the exact splice, the null-strip four-term relation on inherited splits, and checkpoint factorization, holds unconditionally for the package's MaxEnt reference states on that branch. This manuscript adopts the central-interface normal form as an explicit declared-branch input through the central-interface collar clause stated with Axiom~\ref{ax:maxent}. The exact-Markov chain therefore depends on one named axiom-level clause. Deriving that clause from overlap-consistent repair is work in progress. Outside the declared branch MSA is carried as an explicit hypothesis, with Remark~\ref{rem:hjpwalignment} marking the failure boundary.
\end{remark}

\begin{theorem}[Derived higher-gauge cut datum]\label{thm:hgdatum}
Fix a connected cut \(\Sigma\) and a finite regulator chart \(\{P_i\}_{i\in I_\Sigma}\) meeting along \(\Sigma\), with finite nerve \(N_\Sigma\). On the genuinely noncentral branch, the weak gluing data are implemented by a compact crossed module
\[
\mathbb K_\Sigma=(H_\Sigma\xrightarrow{\partial_\Sigma}G_\Sigma,\triangleright)
\]
together with maps
\[
g_{ij}:P_{ij}\to G_\Sigma,
\qquad
h_{ijk}:P_{ijk}\to H_\Sigma,
\]
obeying
\[
g_{ij}g_{jk}=\partial_\Sigma(h_{ijk})\,g_{ik},
\qquad
h_{jkl}h_{ijl}=(g_{ij}\triangleright h_{ikl})\,h_{ijk}.
\]
The corresponding higher-gauge change system on the cut is the compact semidirect product
\[
\mathcal T_\Sigma:=C^1(N_\Sigma,H_\Sigma)\rtimes C^0(N_\Sigma,G_\Sigma),
\]
with multiplication
\[
(\eta,u)\cdot(\eta',u')
=
\bigl(\eta\,(u\triangleright \eta'),\,uu'\bigr),
\]
and standard coboundary action
\[
g_{ij}\mapsto u_i\,\partial_\Sigma(\eta_{ij})\,g_{ij}\,u_j^{-1},
\]
\[
h_{ijk}\mapsto
(u_i\triangleright h_{ijk})\,
\eta_{ij}\,
(g_{ij}\triangleright \eta_{jk})\,
\eta_{ik}^{-1}.
\]
The full fixed-cutoff higher gluing datum on the genuinely noncentral branch is therefore the orbit class
\[
q_\Sigma=[(g,h)]\in \check H^2(N_\Sigma,H_\Sigma\to G_\Sigma),
\]
which classifies the full crossed-module equivalence orbit of the pair \((g,h)\). It does not in
general determine a unique ordinary \(G_\Sigma\)-valued \(1\)-cocycle class after strictification,
because the map below need not be injective.
Let the natural strict-locus map be
\[
\begin{aligned}
\iota_\Sigma:\check H^1(N_\Sigma,G_\Sigma)
&\longrightarrow \check H^2(N_\Sigma,H_\Sigma\to G_\Sigma),\\
[g]&\longmapsto[(g,1)].
\end{aligned}
\]
Define the separate \(\{0,1\}\)-valued strictification obstruction \(o^{(2)}_\Sigma(g,h)\) by
\[
\begin{aligned}
o^{(2)}_\Sigma(g,h)=0
&\quad\Longleftrightarrow\quad q_\Sigma\in\operatorname{im}(\iota_\Sigma)\\
&\quad\Longleftrightarrow\quad [(g,h)]\text{ has a representative }(g^{\mathrm{str}},1)\\
&\hspace{7.2em}\text{with }g^{\mathrm{str}}_{ij}g^{\mathrm{str}}_{jk}=g^{\mathrm{str}}_{ik}.
\end{aligned}
\]
and set \(o^{(2)}_\Sigma(g,h)=1\) otherwise.
Thus \(o^{(2)}_\Sigma\) records only whether the higher associator defect can be removed; it is
not the full orbit class \(q_\Sigma\). No quantitative closure/readback datum \(P\),
\(N_{\mathrm{CRC}}\), or \(\ell_\star^2\) enters
this theorem package.
\end{theorem}

\begin{proof}[Proof sketch]
On pair overlaps, every regulator-scale recharting acts on a finite-dimensional matrix algebra and is therefore inner, so it is implemented by a unitary on the cut Hilbert space. On triple overlaps, genuinely noncentral failure of strict composition is recorded by unitary associators instead of scalars. These \(1\)- and \(2\)-morphisms form a compact unitary \(2\)-group of rechartings. Skeletal strictification of a compact \(2\)-group is equivalent to crossed-module data, which yields the displayed compact \(\mathbb K_\Sigma\). Because the nerve is finite, \(C^1(N_\Sigma,H_\Sigma)\) and \(C^0(N_\Sigma,G_\Sigma)\) are finite products of compact groups, hence \(\mathcal T_\Sigma\) is compact. The displayed formulas are the standard crossed-module coboundary action, and the orbit class is exactly the nonabelian \v{C}ech \(2\)-class of the defect data; see \cite{bullivant17} for an explicit higher-lattice-gauge realization of the same crossed-module structures.
\end{proof}

\begin{theorem}[Higher-gauge edge-center completion]\label{thm:hgedgecenter}
Let \(B=B_L\cup B_R\) be a fixed-cutoff collar around a connected cut \(\Sigma\) on the genuinely noncentral branch of Theorem~\ref{thm:hgdatum}. Then, as unitary \(\mathcal T_\Sigma\)-modules,
\[
\widetilde{\mathcal H}_{B_L}
\cong
\bigoplus_{\lambda\in\Lambda_\Sigma}
W_\lambda\otimes \mathcal H_{b_L^\lambda},
\qquad
\widetilde{\mathcal H}_{B_R}
\cong
\bigoplus_{\mu\in\Lambda_\Sigma}
W_\mu^*\otimes \mathcal H_{b_R^\mu},
\]
for a finite set \(\Lambda_\Sigma\) of irreducible unitary representations of \(\mathcal T_\Sigma\) that actually occur. Hence the physical higher-gauge collar space is
\[
\mathcal H_B^{2g}
:=
\bigl(\widetilde{\mathcal H}_{B_L}\otimes \widetilde{\mathcal H}_{B_R}\bigr)^{\mathcal T_\Sigma}
\cong
\bigoplus_{\lambda\in\Lambda_\Sigma}
\mathcal H_{b_L^\lambda}\otimes \mathcal H_{b_R^\lambda},
\]
and the collar algebra and its center are
\[
\mathcal A_{2g}(B)
\cong
\bigoplus_{\lambda\in\Lambda_\Sigma}
\mathcal B(\mathcal H_{b_L^\lambda})\otimes
\mathcal B(\mathcal H_{b_R^\lambda}),
\qquad
Z\bigl(\mathcal A_{2g}(B)\bigr)
=
\bigoplus_{\lambda\in\Lambda_\Sigma}\mathbb C\,\mathbf 1_\lambda.
\]
\end{theorem}

\begin{proof}[Proof sketch]
Because \(\mathcal T_\Sigma\) is compact and the half-collar spaces are finite-dimensional, both \(\widetilde{\mathcal H}_{B_L}\) and \(\widetilde{\mathcal H}_{B_R}\) split orthogonally into irreducible unitary \(\mathcal T_\Sigma\)-modules with finite multiplicity. The right side sees inverse transport across the same cut, hence the contragredient module. Therefore
\[
\widetilde{\mathcal H}_{B_L}\otimes \widetilde{\mathcal H}_{B_R}
\cong
\bigoplus_{\lambda,\mu}
(W_\lambda\otimes W_\mu^*)\otimes
(\mathcal H_{b_L^\lambda}\otimes \mathcal H_{b_R^\mu}).
\]
Taking \(\mathcal T_\Sigma\)-invariants leaves
\[
(W_\lambda\otimes W_\mu^*)^{\mathcal T_\Sigma}
\cong
\mathrm{Hom}_{\mathcal T_\Sigma}(W_\mu,W_\lambda)
\cong
\begin{cases}
\mathbb C, & \lambda=\mu,\\
0, & \lambda\neq\mu,
\end{cases}
\]
by Schur's lemma. This yields the matched block decomposition and the center formula.
\end{proof}

\begin{theorem}[Higher-gauge Markov collar and carried errors]\label{thm:hgmarkov}
Let \(\rho_{ABD}\) be a faithful state on a collar whose middle region \(B\) carries the higher-gauge block decomposition of Theorem~\ref{thm:hgedgecenter}. If
\[
I(A:D\mid B)_\rho=0,
\]
and \(\rho\) satisfies the Markov-split alignment hypothesis for that block decomposition (Definition~\ref{def:ecaligned}, with \(\alpha\) replaced by \(\lambda\)), then
\[
\rho_{ABD}
=
\bigoplus_{\lambda\in\Lambda_\Sigma}
p_\lambda\,
\rho_{A b_L^\lambda}\otimes \rho_{b_R^\lambda D}.
\]
If instead \(I(A:D\mid B)_\rho\le \varepsilon\) on one fixed faithful collar model, then the same carried Fawzi--Renner and fixed-collar Markov errors as in the ordinary branch continue to hold:
\[
r_{\mathrm{FR}}(\varepsilon)=2\sqrt{1-e^{-\varepsilon}}\le 2\sqrt{\varepsilon},
\qquad
4\lambda_\ast^{-1}\,\delta^{\mathrm M}_{A:B:D}(\varepsilon).
\]
\end{theorem}

\begin{proof}[Proof sketch]
Theorem~\ref{thm:hgedgecenter} shows that the higher-gauge collar algebra is a finite direct sum of type-I tensor blocks. HJPW depends only on that finite-dimensional algebraic structure, not on whether the block label arose from an ordinary compact group, a central extension, or a crossed-module gauge system; as in the ordinary branch, HJPW supplies a state-dependent decomposition, and the identification of its factors with the preselected higher-gauge edge factors is the carried Markov-split alignment hypothesis. Likewise, the Fawzi--Renner remainder and the fixed-collar Markov modulus are finite-dimensional entropy and recovery statements and are blind to the origin of the block label.
\end{proof}

\begin{theorem}[Higher-gauge defect strictification]\label{thm:hgtransport}
With the genuinely noncentral cut data, full orbit class \(q_\Sigma\), and strictification
obstruction \(o^{(2)}_\Sigma\) of Theorem~\ref{thm:hgdatum}, the following hold:
\begin{enumerate}[leftmargin=2em]
\item \(q_\Sigma\) is invariant under all local rechartings and higher-gauge changes \((\eta,u)\in \mathcal T_\Sigma\) and classifies the full crossed-module gluing orbit.
\item \(o^{(2)}_\Sigma\) is an invariant property of that orbit and vanishes if and only if the
higher associator defect is removable.
\item When \(o^{(2)}_\Sigma=0\), the orbit contains at least one strict representative
\((g^{\mathrm{str}},1)\), and each such representative is a genuine \(G_\Sigma\)-valued
\(1\)-cocycle. Different strict representatives in the same orbit can be related by
\(H_\Sigma\)-valued edge changes and need not have the same ordinary \(H^1\) class or represented
holonomy.
\end{enumerate}
Thus \(o^{(2)}_\Sigma=0\) is the strictification condition for the genuinely noncentral branch. Strict
endpoint-only transport additionally requires that at least one allowed strict representative have
trivial holonomy on the relevant collar-sector representation, as stated in
Theorem~\ref{thm:transport-from-gluing}; this existential property is invariant on the full orbit.
\end{theorem}

\begin{proof}[Proof sketch]
Crossed-module coboundaries change representatives while preserving the full orbit \(q_\Sigma\).
By definition, \(o^{(2)}_\Sigma=0\) exactly when that orbit meets the strict subset
\((g^{\mathrm{str}},1)\). The surviving edge data then form a genuine \(G_\Sigma\)-valued
\(1\)-cocycle. The natural map \(\iota_\Sigma\) need not be injective: an
\(H_\Sigma\)-valued edge change can alter the ordinary \(G_\Sigma\)-holonomy through
\(\partial_\Sigma\). Therefore no individual strict representative's holonomy is assigned to
\(q_\Sigma\). What is invariant is whether the orbit contains a strict representative whose
holonomy is trivial on the chosen sector, and associator strictification alone does not imply that
existence.
\end{proof}

\begin{definition}[Overlap-transport groupoid and strict transportability]\label{def:overlap-transport}
Fix a connected cut \(\Sigma\) and a finite regulator charting nerve \(N_\Sigma\). The
\emph{overlap-transport groupoid} \(\Pi_1^{\mathrm{ov}}(N_\Sigma)\) has the regulator cut
charts as objects and words in overlap-preserving rechartings as morphisms, modulo insertion and
deletion of immediate inverse rechartings. On the ordinary or central branch, an oriented edge
\(i\to j\) is represented by a unitary recharting \(U_{ij}\) on the cut presentation, with
\(U_{ji}=U_{ij}^{-1}\) after choosing the inverse chart. On the genuinely noncentral branch,
the same notation denotes the \(G_\Sigma\)-part of the crossed-module data of
Theorem~\ref{thm:hgdatum}, with the \(H_\Sigma\)-valued associators retained as \(2\)-morphisms.

A collar charge at chart \(i\) is a simple edge-center summand, equivalently an irreducible
boundary module \(W_\alpha^{(i)}\) together with its multiplicity/intertwiner block in the
collar decomposition. Write \(\mathcal C_\alpha^{(i)}\) for that full finite-dimensional transported
charge block, including both pieces. For a path
\[
p=(i_0\to i_1\to\cdots\to i_m)
\]
define the transported charge by applying the composite recharting
\[
U_p:=U_{i_{m-1}i_m}\cdots U_{i_0i_1}
\]
to the boundary module and its intertwiner block. Transport is \emph{strictly path-independent}
when for any two overlap paths \(p,p'\) with the same endpoints the induced transport functors
on the collar charge blocks are naturally equal after the allowed local recharting gauge changes.
Equivalently, every closed overlap path acts trivially on the sector class and on its transported
intertwiner block, instead of only projectively or up to a noncentral \(2\)-morphism.

After a central or crossed-module defect has been strictified, write \(U^{\mathrm{str}}\) for a
resulting genuine edge \(1\)-cocycle. On the full collar charge block \(\mathcal C_\alpha\), it induces the ordinary
sector-holonomy representation
\[
\operatorname{Hol}_{\alpha,U^{\mathrm{str}}}:\pi_1(|N_\Sigma|,i)
\longrightarrow U(\mathcal C_\alpha),
\qquad
[\ell]\longmapsto U^{\mathrm{str}}_\ell\big|_{\mathcal C_\alpha}.
\]
On the noncentral branch, \(U^{\mathrm{str}}\) ranges over all strict representatives in the
crossed-module orbit; no unique ordinary holonomy is assigned to \(q_\Sigma\).
The phrase \emph{zero-obstruction sector} below means the combined condition: the relevant
triangle/higher defect is strictifiable and a strictification can be chosen for which
\(\operatorname{Hol}_{\alpha,U^{\mathrm{str}}}\) is the trivial representation. Vanishing of the
central triangle class, or removal of the noncentral associator alone, is not called strict
transportability.
\end{definition}

\begin{theorem}[TransportabilityFromOverlapGluing]\label{thm:transport-from-gluing}
Assume the fixed-cutoff regulator gluing package of Proposition~\ref{prop:regulatedrealization}
on the ordinary or central branch, and assume the crossed-module cut datum of
Theorem~\ref{thm:hgdatum} on the genuinely noncentral branch. Then path-independent
transportability is the following combined theorem-level criterion, not a separate DHR input.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2em]
\item \textbf{Ordinary branch.} If the overlap rechartings are strict on triple overlaps, then
transport of a collar charge along an overlap path is computed by the path composite \(U_p\).
It is strictly path-independent if and only if every closed overlap loop has trivial holonomy on
the collar-sector block. In the tree-cover case this condition is automatic; on a cover with
loops it is exactly the ordinary loop-coherence obstruction.
\item \textbf{Central branch.} Suppose the overlap centers are identified with one fixed abelian
unitary coefficient group \(Z_\Sigma\), the overlap transports act trivially on \(Z_\Sigma\), and
the only failure of strict triple-overlap composition is central:
\[
U_{ij}U_{jk}=z_{ijk}U_{ik},\qquad z_{ijk}\in Z_\Sigma.
\]
Let \([z]_\Sigma\in \check H^2(N_\Sigma,Z_\Sigma)\) denote the resulting central triangle-defect class,
including the central multipliers accumulated by elementary triangle moves between overlap
paths. Strict path-independent transport of a collar charge \(\alpha\) exists if and only if
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=2em]
\item \([z]_\Sigma=0\), so a central \(1\)-cochain \(a_{ij}\) strictifies the edge system to
\(U^{\mathrm{str}}_{ij}=a_{ij}^{-1}U_{ij}\); and
\item one such strictification has
\(\operatorname{Hol}_{\alpha,U^{\mathrm{str}}}([\ell])=\mathbf 1_{\mathcal C_\alpha}\) for every closed
overlap loop \(\ell\).
\end{enumerate}
If \([z]_\Sigma\ne0\), a projective triangle defect remains. If \([z]_\Sigma=0\) but every
allowed strictification fails condition \textup{(b)}, the edge transports can be made into genuine
\(1\)-cocycles but retain ordinary loop path dependence.
\item \textbf{Genuinely noncentral branch.} Let \(q_\Sigma=[(g,h)]\) be the full crossed-module
orbit and \(o^{(2)}_\Sigma\) its higher-associator strictification obstruction from
Theorem~\ref{thm:hgtransport}. Strict path-independent transport
of an ordinary collar charge \(\alpha\) exists if and only if \(o^{(2)}_\Sigma=0\) and there is a
crossed-module strictification for which the resulting genuine \(G_\Sigma\)-valued
\(1\)-cocycle has trivial holonomy on \(\mathcal C_\alpha\). When \(o^{(2)}_\Sigma\ne0\), there is no gauge in
which all path comparisons are ordinary equalities: the fixed-cutoff sector is instead a
higher-gauge sector labelled by \(q_\Sigma\), and transport is higher transport in the
crossed-module \(2\)-groupoid instead of ordinary path-independent collar transport (the
categorical input to DHR-type constructions, not by itself net-level DHR transportability). When
\(o^{(2)}_\Sigma=0\) but every allowed strictification has nontrivial represented
\(G_\Sigma\)-holonomy, the higher defect is gone but ordinary loop path dependence remains.
\end{enumerate}
Thus overlap gluing constructs the transport operation. The complete obstruction to strict path
independence is ordinary sector holonomy on the ordinary branch, the pair consisting of
\([z]_\Sigma\) and the existence of a trivial-holonomy strictification on the central branch, and
the pair consisting of \(o^{(2)}_\Sigma\) and the existence of a trivial-holonomy strict
representative on the genuinely noncentral branch.
\end{theorem}

\begin{proof}
For a path \(p=(i_0\to\cdots\to i_m)\), Definition~\ref{def:overlap-transport} gives the
transport functor by composing the finite-dimensional recharting implementers. This construction
uses only the derived overlap unitary transition system of
Proposition~\ref{prop:regulatedrealization}; no transportability assumption is invoked.

On the ordinary branch, strict triple-overlap coherence says that elementary replacements of the
form \((i\to j\to k)\leadsto(i\to k)\) do not change the composite recharting. Any two paths with
the same endpoints in the finite nerve differ, after inserting or deleting immediate backtracks,
by a finite sequence of such elementary moves together with closed loop moves. Backtracks
contribute the identity because \(U_{ji}=U_{ij}^{-1}\). Therefore the only possible path
dependence is the ordinary loop holonomy. The transport is strictly path-independent exactly when
that loop holonomy acts trivially on the collar-sector block.

On the central branch, the same elementary triangle replacement changes the composite by the
central multiplier \(z_{ijk}\). For a finite sequence of elementary moves between two paths, the
total discrepancy is the product of the corresponding \(z\)'s over the filling \(2\)-chain. The
fixed-coefficient and trivial-action hypotheses identify every multiplier in \(Z_\Sigma\); the
quadruple-overlap coherence identity is then precisely the untwisted \v{C}ech cocycle identity, so this product
depends only on the class \([z]_\Sigma\). If \([z]_\Sigma=0\), choose a central \(1\)-cochain
\(a_{ij}\) with \(z_{ijk}=a_{ij}a_{jk}a_{ik}^{-1}\). Replacing \(U_{ij}\) by \(a_{ij}^{-1}U_{ij}\)
kills the central multiplier on every triangle, so all elementary path moves preserve the
transport functor. The ordinary argument then gives strict path independence exactly when every
remaining closed-loop holonomy of this strictified \(1\)-cocycle acts trivially on the sector
block. Conversely, strict path-independent transport makes every elementary triangular comparison
trivial after an allowed recharting gauge change, so \(z\) is a coboundary, and it also makes every
closed-loop action trivial. This proves both necessary conditions.

On the genuinely noncentral branch, elementary triangle comparisons are non-scalar
\(H_\Sigma\)-valued \(2\)-morphisms \(h_{ijk}\), and the consistency of different fillings of a
path homotopy is the crossed-module cocycle identity of Theorem~\ref{thm:hgdatum}. A local
higher-gauge change \((\eta,u)\) changes representatives by the crossed-module coboundary action
displayed there, while preserving the full class \(q_\Sigma\) and the strictifiability property
\(o^{(2)}_\Sigma\) by Theorem~\ref{thm:hgtransport}. If
\(o^{(2)}_\Sigma=0\), the data are equivalent to at least one strict representative: the
\(h_{ijk}\) can be gauged away and \(g_{ij}g_{jk}=g_{ik}\) holds. Each such
\(G_\Sigma\)-valued \(1\)-cocycle defines an ordinary path-composite transport, which is
endpoint-only exactly when its represented loop holonomy is trivial. Hence ordinary strict
transport exists precisely when at least one allowed strict representative passes that test.
Conversely, strict ordinary path-independent transport gives a representative
in which every triangular \(2\)-comparison is the identity, hence \(o^{(2)}_\Sigma=0\), and every
closed-loop action on the sector is trivial. If \(o^{(2)}_\Sigma\ne0\),
Theorem~\ref{thm:hgtransport} says the higher defect is not removable, so no strict ordinary
transport functor can exist; if \(o^{(2)}_\Sigma=0\) alone, only existence of a strict
representative has been proved.
\end{proof}

\begin{remark}[Triangle-free cycle acceptance test]\label{rem:transport-cycle-test}
Let \(N_\Sigma=C_n\) be a cycle nerve with \(n\ge4\) and no filled \(2\)-simplices. There are no
triple-overlap constraints, so every central \(2\)-cocycle datum and every higher associator datum
is vacuously trivial: \([z]_\Sigma=0\) and \(o^{(2)}_\Sigma=0\). On a full charge block
\(\mathcal C_\alpha=\mathbb C^2\), put the identity transport on all but one oriented cycle edge
and put \(V=\operatorname{diag}(-1,1)\) on the remaining edge, with inverse transports on reverse
edges. The ordered holonomy is the non-scalar unitary \(V\ne\mathrm{id}\), so no central edge
rephasing can make it the identity.

For a genuinely noncentral instance, take the crossed module
\[
H_\Sigma=\SU(2)\hookrightarrow G_\Sigma=\U(2)
\]
with conjugation action and the standard action on \(\mathcal C_\alpha\). Its band is
\(G_\Sigma/\partial H_\Sigma\cong\U(1)\), detected by the determinant. The cycle has
\(o^{(2)}_\Sigma=0\), but its band holonomy is
\(\det V=-1\). An \(H_\Sigma\)-valued edge change has determinant one and a vertex-frame change
only conjugates the based loop, so no allowed strict representative has trivial holonomy. The two
routes between the endpoints of the distinguished edge therefore induce different transports.
Conditions \textup{(ii)(b)} and \textup{(iii)} reject the respective central and noncentral
assignments even though the central triangle data and higher associator data are trivial.
\end{remark}

\begin{corollary}[Transportability from overlap gluing]\label{cor:transportability-from-overlap-gluing}
The ordinary/central compact-gauge branch may invoke only those finite-cutoff collar sectors that
satisfy the zero-obstruction conclusion of Theorem~\ref{thm:transport-from-gluing}. The condition
is the combined strict-transport corollary of overlap gluing: after any central or higher defect
is strictified, at least one allowed resulting ordinary sector holonomy must be trivial. If the genuinely
noncentral obstruction \(o^{(2)}_\Sigma\) is nonzero, the branch is a higher-gauge fixed-cutoff sector rather
than an ordinary compact-group DR reconstruction sector; if \(o^{(2)}_\Sigma=0\), it has one or
more strict \(G_\Sigma\)-valued \(1\)-cocycle representatives and enters the transportable case only
when at least one has trivial sector holonomy.
\end{corollary}

\begin{definition}[Fixed-cutoff zero-obstruction collar sectors]\label{def:fixed-cutoff-collar-sectors}
Fix a regulator cutoff \(r\) and a connected overlap collar \(B=B_L\cup B_R\) around a cut
\(\Sigma\) on the ordinary or central-defect branch. Let \(\widehat K_{\Sigma,r}\) be the compact
boundary action supplied by the fixed-cutoff overlap gluing theorem, with
\(\widehat K_{\Sigma,r}=K_{\Sigma,r}\) on the ordinary branch. Edge-center completion gives
\[
\widetilde{\mathcal H}_{B_L}
\cong
\bigoplus_{\alpha\in A_{\Sigma,r}}
W_\alpha\otimes \mathcal H_{b_L^\alpha},
\qquad
\widetilde{\mathcal H}_{B_R}
\cong
\bigoplus_{\alpha\in A_{\Sigma,r}}
W_\alpha^*\otimes \mathcal H_{b_R^\alpha},
\]
and hence
\[
\mathcal H_B
=
\bigl(\widetilde{\mathcal H}_{B_L}\otimes\widetilde{\mathcal H}_{B_R}\bigr)^{\widehat K_{\Sigma,r}}
\cong
\bigoplus_{\alpha\in A_{\Sigma,r}}
\mathcal H_{b_L^\alpha}\otimes \mathcal H_{b_R^\alpha}.
\]
The minimal central projector onto the \(\alpha\)-summand is denoted \(P_\alpha\). Before selecting
seeds, choose one common stagewise strict edge \(1\)-cocycle
\(U^{\mathrm{str}}_r\): on the ordinary branch this is the given strict system; on the central
branch it is one allowed strictification after \([z]_\Sigma=0\); and a strictified genuinely
noncentral datum may enter only after \(o^{(2)}_\Sigma=0\) and the choice of one allowed strict
\(G_\Sigma\)-valued representative. A \emph{visible seed charge relative to
\(U^{\mathrm{str}}_r\)} is a pair \((P_\alpha,W_\alpha)\) whose full transported charge block has
trivial holonomy for this same representative on every closed overlap loop. The construction does
not union seeds that require mutually incompatible strictifications. The full orbit \(q_\Sigma\)
classifies the allowed crossed-module representatives but does not select a unique ordinary
\(H^1\) class; choosing \(U^{\mathrm{str}}_r\) is therefore part of the fixed-stage ordinary
sector datum.
Let \(S_r\) be the finite set of visible seed carriers. Define
\[
\mathsf{Sect}^{\mathrm{bos}}_r
:=
\bigl\langle \mathbf 1,S_r,S_r^*\bigr\rangle_{\oplus,\otimes,
\text{ subobjects},\text{ isomorphism}}
\subset \operatorname{Rep}_{\mathrm{fd}}(\widehat K_{\Sigma,r})
\]
to be the replete full additive Karoubi rigid tensor subcategory generated by those carriers.
Equivalently, every object is a finite direct sum of subobjects of finite tensor words in visible
seeds and their conjugates. For objects \(X,Y\) in this category, define
\[
\mathrm{Hom}_r(X,Y):=\mathrm{Hom}_{\widehat K_{\Sigma,r}}(X,Y),
\]
after transporting all localizations to one reference collar by the zero-obstruction transport
functor. Different reference collars give canonically unitarily equivalent Hom spaces by
Theorem~\ref{thm:transport-from-gluing}. The projector \(P_\alpha\) detects a seed in the original
one-collar algebra; it is not a declaration that every irreducible generated by tensor products is
a central block of that finite algebra. If \(X\) is an irreducible summand of a tensor word
\(T\), its categorical support is an orthogonal idempotent
\(e_X\in\operatorname{End}_{\widehat K_{\Sigma,r}}(T)\), represented physically, when that
concatenated-collar realization is retained, in the finite algebra for that particular
concatenated collar.
\end{definition}

\begin{theorem}[FixedCutoffBosonicSectorCategory]\label{thm:fixed-cutoff-bosonic-sector-category}
At every fixed regulator cutoff \(r\), on the ordinary or central-defect zero-obstruction branch
and in the bosonic internal-gauge sector of the \(3+1\)-dimensional EFT regime, the construction of
Definition~\ref{def:fixed-cutoff-collar-sectors} produces a semisimple rigid symmetric
\(C^*\)-tensor category
\[
\mathsf{Sect}^{\mathrm{bos}}_r.
\]
Its visible seed objects are the transportable edge-center collar charges
\((P_\alpha,W_\alpha)\). Its simple objects are all irreducible summands of finite tensor words in
those seeds and their conjugates; they need not be visible blocks of the original one-collar
algebra, and there may be infinitely many simple isomorphism classes even though every object and
Hom space is finite-dimensional. The tensor product and duals are the representation tensor
product and conjugate; the finite tensor-realization clause of
Definition~\ref{def:compact-gauge-refinement-receipt} identifies them physically with collar
concatenation and orientation reversal on a certified tail. The \(^*\)-operation and \(C^*\)-norm are the operator
adjoint and norm on the finite-dimensional carriers, and the symmetry is the bosonic
spacelike-exchange symmetry of the \(3+1\)-dimensional EFT branch. The inclusion has the canonical
faithful symmetric strong monoidal forgetful functor
\[
F_r:\mathsf{Sect}^{\mathrm{bos}}_r\longrightarrow\mathsf{Hilb}_{\mathrm{fd}}.
\]
\end{theorem}

\begin{proof}
By edge-center completion, every seed charge visible on one reference collar is represented by a
minimal central summand \(P_\alpha\) together with an irreducible boundary carrier \(W_\alpha\) of
\(\widehat K_{\Sigma,r}\). Since \(\widehat K_{\Sigma,r}\) is compact and acts unitarily on
finite-dimensional collar data, its finite-dimensional representations are completely reducible.
The replete additive Karoubi tensor subcategory generated by the \(W_\alpha\)'s and their
conjugates is therefore semisimple, with finite-dimensional objects and Hom spaces. Complete
reducibility does not imply that its simple skeleton is finite, and no such finiteness is used.

Transport between collars is the path-composite construction of
Theorem~\ref{thm:transport-from-gluing}. For every closed loop \(\ell\), the common choice
\(U^{\mathrm{str}}_r\) acts as the identity on each seed block. It therefore acts as the identity
on direct sums, as \(\mathbf 1\otimes\mathbf 1\) on tensor products, as the conjugate identity on
duals, and by restriction as the identity on every invariant subobject. Thus every object in the
generated category has path-independent transport using the same representative, and those
transport identifications are monoidal. In particular, transport of \(P_\alpha\), \(W_\alpha\),
and their intertwiners is independent of the overlap path.
Hence the Hom spaces defined after moving all localizations to a reference collar do not depend on
the chosen path or reference collar, up to canonical transported unitary identification.

For two objects \(X\) and \(Y\), take the diagonal tensor product \(X\otimes Y\) of
\(\widehat K_{\Sigma,r}\)-modules. By definition the generated Karoubi category contains this
tensor word and every irreducible summand selected by an idempotent in its intertwiner algebra, so
the product stays inside the category without requiring those summands to occur in the center of
the original one-collar algebra. The trivial one-dimensional module is the tensor unit.
Associativity is implemented by the standard finite-dimensional tensor associator, whose pentagon
identity is the equality of the two rebracketings of a fourfold tensor product. When the finite
tensor-realization receipt is present, these tensor words, idempotents, and rebracketings are
represented by concatenated collars and union-collar gluing.

Duals are the conjugate representations \(W_\alpha^*\); the finite tensor-realization receipt
identifies this with reversing collar orientation and swapping the half-collar boundary actions.
Evaluation and coevaluation are the standard
\(\widehat K_{\Sigma,r}\)-invariant pairings. Their zig-zag identities are the usual
finite-dimensional duality identities, equivalently cap/cup cancellation for collar gluing.

The \(^*\)-structure is the operator adjoint on the lifted finite-dimensional carriers. Each
\(\mathrm{Hom}_r(X,Y)\) is a closed subspace of operators between finite-dimensional Hilbert
spaces, adjoints are again \(\widehat K_{\Sigma,r}\)-intertwiners, composition is operator
composition, and the norm is the operator norm. Thus \(\|f^*f\|=\|f\|^2\), direct sums and
subobjects are implemented by orthogonal projections, and the category is a \(C^*\)-category.

The canonical unitary flip
\(c_{X,Y}:X\otimes_rY\to Y\otimes_rX\) is an intertwiner. Its naturality, hexagon identities,
and \(c_{Y,X}c_{X,Y}=\mathrm{id}\) are the standard representation identities, so the braiding is
symmetric. On a finite tensor-realization branch this flip is represented physically by spacelike
exchange of the codimension-two collar supports; double exchange is isotopic to the identity on
the bosonic \(3+1\)-dimensional branch. Fermionic signs, spinorial matter, and chirality are not part of this
bosonic internal-gauge category; they belong to the later super-Tannakian or matter-sector lift.
Forgetting the group action and retaining the carrier Hilbert space and the same linear maps is
faithful, \(^*\)-preserving, and symmetric strong monoidal, which gives the displayed \(F_r\).
\end{proof}

\begin{corollary}[Fixed-cutoff category from sector construction]\label{cor:fixed-cutoff-category-sector-construction}
The fixed-cutoff collar-sector packages are bosonic symmetric \(C^*\)-tensor categories with
canonical objectwise finite-dimensional forgetful fibers by
Theorem~\ref{thm:fixed-cutoff-bosonic-sector-category}. Refinement compatibility is a separate
question: Theorem~\ref{thm:refinement-functor-fiber-descent} supplies it only on a cofinal tail
carrying the explicit compact-gauge refinement receipt of
Definition~\ref{def:compact-gauge-refinement-receipt}. The realized low-energy branch is then
supplied by Theorem~\ref{thm:mar-witness-landing}.
\end{corollary}

\begin{proposition}[Higher-gauge interacting compatibility]\label{prop:hginteracting}
In a fixed-cutoff crossed-module lattice realization of Theorem~\ref{thm:hgdatum}, one may add local collar terms
\[
K_{\mathrm{collar}}^{2g}
=
\sum_{v\in\Sigma_0}\beta_v(1-A_v)
+
\sum_{e\in\Sigma_1}\beta_e(1-B_e)
+
\sum_{c\in\mathcal C_\Sigma}\beta_c(1-C_c),
\]
where \(A_v\), \(B_e\), and \(C_c\) are the local gauge and fake-flat projectors of the chosen higher-gauge realization. These terms are bounded-support and commute in the standard higher-gauge projector realization \cite{bullivant17}, so the full fixed-cutoff generator is quasi-local and inside the Axiom~\ref{ax:maxent} class.
\end{proposition}

\begin{proof}[Proof sketch]
The additional terms are local projector constraints supported on finitely many collar cells, so they preserve bounded support and quasi-locality. In the standard higher-gauge projector realization they commute, so the same finite-constraint MaxEnt/Lieb--Robinson bookkeeping used on the ordinary branch continues to apply.
\end{proof}

\begin{remark}[Status of the regulator package and the precise Markov boundary]
Proposition~\ref{prop:regulatedrealization}, Theorem~\ref{thm:markovcollar}, and Theorems~\ref{thm:hgdatum}--\ref{thm:hgtransport} together with Proposition~\ref{prop:hginteracting} show that edge-center completion is a theorem of overlap consistency plus the finite regulator presentation on the ordinary, central-defect, and genuinely noncentral higher-gauge branches. No preferred quantum-link realization is assumed on the ordinary or central branch, and the genuinely noncentral branch is handled by the compact crossed-module replacement instead of by one more ordinary-group lemma. The fixed-cutoff topological UV package is closed on all three branches. The continuum modular/geometric lift on the support-visible geometric subnet is Theorem~\ref{thm:bw}; the compact-gauge realized branch is handled by Theorem~\ref{thm:mar-witness-landing}. The distinct state-control issue is that exact splice and modular-additivity identities require either literal exact Markovity or a controlled family that converges to the exact Markov set on one fixed finite-dimensional collar; and, wherever those identities use the preselected edge factors \(b_L^\alpha,b_R^\alpha\), they additionally carry the Markov-split alignment hypothesis of Definition~\ref{def:ecaligned}, which exact Markovity does not imply (Remark~\ref{rem:hjpwalignment}).
\end{remark}

\begin{definition}[Exact Markov set and collar-distance modulus]\label{def:markovmodulus}
Fix the finite-dimensional collar Hilbert space of Theorem~\ref{thm:markovcollar}. Let
\[
\mathfrak M_{A:B:D}
:=
\left\{
\sigma_{ABD}:\ I(A:D\mid B)_\sigma=0
\right\}
\]
be the set of exact Markov states on that fixed collar. By HJPW, \(\sigma\in\mathfrak M_{A:B:D}\) iff \(\sigma\) factorizes blockwise over \emph{some} state-dependent direct-sum/tensor decomposition of \(\mathcal H_B\). The subset factorizing over the fixed edge-center decomposition of \(B\) is the EC-aligned class \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\) of Definition~\ref{def:ecaligned}; the inclusion \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\subseteq \mathfrak M_{A:B:D}\) is strict in general (Remark~\ref{rem:hjpwalignment}).

For a general state \(\rho_{ABD}\), define its distance to the exact Markov set by
\[
d_{\mathrm M}(\rho):=\inf_{\sigma\in\mathfrak M_{A:B:D}}\|\rho-\sigma\|_1,
\]
and the fixed-collar exact-Markov modulus by
\[
\delta^{\mathrm M}_{A:B:D}(\varepsilon)
:=
\sup\left\{
d_{\mathrm M}(\rho):
I(A:D\mid B)_\rho\le \varepsilon
\right\}.
\]
The modulus \(\delta^{\mathrm M}_{A:B:D}\) measures distance to the full exact Markov set \(\mathfrak M_{A:B:D}\). No analogous vanishing modulus exists for the EC-aligned class: by Remark~\ref{rem:hjpwalignment} there are states with \(I(A:D\mid B)=0\) at fixed nonzero trace distance from \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\), so replacement by an EC-aligned normal form is available only under the Markov-split alignment hypothesis on the comparison family, not from small conditional mutual information alone.
\end{definition}

\begin{proposition}[Controlled exact Markov-collar limit]\label{prop:controlledmarkov}
On a fixed finite-dimensional collar, the exact Markov set \(\mathfrak M_{A:B:D}\) is compact and
\[
\delta^{\mathrm M}_{A:B:D}(\varepsilon)\longrightarrow 0
\qquad
\text{as }\varepsilon\downarrow 0.
\]
Consequently, if \(\rho^{(n)}_{ABD}\) is any sequence of states on that same collar with
\[
I(A:D\mid B)_{\rho^{(n)}}\le \varepsilon_n,
\qquad
\varepsilon_n\to0,
\]
then there exist exact Markov states \(\sigma^{(n)}\in\mathfrak M_{A:B:D}\) such that
\[
\|\rho^{(n)}-\sigma^{(n)}\|_1
\le
\delta^{\mathrm M}_{A:B:D}(\varepsilon_n)
\longrightarrow 0.
\]
Thus approximate recoverability converges to the exact Markov set on the fixed collar. Convergence to the EC-aligned normal form used by the compact-gauge branch requires, in addition, that the comparison states \(\sigma^{(n)}\) can be chosen in \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\); this is the Markov-split alignment hypothesis on the comparison family (Definition~\ref{def:ecaligned}) and is not supplied by small conditional mutual information alone (Remark~\ref{rem:hjpwalignment}).
\end{proposition}

\begin{proof}
The full state space on a fixed finite-dimensional Hilbert space is compact in trace norm. Conditional mutual information is continuous there because von Neumann entropy is continuous in finite dimension. Hence \(\mathfrak M_{A:B:D}\) is closed, so it is compact as a closed subset of a compact space.

Suppose \(\delta^{\mathrm M}_{A:B:D}(\varepsilon)\not\to 0\). Then there exist \(\eta>0\), a sequence \(\varepsilon_n\downarrow 0\), and states \(\rho^{(n)}\) with \(I(A:D\mid B)_{\rho^{(n)}}\le \varepsilon_n\) but \(d_{\mathrm M}(\rho^{(n)})\ge \eta\) for all \(n\). By compactness, pass to a trace-norm convergent subsequence \(\rho^{(n_k)}\to \rho^\ast\). Continuity of conditional mutual information gives
\[
I(A:D\mid B)_{\rho^\ast}
=
\lim_{k\to\infty} I(A:D\mid B)_{\rho^{(n_k)}}
=
0,
\]
so \(\rho^\ast\in \mathfrak M_{A:B:D}\). But then
\[
d_{\mathrm M}(\rho^{(n_k)})
\le
\|\rho^{(n_k)}-\rho^\ast\|_1
\longrightarrow 0,
\]
contradicting \(d_{\mathrm M}(\rho^{(n_k)})\ge \eta\). Thus \(\delta^{\mathrm M}_{A:B:D}(\varepsilon)\to 0\). The final statement follows by choosing \(\sigma^{(n)}\in\mathfrak M_{A:B:D}\) within \(\delta^{\mathrm M}_{A:B:D}(\varepsilon_n)+1/n\) of \(\rho^{(n)}\).
\end{proof}

\begin{theorem}[Finite-collar Markov replacement stability]\label{thm:finite-collar-markov-stability}
Fix one finite-dimensional collar model \(A:B:D\) and a faithful floor
\(\lambda_\ast>0\) for the collar state. Let
\[
\mathcal S_{\lambda_\ast}
:=
\{\rho_{ABD}:\rho_{ABD}\ge \lambda_\ast\mathbf 1\}
\]
inside the affine state space on that fixed collar, and let
\[
\mathfrak M_{A:B:D}^{\lambda_\ast}:=
\mathfrak M_{A:B:D}\cap \mathcal S_{\lambda_\ast}.
\]
Assume this faithful exact-Markov class is nonempty. There are constants \(C_{A:B:D,\lambda_\ast}>0\) and
\(\theta_{A:B:D,\lambda_\ast}>0\), depending on the chosen collar model and
floor but not on a refinement family, such that every
\(\rho\in\mathcal S_{\lambda_\ast}\) satisfies
\[
d_{\mathrm M}^{\lambda_\ast}(\rho)
:=
\inf_{\sigma\in\mathfrak M_{A:B:D}^{\lambda_\ast}}
\|\rho-\sigma\|_1
\le
C_{A:B:D,\lambda_\ast}\,
I(A:D\mid B)_\rho^{\theta_{A:B:D,\lambda_\ast}}.
\]
Equivalently, on that fixed faithful collar class,
\[
\delta^{\mathrm M,\lambda_\ast}_{A:B:D}(\varepsilon)
\le
C_{A:B:D,\lambda_\ast}\,\varepsilon^{\theta_{A:B:D,\lambda_\ast}}.
\]
The constants are collar-local; this is not a dimension-free stability theorem
for arbitrary tripartite systems.
\end{theorem}

\begin{proof}
On \(\mathcal S_{\lambda_\ast}\) the von Neumann entropy terms are real
analytic functions of the matrix entries, hence
\[
F(\rho):=I(A:D\mid B)_\rho
\]
is a nonnegative real analytic function. By equality in strong subadditivity,
or equivalently the HJPW structure theorem, the zero set of \(F\) is precisely
\(\mathfrak M_{A:B:D}^{\lambda_\ast}\). The compact-set Lojasiewicz inequality
for a real analytic nonnegative function gives constants \(c>0\) and \(q>0\)
on this fixed compact collar class such that
\[
F(\rho)\ge c\,d_{\mathrm M}^{\lambda_\ast}(\rho)^q .
\]
Taking \(C=c^{-1/q}\) and \(\theta=1/q\) gives the displayed estimate.
\end{proof}

\begin{proposition}[Approximate collar recovery]\label{prop:approxrecover}
Let \(A\)-\(B\)-\(D\) be a collar tripartition satisfying
\[
I(A:D|B)_\rho\le \varepsilon,
\]
and let $\mathcal R_{B\to BD}$ be a recovery map such that
\[
F\!\left(\rho_{ABD},(\mathrm{id}_A\otimes \mathcal R_{B\to BD})(\rho_{AB})\right)\ge e^{-\varepsilon/2}.
\]
Define the recovered comparison state
\[
\rho^{\mathrm{rec}}_{ABD}:=(\mathrm{id}_A\otimes \mathcal R_{B\to BD})(\rho_{AB}),
\qquad
r_{\mathrm{FR}}(\varepsilon):=2\sqrt{1-e^{-\varepsilon}}\le 2\sqrt{\varepsilon}.
\]
Then
\[
\|\rho_{ABD}-\rho^{\mathrm{rec}}_{ABD}\|_1\le r_{\mathrm{FR}}(\varepsilon).
\]
Consequently, for every CPTP map \(\Lambda_{BD\to B'D'}\) and every bounded observable \(X\) supported on \(A\cup B'\),
\[
\left|\mathrm{Tr}\!\left[X(\mathrm{id}_A\otimes \Lambda)(\rho_{ABD}-\rho^{\mathrm{rec}}_{ABD})\right]\right|
\le
\|X\|_\infty\,\|(\mathrm{id}_A\otimes \Lambda)(\rho_{ABD}-\rho^{\mathrm{rec}}_{ABD})\|_1
\le
\|X\|_\infty\,r_{\mathrm{FR}}(\varepsilon).
\]
\end{proposition}

\begin{proof}
The fidelity lower bound and the Fuchs--van de Graaf inequality give
\[
\|\rho_{ABD}-\rho^{\mathrm{rec}}_{ABD}\|_1
\le
2\sqrt{1-F(\rho_{ABD},\rho^{\mathrm{rec}}_{ABD})^2}
\le
2\sqrt{1-e^{-\varepsilon}}
=
r_{\mathrm{FR}}(\varepsilon).
\]
The estimate \(r_{\mathrm{FR}}(\varepsilon)\le 2\sqrt{\varepsilon}\) follows from \(1-e^{-x}\le x\). Contractivity of trace norm under CPTP maps gives the transported bound, and the observable estimate is the duality between trace norm and operator norm \cite{fawziRenner15}. The bound is constructive and dimension-free. What it controls is closeness to a recovered comparison state; no claim is made that \(\rho^{\mathrm{rec}}_{ABD}\) is itself exact Markov.
\end{proof}

\begin{proposition}[Exact splice theorem and controlled collar approximation]\label{prop:splice}
Under Theorem~\ref{thm:markovcollar}, let \(\sigma_{ABD}\in \mathfrak M^{\mathrm{EC}}_{A:B:D}\) be EC-aligned exact Markov (Definition~\ref{def:ecaligned}), with normal form
\[
\sigma_{ABD}
=
\bigoplus_\alpha p_\alpha\,
\sigma^{(\alpha)}_{A b_L^\alpha}\otimes \sigma^{(\alpha)}_{b_R^\alpha D}.
\]
Let \(\tau^{(\alpha)}_{b_R^\alpha D'}\) be any normalized family of states compatible with the same right-boundary sectors, and define
\[
\sigma'_{AB D'}
=
\bigoplus_\alpha p_\alpha\,
\sigma^{(\alpha)}_{A b_L^\alpha}\otimes \tau^{(\alpha)}_{b_R^\alpha D'}.
\]
Define the common left algebra
\[
\mathcal A_{A b_L}:=
\bigoplus_\alpha \mathcal B(\mathcal H_{A b_L^\alpha})\otimes \mathbf 1_{b_R^\alpha},
\]
canonically represented on both direct-sum Hilbert spaces. Then:
\begin{enumerate}[leftmargin=2em]
\item for every \(X\in\mathcal A_{A b_L}\),
\[
\mathrm{Tr}(X\sigma'_{AB D'})=\mathrm{Tr}(X\sigma_{ABD});
\]
\item if \(\rho_{ABD}\) is any state on the same fixed collar and \(\sigma_{\mathrm{al}}\in\mathfrak M^{\mathrm{EC}}_{A:B:D}\) is an EC-aligned exact Markov state with
\[
\|\rho_{ABD}-\sigma_{\mathrm{al}}\|_1
\le
\delta_{\mathrm{al}},
\]
then the corresponding exact splice \(\sigma'_{\mathrm{al}}\) satisfies
\[
\left|
\mathrm{Tr}(X\rho_{ABD})-\mathrm{Tr}(X\sigma'_{\mathrm{al}})
\right|
\le
\|X\|_\infty\,\delta_{\mathrm{al}}
\]
for all \(X\in\mathcal A_{A b_L}\).
\end{enumerate}
The splice construction itself requires the EC-aligned normal form, so item 2 takes closeness to \(\mathfrak M^{\mathrm{EC}}_{A:B:D}\) as its input. Small conditional mutual information supplies closeness only to the larger set \(\mathfrak M_{A:B:D}\) via \(\delta^{\mathrm M}_{A:B:D}(\varepsilon)\); upgrading that to \(\delta_{\mathrm{al}}\to0\) is the Markov-split alignment hypothesis on the controlled family (Definition~\ref{def:ecaligned}, Remark~\ref{rem:hjpwalignment}). Hence the exact splice identity used by the compact-gauge branch is justified either at EC-aligned exact Markovity or along a controlled collar family admitting EC-aligned replacements with \(\delta_{\mathrm{al}}(\varepsilon_\delta)\to 0\).
\end{proposition}

\begin{proof}
For item 1, blockwise factorization gives
\[
\mathrm{Tr}(X\sigma'_{AB D'})
=
\sum_\alpha p_\alpha
\mathrm{Tr}\!\left(X_\alpha\sigma^{(\alpha)}_{A b_L^\alpha}\right)
\mathrm{Tr}\!\left(\tau^{(\alpha)}_{b_R^\alpha D'}\right).
\]
Here \(X_\alpha\) denotes the \(\alpha\)-block of \(X\) in \(\mathcal A_{A b_L}\). Each \(\tau^{(\alpha)}\) is normalized, so the second factor is \(1\). The same computation for \(\sigma_{ABD}\) gives the same value because the original right factor is likewise normalized.

For item 2, \(\sigma_{\mathrm{al}}\) is EC-aligned by hypothesis, so item 1 applies to it:
\[
\mathrm{Tr}(X\sigma'_{\mathrm{al}})=\mathrm{Tr}(X\sigma_{\mathrm{al}}).
\]
Therefore
\[
\left|
\mathrm{Tr}(X\rho_{ABD})-\mathrm{Tr}(X\sigma'_{\mathrm{al}})
\right|
=
\left|
\mathrm{Tr}\!\left[X(\rho_{ABD}-\sigma_{\mathrm{al}})\right]
\right|
\le
\|X\|_\infty\,\|\rho_{ABD}-\sigma_{\mathrm{al}}\|_1
\le
\|X\|_\infty\,\delta_{\mathrm{al}}.
\]
\end{proof}

\begin{proposition}[Transport of modular-additivity errors from the exact Markov reference]\label{prop:modulartransport}
Let \(K_X(\omega):=-\log \omega_X\) for a faithful reduced state on region \(X\), and define the modular defect
\[
\Delta K(\omega):=
K_{ABD}(\omega)-K_{AB}(\omega)-K_{BD}(\omega)+K_B(\omega).
\]
Fix a collar and let \(\rho\) be a faithful state with \(I(A:D\mid B)_\rho\le \varepsilon\). Choose \(\sigma_\varepsilon\in \mathfrak M_{A:B:D}\) with
\[
\|\rho-\sigma_\varepsilon\|_1\le \delta^{\mathrm M}_{A:B:D}(\varepsilon).
\]
Assume that the four marginals \(\rho_X\) and \((\sigma_\varepsilon)_X\) for \(X\in\{ABD,AB,BD,B\}\) all satisfy
\[
\rho_X\ge \lambda_\ast \mathbf 1,
\qquad
(\sigma_\varepsilon)_X\ge \lambda_\ast \mathbf 1
\]
on their supports for some \(\lambda_\ast>0\). Then
\[
\|\Delta K(\rho)-\Delta K(\sigma_\varepsilon)\|_\infty
\le
4\lambda_\ast^{-1}\,\delta^{\mathrm M}_{A:B:D}(\varepsilon).
\]
For any \(\sigma_\varepsilon\in\mathfrak M_{A:B:D}\), the operator \(\Delta K(\sigma_\varepsilon)\) is blockwise constant for the state's \emph{own} HJPW decomposition; it lies in the collar center \(Z(\mathcal A_{\mathrm{EC}}(B))\) exactly when \(\sigma_\varepsilon\) can be chosen EC-aligned, \(\sigma_\varepsilon\in\mathfrak M^{\mathrm{EC}}_{A:B:D}\), which is the Markov-split alignment hypothesis on the comparison family (Definition~\ref{def:ecaligned}). Under that hypothesis every matrix element of the modular defect of \(\rho\) is within \(4\lambda_\ast^{-1}\delta^{\mathrm M}_{A:B:D}(\varepsilon)\) of the EC-central exact Markov value.
\end{proposition}

\begin{proof}
By monotonicity of trace distance under partial trace,
\[
\|\rho_X-(\sigma_\varepsilon)_X\|_1
\le
\|\rho-\sigma_\varepsilon\|_1
\le
\delta^{\mathrm M}_{A:B:D}(\varepsilon)
\]
for each \(X\in\{ABD,AB,BD,B\}\). On the interval \([\lambda_\ast,1]\), the function \(\log x\) has derivative bounded by \(\lambda_\ast^{-1}\). By the standard integral representation of the operator logarithm, this implies the operator-norm Lipschitz bound
\[
\|K_X(\rho)-K_X(\sigma_\varepsilon)\|_\infty
=
\|\log (\sigma_\varepsilon)_X-\log \rho_X\|_\infty
\le
\lambda_\ast^{-1}\,\|\rho_X-(\sigma_\varepsilon)_X\|_\infty
\le
\lambda_\ast^{-1}\,\delta^{\mathrm M}_{A:B:D}(\varepsilon).
\]
Summing the four region contributions gives
\[
\|\Delta K(\rho)-\Delta K(\sigma_\varepsilon)\|_\infty
\le
4\lambda_\ast^{-1}\,\delta^{\mathrm M}_{A:B:D}(\varepsilon).
\]
For \(\sigma_\varepsilon\in \mathfrak M_{A:B:D}\), the exact HJPW block factorization implies that \(\Delta K(\sigma_\varepsilon)\) is blockwise constant on the blocks of the state's own HJPW decomposition; when \(\sigma_\varepsilon\in\mathfrak M^{\mathrm{EC}}_{A:B:D}\) those blocks are the edge-center blocks and \(\Delta K(\sigma_\varepsilon)\in Z(\mathcal A_{\mathrm{EC}}(B))\), so the same bound controls all matrix elements relative to the EC-central exact Markov modular-additivity value.
\end{proof}

\begin{theorem}[Finite-stage modular-defect propagation]\label{thm:modular-defect-propagation}
Consider a fixed finite branch calculation that uses \(N\) collar or strip
modular-additivity identities, followed by finitely many sums, products,
commutators with bounded operators, bounded functional-calculus operations on
a fixed spectral interval, and bounded-time modular transports. Replace the
\(j\)-th exact identity by its finite-stage controlled form with errors
\[
r_{\mathrm{FR}}(\varepsilon_j),\qquad
\delta^{\mathrm M}_j(\varepsilon_j),\qquad
\eta^{\mathrm{reg}}_j,
\]
where \(\eta^{\mathrm{reg}}_j\) denotes the regularized support-visible
transport remainder when no common full-algebra floor is used. Then every
bounded downstream modular observable \(O\) produced by that calculation obeys
\[
\left|
\langle O\rangle_{\mathrm{finite}}
-
\langle O\rangle_{\mathrm{exact}}
\right|
\le
\mathcal P_O\!\left(
\{r_{\mathrm{FR}}(\varepsilon_j)\}_{j=1}^N,
\{\delta^{\mathrm M}_j(\varepsilon_j)\}_{j=1}^N,
\{\eta^{\mathrm{reg}}_j\}_{j=1}^N
\right),
\]
for a polynomial-continuity modulus \(\mathcal P_O\) whose coefficients depend
only on the fixed collar models, the bounded-time interval, the operator norms,
and the declared faithful floors or regularization schedules. In particular
\(\mathcal P_O\to0\) as all listed errors tend to zero.
\end{theorem}

\begin{proof}
Induct over the expression tree defining \(O\). Sums and products are
controlled by triangle inequalities and submultiplicativity on the bounded
operator class. Commutators satisfy
\[
\|[A,B]-[A',B']\|
\le
\|A-A'\|\,\|B\|+\|A'\|\,\|B-B'\|
+\|B-B'\|\,\|A-A'\|,
\]
with all norms bounded on the fixed calculation. Bounded functional calculus
on a fixed spectral interval is uniformly continuous, and it is Lipschitz for
the logarithmic comparisons when the floor \(\lambda_\ast\) is present. For a
bounded-time modular transport generated by \(K\) and \(K'\), Duhamel's formula
gives
\[
\|e^{itK}Xe^{-itK}-e^{itK'}Xe^{-itK'}\|
\le
2|t|\,\|X\|\,\|K-K'\|+O(\|K-K'\|^2)
\]
uniformly for \(t\) in the chosen compact interval. When \(K-K'\) is not an
unregularized full-algebra bounded operator, Theorem~\ref{thm:regularized-modular-transport}
supplies the support-visible matrix-element replacement and its remainder
\(\eta^{\mathrm{reg}}_j\). Composing these finitely many continuity estimates
gives the displayed polynomial modulus.
\end{proof}

\begin{theorem}[Collar-locality of dimension-dependent constants]\label{thm:dimension-quarantine}
All constants used in exact-Markov replacement, logarithmic modular
comparison, regularized modular transport, and the finite-stage propagation of
modular defects are functions only of the declared fixed local collar model,
its support-visible dimension, the chosen faithful floor or regularization
schedule, the bounded observable class, and the bounded modular-time interval.
No estimate used in the BW/Lorentz/null-modular/Einstein branch requires a
dimension-free trace-norm stability theorem from small conditional mutual
information to exact Markov normal form for arbitrary tripartite quantum
systems.
\end{theorem}

\begin{proof}
The Fawzi--Renner term \(r_{\mathrm{FR}}\) is the only one-shot constructive
recoverability estimate used here, and it compares the state to a recovered
comparison state instead of the exact Markov set. The exact-Markov
replacement modulus \(\delta^{\mathrm M}\) is defined after pullback to one
fixed finite collar model; Theorem~\ref{thm:finite-collar-markov-stability}
gives a rate only on a fixed faithful collar class. Logarithmic comparison uses
the local floor \(\lambda_\ast\), while the BW branch avoids a refinement-uniform
full-algebra floor by using the regularized support-visible transport theorem.
The propagation theorem above then composes only those collar-local estimates.
\end{proof}

\begin{remark}[What is and is not carried forward]
There are therefore two distinct quantitative controls, and this paper keeps them separate:
\begin{enumerate}[leftmargin=2em]
\item the constructive one-shot recoverability bound \(r_{\mathrm{FR}}(\varepsilon)=O(\varepsilon^{1/2})\), which compares the physical state to a recovered comparison state and is enough for bounded-observable statements at one regulator stage;
\item the fixed-collar exact-Markov modulus \(\delta^{\mathrm M}_{A:B:D}(\varepsilon)\to 0\), which compares the physical state to the exact Markov set and is the correct quantity for justifying exact splice or modular-additivity identities in a controlled limit, with an additional factor \(4\lambda_\ast^{-1}\) when logarithms are involved.
\end{enumerate}
Later spatial and null collar theorems therefore use exact identities only in two regimes: literal exact Markovity, or a controlled refinement or scaling family in which the relevant \(\delta^{\mathrm M}(\varepsilon_\delta)\) tends to zero after transport to one fixed finite-dimensional collar model. The manuscript does \emph{not} claim a universal dimension-free one-shot trace-norm estimate from small conditional mutual information directly to an exact Markov state.
\end{remark}

\begin{remark}[Floor transfer to the exact-Markov reference]
On one fixed finite-dimensional collar model, Proposition~\ref{prop:modulartransport} does not require a second independent faithfulness input on the exact-Markov comparison family. Suppose the transported physical marginals satisfy
\[
\rho_X\ge \bar\lambda_{m,\delta}\mathbf 1
\]
for all sufficiently late stages for each \(X\in\{ABD,AB,BD,B\}\), and choose exact-Markov replacements \(\sigma_{n,m,\delta}\) with
\[
\|\rho_X-(\sigma_{n,m,\delta})_X\|_1
\le
\delta^{\mathrm M}_{m,\delta}(\varepsilon_{n,m,\delta})
\longrightarrow 0.
\]
Then \(\|\rho_X-(\sigma_{n,m,\delta})_X\|_\infty\le \|\rho_X-(\sigma_{n,m,\delta})_X\|_1\), so for all sufficiently large \(n\),
\[
(\sigma_{n,m,\delta})_X
\ge
\tfrac12\bar\lambda_{m,\delta}\mathbf 1.
\]
Thus a lower spectral bound, when available on a fixed collar model, is inherited by the exact-Markov reference once the exact-Markov modulus tends to zero. The support-visible theorem below does not require such a bound uniformly across the full refining matrix algebra.
\end{remark}

\begin{proposition}[Generalized-entropy split]\label{prop:gensplit}
If the reduced cap state takes the block form
\[
\rho_C=
\bigoplus_\alpha p_\alpha
\left(
\rho^{(\alpha)}_{\mathrm{bulk},C}\otimes
\frac{\mathbf 1^{(\alpha)}_{\mathrm{edge}}}{d_\alpha}
\right),
\]
then
\[
S(\rho_C)=S_{\mathrm{bulk}}(C)+\mathrm{Tr}(\rho_C L_C),
\]
where
\[
S_{\mathrm{bulk}}(C)=H(p_\alpha)+\sum_\alpha p_\alpha S(\rho^{(\alpha)}_{\mathrm{bulk},C}),
\qquad
L_C=\sum_\alpha (\log d_\alpha)P_\alpha.
\]
\end{proposition}

\begin{proof}
The entropy of a direct sum is
\[
S\!\left(\bigoplus_\alpha p_\alpha \sigma_\alpha\right)
=
H(p_\alpha)+\sum_\alpha p_\alpha S(\sigma_\alpha).
\]
Apply this identity with
\[
\sigma_\alpha=
\rho^{(\alpha)}_{\mathrm{bulk},C}\otimes
\frac{\mathbf 1^{(\alpha)}_{\mathrm{edge}}}{d_\alpha}.
\]
Since
\[
S(\sigma_\alpha)=S(\rho^{(\alpha)}_{\mathrm{bulk},C})+\log d_\alpha,
\]
the first statement follows.
\end{proof}

\begin{definition}[Effective Newton constant in the refinement dictionary]\label{def:newton}
In the refinement-scaling regime, if
\[
\mathrm{Tr}(\rho_C L_C)\approx N_\Sigma \bar\ell(t),
\qquad
A(\partial C)\approx N_\Sigma a_{\mathrm{cell}},
\]
then matching $\mathrm{Tr}(\rho_C L_C)$ to the area term \(A(\partial C)/(4G_{\mathrm{geom}})\) defines the geometric coupling
\[
G_{\mathrm{geom}}:=\frac{a_{\mathrm{cell}}}{4\bar\ell(t)}.
\]
This is a continuum dictionary identification. The area scale entering \(a_{\mathrm{cell}}\) is
supplied by the separate scale-readback fixed point, not by solving this equation for \(G\).
\end{definition}

\begin{proposition}[Shared edge-entropy identity on the realized product-group branch]\label{prop:sharededgeentropy}
On the realized product-group branch
\[
G_{\mathrm{phys}}
=
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6},
\]
let
\[
R=R_3\boxtimes R_2\boxtimes q
\]
be a lifted product presentation of one cut sector on the quotient branch, and let the
\(R\)-sector contribution of the collar edge-center entropy operator be
\[
\bigl(L_C\bigr)\!\mid_R=\log d_R.
\]
Then
\[
\bigl(L_C\bigr)\!\mid_R
=
L_C^{(3)}+L_C^{(2)},
\qquad
L_C^{(3)}:=\log d_{R_3},
\qquad
L_C^{(2)}:=\log d_{R_2},
\]
because every irreducible \( \U(1) \) representation is one-dimensional and contributes \(\log 1=0\). Consequently, on the product heat-kernel branch
\[
\ellbar_{\mathrm{shared}}
=
\langle L_C\rangle
=
\ellbar_{\mathrm{SU(3)}}(t_{3,\mathrm{run}})
+
\ellbar_{\mathrm{SU(2)}}(t_{2,\mathrm{run}}).
\]
If the same branch satisfies the D10 pixel law
\[
\ellbar_{\mathrm{SU(2)}}(t_{2,\mathrm{run}})
\;+\;
\ellbar_{\mathrm{SU(3)}}(t_{3,\mathrm{run}})
=
P/4,
\]
then
\[
\ellbar_{\mathrm{shared}}=P/4.
\]
\end{proposition}

\begin{proof}
For the lifted product presentation \(R=R_3\boxtimes R_2\boxtimes q\) of a sector on the quotient
branch,
\[
d_R=d_{R_3}d_{R_2}d_q.
\]
Every irreducible \( \U(1) \) representation is one-dimensional, so \(d_q=1\). Therefore
\[
\log d_R
=
\log d_{R_3}+\log d_{R_2}+\log d_q
=
\log d_{R_3}+\log d_{R_2}.
\]
This proves the sector identity
\[
\bigl(L_C\bigr)\!\mid_R=L_C^{(3)}+L_C^{(2)}.
\]
On the product heat-kernel branch, expectation values add, so
\[
\ellbar_{\mathrm{shared}}
=
\langle L_C\rangle
=
\ellbar_{\mathrm{SU(3)}}(t_{3,\mathrm{run}})
+
\ellbar_{\mathrm{SU(2)}}(t_{2,\mathrm{run}}).
\]
If the same branch satisfies the D10 pixel law, the right-hand side equals \(P/4\). \qedhere
\end{proof}

\begin{proposition}[Local scale-certificate package on the gravity row]\label{prop:gsi}
On the declared local extension surface, let the selected no-\(G\) scale certificate supply
\[
\gamma_\star=\frac{\ell_\star\nu_{\mathrm{Cs}}}{c},
\qquad
B_\star=\frac{3\pi}{\ell_\star^2}
\]
on the observation-located scale branch. Equivalently,
\(\ell_\star^2=3\pi/B_\star\). The local cell has the two readings
\[
a_{\mathrm{cell}}=P\ell_\star^2,
\qquad
\ellbar_{\mathrm{shared}}=\frac{P}{4}.
\]
Then the edge area law gives
\[
G_{\mathrm{geom}}
:=
\frac{a_{\mathrm{cell}}}{4\ellbar_{\mathrm{shared}}}
=
\ell_\star^2,
\qquad
G_{\mathrm{SI}}
=
\frac{c^3\ell_\star^2}{\hbar}.
\]
More generally, if \(\widehat L(P)\), \(\widehat T(P)\), \(\widehat E(P)\), and
\(\widehat\Theta(P)\) denote dimensionless branch outputs on that same local branch, then
\[
L_{\mathrm{loc}}=\sqrt{a_{\mathrm{cell}}}\,\widehat L(P),
\qquad
t_{\mathrm{loc}}=\frac{\sqrt{a_{\mathrm{cell}}}}{c_\star}\,\widehat T(P),
\]
\[
E_{\mathrm{loc}}=\frac{\hbar c_\star}{\sqrt{a_{\mathrm{cell}}}}\,\widehat E(P),
\qquad
\Theta_{\mathrm{loc}}=\frac{\hbar c_\star}{k_B\sqrt{a_{\mathrm{cell}}}}\,\widehat\Theta(P).
\]
Thus, at fixed \(P\), local lengths scale with \(a_{\mathrm{cell}}^{1/2}\) alone, local times
use that same \(a_{\mathrm{cell}}^{1/2}\) scale divided by the structural Lorentz output \(c_\star\),
and local mass/energy and temperature rows use the inverse \(a_{\mathrm{cell}}^{1/2}\) scale
dressed only by the familiar-unit display conventions \(\hbar\) and \(k_B\).
\end{proposition}

\begin{proof}
The OPH scale-readback map supplies \(\ell_\star^2\) before the Newton area-law readout is
evaluated. By Proposition~\ref{prop:sharededgeentropy},
\[
G_{\mathrm{geom}}
=
\frac{a_{\mathrm{cell}}}{4(P/4)}
=
\frac{a_{\mathrm{cell}}}{P}.
\]
Using the local cell-area reading \(a_{\mathrm{cell}}=P\ell_\star^2\), this becomes
\[
G_{\mathrm{geom}}=\ell_\star^2.
\]
The SI display relation is
\[
\ell_\star^2=\frac{\hbar G_{\mathrm{SI}}}{c^3},
\]
so
\[
G_{\mathrm{SI}}
=
\frac{c^3\ell_\star^2}{\hbar}.
\]
The following formulas are dimensional bookkeeping on the same declared local branch. Because \(P\)
is dimensionless and \(a_{\mathrm{cell}}\) is the only local microscopic area datum, every local
length readout is \(\sqrt{a_{\mathrm{cell}}}\) times a dimensionless branch quantity. The structural
Lorentz output \(c\) converts that same local ruler to seconds, while the familiar-unit display
constants \(\hbar\) and \(k_B\) convert the inverse local ruler to energy/mass rows and to Kelvin
rows. \qedhere
\end{proof}

Proposition~\ref{prop:splice} is the algebraic version of interior invariance under compatible exterior substitutions. Proposition~\ref{prop:modulartransport} is the precise bridge from small collar conditional mutual information to the exact modular identities later used by the spatial and null branches: at finite stage one carries a remainder, and exact identities appear only when that remainder is zero or tends to zero in the controlled collar limit. Proposition~\ref{prop:gensplit} isolates the exact entropy split, while Definition~\ref{def:newton} supplies the continuum identification that turns the edge center into a gravitational coupling.
Proposition~\ref{prop:sharededgeentropy} identifies the shared edge entropy on the realized product-group branch with the same \(\SU(2)+\SU(3)\) quantity used by the D10 pixel law, and Proposition~\ref{prop:gsi} makes the scale-readout cancellation and familiar-unit display explicit.

\section{Modular Geometry, Relativity, and Einstein Dynamics}\label{sec:gravity}

\subsection{Geometric modular flow}

Before stating the continuum modular theorem, fix the algebraic target. At fixed cutoff, the full operational patch algebra contains geometric overlap data, declared record summaries, and compare/write/verify pointer layers. The BW question should be asked only on the overlap-generated geometric subnet, not on the entire operational algebra.

\begin{definition}[Operational total algebra, geometric subnet, and auxiliary/record sector]\label{def:geosubnet}
At fixed cutoff \(n\) and patch \(P\), let \(\mathcal A_n^{\mathrm{tot}}(P)\) denote the operational patch algebra consisting of the physical patch algebra together with the declared overlap-readable summaries used by the compare/write/verify surface. Let \(B_{IJ}\subset P\) range over overlap collars incident on \(P\), let \(\Pi_\alpha^{(IJ)}\) denote the overlap sector projectors, and let \(Q_a^{(IJ)}\) denote the boundary observables carrying the geometric cut data. Define the geometric subnet by
\[
\mathcal A_n^{\mathrm{geo}}(P)
:=
W^\ast\!\Big\langle
\bigcup_{B_{IJ}\subset P}
\iota_{IJ\to P}\!\bigl(
\{\Pi_\alpha^{(IJ)}\}_\alpha\cup\{Q_a^{(IJ)}\}_a
\bigr)
\Big\rangle_{\mathrm{repair,isotony}}
\Big/
\mathcal N_n(P),
\]
where \(\mathcal N_n(P)\) is the maximal repair-invariant overlap-trivial kernel, namely the maximal part whose restriction to every overlap algebra inside \(P\) is scalar. The complementary operational sector generated by record summaries, pointer registers, and other interface-inert observables is denoted \(\mathcal A_n^{\mathrm{aux/rec}}(P)\).
\end{definition}

\begin{theorem}[Geometric subnet and operational primeness]\label{thm:geosubnet}
For each fixed-cutoff patch \(P\), the operational algebra admits a canonical quotient
\[
\pi_{n,P}^{\mathrm{geo}}:\mathcal A_n^{\mathrm{tot}}(P)\twoheadrightarrow \mathcal A_n^{\mathrm{geo}}(P)
\]
with the following properties:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2em]
\item \(\mathcal A_n^{\mathrm{geo}}(P)\) is generated by the overlap sector projectors and geometric boundary observables, and is closed under repair and isotony;
\item the record-summary block, pointer algebra, and interface-inert auxiliary observables lie in the complementary operational sector \(\mathcal A_n^{\mathrm{aux/rec}}(P)\) and do not enlarge \(\mathcal A_n^{\mathrm{geo}}(P)\);
\item if \(N\subset \mathcal A_n^{\mathrm{geo}}(P)\) is a repair-invariant subalgebra whose restriction to every overlap algebra inside \(P\) is scalar, then \(N=\mathbb C\,\mathbf 1\).
\end{enumerate}
\end{theorem}

\begin{proof}
Items \textup{(i)} and \textup{(ii)} are the content of Definition~\ref{def:geosubnet}. For item \textup{(iii)}, if such an \(N\) were nontrivial, then its pullback under \(\pi_{n,P}^{\mathrm{geo}}\) would define a nontrivial repair-invariant overlap-trivial component of \(\mathcal A_n^{\mathrm{tot}}(P)\), contradicting the maximality of \(\mathcal N_n(P)\). Thus no nontrivial overlap-trivial factor survives inside \(\mathcal A_n^{\mathrm{geo}}(P)\).
\end{proof}

The collar analysis proves a fixed-cutoff statement on the finite type-I regulator net: the reduced cap state has a literal density matrix, its modular Hamiltonian exists, and its nonadditive part is confined to a shrinking collar up to carried errors. The Lorentz claim is therefore not a literal statement about the finite regulator matrices. The target object is a support-visible realized scaling-limit geometric cap pair
\[
(\mathcal A_\infty^{\mathrm{geo}}(C),\omega_\infty^{\mathrm{geo},C})
\]
for each round cap \(C\subset S^2\). Axiom~\ref{ax:maxent} controls the state-side realized branch across refinement through one common finite-dimensional MaxEnt family, and Theorem~\ref{thm:geosubnet} removes the overlap-trivial auxiliary/record layers from the BW target. The theorem below uses support-visible regularized modular transport and the finite cap-normal BW certificate of Theorem~\ref{thm:finite-cap-bw-certificate}. The analytic modular-transport branch is closed under the stated regularization and multiresolution hypotheses; geometric BW identification additionally requires the cap-normal, support-order, cross-ratio, mixed-GNS, and geometric \(2\pi\)-KMS certificate.

Fix a cap \(C\subset S^2\) and a shrinking collar family \((A_\delta,B_\delta,D_\delta)\) around \(\partial C\), with \(\delta\downarrow 0\) and \(A_\delta\cup B_\delta\cup D_\delta\) covering a neighborhood of the cut. Write
\[
\varepsilon_\delta:=I(A_\delta:D_\delta\mid B_\delta)_\omega,
\qquad
r_{\mathrm{FR}}(\varepsilon_\delta):=
2\sqrt{1-e^{-\varepsilon_\delta}}
\le 2\sqrt{\varepsilon_\delta},
\]
and, on each fixed faithful collar model,
\[
\eta_\delta^{\mathrm M}
:=
4\lambda_\ast^{-1}\,
\delta^{\mathrm M}_{A_\delta:B_\delta:D_\delta}(\varepsilon_\delta),
\]
where \(\lambda_\ast>0\) is the lower spectral bound used to compare modular Hamiltonians. Every exact collar identity below is therefore to be read in one of two ways:
\begin{enumerate}[leftmargin=2em]
\item literal exactness when the reference collar state is exact Markov; or
\item a controlled collar family for which
\[
\delta^{\mathrm M}_{A_\delta:B_\delta:D_\delta}(\varepsilon_\delta)\to 0
\qquad(\delta\downarrow 0),
\]
with the finite-stage errors \(r_{\mathrm{FR}}(\varepsilon_\delta)\) and \(\eta_\delta^{\mathrm M}\) carried explicitly.
\end{enumerate}

On the finite-range conditional-mixing branch, Theorem~\ref{thm:collar-cmi-decay} supplies
\(\varepsilon_\delta\le c|\partial C|_{\mathrm{UV}}e^{-\delta/\xi}\). Vanishing of this
quantity uses the full rate condition of Corollary~\ref{cor:collar-cmi-double-scaling}; the ratio
\(\delta/\ell_{\mathrm{UV}}\to\infty\) without boundary-count control is not used below.

For each cap \(C\), let \(\lambda_C(s)\subset \Conf^+(S^2)\) denote the standard cap-preserving conformal one-parameter subgroup, normalized so that the null blow-up near a smooth cut acts by \(v\mapsto e^{-s}v\), and let \(\alpha_{\lambda_C(s)}\) denote the induced automorphism of the scaling-limit cap net.

\subsubsection{Finite cap-normal certificate for the support-visible BW limit}

\begin{definition}[Oriented cap normal and BW frame]\label{def:bw-framed-cap}
Identify \(\Omega\in S^2\) with the future null ray \(q(\Omega)=(1,\Omega)\in\mathbb R^{3,1}\),
with \(\eta(x,y)=-x^0y^0+\mathbf x\cdot\mathbf y\). For a round cap
\[
C=C(u,\theta)=\{\Omega:u\cdot\Omega\ge\cos\theta\},
\qquad 0<\theta<\pi,
\]
define its oriented spacelike normal by
\[
n_C=(\cot\theta,\csc\theta\,u).
\]
Then \(\eta(n_C,n_C)=1\) and
\[
\eta(n_C,q(\Omega))=\frac{u\cdot\Omega-\cos\theta}{\sin\theta},
\]
so \(C=\{\Omega:\eta(n_C,q(\Omega))\ge0\}\). The sign reversal \(n_C\mapsto -n_C\)
selects the complementary cap. A nondegenerate cap class fixes
\[
\theta_0\le \theta\le \pi-\theta_0,\qquad 0<\theta_0<\frac{\pi}{2},
\]
so the cap-normal map lands in a compact subset of de Sitter space
\(\{n:\eta(n,n)=1\}\).

A BW-framed cap is
\[
\widehat C=(C,n_C,p_C^-,p_C^+),
\]
where \(p_C^\pm\in\partial C\) are distinct ordered boundary points. Choose any
orientation-preserving M\"obius map \(h_{\widehat C}\) with
\[
h_{\widehat C}(C)=\mathbb H,\qquad
h_{\widehat C}(p_C^-)=0,\qquad
h_{\widehat C}(p_C^+)=\infty .
\]
The independently normalized geometric cap flow is
\[
\lambda_{\widehat C}(s)(z)
=h_{\widehat C}^{-1}(e^{-s}h_{\widehat C}(z)).
\]
This parameter \(s\) is geometric; it is not the modular parameter \(t\).
\end{definition}

\begin{definition}[Finite cap-normal BW certificate]\label{def:finite-cap-bw-certificate}
A cofinal regulator branch carries \(\mathsf{FiniteCapBWCertificate}\) when it supplies the
following primitive data and vanishing envelopes on the support-visible prime geometric subnet:
\begin{enumerate}[label=\textup{C\arabic*.},leftmargin=2.4em]
\item cap and point meshes with \(h_r^{\mathrm{cap}}\to0\), \(h_r^{\mathrm{pt}}\to0\), unit
cap-normal residuals tending to zero, nondegenerate cap radii, boundary-incidence control, and
refinement-compatible cap normals;
\item ordered BW frame points \(p_C^-,p_C^+\) on every anchor cap, with frame separation and
orientation bounded away from degeneration;
\item finite cap algebras satisfying isotony, support-order separation, and a support-visible
automorphism quotient whose cap-support action is faithful;
\item the exact modular-compatible reference tower and the cap-family-uniform compact-time
regularized modular bound of Theorem~\ref{thm:strong-local-modular-scaling};
\item mixed-GNS Cauchy residuals and support-covariance residuals tending to zero uniformly on
compact modular-time intervals, with both \(t\) and \(-t\) controlled;
\item approximate identity, inverse, and group-law residuals for the finite support flow,
compact-time equicontinuity, anchor-cap/frame preservation, held-out complex cross-ratio
convergence on separated quartets, and an orientation witness excluding anti-M\"obius limits;
\item an independently parameterized geometric \(2\pi\)-KMS strip residual tending to zero, with
uniform strip bounds and refinement-compatible matrix elements;
\item nontriviality plus either a wrong-\(\beta\) lower gap on a predeclared interval or the
finite type-I generator-distance/noncentrality bound
\[
\inf_{Z\in Z(M_r(C))_{\mathrm{sa}}}
\|K_{r,C}^{(a_r)}-2\pi B_{r,C}-Z\|_{2,\omega_r}\to0,
\qquad
\inf_{Z\in Z(M_r(C))_{\mathrm{sa}}}\|B_{r,C}-Z\|_{2,\omega_r}\ge v_\ast>0 .
\]
\end{enumerate}
The certificate is a branch hypothesis. This paper does not prove
\[
\mathsf{BareFiniteOPHConsensus}\Longrightarrow \mathsf{FiniteCapBWCertificate}.
\]
That production implication belongs to the Einstein branch-entry program.
\end{definition}

\begin{proposition}[Why the certificate clauses are necessary]\label{prop:bw-certificate-countermodels}
The certificate cannot be compressed to cap normals, finite cap IDs, ordinary KMS language, or
pointwise weak matrix convergence.
\end{proposition}

\begin{proof}
First, a round cap and its oriented normal determine the cap but not a cap-preserving
one-parameter subgroup. After conjugating the cap to the disk, its orientation-preserving
stabilizer is \(\mathrm{PSU}(1,1)\), which contains elliptic, hyperbolic, and parabolic
one-parameter subgroups. The ordered boundary frame is the extra datum selecting the BW axis and
direction.

Second, a finite cap-ID set cannot carry a nontrivial continuous boost as permutations. Every
continuous homomorphism \(\mathbb R\to\operatorname{Sym}(\mathcal C_r)\) is constant because
\(\mathbb R\) is connected and \(\operatorname{Sym}(\mathcal C_r)\) is discrete. A finite
simulator may sample and project a continuous cap flow, but the projection must carry mesh error.

Third, modular KMS alone does not pick \(2\pi\). If \(\sigma_t^\omega\) is the modular group, then
\(\alpha_s^{(\kappa)}=\sigma_{s/\kappa}^\omega\) makes \(\omega\) a \(\kappa\)-KMS state for
every \(\kappa>0\). The value \(2\pi\) is fixed only after the geometric parameter \(s\) has been
normalized independently and the state is shown to be \(2\pi\)-KMS for that geometric flow.

Fourth, pointwise weak matrix convergence does not preserve automorphisms: on \(\ell^2(\mathbb Z)\),
the bilateral shifts \(S^n\) are unitary but converge weakly to \(0\). The quadratic mixed-GNS
Cauchy residual and inverse-time control prevent this collapse.
\end{proof}

\begin{theorem}[Finite cap-net convergence to the support-visible BW automorphism]\label{thm:finite-cap-bw-certificate}
Let \((\mathfrak B_r)_{r\in I}\) be a cofinal family of finite cap-normal BW systems satisfying
\(\mathsf{FiniteCapBWCertificate}\). Then every nondegenerate BW-framed cap \(\widehat C\) has a
unique support-visible prime geometric scaling-limit cap pair
\[
(\mathcal A_\infty^{\mathrm{geo,sv}}(C),\omega_\infty^{\mathrm{geo},C})
\]
and
\[
\boxed{\;
\sigma_t^{\omega_\infty^{\mathrm{geo},C}}
=
\alpha_{\lambda_{\widehat C}(2\pi t)} .
\;}
\]
Moreover, for every compact modular-time interval and every fixed support-visible test triple,
the finite transported regularized modular matrix elements converge to the BW matrix elements:
\[
\sup_{|t|\le T}
\left|
\omega_r(B_r^\ast\tau_t^{r,C_r}(A_r)D_r)
-
\omega_\infty(B^\ast\alpha_{\lambda_{\widehat C}(2\pi t)}(A)D)
\right|\to0 .
\]
Cap inclusion, round-cap structure, and complex cross-ratios of separated quartets are preserved.
If the limiting cap algebra is type I, the inner-generator specialization is
\[
K_C=2\pi B_C+Z_C,\qquad Z_C\in Z(\mathcal A(C))_{\mathrm{sa}},
\]
and in a factor \(Z_C=c_C\mathbf1\). No density-matrix generator identity is asserted in the
generic non-type-I case.
\end{theorem}

\begin{proof}
The mixed-GNS Cauchy residual and the exact reference tower produce a unique strongly continuous
unitary implementation of the limiting modular automorphism group on the support-visible GNS
direct limit. Support covariance and support-order separation make the modular image of every
test-cap algebra read as a unique cap-support flow, while the approximate identity, inverse, and
group-law residuals pass to the limit.

Cap-normal compactness gives round-cap limits, and support-order reflection preserves cap
inclusion. Held-out complex cross-ratio convergence on dense point meshes, with conditioned
anchors and an orientation witness, forces every support-flow cluster limit to lie in
\(\mathrm{PSL}(2,\mathbb C)\). Since the flow preserves the anchor cap and the ordered boundary
frame, framed-cap rigidity gives
\[
f_t^C=\lambda_{\widehat C}(\kappa_C t)
\]
for a unique \(\kappa_C>0\).

The geometric strip residual, normal-family bound, and refinement-compatible geometric matrix
elements pass the \(2\pi\)-KMS condition to the limiting independently normalized geometric flow.
KMS uniqueness for a faithful normal state gives
\[
\sigma_t^{\omega_\infty^{\mathrm{geo},C}}
=\alpha_{\lambda_{\widehat C}(2\pi t)}.
\]
The wrong-\(\beta\) gap excludes any fixed normalization separated from \(2\pi\), while
nontriviality excludes the only exact multiple-temperature exception. Since every convergent
subnet has the same BW limit, compactness upgrades subnet convergence to convergence of the
cofinal branch. The type-I generator statement follows because two inner implementations of the
same automorphism differ by a central self-adjoint term.
\end{proof}

\begin{corollary}[Geometric modular action on certified caps]\label{cor:certified-cap-modular-action}
Let
\[
(\mathcal A_\infty^{\mathrm{geo,sv}}(C),\omega_\infty^{\mathrm{geo},C})
\]
be a scaling-limit cap pair emitted by Theorem~\ref{thm:finite-cap-bw-certificate}. Then
\[
\sigma_t^{\omega_\infty^{\mathrm{geo},C}}
=
\alpha_{\lambda_{\widehat C}(2\pi t)}.
\]
If the limit cap algebra is type I, this may be represented as
\[
K_C=2\pi B_C+Z_C,\qquad Z_C\in Z(\mathcal A(C))_{\mathrm{sa}}.
\]
In the generic non-type-I case, the automorphism identity is the complete statement.
\end{corollary}

\begin{remark}[BW is a conditional scaling-limit branch]\label{rem:bw-conditional-branch}
The Lorentz/BW statement is not ``finite cells imply Lorentz invariance.''  The branch theorem is
the conditional implication
\[
\begin{gathered}
\mathsf{FiniteCapBWCertificate}\\
\Longrightarrow
\sigma_t^{\omega_\infty^{\mathrm{geo},C}}
=
\alpha_{\lambda_{\widehat C}(2\pi t)} .
\end{gathered}
\]
The certificate includes support-visible cap-pair extraction, cap-family-uniform regularized
modular transport, support-readable covariance, framed-cap/cross-ratio rigidity, independently
normalized geometric \(2\pi\)-KMS convergence, and wrong-normalization controls. Finite type-I
regulators supply collar control and regularized support-visible matrix elements; they do not make
the full finite operational algebra, pointer/record sectors, or off-support directions Lorentz
covariant, and bare finite consensus does not by itself produce this certificate.
\end{remark}

\begin{proposition}[Support-visible cap-pair extraction on the local GNS support quotient]\label{prop:cap-pair-extraction}
Fix a round cap \(C\subset S^2\). Under Axioms~\ref{ax:screen}--\ref{ax:entropy}, Theorem~\ref{thm:geosubnet}, and the derived fixed-cutoff regulator/collar/consensus package, consider the transported geometric cap-local test family on \(\mathcal A_n^{\mathrm{geo}}(C_n)\), its projectively compatible transported marginals, the asymptotic transport-equivalence certificate, and a cutoff schedule satisfying Theorem~\ref{thm:regularized-modular-transport}. Along a cofinal refinement subnet:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2em]
\item the transported cap marginals admit local weak-\(*\) limits on every support-visible geometric cap subalgebra;
\item the compatible local limits glue to a state on \(\mathcal A_\infty^{\mathrm{geo,sv}}(C)\);
\item the GNS representation gives a cap pair
\[
(\mathcal A_\infty^{\mathrm{geo,sv}}(C),\omega_\infty^{\mathrm{geo},C})
\]
faithful on the local support quotient, and the regularized support-visible modular matrix elements converge to its modular automorphism group.
\end{enumerate}
\end{proposition}

\begin{proof}
For each fixed local collar model, the finite-stage state spaces are weak-\(*\) compact. The transported marginal family is projectively compatible up to the refinement-equivalence certificate supplied by the consensus package, so the usual diagonal subnet argument gives compatible local weak-\(*\) limits on the cap-local test family. Theorem~\ref{thm:regularized-modular-transport} controls the regularized modular matrix elements on every bounded support-visible collar observable under the stated cutoff schedule. Passing to the GNS representation of the glued state quotients the null directions and leaves a faithful representation on the local support. This gives the displayed support-visible cap pair and its modular automorphism group.
\end{proof}

\begin{lemma}[Support-readable modular covariance]\label{lem:support-readable-modular-covariance}
Let \((\mathcal A_\infty^{\mathrm{geo,sv}}(C),\omega_\infty^{\mathrm{geo},C})\) be the cap pair
of Proposition~\ref{prop:cap-pair-extraction}. Assume the extracted support-visible prime
geometric subnet satisfies outer regularity / minimal support: for every cap-local observable
\(O\), the intersection of all connected regions \(P\) with
\(O\in\mathcal A_\infty^{\mathrm{geo,sv}}(P)\) is again a connected region, denoted
\(\operatorname{supp}(O)\). For every connected cap-local region \(R\subset C\), define
\[
f_t^C(R)
:=
\bigcup_{O\in\mathcal A_\infty^{\mathrm{geo,sv}}(R)}
\operatorname{supp}\!\left(\sigma_t^{\omega_\infty^{\mathrm{geo},C}}(O)\right).
\]
Then the modular automorphism group induces a one-parameter support map on cap-local regions:
\[
\sigma_t^{\omega_\infty^{\mathrm{geo},C}}
\!\left(\mathcal A_\infty^{\mathrm{geo,sv}}(R)\right)
=
\mathcal A_\infty^{\mathrm{geo,sv}}\!\left(f_t^C(R)\right).
\]
\end{lemma}

\begin{proof}
The modular group is an automorphism group of the cap algebra. By outer regularity / minimal
support, the support of each cap-local observable is readable from the net labeling after GNS
quotienting of null directions. Thus the displayed definition of \(f_t^C(R)\) is intrinsic to the
support-visible net. The inclusion ``\(\subseteq\)'' follows by construction. Applying the same
argument to the inverse automorphism \(\sigma_{-t}^{\omega_\infty^{\mathrm{geo},C}}\) gives the
reverse inclusion, hence equality.
\end{proof}

\begin{theorem}[Projective Markov replacement compatibility]\label{thm:projective-markov-replacement}
Let \(\rho_n\) be a cofinal refinement family, and let \(R_{n\to m}\) denote
restriction to a fixed local collar model \(m\). Suppose that for each fixed
\(m\)
\[
I(A_m:D_m\mid B_m)_{R_{n\to m}\rho_n}\le \varepsilon_{n,m},
\qquad
\delta^{\mathrm M}_{m}(\varepsilon_{n,m})\to0
\quad(n\to\infty),
\]
and suppose the finite-stage restriction maps commute with the physical
quotient and normal-form maps up to the declared refinement-equivalence
certificate. Then, after passing to a cofinal subnet, one can choose exact
Markov replacements \(\sigma_{n,m}\in\mathfrak M_m\) such that for every fixed
\(k\le m\),
\[
\|R_{m\to k}\sigma_{n,m}-\sigma_{n,k}\|_1\to0.
\]
Hence the exact-Markov comparison states define a projective support-visible
Markov comparison class in the scaling limit.
\end{theorem}

\begin{proof}
For each fixed \(m\), Proposition~\ref{prop:controlledmarkov} gives exact
Markov replacements within
\(\delta^{\mathrm M}_{m}(\varepsilon_{n,m})+o(1)\) of \(R_{n\to m}\rho_n\).
The exact Markov sets \(\mathfrak M_m\) are compact on fixed collars, so a
diagonal subnet has limits on every fixed \(m\). Restriction maps are
continuous and, by hypothesis, commute with the physical quotient and normal
form up to the same refinement-equivalence certificate used by the cap-local
test family. Therefore the restriction of the \(m\)-limit to a smaller fixed
collar \(k\) agrees with the \(k\)-limit. Pulling the chosen approximants along
the diagonal subnet gives the displayed asymptotic compatibility.
\end{proof}

\begin{proposition}[Framed-cap rigidity from surviving cut data]\label{prop:round-cap-rigidity}
Let \(\widehat C=(C,n_C,p_C^-,p_C^+)\) be a BW-framed cap, and let the cap pair be the
support-visible extracted pair of Proposition~\ref{prop:cap-pair-extraction}. Assume the modular
support map of Lemma~\ref{lem:support-readable-modular-covariance} acts by orientation-preserving
conformal maps on the support-visible cap geometry and preserves the anchor cap and its ordered
boundary frame. Then any continuous one-parameter subgroup preserving this framed data is
\(\lambda_{\widehat C}(\kappa t)\) for a unique \(\kappa>0\).
\end{proposition}

\begin{proof}
Choose the M\"obius map \(h_{\widehat C}\) of Definition~\ref{def:bw-framed-cap}. The
orientation-preserving conformal maps of the upper half-plane preserving \(0\) and \(\infty\)
individually are exactly \(z\mapsto a z\), \(a>0\). For a continuous one-parameter group,
\(a(t+s)=a(t)a(s)\), so \(a(t)=e^{-\kappa t}\) after the declared frame orientation fixes the sign.
Transporting this subgroup back to \(C\) gives \(\lambda_{\widehat C}(\kappa t)\). Uniqueness of
\(\kappa\) follows from nontriviality of the dilation subgroup. The cap normal alone is not enough:
it fixes the cap side, not the ordered boundary fixed points.
\end{proof}

\begin{theorem}[Finite cap-net support-visible BW scaling theorem]\label{thm:bw}
Assume Axioms~\ref{ax:screen}--\ref{ax:entropy}, Theorem~\ref{thm:geosubnet}, and the derived fixed-cutoff regulator/collar/consensus package established above. Assume also that the cofinal branch carries the finite cap-normal BW certificate of Definition~\ref{def:finite-cap-bw-certificate}: cap-normal density and nondegeneracy, BW framing, support-order faithfulness, cap-family-uniform mixed-GNS modular convergence, support covariance, held-out oriented cross-ratio convergence, independently normalized geometric \(2\pi\)-KMS convergence, and wrong-normalization separation. For each OPH-realized observer-supporting refinement branch and each nondegenerate BW-framed cap \(\widehat C=(C,n_C,p_C^-,p_C^+)\), the support-visible prime geometric cap net admits a weak-\(*\)/GNS scaling-limit cap pair
\[
(\mathcal A_\infty^{\mathrm{geo,sv}}(C),\omega_\infty^{\mathrm{geo},C}).
\]
Then:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2em]
\item At each finite regulator stage, the cap algebra is type I, the reduced cap state has a density matrix \(\rho_C^{(\delta)}\), and its modular Hamiltonian
\[
K_C^{(\delta)}:=-\log \rho_C^{(\delta)}
\]
has nonadditive part confined to the shrinking collar up to the carried errors measured by \(r_{\mathrm{FR}}(\varepsilon_\delta)\), the fixed-collar replacement modulus \(\delta^{\mathrm M}\), and the regularized support-visible modular transport bound of Theorems~\ref{thm:regularized-modular-transport} and \ref{thm:support-visible-modular-convergence}. In particular, on each fixed collar model the physical collar state differs from its constructive recovered comparison state by \(r_{\mathrm{FR}}(\varepsilon_\delta)\) in trace norm, and the support-visible modular matrix elements converge under the displayed cutoff schedule independently of the exact-Markov replacement sequence.

\item For every bounded support-visible cap-local observable \(O\), the regularized modular
matrix elements converge in the local weak-\(*\)/GNS support-quotient topology supplied by
Proposition~\ref{prop:cap-pair-extraction}. The convergence is controlled by the explicit error
budget
\[
r_{\mathrm{FR}}(\varepsilon_\delta),\qquad
\delta^{\mathrm M}_{A_\delta:B_\delta:D_\delta}(\varepsilon_\delta),\qquad
\frac{\Delta_\delta}{a_\delta},\qquad
d_{m,\delta}a_\delta,\qquad
\Delta_\delta|\log a_\delta|,
\]
which vanishes under the stated Markov-replacement and cutoff schedule.

\item On the support-visible scaling-limit cap pair, the modular automorphism group is geometric:
\[
\sigma_t^{\omega_\infty^{\mathrm{geo},C}}
=
\alpha_{\lambda_{\widehat C}(2\pi t)}.
\]
Equivalently, the modular parameter \(t\) and the geometric cap-dilation parameter \(s\) are related by
\[
s=2\pi t.
\]

\item No separate cap-isotropy/\(\mathrm{SO}(2)\)-equivariance selector, finite-cell Lorentz-invariance premise, or unregularized full-algebra common floor is used in this theorem. The conformal support-map regularity, framed-cap/cross-ratio rigidity, and geometric \(2\pi\)-KMS normalization are explicit certificate clauses, not hidden finite-regulator Lorentz premises. The target algebra is the support-visible prime geometric subnet.

\item If the scaling-limit cap algebra happens to be type I, item \textup{(iii)} may be written as the operator identity
\[
K_C=2\pi B_C+Z_C,\qquad Z_C\in Z(\mathcal A(C))_{\mathrm{sa}}.
\]
If the cap algebra is a factor, \(Z_C=c_C\mathbf1\). In the generic continuum case, where the scaling-limit cap algebra has left the regulator class and is expected in QFT examples to be non-type-I, the correct theorem statement is item \textup{(iii)} itself, and the geometric modular action is generally outer instead of inner.
\end{enumerate}

Consequently, on a branch carrying the multiresolution regulator certificate of
Assumption~\ref{ass:multiresolution-regulator-certificate}, the transported regularized modular
action on every fixed support-visible geometric local algebra converges uniformly on compact
modular-time intervals to the geometric cap-dilation action. Without that certificate, the theorem
identifies only the scaling-limit cap-pair modular automorphism. It does not assert compact-time
convergence of finite-regulator modular groups beyond the stated certificate, a refinement-uniform unregularized spectral floor
for every off-support direction of the full finite matrix algebra, or Lorentz covariance for
record/pointer or interface-inert auxiliary registers outside the extracted geometric subnet.
\end{theorem}

\begin{proof}
Step 1: fixed-cutoff collar control. On the finite type-I regulator net, Propositions~\ref{prop:splice}, \ref{prop:modulartransport}, and \ref{prop:gensplit} localize the modular defect to the shrinking collar and quantify the discrepancy between the physical collar state, its constructive recovered comparison state, and its exact-Markov reference by the carried errors \(r_{\mathrm{FR}}(\varepsilon_\delta)\) and \(\eta_\delta^{\mathrm M}\).

Step 2: support-visible regularization. Proposition~\ref{prop:commonfloor-collapse} shows that a refinement-uniform common floor on the full finite matrix algebra is unavailable in general. Theorem~\ref{thm:regularized-modular-transport} supplies the needed replacement: for \(K_a(\rho)=-\log(\rho+a\mathbf1)\) and bounded support-visible collar observables, the modular matrix-element difference is bounded by
\[
\|O\|\left(\frac{4\Delta_n}{a}+d_{m,\delta}a+4\Delta_n|\log a|\right).
\]
Choosing \(a_n\downarrow0\) with \(\Delta_n/a_n\to0\), \(d_{m,\delta}a_n\to0\), and \(\Delta_n|\log a_n|\to0\) makes the right-hand side vanish on every fixed local collar model. Theorems~\ref{thm:projective-markov-replacement} and \ref{thm:support-visible-modular-convergence} then make the exact-Markov comparison family projectively compatible and replacement-independent on support-visible observables. Thus the theorem concerns the support-visible scaling limit instead of off-support full-algebra directions.

Step 3: scaling-limit cap-pair extraction. Theorem~\ref{thm:geosubnet} fixes the target algebra as the overlap-generated prime geometric subnet, with overlap-trivial auxiliary/record factors removed. Proposition~\ref{prop:cap-pair-extraction} supplies the support-visible weak-\(*\)/GNS cap pair from the transported cap-local test family, the projectively compatible marginal family, the asymptotic transport-equivalence certificate, and the regularized modular transport cutoff schedule.

Step 4: certificate-level geometric identification on the prime subnet. Lemma~\ref{lem:support-readable-modular-covariance} makes the modular automorphism group induce a support map on cap-local regions of the extracted prime geometric subnet. The finite cap-normal certificate supplies support-order faithfulness, cap-frame preservation, held-out complex cross-ratio convergence, orientation preservation, and compact-time equicontinuity. By Theorem~\ref{thm:finite-cap-bw-certificate}, the limiting support flow is the framed cap flow. Thus
\[
\sigma_t^{\omega_\infty^{\mathrm{geo},C}}=\alpha_{\lambda_C(\kappa_C t)}.
\]
with the certificate-selected frame understood in the notation \(\lambda_C\).

Step 5: normalization. The certificate does not use the false shortcut that modular KMS alone
selects \(2\pi\). Instead, its independently normalized geometric strip residual passes the
\(2\pi\)-KMS condition to \(s\mapsto\alpha_{\lambda_{\widehat C}(s)}\), and KMS uniqueness gives
\[
\sigma_t^{\omega_\infty^{\mathrm{geo},C}}
=
\alpha_{\lambda_{\widehat C}(2\pi t)}.
\]
The wrong-\(\beta\) gap excludes every fixed normalization separated from \(2\pi\), and
nontriviality excludes the only exact multiple-temperature exception.

Step 6: operator versus automorphism form. If the limit cap algebra is type I, one can represent the modular automorphism group by a modular Hamiltonian \(K_C=-\log\rho_C\) and a geometric generator \(B_C\). Equality of the implemented automorphisms gives \(K_C=2\pi B_C+Z_C\) for a central self-adjoint \(Z_C\). If the limit algebra leaves the regulator class, the modular automorphism group is well defined while the inner operator representative need not exist inside \(\mathcal A_\infty^{\mathrm{geo,sv}}(C)\). In that case the automorphism identity is the full theorem statement. This is exactly the observer-facing content needed for Lorentz kinematics, the null half-sided modular bridge, and the local Einstein branch.
\end{proof}

\begin{remark}[Finite modular-flow core versus BW geometry]\label{rem:finite-modular-flow-core}
At finite regulator and on finite-dimensional faithful cap algebras, the
modular clock itself has a purely algebraic core: a positive density matrix
\(\rho\) has a modular Hamiltonian \(H=-\log\rho\), the maps
\[
\sigma_z(A)=e^{-izH}Ae^{izH}
\]
form a complex-parameter automorphism family, real \(z=t\) gives the
one-parameter \(^*\)-automorphism flow, the state is invariant under the flow,
and the \(z=-i\) boundary value is the modular operator appearing in the KMS
identity.  The OPHProofChain finite Lean audit formalizes this
matrix-algebra core, including
the KMS boundary condition and uniqueness within Hamiltonian-implemented flows
up to the additive scalar in \(H\).

This finite result is not the BW theorem.  It proves that the finite
density-matrix modular object really is a real-time modular flow.  The OPH
physics in Theorem~\ref{thm:bw} is the additional support-visible scaling-limit
identification of that modular flow with the geometric cap-dilation subgroup
\(\alpha_{\lambda_C(2\pi t)}\).
\end{remark}

\begin{definition}[BW-branch observer-relative time reading]\label{def:modulartime}
On the branch satisfying the hypotheses of Theorem~\ref{thm:bw}, OPH uses the modular
automorphism parameter \(t\) of the extracted cap pair
\((\mathcal A_\infty^{\mathrm{geo}}(C),\omega_\infty^{\mathrm{geo},C})\) as that cap
observer's relative time parameter. This is a declared BW-branch reading of the geometric
modular flow derived in Theorem~\ref{thm:bw}; it is not an additional proof that arbitrary
operational clocks, global time, or the full problem of time have been derived from the axioms.
\end{definition}

\begin{remark}[BW-side UV scaffold after the geometric-subnet split]
Theorem~\ref{thm:geosubnet} fixes the target algebra: the continuum Lorentz claim is asked only on the support-visible extracted prime geometric subnet, not on the full operational algebra. Record/pointer/interface-inert observables are outside that geometric subnet, and off-support directions that disappear in the limiting GNS support are not observer-facing data.

The transported geometric cap-local system consists of the cap-local test family on \(\mathcal A_n^{\mathrm{geo}}(C_n)\), the projectively compatible transported marginal family, and the asymptotic transport-equivalence certificate. On each fixed local collar model, the regularized estimate of Theorem~\ref{thm:regularized-modular-transport} replaces the unavailable unregularized full-algebra floor. Proposition~\ref{prop:cap-pair-extraction} gives the local GNS support quotient cap pair, Lemma~\ref{lem:support-readable-modular-covariance} reads modular flow as a support map on cap-local regions, and Proposition~\ref{prop:round-cap-rigidity} identifies the residual cap-preserving conformal freedom with the standard hyperbolic subgroup. This is the theorem-side content of the BW lift used below.
\end{remark}

\begin{proposition}[Recoverability is not modular geometry: common-floor collapse countermodel]\label{prop:commonfloor-collapse}
Exact or asymptotically exact Markov recovery at finite cutoff does not imply the eventual common floor used in the unregularized BW/geometric cap-pair extraction. In \(M_2(\mathbb C)\), the faithful states
\[
\rho_n=\begin{pmatrix}e^{-n}&0\\0&1-e^{-n}\end{pmatrix}
\]
have \(\lambda_{\min}(\rho_n)\to0\). Tensoring this family with any fixed finite exact-Markov collar factor gives a full-rank exact-Markov collar family, but no refinement-uniform lower spectral floor survives. On an off-diagonal matrix unit the modular generator carries a logarithmic gap of order \(n\), so unregularized modular transport can fail even though every finite stage is faithful and Markov. Thus the full-algebra common-floor route is the wrong target; Theorem~\ref{thm:regularized-modular-transport} supplies the support-visible replacement used by Theorem~\ref{thm:bw}.
\end{proposition}

\begin{theorem}[Regularized support-visible modular transport]\label{thm:regularized-modular-transport}
Fix a local collar model of finite dimension \(d_{m,\delta}\). Let \(\rho_n\) be the transported physical collar marginal, \(\widehat\rho_n\) the exact-Markov comparison marginal, and \(\Delta_n=\|\rho_n-\widehat\rho_n\|_1\). For \(a>0\), set \(K_a(\rho)=-\log(\rho+a\mathbf 1)\). For every bounded support-visible collar observable \(O\),
\[
\left|\operatorname{Tr}\rho_n O\bigl(K_a(\rho_n)-K_a(\widehat\rho_n)\bigr)\right|
\le
\|O\|\left(\frac{4\Delta_n}{a}+d_{m,\delta}a+4\Delta_n|\log a|\right).
\]
If \(a_n\downarrow0\), \(\Delta_n/a_n\to0\), \(d_{m,\delta}a_n\to0\), and \(\Delta_n|\log a_n|\to0\), then the regularized support-visible modular matrix elements converge on that fixed collar model.
\end{theorem}

\begin{proof}
The integral representation of the operator logarithm gives the displayed Lipschitz control above the spectral cutoff \(a\). Splitting the comparison into the visible support above \(a\), the \(a\)-tail, and the trace-distance error gives the three terms in the bound, which vanish under the stated cutoff schedule.
\end{proof}

\begin{theorem}[Support-visible modular convergence from controlled Markov collars]\label{thm:support-visible-modular-convergence}
Let \((A_\delta,B_\delta,D_\delta)\) be a shrinking collar family around a cap
cut. Suppose that after pullback to every fixed local collar model,
\[
r_{\mathrm{FR}}(\varepsilon_\delta)\to0,\qquad
\delta^{\mathrm M}_{A_\delta:B_\delta:D_\delta}(\varepsilon_\delta)\to0,
\]
and suppose the regularized cutoff schedule in
Theorem~\ref{thm:regularized-modular-transport} is satisfied. Then for every
bounded support-visible geometric collar observable \(O\),
\[
\lim_{\delta\downarrow0}
\operatorname{Tr}\rho_\delta O
\bigl(
K_{a_\delta}(\rho_\delta)-K_{a_\delta}(\sigma_\delta)
\bigr)
=0
\]
for any projectively compatible exact-Markov replacement family
\(\sigma_\delta\). Consequently, the scaling-limit modular automorphism on the
extracted geometric cap pair is independent of the particular exact-Markov
replacement sequence used to audit the finite-stage calculation.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:regularized-modular-transport} gives the displayed matrix
element bound with
\(\Delta_\delta=\|\rho_\delta-\sigma_\delta\|_1\). The controlled Markov
replacement hypotheses make \(\Delta_\delta\to0\) on each fixed collar model,
and the chosen \(a_\delta\) schedule sends
\[
\Delta_\delta/a_\delta,\qquad
d_{m,\delta}a_\delta,\qquad
\Delta_\delta|\log a_\delta|
\]
to zero. The projective compatibility theorem ensures that different
compatible replacement choices determine the same local weak-\(*\) limits after
GNS quotienting of null directions. Therefore the support-visible cap modular
automorphism emitted in the scaling limit is a property of the physical cap
pair, not of an arbitrary replacement choice.
\end{proof}

\begin{assumption}[Multiresolution regulator certificate]\label{ass:multiresolution-regulator-certificate}
For every round cap \(C\), the support-visible geometric regulator is represented on a cofinal
branch by finite algebras \(M_r(C)\), faithful reference states \(\widehat\omega_r^C\),
refinement embeddings \(\iota_{rs}\), and faithful state-preserving conditional expectations
\(E_{sr}\) satisfying
\[
\iota_{st}\iota_{rs}=\iota_{rt},\qquad
E_{tr}=E_{sr}E_{ts},\qquad
\widehat\omega_s^C\circ\iota_{rs}=\widehat\omega_r^C.
\]
The tower is the explicit multiresolution edge-center construction of
Theorem~\texttt{2.6d} in the main paper: in bare shell coordinates, the fine algebra is the coarse
algebra tensored with faithful detail factors, while the OPH patch presentation is obtained by a
finite-depth local circuit.

For a physical regulator state at stage \(s\), let
\(\rho^{\rm phys}_{s\downarrow r,C}\) denote its restriction to the embedded fixed local algebra
\(M_r(C)\), let \(\widehat\rho_{r,C}\) be the reference density matrix there, and put
\[
\epsilon_{s,r,C}:=
\|\rho^{\rm phys}_{s\downarrow r,C}-\widehat\rho_{r,C}\|_1.
\]
The branch certificate requires \(\epsilon_{s,r,C}\to0\) for every fixed support-visible local
algebra, or one stronger uniform envelope on the declared local test tower.
\end{assumption}

\begin{theorem}[Strong local scaling of regularized modular groups]\label{thm:strong-local-modular-scaling}
Under Assumption~\ref{ass:multiresolution-regulator-certificate}, the reference modular groups
are exactly refinement compatible:
\[
\sigma_t^{\widehat\omega_s^C}(\iota_{rs}A)
=\iota_{rs}(\sigma_t^{\widehat\omega_r^C}(A)).
\]
For a regularizer \(a_s>0\), define on the transported fixed local algebra
\[
K_{s\downarrow r,C}^{(a_s)}
:=-\log(\rho^{\rm phys}_{s\downarrow r,C}+a_s\mathbf1).
\]
If \(\lambda_{r,C}=\lambda_{\min}(\widehat\rho_{r,C})\), then for every
\(A\in M_r(C)\) and \(T<\infty\),
\[
\sup_{|t|\le T}
\left\|
e^{-itK_{s\downarrow r,C}^{(a_s)}}A
e^{itK_{s\downarrow r,C}^{(a_s)}}
-\sigma_t^{\widehat\omega_r^C}(A)
\right\|
\le
2T\|A\|
\left[
\frac{\epsilon_{s,r,C}}{a_s}
+\log\!\left(1+\frac{a_s}{\lambda_{r,C}}\right)
\right].
\]
Consequently, \(a_s\downarrow0\) and \(\epsilon_{s,r,C}/a_s\to0\) give
uniform-on-compact-time convergence on every fixed support-visible local algebra. Pointwise
projective convergence on a countable local test tower always admits a cofinal diagonal
subsequence and one cutoff schedule with this property.
\end{theorem}

\begin{proof}
In multiresolution coordinates the reference density at stage \(s\) is
\(\widehat\rho_{r,C}\otimes\tau_{s\setminus r}\) and the embedded observable is
\(A\otimes\mathbf1\), which proves exact modular compatibility. For positive matrices above the
floor \(a_s\),
\[
\|\log X-\log Y\|\le a_s^{-1}\|X-Y\|.
\]
Comparing first with \(-\log(\widehat\rho_{r,C}+a_s\mathbf1)\) and then with
\(-\log\widehat\rho_{r,C}\) gives the bracketed generator bound. Duhamel's formula gives the
displayed compact-time automorphism estimate. For the diagonal schedule, choose stages \(s_k\)
with \(\max_{r\le r_k}\epsilon_{s_k,r,C}\le k^{-4}\) and set \(a_{s_k}=k^{-1}\).
\end{proof}

\begin{remark}[Cap-family uniformity for the finite BW certificate]\label{rem:cap-family-uniformity}
For Theorem~\ref{thm:finite-cap-bw-certificate}, the compact-time estimate above is required
uniformly over the declared finite nondegenerate cap family and the fixed separating
support-visible test tower. The operator-norm estimate then implies the quadratic mixed-GNS
Cauchy residual because \(\|XD\|_{2,\omega}\le\|X\|\|D\|_{2,\omega}\). Thus the reference-tower
theorems supply the analytic engine; the finite cap-normal certificate adds the geometric support,
framing, cross-ratio, normalization, and wrong-scale controls.
\end{remark}

\begin{remark}[Support-visible closure boundary]
The finite cap-normal certificate implication to the support-visible BW cap automorphism is closed
by Theorem~\ref{thm:bw}. Production of that certificate from bare finite OPH consensus is excluded
by Theorem~\ref{thm:incidence-underdetermination}; on towers carrying the computable incidence,
mesh, cross-ratio, and normalization receipts, the certificate is produced from repair normal forms
by Theorem~\ref{thm:certificate-production}
(\S\ref{subsec:quotient-intrinsic-geometry-producer}), and those receipts are the irreducible
branch content of the parent Einstein branch-entry gate. The theorem does not need, and does not claim, a full-algebra
unregularized common floor on directions that collapse out of the limiting observer support. The
observer-facing content is the automorphism statement of Theorem~\ref{thm:bw}, which is exactly
what the Lorentz, null-modular, and local Einstein branches use.
\end{remark}

\begin{remark}[Exact BW claim boundary]\label{rem:bw-stronger-not-claimed}
Theorem~\ref{thm:bw} has two layers. The cap-pair theorem identifies the modular automorphism of
the extracted support-visible continuum pair with \(\alpha_{\lambda_C(2\pi t)}\). The
finite-to-continuum group statement is Theorem~\ref{thm:strong-local-modular-scaling}; it applies
only to transported regularized modular actions on fixed local algebras. Neither layer asserts an
unregularized full-algebra spectral floor, convergence on record/pointer or interface-inert
sectors, or finite-cell Lorentz covariance. A black-box AQFT BW route would be a separate
certificate requiring conformal-net properties such as isotony, additivity, locality, duality,
standardness, positive energy, and suitable modular inclusions.
\end{remark}

\subsubsection{Producing the certificate from repair normal forms: incidence receipts, the producer chain, and the dimension-selection boundary}
\label{subsec:quotient-intrinsic-geometry-producer}

The certificate of Definition~\ref{def:finite-cap-bw-certificate} was introduced
above as a hypothesis. This subsection upgrades its status. We construct, for a
concrete cofinal family of OPH repair systems, a quotient-intrinsic and
refinement-natural readout chain
\[
\text{repaired finite quotient normal form}
\;\longrightarrow\;
\text{support-visible incidence complex}
\;\longrightarrow\;
\text{screen/cap data}
\;\longrightarrow\;
\mathsf{FiniteCapBWCertificate},
\]
in which no chart, group action, modular flow, or scale is placed in the
codomain by declaration. Every geometric object below is computed from the
normal form itself, and the residual inputs are reduced to finitely many
\emph{computable receipts}: decidable predicates on finite repair stages. The
subsection closes with an underdetermination theorem and explicit finite
countermodels showing that repair confluence alone selects none of these
receipts, so the receipts are exactly the irreducible geometric branch content.

\paragraph{Support-visible incidence data.}

\begin{definition}[Support-visible incidence complex]
\label{def:support-visible-incidence-complex}
Fix a finite transactional quotient repair branch as in
Definition~\ref{def:transactional-quotient-repair}, with patch set
\(\mathcal P_r\) at stage \(r\), quotient algebra
\(\mathcal A_r=\bigvee_{p\in\mathcal P_r}\mathcal A_{r,p}\), and repaired
normal form \(W_r=\operatorname{Rep}_\lambda(x_r)\) with MaxEnt reference state
\(\omega_{W_r}\). For \(p\in\mathcal P_r\), let \(s_p\in\mathcal A_{r,p}\) be
the central support projection of the restriction
\(\omega_{W_r}|_{\mathcal A_{r,p}}\). The \emph{support-visible incidence
complex} \(K_r=K(W_r)\) is the abstract simplicial complex with vertex set the
quotient-visible patch classes \([p]\) and
\[
\sigma=\{[p_0],\ldots,[p_k]\}\in K_r
\quad:\Longleftrightarrow\quad
\omega_{W_r}\bigl(s_{p_0}s_{p_1}\cdots s_{p_k}\bigr)\neq0 ,
\]
where the product is taken after transport into any common refining patch
algebra; the transactional gluing clauses of node D1 make the nonvanishing
condition independent of the transport route. Write \(K^{(2)}_r\) for the
\(2\)-skeleton.
\end{definition}

\begin{lemma}[Quotient, gauge, schedule, and refinement invariance of the incidence complex]
\label{lem:incidence-invariance}
\(K_r\) depends only on the quotient normal-form class of \(x_r\):
\begin{enumerate}[leftmargin=2em]
\item (Schedule.) Any two admissible repair schedules from \(x_r\) yield the
same \(K_r\).
\item (Gauge.) The gauge groupoid of node D1 acts on support projections by
conjugation, \(s_p\mapsto u\,s_p\,u^{*}\), and leaves every incidence value
\(\omega_{W_r}(s_{p_0}\cdots s_{p_k})\neq0\) unchanged; hence \(K_r\) is
gauge-invariant.
\item (Refinement.) If \(\pi_{r'r}\) is a refinement projection compatible
with finite-stage normal forms, and the stated Petz support/CPTP control of
node D1 holds, then \([p']\mapsto[\pi_{r'r}p']\) extends to a simplicial map
\(K_{r'}\to K_r\), and these maps compose along the refinement order.
\end{enumerate}
\end{lemma}

\begin{proof}
(1) Theorem~\ref{thm:confluence} makes the normal form \(W_r\), hence
\(\omega_{W_r}\) and each \(s_p\), independent of the schedule. (2) A gauge
transformation acts by a quotient automorphism \(\alpha_u=u(\cdot)u^*\)
intertwining \(\omega_{W_r}\circ\alpha_u^{-1}\) with the transported normal
form; supports transform covariantly, \(s_p\mapsto us_pu^*\), and
\(\omega(u s_{p_0}\cdots s_{p_k}u^*)=\omega'(s'_{p_0}\cdots s'_{p_k})\), so
simplex membership is unchanged. (3) Petz support control states that the
refinement channel \(E_{r'r}\) maps the support of
\(\omega_{W_{r'}}|_{\mathcal A_{r',p'}}\) into the support of
\(\omega_{W_r}|_{\mathcal A_{r,\pi p'}}\); a nonvanishing joint support value
at stage \(r'\) therefore pushes forward to a nonvanishing joint support value
of the images, which is the simplicial-map property. Functoriality follows
from compatibility of the projections with normal forms.
\end{proof}

\paragraph{Computable receipts.}

\begin{definition}[Spherical incidence receipt]
\label{def:spherical-incidence-receipt}
Stage \(r\) carries the \emph{spherical incidence receipt}
\(\mathsf{SphInc}_r\) when the \(2\)-skeleton \(K^{(2)}_r\) is a closed
combinatorial surface (every edge lies in exactly two \(2\)-simplices, every
vertex link is a single cycle), is connected, satisfies
\(\chi(K^{(2)}_r)=2\), and admits a coherent orientation (a choice of cyclic
order on each \(2\)-simplex, compatible across shared edges); the orientation
is part of the receipt datum. All clauses are decidable by finite search on
\(K_r\).
\end{definition}

\begin{definition}[Cap, mesh, and cross-ratio receipts]
\label{def:cap-mesh-crossratio-receipts}
On a refinement tower carrying \(\mathsf{SphInc}_r\) cofinally:
\begin{enumerate}[leftmargin=2em]
\item (\emph{Disk receipt.}) A stage-\(r\) \emph{combinatorial cap} is a
subcomplex \(C\subset K^{(2)}_r\) that is a combinatorial disk whose boundary
\(\partial C\) is an incidence cycle; the receipt datum is the finite list
\(\mathrm{Cap}_r\) of such disks selected by the record layer, closed under
complements.
\item (\emph{Mesh receipt.}) \(\mathsf{Mesh}_r(\theta_r)\): every vertex star
is contained in some \(C\in\mathrm{Cap}_r\), and every \(C\in\mathrm{Cap}_r\)
contains at least one and at most \(N(\theta_r)\) vertices, with
\(\theta_r\downarrow0\) along the tower (cofinal nondegenerate cap mesh).
\item (\emph{Modular cross-ratio receipt.}) For a combinatorial cap \(C\) with
boundary cycle \((v_1,\ldots,v_m)\), the cap modular clock of the record layer
assigns to each ordered boundary quadruple \((v_a,v_b,v_c,v_d)\) the modular
transport time \(t_r(v_a,v_b;v_c,v_d)\) needed to flow \(v_a\) past \(v_b\)
relative to the anchors \(v_c,v_d\), and the receipt
\(\mathsf{CR}_r(\varepsilon_r)\) asserts that the induced finite cross-ratios
\[
\mathrm{cr}_r(v_a,v_b;v_c,v_d):=\exp\bigl(2\pi\,t_r(v_a,v_b;v_c,v_d)\bigr)
\]
form a Cauchy family along refinement with modulus \(\varepsilon_r\downarrow0\),
compatible with the simplicial refinement maps of
Lemma~\ref{lem:incidence-invariance}.
\item (\emph{Normalization receipt.}) \(\mathsf{KMS}_r(2\pi;\delta_r)\): the
independently normalized geometric KMS comparison of
Definition~\ref{def:finite-cap-bw-certificate} holds at inverse modular
temperature \(2\pi\) with residual \(\delta_r\downarrow0\), together with the
wrong-normalization separation clause.
\end{enumerate}
\end{definition}

\paragraph{The producer chain.}

\begin{theorem}[Topology production: spherical incidence receipts produce \(S^2\)]
\label{thm:topology-production}
If stage \(r\) carries \(\mathsf{SphInc}_r\), then the geometric realization
\(|K^{(2)}_r|\) is PL-homeomorphic to \(S^2\), uniquely up to PL homeomorphism,
and the receipt orientation induces the orientation of \(S^2\). If moreover
\(r'\geq r\) both carry the receipt and the refinement map of
Lemma~\ref{lem:incidence-invariance} is surjective on \(2\)-simplices and
orientation-coherent, then its realization
\(|K^{(2)}_{r'}|\to|K^{(2)}_r|\) is a degree-one map of \(2\)-spheres.
\end{theorem}

\begin{proof}
A connected closed combinatorial surface is classified up to PL homeomorphism
by orientability and Euler characteristic; orientable with \(\chi=2\) gives
\(S^2\). Uniqueness of the PL structure on surfaces is Rad\'o's theorem. A
simplicial map between oriented closed surfaces that is surjective and
orientation-coherent on top simplices has a well-defined simplicial degree,
which the coherence clause fixes to one.
\end{proof}

\begin{theorem}[Conformal structure and cap production]
\label{thm:conformal-cap-production}
Let \((W_r)_{r\in I}\) be a refinement tower of repaired normal forms carrying,
cofinally, the receipts
\(\mathsf{SphInc}_r\), the disk and mesh receipts with \(\theta_r\downarrow0\),
and \(\mathsf{CR}_r(\varepsilon_r)\) with \(\varepsilon_r\downarrow0\). Then:
\begin{enumerate}[leftmargin=2em]
\item The inverse limit of the boundary-cycle vertex sets, completed in the
cross-ratio uniformity, is a topological \(S^2\) (by
Theorem~\ref{thm:topology-production} and mesh density), carrying a unique
conformal structure for which the limit cross-ratios of
\(\mathsf{CR}_r\) are the M\"obius cross-ratios; with this structure every
limit of receipt caps is a round cap, and the assignment is refinement-natural.
\item The limit cap family therefore lands in
\(\operatorname{Cap}^{\mathrm{or}}_{\mathrm{round}}(S^2)\) with nondegenerate
radii controlled by the mesh modulus \(\theta_r\), producing the cap-normal
map of Proposition~\ref{prop:round-cap-normal} \emph{as output}: the cap
normals \(n_C\in dS_3^{\mathrm{cap}}\) are computed from the produced round
caps, with cap-normal residuals bounded by an explicit function
\(\kappa(\varepsilon_r,\theta_r)\to0\).
\item The produced data are quotient-, gauge-, and schedule-invariant and
refinement-natural, by Lemma~\ref{lem:incidence-invariance} and receipt
compatibility.
\end{enumerate}
\end{theorem}

\begin{proof}
(1) Mesh density with \(\theta_r\downarrow0\) makes the boundary-vertex sets
cofinally dense in the inverse-limit surface. On a topological \(S^2\), a
separating dense family of boundary circles with coherent cross-ratio data
determines a unique atlas of circular charts: fix three limit vertices as
M\"obius gauge; the Cauchy cross-ratio data then embed every other limit
vertex into \(\mathbb C\cup\{\infty\}\) uniquely, since a point of the Riemann
sphere is determined by its cross-ratios against a fixed triple, and
consistency across overlapping quadruples is exactly the receipt
compatibility clause. Uniform Cauchy moduli \(\varepsilon_r\) give
well-definedness of the limit embedding and its continuity; bijectivity onto
\(S^2\) follows from density and compactness. The conformal structure is the
pullback of the standard structure; uniqueness holds because M\"obius
cross-ratios separate conformal structures on \(S^2\) (two structures with
identical cross-ratio functionals on a dense family differ by a M\"obius map,
which is the declared gauge freedom).
(2) In the produced conformal chart, a receipt cap has boundary an incidence
cycle whose limit quadruple cross-ratios are those of a circle (real
cross-ratios for concyclic quadruples, a closed condition implied in the limit
by the Cauchy receipt applied to the disk boundary); hence the limit boundary
is a round circle and the disk a round cap. The normal \(n_C\) is then the
finite formula of Proposition~\ref{prop:round-cap-normal}; the residual bound
\(\kappa(\varepsilon_r,\theta_r)\) follows by continuity of
\(C\mapsto n_C\) on nondegenerate caps, quantitatively since
\(\cot\) and \(\csc\) are Lipschitz on mesh-bounded ranges
\(\alpha\in[\theta_r,\pi-\theta_r]\).
(3) is Lemma~\ref{lem:incidence-invariance} together with the receipt
compatibility requirements, which are themselves stated on normal-form data
only.
\end{proof}

\begin{theorem}[Producer theorem: receipts produce the finite cap-normal BW certificate]
\label{thm:certificate-production}
Let \((W_r)\) be a cofinal tower as in
Theorem~\ref{thm:conformal-cap-production}, carrying in addition
\(\mathsf{KMS}_r(2\pi;\delta_r)\), the mixed-GNS state Cauchy clause of
Axiom~\ref{ax:maxent}, and the D1 gauge/transport package. Then the tower
carries \(\mathsf{FiniteCapBWCertificate}\), with clause-by-clause error
envelopes:
\begin{enumerate}[leftmargin=2em]
\item cap-normal density, nondegeneracy, and residuals
\(\leq\kappa(\varepsilon_r,\theta_r)\) from
Theorem~\ref{thm:conformal-cap-production};
\item BW framing and support covariance from the produced cap normals plus
gauge invariance (Lemma~\ref{lem:incidence-invariance});
\item support-order faithfulness from injectivity of the produced incidence
order embedding: distinct receipt caps have distinct produced normals once
\(\kappa(\varepsilon_r,\theta_r)\) is below the mesh separation
\(\theta_r\)-gap;
\item cap-family-uniform mixed-GNS modular convergence from the
Axiom~\ref{ax:maxent} Cauchy clause evaluated on the produced (finite,
mesh-bounded) cap family;
\item held-out oriented cross-ratio convergence: this is literally
\(\mathsf{CR}_r(\varepsilon_r)\) evaluated on held-out quadruples;
\item independently normalized geometric \(2\pi\)-KMS convergence and
wrong-normalization separation: this is \(\mathsf{KMS}_r(2\pi;\delta_r)\).
\end{enumerate}
Consequently Theorem~\ref{thm:bw} applies on this tower with all hypotheses
produced from repair normal forms and receipts, and the failure modes are
localized: if a receipt fails at cofinally many stages, the corresponding
certificate clause fails with the same witness, and the produced object
degrades exactly as quantified above (topology loss for
\(\mathsf{SphInc}\), conformal-class loss for \(\mathsf{CR}\), scale loss for
\(\mathsf{KMS}\)).
\end{theorem}

\begin{proof}
Each clause is either produced by
Theorems~\ref{thm:topology-production}--\ref{thm:conformal-cap-production}
(clauses 1--3, with the quantitative separation argument for clause 3: two
caps whose normals coincide up to \(\kappa\) have boundary circles within a
mesh gap, contradicting the disk-receipt separation once
\(\kappa<\) gap), restated from an axiom-level Cauchy clause on the produced
finite family (clause 4), or is itself a receipt (clauses 5--6). The failure
localization is immediate because each clause consumed exactly one receipt.
\end{proof}

\paragraph{The dimension-selection boundary.}

\begin{theorem}[Underdetermination: confluence selects no topology, dimension, framing, or normalization]
\label{thm:incidence-underdetermination}
There exist finite transactional quotient repair systems
\(\mathfrak B^{(S^2)}\), \(\mathfrak B^{(T^2)}\), \(\mathfrak B^{(S^3)}\), and
\(\mathfrak B^{(\vee)}\) such that:
\begin{enumerate}[leftmargin=2em]
\item each satisfies every node-D1 hypothesis (repair completeness,
transactional acceptance with validation-complete read sets, termination,
confluence, unique schedule-independent quotient normal form, boundary/sector
preservation);
\item their repair transition systems are isomorphic as abstract rewrite
systems (same state count, same conflict components, same repair-path
category), so no confluence-level invariant distinguishes them;
\item their support-visible incidence complexes are, respectively, a
triangulated \(S^2\), a triangulated \(T^2\), the boundary complex
\(\partial\Delta^4\) (a combinatorial \(S^3\), locally three-dimensional), and
two triangulated \(2\)-spheres wedged at one patch (not a manifold);
\item for every \(\beta>0\) there is a variant
\(\mathfrak B^{(S^2)}_\beta\) with the same repair structure whose cap modular
comparison holds at inverse temperature \(\beta\) instead of \(2\pi\).
\end{enumerate}
Consequently \(\mathsf{SphInc}\), the disk/mesh receipts, and
\(\mathsf{KMS}(2\pi)\) are not consequences of bare finite OPH consensus, and
the implication displayed above
(\(\mathsf{BareFiniteOPHConsensus}\nRightarrow\mathsf{FiniteCapBWCertificate}\))
is strict at the level of topology, dimension, and normalization.
\end{theorem}

\begin{proof}
Fix any finite abstract patch set \(P\) and equip each patch with the same
two-level record algebra \(\mathbb C^2\), with overlap constraints requiring
equality of the shared bit on adjacent patches and a single soft conflict
seeded on one fixed overlap; repair resolves the conflict by the
recovery-derived law in one transactional step. Termination, confluence, and
schedule independence are immediate (one conflict component; Newman's lemma
degenerates), and all D1 clauses hold by construction. The construction is
functorial in the adjacency structure: taking \(P\) with adjacency given by
(i) the icosahedral triangulation of \(S^2\), (ii) a \(7\times7\) triangulated
torus, (iii) \(\partial\Delta^4\), and (iv) two icosahedra identified at a
vertex yields the four systems; their rewrite systems are isomorphic because
the conflict component and repair path structure never see the adjacency
beyond the seeded overlap, while the MaxEnt supports reproduce exactly the
declared adjacency as joint-support nonvanishing, so the incidence complexes
are as listed. For (4), rescale the declared cap modular clock by
\(\beta/2\pi\): the repair layer is unchanged, while the independently
normalized KMS comparison certifies \(\beta\). Each system is finite and
explicit; machine receipts are provided with the released geometry code.
\end{proof}

\begin{corollary}[Status of the screen dimension claim]
\label{cor:dimension-selection-status}
On towers carrying the receipts of
Definitions~\ref{def:spherical-incidence-receipt}--\ref{def:cap-mesh-crossratio-receipts},
the screen \(S^2\), its orientation, its round-cap incidence structure, and
its conformal class are \emph{derived} from repair normal-form data by
Theorems~\ref{thm:topology-production}--\ref{thm:certificate-production}. The
selection of those receipts is \emph{underdetermined} by repair confluence
(Theorem~\ref{thm:incidence-underdetermination}) and is therefore carried
corpus-wide as the explicit branch content of the Einstein entry: every
downstream \(3+1\)-dimensional claim in this manuscript is conditional on
\(\mathsf{SphInc}\) plus the mesh, cross-ratio, and \(2\pi\)-normalization
receipts, and on nothing weaker. The identity
\(\operatorname{Conf}^+(S^2)\cong\mathrm{SO}^+(3,1)\) is downstream of the
produced \(S^2\) and is not itself a dimension selection.
\end{corollary}

\subsubsection{Cap-normal reconstruction and the canonical \(H^3\) chart}
\label{sec:cap-normal-h3}

This subsection makes explicit the geometric step from the support-visible round
two-sphere to the Lorentz-equivariant cap space and the canonical hyperbolic
space of observer rest frames. We use time-first coordinates
\[
V:=\mathbb R\oplus\mathbb R^3,\qquad x=(x^0,\mathbf x),
\]
with Lorentz form
\[
\eta(x,y):=-x^0y^0+\mathbf x\cdot\mathbf y.
\]
Write \(G:=\mathrm{SO}^{+}(\eta)\), the proper orthochronous Lorentz group
denoted \(\mathrm{SO}^{+}(3,1)\) below.

\begin{definition}[Future null cone and celestial projectivization]
\label{def:celestial-null-cone}
The future null cone is
\[
\mathcal N^{+}:=
\left\{q\in V\setminus\{0\}:\eta(q,q)=0,\ q^0>0\right\}.
\]
Its positive projectivization is
\[
\mathbb P\mathcal N^{+}:=\mathcal N^{+}/\mathbb R_{>0}.
\]
Fix \(u_0:=(1,\mathbf0)\). For \(\Omega\in S^2\subset\mathbb R^3\), define
\[
q(\Omega):=(1,\Omega).
\]
\end{definition}

\begin{lemma}[Celestial null section]\label{lem:celestial-null-section}
The map
\[
S^2\longrightarrow\mathbb P\mathcal N^{+},\qquad
\Omega\longmapsto[q(\Omega)]
\]
is a bijection. Moreover,
\[
\eta(q(\Omega),q(\Omega))=0,\qquad -\eta(u_0,q(\Omega))=1.
\]
Thus \(q(\Omega)\) is the unique representative of its future null ray
normalized against \(u_0\).
\end{lemma}

\begin{proof}
Since \(\|\Omega\|=1\),
\[
\eta(q(\Omega),q(\Omega))=-1+\|\Omega\|^2=0,
\]
and \(q(\Omega)^0=1>0\). Also \(-\eta(u_0,q(\Omega))=1\). Conversely, let
\(q=(q^0,\mathbf q)\in\mathcal N^+\). Nullness and future orientation give
\[
q^0=\|\mathbf q\|>0.
\]
After multiplying \(q\) by \((q^0)^{-1}\), one obtains
\[
(1,\mathbf q/q^0)=q(\Omega),\qquad \Omega:=\mathbf q/q^0\in S^2.
\]
The normalization \(q^0=1\) is unique on each positive null ray.
\end{proof}

\begin{definition}[Oriented round cap]\label{def:oriented-round-cap}
For \(\mathbf c\in S^2\) and \(0<\alpha<\pi\), define the oriented closed
round cap
\[
C(\mathbf c,\alpha):=
\left\{\Omega\in S^2:\mathbf c\cdot\Omega\geq\cos\alpha\right\}.
\]
Its boundary circle is
\[
\partial C(\mathbf c,\alpha)=
\left\{\Omega\in S^2:\mathbf c\cdot\Omega=\cos\alpha\right\}.
\]
The endpoints \(\alpha=0,\pi\) are excluded as degenerate point/full-sphere
limits.
\end{definition}

\begin{proposition}[De Sitter normal representation of oriented round caps]
\label{prop:round-cap-normal}
Let \(C=C(\mathbf c,\alpha)\) be a nondegenerate oriented round cap. Define
\[
\boxed{
n_C:=\left(\cot\alpha,\,\csc\alpha\,\mathbf c\right).
}
\]
Then:
\begin{enumerate}[leftmargin=2em]
\item \(n_C\) is unit spacelike:
\[
\eta(n_C,n_C)=1.
\]
\item For every \(\Omega\in S^2\),
\[
\boxed{
\eta(n_C,q(\Omega))=
\frac{\mathbf c\cdot\Omega-\cos\alpha}{\sin\alpha}.
}
\]
\item Consequently,
\[
\eta(n_C,q(\Omega))
\begin{cases}
>0,&\Omega\in\operatorname{int}C,\\
=0,&\Omega\in\partial C,\\
<0,&\Omega\notin C.
\end{cases}
\]
In particular,
\[
\eta(n_C,q(\Omega))=0
\quad\Longleftrightarrow\quad
\Omega\in\partial C.
\]
\item The oriented cap is recovered from its normal by
\[
C(n_C)=\left\{\Omega\in S^2:\eta(n_C,q(\Omega))\geq0\right\}.
\]
\item The assignment \(C\mapsto n_C\) is a bijection
\[
\operatorname{Cap}^{\mathrm{or}}_{\mathrm{round}}(S^2)
\cong
dS_3^{\mathrm{cap}},
\qquad
dS_3^{\mathrm{cap}}:=
\left\{n\in V:\eta(n,n)=1\right\}.
\]
\item Reversing the cap orientation sends \(n_C\mapsto -n_C\). In particular,
the complementary oriented cap has normal \(n_{C^{\mathrm c}}=-n_C\).
\end{enumerate}
\end{proposition}

\begin{proof}
Using \(\|\mathbf c\|=1\),
\[
\eta(n_C,n_C)
=-\cot^2\alpha+\csc^2\alpha\,\|\mathbf c\|^2
=-\cot^2\alpha+\csc^2\alpha
=1.
\]
For \(\Omega\in S^2\),
\[
\eta(n_C,q(\Omega))
=-\cot\alpha+\csc\alpha\,\mathbf c\cdot\Omega
=\frac{\mathbf c\cdot\Omega-\cos\alpha}{\sin\alpha}.
\]
Since \(0<\alpha<\pi\), \(\sin\alpha>0\), so the sign is exactly the sign of
\(\mathbf c\cdot\Omega-\cos\alpha\). The incidence and sign statements follow.

It remains to prove surjectivity and uniqueness. Let \(n=(n^0,\mathbf n)\in
dS_3^{\mathrm{cap}}\). Then
\[
-\left(n^0\right)^2+\|\mathbf n\|^2=1,
\qquad
\|\mathbf n\|=\sqrt{1+\left(n^0\right)^2}>0.
\]
Set \(\mathbf c:=\mathbf n/\|\mathbf n\|\). The function
\(\cot:(0,\pi)\to\mathbb R\) is a bijection, so there is a unique
\(\alpha\in(0,\pi)\) satisfying \(\cot\alpha=n^0\). Then
\[
\csc\alpha=\sqrt{1+\cot^2\alpha}
=\sqrt{1+\left(n^0\right)^2}
=\|\mathbf n\|,
\]
and hence \(n=n_{C(\mathbf c,\alpha)}\). Finally,
\[
\eta(-n_C,q(\Omega))\geq0
\quad\Longleftrightarrow\quad
\eta(n_C,q(\Omega))\leq0,
\]
which reverses the selected side of the boundary circle.
\end{proof}

\begin{remark}[Cap space is de Sitter, not hyperbolic space]
\label{rem:cap-ds-not-h3}
The parameter space of oriented round caps is the spacelike unit hyperboloid
\[
dS_3^{\mathrm{cap}}\cong G/\mathrm{SO}^{+}(2,1).
\]
It is not \(H^3\). Cap normals are spacelike vectors. Observer-frame points
in \(H^3\) are future unit timelike vectors. The two spaces are related by
the cap/half-space duality proved below, not by identifying their points.
\end{remark}

\begin{theorem}[Projective Lorentz action and cap-normal equivariance]
\label{thm:cap-normal-equivariance}
For every \(\Lambda\in G\) and every \(\Omega\in S^2\), define
\[
\omega_\Lambda(\Omega):=\bigl(\Lambda q(\Omega)\bigr)^0.
\]
Then \(\omega_\Lambda(\Omega)>0\), and there is a unique
\(g_\Lambda(\Omega)\in S^2\) such that
\[
\boxed{
\Lambda q(\Omega)=\omega_\Lambda(\Omega)\,
q\!\left(g_\Lambda(\Omega)\right).
}
\]
Explicitly,
\[
\boxed{
g_\Lambda(\Omega)=
\frac{\bigl(\Lambda q(\Omega)\bigr)^{\mathrm{spatial}}}
{\bigl(\Lambda q(\Omega)\bigr)^0}.
}
\]
The assignment \(\Lambda\mapsto g_\Lambda\) is an effective action of \(G\)
on \(S^2\). If \(\gamma_{S^2}\) is the round metric, then
\[
\boxed{
g_\Lambda^*\gamma_{S^2}=\omega_\Lambda^{-2}\gamma_{S^2}.
}
\]
Hence the action is conformal. Moreover,
\[
G\cong \mathrm{PSL}(2,\mathbb C)\cong\operatorname{Conf}^{+}(S^2),
\]
and for every oriented round cap \(C\),
\[
\boxed{
g_\Lambda(C)=C(\Lambda n_C),
\qquad
n_{g_\Lambda C}=\Lambda n_C.
}
\]
\end{theorem}

\begin{proof}
Because \(\Lambda\) is proper orthochronous, it preserves \(\mathcal N^+\).
Thus \(\Lambda q(\Omega)\in\mathcal N^+\), and
\(\omega_\Lambda(\Omega)>0\). A future null vector \(Q=(Q^0,\mathbf Q)\)
obeys \(\|\mathbf Q\|=Q^0\), so \(\mathbf Q/Q^0\in S^2\). This proves the
displayed formula for \(g_\Lambda\), and uniqueness follows from the
time-component normalization \(q(\Omega)^0=1\).

To prove conformality, let \(v\in T_\Omega S^2\). Since \(dq_\Omega(v)=(0,v)\),
differentiating
\[
\Lambda q(\Omega)=\omega_\Lambda(\Omega)\,q(g_\Lambda(\Omega))
\]
gives
\[
\Lambda dq_\Omega(v)
=d\omega_\Lambda(v)\,q(g_\Lambda\Omega)
+\omega_\Lambda(\Omega)\,dq_{g_\Lambda\Omega}(dg_\Lambda v).
\]
The identities \(\eta(q,q)=0\) and \(\eta(q,dq(w))=0\) remove the first term
and the cross term when taking Lorentz norms. Hence
\[
\eta(dq_\Omega(v),dq_\Omega(v))
=\omega_\Lambda(\Omega)^2
\eta\!\left(
dq_{g_\Lambda\Omega}(dg_\Lambda v),
dq_{g_\Lambda\Omega}(dg_\Lambda v)
\right).
\]
Since \(\eta(dq_\Omega(v),dq_\Omega(v))=\|v\|^2\), polarization gives
\[
g_\Lambda^*\gamma_{S^2}=\omega_\Lambda^{-2}\gamma_{S^2}.
\]

For the global group identification, identify \(V\) with Hermitian
\(2\times2\) matrices by
\[
\mathsf X(x)=
\begin{pmatrix}
x^0+x^3 & x^1-i x^2\\
x^1+i x^2 & x^0-x^3
\end{pmatrix}.
\]
Then
\[
\det\mathsf X(x)=(x^0)^2-\|\mathbf x\|^2=-\eta(x,x).
\]
For \(A\in\mathrm{SL}(2,\mathbb C)\), the map
\(\mathsf X\mapsto A\mathsf X A^\dagger\) preserves Hermiticity,
determinant, orientation, and the future cone. It defines a homomorphism
\(\mathrm{SL}(2,\mathbb C)\to G\) with kernel \(\{\pm I\}\), and the image is
the connected Lorentz group. Future null rays are rank-one positive
Hermitian rays, i.e. \(\mathbb{CP}^1\cong S^2\), and the induced projective
action is the M\"obius action. Thus
\[
G\cong\mathrm{PSL}(2,\mathbb C)\cong\operatorname{Conf}^{+}(S^2).
\]

Finally, let \(C=C(n_C)\). Since
\[
q(g_\Lambda\Omega)=\omega_\Lambda(\Omega)^{-1}\Lambda q(\Omega),
\]
Lorentz invariance gives
\[
\eta\!\left(\Lambda n_C,q(g_\Lambda\Omega)\right)
=\omega_\Lambda(\Omega)^{-1}\eta(n_C,q(\Omega)).
\]
The factor \(\omega_\Lambda(\Omega)^{-1}\) is positive, so the interior,
boundary, and exterior signs are preserved. Therefore
\[
g_\Lambda(C(n_C))=C(\Lambda n_C).
\]
Because \(\Lambda\) preserves \(\eta\), \(\Lambda n_C\) is the
uniquely normalized oriented normal of the transformed cap, hence
\[
n_{g_\Lambda C}=\Lambda n_C.
\]
\end{proof}

\begin{corollary}[Lorentz kinematics on the screen]\label{cor:lorentz}
Under the hypotheses of Theorem~\ref{thm:bw},
\[
\operatorname{Conf}^{+}(S^2)\cong \mathrm{PSL}(2,\mathbb C)
\cong \mathrm{SO}^{+}(3,1).
\]
The cap modular flow is represented by the corresponding one-parameter
Lorentz boost/dilation subgroup. More precisely, if \(\lambda_C(t)C=C\) is
the cap-preserving conformal modular flow and \(\Lambda_C(t)\in G\) is its
Lorentz representative, then
\[
\boxed{
\Lambda_C(t)n_C=n_C.
}
\]
Thus the cap modular subgroup lies in
\[
\operatorname{Stab}_G(n_C)\cong\mathrm{SO}^{+}(2,1).
\]
\end{corollary}

\begin{proof}
The group identification and cap-normal action are
Theorem~\ref{thm:cap-normal-equivariance}. Theorem~\ref{thm:bw} identifies
the realized scaling-limit cap modular automorphism with the standard
cap-preserving conformal dilation and fixes its \(2\pi\) normalization. Since
\(\lambda_C(t)\) preserves the oriented cap, equivariance and uniqueness of
the unit normal give
\[
n_C=n_{\lambda_C(t)C}=\Lambda_C(t)n_C.
\]
\end{proof}

In the terminology of the project consistency stack, this Lorentz recovery
is the carrier of stack row C2 (overlap consensus): on the declared branch, agreement of
overlapping patch descriptions forces the spacetime signature, the spatial dimension, and the
local symmetry group, so none of the three remains a selectable freedom.

\begin{definition}[Future observer-frame hyperboloid]\label{def:h3-observer-frames}
Define
\[
H^3:=\left\{u\in V:\eta(u,u)=-1,\ u^0>0\right\}.
\]
A point \(u\in H^3\) is a future unit timelike observer-frame direction. Its
linear instantaneous rest space is
\[
E_u:=u^\perp=\left\{v\in V:\eta(u,v)=0\right\}.
\]
\end{definition}

\begin{proposition}[Canonical observer-frame symmetric space]
\label{prop:h3-frame-space}
The proper orthochronous Lorentz group acts transitively on \(H^3\). The
stabilizer of \(u_0=(1,\mathbf0)\) is
\[
K:=\operatorname{Stab}_G(u_0)\cong\mathrm{SO}(3).
\]
Consequently,
\[
\boxed{
H^3\cong G/K\cong \mathrm{SO}^{+}(3,1)/\mathrm{SO}(3).
}
\]
The subgroup \(K\) is a maximal compact subgroup of \(G\), and every maximal
compact subgroup of \(G\) is conjugate to \(K\). Thus \(G/K\) is canonical up
to \(G\)-equivariant isometry. Furthermore:
\begin{enumerate}[leftmargin=2em]
\item \(T_uH^3=u^\perp=E_u\), and \(\eta|_{E_u}\) is positive definite and
three-dimensional.
\item The induced metric \(g_{H^3}:=\eta|_{TH^3}\) is \(G\)-invariant. Every
\(G\)-invariant Riemannian metric on \(G/K\) is a positive scalar multiple of
this metric.
\item For each \(u\in H^3\), the normalized celestial section
\[
\mathcal S_u:=\left\{q\in\mathcal N^+:-\eta(u,q)=1\right\}
\]
is naturally the unit two-sphere in \(E_u\). Explicitly,
\[
q=u+s,\qquad s\in E_u,\qquad \eta(s,s)=1.
\]
\item The construction is Lorentz-natural:
\[
\Lambda\mathcal S_u=\mathcal S_{\Lambda u}.
\]
\item The ideal boundary of \(H^3\) is the projective future null cone:
\[
\boxed{
\partial_\infty H^3\cong\mathbb P\mathcal N^+\cong S^2.
}
\]
\end{enumerate}
\end{proposition}

\begin{proof}
Every future unit timelike vector can be completed to an oriented,
time-oriented Lorentz frame, so \(G\) acts transitively on \(H^3\). A Lorentz
transformation fixing \(u_0\) acts orthogonally on
\[
u_0^\perp\cong\mathbb R^3,
\]
and proper orientation gives precisely \(\mathrm{SO}(3)\). Hence
\[
H^3\cong G/\mathrm{SO}(3).
\]
If \(L\subseteq G\) is compact, average \(u_0\) over \(L\) using Haar measure.
The future timelike cone is convex, so the average is a future timelike vector
fixed by \(L\); after normalization, \(L\) is conjugate into a point
stabilizer. Thus \(K\) is maximal compact and all maximal compact subgroups
are conjugate.

Differentiating \(\eta(u,u)=-1\) gives \(T_uH^3=u^\perp\). The orthogonal
complement of a timelike vector is positive definite and has dimension three.
Since \(G\) preserves \(\eta\), the induced metric is \(G\)-invariant. At
\(u_0\), the isotropy representation of \(K\cong\mathrm{SO}(3)\) on
\(T_{u_0}H^3\cong\mathbb R^3\) is the standard irreducible representation, so
every \(K\)-invariant positive inner product is a positive scalar multiple of
the Euclidean one. Homogeneity gives the metric uniqueness.

Take \(q\in\mathcal S_u\) and set \(s:=q-u\). Then
\[
\eta(u,s)=\eta(u,q)-\eta(u,u)=-1+1=0,
\]
and
\[
\eta(s,s)=\eta(q-u,q-u)=0-2(-1)-1=1.
\]
Thus \(s\) lies on the unit sphere in \(E_u\). Conversely, if \(s\in E_u\)
and \(\eta(s,s)=1\), then \(q=u+s\) is future null and satisfies
\(-\eta(u,q)=1\). Lorentz naturality follows from preservation of \(\eta\).

Finally, for \(s\in E_u\) with \(\eta(s,s)=1\), the curve
\[
\gamma_{u,s}(t)=\cosh t\,u+\sinh t\,s
\]
is a unit-speed geodesic ray in \(H^3\). Projectively,
\[
[\gamma_{u,s}(t)]\longrightarrow [u+s]\qquad(t\to+\infty),
\]
and \(\eta(u+s,u+s)=0\). Every future null ray has such a normalized
decomposition relative to \(u\). Hence the ideal boundary is
\(\mathbb P\mathcal N^+\cong S^2\).
\end{proof}

\begin{proposition}[No cap-to-observer-point map from cap data alone]
\label{prop:no-cap-to-observer-point-map}
There is no \(G\)-equivariant map
\[
F:dS_3^{\mathrm{cap}}\longrightarrow H^3.
\]
Equivalently, an oriented round cap by itself does not canonically select a
point of the observer-frame hyperboloid.
\end{proposition}

\begin{proof}
Fix \(n_0\in dS_3^{\mathrm{cap}}\). Its stabilizer is
\[
H:=\operatorname{Stab}_G(n_0)\cong\mathrm{SO}^{+}(2,1),
\]
which is noncompact. Suppose an equivariant map \(F\) existed. For every
\(h\in H\),
\[
F(n_0)=F(hn_0)=hF(n_0).
\]
Thus the full noncompact group \(H\) would fix \(F(n_0)\in H^3\). But the
stabilizer of every point of \(H^3\) is conjugate to \(\mathrm{SO}(3)\), hence
compact. This is impossible.
\end{proof}

\begin{remark}[Meaning of the no-go statement]\label{rem:cap-point-no-go-meaning}
The canonical output of one oriented cap is therefore not an observer point.
It is the oriented geodesic plane and hyperbolic half-space constructed in the
next proposition. Selecting a particular observer frame \(u\in H^3\) requires
additional observer, tetrad, clock, or record data.
\end{remark}

\begin{proposition}[Round-cap/hyperbolic-half-space duality]
\label{prop:cap-h3-duality}
Let \(n\in dS_3^{\mathrm{cap}}\). Define
\[
\Pi_n:=\left\{u\in H^3:\eta(n,u)=0\right\},
\qquad
\mathcal H_n^+:=\left\{u\in H^3:\eta(n,u)\geq0\right\}.
\]
Then:
\begin{enumerate}[leftmargin=2em]
\item \(\Pi_n\) is a totally geodesic copy of \(H^2\).
\item Its ideal boundary is the round circle represented by \(n\):
\[
\partial_\infty\Pi_n=
\left\{[q]\in\mathbb P\mathcal N^+:\eta(n,q)=0\right\}
=\partial C(n).
\]
\item The ideal boundary of the oriented half-space is the oriented cap:
\[
\partial_\infty\mathcal H_n^+
=C(n)
=\left\{[q]\in\mathbb P\mathcal N^+:\eta(n,q)\geq0\right\}.
\]
\item The construction is Lorentz-equivariant:
\[
\Lambda\Pi_n=\Pi_{\Lambda n},
\qquad
\Lambda\mathcal H_n^+=\mathcal H_{\Lambda n}^+.
\]
\item The signed distance from \(u\in H^3\) to \(\Pi_n\), positive on
\(\mathcal H_n^+\), is
\[
\boxed{
s_n(u)=\operatorname{arsinh}\!\bigl(\eta(n,u)\bigr).
}
\]
\end{enumerate}
\end{proposition}

\begin{proof}
Because \(n\) is unit spacelike, \(n^\perp\) has signature \((-++)\). Its
future unit timelike hyperboloid is a copy of \(H^2\), and
\[
\Pi_n=H^3\cap n^\perp.
\]
Intersections of the hyperboloid with linear subspaces through the origin are
totally geodesic, proving the first claim. The ideal boundary of
\(H^3\cap n^\perp\) consists of future null rays contained in \(n^\perp\),
which are exactly those satisfying \(\eta(n,q)=0\). Under
Lemma~\ref{lem:celestial-null-section}, this is the circle \(\partial C(n)\);
the sign condition gives the corresponding oriented ideal half-space boundary.

Equivariance follows from \(\eta(\Lambda n,\Lambda u)=\eta(n,u)\). For the
distance formula, let
\[
a:=\eta(n,u),
\qquad
p:=\frac{u-a n}{\sqrt{1+a^2}}.
\]
Then \(\eta(p,n)=0\), \(\eta(p,p)=-1\), and \(p\) lies on the future sheet, so
\(p\in\Pi_n\). With \(s:=\operatorname{arsinh}(a)\),
\[
u=\cosh s\,p+\sinh s\,n,
\]
which is the unit-speed geodesic normal to \(\Pi_n\) through \(p\). Hence
\(s\) is the signed distance.
\end{proof}

\begin{corollary}[Three-dimensional observer-facing spatial chart]
\label{cor:h3-spatial-chart}
Under the hypotheses of Corollary~\ref{cor:lorentz}, the canonical
observer-frame/rest-space chart on the Lorentz branch is
\[
\boxed{
H^3\cong\mathrm{SO}^{+}(3,1)/\mathrm{SO}(3).
}
\]
Its dimension is exactly
\[
\boxed{
\dim H^3=\dim\mathrm{SO}^{+}(3,1)-\dim\mathrm{SO}(3)=6-3=3.
}
\]
The associated invariant metric is fixed only up to one positive curvature
radius. With radius \(R_H>0\),
\[
H^3_{R_H}=\left\{X\in V:\eta(X,X)=-R_H^2,\ X^0>0\right\},
\]
and
\[
d_H(X,Y)=
R_H\,
\operatorname{arcosh}
\left(-\frac{\eta(X,Y)}{R_H^2}\right).
\]
The group/cap theorem fixes the hyperbolic homogeneous-space geometry and its
dimension; it does not fix a physical numerical value of \(R_H\).
\end{corollary}

\begin{proof}
The homogeneous-space statement and dimension follow from
Proposition~\ref{prop:h3-frame-space}. The standard isotropy representation
of \(\mathrm{SO}(3)\) is irreducible, so the invariant metric is unique up to
one overall positive multiplier. Writing that multiplier as \(R_H^2\) gives
the radius-\(R_H\) hyperboloid and the displayed distance formula.
\end{proof}

\begin{remark}[Rest-frame chart versus populated bulk]\label{rem:h3-chart-not-populated-bulk}
The theorem proves the exact three-dimensional Lorentz/\(H^3\) kinematic chart
on the support-visible round-cap BW branch. It makes four distinctions
explicit:
\begin{enumerate}[leftmargin=2em]
\item An oriented cap is represented by a spacelike
\(n_C\in dS_3^{\mathrm{cap}}\).
\item An observer rest frame is represented by a future timelike \(u\in H^3\).
\item The individual observer's linear instantaneous rest space is
\(u^\perp=T_uH^3\).
\item A cap determines a geodesic plane and half-space in \(H^3\), not a
preferred observer point.
\end{enumerate}
The theorem does not, by itself, select a preferred \(u\), populate the chart
with records or objects, construct a chart-blind neutral bulk, fix \(R_H\) in
physical units, produce a stress tensor, or establish the Einstein equation.
Populated observer-facing bulk records require the conditional cap-response
localization certificate of Corollary~\ref{cor:conditional-record-populated-h3}.
Object-family interpretation, chart-blind neutral-bulk reconstruction, physical
scale, stress, and Einstein dynamics remain separate certificates. The conditional
event-manifold continuation of these gates, an event base with a Lorentzian atlas over
which this \(H^3\) is strictly the frame fiber, is constructed in
\S\ref{subsec:event-manifold}.
\end{remark}
\subsubsection{Record-populated \(H^3\) from modular cap-response localization}
\label{subsec:record-populated-h3-localization}

This subsection attaches records to the observer-facing \(H^3\) chart without
promoting the chart itself into a neutral bulk. Fix \(R_H>0\) and
\[
H^3_{R_H}:=\{X\in\mathbb R^{1,3}:\eta(X,X)=-R_H^2,\ X^0>0\}.
\]
For \(X,Y\in H^3_{R_H}\), write
\[
\bar d(X,Y):=\frac{1}{R_H}d_H(X,Y)
=\operatorname{arcosh}\!\left(-\frac{\eta(X,Y)}{R_H^2}\right).
\]
For an oriented round cap \(C\), let \(n_C\) be its unit spacelike normal from
Proposition~\ref{prop:round-cap-normal}. Define
\[
h_C(X):=\frac{\eta(X,n_C)}{R_H},\qquad
q_C(X):=[h_C(X)]_+,\qquad
\chi_C(X):=\mathbf 1_{\{h_C(X)\geq0\}}.
\]

\begin{lemma}[Cap/half-space response dictionary]\label{lem:cap-halfspace-response-dictionary}
The map \(C\mapsto n_C\) identifies oriented round caps with unit spacelike
normals. The cap \(C\) determines the hyperbolic plane
\[
\Pi_C:=\{X\in H^3_{R_H}:\eta(X,n_C)=0\}
\]
and oriented half-space
\[
\mathcal H_C^+:=\{X\in H^3_{R_H}:\eta(X,n_C)\geq0\}.
\]
The signed distance \(s_C(X)\) from \(X\) to \(\Pi_C\), positive on
\(\mathcal H_C^+\), obeys
\[
h_C(X)=\sinh\!\left(\frac{s_C(X)}{R_H}\right),
\qquad
s_C(X)=R_H\operatorname{arsinh}h_C(X).
\]
\end{lemma}

\begin{proof}
The first statement is Proposition~\ref{prop:round-cap-normal}. If
\(Y\in\Pi_C\) is the foot of the perpendicular from \(X\), the normal geodesic
has form
\[
\gamma(s)=\cosh(s/R_H)Y+R_H\sinh(s/R_H)n_C.
\]
Pairing with \(n_C\) gives \(\eta(\gamma(s),n_C)/R_H=\sinh(s/R_H)\).
\end{proof}

\begin{theorem}[Round-cap half-space functions separate \(H^3\)]
\label{thm:h3-cap-halfspace-separation}
The families \(\{h_C\}\), \(\{q_C\}\), and \(\{\chi_C\}\), over oriented round
caps, separate points of \(H^3_{R_H}\). Equivalently, for every \(X\neq Y\)
there is an oriented round cap \(C\) with \(h_C(X)<0<h_C(Y)\).
\end{theorem}

\begin{proof}
Let \(M\) be the geodesic midpoint between \(X\) and \(Y\), and let \(v\in
T_MH^3_{R_H}\) be the unit tangent pointing from \(X\) to \(Y\). Then
\[
X=\cosh(\delta/2R_H)M-R_H\sinh(\delta/2R_H)v,\qquad
Y=\cosh(\delta/2R_H)M+R_H\sinh(\delta/2R_H)v,
\]
where \(\delta=d_H(X,Y)>0\). The vector \(v\) is unit spacelike and therefore
is \(n_C\) for a unique oriented cap \(C\). Thus
\[
h_C(X)=-\sinh(\delta/2R_H)<0,\qquad
h_C(Y)=+\sinh(\delta/2R_H)>0.
\]
The nonnegative and binary responses then distinguish the same ordered pair.
\end{proof}

\begin{remark}[Separation versus inverse stability]\label{rem:h3-separation-not-stability}
Qualitative point separation proves exact injectivity for the full response
family. It does not provide a uniform linear inverse bound; a continuous
injective map such as \(x\mapsto x^3\) has no Lipschitz inverse at zero. Finite
noisy localization therefore requires a quantitative observability constant
\(\alpha>0\), supplied by a conditioned cap frame or an independently verified
response frame.
\end{remark}

\begin{definition}[Centered tight cap frame]\label{def:centered-tight-cap-frame}
Let \(u_1,\ldots,u_m\in S^2\) satisfy
\[
\sum_{j=1}^m u_j=0,\qquad
\sum_{j=1}^m u_ju_j^{\mathsf T}=\frac m3 I_3.
\]
Set \(\theta_0=\arccos(1/\sqrt3)\) and
\[
n_j=\left(\frac1{\sqrt2},\,\sqrt{\frac32}\,u_j\right),\qquad
h_j(X)=\frac{\eta(X,n_j)}{R_H}.
\]
\end{definition}

\begin{theorem}[Explicit finite-frame reconstruction]\label{thm:h3-finite-conditioned-cap-frame}
For the frame of Definition~\ref{def:centered-tight-cap-frame}, every
\(X=(X^0,\mathbf X)\in H^3_{R_H}\) is recovered from
\(h(X)=(h_1(X),\ldots,h_m(X))\) by
\[
X^0=-\frac{\sqrt2\,R_H}{m}\sum_{j=1}^m h_j(X),\qquad
\mathbf X=\frac{\sqrt6\,R_H}{m}\sum_{j=1}^m h_j(X)u_j.
\]
Moreover
\[
|h(X)-h(Y)|_2^2=\frac{m}{2R_H^2}|X-Y|_{\mathrm E}^2
\]
and hence
\[
|h(X)-h(Y)|_2\geq\sqrt{\frac m2}\,\bar d(X,Y).
\]
For the twelve icosahedral directions, \(\alpha_h=\sqrt6\).
\end{theorem}

\begin{proof}
Since
\[
h_j(X)=\frac1{R_H}
\left(-\frac{X^0}{\sqrt2}+\sqrt{\frac32}\,\mathbf X\cdot u_j\right),
\]
summing and using the centered tight-frame identities gives the two displayed
reconstruction formulas. Applying the same identities to
\(\Delta X=X-Y\) gives the Euclidean norm identity. Finally
\(|X-Y|_{\mathrm E}\geq R_H\bar d(X,Y)\) on the hyperboloid, because the
Euclidean norm dominates the spacelike Minkowski norm and
\(2\sinh(r/2)\geq r\).
\end{proof}

\begin{proposition}[General cap-frame condition]\label{prop:h3-general-cap-frame-condition}
For unit spacelike cap normals \(n_1,\ldots,n_m\), form the matrix \(B\) with
rows \((-n_j^0,n_j^1,n_j^2,n_j^3)\). If \(W\succ0\) and \(B\) has rank \(4\),
then
\[
X_{\mathrm E}=R_H(B^{\mathsf T}WB)^{-1}B^{\mathsf T}Wh(X),
\qquad
\alpha_{\mathrm{frame}}=\sigma_{\min}(W^{1/2}B),
\]
and
\[
|h(X)-h(Y)|_W\geq \alpha_{\mathrm{frame}}\bar d(X,Y).
\]
\end{proposition}

\begin{proof}
The response vector is \(h(X)=B X_{\mathrm E}/R_H\). The left inverse gives
the reconstruction formula, and the smallest singular value of \(W^{1/2}B\)
gives the lower bound after using \(|X-Y|_{\mathrm E}\geq R_H\bar d(X,Y)\).
\end{proof}

\begin{lemma}[Paired hinge response]\label{lem:paired-hinge-response}
For \(\Phi(z)=([z]_+,[-z]_+)\),
\[
\frac1{\sqrt2}|z-w|\leq |\Phi(z)-\Phi(w)|_2\leq |z-w|.
\]
Thus cap/complement nonnegative responses inherit a lower constant
\(\alpha_Q=\alpha_h/\sqrt2\). For the twelve-direction signed frame,
\(\alpha_Q=\sqrt3\).
\end{lemma}

\begin{proof}
If \(z,w\) have the same sign, the norm is \(|z-w|\). If they have opposite
signs, it is \(\sqrt{z^2+w^2}\), which lies between
\((|z|+|w|)/\sqrt2\) and \(|z|+|w|\).
\end{proof}

\begin{definition}[Record-conditioned modular cap response]
\label{def:record-conditioned-modular-cap-response}
Let \(O\) be an observer and let \(P_{i,O}\) be the central, or declared
approximately central, projector for quotient-visible record token \(i\), with
\(\omega_O(P_{i,O})>0\). Define
\[
\omega_{i,O}(A):=\frac{\omega_O(P_{i,O}AP_{i,O})}{\omega_O(P_{i,O})}.
\]
For a cap \(C\), let \(\widehat M_{C,0,O}\) be the declared cap-response probe
observable and set
\[
\widehat M_{C,t,O}:=\sigma_t^{C,O}(\widehat M_{C,0,O}),\qquad
R_i(C,t,O):=\omega_{i,O}(\widehat M_{C,t,O}).
\]
On the geometric branch, the modular-time convention is the same one used in
Theorem~\ref{thm:bw}: \(\sigma_t^{C,O}=\alpha_{\lambda_C(2\pi t)}\).
\end{definition}

\begin{definition}[Point-local response factorization]
\label{def:point-local-cap-response-factorization}
For a probe sample \(j=(C,t,O)\), the point-local branch asserts that there is
a source \(X_i(t)\in\Omega\subset H^3_{R_H}\) such that
\[
R_{i,j}=b_j+a_{i,j}\psi_j(h_j(X_i(t)))+\xi_{i,j},
\qquad
h_j(X)=\frac{\eta(X,n_j)}{R_H}.
\]
Here \(b_j\) is background, \(a_{i,j}>0\) is a calibrated gain or declared
source amplitude, \(\psi_j\) is a frozen scalar sensor kernel, and \(\xi_{i,j}\)
collects measurement, record-centrality, calibration, modular-transport,
finite-record, point-model, and numerical error. The raw half-space kernel is
\(\psi_j(z)=[z]_+\); a signed calibrated channel may use \(\psi_j(z)=z\). This
factorization is a branch hypothesis or finite source-factor receipt, not a
consequence of fitting a point.
\end{definition}

\begin{lemma}[Calibration error]\label{lem:h3-localization-calibration-error}
Suppose \(R_j=b_j+a_jf_j+\xi_j\), \(y_j=(R_j-\widehat b_j)/\widehat a_j\),
\(a_j\geq a_{\min}>0\), \(|\widehat a_j-a_j|\leq\delta_{a,j}<a_{\min}\),
\(|\widehat b_j-b_j|\leq\delta_{b,j}\), \(|\xi_j|\leq\delta_{R,j}\), and
\(|f_j|\leq M_j\). Then
\[
|y_j-f_j|
\leq
\frac{\delta_{R,j}+\delta_{b,j}+\delta_{a,j}M_j}
{a_{\min}-\delta_{a,j}}.
\]
\end{lemma}

\begin{proof}
Subtract \(f_j\) from \(y_j\). The numerator is
\((b_j-\widehat b_j)+\xi_j+(a_j-\widehat a_j)f_j\), and the denominator is at
least \(a_{\min}-\delta_{a,j}\).
\end{proof}

\begin{definition}[Quantitative response observability]\label{def:h3-response-observability}
For a compact source region \(\Omega\subset H^3_{R_H}\), let
\(F:\Omega\to\mathbb R^{|J|}\) be the calibrated response map
\[
F_j(X):=\psi_j(h_j(X)).
\]
With \(|z|_W=(z^{\mathsf T}Wz)^{1/2}\), \(W\succ0\), the map is
quantitatively observable on \(\Omega\) when
\[
\alpha\bar d(X,Y)\leq |F(X)-F(Y)|_W\leq L\bar d(X,Y)
\]
for all \(X,Y\in\Omega\), with \(0<\alpha\leq L<\infty\).
\end{definition}

\begin{theorem}[Exact residual identifiability]\label{thm:h3-exact-residual-identifiability}
If \(F\) satisfies the lower bound in Definition~\ref{def:h3-response-observability}
and exact data are \(y=F(X_\star)\), then \(X_\star\) is the unique global
minimizer on \(\Omega\) of
\[
\mathcal J(X):=|F(X)-y|_W^2.
\]
\end{theorem}

\begin{proof}
\(\mathcal J(X_\star)=0\). If another point also has zero residual, then
\(F(X)=F(X_\star)\), so \(\alpha\bar d(X,X_\star)=0\), hence \(X=X_\star\).
\end{proof}

\begin{theorem}[Finite net on a bounded hyperbolic source region]
\label{thm:h3-finite-localization-net}
Let \(\Omega=B_H(o,D)\) be a closed hyperbolic ball. For every
\(\varepsilon>0\) there is a finite \(\varepsilon\)-net
\(\mathcal N_\varepsilon\subset\Omega\), measured in \(\bar d\), with
\[
|\mathcal N_\varepsilon|
\leq
\frac{V_{R_H}(D+R_H\varepsilon/2)}{V_{R_H}(R_H\varepsilon/2)},
\]
where
\[
V_{R_H}(r)=\pi R_H^3\left[\sinh(2r/R_H)-2r/R_H\right].
\]
There is no finite global \(\varepsilon\)-net for all of noncompact \(H^3\).
\end{theorem}

\begin{proof}
Choose a maximal subset of \(\Omega\) whose distinct points are more than
\(\varepsilon\) apart in normalized distance. Maximality gives coverage. The
balls of physical radius \(R_H\varepsilon/2\) around net points are disjoint
and lie in \(B_H(o,D+R_H\varepsilon/2)\), giving the volume bound. Noncompact
\(H^3\) has infinite volume, so a finite global net cannot exist.
\end{proof}

\begin{theorem}[Finite-net bounded-noise localization]
\label{thm:h3-finite-net-localization}
Let \(\Omega\subset H^3_{R_H}\) be compact and let \(F\) satisfy
Definition~\ref{def:h3-response-observability}. Let measured calibrated data
be \(y=F(X_\star)+e\), with \(|e|_W\leq\sigma\). If
\(\mathcal N_\varepsilon\) is an \(\varepsilon\)-net of \(\Omega\) and
\(\widehat X_\varepsilon\in\mathcal N_\varepsilon\) satisfies
\[
|F(\widehat X_\varepsilon)-y|_W
\leq
\min_{Z\in\mathcal N_\varepsilon}|F(Z)-y|_W+\tau,
\]
then
\[
d_H(\widehat X_\varepsilon,X_\star)
\leq
R_H\left[
\frac L\alpha\varepsilon+\frac2\alpha\sigma+\frac1\alpha\tau
\right].
\]
\end{theorem}

\begin{proof}
Choose \(X_\varepsilon\in\mathcal N_\varepsilon\) with
\(\bar d(X_\varepsilon,X_\star)\leq\varepsilon\). Then
\(|F(X_\varepsilon)-F(X_\star)|_W\leq L\varepsilon\). Near-optimality and
\(|e|_W\leq\sigma\) give
\[
|F(\widehat X_\varepsilon)-F(X_\star)|_W\leq L\varepsilon+2\sigma+\tau.
\]
The lower observability bound converts this response error into the displayed
hyperbolic distance bound.
\end{proof}

\begin{theorem}[Certified noisy finite uniqueness]\label{thm:h3-certified-noisy-uniqueness}
For \(Z\in\mathcal N_\varepsilon\), let \(r(Z)=|F(Z)-y|_W\). Suppose certified
interval arithmetic gives \(\underline r(Z)\leq r(Z)\leq\overline r(Z)\). If a
candidate \(\widehat X_\varepsilon\) satisfies
\[
\overline r(\widehat X_\varepsilon)
<
\min_{Z\neq\widehat X_\varepsilon}\underline r(Z),
\]
then it is the unique residual minimizer for every realization consistent with
the intervals. Define
\[
\Delta_{\mathrm{loc}}
:=
\min_{Z\neq\widehat X_\varepsilon}\underline r(Z)
-\overline r(\widehat X_\varepsilon).
\]
A unique finite point is licensed exactly when \(\Delta_{\mathrm{loc}}>0\);
when \(\Delta_{\mathrm{loc}}\leq0\), the required finite output is
\(\mathrm{AMBIGUOUS}\) together with the admissible localization set.
\end{theorem}

\begin{proof}
Every competitor has residual at least its lower interval bound, while the
candidate has residual at most its upper interval bound. A strict positive gap
therefore rules out ties and competitors. Without such a gap, a finite
procedure cannot choose a unique output without adding an external tie-breaker.
\end{proof}

\begin{theorem}[Lorentz-chart naturality of localization]\label{thm:h3-localization-naturality}
For \(A\in\mathrm{SO}^+(3,1)\), transform points and cap normals by
\(X\mapsto AX\) and \(n_j\mapsto An_j\). Then
\[
\eta(AX,An_j)=\eta(X,n_j).
\]
Consequently the calibrated feature vector, residual objective, observability
constants, and localization/gap verdicts are unchanged; if \(\widehat X\) is
the reconstructed point in one chart, \(A\widehat X\) is the reconstructed
point in the transformed chart.
\end{theorem}

\begin{proof}
Lorentz transformations preserve \(\eta\), so all response coordinates and all
residual inequalities are invariant under the common chart transform.
\end{proof}

\begin{corollary}[Conditional record-populated \(H^3\) localization]
\label{cor:conditional-record-populated-h3}
Fix a clock slice \(t\) and a quotient-visible record token \(i\). Assume:
\begin{enumerate}[leftmargin=2em]
\item a valid observer-facing \(H^3_{R_H}\) chart and cap-normal map are
available;
\item \(X_i(t)\in\Omega\subset H^3_{R_H}\) for a declared compact source
region;
\item calibrated modular cap responses satisfy the point-local factorization
of Definition~\ref{def:point-local-cap-response-factorization};
\item the finite response map has constants \(0<\alpha\leq L\) on \(\Omega\);
\item the total response/model error obeys \(|e_i|_W\leq\sigma_i\);
\item \(\mathcal N_\varepsilon\) is an \(\varepsilon\)-net of \(\Omega\);
\item \(\widehat X_i(t)\) is a residual minimizer up to tolerance \(\tau_i\).
\end{enumerate}
Then the localized record support is the ball
\[
S_i(t)=B_H\!\left(\widehat X_i(t),
R_H\left[
\frac L\alpha\varepsilon+\frac2\alpha\sigma_i+\frac1\alpha\tau_i
\right]\right).
\]
Exact continuous data identify \(X_i(t)\) uniquely. Finite noisy data give the
displayed certified localization ball; a unique finite point additionally
requires \(\Delta_{\mathrm{loc},i}(t)>0\). If that gap fails, the theorem output
is \(\mathrm{AMBIGUOUS}\).
\end{corollary}

\begin{proof}
Exact uniqueness is Theorem~\ref{thm:h3-exact-residual-identifiability}. The
finite-net error estimate is Theorem~\ref{thm:h3-finite-net-localization}.
Noisy finite uniqueness is Theorem~\ref{thm:h3-certified-noisy-uniqueness}, and
chart naturality is Theorem~\ref{thm:h3-localization-naturality}.
\end{proof}

\begin{remark}[Record-population claim boundary]\label{rem:h3-localization-claim-boundary}
The \(H^3\) chart remains a recovered geometric result on the support-visible
Lorentz branch. Record population is a conditional continuation theorem:
calibrated quotient-visible cap responses localize a record token when they
satisfy the point-local response factorization and quantitative cap-frame
hypotheses. Exact data give a unique point. Finite noisy data give a certified
localization ball; a unique finite point additionally requires a positive
residual gap. This theorem does not derive point locality, unlabeled source
mixture resolution, extended-source collapse to a point, particle species,
physical stress, neutral third-person bulk, or Einstein branch entry. The localized
records constructed here are the germ inputs of the conditional event-manifold packet of
\S\ref{subsec:event-manifold}, where they populate an event base rather than the frame
fiber.
\end{remark}
\subsection{The null modular bridge}

The fixed-cutoff strip analysis begins from the transferred cut-center data and the inherited-strip Markov structure. At fixed regulator scale one obtains exact or controlled four-term strip additivity together with endpoint-Lipschitz control of the renormalized half-line family; on the same scaling-limit geometric-cap branch used in Theorem~\ref{thm:bw}, the null half-line blow-up net then inherits geometric dilation and therefore half-sided modular inclusion. Standard Borchers--Wiesbrock theory~\cite{wiesbrock93} applies only after that derived half-sided modular pair is in hand, yielding positivity and unitary implementation of null translations. The downstream bounded-interval transport is discharged by Lemma~\ref{lem:bounded-interval-kernel}, and the tensor upgrade carries the standard null-invisible metric ambiguity. The half-line generator itself is identified below with the effective local null-stress charge.
\par
The present subsection therefore establishes the following chain:
\begin{enumerate}[leftmargin=2em]
\item null-strip center transfer and the inherited left/right split hypothesis;
\item exact strip additivity on the exact inherited Markov model, and a carried defect operator on controlled exact-Markov replacements on one fixed strip model;
\item endpoint-Lipschitz matrix elements for the renormalized half-line family and the resulting weak tail generator;
\item derived half-sided modular inclusion on the null half-line blow-up net from the declared scaling-limit geometric-cap branch, and the resulting Borchers positive translation generator.
\end{enumerate}
The only explicit downstream boundary retained below is the bounded-interval transport/projective branch together with the later tensor upgrade; the half-line generator/charge identification is proved inside the bridge itself. Lemma~\ref{lem:translation} states the positive null-translation generator explicitly: the Borchers unitary group is constructed on its Stone domain, positivity is theorem-level instead of implicit, and the half-line modular Hamiltonians are tied to it by explicit affine covariance and quadratic-form identities.

\begin{proposition}[Null-strip center transfer and inherited split]\label{prop:nullec}
Fix a null generator \(\Omega\) and a regulated tripartition
\[
I_-=(v_1,v_2),\qquad
J=(v_2,v_3),\qquad
I_+=(v_3,v_4),
\]
with cuts
\[
\Gamma_-:=\{v=v_2\},
\qquad
\Gamma_+:=\{v=v_3\}.
\]
Assume the derived fixed-cutoff regulator/collar package established above, and assume that the two null cuts inherit the ordinary or central-defect boundary-redundancy data of Proposition~\ref{prop:regulatedrealization} in the following precise sense:
\begin{enumerate}[leftmargin=2em,label=(\roman*)]
\item each cut \(\Gamma_\pm\) carries a compact derived boundary action \(\widehat K_\pm\) on a reference cut Hilbert space, with \(\widehat K_\pm=K_\pm\) on the ordinary branch;
\item in a compatible type-I regulator presentation, the adjacent regions carry inverse transport across each cut, so for irreducible \(\widehat K_\pm\)-modules \(W_{\alpha_\pm}\) one has decompositions
\[
\tilde{\mathcal H}_{I_-}
\cong
\bigoplus_{\alpha_-}
W_{\alpha_-}\otimes \mathcal H_{i_-^{\alpha_-}},
\]
\[
\tilde{\mathcal H}_{J}
\cong
\bigoplus_{\alpha_-,\alpha_+}
W_{\alpha_-}^{*}\otimes
\mathcal H_{j^{\alpha_-,\alpha_+}}\otimes
W_{\alpha_+},
\]
\[
\tilde{\mathcal H}_{I_+}
\cong
\bigoplus_{\alpha_+}
W_{\alpha_+}^{*}\otimes \mathcal H_{i_+^{\alpha_+}};
\]
\item the gauge-invariant strip algebra is the commutant of the transported boundary action on \(\tilde{\mathcal H}_J\), so that the pair \((\alpha_-,\alpha_+)\) is a central cut label;
\item for each \((\alpha_-,\alpha_+)\), the multiplicity space \(\mathcal H_{j^{\alpha_-,\alpha_+}}\) admits a chosen factorization
\[
\mathcal H_{j^{\alpha_-,\alpha_+}}
\cong
\mathcal H_{j_L^{\alpha_-,\alpha_+}}\otimes
\mathcal H_{j_R^{\alpha_-,\alpha_+}}
\]
such that, blockwise, \(\mathcal A(I_-\cup J)\) acts only on
\(\mathcal H_{i_-^{\alpha_-}}\otimes \mathcal H_{j_L^{\alpha_-,\alpha_+}}\)
and \(\mathcal A(J\cup I_+)\) acts only on
\(\mathcal H_{j_R^{\alpha_-,\alpha_+}}\otimes \mathcal H_{i_+^{\alpha_+}}\).
\end{enumerate}
Then the strip algebra has the inherited central decomposition
\[
\mathcal A(J)
\cong
\bigoplus_{\alpha_-,\alpha_+}
\mathcal B(\mathcal H_{j^{\alpha_-,\alpha_+}}),
\qquad
Z(\mathcal A(J))
=
\bigoplus_{\alpha_-,\alpha_+}\mathbb C\,P_{\alpha_-,\alpha_+},
\]
and, under item (iv),
\[
\mathcal A(J)
\cong
\bigoplus_{\alpha_-,\alpha_+}
\mathcal B(\mathcal H_{j_L^{\alpha_-,\alpha_+}})
\otimes
\mathcal B(\mathcal H_{j_R^{\alpha_-,\alpha_+}}).
\]
The glued tripartition carries the block decomposition
\[
\mathcal H_{I_-\cup J\cup I_+}
\cong
\bigoplus_{\alpha_-,\alpha_+}
\mathcal H_{i_-^{\alpha_-}}
\otimes
\mathcal H_{j_L^{\alpha_-,\alpha_+}}
\otimes
\mathcal H_{j_R^{\alpha_-,\alpha_+}}
\otimes
\mathcal H_{i_+^{\alpha_+}}.
\]
Thus the two null cuts transfer the same center data as the spatial collar branch, while the left/right split of the strip multiplicity spaces is exactly the extra decomposition-inheritance hypothesis and is not forced by center transfer alone.
\end{proposition}

\begin{proof}
By complete reducibility of the finite-dimensional unitary actions \(\widehat K_\pm\), the displayed decompositions of \(\tilde{\mathcal H}_{I_-}\), \(\tilde{\mathcal H}_J\), and \(\tilde{\mathcal H}_{I_+}\) exist. Under item (iii), the strip algebra is the commutant of the transported \(\widehat K_-\times \widehat K_+\) action on
\[
\tilde{\mathcal H}_J
=
\bigoplus_{\alpha_-,\alpha_+}
W_{\alpha_-}^{*}\otimes
\mathcal H_{j^{\alpha_-,\alpha_+}}\otimes
W_{\alpha_+}.
\]
Write an operator \(X\in \mathcal B(\tilde{\mathcal H}_J)\) in matrix form relative to that direct sum. The block
\[
X_{(\alpha_-,\alpha_+),(\beta_-,\beta_+)}
\]
intertwines
\[
W_{\alpha_-}^{*}\otimes W_{\alpha_+}
\longrightarrow
W_{\beta_-}^{*}\otimes W_{\beta_+}
\]
for the product action of \(\widehat K_-\times \widehat K_+\). By Schur's lemma, such an intertwiner is zero unless \((\alpha_-,\alpha_+)=(\beta_-,\beta_+)\), and when the sector pair agrees it is scalar on the representation factors. Therefore the commutant is exactly
\[
\mathcal A(J)
\cong
\bigoplus_{\alpha_-,\alpha_+}
\mathcal B(\mathcal H_{j^{\alpha_-,\alpha_+}}),
\]
and the center is generated by the corresponding block projectors \(P_{\alpha_-,\alpha_+}\).

For the glued tripartition, tensor the three regulator Hilbert spaces and decompose:
\[
\tilde{\mathcal H}_{I_-}\otimes \tilde{\mathcal H}_{J}\otimes \tilde{\mathcal H}_{I_+}
\cong
\bigoplus_{\alpha_-,\beta_-,\alpha_+,\beta_+}
(W_{\alpha_-}\otimes W_{\beta_-}^{*})
\otimes
\mathcal H_{i_-^{\alpha_-}}
\otimes
\mathcal H_{j^{\beta_-,\beta_+}}
\otimes
(W_{\beta_+}\otimes W_{\alpha_+}^{*})
\otimes
\mathcal H_{i_+^{\alpha_+}}.
\]
Taking \(\widehat K_-\times\widehat K_+\)-invariants and applying Schur's lemma to each cut gives
\[
(W_{\alpha_-}\otimes W_{\beta_-}^{*})^{\widehat K_-}
\cong
\begin{cases}
\mathbb C, & \alpha_-=\beta_-,\\
0, & \alpha_-\neq \beta_-,
\end{cases}
\qquad
(W_{\beta_+}\otimes W_{\alpha_+}^{*})^{\widehat K_+}
\cong
\begin{cases}
\mathbb C, & \beta_+=\alpha_+,\\
0, & \beta_+\neq \alpha_+,
\end{cases}
\]
so only matching cut sectors survive and one obtains
\[
\mathcal H_{I_-\cup J\cup I_+}
\cong
\bigoplus_{\alpha_-,\alpha_+}
\mathcal H_{i_-^{\alpha_-}}\otimes
\mathcal H_{j^{\alpha_-,\alpha_+}}\otimes
\mathcal H_{i_+^{\alpha_+}}.
\]
If item (iv) holds, substitute the chosen factorization
\[
\mathcal H_{j^{\alpha_-,\alpha_+}}
\cong
\mathcal H_{j_L^{\alpha_-,\alpha_+}}\otimes
\mathcal H_{j_R^{\alpha_-,\alpha_+}}
\]
to obtain the displayed inherited split and the stated action of the left and right union algebras. Nothing in the Schur-lemma argument itself forces item (iv); it is exactly the extra structural condition required to reproduce the same blockwise tensor pattern as Theorem~\ref{thm:markovcollar}.
\end{proof}

\begin{corollary}[Exact or controlled four-term null modular relation on an inherited strip model]\label{cor:n1}
Fix one finite-dimensional regulated strip model satisfying Proposition~\ref{prop:nullec}, and define
\[
\mathfrak M_{I_-:J:I_+}
:=
\left\{
\sigma:\ I(I_-:I_+\mid J)_\sigma=0
\right\},
\]
\[
\delta^{\mathrm M}_{I_-:J:I_+}(\varepsilon)
:=
\sup\left\{
\inf_{\sigma\in\mathfrak M_{I_-:J:I_+}}\|\rho-\sigma\|_1:
I(I_-:I_+\mid J)_\rho\le \varepsilon
\right\}.
\]
For any state \(\eta\) on this strip model, write
\[
\Delta K_J(\eta)
:=
K_{I_-\cup J\cup I_+}(\eta)-K_{I_-\cup J}(\eta)-K_{J\cup I_+}(\eta)+K_J(\eta).
\]

If the reference state \(\omega\) is exact Markov and EC-aligned on this inherited decomposition (the inherited-split form of Definition~\ref{def:ecaligned}, with sector pairs \(\alpha=(\alpha_-,\alpha_+)\) and factors \(j_L,j_R\)), then
\[
\Delta K_J(\omega)\in Z(\mathcal A(J)),
\]
and in the canonical blockwise identification of Proposition~\ref{prop:nullec} one may take
\[
\Delta K_J(\omega)=0.
\]
Equivalently, without fixing that normalization there exists a central operator
\[
K_{\partial,J}(\omega)\in Z(\mathcal A(J))
\]
such that
\[
K_{I_-\cup J\cup I_+}(\omega)
=
K_{I_-\cup J}(\omega)+K_{J\cup I_+}(\omega)-K_J(\omega)+K_{\partial,J}(\omega).
\]

If instead \(I(I_-:I_+\mid J)_\omega\le \varepsilon\), then on this fixed strip model one may choose an exact Markov state \(\widetilde\omega_J\in \mathfrak M_{I_-:J:I_+}\), assumed EC-aligned on the inherited split wherever the central identification below is used (the strip form of the Markov-split alignment hypothesis), with
\[
\|\omega-\widetilde\omega_J\|_1
\le
\delta^{\mathrm M}_{I_-:J:I_+}(\varepsilon).
\]
Define the carried defect operator
\[
\mathfrak D_J(\omega,\widetilde\omega_J)
:=
\Delta K_J(\omega)-\Delta K_J(\widetilde\omega_J).
\]
Then
\[
K_{I_-\cup J\cup I_+}(\omega)
=
K_{I_-\cup J}(\omega)+K_{J\cup I_+}(\omega)-K_J(\omega)
+K_{\partial,J}(\widetilde\omega_J)
+\mathfrak D_J(\omega,\widetilde\omega_J),
\]
where
\[
K_{\partial,J}(\widetilde\omega_J):=\Delta K_J(\widetilde\omega_J)\in Z(\mathcal A(J)).
\]
For every bounded observable \(O\) in \(\mathcal A(I_-\cup J)\) or \(\mathcal A(J\cup I_+)\),
\[
\bigl|\omega(O)-\widetilde\omega_J(O)\bigr|
\le
\|O\|_\infty\,
\delta^{\mathrm M}_{I_-:J:I_+}(\varepsilon).
\]
If the marginals entering \(\Delta K_J\) for \(\omega\) and \(\widetilde\omega_J\) are uniformly faithful with lower spectral bound \(\lambda_\ast>0\), then
\[
\|\mathfrak D_J(\omega,\widetilde\omega_J)\|_\infty
\le
4\lambda_\ast^{-1}\,
\delta^{\mathrm M}_{I_-:J:I_+}(\varepsilon).
\]
Independently, the Fawzi--Renner recovery map supplies a constructive comparison state with trace-norm error
\[
r_{\mathrm{FR}}(\varepsilon)
=
2\sqrt{1-e^{-\varepsilon}}
\le
2\sqrt{\varepsilon}.
\]
Hence the exact four-term strip relation is available only at EC-aligned exact Markovity, or along a controlled strip family on one fixed inherited strip model admitting EC-aligned replacements for which
\[
\delta^{\mathrm M}_{I_-:J:I_+}(\varepsilon_J)\to 0.
\]
In the controlled case, \(\mathfrak D_J\) is carried explicitly at each finite stage.
\end{corollary}

\begin{proof}
Assume first that \(\omega\) is exact Markov and EC-aligned on the inherited split of Proposition~\ref{prop:nullec}. The HJPW structure theorem gives blockwise factorization over a state-dependent decomposition of \(\mathcal H_J\); the alignment hypothesis identifies that decomposition with the inherited split, so that on each sector pair \(\alpha=(\alpha_-,\alpha_+)\),
\[
\omega_{I_-JI_+}|_\alpha
=
p_\alpha\,
\omega_{I_-\,j_L}^{(\alpha)}
\otimes
\omega_{j_R\,I_+}^{(\alpha)}.
\]
Accordingly,
\[
K_{I_-\cup J\cup I_+}(\omega)\big|_\alpha
=
(-\log p_\alpha)\mathbf 1
+
K_{I_-\,j_L}^{(\alpha)}\otimes \mathbf 1_{j_R I_+}
+
\mathbf 1_{I_- j_L}\otimes K_{j_R I_+}^{(\alpha)}.
\]
Tracing over \(I_+\), \(I_-\), or both gives the marginal block formulas
\[
K_{I_-\cup J}(\omega)\big|_\alpha
=
(-\log p_\alpha)\mathbf 1
+
K_{I_-\,j_L}^{(\alpha)}\otimes \mathbf 1_{j_R}
+
\mathbf 1_{I_- j_L}\otimes K_{j_R}^{(\alpha)},
\]
\[
K_{J\cup I_+}(\omega)\big|_\alpha
=
(-\log p_\alpha)\mathbf 1
+
K_{j_L}^{(\alpha)}\otimes \mathbf 1_{j_R I_+}
+
\mathbf 1_{j_L}\otimes K_{j_R I_+}^{(\alpha)},
\]
\[
K_J(\omega)\big|_\alpha
=
(-\log p_\alpha)\mathbf 1
+
K_{j_L}^{(\alpha)}\otimes \mathbf 1_{j_R}
+
\mathbf 1_{j_L}\otimes K_{j_R}^{(\alpha)}.
\]
Subtracting the last three expressions from the first gives zero on every block. Thus, in the canonical blockwise identification supplied by Proposition~\ref{prop:nullec},
\[
\Delta K_J(\omega)=0.
\]
If one chooses to keep the blockwise endpoint-label bookkeeping explicit instead of absorbing those constants into the canonical identification, the remainder is a direct sum of block constants and is therefore central. This yields the stated central form with \(K_{\partial,J}(\omega)\in Z(\mathcal A(J))\).

For the controlled statement, apply Proposition~\ref{prop:controlledmarkov} on this fixed finite-dimensional strip model, relabeling \(A,B,D\) there as \(I_-,J,I_+\). This yields an exact Markov replacement \(\widetilde\omega_J\in \mathfrak M_{I_-:J:I_+}\) with the displayed trace-norm bound. The identity
\[
\Delta K_J(\omega)=\Delta K_J(\widetilde\omega_J)+\mathfrak D_J(\omega,\widetilde\omega_J)
\]
is tautological, so the displayed four-term formula follows from the exact-Markov case applied to \(\widetilde\omega_J\). The observable estimate is immediate from
\[
\bigl|\omega(O)-\widetilde\omega_J(O)\bigr|
\le
\|O\|_\infty\,
\|\omega-\widetilde\omega_J\|_1.
\]
Finally, Proposition~\ref{prop:modulartransport}, again relabeled \(A,B,D\mapsto I_-,J,I_+\), yields the operator-norm bound on \(\mathfrak D_J\) whenever the relevant marginals have the stated lower spectral bound. The Fawzi--Renner estimate is the same one-shot recoverability bound used elsewhere and is independent of the exact-Markov replacement modulus.
\end{proof}

\begin{definition}[Renormalized null modular functional]
For a null interval \(I\) on generator \(\Omega\), let \(K_\partial(I,\Omega)\) denote the central endpoint-label term singled out by Corollary~\ref{cor:n1} on the inherited strip model, or by its controlled exact-Markov replacement when that model is used as reference. Define
\[
\widetilde K[I,\Omega]
:=
K[I,\Omega]-K_\partial(I,\Omega).
\]
For a null half-line \(H_a:=(a,\infty)\), abbreviate
\[
\widetilde K_a(\Omega):=\widetilde K[H_a,\Omega].
\]
\end{definition}

\begin{proposition}[Endpoint-Lipschitz null modular families and weak tail generator]\label{prop:n3}
Under the derived quasi-local propagation and bounded-interval endpoint-Lipschitz control internal to Axiom~\ref{ax:maxent}, the renormalized interval family obeys the following matrix-element bounds on every fixed local-energy-bounded domain. For bounded intervals
\[
I=(a,b),\qquad
I'=(a',b'),
\]
contained in one compact endpoint window,
\[
\bigl|\langle \psi,(\widetilde K[I',\Omega]-\widetilde K[I,\Omega])\phi\rangle\bigr|
\le
C_{\psi,\phi,\Omega}\,\bigl(|a'-a|+|b'-b|\bigr).
\]
In particular the matrix elements of \(\widetilde K[I,\Omega]\) are jointly Lipschitz in the two endpoints and therefore have finite variation there.

For null half-lines \(H_a=(a,\infty)\), one likewise has
\[
\bigl|\langle \psi,(\widetilde K_{a'}(\Omega)-\widetilde K_a(\Omega))\phi\rangle\bigr|
\le
C_{\psi,\phi,\Omega}\,|a'-a|
\]
for \(a,a'\) in every compact window. Hence, for fixed \(\psi,\phi\),
\[
f_{\psi,\phi}(a):=\langle\psi,\widetilde K_a(\Omega)\phi\rangle
\]
is locally Lipschitz and therefore absolutely continuous. Its distributional derivative defines a locally \(L^\infty\) sesquilinear-form density
\[
\langle\psi,q(a,\Omega)\phi\rangle
:=
-\frac{1}{2\pi}\,\partial_a f_{\psi,\phi}(a),
\]
and for \(a<b\),
\[
\langle\psi,(\widetilde K_b(\Omega)-\widetilde K_a(\Omega))\phi\rangle
=
-2\pi\int_a^b \langle\psi,q(v,\Omega)\phi\rangle\,dv.
\]
The object \(q(a,\Omega)\) is the weak tail generator instead of a local operator-valued density; its identification with the positive self-adjoint Borchers generator occurs only after the derived half-sided modular inclusion of Corollary~\ref{cor:n2} and Lemma~\ref{lem:translation}.
\end{proposition}

\begin{proof}
The bounded-interval endpoint-control statement derived from Axiom~\ref{ax:maxent} applies precisely to the renormalized family obtained after removal of the central endpoint term. Therefore, for intervals contained in one fixed compact endpoint window,
\[
\bigl|\langle\psi,(\widetilde K[I',\Omega]-\widetilde K[I,\Omega])\phi\rangle\bigr|
\le
C_{\psi,\phi,\Omega}\,|I'\Delta I|,
\]
where \(I'\Delta I\) is the symmetric difference of the two intervals. If
\[
I=(a,b),\qquad I'=(a',b'),
\]
then
\[
|I'\Delta I|
\le
|a'-a|+|b'-b|,
\]
which gives the displayed joint endpoint-Lipschitz bound.

For half-lines \(H_a=(a,\infty)\) and \(H_{a'}=(a',\infty)\), the symmetric difference is the bounded interval between the two endpoints, so
\[
|H_{a'}\Delta H_a|=|a'-a|.
\]
Because the central endpoint-label term has been removed in the definition of \(\widetilde K_a\), the same endpoint-control estimate yields
\[
\bigl|\langle\psi,(\widetilde K_{a'}(\Omega)-\widetilde K_a(\Omega))\phi\rangle\bigr|
\le
C_{\psi,\phi,\Omega}\,|a'-a|.
\]

Hence, on every compact \(a\)-interval, the function
\[
f_{\psi,\phi}(a):=\langle\psi,\widetilde K_a(\Omega)\phi\rangle
\]
is Lipschitz. A Lipschitz function on a compact interval is absolutely continuous, so it has an almost-everywhere derivative in \(L^\infty\) and obeys the fundamental theorem of calculus:
\[
f_{\psi,\phi}(b)-f_{\psi,\phi}(a)=\int_a^b \partial_v f_{\psi,\phi}(v)\,dv.
\]
Define
\[
\langle\psi,q(v,\Omega)\phi\rangle
:=
-\frac{1}{2\pi}\,\partial_v f_{\psi,\phi}(v)
\]
distributionally. Substituting this definition into the previous identity gives
\[
\langle\psi,(\widetilde K_b(\Omega)-\widetilde K_a(\Omega))\phi\rangle
=
-2\pi\int_a^b \langle\psi,q(v,\Omega)\phi\rangle\,dv.
\]
This is exactly the claimed weak-tail formula.
\end{proof}

\begin{theorem}[Downstream density-upgrade template]\label{lem:density}
Fix a null generator \(\Omega\) and the renormalized half-line family \(\widetilde K_a(\Omega)\) of Proposition~\ref{prop:n3}. For fixed vectors \(\psi,\phi\) in a common dense domain, let
\[
f_{\psi,\phi}(a):=\langle\psi,\widetilde K_a(\Omega)\phi\rangle,
\qquad
q_{\psi,\phi}(a):=\langle\psi,q(a,\Omega)\phi\rangle
=
-\frac{1}{2\pi}\,\partial_a f_{\psi,\phi}(a).
\]
Assume in addition that \(q_{\psi,\phi}\) is weakly differentiable in \(a\), that
\[
\lim_{a\to+\infty} f_{\psi,\phi}(a)=0,
\qquad
\lim_{a\to+\infty} q_{\psi,\phi}(a)=0,
\]
and define distributionally
\[
\langle\psi,p(a,\Omega)\phi\rangle
:=
-\partial_a q_{\psi,\phi}(a)
=
\frac{1}{2\pi}\,\partial_a^2 f_{\psi,\phi}(a).
\]
Then
\[
q_{\psi,\phi}(a)
=
\int_a^\infty \langle\psi,p(v,\Omega)\phi\rangle\,dv,
\]
and
\[
\langle\psi,\widetilde K_a(\Omega)\phi\rangle
=
2\pi\int_a^\infty (v-a)\,\langle\psi,p(v,\Omega)\phi\rangle\,dv.
\]
This statement is not part of the present fixed-cutoff bridge; it records the exact additional input/output package carried into the downstream density-upgrade task.
\end{theorem}

\paragraph{Null half-line blow-up net.}
Fix a smooth cut point and choose affine coordinate \(v\) on generator \(\Omega\) so that the cut sits at \(v=0\). For \(a\ge 0\), write
\[
H_a:=(a,\infty),
\qquad
\mathcal M_a(\Omega)
:=
\overline{\bigvee_{a<c<d<\infty}\mathcal A((c,d),\Omega)}.
\]
Thus \(\mathcal M_a(\Omega)\) is the half-line blow-up algebra generated by bounded null interval algebras inside \(H_a\). By isotony of the null interval net,
\[
a\le b
\quad\Longrightarrow\quad
\mathcal M_b(\Omega)\subseteq \mathcal M_a(\Omega).
\]

\begin{corollary}[Derived half-sided modular inclusion on null half-lines]\label{cor:n2}
On the scaling-limit geometric-cap branch of Theorem~\ref{thm:bw}, the blow-up modular action near a smooth entangling cut acts on the null coordinate by
\[
v\mapsto e^{-2\pi t}v.
\]
Therefore, for every \(a\ge 0\),
\[
\sigma_t^\omega\bigl(\mathcal M_a(\Omega)\bigr)
=
\mathcal M_{e^{-2\pi t}a}(\Omega).
\]
Hence, for every \(a>0\),
\[
\sigma_t^\omega\bigl(\mathcal M_a(\Omega)\bigr)\subseteq \mathcal M_a(\Omega)
\qquad (t\le 0),
\]
so the inclusion
\[
\mathcal M_a(\Omega)\subset \mathcal M_0(\Omega)
\]
is half-sided modular. Equivalently, after the harmless convention change \(t\mapsto -t\), one recovers the standard positive-time half-sided-inclusion form. The half-sided-inclusion step is therefore derived from the null-interval structure, isotony, and the scaling-limit geometric action instead of imported as an additional modular-QFT ingredient.
\end{corollary}

\begin{proof}
By Theorem~\ref{thm:bw}, on every controlled collar family whose carried remainder vanishes in the refinement limit, the cap modular flow converges to the exact geometric cap dilation with \(2\pi\) normalization. Blow up the cap near a smooth cut and restrict to the chosen null generator. In that tangent limit, the cap-preserving flow becomes the null dilation \(v\mapsto e^{-2\pi t}v\). For every bounded interval \((c,d)\subset H_a\), the blow-up action therefore sends
\[
\mathcal A((c,d),\Omega)\longmapsto \mathcal A((e^{-2\pi t}c,e^{-2\pi t}d),\Omega).
\]
Taking the von Neumann closure of the algebra generated by all such intervals gives
\[
\sigma_t^\omega(\mathcal M_a(\Omega))
=
\mathcal M_{e^{-2\pi t}a}(\Omega).
\]
If \(t\le 0\), then \(e^{-2\pi t}a\ge a\), hence
\[
H_{e^{-2\pi t}a}\subseteq H_a.
\]
Isotony of the null interval net therefore implies
\[
\mathcal M_{e^{-2\pi t}a}(\Omega)\subseteq \mathcal M_a(\Omega).
\]
This is exactly the half-sided modular-inclusion property for the pair \(\mathcal M_a(\Omega)\subset \mathcal M_0(\Omega)\). Reparametrizing the modular parameter by \(t\mapsto -t\) gives the more common positive-time convention if desired.
\end{proof}

\begin{lemma}[Positive null-translation generator]\label{lem:translation}
For the derived half-sided modular inclusion
\[
\mathcal M_a(\Omega)\subset \mathcal M_0(\Omega)
\qquad (a>0)
\]
of Corollary~\ref{cor:n2}, let \(\Delta_0(\Omega)\) be the modular operator of the standard pair \((\mathcal M_0(\Omega),\omega)\) and define
\[
K_0(\Omega):=-\log \Delta_0(\Omega).
\]
Then Borchers--Wiesbrock yields a unique strongly continuous one-parameter unitary group
\[
U_\Omega(a)=e^{iaP_\Omega},
\qquad a\in\mathbb R,
\]
such that
\[
U_\Omega(a)\omega=\omega,
\qquad
U_\Omega(a)\,\mathcal M_b(\Omega)\,U_\Omega(a)^*=\mathcal M_{a+b}(\Omega)
\quad (a,b\ge 0),
\]
and whose generator \(P_\Omega\) is positive and self-adjoint on the Stone domain
\[
D(P_\Omega)
:=
\left\{
\psi\in\mathcal H:
\lim_{a\to 0}\frac{U_\Omega(a)\psi-\psi}{ia}\ \text{exists}
\right\}.
\]
Also,
\[
\Delta_0(\Omega)^{it}U_\Omega(a)\Delta_0(\Omega)^{-it}
=
U_\Omega(e^{-2\pi t}a),
\qquad
\Delta_0(\Omega)^{it}P_\Omega\Delta_0(\Omega)^{-it}
=
e^{-2\pi t}P_\Omega,
\]
and on the common invariant analytic core of \(K_0(\Omega)\) and \(P_\Omega\),
\[
[K_0(\Omega),P_\Omega]=-\,i\,2\pi P_\Omega.
\]

For each \(a\ge 0\), let \(\Delta_a(\Omega)\) be the modular operator of the translated standard pair \((\mathcal M_a(\Omega),\omega)\) and define
\[
K_a(\Omega):=-\log \Delta_a(\Omega).
\]
Then
\[
\Delta_a(\Omega)=U_\Omega(a)\Delta_0(\Omega)U_\Omega(a)^*,
\qquad
K_a(\Omega)=U_\Omega(a)K_0(\Omega)U_\Omega(a)^*,
\]
hence
\[
K_a(\Omega)=K_0(\Omega)-2\pi a\,P_\Omega
\]
as a quadratic-form identity on \(D(K_0(\Omega))\cap D(P_\Omega)\). Equivalently,
\[
\langle\psi,(K_b(\Omega)-K_a(\Omega))\phi\rangle
=
-2\pi(b-a)\,\langle\psi,P_\Omega\phi\rangle
\]
for all \(\psi,\phi\in D(K_0(\Omega))\cap D(P_\Omega)\).

In the canonical blockwise normalization of Corollary~\ref{cor:n1}, where the half-line endpoint term has been absorbed into the central part, the weak endpoint derivative of Proposition~\ref{prop:n3} agrees with the Borchers generator:
\[
\langle\psi,P_\Omega\phi\rangle
=
-\frac{1}{2\pi}\frac{d}{da}\Big|_{a=0^+}
\langle\psi,\widetilde K_a(\Omega)\phi\rangle
\]
for the same domain vectors. The half-sided-inclusion step proves only this affine half-line pair \((K_0(\Omega),P_\Omega)\); bounded-interval modular-Hamiltonian formulas are downstream consequences of the bounded-interval kernel discharged in Lemma~\ref{lem:bounded-interval-kernel}.
\end{lemma}

\begin{proof}
Corollary~\ref{cor:n2} gives the required half-sided modular inclusion. The standard Borchers--Wiesbrock theorem for a standard half-sided inclusion~\cite{wiesbrock93} then yields a unique strongly continuous unitary group \(U_\Omega(a)\) with \(U_\Omega(a)\omega=\omega\), the translation law for the nested half-line net, and a positive self-adjoint generator \(P_\Omega\); Stone's theorem gives the displayed domain formula.

The affine covariance relation
\[
\Delta_0(\Omega)^{it}U_\Omega(a)\Delta_0(\Omega)^{-it}
=
U_\Omega(e^{-2\pi t}a)
\]
is the Borchers relation. Differentiating at \(a=0\) gives
\[
\Delta_0(\Omega)^{it}P_\Omega\Delta_0(\Omega)^{-it}
=
e^{-2\pi t}P_\Omega.
\]
Since \(\Delta_0(\Omega)^{it}=e^{-itK_0(\Omega)}\), differentiating at \(t=0\) on the common analytic core yields
\[
-i[K_0(\Omega),P_\Omega]=-2\pi P_\Omega,
\]
hence
\[
[K_0(\Omega),P_\Omega]=-\,i\,2\pi P_\Omega.
\]

Because \(U_\Omega(a)\omega=\omega\) and
\[
\mathcal M_a(\Omega)=U_\Omega(a)\mathcal M_0(\Omega)U_\Omega(a)^*,
\]
the modular operator of the translated standard pair is
\[
\Delta_a(\Omega)=U_\Omega(a)\Delta_0(\Omega)U_\Omega(a)^*,
\]
so
\[
K_a(\Omega)=U_\Omega(a)K_0(\Omega)U_\Omega(a)^*.
\]
Differentiating this identity in \(a\) on \(D(K_0(\Omega))\cap D(P_\Omega)\) gives
\[
\frac{d}{da}K_a(\Omega)
=
i[P_\Omega,K_a(\Omega)]
=
-2\pi P_\Omega,
\]
because the commutator relation just proved is invariant under conjugation by \(U_\Omega(a)\). Integrating from \(0\) to \(a\) yields the displayed quadratic-form identity, and taking matrix elements gives the equivalent form. Proposition~\ref{prop:n3} had produced the weak endpoint derivative of the renormalized half-line family; in the canonical normalization of Corollary~\ref{cor:n1} the central term has been removed, so that weak derivative is exactly the Borchers generator. The final sentence is the explicit claim boundary: bounded intervals require the additional projective interval action not supplied by half-sided inclusion alone.
\end{proof}

\begin{theorem}[The half-line generator is the local null-stress charge]\label{thm:stress}
Fix a null generator \(\Omega\) and work in the canonical blockwise normalization of Corollary~\ref{cor:n1}. Let \(\widetilde K_a(\Omega)\) denote the renormalized modular Hamiltonian of the half-line \(H_a\), and let \(P_\Omega\) be the positive Borchers generator of Lemma~\ref{lem:translation}. Then on
\[
D_\Omega:=D(K_0(\Omega))\cap D(P_\Omega)
\]
one has
\[
\langle\psi,P_\Omega\phi\rangle
=
-\frac{1}{2\pi}\frac{d}{da}\Big|_{a=0^+}
\langle\psi,\widetilde K_a(\Omega)\phi\rangle
\qquad (\psi,\phi\in D_\Omega),
\]
and this operator is exactly the local null-stress charge of the effective spacetime description on that same half-line family.

Equivalently, if the effective spacetime description writes the same renormalized family as
\[
\widetilde K^{\mathrm{eff}}_a(\Omega)
=
2\pi\,Q^{\mathrm{mod}}_a(\Omega)+K_{\partial}(a,\Omega),
\]
with \(Q^{\mathrm{mod}}_a(\Omega)\) the standard local null modular-energy term and \(K_{\partial}(a,\Omega)\) central and endpoint-supported, then
\[
Q_{kk}(\Omega)
:=
-\frac{1}{2\pi}\frac{d}{da}\Big|_{a=0^+}\widetilde K^{\mathrm{eff}}_a(\Omega)
\]
satisfies
\[
P_\Omega = Q_{kk}(\Omega)
\]
as a quadratic-form identity on \(D_\Omega\).

Hence the renormalized half-line null generator is not a separate EFT-side input: it is the same operator that the effective spacetime description calls the local null-stress charge of the null half-line.
\end{theorem}

\begin{proof}
Lemma~\ref{lem:translation} proves the first displayed identity: in the canonical normalization of Corollary~\ref{cor:n1}, the weak endpoint derivative of the renormalized half-line family is exactly the Borchers generator. Passing to the effective spacetime description does not change the operator family; it rewrites the same \(\widetilde K_a(\Omega)\) in local continuum variables appropriate to the local Lorentzian regime. In that description, the local null-stress charge is precisely the right endpoint derivative
\[
-\frac{1}{2\pi}\frac{d}{da}\Big|_{a=0^+}\widetilde K^{\mathrm{eff}}_a(\Omega)
\]
of the same half-line modular family. Because \(\widetilde K^{\mathrm{eff}}_a(\Omega)\) and \(\widetilde K_a(\Omega)\) represent the same renormalized modular Hamiltonians, their right derivatives agree on \(D_\Omega\). Therefore the OPH generator and the effective null-stress charge coincide:
\[
P_\Omega = Q_{kk}(\Omega).
\]
The endpoint-supported central term does not alter the noncentral generator; in the canonical blockwise normalization it is absorbed into the central part fixed in Corollary~\ref{cor:n1}. This proves the identification.
\end{proof}

\paragraph{Imported input and downstream boundary.}
The only continuum input used above is the standard local modular-Hamiltonian form on the effective description of that same half-line family. It is used only to name, in continuum language, the operator fixed by the OPH half-line derivative. There is no separate ``null-stress identification'' assumption. The downstream boundary is only:
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item transport of the half-line statement to bounded null intervals, carried by the affine/projective covariance and endpoint control of Lemma~\ref{lem:bounded-interval-kernel}; and
\item reconstruction of a full local symmetric tensor from the directional charges, which is determined only up to the null-invisible metric term \(\phi g_{ab}\).
\end{enumerate}
So the gap closed here is the generator/charge identification itself: inside the null bridge and on the declared half-line family, \(P_\Omega\) is exactly the local null-stress charge.

\begin{lemma}[Null data determine the stress tensor modulo a metric term]\label{lem:nullreconstruct}
Let \(X_{ab}\) be a symmetric tensor. If
\[
X_{ab}k^ak^b=0
\]
for every null vector \(k\) at a point, then
\[
X_{ab}=\phi g_{ab}
\]
for some scalar \(\phi\).
\end{lemma}

\begin{proof}
Write
\[
X_{ab}=Y_{ab}+\phi g_{ab}
\]
with \(Y_{ab}\) traceless. Since \(g_{ab}k^ak^b=0\) on null vectors, the hypothesis implies \(Y_{ab}k^ak^b=0\) for all null \(k\). In local inertial coordinates let \(k=(1,\hat n)\) with \(|\hat n|=1\). Then
\[
Y_{ab}k^ak^b
=
Y_{00}+2\hat n^iY_{0i}+\hat n^i\hat n^jY_{ij}.
\]
Oddness under \(\hat n\mapsto-\hat n\) forces \(Y_{0i}=0\). Averaging that relation over \(S^2\) gives
\[
Y_{00}+\frac13\delta^{ij}Y_{ij}=0.
\]
Tracelessness of \(Y_{ab}\) gives
\[
-Y_{00}+\delta^{ij}Y_{ij}=0,
\]
so both \(Y_{00}\) and the spatial trace \(\delta^{ij}Y_{ij}\) vanish. The condition is therefore
\[
\hat n^i\hat n^j Y_{ij}^{\mathrm{TF}}=0
\qquad
\text{for all }\hat n\in S^2,
\]
where \(Y_{ij}^{\mathrm{TF}}\) is the traceless spatial part. The \(\ell=2\) spherical harmonics are linearly independent, so this implies \(Y_{ij}^{\mathrm{TF}}=0\). Hence \(Y_{ab}=0\) and therefore \(X_{ab}=\phi g_{ab}\).
\end{proof}

\begin{remark}[Claim boundary in the null bridge]
The c.12-local bridge ends with explicit theorem-level objects: the positive self-adjoint null-translation generator \(P_\Omega\) on its Stone domain, its Borchers affine covariance relation, the half-line modular identities above, and the exact half-line generator/charge identification of Theorem~\ref{thm:stress}. The downstream boundary is transport to bounded null intervals through Lemma~\ref{lem:bounded-interval-kernel} and the tensor upgrade modulo the null-invisible metric term. The density-upgrade template of Theorem~\ref{lem:density} is recorded separately and does not carry the operator-identification burden.
\end{remark}
\subsubsection{Null-net standardness, derived translations, and the four-translation assembly}
\label{subsec:null-net-standardness}

The bridge above consumes four inputs whose status this subsubsection
settles: (i) cyclicity/separation of the common vector for the
half-line and interval algebras actually used, which the Borchers--Wiesbrock
step requires and which no previous statement proved on the realized branch;
(ii) the inference from locality of the global finite-range MaxEnt generator
to endpoint-Lipschitz control of \emph{reduced} interval modular Hamiltonians,
which is invalid in general; (iii) the affine/projective bounded-interval
covariance used by Lemma~\ref{lem:bounded-interval-kernel}; and (iv) the
compatibility of the per-direction Borchers generators with one four-dimensional
translation representation. Each item below is classified as a finite theorem,
a scaling-limit theorem, or an explicit receipt; no Lorentz or translation
representation is assumed anywhere in this subsubsection before it is derived.

\paragraph{The common null GNS net.}

\begin{definition}[Common null interval net]
\label{def:common-null-gns-net}
Fix the produced support-visible cap pair of Theorem~\ref{thm:bw}, on the
producer branch of Theorem~\ref{thm:certificate-production}, a produced round
cap \(C_0\), and a boundary point \(\xi\in\partial C_0\). Let
\(\{H_a\}_{a\in\mathbb R}\), \(H_a=(a,\infty)\), be the null half-line
blow-up family at \(\xi\) used by Corollary~\ref{cor:n2}, and let
\((\mathcal H,\Omega)\) be the GNS space of the produced scaling-limit state.
For half-lines set \(\mathcal N(H_a)\) equal to the weak closure of the
blow-up strip algebras of Proposition~\ref{prop:nullec}; for a bounded open
interval \(I=(a,b)\) set
\[
\mathcal N(I):=\mathcal N(H_a)\wedge \mathcal N(H_b)',
\]
and for the left half-lines \(\check H_b=(-\infty,b)\) set
\(\check{\mathcal N}(\check H_b):=\mathcal N(H_b)'\wedge\mathcal N(\mathbb R)\),
where \(\mathcal N(\mathbb R)\) is the full blow-up algebra. Isotony holds by
construction, and locality holds in the form
\(\mathcal N(H_b)\subseteq\mathcal N(H_a)'\vee\mathcal N(I)\) inherited from
support-local disjoint commutation of node D1 at every finite stage. The
\emph{nontriviality receipt} \(\mathsf{NTI}_r(d_{\min})\) asserts that at stage
\(r\) every strip difference algebra over a nonempty interval has a
relative commutant of dimension at least \(d_{\min}\geq2\) inside the ambient
strip; on towers where \(\mathsf{NTI}\) holds cofinally, all
\(\mathcal N(I)\neq\mathbb C\,1\).
\end{definition}

\begin{theorem}[Stagewise standardness and its limit]
\label{thm:null-net-standardness}
At every finite stage \(r\), the MaxEnt reference state is faithful on the
finite quotient algebra, so its GNS vector \(\Omega_r\) is separating for
every strip subalgebra. Assume additionally:
\begin{enumerate}[leftmargin=2em]
\item the cap-family-uniform mixed-GNS Cauchy clause of
Definition~\ref{def:finite-cap-bw-certificate} on the blow-up family;
\item the support-visible branch (no support collapse:
Proposition~\ref{prop:commonfloor-collapse} marks the excluded boundary);
\item the \emph{half-line cyclicity receipt} \(\mathsf{Cyc}_r(\delta_r)\):
for every half-line \(H\) of either orientation and every vector in the
stage-\(r\) reference frame of the tower, the subspace
\(\mathcal N_r(H)\Omega_r\) approximates it to accuracy \(\delta_r\), with
\(\delta_r\downarrow0\) cofinally.
\end{enumerate}
Then in the limit net of Definition~\ref{def:common-null-gns-net}:
\begin{enumerate}[leftmargin=2em]
\item \(\Omega\) is cyclic for \(\mathcal N(H)\) for every half-line \(H\) of
either orientation;
\item \(\Omega\) is separating for every \(\mathcal N(H)\) and every
\(\mathcal N(I)\);
\item every inclusion \(\mathcal N(H_{a})\subseteq\mathcal N(H_{b})\)
(\(a\geq b\)) is an inclusion of algebras standard with respect to the same
\(\Omega\).
\end{enumerate}
\end{theorem}

\begin{proof}
Finite stage: a faithful state on a finite-dimensional von Neumann algebra has
a separating GNS vector, and separation passes to subalgebras. Limit
cyclicity: fix \(\psi\in\mathcal H\) and \(\varepsilon>0\); the mixed-GNS
Cauchy clause supplies a stage \(r\) and a reference-frame vector
\(\psi_r\) with \(\|\psi-\psi_r\|<\varepsilon/3\) together with an
approximation of stage-\(r\) strip elements by limit elements with defect
\(<\varepsilon/3\) on \(\Omega\); the receipt \(\mathsf{Cyc}_r(\delta_r)\)
with \(\delta_r<\varepsilon/3\) then gives \(n\in\mathcal N(H)\) with
\(\|n\Omega-\psi\|<\varepsilon\). Separation: the opposite-orientation
half-line \(\check H\) obeys
\(\check{\mathcal N}(\check H)\subseteq\mathcal N(H)'\) by locality, and
\(\Omega\) is cyclic for \(\check{\mathcal N}(\check H)\) by item (1);
a vector cyclic for a subalgebra of the commutant is separating for the
algebra. Intervals inherit separation from
\(\mathcal N(I)\subseteq\mathcal N(H_a)\). Standardness of the inclusions is
the conjunction of (1) and (2) for both members.
\end{proof}

\begin{remark}[Reeh--Schlieder upgrade: interval cyclicity is derived, not assumed]
\label{rem:reeh-schlieder-upgrade}
Cyclicity for \emph{bounded} intervals is deliberately not a receipt. After
Theorem~\ref{thm:derived-hsm-production} below produces the positive
translation generator, the standard Reeh--Schlieder/Borchers argument applies:
given weak additivity
\(\bigvee_{a}U(a)\mathcal N(I)U(a)^{*}=\mathcal N(\mathbb R)\) (a finite-stage
receipt on the same tower), positivity of \(P\) makes
\(a\mapsto U(a)\) boundary values of an operator-valued analytic function, and
the usual edge-of-the-wedge argument propagates cyclicity from half-lines to
every \(\mathcal N(I)\), \(I\) open nonempty. Thus interval standardness is a
theorem downstream of one half-line receipt, not an independent assumption.
\end{remark}

\paragraph{The derived half-sided inclusion.}

\begin{theorem}[Produced geometric dilation and derived half-sided inclusion]
\label{thm:derived-hsm-production}
On the producer branch of Theorem~\ref{thm:certificate-production}, the
modular automorphism group \(\sigma^{\Omega}_t\) of
\((\mathcal N(H_0),\Omega)\) acts on the blow-up net by the produced cap flow:
\[
\sigma^{\Omega}_t\bigl(\mathcal N(H_a)\bigr)=\mathcal N\bigl(H_{e^{-2\pi t}a}\bigr),
\qquad a\geq0 .
\]
In particular \(\Delta^{it}\mathcal N(H_1)\Delta^{-it}\subseteq\mathcal N(H_1)\)
for \(t\leq0\), so \(\bigl(\mathcal N(H_1)\subseteq\mathcal N(H_0),\Omega\bigr)\)
is a half-sided modular inclusion of algebras standard by
Theorem~\ref{thm:null-net-standardness}. No dilation, translation, or Lorentz
unitary is assumed: the geometric action is the support-flow identification
produced by Theorems~\ref{thm:certificate-production} and \ref{thm:bw},
transported through the blow-up exactly as in Corollary~\ref{cor:n2}. The
Borchers--Wiesbrock theorem~\cite{wiesbrock93,arakiZsido05} then yields a
unique strongly continuous unitary group \(U(a)=e^{iaP}\) with
\begin{enumerate}[leftmargin=2em]
\item \(P\geq0\) self-adjoint on its Stone domain, \(U(a)\Omega=\Omega\);
\item \(U(a)\mathcal N(H_b)U(a)^{*}=\mathcal N(H_{a+b})\) for \(a\geq 0\), and
for all \(a\in\mathbb R\) on the algebras where both sides are defined;
\item \(\Delta^{it}U(a)\Delta^{-it}=U(e^{-2\pi t}a)\) and \(JU(a)J=U(-a)\).
\end{enumerate}
This re-derives Corollary~\ref{cor:n2} and Lemma~\ref{lem:translation} with
the declared scaling-limit branch replaced by the produced one, and with the
standardness hypotheses of the Borchers--Wiesbrock input proved rather
than labeled.
\end{theorem}

\begin{proof}
The produced cap flow of Theorem~\ref{thm:bw} is, on the blow-up family, the
one-parameter dilation of the half-line endpoint with the certified \(2\pi\)
normalization; this is precisely the computation of Corollary~\ref{cor:n2},
with the certificate produced by Theorem~\ref{thm:certificate-production}
instead of declared. Monotonicity \(e^{-2\pi t}\geq1\) for \(t\leq0\) gives
the compression property. Theorem~\ref{thm:null-net-standardness} supplies the
standard-pair hypotheses. The conclusion package, including the Stone domain
and the affine commutation relations, is the corrected Borchers--Wiesbrock
theorem~\cite{wiesbrock93,arakiZsido05}.
\end{proof}

\paragraph{Regional modular locality: theorem and counterexample boundary.}

\begin{theorem}[Markov modular locality on the central-interface branch]
\label{thm:markov-modular-locality}
Work on the declared central-interface branch of Axiom~\ref{ax:maxent}, on
which Theorem~\ref{thm:msaderivation} derives exact collar Markovianity of the
MaxEnt reference states across every collar cut. Let \(I\) be a strip interval
whose two endpoint cuts both carry the exact Markov property. Then the reduced
modular Hamiltonian \(K_I=-\log\rho_I\) decomposes as
\[
K_I=\sum_{\text{cells } c\subseteq I}k_c \;+\; k^{L}_{\partial I}+k^{R}_{\partial I},
\]
where each \(k_c\) is the retained local MaxEnt term of cell \(c\) and the two
boundary blocks act on the Hayden--Jozsa--Petz--Winter interface factors of
the corresponding cuts~\cite{hjpw04}, with
\(\|k^{L/R}_{\partial I}\|\) bounded by the uniform interface constants of the
declared collar family, independently of \(|I|\). Consequently the
renormalized half-line family of Corollary~\ref{cor:n1} has endpoint-Lipschitz
matrix elements on the finite-rank domain of Proposition~\ref{prop:n3}, with
Lipschitz constant the uniform interface bound. This replaces the earlier
informal inference from locality of the \emph{global} generator, which is
invalid without the Markov clause by
Proposition~\ref{prop:gibbs-modular-nonlocality-witness}.
\end{theorem}

\begin{proof}
Vanishing conditional mutual information across a cut
\(I(A:C\mid B)_{\rho}=0\) gives, by the structure
theorem~\cite{hjpw04}, a decomposition of the cut collar
\(\mathcal H_B=\bigoplus_k\mathcal H_{b_k^{L}}\otimes\mathcal H_{b_k^{R}}\)
with
\(\rho_{ABC}=\bigoplus_k p_k\,\rho_{Ab_k^{L}}\otimes\rho_{b_k^{R}C}\).
Applying this at both endpoint cuts of \(I\) and restricting to \(I\) yields
\(\rho_I=\bigoplus_{k,l}p_{kl}\,
\rho^{L}_{k}\otimes\rho^{\mathrm{bulk}}_{I}\otimes\rho^{R}_{l}\)
with the bulk factor the MaxEnt Gibbs state of the retained cell terms in
\(I\); taking \(-\log\) gives the displayed sum, the direct-sum labels being
carried by the central interface projections, whose blocks are exactly
\(k^{L/R}_{\partial I}\). The interface blocks are functions of the boundary
charges retained by the central-interface clause, so their norms carry the
declared uniform constants. Endpoint variation of \(K_{I_a}\) then changes
only one boundary block and the cells in the swept collar, giving the
Lipschitz bound cellwise.
\end{proof}

\begin{proposition}[Finite witness: Gibbs locality does not imply modular locality]
\label{prop:gibbs-modular-nonlocality-witness}
There is an explicit four-site spin chain with translation-invariant
nearest-neighbour Hamiltonian \(H\) and inverse temperature \(\beta=1\) such
that, for \(I\) the first three sites, the interaction expansion of
\(-\log\rho_I\) contains a nonzero term coupling the two endpoint sites of
\(I\) whose norm exceeds every bound obtained from the naive locality
inference; the witness values are machine-verified by exact diagonalization
with certified tolerances in the repository receipts. Hence exact or controlled Markovianity (or the
central-interface clause that derives it) is a genuine additional hypothesis,
and the boundary between Theorem~\ref{thm:markov-modular-locality} and its
failure is exactly the failure of collar Markovianity, quantified by the
collar conditional mutual information.
\end{proposition}

\begin{proof}
Take \(H=\sum_{i=1}^{3}\bigl(Z_iZ_{i+1}+gX_i\bigr)+gX_4\) with \(g=1\). At
second order in \(\beta\), the cluster expansion of \(-\log\rho_I\) acquires
the commutator correction
\(\tfrac{\beta^2}{2}\,\mathbb E_{\mathrm{tr}}\!\left[[H_{I\partial},H_{\partial I^c}]\right]\)-type
terms which do not cancel for noncommuting nearest-neighbour couplings and
which, after the partial trace over site 4, generate a weight-two Pauli term
supported on sites \(\{1,3\}\); its coefficient is nonzero at \(g=1\),
\(\beta=1\), as certified numerically to interval-arithmetic accuracy in the
repository receipt. Since the collar CMI of this state across the cut
\(3\,|\,4\) is strictly positive (also certified), the example sits strictly
outside the Markov branch, as claimed.
\end{proof}

\paragraph{Bounded intervals and the four-translation assembly.}

\begin{theorem}[M\"obius covariance and the projective bounded-interval action]
\label{thm:mobius-bounded-intervals}
Assume Theorem~\ref{thm:derived-hsm-production} for the half-line family at
\(\xi\) and for the opposite-orientation family (equivalently, the reflected
inclusion obtained from \(J\mathcal N(H_0)J\)), with common \(\Omega\), on a
tower carrying \(\mathsf{NTI}\) cofinally. Then the two derived translation
groups and the modular dilations generate a strongly continuous (anti-)unitary
positive-energy representation of \(\mathrm{PSL}(2,\mathbb R)\) acting on the
compactified null line~\cite{wiesbrock93,glw98}, and
\[
\mathcal N(gI)=U_g\,\mathcal N(I)\,U_g^{*}
\]
for every M\"obius \(g\) and bounded or half-infinite \(I\), with isotony and
locality preserved. The bounded-interval modular kernels are the projective
transports of the half-line kernels; if the finite-stage kernel residuals obey
\(\epsilon_r=o(\ell_r^4)\) along the declared scaling, the transported kernels
satisfy the \(o(\ell^4)\) requirement consumed by
Lemma~\ref{lem:bounded-interval-kernel}. The projective bounded-interval
covariance previously used is therefore derived on this branch, with the
kernel-residual scaling the only quantitative receipt.
\end{theorem}

\begin{proof}
The generating result for two half-sided modular inclusions with common
standard vector is the Wiesbrock/Guido--Longo--Wiesbrock
theorem~\cite{wiesbrock93,glw98}: the modular group of
\(\mathcal N(H_0)\) and the two derived translation groups satisfy the
\(\mathrm{PSL}(2,\mathbb R)\) commutation relations proved in
Theorem~\ref{thm:derived-hsm-production}(3) and its reflection; integrability
to the simply connected cover and descent to \(\mathrm{PSL}(2,\mathbb R)\)
follow from the affine relations plus \(U(a)\Omega=\Omega\), and positivity of
the rotation generator is equivalent to positivity of the two translation
generators. Covariant interval algebras are then defined by transport;
consistency on overlaps of group elements mapping \(I\) to itself follows
because the stabilizer of an interval is generated by its own modular
dilations, which fix \(\mathcal N(I)\) by Takesaki modular
theory~\cite{takesaki72}. \(\mathsf{NTI}\) guarantees the transported algebras
are nontrivial and that intersections realize
\(\mathcal N(I)=\mathcal N(H_a)\wedge\mathcal N(H_b)'\). The kernel-residual
propagation is linear along the transport, giving the stated \(o(\ell^4)\)
transfer.
\end{proof}

\begin{definition}[Modular-intersection receipt]
\label{def:modular-intersection-receipt}
For two produced caps \(C,\tilde C\) with transverse boundary circles, write
\(\mathsf{MI}_r(C,\tilde C;\varepsilon)\) for the finite-stage statement that
the stage-\(r\) modular data of the pair
\(\bigl(\mathcal M_r(C),\mathcal M_r(\tilde C),\Omega_r\bigr)\) satisfy the
Wiesbrock modular-intersection relations~\cite{wiesbrock98} up to residual
\(\varepsilon\): the compressions of each modular group into the intersection
algebra agree with the intersection's own modular group, and the mixed
commutation relations of the two modular groups close on a common dense core.
The receipt is decidable at every finite stage and carries a convergence
envelope \(\varepsilon_r\downarrow0\).
\end{definition}

\begin{theorem}[Four-translation assembly with future-cone spectrum]
\label{thm:four-translation-assembly}
Assume the producer branch with BW framing (so the produced
\(G=\mathrm{SO}^{+}(3,1)\) action on caps is unitarily implemented with
invariant \(\Omega\)), Theorem~\ref{thm:derived-hsm-production} applied at
every produced null direction \(\Omega\in S^2\) (yielding positive generators
\(P_{\Omega}\)), and \(\mathsf{MI}_r\) cofinally on transverse produced cap
pairs. Then:
\begin{enumerate}[leftmargin=2em]
\item (\emph{Covariance; theorem, no receipt.}) For every \(\Lambda\in G\),
\[
U(\Lambda)\,P_{\Omega}\,U(\Lambda)^{*}
=\omega_{\Lambda}(\Omega)\,P_{g_{\Lambda}(\Omega)},
\]
with \(\omega_\Lambda,g_\Lambda\) as in
Theorem~\ref{thm:cap-normal-equivariance}: the blow-up construction is
natural, so the generator transforms with the null-vector weight.
\item (\emph{Additivity on the \(\mathsf{MI}\) branch.}) Generators of
distinct null directions strongly commute on a common core, and whenever
\(\sum_i c_i\,q(\Omega_i)=0\) in \(V\) one has
\(\sum_i c_iP_{\Omega_i}=0\) on that core. Hence there is a unique
four-parameter strongly continuous unitary group \(x\mapsto U(x)\),
\(x\in V\), with self-adjoint generators \(P^{\mu}\) satisfying
\(P(q(\Omega))=P_{\Omega}\).
\item (\emph{Spectrum.}) \(\eta(q,P)\ge0\) for every future null \(q\), so the
joint spectrum of \(P^\mu\) lies in the closed future cone.
\item (\emph{Poincar\'e closure.}) \(U(\Lambda)U(x)U(\Lambda)^{*}=U(\Lambda x)\),
so \((U(\Lambda),U(x))\) is a positive-energy unitary representation of the
proper orthochronous Poincar\'e group~\cite{bgl93}.
\end{enumerate}
A family of per-direction generators without the \(\mathsf{MI}\) relations
does not satisfy item (2); the receipt is exactly the acceptance boundary
between one commuting four-translation representation and unrelated
one-generator-per-direction constructions.
\end{theorem}

\begin{proof}
(1) Conjugating the half-sided inclusion at direction \(\Omega\) by
\(U(\Lambda)\) yields the half-sided inclusion at \(g_\Lambda(\Omega)\) with
the affine parameter rescaled by \(\omega_\Lambda(\Omega)\), by
Theorem~\ref{thm:cap-normal-equivariance} applied to the blow-up family;
uniqueness of the Borchers generator in
Theorem~\ref{thm:derived-hsm-production} then forces the displayed weight.
(2) The \(\mathsf{MI}\) relations in the limit give, for each transverse pair,
the commutation of the associated translation unitaries through the
modular-intersection theorem of~\cite{wiesbrock98}; strong commutativity of
the generators follows on the joint Stone core. For the linearity relation,
fix a dependent family \(\sum_ic_iq(\Omega_i)=0\); the covariance (1) and
commutativity reduce the claim to the stabilizer direction, where the two
sides generate the same one-parameter group by the uniqueness clause of the
Borchers--Wiesbrock theorem applied to the common compressed inclusion; the
finite-stage residual is controlled by \(\varepsilon_r\) and vanishes in the
limit. Uniqueness and existence of \(U(x)\) then follow by choosing four
null directions in general position and checking independence of the choice
via the same relation. (3) is positivity of each \(P_\Omega\) plus density of
\(\{q(\Omega)\}\) in the generating rays of the dual cone. (4) combines (1)
and (2); the group law on the semidirect product holds on the core and
extends by continuity.
\end{proof}

\begin{remark}[Re-audit ledger for the earlier conditional closures]
\label{rem:null-net-reaudit}
Relative to the earlier conditional packets: the left/right null-strip tensor
split of Proposition~\ref{prop:nullec} is a fixed-cutoff branch input;
exact-or-controlled Markovianity is a theorem on the
central-interface branch (Theorem~\ref{thm:markov-modular-locality}) with an
explicit counterexample boundary
(Proposition~\ref{prop:gibbs-modular-nonlocality-witness}); the standardness
hypotheses consumed by every Borchers--Wiesbrock invocation are proved
(Theorem~\ref{thm:null-net-standardness}), with one half-line cyclicity
receipt and the Reeh--Schlieder upgrade
(Remark~\ref{rem:reeh-schlieder-upgrade}); the half-sided inclusion itself is
derived on the produced branch (Theorem~\ref{thm:derived-hsm-production});
bounded-interval projective covariance is derived
(Theorem~\ref{thm:mobius-bounded-intervals}) with the kernel-residual scaling
as the only quantitative receipt; and the four-translation assembly is a
theorem on the \(\mathsf{MI}\) branch
(Theorem~\ref{thm:four-translation-assembly}). Finite theorems: stagewise
standardness, receipts decidability, the witness proposition. Scaling-limit
theorems: limit standardness, derived inclusion, M\"obius covariance,
assembly. Branch receipts: \(\mathsf{Cyc}\), \(\mathsf{NTI}\), weak
additivity, \(\mathsf{MI}\), kernel-residual scaling, and the fixed-cutoff
strip split.
\end{remark}

\subsection{From repaired records to a conditional Lorentzian event manifold}
\label{subsec:event-manifold}

Corollaries~\ref{cor:lorentz} and \ref{cor:h3-spatial-chart} are statements
about Lorentz-group and observer-frame \emph{kinematics}: \(H^3\) is the
hyperboloid of future unit timelike frames, not a spatial slice of physical
events, and Remark~\ref{rem:h3-chart-not-populated-bulk} lists what the chart
theorem does not do. The Einstein package below
(Theorems~\ref{thm:equilibrium}--\ref{cor:einstein}) nevertheless consumes a
locally Lorentzian \(d=4\) regime with local inertial coordinates, causal
diamonds, geodesic balls, a metric-compatible connection, and curvature. This
subsection constructs that consumer interface: a quotient-intrinsic event
space \(\mathcal E\), a four-dimensional atlas of signature \((-{+}{+}{+})\),
tetrads, metric, connection, and glued observer clocks, from the outputs of
the producer chain
(Theorems~\ref{thm:certificate-production}, \ref{thm:bw}), the record
localization packet (Corollary~\ref{cor:conditional-record-populated-h3}), and
the derived translations
(Theorems~\ref{thm:derived-hsm-production},
\ref{thm:four-translation-assembly}). The construction cleanly separates the
event-manifold \emph{base} from the \(H^3\) \emph{fiber} of unit timelike
frames at each event, keeps every additional input as an explicitly named
receipt, and closes with countermodels showing that \(\dim H^3=3\) by itself
promotes nothing.

Here ``gluing observer spaces'' is shorthand for a precise descent operation,
not for assuming a pre-existing common space. Located record germs in
different first-person charts are identified when their transported certified
boxes represent the same coincidence class; the overlap-cocycle receipt then
checks that the surviving rank-four chart transitions are compatible
Poincar\'e transformations. The descended event classes, causal order, and
metric are consequently independent of which observer chart presents them.
The three spatial frame responses and the modular clock supply the local
\(3{+}1\) chart; generalized-entropy stationarity and the null-stress bridge,
not gluing alone, supply the subsequent Jacobson-type Einstein equation.

\paragraph{Events as coincidence classes of record germs.}

\begin{definition}[Record germs and intrinsic coincidence]
\label{def:record-coincidence}
Fix a refinement tower on the producer branch. A stage-\(r\) \emph{located
record datum} is a quotient-visible record token \(i\) together with its
certified localization output
\(S_{i}(t)=B_H(\widehat X_i(t),\rho_i(t))\subset H^3_{R_H}\) from
Corollary~\ref{cor:conditional-record-populated-h3} in some observer chart, a
modular clock coordinate \(\tau_i\) read from the derived translation/clock
line of Theorem~\ref{thm:derived-hsm-production} with the certified \(2\pi\)
normalization, and a clock error bar \(\varsigma_i\). Its \emph{certified box}
is \([\tau_i\pm\varsigma_i]\times S_i(t)\) transported between observer charts
by the D1 gauge/transport package and
Theorem~\ref{thm:h3-localization-naturality}. A \emph{record germ} is a
refinement-compatible family \((i_r)_{r\geq r_0}\) of located record data
whose transported certified boxes are nested up to transport defect and whose
radii \(\rho_{i_r}+\varsigma_{i_r}\to0\) cofinally; a germ is a Cauchy filter
of certified boxes. Two germs are \emph{coincident} when, after common
refinement, their transported certified boxes intersect at cofinally many
stages. Coincidence uses only normal-form data: certified balls, clock reads,
and transport maps.
\end{definition}

\begin{lemma}[Quotient, gauge, schedule, refinement, and chart invariance]
\label{lem:event-quotient-invariance}
The germ set, the coincidence relation, and the box uniformity are invariant
under: repair schedule (Theorem~\ref{thm:confluence} fixes the normal form);
gauge (support covariance of node D1 and
Lemma~\ref{lem:incidence-invariance}); refinement (Petz support/CPTP transport
of certified boxes along the tower maps); and Lorentz chart change
(Theorem~\ref{thm:h3-localization-naturality} for the spatial factor, the
covariance clause of Theorem~\ref{thm:four-translation-assembly}(1) for the
clock factor). In particular coincidence is an observer-independent relation.
\end{lemma}

\begin{proof}
Each datum entering Definition~\ref{def:record-coincidence} was individually
proved invariant in the quoted statements; intersection and nesting of
transported boxes are expressed through \(\eta\)-invariant quantities
(hyperbolic distances, affine clock differences), so the derived relation
inherits every invariance.
\end{proof}

\begin{definition}[Event space and its unconditional regularity class]
\label{def:event-space}
The \emph{event space} \(\mathcal E\) is the set of coincidence classes of
record germs, equipped with the uniformity generated by the certified boxes.
Unconditionally, \(\mathcal E\) is a second-countable, completely regular
uniform space (the tower is countable and each stage carries finitely many
tokens); it need be neither Hausdorff nor a manifold. This is the precise
regularity class obtained without receipts; everything stronger below is
conditional and cited as such.
\end{definition}

\begin{definition}[Event-manifold receipts]
\label{def:event-manifold-receipts}
On a declared bounded region of interest:
\begin{enumerate}[leftmargin=2em]
\item[\(\mathsf{(E1)}\)] \emph{Population density}: every certified box of
every stage contains a germ, and the covering radii shrink with a declared
modulus \(\rho_r\downarrow0\) (record-dense branch).
\item[\(\mathsf{(E2)}\)] \emph{Separation gaps}: distinct germs achieve
certified disjoint boxes at some common stage, with the residual-gap
certificates \(\Delta_{\mathrm{loc}}>0\) of
Theorem~\ref{thm:h3-certified-noisy-uniqueness} uniform on the region.
\item[\(\mathsf{(E3)}\)] \emph{Rank-four frame}: every point of the region is
covered by a calibrated response frame of rank four (a rank-three
conditioned spatial cap frame as in
Proposition~\ref{prop:h3-general-cap-frame-condition}, augmented by one
derived modular clock line), with uniform observability constants
\(0<\alpha\leq L\).
\item[\(\mathsf{(E4)}\)] \emph{Overlap cocycle}: on chart overlaps the frame
transition data agree with a Poincar\'e transformation
(element of \(\mathrm{SO}^{+}(3,1)\ltimes V\)) up to residuals
\(\varepsilon_r\downarrow0\), and the transitions satisfy the cocycle law up
to the same residuals; decidable at every finite stage.
\end{enumerate}
\end{definition}

\begin{theorem}[Conditional event four-manifold]
\label{thm:event-4-manifold}
Assume \(\mathsf{(E1)}\)--\(\mathsf{(E3)}\) on a region. Then the
corresponding subspace \(\mathcal E_U\subseteq\mathcal E\) is Hausdorff,
second countable, and locally compact, and every rank-four frame chart
\[
\varphi:\;\mathcal E_U\supseteq W\longrightarrow\mathbb R^4,
\qquad
\varphi(e)=\bigl(\tau(e),X_{\mathrm E}(e)\bigr)
\]
(clock read, then frame reconstruction as in
Proposition~\ref{prop:h3-general-cap-frame-condition}) is a bi-Lipschitz
homeomorphism onto an open subset of \(\mathbb R^4\) with constants
\(L/\alpha\); overlapping charts have bi-Lipschitz transition maps. Hence
\(\mathcal E_U\) is a topological four-manifold with a locally bi-Lipschitz
atlas. Under the additional second-order response modulus
\(\mathsf{(E4')}\) (uniform \(C^{1,1}\) control of the calibrated responses),
the atlas is \(C^{1,1}\). Without \(\mathsf{(E2)}\) the Hausdorff property can
fail and only Definition~\ref{def:event-space} survives
(Proposition~\ref{prop:event-countermodels}(iii)); without \(\mathsf{(E1)}\)
the dimension can drop
(Proposition~\ref{prop:event-countermodels}(i)).
\end{theorem}

\begin{proof}
\emph{Hausdorff.} Distinct classes contain non-coincident germs, so
\(\mathsf{(E2)}\) supplies a stage with certified disjoint boxes; boxes
generate the uniformity, so the corresponding box neighborhoods separate the
classes. \emph{Second countability} is
Definition~\ref{def:event-space}. \emph{Charts.} On a box neighborhood \(W\),
\(\mathsf{(E3)}\) gives for germ representatives the two-sided bound
\[
\alpha\,\bar d\bigl(e,e'\bigr)\;\leq\;
\bigl|\varphi(e)-\varphi(e')\bigr|\;\leq\;
L\,\bar d\bigl(e,e'\bigr)
\]
with \(\bar d\) the box (product hyperbolic-plus-clock) distance: the spatial
component is Proposition~\ref{prop:h3-general-cap-frame-condition}, the clock
component is the affine clock line with its calibration constants, and the
constants combine in quadrature. Thus \(\varphi\) is injective and
bi-Lipschitz onto its image. \emph{Open image.} \(\mathcal E_U\) is complete
in the box uniformity (germs are Cauchy filters of boxes, and every Cauchy
filter of certified boxes is itself a germ by
Definition~\ref{def:record-coincidence}), so \(\varphi(W)\) is complete,
hence closed in the target box; \(\mathsf{(E1)}\) makes \(\varphi(W)\)
\(\rho_r\)-dense in that box for every \(r\); closed and dense gives the whole
open box. Local compactness follows. Transitions of bi-Lipschitz charts are
bi-Lipschitz; the \(C^{1,1}\) upgrade is the chain rule for the
second-order modulus \(\mathsf{(E4')}\), Rademacher differentiability
supplying the almost-everywhere derivatives with Lipschitz representatives.
The failure statements are the countermodels below.
\end{proof}

\paragraph{Causal structure, signature, and time orientation.}

\begin{definition}[Intrinsic precedence and diamonds]
\label{def:intrinsic-precedence}
For germs \(x,y\), declare \(x\preceq y\) when some located representative of
\(y\) has a validated transactional read-set ancestry (node D1) containing a
located representative of \(x\), cofinally in refinement. The relation is
schedule-independent (ancestry of the normal form is
reachability-invariant by node D1) and gauge/refinement invariant as in
Lemma~\ref{lem:event-quotient-invariance}. Causal diamonds are
\(D(p,q):=\{e\in\mathcal E:\ p\preceq e\preceq q\}\).
\end{definition}

\begin{theorem}[Local cone structure, signature \((-{+}{+}{+})\), and time orientation]
\label{thm:event-causal-structure}
Assume \(\mathsf{(E1)}\)--\(\mathsf{(E4)}\) and the
\(\mathsf{MI}\)/assembly branch of
Theorem~\ref{thm:four-translation-assembly}. Then, near every event \(p\) in
the region:
\begin{enumerate}[leftmargin=2em]
\item the chart \(\varphi\) transports \(\preceq\) to the cone order of
\(\eta\) up to \(o(1)\) envelopes: \(e\in D(p,q)\) iff
\(\varphi(e)-\varphi(p)\) and \(\varphi(q)-\varphi(e)\) lie in the closed
future cone up to the receipt residuals;
\item the local cone at \(p\) is linearly isomorphic to the standard cone of
\(\eta\): its sphere of null generators is the produced celestial \(S^2\) of
Theorem~\ref{thm:conformal-cap-production} with its produced conformal
structure, and a proper convex cone in \(\mathbb R^4\) whose projectivized
boundary is conformally that \(S^2\) is the cone of a quadratic form of
Lorentz signature; hence each tangent space carries signature
\((-{+}{+}{+})\), with exactly one time dimension and three spatial
dimensions;
\item the transactional direction of repair ancestry selects one component of
the timelike double cone at every event, consistently across overlaps
(\(\mathsf{(E4)}\) transitions are orthochronous because they preserve
\(\preceq\)); this is the time orientation;
\item causal compatibility on overlaps: the transition maps preserve cones
and cone orders exactly in the limit, up to the \(\varepsilon_r\) residuals at
finite stage.
\end{enumerate}
\end{theorem}

\begin{proof}
(1) The derived translations move certified boxes along null and timelike
directions of the chart with unit affine weight
(Theorem~\ref{thm:derived-hsm-production}(2)); a located record in the
read-set ancestry of another is connected to it by a finite chain of
transactionally validated collar transports, each of which the blow-up chart
represents inside the closed future cone up to the calibration residuals of
the frame; composing the chain and passing to the germ limit gives the cone
order with \(o(1)\) defect. Conversely, a chart pair in the open cone
interior admits, by \(\mathsf{(E1)}\), a chain of populated boxes realizing
ancestry. (2) The null directions at \(p\) are exactly the blow-up directions
of the produced caps through \(p\)'s boxes, so the projectivized cone boundary
is the produced \(S^2\); if a proper convex cone \(K\subset\mathbb R^4\) has
projectivized boundary a quadric conformally equivalent to the round
\(S^2\subset\mathbb{RP}^3\), then \(K=\{x:\ q(x)\leq0,\ x^0\geq0\}\) for a
quadratic form \(q\) vanishing on that quadric; a real quadratic form in four
variables whose zero set is a nondegenerate real quadric projectively
equivalent to a sphere has signature \((1,3)\) up to overall sign, which is
Lorentz signature; normalizing the time direction inside \(K\) gives
\((-{+}{+}{+})\). (3) Repair transactions are directed (commits are not
invertible moves on the quotient by strict descent), so ancestry orients each
timelike chain; schedule independence makes the orientation well defined on
germs, and \(\mathsf{(E4)}\) transitions preserve \(\preceq\), hence map
future cones to future cones. (4) is \(\mathsf{(E4)}\) plus (2), Poincar\'e
maps being exactly the affine maps preserving \(\eta\)-cones.
\end{proof}

\begin{proposition}[\(H^3\) is the frame fiber over events, not a spatial slice]
\label{prop:h3-fiber-not-slice}
On the branch of Theorem~\ref{thm:event-causal-structure}, define the frame
bundle
\[
F(\mathcal E):=\bigl\{(e,u):\ e\in\mathcal E_U,\
u\in T_e\mathcal E\ \text{future unit timelike}\bigr\}.
\]
Each fiber is the hyperboloid \(H^3\cong\mathrm{SO}^{+}(3,1)/\mathrm{SO}(3)\)
of Corollary~\ref{cor:h3-spatial-chart}, and the record-localization chart of
Corollary~\ref{cor:conditional-record-populated-h3} is a chart on the
\emph{fiber} data of located observers, not on the event base. Moreover, in
the homogeneous local model there is no Lorentz-equivariant section
\(\mathcal E\to F(\mathcal E)\): the stabilizer of an event in the local model
is the full Lorentz group, which fixes no point of \(H^3\)
(Proposition~\ref{prop:h3-frame-space}); selecting \(u\) requires observer,
tetrad, clock, or record data, exactly as in
Remark~\ref{rem:cap-point-no-go-meaning}. Identifying velocity space
\(H^3\) with a spatial slice of \(\mathcal E\) is therefore excluded
structurally, independently of the dimension coincidence
\(\dim H^3=3\).
\end{proposition}

\begin{proof}
The fiber statement is Definition~\ref{def:h3-observer-frames} applied in
\((T_e\mathcal E,g_e)\), which carries Lorentz signature by
Theorem~\ref{thm:event-causal-structure}(2). For the no-section statement,
an equivariant section would assign to the model event a point of \(H^3\)
fixed by its stabilizer \(\mathrm{SO}^{+}(3,1)\), whose point stabilizers on
\(H^3\) are the compact \(\mathrm{SO}(3)\) subgroups; a noncompact group
cannot fix a point with compact stabilizer, as in
Proposition~\ref{prop:no-cap-to-observer-point-map}.
\end{proof}

\paragraph{Tetrads, metric, connection, clocks.}

\begin{theorem}[Tetrads, Lorentzian metric, and curvature readout]
\label{thm:event-tetrad-metric}
Assume \(\mathsf{(E1)}\)--\(\mathsf{(E4)}\). Then:
\begin{enumerate}[leftmargin=2em]
\item each rank-four frame chart defines a tetrad
\(e_{\,\mu}^{a}\) (the frame differentials of the three conditioned cap
responses and the clock line), and the transition functions of overlapping
tetrads are the \(\mathsf{(E4)}\) Poincar\'e data, satisfying the cocycle law
in the limit;
\item \(g:=\eta_{ab}\,e^{a}\otimes e^{b}\) is a well-defined Lorentzian metric
on \(\mathcal E_U\), independent of the chart by (1); its conformal class is
produced (Theorem~\ref{thm:conformal-cap-production} on the celestial factor,
Theorem~\ref{thm:four-translation-assembly} fixing the relative time/space
normalization through the affine clock weights), while the single overall
physical scale is the separate scale certificate
(the \(R_H\)/cell-ruler receipts of Definition~\ref{def:newton}); the Weyl
representative is therefore produced and only the global conformal factor's
absolute normalization is a receipt;
\item on the \(\mathsf{(E4')}\) branch the atlas is \(C^{1,1}\), the
Levi-Civita connection of \(g\) exists with locally bounded Christoffel
symbols, geodesics and geodesic balls exist locally, and the curvature is
defined almost everywhere as a locally bounded measurable readout; on the
declared smooth scaling branch the readout upgrades to the smooth curvature
tensor consumed by Lemma~\ref{lem:smallball} and
Theorems~\ref{thm:fixed-volume-small-ball-area}--\ref{cor:einstein}. This is
the precise interface through which the Einstein package's ``locally
Lorentzian \(d=4\) scaling regime'' is supplied rather than assumed.
\end{enumerate}
\end{theorem}

\begin{proof}
(1) is Theorem~\ref{thm:event-4-manifold} plus \(\mathsf{(E4)}\); tetrad
transitions are the derivatives of the chart transitions, which are affine
Poincar\'e in the limit, so the cocycle law is inherited. (2) The
\(\eta\)-contraction of Poincar\'e-related tetrads is chart-independent;
conformal-class production is quoted; the scale statement repeats
Corollary~\ref{cor:h3-spatial-chart}'s boundary (no physical \(R_H\) from
group data) in the produced setting. (3) On a \(C^{1,1}\) atlas the metric is
Lipschitz, so Christoffel symbols exist a.e.\ and are locally bounded
(Rademacher), local geodesic existence follows from Picard--Lindel\"of with
measurable right-hand side in the Carath\'eodory sense, and the Riemann tensor
is a.e.\ defined and locally bounded; smoothness on the declared branch is a
declared upgrade, exactly as consumed downstream.
\end{proof}

\begin{theorem}[Glued modular clocks and scheduler-independent histories]
\label{thm:clock-gluing}
Assume \(\mathsf{(E1)}\)--\(\mathsf{(E4)}\). Along every maximal
\(\preceq\)-chain of germs carrying frame data (an observer history), the
derived modular clock of Theorem~\ref{thm:derived-hsm-production}, in the
certified \(2\pi\) normalization, defines a monotone proper-time
parameterization; on overlaps of two histories the transition law is the
Lorentz reparameterization
\(d\tau'/d\tau=-\eta(u,u')\) determined by the two frame vectors, and it is
scheduler-independent because every ingredient is a normal-form invariant
(Lemma~\ref{lem:event-quotient-invariance}). Global statements are explicitly
assumption-gated: existence of a global time function is equivalent to stable
causality of \((\mathcal E_U,g)\), and global hyperbolicity is carried as the
\emph{record-Cauchy receipt} (every inextendible \(\preceq\)-chain in the
region meets the declared record family), which this manuscript does not
derive. No global causality claim is made beyond these named assumptions.
\end{theorem}

\begin{proof}
Monotonicity along a history follows from
Theorem~\ref{thm:event-causal-structure}(3): ancestry orients the chain, and
the derived clock increases along the transactional direction by positivity
of the generator (Theorem~\ref{thm:derived-hsm-production}(1)). The overlap
law is the chain rule for the two affine clock lines evaluated on the same
germ chain, with the Lorentz factor \(-\eta(u,u')\) produced by the frame
transition of \(\mathsf{(E4)}\). Scheduler independence is
Lemma~\ref{lem:event-quotient-invariance}. The global equivalences are the
standard Lorentzian statements, quoted here only to name the receipts.
\end{proof}

\paragraph{Countermodels and claim boundary.}

\begin{proposition}[Countermodels: the receipts are jointly irreducible]
\label{prop:event-countermodels}
Each of the following explicit systems satisfies the full producer branch
(Theorems~\ref{thm:certificate-production}, \ref{thm:bw}), hence carries the
exact Lorentz/\(H^3\) kinematics of Corollaries~\ref{cor:lorentz} and
\ref{cor:h3-spatial-chart} verbatim, and fails exactly one event receipt with
the stated consequence; machine receipts are in the repository.
\begin{enumerate}[leftmargin=2em]
\item (\emph{Population deficit; fails \(\mathsf{(E1)}\).}) Records confined
to a single observer worldline stack: \(\mathcal E\) is a one-dimensional
chain (or a \((1{+}2)\)-dimensional sheet for a planar stack), while
\(\dim H^3=3\) throughout. The event dimension is a population output, not a
kinematic one.
\item (\emph{Label inflation; fails the intended reading of
\(\mathsf{(E3)}\).}) Doubling every record with a persistent internal label
that survives all separation tests yields
\(\mathcal E\cong M^4\times\{0,1\}\), and a continuum label yields a
five-dimensional event space, with identical screen and frame kinematics; the
rank-four frame receipt is what excludes surviving extra coordinates.
\item (\emph{Reconciliation branching; fails \(\mathsf{(E2)}\).}) Two germ
families sharing every certified box up to stage \(r_\star\) and separating
afterwards with permanently failed residual gaps
(\(\Delta_{\mathrm{loc}}\leq0\), output \(\mathrm{AMBIGUOUS}\) by
Theorem~\ref{thm:h3-certified-noisy-uniqueness}) produce the standard
non-Hausdorff doubled-germ quotient: a line with doubled origin pattern
inside \(\mathcal E\). The finite-stage witness of the failure is exactly the
\(\mathrm{AMBIGUOUS}\) verdict, so non-Hausdorff formation is detectable, and
Definition~\ref{def:event-space} is the unconditional regularity class.
\end{enumerate}
In particular no argument of the form ``\(\dim H^3=3\) therefore spacetime is
\(3{+}1\)-dimensional'' is valid: dimension, Hausdorffness, and manifoldness
of the event base are controlled by \(\mathsf{(E1)}\)--\(\mathsf{(E4)}\) and
by nothing weaker.
\end{proposition}

\begin{proof}
(i) Take the producer-branch tower and restrict the record layer to tokens
whose localization balls follow one timelike chain (one located observer);
every construction upstream of records is untouched, while
Definition~\ref{def:event-space} yields the chain. (ii) Tensor the record
layer with a two-point (respectively interval-valued) internal register
transported trivially; boxes never separate the register, so coincidence
classes split accordingly. (iii) Seed a reconciliation defect at stage
\(r_\star\) as in the obstruction gates of node D1 so that two token families
carry intersecting boxes before \(r_\star\) and disjoint uncertified boxes
after; the residual-gap certificate then fails permanently by construction.
Each construction preserves the screen-side producer data because it modifies
only the record layer downstream of the certificate.
\end{proof}

\begin{remark}[Claim boundary for the event-manifold packet]
\label{rem:event-manifold-claim-boundary}
Proved here, conditionally and quotient-intrinsically: event classes and
their invariances (Lemma~\ref{lem:event-quotient-invariance}); the
unconditional regularity class (Definition~\ref{def:event-space}); the
conditional four-manifold atlas (Theorem~\ref{thm:event-4-manifold}); local
cones, signature \((-{+}{+}{+})\), time orientation, and overlap causal
compatibility (Theorem~\ref{thm:event-causal-structure}); the strict
base/fiber separation with a no-section no-go
(Proposition~\ref{prop:h3-fiber-not-slice}); tetrads, produced conformal
metric, connection/curvature readout with explicit regularity
(Theorem~\ref{thm:event-tetrad-metric}); glued scheduler-independent clocks
(Theorem~\ref{thm:clock-gluing}); and the countermodels
(Proposition~\ref{prop:event-countermodels}). Carried as named receipts:
\(\mathsf{(E1)}\)--\(\mathsf{(E4)}\) (with \(\mathsf{(E4')}\) and the smooth
upgrade), the \(\mathsf{MI}\)/assembly branch, the absolute conformal scale,
stable causality, and the record-Cauchy receipt. On branches without these
receipts, the corpus-wide claim is exactly Lorentz-group and observer-frame
kinematics, as stated in Remark~\ref{rem:h3-chart-not-populated-bulk}.
\end{remark}

\subsection{Generalized entropy and the Einstein equation}

From this point through Theorem~\ref{cor:einstein} we specialize to the physical $d=4$ scaling branch. The claim boundary is explicit. The only standard geometric input used below, beyond D3 and D4, is the fixed-volume area-variation identity for a small geodesic ball. The small-ball modular kernel used below is \emph{not} imported from a separate EFT law: it is the local expression of the geometric cap generator $B_C$ from Theorem~\ref{thm:bw}, evaluated using the half-line null-stress identification of Theorem~\ref{thm:stress} together with the bounded-interval kernel of Lemma~\ref{lem:bounded-interval-kernel}.

For a reference state $\omega$ and a small cap $C$,
\[
\delta S_C=\delta \langle K_C\rangle.
\]
By Theorem~\ref{thm:bw},
\[
\delta S_C = 2\pi\,\delta\langle B_C\rangle.
\]
By Proposition~\ref{prop:gensplit},
\[
S_{\mathrm{gen}}(C)=\mathrm{Tr}(\rho L_C)+S_{\mathrm{bulk}}(C).
\]
Together with Definition~\ref{def:newton}, this identifies the area term as the coarse-grained form of the edge entropy density instead of an independent postulate. After this edge-center split, the first-law piece entering the small-ball argument is the bulk contribution:
\[
\delta S_{\mathrm{bulk}}(C)=2\pi\,\delta\langle B_C\rangle.
\]

\begin{definition}[Admissible fixed-cap MaxEnt variation]\label{def:equilibriumvariation}
Fix a cap \(C\) and a realized reference state \(\omega_C\) on the cap-reduced realized MaxEnt branch. An admissible fixed-cap MaxEnt variation is a first-order variation
\[
\delta\rho_C=\frac{d}{ds}\Big|_{s=0}\rho_C(s)
\]
along a \(C^1\) curve \(s\mapsto \rho_C(s)\) such that:
\begin{enumerate}[leftmargin=2em]
\item every \(\rho_C(s)\) lies in the same cap-label-preserving block class of Proposition~\ref{prop:gensplit}, so the same edge-center operator \(L_C\) and sector projectors \(P_\alpha\) apply;
\item the cap \(C\), its boundary sector, charge labels, size/volume, and the optional conserved charges \(Q_b\) are held fixed;
\item the support-visible cap geometry varies only through the declared geometric tangent readout and does not change hidden carrier representatives, port labels, worker schedule, or gauge presentation;
\item the Axiom~\ref{ax:maxent} constraint values are fixed to first order, except for the declared stress-energy perturbation channel:
\[
\frac{d}{ds}\Big|_{s=0}\mathrm{Tr}(\rho_C(s) O_a(x))=0,
\qquad
\frac{d}{ds}\Big|_{s=0}\mathrm{Tr}(\rho_C(s) Q_b)=0
\]
for every retained local constraint \(O_a(x)\) supported in the fixed cap neighborhood and every retained conserved charge \(Q_b\); and
\item in the associated small-ball/diamond readout, the carried modular/stress remainder satisfies the Einstein-branch scaling condition
\[
\delta\langle E^{(\eta)}_{C,\ell}\rangle=o(\ell^4).
\]
\end{enumerate}
Shape or null-cut deformations are denoted separately by \(\delta_{\mathrm{shape}}\) or \(\partial_\lambda\); they are not part of this fixed-cap variation class.
\end{definition}

\begin{theorem}[Derived fixed-cap generalized-entropy stationarity]\label{thm:equilibrium}
Let \(C\) be a fixed cap and let \(\omega_C\) be a realized reference state on the cap-reduced realized MaxEnt branch of Axiom~\ref{ax:maxent}. For every admissible fixed-cap MaxEnt variation \(\delta\) of Definition~\ref{def:equilibriumvariation},
\[
\delta S_{\mathrm{gen}}(C)=0.
\]
Equivalently, the realized reference state is stationary for generalized entropy on the allowed fixed-cap variation class selected by the realized MaxEnt family.
\end{theorem}

\begin{proof}
Axiom~\ref{ax:maxent} selects the realized branch by entropy maximization on the finite-dimensional constraint surface cut out by the retained local constraints and optional conserved charges. Definition~\ref{def:equilibriumvariation} restricts to first-order tangent directions that stay on that same fixed-cap constraint surface. Hence the first variation of the cap entropy vanishes at the realized reference state:
\[
\delta S(\rho_C)\big|_{\omega_C}=0.
\]
For the same cap-label-preserving block class, Proposition~\ref{prop:gensplit} gives
\[
S(\rho_C)=S_{\mathrm{bulk}}(C)+\mathrm{Tr}(\rho_C L_C)=S_{\mathrm{gen}}(C).
\]
Differentiating this identity along the admissible curve yields
\[
\delta S_{\mathrm{gen}}(C)=\delta S(\rho_C)\big|_{\omega_C}=0.
\]
\end{proof}

\begin{remark}[Claim boundary of the fixed-cap generalized-entropy stationarity theorem]
Theorem~\ref{thm:equilibrium} internalizes only the fixed-cap, cap-label-preserving, constraint-preserving first-order variation class selected by Axiom~\ref{ax:maxent}. It does not claim generalized-entropy stationarity for arbitrary shape deformations, arbitrary null-cut deformations, or arbitrary off-branch perturbations outside that realized MaxEnt family.
\end{remark}

\begin{lemma}[Internal d=4 small-ball bridge]\label{lem:smallball}
Assume the hypotheses of Theorem~\ref{thm:stress}, together with the bounded-interval kernel of Lemma~\ref{lem:bounded-interval-kernel}. Let $p$ be the cap center and let $u^a$ be the future-directed unit tangent of the local diamond rest frame at $p$. In local inertial coordinates $(t,x^i)$ adapted to $u^a$, let $D_\ell$ be the causal diamond whose $t=0$ slice is the Euclidean ball
\[
B_\ell=\{t=0,\ r<\ell\},
\qquad
r^2=\delta_{ij}x^ix^j.
\]
Then
\[
\delta S_{\mathrm{bulk}}(C)
=
2\pi\int_{B_\ell}\frac{\ell^2-r^2}{2\ell}\,\delta\langle T_{00}\rangle\,d^3x
+
\delta\langle E^{(\eta)}_{C,\ell}\rangle.
\]
If $\delta\langle T_{00}\rangle$ is also approximately constant across $B_\ell$ and
\[
\delta\langle E^{(\eta)}_{C,\ell}\rangle=o(\ell^4)
\]
along the same scaling family, then in $d=4$,
\[
\delta S_{\mathrm{bulk}}(C)
=
\frac{8\pi^2\ell^4}{15}\,\delta\langle T_{00}\rangle
+O(\ell^5\partial T)+o(\ell^4).
\]
\end{lemma}

\begin{proof}
Work in the local Lorentzian scaling regime around $p$. On the geometric-subnet branch of Theorem~\ref{thm:bw}, the cap modular flow is the geometric flow of the diamond-preserving conformal Killing field. In the tangent diamond $D_\ell$, that field is
\[
\xi_{D_\ell}
=
\frac{1}{2\ell}
\Bigl((\ell^2-r^2-t^2)\,\partial_t-2t\,x^i\partial_i\Bigr),
\]
so on the $t=0$ slice one has
\[
\xi_{D_\ell}\!\cdot n=\frac{\ell^2-r^2}{2\ell},
\]
with $n^a=u^a$ the slice normal at the center.

The same kernel is the bounded-interval kernel of Lemma~\ref{lem:bounded-interval-kernel}. Along each null generator of the diamond, Theorem~\ref{thm:stress} identifies the half-line generator constructed above with the local null-stress charge, and Lemma~\ref{lem:bounded-interval-kernel} transports that identification to the affine-covariant interval weight that vanishes at the two diamond endpoints. On the $t=0$ slice that weight is exactly $(\ell^2-r^2)/(2\ell)$. Therefore the null-stress bridge reconstructs the bulk modular charge of the geometric generator as
\[
\delta\langle B_C\rangle
=
\int_{B_\ell}\frac{\ell^2-r^2}{2\ell}\,\delta\langle T_{00}\rangle\,d^3x
+\frac{1}{2\pi}\,\delta\langle E^{(\eta)}_{C,\ell}\rangle.
\]
Multiplying by the first-law factor $2\pi$ gives the displayed formula for $\delta S_{\mathrm{bulk}}(C)$.

If $\delta\langle T_{00}\rangle$ is approximately constant across $B_\ell$, then
\[
\int_{B_\ell}\frac{\ell^2-r^2}{2\ell}\,\delta\langle T_{00}\rangle\,d^3x
=
\frac{4\pi\ell^4}{15}\,\delta\langle T_{00}\rangle
+O(\ell^5\partial T).
\]
\noindent
The additional hypothesis $\delta\langle E^{(\eta)}_{C,\ell}\rangle=o(\ell^4)$ then yields
\[
\delta S_{\mathrm{bulk}}(C)
=
2\pi\cdot\frac{4\pi\ell^4}{15}\,\delta\langle T_{00}\rangle
+O(\ell^5\partial T)+o(\ell^4),
\]
which is exactly the stated coefficient. No separate EFT small-ball first law has been used: the kernel comes from the geometric cap generator together with the D4 null-stress bridge.
\end{proof}

\begin{theorem}[Finite-cutoff Einstein remainder bound]\label{thm:einstein-remainder}
On the Lorentz/null-modular/Einstein branch, before taking the controlled
collar and small-ball limits, the small-ball rest-frame relation has the form
\[
\delta\!\left(G_{00}+\Lambda g_{00}\right)
=
8\pi G\,\delta\langle T_{00}\rangle
+\mathcal E_{\ell,\delta},
\]
where, on one fixed faithful collar model and for a bounded support-visible
observable class,
\[
|\mathcal E_{\ell,\delta}|
\le
C_1 r_{\mathrm{FR}}(\varepsilon_\delta)
+C_2\delta^{\mathrm M}_{A_\delta:B_\delta:D_\delta}(\varepsilon_\delta)
+C_3\eta^{\mathrm{reg}}_\delta
+C_4\ell\,\|\partial T\|
+o_\delta(1)+o_\ell(1).
\]
Here \(\eta^{\mathrm{reg}}_\delta\) is the regularized support-visible modular
transport remainder, and the constants depend only on the fixed collar model,
the bounded observable class, and the local small-ball chart. If the controlled
collar limit removes the first three terms and the small-ball limit removes
the derivative and geometric remainders, the exact rest-frame relation of
Theorem~\ref{thm:einstein} follows.
\end{theorem}

\begin{proof}
Lemma~\ref{lem:smallball} expresses the bulk entropy variation as the geometric
cap-kernel stress term plus the carried modular/collar operator
\(E^{(\eta)}_{C,\ell}\) and the ordinary long-wavelength derivative
remainder. The finite-stage modular-defect propagation theorem bounds
expectations of \(E^{(\eta)}_{C,\ell}\) by the Fawzi--Renner observable error,
the fixed-collar Markov replacement modulus, and the support-visible
regularized modular-transport remainder. Inserting that estimate into
fixed-cap generalized-entropy stationarity and dividing by the
small-ball coefficient gives the displayed \(\mathcal E_{\ell,\delta}\).
\end{proof}

\begin{proposition}[Conditional modular-remainder stress continuation]\label{prop:conditional-modular-remainder-stress}
The finite-cutoff remainder in Theorem~\ref{thm:einstein-remainder} is not, by
itself, a dark-sector stress tensor.  On a declared quotient-invariant
collar-localization continuation branch, suppose the carried collar modular
identity
\[
  -\langle K_{ABD}-K_{AB}-K_{BD}+K_B\rangle=I(A:D|B)
\]
is source-localized to the same small-ball operator
\(E_{B_\ell,r}^{(\delta)}\) that enters fixed-cap generalized-entropy
stationarity, with residual \(\epsilon_{\rm loc}\).  Suppose also that the
source is allocated to positive quotient-visible causal packets and lifted
covariantly with rest frame \(u^a\).  Then the continuation branch defines an
effective repair stress whose rest-energy density is
\[
  T_A^{ab}u_a u_b
  =
  \frac{15\hbar c}{8\pi^2\ell^4}R_{r,\ell}
  +O(\epsilon_{\rm loc})+\hbox{small-ball and regulator errors},
\]
where \(R_{r,\ell}\) is in nats and \(\ell\) is the proper geodesic small-ball
radius.  The stress is separately conserved only on the zero first-moment
repair branch; otherwise conservation is joint with the explicit recipient
stress.
\end{proposition}

\begin{remark}[Scalar-to-tensor boundary]
The scalar collar quantity \(I(A:D|B)\) cannot, alone, determine a symmetric
rank-two stress tensor or a universal local energy expectation.  The stress
continuation also needs the packet factorization, causal packet directions,
allocation rule, rest frame, source-localization map, and transport law.  Until
those receipts pass, finite collar CMI is a recoverability and diagnostic
quantity instead of a physical dark/anomaly density source.
\end{remark}

\begin{theorem}[Fixed-volume small-ball area variation]\label{thm:fixed-volume-small-ball-area}
For a small geodesic ball \(B_\ell\) centered at \(p\) with local rest-frame
velocity \(u^a\), the fixed-volume first variation of the boundary area is
\[
\delta A\big|_{V,\Lambda}
=
-\frac{4\pi\ell^4}{15}\,
\delta\!\left[(G_{ab}+\Lambda g_{ab})u^a u^b\right]
+o(\ell^4).
\]
Therefore the area part of the generalized entropy satisfies
\[
\delta S_{\mathrm{area}}
=
\frac{\delta A}{4G}
=
-\frac{1}{4G}\frac{4\pi\ell^4}{15}\,
\delta\!\left[(G_{ab}+\Lambda g_{ab})u^a u^b\right]
+o(\ell^4).
\]
\end{theorem}

\begin{proof}
This is the standard fixed-volume small-geodesic-ball identity used in
Jacobson-style entanglement-equilibrium derivations. In \(3+1\) dimensions the
coefficient is \(\Omega_2\ell^4/(4^2-1)=4\pi\ell^4/15\). The sign is fixed by
the fact that positive curvature decreases the area of a fixed-volume small
ball. The metric-term ambiguity left by null data is represented by
\(\Lambda g_{ab}\).
\end{proof}

\begin{theorem}[Jacobson-type rest-frame relation from derived fixed-cap generalized-entropy stationarity]\label{thm:einstein}
Assume Axioms~\ref{ax:screen}--\ref{ax:entropy}, Assumption~\ref{ass:technical}, and the hypotheses of Theorem~\ref{thm:stress}, Lemma~\ref{lem:smallball}, Theorem~\ref{thm:equilibrium}, and Theorem~\ref{thm:fixed-volume-small-ball-area}. Then, for every sufficiently small cap centered at $p$ and every admissible fixed-cap MaxEnt variation $\delta$ about a realized reference state $\omega$ in the locally Lorentzian $d=4$ scaling regime, if $u^a$ is the future-directed unit tangent of the local diamond rest frame at $p$, one has
\[
\delta\!\Bigl[(G_{ab}+\Lambda g_{ab})u^a u^b\Bigr]
=
8\pi G\,u^a u^b\,\delta\langle T_{ab}\rangle
\]
at $p$. In the adapted rest frame $u^a=(1,0,0,0)$, this is
\[
\delta\!\left(G_{00}+\Lambda g_{00}\right)=8\pi G\,\delta\langle T_{00}\rangle.
\]
\end{theorem}

\begin{proof}
Theorem~\ref{thm:equilibrium} gives the fixed-cap generalized-entropy stationarity condition
\[
0=\delta S_{\mathrm{gen}}(C)
=
\delta S_{\mathrm{bulk}}(C)+\frac{\delta A}{4G}.
\]
By Lemma~\ref{lem:smallball},
\[
\delta S_{\mathrm{bulk}}(C)
=
\frac{8\pi^2\ell^4}{15}\,u^a u^b\,\delta\langle T_{ab}\rangle
+O(\ell^5\partial T)+o(\ell^4),
\]
where in the adapted rest frame the contraction is $\delta\langle T_{00}\rangle$.

By Theorem~\ref{thm:fixed-volume-small-ball-area}, the fixed-volume small-ball area variation gives
\[
\delta A\big|_{V,\Lambda}
=
-\frac{4\pi\ell^4}{15}\,
\delta\!\Bigl[(G_{ab}+\Lambda g_{ab})u^a u^b\Bigr].
\]
Therefore
\[
0
=
\frac{8\pi^2\ell^4}{15}\,u^a u^b\,\delta\langle T_{ab}\rangle
-\frac{\pi\ell^4}{15G}\,
\delta\!\Bigl[(G_{ab}+\Lambda g_{ab})u^a u^b\Bigr]
+O(\ell^5\partial T)+o(\ell^4).
\]
Dividing by $\ell^4$ and taking the small-ball limit removes the $O(\ell^5\partial T)+o(\ell^4)$ terms and yields
\[
\delta\!\Bigl[(G_{ab}+\Lambda g_{ab})u^a u^b\Bigr]
=
8\pi G\,u^a u^b\,\delta\langle T_{ab}\rangle.
\]
This is precisely the desired rest-frame scalar relation.
\end{proof}

\begin{theorem}[Timelike scalar data upgrade to tensor Einstein]\label{cor:einstein}
If the first-variation relation of Theorem~\ref{thm:einstein} holds for all local observer four-velocities and all reference states in a connected scaling branch, then
\[
G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle
\]
throughout that branch. The only local ambiguity is the metric term isolated by Lemma~\ref{lem:nullreconstruct}, and that ambiguity is exactly the same branch constant $\Lambda$.
\end{theorem}

\begin{proof}
Define
\[
Y_{ab}:=G_{ab}+\Lambda g_{ab}-8\pi G\,\langle T_{ab}\rangle.
\]
At any point $p$, Theorem~\ref{thm:einstein} gives
\[
u^a u^b\,\delta Y_{ab}=0
\]
for the unit future-directed four-velocity $u^a$ of the local diamond rest frame. By the Lorentz branch of Theorem~\ref{thm:bw} and overlap consistency across observers through the same point, these local rest frames exhaust all timelike directions. Hence
\[
u^a u^b\,\delta Y_{ab}=0
\qquad
\text{for every unit timelike }u^a.
\]

Choose local inertial coordinates at $p$ and write
\[
u^a=\gamma(1,v^i),
\qquad
|\vec v|<1,
\qquad
\gamma=(1-|\vec v|^2)^{-1/2}.
\]
Then
\[
0=u^a u^b\,\delta Y_{ab}
=
\gamma^2\Bigl(\delta Y_{00}+2v^i\delta Y_{0i}+v^iv^j\delta Y_{ij}\Bigr)
\]
for every $|\vec v|<1$. The quadratic polynomial in $v^i$ therefore vanishes on an open ball, so all of its coefficients vanish:
\[
\delta Y_{00}=0,\qquad
\delta Y_{0i}=0,\qquad
\delta Y_{ij}=0.
\]
Thus
\[
\delta Y_{ab}=0
\]
as a full tensor.

Along any path of admissible fixed-cap MaxEnt variations inside the connected scaling branch, $Y_{ab}$ is therefore constant. The null bridge isolated the only purely local freedom as a metric term via Lemma~\ref{lem:nullreconstruct}; fixing that term on one maximally symmetric reference state determines the same branch constant $\Lambda$. Equivalently,
\[
Y_{ab}=0,
\]
so
\[
G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle
\]
throughout the branch.
\end{proof}

\begin{lemma}[Constancy of the metric-term residue]\label{lem:lambda-constancy}
Let \(U\) be a connected local chart on the Lorentzian scaling branch. Suppose
the pointwise null-data/Jacobson step gives
\[
F_{ab}=\kappa T_{ab}+\lambda(x)g_{ab}
\]
on \(U\), where \(F_{ab}\) is the geometric side, \(T_{ab}\) is the matter
stress tensor, \(\nabla^aF_{ab}=0\), \(\nabla^aT_{ab}=0\), and
\(\nabla_cg_{ab}=0\). Then \(\lambda(x)\) is constant on \(U\). Thus the
local metric-term ambiguity is one branch constant \(\Lambda\), not an
arbitrary scalar field, once the Bianchi identity, local stress conservation,
and chart connectivity are present.
\end{lemma}

\begin{proof}
Taking the divergence of the displayed equation gives
\[
0=\nabla^aF_{ab}
=\kappa\nabla^aT_{ab}+\nabla^a(\lambda g_{ab})
=\nabla_b\lambda.
\]
Hence the gradient of \(\lambda\) vanishes. On a connected chart, a scalar with
zero gradient is constant. Without connectivity the same pointwise null-data
argument can assign different constants on different components, so the
connectivity hypothesis is load-bearing.
\end{proof}

\begin{remark}[Formal algebra core of the Einstein branch]\label{rem:formal-einstein-core}
The OPHProofChain finite-algebra audit contains a sorry-free Lean formalization of the
algebraic part of this subsection. The formalized core includes: the
rest-frame arithmetic in Theorem~\ref{thm:einstein}; the upgrade from all
future unit timelike directions to the full tensor equation in
Theorem~\ref{cor:einstein}; the null-cone/Jacobson residue
\(F=\kappa T+\lambda g\); and Lemma~\ref{lem:lambda-constancy} in a discrete
chart model with an explicit connectivity hypothesis. This formalization does
not derive the branch hypotheses themselves. Fixed-cap generalized-entropy
stationarity, the internal small-ball bridge, the fixed-volume area-variation
identity, bounded-interval transport, and the support-visible BW/geometric
scaling branch remain exactly the named inputs listed in the dependency table.
It therefore sharpens the status of the Einstein result: the algebra after
those branch inputs is theorem-grade, while bare finite consensus alone is not
Einstein-complete.
\end{remark}

\subsection{Edge-entropy/area law identifies the Einstein/Newton coupling}\label{subsec:edge-entropy-newton-coupling}

The Jacobson-type chain of Theorems~\ref{thm:equilibrium}, \ref{thm:einstein}, and \ref{cor:einstein} produces an Einstein equation \(G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle\) on every connected locally Lorentzian \(d=4\) scaling branch. The next theorem identifies the coefficient \(G\) in that equation with the OPH edge-entropy/area-law ratio \(a_{\mathrm{cell}}/(4\bar\ell_{\mathrm{shared}})\) of Definition~\ref{def:newton}, and tracks the same \(G\) through the standard linearization into the Newton coupling of the weak-field, slow-motion, classical-source limit. The identification is structural: the same \(G\) propagates literally through the algebra from the edge-entropy/area-law dictionary into the Einstein equation and into the Newton-Poisson limit, with no separate Newton coefficient introduced or matched against a measured constant at any step.

\begin{theorem}[Edge-entropy/area law identifies the Einstein/Newton coupling]\label{thm:edge-entropy-newton-coupling}
Assume Axioms~\ref{ax:screen}--\ref{ax:entropy}, Assumption~\ref{ass:technical}, the hypotheses of Theorem~\ref{thm:bw} (BW scaling on the prime geometric subnet), Theorem~\ref{thm:stress} (half-line generator/null-stress identification), Lemma~\ref{lem:nullreconstruct} (null-data uniqueness modulo a metric term), Theorem~\ref{thm:equilibrium} (derived fixed-cap generalized-entropy stationarity), Lemma~\ref{lem:smallball} (internal \(d=4\) small-ball bridge), Theorem~\ref{thm:einstein} (Jacobson-type rest-frame relation), and Theorem~\ref{cor:einstein} (internal tensor upgrade). Work in the refinement-scaling regime of Definition~\ref{def:newton}, in which \(\mathrm{Tr}(\rho_C L_C)\approx N_\Sigma\,\bar\ell(t)\) and \(A(\partial C)\approx N_\Sigma\,a_{\mathrm{cell}}\). Define the OPH edge-entropy/area-law coupling
\[
G_{\mathrm{geom}}:=\frac{a_{\mathrm{cell}}}{4\bar\ell(t)}.
\]
Then on every connected locally Lorentzian \(d=4\) scaling branch:

\textbf{(i) Einstein branch.} The coefficient \(G\) appearing in
\[
G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle
\]
of Theorem~\ref{cor:einstein} is exactly \(G_{\mathrm{geom}}\).

\textbf{(ii) Realized product-group local-pixel form.} If, in addition, the realized product-group hypotheses of Proposition~\ref{prop:sharededgeentropy} hold and the local pixel branch satisfies the D10 pixel law, so that \(\bar\ell_{\mathrm{shared}}=P/4\) and \(a_{\mathrm{cell}}=P\,\ell_\star^2\) (Proposition~\ref{prop:gsi}), then
\[
G_{\mathrm{geom}}=\frac{a_{\mathrm{cell}}}{4\bar\ell_{\mathrm{shared}}}=\ell_\star^2,
\]
and the Einstein equation on that branch reads \(G_{ab}+\Lambda g_{ab}=8\pi\,\ell_\star^2\,\langle T_{ab}\rangle\).

\textbf{(iii) Newton-Poisson weak-field limit.} On a static, weak-field background \(g_{ab}=\eta_{ab}+h_{ab}\) with \(|h_{ab}|\ll 1\), in the slow-motion (\(|v|\ll 1\) in geometric units) classical-source reduction \(T_{00}\to\rho\), \(|T_{ij}|\ll T_{00}\), the linearization of (i) in the harmonic gauge gives
\[
\nabla^2\Phi=4\pi\,G_{\mathrm{geom}}\,\rho,
\qquad
\ddot{\mathbf x}=-\nabla\Phi,
\]
where \(\Phi:=-\tfrac12 h_{00}\) is the Newtonian potential and the geodesic equation in the same limit yields the displayed acceleration. The Newton coupling in this limit is the same \(G_{\mathrm{geom}}=a_{\mathrm{cell}}/(4\bar\ell_{\mathrm{shared}})\) as in (i).

In particular, the OPH edge-entropy/area-law ratio \(a_{\mathrm{cell}}/(4\bar\ell_{\mathrm{shared}})\) is the structural Einstein and Newton coupling on the realized branch.
\end{theorem}

\begin{proof}
\textbf{(i)} The first variation of the generalized entropy on a fixed cap \(C\) is, by Proposition~\ref{prop:gensplit} together with the area-term identification of Definition~\ref{def:newton},
\[
\delta S_{\mathrm{gen}}(C)
=\delta S_{\mathrm{bulk}}(C)
+\delta\!\Bigl(\frac{A(\partial C)}{4G_{\mathrm{geom}}}\Bigr)
=\delta S_{\mathrm{bulk}}(C)+\frac{\delta A}{4G_{\mathrm{geom}}}.
\]
The coefficient \(1/(4G_{\mathrm{geom}})=\bar\ell(t)/a_{\mathrm{cell}}\) in front of \(\delta A\) is fixed by Definition~\ref{def:newton}: it is the refinement-scaling matching of \(\mathrm{Tr}(\rho_C L_C)\) to the area term, and uses no input outside the OPH edge-center entropy operator and the cell-area scaling. Theorem~\ref{thm:equilibrium} gives \(\delta S_{\mathrm{gen}}(C)=0\) on the admissible fixed-cap MaxEnt class, so the same coefficient enters the small-ball balance
\[
0=\delta S_{\mathrm{bulk}}(C)+\frac{\delta A}{4G_{\mathrm{geom}}}.
\]
Lemma~\ref{lem:smallball} expresses \(\delta S_{\mathrm{bulk}}(C)\) in terms of \(u^au^b\,\delta\langle T_{ab}\rangle\) using only the geometric cap generator and the D4 null-stress bridge, with no extra small-ball first law and no measured constant. The standard fixed-volume area-variation identity for a small geodesic ball in \(d=4\) gives
\[
\delta A\big|_{V,\Lambda}=-\frac{4\pi\ell^4}{15}\,\delta\!\Bigl[(G_{ab}+\Lambda g_{ab})u^au^b\Bigr],
\]
and the proof of Theorem~\ref{thm:einstein} divides through by \(\ell^4/(15)\) to obtain the rest-frame scalar relation. The factor of \(G\) on the right-hand side of Theorem~\ref{thm:einstein} is exactly the same \(G_{\mathrm{geom}}\) introduced through Definition~\ref{def:newton}, because nothing else has been substituted between \(\delta S_{\mathrm{gen}}(C)=0\) and the rest-frame relation. Theorem~\ref{cor:einstein} then promotes the rest-frame scalar relation to the tensor equation \(G_{ab}+\Lambda g_{ab}=8\pi G_{\mathrm{geom}}\,\langle T_{ab}\rangle\) using the Lorentz branch of Theorem~\ref{thm:bw}, the rest-frame coverage of timelike directions, and the null-data uniqueness of Lemma~\ref{lem:nullreconstruct}. Hence the coefficient \(G\) in Theorem~\ref{cor:einstein} is \(G_{\mathrm{geom}}\).

\textbf{(ii)} On the realized product-group branch, Proposition~\ref{prop:sharededgeentropy} together with the D10 pixel law gives \(\bar\ell_{\mathrm{shared}}=P/4\), and Proposition~\ref{prop:gsi} gives \(a_{\mathrm{cell}}=P\,\ell_\star^2\). Therefore
\[
G_{\mathrm{geom}}=\frac{a_{\mathrm{cell}}}{4\bar\ell_{\mathrm{shared}}}=\frac{P\,\ell_\star^2}{4(P/4)}=\ell_\star^2.
\]
Substituting into part (i) yields the displayed local-pixel Einstein equation.

\textbf{(iii)} Reduce (i) in the Newton-Poisson regime, using signature \((-,+,+,+)\) and geometric units \(c=1\). On laboratory and solar-system scales the curvature radius \(r\) of the Newtonian source is much smaller than the cosmological horizon \(r_{\mathrm{dS}}=\sqrt{3/\Lambda}\) (Corollary~\ref{cor:lambda-parameters}), so all \(\Lambda\)-dependent corrections to \(\Phi\) are bounded by \(\Lambda\,r^2\) and are dropped at this scale; the Newton-Poisson reduction of (i) therefore coincides with the reduction of \(G_{ab}=8\pi G_{\mathrm{geom}}\,\langle T_{ab}\rangle\). Write \(g_{ab}=\eta_{ab}+h_{ab}\) with \(|h_{ab}|\ll 1\), \(h:=\eta^{ab}h_{ab}\), and \(\bar h_{ab}:=h_{ab}-\tfrac12\eta_{ab}h\). In the harmonic gauge \(\partial^a\bar h_{ab}=0\) the linearization of \(G_{ab}=8\pi G_{\mathrm{geom}}\,\langle T_{ab}\rangle\) about flat space is the standard linearized-Einstein wave equation
\[
\Box\,\bar h_{ab}=-16\pi G_{\mathrm{geom}}\,T_{ab},
\qquad
\Box:=\eta^{ab}\partial_a\partial_b=-\partial_t^2+\nabla^2.
\]
For a static, classical, slow-motion source with \(T_{00}=\rho\) and \(|T_{0i}|,|T_{ij}|\ll T_{00}\), time derivatives drop and the dominant component is the time-time component:
\[
\nabla^2\bar h_{00}=-16\pi G_{\mathrm{geom}}\,\rho.
\]
On the static weak-field branch with the standard Newtonian-limit metric \(g_{00}=-(1+2\Phi)\), \(g_{ij}=(1-2\Phi)\delta_{ij}\), one has \(h_{00}=-2\Phi\), \(h_{ij}=-2\Phi\,\delta_{ij}\), and
\[
h=\eta^{ab}h_{ab}=-h_{00}+\delta^{ij}h_{ij}=2\Phi-6\Phi=-4\Phi,
\qquad
\bar h_{00}=h_{00}-\tfrac12\eta_{00}h=-2\Phi-\tfrac12(-1)(-4\Phi)=-4\Phi.
\]
Substituting \(\bar h_{00}=-4\Phi\) into the displayed wave equation gives
\[
\nabla^2(-4\Phi)=-16\pi G_{\mathrm{geom}}\,\rho
\quad\Longleftrightarrow\quad
\nabla^2\Phi=4\pi G_{\mathrm{geom}}\,\rho,
\]
which is the Newton-Poisson equation with coupling \(G_{\mathrm{geom}}\). The geodesic equation \(\ddot x^a+\Gamma^a_{bc}\dot x^b\dot x^c=0\) in the slow-motion limit reduces to \(\ddot x^i=-\Gamma^i_{00}=-\partial^i\Phi\), i.e.\ \(\ddot{\mathbf x}=-\nabla\Phi\). All factors of \(G\) in this reduction are the same \(G_{\mathrm{geom}}\) as in part (i): no measured Newton constant, no Planck area, and no measured cosmological constant has been substituted.
\end{proof}

\begin{remark}[Dependencies and forbidden inputs for Theorem~\ref{thm:edge-entropy-newton-coupling}]\label{rem:edge-entropy-newton-coupling-scope}
\textbf{Dependencies.} The proof composes Axioms~\ref{ax:screen}--\ref{ax:entropy} (screen net, overlap consistency, MaxEnt, MAR, recoverable generalized entropy), Assumption~\ref{ass:technical}, Theorem~\ref{thm:bw} (BW scaling theorem on the prime geometric subnet), Theorem~\ref{thm:stress} (half-line generator/null-stress identification), Lemma~\ref{lem:nullreconstruct} (null-data uniqueness modulo a metric term), Proposition~\ref{prop:gensplit} (generalized-entropy split), Definition~\ref{def:newton} (refinement-scaling area-term identification), Theorem~\ref{thm:equilibrium} (derived fixed-cap generalized-entropy stationarity), Lemma~\ref{lem:smallball} (internal \(d=4\) small-ball bridge), Theorem~\ref{thm:einstein} (Jacobson-type rest-frame relation), and Theorem~\ref{cor:einstein} (internal tensor upgrade). Part (ii) additionally invokes Proposition~\ref{prop:sharededgeentropy} (shared edge-entropy identity on the realized product-group branch with the D10 pixel law) and Proposition~\ref{prop:gsi} (local scale-certificate package on the gravity row, supplying \(a_{\mathrm{cell}}=P\,\ell_\star^2\) from the no-\(G\) scale certificate of Theorem~\ref{thm:scale-bridge-desitter}). Part (iii) uses only the standard linearization of part (i) on a flat background; it imports no further OPH structure beyond the validity of the small-ball/scaling regime that supports Theorems~\ref{thm:einstein} and \ref{cor:einstein}.

\textbf{Forbidden inputs.} The proof of Theorem~\ref{thm:edge-entropy-newton-coupling} does not use:
\begin{itemize}[leftmargin=2em]
\item the measured Newton constant \(G_N\) in any unit system;
\item the measured Planck area \(\hbar G_N/c^3\) or any other \(G_N\)-derived length scale;
\item the measured cosmological constant \(\Lambda_{\mathrm{obs}}\) (the cosmological constant appearing in (i) is the branch constant isolated by Lemma~\ref{lem:nullreconstruct}; its numerical value remains open unless the conditional global-capacity hypotheses are discharged);
\item a gravity-calibrated clock scale, in particular the cesium frequency \(\nu_{\mathrm{Cs}}\) tied to a chosen value of \(G_N\) or to a chosen Planck unit.
\end{itemize}
The constant \(G_{\mathrm{geom}}=a_{\mathrm{cell}}/(4\bar\ell_{\mathrm{shared}})\) is supplied entirely by the OPH edge-entropy/area-law data: \(a_{\mathrm{cell}}\) and \(\bar\ell_{\mathrm{shared}}\) come from Axioms~\ref{ax:screen}--\ref{ax:entropy}, Proposition~\ref{prop:sharededgeentropy}, and Proposition~\ref{prop:gsi}, with the cell-area scale \(\ell_\star^2\) supplied by the separate no-\(G\) scale certificate of Theorem~\ref{thm:scale-bridge-desitter}. The SI display \(G_{\mathrm{SI}}=c^3\ell_\star^2/\hbar\) of Proposition~\ref{prop:gsi} is a downstream unit-translation step and is not used in the proof of (i)-(iii).

\textbf{Claim boundary.} Theorem~\ref{thm:edge-entropy-newton-coupling} asserts only the identification of the coefficient \(G\) in (i)-(iii) with \(G_{\mathrm{geom}}\). It does not extend to non-scaling regimes, to fixed-cap variations outside the admissible MaxEnt class of Definition~\ref{def:equilibriumvariation}, or to gravitational regimes that violate the small-ball/scaling hypotheses of Lemma~\ref{lem:smallball}. The finite-cutoff remainder of Theorem~\ref{thm:einstein-remainder} controls the carried error before those limits are taken.

\textbf{Refinement-scaling dictionary scope.} The structural content of (i)-(iii) is derived: the same \(G_{\mathrm{geom}}\) propagates literally through Theorems~\ref{thm:equilibrium}, \ref{thm:einstein}, and \ref{cor:einstein} into the Einstein equation and through the standard linearization into the Newton-Poisson limit. Theorem~\ref{thm:edge-entropy-newton-coupling} as stated takes the matching \(\mathrm{Tr}(\rho_C L_C)=A(\partial C)/(4G_{\mathrm{geom}})\) of Definition~\ref{def:newton} as a starting form, so the factor of \(4\) is inherited at the level of this theorem. Corollary~\ref{cor:factor-of-four-derived} below tightens this by running the same Jacobson chain with only the linear-in-area scaling \(\mathrm{Tr}(\rho_C L_C)\propto A(\partial C)\), itself derived inside OPH from the Markov-collar/refinement-stability structure of the screen net (Theorem~\ref{thm:markovcollar}, Proposition~\ref{prop:gensplit}, together with the discrete-to-continuum scaling \(\mathrm{Tr}(\rho_C L_C)\approx N_\Sigma\bar\ell(t)\) and \(A(\partial C)\approx N_\Sigma a_{\mathrm{cell}}\) of Definition~\ref{def:newton}), and identifying the factor of \(4\) as the ratio of the resulting OPH structural Einstein-equation coefficient to the constant \(8\pi\) entering the standard Newton-Poisson convention \(\nabla^2\Phi=4\pi G_N\rho\). The convention used by Corollary~\ref{cor:factor-of-four-derived} is the standard naming of the Newton coupling.
\end{remark}

\begin{corollary}[Factor of \(4\) in \(G_{\mathrm{geom}}\) from the OPH structural Einstein-equation coefficient and the Newton-Poisson convention]\label{cor:factor-of-four-derived}
Assume Axioms~\ref{ax:screen}--\ref{ax:entropy}, Assumption~\ref{ass:technical}, and the hypotheses of Theorems~\ref{thm:bw}, \ref{thm:stress}, \ref{thm:equilibrium}, Lemma~\ref{lem:nullreconstruct}, and Lemma~\ref{lem:smallball}. Take as the only refinement-scaling input the linear-in-area scaling
\[
\mathrm{Tr}(\rho_C L_C)\approx\frac{\bar\ell(t)}{a_{\mathrm{cell}}}\,A(\partial C),
\]
which follows from \(\mathrm{Tr}(\rho_C L_C)\approx N_\Sigma\bar\ell(t)\) and \(A(\partial C)\approx N_\Sigma a_{\mathrm{cell}}\) (the two cell-decomposition identifications of Definition~\ref{def:newton}, with no \(1/(4G_{\mathrm{geom}})\) form invoked). Then on every connected locally Lorentzian \(d=4\) scaling branch:

\textbf{(a) OPH structural Einstein-equation coefficient.} The Jacobson chain produces
\[
G_{ab}+\Lambda g_{ab}=\kappa_{\mathrm{OPH}}\,\langle T_{ab}\rangle,
\qquad
\kappa_{\mathrm{OPH}}=\frac{2\pi\,a_{\mathrm{cell}}}{\bar\ell(t)},
\]
where \(\kappa_{\mathrm{OPH}}\) is determined by the structural OPH inputs alone, with no naming convention chosen for the gravitational coupling.

\textbf{(b) Newton coupling from the Newton-Poisson convention.} Repeating the slow-motion, weak-field, classical-source linearization of (a) as in part (iii) of Theorem~\ref{thm:edge-entropy-newton-coupling}, with the general coefficient \(\kappa\) in place of \(8\pi G_{\mathrm{geom}}\), yields
\[
\nabla^2\Phi=\frac{\kappa_{\mathrm{OPH}}}{2}\,\rho.
\]
Define the Newton coupling \(G_N\) by the standard physics convention \(\nabla^2\Phi=4\pi G_N\,\rho\). Then \(\kappa_{\mathrm{OPH}}=8\pi G_N\).

\textbf{(c) Factor of \(4\).} Combining (a) and (b),
\[
G_N=\frac{\kappa_{\mathrm{OPH}}}{8\pi}=\frac{2\pi\,a_{\mathrm{cell}}/\bar\ell(t)}{8\pi}=\frac{a_{\mathrm{cell}}}{4\bar\ell(t)}=G_{\mathrm{geom}}.
\]
Hence the factor of \(4\) in \(G_{\mathrm{geom}}=a_{\mathrm{cell}}/(4\bar\ell(t))\) is the ratio of the OPH structural coefficient \(\kappa_{\mathrm{OPH}}=2\pi\,a_{\mathrm{cell}}/\bar\ell(t)\) to the Newton-Poisson constant \(8\pi\) entering the convention \(\nabla^2\Phi=4\pi G_N\rho\). Equivalently, the dictionary identification \(\mathrm{Tr}(\rho_C L_C)=A(\partial C)/(4G_{\mathrm{geom}})\) of Definition~\ref{def:newton} is recoverable from the structural OPH inputs and the Newton-Poisson convention via (c).
\end{corollary}

\begin{proof}
\textbf{(a)} Theorem~\ref{thm:equilibrium} and Proposition~\ref{prop:gensplit} give
\[
0=\delta S_{\mathrm{gen}}(C)=\delta S_{\mathrm{bulk}}(C)+\delta\!\bigl(\mathrm{Tr}(\rho_C L_C)\bigr)=\delta S_{\mathrm{bulk}}(C)+\frac{\bar\ell(t)}{a_{\mathrm{cell}}}\,\delta A,
\]
where the last equality uses the linear-in-area scaling. By Lemma~\ref{lem:smallball},
\[
\delta S_{\mathrm{bulk}}(C)=\frac{8\pi^2\ell^4}{15}\,u^au^b\,\delta\langle T_{ab}\rangle+O(\ell^5\partial T)+o(\ell^4),
\]
and the standard fixed-volume area-variation identity for a small geodesic ball in \(d=4\) gives
\[
\delta A\big|_{V,\Lambda}=-\frac{4\pi\ell^4}{15}\,\delta\!\bigl[(G_{ab}+\Lambda g_{ab})u^au^b\bigr].
\]
Substituting,
\[
0=\frac{8\pi^2\ell^4}{15}\,u^au^b\,\delta\langle T_{ab}\rangle-\frac{\bar\ell(t)}{a_{\mathrm{cell}}}\,\frac{4\pi\ell^4}{15}\,\delta\!\bigl[(G_{ab}+\Lambda g_{ab})u^au^b\bigr]+O(\ell^5\partial T)+o(\ell^4).
\]
Dividing by \(\ell^4\) and taking the small-ball limit removes the remainder terms and yields
\[
\delta\!\bigl[(G_{ab}+\Lambda g_{ab})u^au^b\bigr]=\frac{2\pi\,a_{\mathrm{cell}}}{\bar\ell(t)}\,u^au^b\,\delta\langle T_{ab}\rangle.
\]
The tensor upgrade of Theorem~\ref{cor:einstein} (using the Lorentz branch of Theorem~\ref{thm:bw} and the null-data uniqueness of Lemma~\ref{lem:nullreconstruct}) promotes this rest-frame relation to \(G_{ab}+\Lambda g_{ab}=(2\pi\,a_{\mathrm{cell}}/\bar\ell(t))\,\langle T_{ab}\rangle\), which is the displayed equation with \(\kappa_{\mathrm{OPH}}=2\pi\,a_{\mathrm{cell}}/\bar\ell(t)\). This step uses the structural linear-in-area scaling before a \(1/(4G_{\mathrm{geom}})\) naming convention is introduced.

\textbf{(b)} Linearize \(G_{ab}+\Lambda g_{ab}=\kappa\,\langle T_{ab}\rangle\) on a flat background as in part (iii) of Theorem~\ref{thm:edge-entropy-newton-coupling}, with the coefficient \(\kappa\) kept general. Signature \((-,+,+,+)\), geometric units \(c=1\). The harmonic-gauge linearized Einstein equation, with \(\Lambda\)-dependent corrections at scales \(r\ll r_{\mathrm{dS}}=\sqrt{3/\Lambda}\) bounded by \(\Lambda r^2\) and dropped exactly as in part (iii), is
\[
\Box\,\bar h_{ab}=-2\kappa\,T_{ab}.
\]
For a static, classical, slow-motion source with \(T_{00}=\rho\) and \(|T_{0i}|,|T_{ij}|\ll T_{00}\), this reduces to
\[
\nabla^2\bar h_{00}=-2\kappa\,\rho.
\]
The standard Newtonian-limit metric \(g_{00}=-(1+2\Phi)\), \(g_{ij}=(1-2\Phi)\delta_{ij}\) gives \(\bar h_{00}=-4\Phi\), so
\[
\nabla^2(-4\Phi)=-2\kappa\,\rho
\quad\Longleftrightarrow\quad
\nabla^2\Phi=\frac{\kappa}{2}\,\rho.
\]
Comparing with the Newton-Poisson convention \(\nabla^2\Phi=4\pi G_N\,\rho\) gives \(\kappa=8\pi G_N\). Substituting \(\kappa_{\mathrm{OPH}}\) from (a) yields \(\kappa_{\mathrm{OPH}}=8\pi G_N\), as displayed.

\textbf{(c)} Solve (b) for \(G_N\) and substitute (a):
\[
G_N=\frac{\kappa_{\mathrm{OPH}}}{8\pi}=\frac{2\pi\,a_{\mathrm{cell}}/\bar\ell(t)}{8\pi}=\frac{a_{\mathrm{cell}}}{4\bar\ell(t)}.
\]
This is exactly \(G_{\mathrm{geom}}\) of Definition~\ref{def:newton}; the factor of \(4\) is the ratio of the OPH structural coefficient \(\kappa_{\mathrm{OPH}}\) to the Newton-Poisson constant \(8\pi\). Equivalently, the dictionary form \(\mathrm{Tr}(\rho_C L_C)=A(\partial C)/(4G_{\mathrm{geom}})\) of Definition~\ref{def:newton} follows by substituting \(G_{\mathrm{geom}}=a_{\mathrm{cell}}/(4\bar\ell(t))\) into the structural linear-in-area scaling \(\mathrm{Tr}(\rho_C L_C)=(\bar\ell(t)/a_{\mathrm{cell}})\,A(\partial C)\).
\end{proof}

\begin{remark}[Forbidden inputs preserved by Corollary~\ref{cor:factor-of-four-derived}]\label{rem:factor-of-four-forbidden-inputs}
The forbidden-input list of Remark~\ref{rem:edge-entropy-newton-coupling-scope} carries through Corollary~\ref{cor:factor-of-four-derived} unchanged: the proof uses no measured Newton constant \(G_N\) (the symbol \(G_N\) appears only as the constant defined by the convention \(\nabla^2\Phi=4\pi G_N\rho\), with its OPH value derived in (c)), no measured Planck area, no measured cosmological constant, and no gravity-calibrated clock scale. The only convention imported beyond the OPH inputs is the standard physics naming of the Newton coupling via the Newton-Poisson equation.
\end{remark}

\subsection{Einstein branch closure: local stress, entropy bridge, uniform small-diamond limit, and the composed branch-entry theorem}
\label{subsec:einstein-branch-closure}

The Einstein package above consumes four inputs whose construction this
subsection owns: (i) a local, symmetric, normalized, conserved stress tensor
whose null charges are the modular generators, rather than an effective-field
stress tensor named after the fact; (ii) a generalized-entropy first law with
the edge/center term carried explicitly and a stationarity proof compatible
with a \emph{changing} stress channel; (iii) a single uniform scaling family
replacing the per-radius diagonal choice of Lemma~\ref{lem:diagonal-remainder},
and a base condition converting first-variation constancy into an absolute
tensor equation; and (iv) the composition of the entire chain from repaired
normal forms to the semiclassical Einstein equation into one typed theorem
with a partitioned input list, no-hidden-geometry audit, and an explicit
nonemptiness status for the realized branch. Throughout, every statement is
classified as exact finite, scaling-limit, semiclassical expectation-value,
conditional physical identification, or numerical/empirical.

\subsubsection{The local conserved stress tensor from modular charges}
\label{subsubsec:local-stress-from-modular-charges}

\begin{theorem}[Null tomography for symmetric tensors]
\label{thm:null-tomography}
Let \(T\) be a symmetric bilinear form on \((\mathbb R^4,\eta)\). The
restriction of \(v\mapsto T(v,v)\) to the null cone determines \(T\) up to a
multiple of \(\eta\): if \(T(k,k)=T'(k,k)\) for every null \(k\), then
\(T'-T=\phi\,\eta\) for some \(\phi\in\mathbb R\). Conversely, a function
\(k\mapsto\tau(k)\) on the future null cone arises as \(k\mapsto T(k,k)\) for
a (then \(\eta\)-ambiguous) symmetric \(T\) if and only if it is homogeneous
of degree two and satisfies the finite linear compatibility relations
\[
\sum_i c_i\,k_i\otimes k_i=0
\;\Longrightarrow\;
\sum_i c_i\,\tau(k_i)=0 ,
\]
over all finite null families. Nine linearly independent null directions
suffice to reconstruct the \(\eta\)-trace-free part of \(T\) by solving the
corresponding linear system, and the reconstruction is Lipschitz in the
charge data on any direction family with nonvanishing ninth singular value.
\end{theorem}

\begin{proof}
The symmetric square vectors \(k\otimes k\), \(k\) null, span the
\(\eta\)-orthogonal complement of nothing less than the full ten-dimensional
symmetric space except for the relation \(\eta^{ab}(k\otimes k)_{ab}=0\):
concretely, polarization of \(T(k,k)\) over null \(k=(1,\Omega)\),
\(\Omega\in S^2\), yields all components \(T_{00}\),
\(T_{0i}+T_{i0}\), and the symmetric spatial moments \(T_{ij}\Omega^i\Omega^j\)
against the \(\ell\leq2\) spherical harmonics, which determine \(T_{ij}\) up
to its trace; the only undetermined combination is
\(T_{00}+\delta^{ij}T_{ij}\) paired against \(\ell=0\), i.e.\ the
\(\eta\)-trace. A symmetric form vanishing on the whole null cone is
therefore proportional to \(\eta\) (the standard null-invisibility statement,
used in the tensor upgrade of Theorem~\ref{thm:einstein}). The
converse and the nine-direction count follow because
\(\dim\operatorname{span}\{k\otimes k:\ k\ \text{null}\}=9\); Lipschitz
stability is the finite-dimensional least-squares bound with constant
\(1/\sigma_9\) of the direction design matrix.
\end{proof}

\begin{definition}[Local charge domain and smeared null charges]
\label{def:local-charge-domain}
Work on an event region of Theorem~\ref{thm:event-4-manifold} carrying
receipts \(\mathsf{E1}\)--\(\mathsf{E4}\), the derived translations of
Theorem~\ref{thm:derived-hsm-production}, and the assembly branch of
Theorem~\ref{thm:four-translation-assembly}. The test space
\(\mathcal D\) consists of Lipschitz compactly supported functions on the
region. For a null direction \(\Omega\) and \(f\in\mathcal D\) supported on a
chart, define the smeared null charge as the weak refinement limit
\[
T[f;\Omega]\;:=\;\lim_r\ \sum_{I\in\mathcal P_r}
f(a_I)\,\bigl\langle \widetilde K_{I}(\Omega)\bigr\rangle'\, ,
\]
where \(\mathcal P_r\) are the stage-\(r\) bounded null intervals of
Theorem~\ref{thm:mobius-bounded-intervals} along the \(\Omega\)-generator
through the chart, \(\widetilde K_I\) their renormalized modular
Hamiltonians, and \(\langle\cdot\rangle'\) the endpoint derivative of
Proposition~\ref{prop:n3} in the canonical normalization of
Corollary~\ref{cor:n1}. Existence of the limit on \(\mathcal D\) with
refinement-uniform errors is the kernel-residual receipt of
Theorem~\ref{thm:mobius-bounded-intervals} (scaling-limit statement).
\end{definition}

\begin{theorem}[Construction of the local conserved stress tensor]
\label{thm:local-stress-construction}
On the domain of Definition~\ref{def:local-charge-domain}, with the
\(\mathsf{MI}\)/assembly branch and the collar-uniform recovery constants
(the collar CMI interface of node D2), the family
\(\{T[f;\Omega]\}_{\Omega\in S^2}\) satisfies the compatibility relations of
Theorem~\ref{thm:null-tomography} for every \(f\), and therefore defines a
unique semiclassical expectation tensor field
\(\langle T_{ab}\rangle\in L^\infty_{\mathrm{loc}}\) modulo
\(\phi\,g_{ab}\), with:
\begin{enumerate}[leftmargin=2em]
\item (\emph{Symmetry and locality.}) \(\langle T_{ab}\rangle\) is symmetric
by construction, and \(T[f;\Omega]\) depends only on the record data in the
causal support of \(f\) (support-local commutation of node D1 through the
blow-up).
\item (\emph{Covariance and common normalization.}) Under the produced
Poincar\'e action, \(T[f;\Omega]\) transforms with the null weight of
Theorem~\ref{thm:four-translation-assembly}(1); the linearity clause
\ref{thm:four-translation-assembly}(2) is exactly the statement that the
directional charges carry one common normalization, so the tomography system
is consistent across directions rather than per-direction rescaled.
\item (\emph{Generator identification.}) For every \(\Omega\),
\(P_\Omega=\int T_{kk}\) as quadratic forms on the common Stone core: this is
Theorem~\ref{thm:stress} upgraded from named identification to construction,
because the right-hand side is Definition~\ref{def:local-charge-domain}
rather than an assumed effective density; endpoint/collar errors are uniform
under refinement by the kernel-residual receipt.
\item (\emph{Ward identity.}) In the weak (distributional) sense on the
\(C^{1,1}\) atlas,
\(\nabla^a\langle T_{ab}\rangle=0\): for \(b\) a translation direction,
invariance of the charges under the derived translations
(\(U(x)\)-conjugation moves \(f\) by \(x\) and leaves the limit unchanged)
gives vanishing coordinate divergence in each chart, and the
\(\mathsf{E4}\) Poincar\'e transitions preserve this statement, so the
covariant divergence vanishes almost everywhere.
\item (\emph{Ambiguity classification.}) The full ambiguity is
\(\phi\,g_{ab}\) (null-invisible; fixed downstream by the base condition of
Theorem~\ref{thm:absolute-einstein-base-condition}) plus improvement terms
\(\partial^c\partial^d\chi_{[ca][db]}\) with \(\chi\) supported like \(f\),
which do not change any charge on closed faces; no other ambiguity survives
the tomography relations.
\end{enumerate}
Statement levels: (1), (2), (5) scaling-limit theorems on the named branch;
(3) scaling-limit theorem given the kernel-residual receipt; (4)
semiclassical expectation-value statement.
\end{theorem}

\begin{proof}
Compatibility: a dependent null family \(\sum c_ik_i\otimes k_i=0\) pulls back
under the blow-up to a dependent family of translation generators; by
Theorem~\ref{thm:four-translation-assembly}(2), \(\sum c_iP_{\Omega_i}=0\),
and the same relation holds for the endpoint-derivative densities after
smearing because each \(T[f;\Omega]\) is the \(f\)-weighted disintegration of
\(P_\Omega\) along its generator (Definition~\ref{def:local-charge-domain}
and Lemma~\ref{lem:translation}); the finite-stage defect is bounded by the
\(\mathsf{MI}\) residual \(\varepsilon_r\) and vanishes in the limit.
Theorem~\ref{thm:null-tomography} then yields the tensor with the stated
ambiguity, measurably in the base point by the Lipschitz reconstruction
bound applied chartwise. Symmetry is built into the tomography. Locality is
support-local commutation transported through the blow-up: intervals outside
the causal support of \(f\) contribute commuting differences whose endpoint
derivatives vanish in the canonical normalization. Covariance is
Theorem~\ref{thm:four-translation-assembly}(1) applied to each interval
charge, plus naturality of the partition family under the M\"obius transport
of Theorem~\ref{thm:mobius-bounded-intervals}. The generator identification
integrates the disintegration against \(f\to1\) on the generator through the
chart, with the monotone refinement errors controlled by the kernel-residual
receipt; this is exactly the content of Theorem~\ref{thm:stress} with the
density constructed. For the Ward identity, fix a chart and a coordinate
direction \(x^\mu\); then
\(T[f(\cdot-x);\Omega]=\langle U(x)^{*}(\cdots)U(x)\rangle\)-transported
charges equal \(T[f;\Omega]\) up to the state-variation term, which vanishes
because \(\Omega\)-invariance \(U(x)\Omega=\Omega\) holds for the reference
state and the semiclassical expectation is taken in that state; dividing by
\(|x|\) and letting \(x\to0\) gives \(\partial^\mu T[\partial_\mu f;\Omega]=0\),
i.e.\ the weak coordinate conservation, for every \(\Omega\), hence for the
reconstructed tensor. Chart transitions are Poincar\'e by \(\mathsf{E4}\), so
the statement globalizes to the a.e.\ covariant divergence on the
\(C^{1,1}\) atlas. The ambiguity classification is
Theorem~\ref{thm:null-tomography} plus the standard improvement-term
observation that double-divergence additions with antisymmetrized index
blocks change no face charge.
\end{proof}

\begin{definition}[Universal-coupling receipt]
\label{def:universal-coupling-receipt}
\(\mathsf{UC}\): the tensor of Theorem~\ref{thm:local-stress-construction}
(constructed from the \emph{same} modular data as the entropy first law
below) is the sole source entering the geometric branch: no record sector
carries a second, differently normalized coupling to the produced metric.
This is a physical-identification receipt, not a theorem; it is the
equivalence-principle step, and it is falsifiable on any branch carrying a
sector whose modular charges decouple from its entropy response.
\end{definition}

\begin{proposition}[Countermodel: positive generators without a local stress tensor]
\label{prop:no-local-stress-countermodel}
There are directional charge families in which every \(P_\Omega\) exists,
is positive, and is translation-covariant \emph{per direction}, but no
symmetric tensor field reproduces them: any family violating one linear
compatibility relation of Theorem~\ref{thm:null-tomography} (equivalently,
any branch without the \(\mathsf{MI}\) linearity clause) admits no rank-two
source, and the least-squares tomography residual is bounded below by the
violation size times \(\sigma_9^{-1}\). Machine receipts construct such a
family explicitly and verify both the irreducible residual and the exact
reconstruction of consistent families. Scalar
collar CMI data alone likewise admit no promotion to a rank-two source: a
scalar function of cuts determines only the \(\ell=0\) moment of
Theorem~\ref{thm:null-tomography} and leaves the nine-dimensional trace-free
part undetermined.
\end{proposition}

\begin{proof}
Take any consistent family and add to one direction's charge a bump violating
one dependent-family relation; Theorem~\ref{thm:null-tomography} shows
solvability fails, and the quantitative residual bound is the least-squares
lower bound. The scalar statement is the rank count in the same theorem.
\end{proof}

\subsubsection{The generalized-entropy first law with the edge term, and stationarity with a changing stress channel}
\label{subsubsec:entropy-bridge-repair}

Work on the central-interface branch of Axiom~\ref{ax:maxent}
(Theorem~\ref{thm:msaderivation}), where the collar algebra of a cap \(C\)
has center generated by the boundary-charge functions, the reference state
decomposes as \(\rho_C=\bigoplus_\alpha p_\alpha\,\rho_\alpha\) over central
sectors \(\alpha\), and the type-I generator form
\(K_C=2\pi B_C+Z_C\) holds with \(Z_C\) central
(the form used by Theorem~\ref{thm:bw} and the compact first-law
bookkeeping). Define
\[
S_{\mathrm{bulk}}(C):=\sum_\alpha p_\alpha S(\rho_\alpha),
\qquad
S_{\mathrm{edge}}(C):=H(\{p_\alpha\})+\sum_\alpha p_\alpha\log d_\alpha ,
\]
with \(d_\alpha\) the declared edge-sector dimension weights, so that
\(S(\rho_C)=S_{\mathrm{bulk}}+H(p)\) and \(S_{\mathrm{edge}}\) is the
edge/center functional whose refinement limit supplies the area term in
Definition~\ref{def:newton}.

\begin{theorem}[Bulk/edge/central first law, exact finite form]
\label{thm:bulk-edge-central-first-law}
For any differentiable variation \(\rho(\epsilon)\) of the reference state
with \(\operatorname{Tr}\delta\rho=0\), writing
\(\delta X:=\tfrac{d}{d\epsilon}X|_{0}\):
\begin{enumerate}[leftmargin=2em]
\item (\emph{First law.})
\(\delta S(\rho_C)=\langle K_C\,\delta\rho\rangle
=2\pi\,\delta\langle B_C\rangle+\delta\langle Z_C\rangle\),
exactly, at fixed operators \(B_C,Z_C\).
\item (\emph{Edge term identification and corrected bookkeeping.}) On
variations preserving the central-interface class, \(Z_C\) acts sectorwise as
\((-\log p_\alpha+z_\alpha)\mathbf 1\) with \(z_\alpha\) fixed by the
declared normalization, and
\(\delta\langle Z_C\rangle=\delta H(p)+\sum_\alpha z_\alpha\,\delta p_\alpha
=\delta S_{\mathrm{edge}}\)
exactly when \(z_\alpha=\log d_\alpha\). Substituting into (1), the corrected
bookkeeping is the exact split
\[
\boxed{\;\delta S(\rho_C)
=2\pi\,\delta\langle B_C\rangle+\delta S_{\mathrm{edge}}\;}
\]
with no dropped term: total entropy variation equals modular (Clausius) flux
plus edge/area response, and the same \(\delta S_{\mathrm{edge}}\) appears
exactly once, as \(\delta A/(4G)\), through Definition~\ref{def:newton}. The
earlier step \(\delta S_{\mathrm{bulk}}=2\pi\delta\langle B_C\rangle\) is
\emph{not} an identity: since
\(\delta S=\delta S_{\mathrm{bulk}}+\delta H(p)\), one has
\(\delta S_{\mathrm{bulk}}
=2\pi\delta\langle B_C\rangle+\sum_\alpha z_\alpha\,\delta p_\alpha\),
so the naive form is valid exactly on the fixed-edge-sector-weight class
(\(\delta p_\alpha=0\)) and otherwise carries the explicit central flux
\(\sum_\alpha z_\alpha\delta p_\alpha
=\delta S_{\mathrm{edge}}-\delta H(p)\). Both the exact split and the
quantitative naive-step defect are certified numerically in the repository
receipts.
\item (\emph{Type-I boundary.}) Item (2) is a finite/type-I statement; on the
generic automorphism-level branch of Theorem~\ref{thm:bw} the algebraic
replacement is the relative-entropy form
\(\delta S(\rho\Vert\rho_{\mathrm{ref}})=0\) at first order together with
sector-weight variation, and the identity holds for the declared
central-sector weights without invoking a global density matrix. This is the
precise algebraic substitute for the density-matrix step, stated at
expectation-value level.
\end{enumerate}
\end{theorem}

\begin{proof}
(1) is \(\delta S=-\operatorname{Tr}(\delta\rho\log\rho)\) (the
\(\operatorname{Tr}\delta\rho=0\) term removes the normalization), followed
by the split \(-\log\rho=K_C=2\pi B_C+Z_C\). (2) On the central-interface
class, \(\rho=\oplus_\alpha p_\alpha\rho_\alpha\) gives
\(-\log\rho=\oplus_\alpha(-\log p_\alpha+(-\log\rho_\alpha))\); the central
part is \(-\log p_\alpha+z_\alpha\) after moving the sectorwise constant
\(z_\alpha\) between \(Z\) and \(2\pi B\) per the declared normalization.
The central term pairs with \(\delta\rho\) through the sector traces:
\(\delta\langle Z\rangle=\sum_\alpha(-\log p_\alpha+z_\alpha)\delta p_\alpha
=\delta H(p)+\sum_\alpha z_\alpha\delta p_\alpha\)
using \(\sum_\alpha\delta p_\alpha=0\); choosing
\(z_\alpha=\log d_\alpha\) matches \(\delta S_{\mathrm{edge}}\) term by term,
and substituting into (1) gives the boxed split. The naive-step statement
follows from \(S=S_{\mathrm{bulk}}+H(p)\):
\(\delta S_{\mathrm{bulk}}=\delta S-\delta H(p)
=2\pi\delta\langle B\rangle+\delta\langle Z\rangle-\delta H(p)
=2\pi\delta\langle B\rangle+\sum_\alpha z_\alpha\delta p_\alpha\). (3) restates (2) through Araki relative entropy: first-order
stationarity of \(S(\rho\Vert\rho_{\mathrm{ref}})\) at
\(\rho=\rho_{\mathrm{ref}}\) is the same identity with
\(\langle K\,\delta\rho\rangle\) read as the relative-modular pairing, and
sector weights are declared data of the central-interface branch.
\end{proof}

\begin{theorem}[MaxEnt stationarity with a changing stress channel]
\label{thm:maxent-lagrange-stationarity}
Let \(\rho(t)\) be the MaxEnt family maximizing \(S\) subject to the modular
stress constraint \(\langle T_{ff}\rangle=t\) (the realized cap-label-preserving
family of Theorem~\ref{thm:equilibrium}), with Lagrange multiplier
\(\lambda(t)\). Then, exactly and without assuming the constraint surface is
fixed:
\[
\frac{dS}{dt}=\lambda(t),
\]
and on the branch where the constraint is the certified modular charge with
the \(2\pi\)-KMS normalization, \(\lambda=2\pi\) at the reference point.
Consequently the generalized-entropy stationarity of
Theorem~\ref{thm:equilibrium} extends to the \emph{coupled} variation class
(fiber variations at fixed constraint value \emph{plus} first-order changes
of the constraint value along the MaxEnt family): fiber variations satisfy
\(\delta S\leq0\) with equality at the MaxEnt point, along-family variations
satisfy \(\delta S=\lambda\,\delta t\) exactly, and combining with the exact
split of Theorem~\ref{thm:bulk-edge-central-first-law} yields the Clausius
balance consumed downstream,
\[
\delta S_{\mathrm{edge}}
=\lambda\,\delta t-2\pi\,\delta\langle B_C\rangle ,
\qquad \lambda=2\pi ,
\]
for every coupled variation: the edge/area response equals the
constraint-channel flux minus the bulk modular flux. This resolves the
fixed-surface/changing-channel mismatch: the term missing from the
fixed-constraint argument when the stress channel moves is exactly
\(\lambda\,\delta t\), supplied by the envelope identity rather than
asserted. The variation class
is nonempty and distinguishes state, constraint-value, and edge-sector
directions; shape/null-cut and metric variations are \emph{not} covered by
this theorem and retain their separate status.
\end{theorem}

\begin{proof}
The MaxEnt state at constraint value \(t\) is
\(\rho(t)=e^{-\lambda(t)T_{ff}-\mu(t)}/Z\)-type within the declared family;
differentiating \(S(\rho(t))=\lambda t+\mu+\log Z\)-form along the family and
using the constraint derivative gives the exact envelope identity
\(dS/dt=\lambda\) (the standard Legendre/envelope computation, exact at
finite dimension: \(dS/dt=-\operatorname{Tr}(\dot\rho\log\rho)
=\lambda\operatorname{Tr}(\dot\rho T_{ff})+\mu\operatorname{Tr}\dot\rho
=\lambda\)). The KMS normalization identifies \(\lambda=2\pi\) at the
reference point by Theorem~\ref{thm:bw}. For the coupled class, decompose any
first-order variation into a component along the MaxEnt family (constraint
value moves by \(\delta t\)) and a component in the fixed-\(t\) fiber;
the fiber component obeys \(\delta S\leq0\) with equality on the family
(MaxEnt optimality, first order zero), and the along-family component
contributes \(\delta S=\lambda\delta t\) by the envelope identity, with the
constraint charge identified as the modular charge through
Theorem~\ref{thm:local-stress-construction}(3). Substituting
\(\delta S=2\pi\delta\langle B\rangle+\delta S_{\mathrm{edge}}\) from the
boxed split gives the displayed Clausius balance. Nonemptiness of the class is
witnessed by the family itself and by the sector-weight variations of
Theorem~\ref{thm:bulk-edge-central-first-law}(2).
\end{proof}

\begin{proposition}[Countermodels: MaxEnt, small CMI, or a central split alone do not give the gravitational law]
\label{prop:entropy-coefficient-countermodel}
(i) For any coefficient \(\gamma\neq1/(4G)\) in a trial functional
\(S_\gamma:=S_{\mathrm{out}}+\gamma A\), the coupled-class stationarity of
Theorem~\ref{thm:maxent-lagrange-stationarity} fails at first order by
exactly \((\gamma-\tfrac1{4G})\,\delta A\neq0\) on any variation moving the
edge sector: the coefficient is fixed by the edge/center dictionary of
Definition~\ref{def:newton} and by nothing weaker. (ii) A blockwise state
with exactly zero collar CMI and a central split, but edge weights
\(z_\alpha\neq\log d_\alpha\), breaks the edge identification: the defect
\(\delta\langle Z\rangle-\delta S_{\mathrm{edge}}
=\sum_\alpha(z_\alpha-\log d_\alpha)\delta p_\alpha\)
is nonzero for generic sector-weight variations, so the area dictionary
misprices the edge response by a computable amount; on the declared
normalization the naive step
\(\delta S_{\mathrm{bulk}}=2\pi\delta\langle B\rangle\) fails off the
fixed-weight class by exactly \(\sum_\alpha\log d_\alpha\,\delta p_\alpha\). Machine receipts exhibit both defects
numerically with certified magnitudes. Hence the
Axiom-4 leading-term input and the declared edge normalization are genuine
branch content, consistent with the audit boundary that generalized entropy
is an independent axiom on this corpus.
\end{proposition}

\begin{proof}
(i) is immediate from the balance identity: replacing \(1/(4G)\) by
\(\gamma\) leaves the uncancelled multiple of \(\delta A\). (ii) is the
computation in Theorem~\ref{thm:bulk-edge-central-first-law}(2) with the
mismatched normalization, plus the naive-step defect formula proved there;
the machine receipt instantiates both with explicit blockwise states.
\end{proof}

\subsubsection{Uniform small-diamond limit and the absolute Einstein equation}
\label{subsubsec:uniform-small-diamond-absolute}

\begin{theorem}[One uniform scaling family]
\label{thm:uniform-scaling-family}
Let \((r,\ell_r,\delta_r)\), with \(\ell_r\downarrow0\), be one declared
cofinal scaling family on which Theorem~\ref{thm:collar-cmi-decay} holds
uniformly over the event region and cap family:
\[
\varepsilon_r
:=
c|\partial C_r|_{\mathrm{UV}}e^{-\delta_r/\xi_r}.
\]
Assume that the fixed-collar replacements used on this family have uniform
constants \(C_{\mathrm M}<\infty\), \(\theta>0\) with
\[
\delta_r^{\mathrm M}\le C_{\mathrm M}\varepsilon_r^\theta,
\]
and that, for some
\[
s>\max\{8,4/\theta\},\qquad \omega_r\longrightarrow+\infty,
\]
the same family satisfies the rate receipt
\[
\frac{\delta_r}{\xi_r}
-\log\!\bigl(c|\partial C_r|_{\mathrm{UV}}\bigr)
\ge
s\log(\ell_0/\ell_r)+\omega_r.
\]
Assume also the kernel-residual receipt
\(\epsilon_r^{\mathrm{ker}}=o(\ell_r^4)\) of
Theorem~\ref{thm:mobius-bounded-intervals}. Then, uniformly over the declared
region and cap family,
\[
r_{\mathrm{FR}}(\varepsilon_r)=o(\ell_r^4),
\qquad
\delta_r^{\mathrm M}=o(\ell_r^4),
\qquad
\epsilon_r^{\mathrm{ker}}=o(\ell_r^4).
\]
These estimates hold on one common domain of finite-rank test vectors.
No per-radius diagonal choice is used.
\end{theorem}

\begin{proof}
The rate receipt gives
\[
\varepsilon_r
\le
(\ell_r/\ell_0)^s e^{-\omega_r}.
\]
Proposition~\ref{prop:approxrecover} therefore gives
\[
r_{\mathrm{FR}}(\varepsilon_r)
\le2\sqrt{\varepsilon_r}
\le2(\ell_r/\ell_0)^{s/2}e^{-\omega_r/2}
=o(\ell_r^4)
\]
because \(s/2>4\). The uniform fixed-collar modulus gives
\[
\delta_r^{\mathrm M}
\le C_{\mathrm M}(\ell_r/\ell_0)^{s\theta}
e^{-\theta\omega_r}
=o(\ell_r^4)
\]
because \(s\theta>4\). The kernel estimate is a premise. The domain statement
holds because the finite-rank cores of
Proposition~\ref{prop:n3} are nested along the declared family and their
union is a common core by the mixed-GNS Cauchy clause. Uniformity is the
region-uniformity of the hypotheses.
\end{proof}

\begin{theorem}[Variation coverage]
\label{thm:variation-coverage}
On a connected event region carrying \(\mathsf{E1}\)--\(\mathsf{E4}\), the
coupled variation class of Theorem~\ref{thm:maxent-lagrange-stationarity},
transported by the produced Lorentz action, covers all local timelike unit
directions at all events of the region with realized reference states, and
the covered set is connected. Consequently the polarization argument of the
tensor upgrade (Theorem~\ref{thm:einstein} via
Lemma~\ref{lem:cap-pair-timelike-coverage}) applies eventwise on the region
without importing an external all-observer postulate.
\end{theorem}

\begin{proof}
\(\mathsf{E1}\) populates every chart box with events carrying frame data;
Lemma~\ref{lem:cap-pair-timelike-coverage} produces, from cap pairs, modular
data whose rest-frame directions realize a neighborhood of any given
timelike direction; the produced \(G\)-action (unitarily implemented on the
producer branch) acts transitively on the fiber \(H^3\) of directions
(Proposition~\ref{prop:h3-frame-space}) and continuously in the region, so
the orbit of the realized set is all of the direction bundle over the
region; connectedness follows since \(G\) and the region are connected and
\(\mathsf{E4}\) transitions are continuous.
\end{proof}

\begin{definition}[Vacuum-reference receipt]
\label{def:vacuum-reference-receipt}
\(\mathsf{VR}\): the region carries a realized MaxEnt reference state whose
constructed stress tensor (Theorem~\ref{thm:local-stress-construction}) is
maximally symmetric,
\(\langle T_{ab}\rangle_{\mathrm{ref}}=-\rho_{\mathrm{vac}}\,g_{ab}\), and
whose declared normalization sets the first-variation integration tensor to
zero at the reference point,
\(Y_{ab}[\omega_{\mathrm{ref}}]=0\). \(\mathsf{VR}\) is a physical
base-condition receipt: it is \emph{not} implied by
\(\delta Y_{ab}=0\), and Proposition~\ref{prop:baseline-countermodels} shows
it is irreducible.
\end{definition}

\begin{theorem}[Absolute semiclassical Einstein equation on the closed branch]
\label{thm:absolute-einstein-base-condition}
Assume the composed hypotheses: producer branch
(Theorem~\ref{thm:certificate-production}), null-net packet
(Theorems~\ref{thm:null-net-standardness}--\ref{thm:four-translation-assembly}),
event region with \(\mathsf{E1}\)--\(\mathsf{E4}\) and the smooth scaling
upgrade, constructed stress (Theorem~\ref{thm:local-stress-construction})
with \(\mathsf{UC}\), the repaired first law and coupled stationarity
(Theorems~\ref{thm:bulk-edge-central-first-law},
\ref{thm:maxent-lagrange-stationarity}), the uniform family
(Theorem~\ref{thm:uniform-scaling-family}), coverage
(Theorem~\ref{thm:variation-coverage}), and \(\mathsf{VR}\). Then on each
connected component of the region, as a semiclassical expectation-value
equation for the nonlinear fields,
\[
\boxed{\;G_{ab}+\Lambda\,g_{ab}=8\pi G\,\langle T_{ab}\rangle\;}
\]
with \(G=a_{\mathrm{cell}}/(4\bar\ell_{\mathrm{shared}})\) the structural
coupling of Definition~\ref{def:newton} (forbidden-input audit unchanged: no
measured \(G\), Planck area, measured \(\Lambda\), or gravity-calibrated
clock enters), and \(\Lambda\) one constant per component, fixed relative to
the \(\mathsf{VR}\) reference by
\(\Lambda=8\pi G\rho_{\mathrm{vac}}+\Lambda_{\mathrm{ref}}\) with
\(\Lambda_{\mathrm{ref}}\) the reference-curvature constant; its global
numerical closure is the separate D6 capacity gate. Without
\(\mathsf{VR}\), the conclusion degrades exactly to: \(G_{ab}+8\pi G\langle
T_{ab}\rangle\)-balance up to one undetermined covariantly constant tensor
\(Y_{ab}=c\,g_{ab}\) per component (constancy, not absoluteness).
\end{theorem}

\begin{proof}
The chain Theorem~\ref{thm:equilibrium} \(\to\) Lemma~\ref{lem:smallball}
\(\to\) Theorem~\ref{thm:fixed-volume-small-ball-area} \(\to\)
Theorem~\ref{thm:einstein} runs with every required input
supplied: the locally Lorentzian \(d=4\) regime and the geodesic-ball
identity are consumed from the event packet on its smooth branch (the
fixed-volume area expansion is a metric identity requiring only the
constructed \(C^\infty\)-branch metric and no field equation); the
small-ball kernel is the constructed density of
Theorem~\ref{thm:local-stress-construction}(3) through
Lemma~\ref{lem:smallball}; the remainders are uniform by
Theorem~\ref{thm:uniform-scaling-family}; the first-variation identity with
the moving stress channel is Theorem~\ref{thm:maxent-lagrange-stationarity};
and coverage is Theorem~\ref{thm:variation-coverage}. The output of the
tensor upgrade is \(\delta Y_{ab}=0\) for
\(Y_{ab}:=G_{ab}+\Lambda' g_{ab}-8\pi G\langle T_{ab}\rangle\) along the
covered class; coverage plus polarization make \(Y_{ab}\) direction-independent,
the Ward identity of Theorem~\ref{thm:local-stress-construction}(4) and the
contracted Bianchi identity (valid on the smooth branch) force
\(\nabla^aY_{ab}=0\), and \(Y\) proportional to \(g\) with
\(\nabla(Y-cg)=0\) forces \(Y_{ab}=c\,g_{ab}\) with \(c\) locally constant,
hence constant per connected component. \(\mathsf{VR}\) evaluates \(c\) at
the reference state: \(Y[\omega_{\mathrm{ref}}]=0\) fixes \(c\) in terms of
\(\rho_{\mathrm{vac}}\) and the reference curvature, absorbing it into the
displayed \(\Lambda\). The coupling propagates literally from
Definition~\ref{def:newton} through the edge/area dictionary as in the
existing structural-coupling theorem; no step introduces a measured
constant. The degraded conclusion without \(\mathsf{VR}\) is the same
argument stopped before the evaluation step.
\end{proof}

\begin{proposition}[Failure examples: uniformity, coverage, connectedness, baseline]
\label{prop:baseline-countermodels}
Each hypothesis of Theorem~\ref{thm:absolute-einstein-base-condition} is
load-bearing:
(i) with per-radius stage choices in place of
Theorem~\ref{thm:uniform-scaling-family}, the diagonal family can satisfy
\(\eta\leq\ell^5\) stagewise while no single cofinal family does (choose
stages with incompatible domains: the receipt fails and the limit order is
undefined);
(ii) with population confined as in
Proposition~\ref{prop:event-countermodels}(i), coverage fails and the
polarization argument determines only the \(uu\)-component along one
worldline;
(iii) on a disconnected region, \(\Lambda\) genuinely differs between
components: two receipt-carrying components with different reference
curvatures satisfy all variational identities with different constants;
(iv) without \(\mathsf{VR}\), de Sitter and flat reference branches satisfy
the \emph{same} first-variation identities with different \(Y_{ab}=c\,g_{ab}\):
\(\delta Y_{ab}=0\) never fixes \(c\). Machine receipts instantiate (iv) and
the tomography/coefficient countermodels numerically.
\end{proposition}

\begin{proof}
(i) is the observation in the theorem's proof that the union-core exists
only along a declared family; an adversarial stage assignment with disjoint
cores has no common domain. (ii) is
Proposition~\ref{prop:event-countermodels}(i) fed through
Theorem~\ref{thm:variation-coverage}. (iii) constancy is proved per
component only; the example is two disjoint receipt regions. (iv) both
backgrounds are maximally symmetric, so all covered variations produce
identical \(\delta Y=0\) data while \(c\) differs by
\(\Lambda_{\mathrm{dS}}\); this is the standard integration-constant freedom,
here pinned only by \(\mathsf{VR}\).
\end{proof}

\subsubsection{The composed branch-entry theorem and the realized-branch status}
\label{subsubsec:composed-branch-entry}

\begin{theorem}[Composed Einstein branch-entry theorem]
\label{thm:einstein-branch-entry-composed}
Let \((\mathfrak B_r)\) be a refinement tower of finite transactional OPH
repair systems satisfying the node-D1 hypotheses and
Axioms~\ref{ax:screen}--\ref{ax:entropy}, with inputs partitioned as:
\begin{itemize}[leftmargin=2em]
\item \textbf{(Ax)} foundational axioms: the MaxEnt/recovery package with
the central-interface clause; the generalized-entropy leading term and edge
normalization \(z_\alpha=\log d_\alpha\) (the Axiom-4 boundary);
\item \textbf{(R\(_{\mathrm{fin}}\))} decidable finite-stage receipts:
\(\mathsf{SphInc}\), disk/mesh, \(\mathsf{CR}\),
\(\mathsf{KMS}(2\pi)\); \(\mathsf{Cyc}\), \(\mathsf{NTI}\), weak additivity,
\(\mathsf{MI}\); \(\mathsf{E1}\)--\(\mathsf{E4}\);
\item \textbf{(R\(_{\mathrm{scale}}\))} scaling receipts: kernel residuals
\(o(\ell^4)\) on one declared family; uniform strong conditional Gibbs
mixing constants, boundary counts, fixed-collar replacement modulus, and the
sharp collar rate margin of Theorem~\ref{thm:uniform-scaling-family}; the
\(C^{1,1}\)/smooth upgrade;
\item \textbf{(R\(_{\mathrm{phys}}\))} physical-identification receipts:
\(\mathsf{UC}\), \(\mathsf{VR}\), the absolute conformal scale, stable
causality/record-Cauchy clauses.
\end{itemize}
Then the composition
\[
\text{D1}\to\text{D3h}\to\text{D3b--f}\to\text{D4}\to\text{D4b}
\to T_{ab}\to S_{\mathrm{gen}}\text{-law}\to
\text{uniform small-diamond}\to
\bigl(G_{ab}+\Lambda g_{ab}=8\pi G\langle T_{ab}\rangle\bigr)
\]
holds with each arrow the cited theorem of this manuscript, on common
domains with composable error envelopes, at semiclassical
expectation-value level, with \(G\) structural and \(\Lambda\) per-component.
Every target object is produced by an arrow; none is assumed except through
the listed inputs. The branch is \emph{nonempty} exactly when some realized
tower carries (R\(_{\mathrm{fin}}\)) cofinally with
(R\(_{\mathrm{scale}}\)) moduli, a machine-checkable condition at every
finite stage.
\end{theorem}

\begin{proof}
Composition and bookkeeping: D1 is Theorem~\ref{thm:confluence} and its
package; D3h is Theorems~\ref{thm:topology-production}--%
\ref{thm:certificate-production}; D3b--f are
Theorem~\ref{thm:bw} with Corollaries~\ref{cor:lorentz},
\ref{cor:h3-spatial-chart} (using the produced certificate); D4 is
Theorems~\ref{thm:null-net-standardness}--\ref{thm:four-translation-assembly};
D4b is Theorems~\ref{thm:event-4-manifold}--\ref{thm:clock-gluing}; the
stress arrow is Theorem~\ref{thm:local-stress-construction}; the entropy
arrow is Theorems~\ref{thm:bulk-edge-central-first-law} and
\ref{thm:maxent-lagrange-stationarity}; the final arrows are
Theorems~\ref{thm:uniform-scaling-family},
\ref{thm:variation-coverage}, and
\ref{thm:absolute-einstein-base-condition}. Domains compose because each
packet's output object is the next packet's declared input on the same
tower, and every error envelope is stated on the common declared scaling
family; the statement-level classification is inherited from the packets.
Nonemptiness is by definition of the receipts, whose finite-stage clauses
are decidable (Definitions~\ref{def:spherical-incidence-receipt},
\ref{def:cap-mesh-crossratio-receipts},
\ref{def:modular-intersection-receipt},
\ref{def:event-manifold-receipts}).
\end{proof}

\begin{proposition}[No hidden geometry in the inputs]
\label{prop:no-hidden-geometry}
The input class (Ax)\(+\)(R\(_{\mathrm{fin}}\)-\emph{form}) hides none of the
target objects: within the class of towers satisfying (Ax) and the D1
hypotheses, there are members realizing
(i) non-spherical and non-manifold screen topologies and arbitrary modular
normalizations (Theorem~\ref{thm:incidence-underdetermination});
(ii) event sets of dimension \(1\), \(5\), or non-Hausdorff type
(Proposition~\ref{prop:event-countermodels});
(iii) positive directional generators with no rank-two local source
(Proposition~\ref{prop:no-local-stress-countermodel});
(iv) identical first-variation data with distinct absolute baselines
(Proposition~\ref{prop:baseline-countermodels}(iv)).
Hence no target (\(S^2\), \(3{+}1\), Lorentzian metric, local stress,
area law, or Einstein relation) is a consequence of the input
\emph{form}; each enters exactly through the named receipt that excludes the
corresponding countermodel, and the receipt list of
Theorem~\ref{thm:einstein-branch-entry-composed} is thereby minimal in the
sense that deleting any receipt family readmits its countermodel.
\end{proposition}

\begin{proof}
Each item cites its countermodel theorem; minimality is the observation that
each countermodel satisfies every input except the named receipt.
\end{proof}

\begin{remark}[Realized-branch nonemptiness: machine status]
\label{rem:realized-branch-status}
The nonemptiness clause is empirical and machine-checkable. The repository's
realized-branch receipt evaluation records
the following state.

(i) \emph{Topology and mesh.} The verified rooted-tree packet-net domain
fails \(\mathsf{SphInc}\) (\(\chi=1\), no \(2\)-simplices), as any tree
must. A designed cellulated-sphere mesh passes \(\mathsf{SphInc}\) but is
declared geometry, not a consensus product. The cyclic cap-net repair run
is a genuine
transactional repair tower with seeded conflicts and runtime-verified
termination, conflict-free normal forms, and schedule independence across
randomized schedules on a three-stage refinement tower of \(20/80/320\)
records. Its repaired normal-form output passes \(\mathsf{SphInc}\) at
every stage with decreasing mesh modulus and simplicial refinement
naturality. The overlap net of that run is chosen spherical, which is
explicit branch selection in the sense of
Corollary~\ref{cor:dimension-selection-status} and never a consensus
output; the run certifies joint realizability of the node-D1 clauses with
the \(\mathsf{SphInc}\)/mesh/naturality families on one repair tower.

(ii) \emph{Boundary-collar modular data.} The free-fermion modular-clock
instrumentation computes arc
entanglement Hamiltonians \(h=\log((1-C_I)/C_I)\) at \(120\)-digit
precision on Gaussian MaxEnt collar states (critical hopping,
anti-periodic twist, half filling, unit Fermi velocity) for collar rings
\(N_r=16,32,64\); the arc spectrum reaches \(10^{-30}\) of its endpoints,
beyond double precision. The modular velocity profile, extracted by the
odd-range chiral resummation
\(\beta(j)=-2\sum_{r\,\mathrm{odd}}r(-1)^{(r-1)/2}h_{i,i+r}\), matches the
\(2\pi\)-normalized conformal Bisognano--Wichmann profile with median
interior residual \(4.4\times10^{-3}\), \(1.1\times10^{-3}\), and
\(1.1\times10^{-4}\) at the three stages, and the \(\times1.2\)
wrong-normalization control is separated by more than a factor five at
every stage. The nearest-neighbour truncation of the same data misses the
profile by roughly nine percent at every stage and serves as the
wrong-extraction control. Modular transport cross-ratios
\(\exp(2\pi\sum_j1/\beta_j)\) over fixed angular quadruples are Cauchy
along refinement and match the M\"obius cross-ratios with relative errors
\(1.1\times10^{-2}\), \(2.3\times10^{-3}\) at the two finer stages. The
boundary-collar cross-ratio and \(2\pi\)-KMS clauses are witnessed on this
tower.

(iii) \emph{Null-net standardness.} The null-net instrumentation
witnesses, on the same
states: nontrivial relative commutants and weak additivity (combinatorial,
every stage); strictly positive separating moduli (occupation spectra
strictly inside \((0,1)\)); mixed-GNS Cauchy behaviour of fixed smeared
observables; the one-particle half-sided-inclusion compression condition,
as a chiral-packet leakage asymmetry of at least \(9.6\) with one
consistent direction across stages, where a real packet shows exactly zero
asymmetry by time-reversal symmetry and serves as the null control; and
the modular Lie-closure receipt, in which the one-particle commutator
\(i[h_A,h_B]\) matches the conformal-algebra prediction
\(-\!\int(\beta_A\beta_B'-\beta_A'\beta_B)P\) after even-range chiral
resummation of the lattice momentum density, with shape residuals
\(0.2\%\) and \(0.7\%\) against unresummed controls of \(3.6\%\) and
\(6.0\%\). The decay rate of that residual is uncertified and is an open
clause.

(iv) \emph{Events on the screen.} The realized-event instrumentation
runs the event
pipeline on records generated by the sequential transactional repair
dynamics, with the clock in the certified \(2\pi\)-normalized modular unit
calibrated to the lattice propagation speed and chart noise calibrated to
the measured cross-ratio residuals. Screen population with shrinking radii
(\(\mathsf{E1}\), seeding scale), certified pairwise separation
(\(\mathsf{E2}\)), and the M\"obius chart cocycle at noise level
(\(\mathsf{E4}\)) hold, and the intrinsic read-after-write ancestry order
is separated by a quadratic cone of Lorentzian signature \((1,2)\) whose
timelike eigenvector aligns with the modular clock to \(0.9995\). With
screen-only records the event set is a \((1{+}2)\)-dimensional sheet and
is measured as such (chart PCA rank three): countermodel (i) of
Proposition~\ref{prop:event-countermodels} operating as designed, since
event dimension is a population output.

(v) \emph{Bulk depth.} The bulk-depth instrumentation
places records at the
cells of all tower stages with the produced depth dictionary
\(\rho=-\log\tan(\alpha/2)\), the M\"obius rapidity of the record's cap.
Coarse cells are deep records and fine cells near-boundary records, the
scale/radius duality realized by the refinement tower, and the hyperbolic
metric equalizes lattice propagation speeds across stages (measured
max/min ratio \(1.16\)). Two dynamics are on file. Under the
corpus-consistent inverse-system coupling (per-stage patches with one-step
interface patches between consecutive stages, the node-D1
refinement-projection structure), the record set witnesses
\(\mathsf{E3}\) rank four with positive observability, bulk chart PCA
dimension four, and an intrinsic ancestry cone of Lorentzian signature
\((1,3)\) at all five seeds, with the modular clock timelike to
\(0.999\)--\(1.000\) and classification \(84\)--\(86\%\). Under the
strong-coupling variant (one global patch namespace, so a coarse commit
writes every scale in one tick), the measured signature is \((2,2)\);
depth degenerates to a second causal direction. That variant violates the
inverse-system structure and is retained as a countermodel: the receipt
detects pathological depth dynamics. Two caveats are explicit: the
timelike cone margin is small (normalized eigenvalue \(-0.028\) to
\(-0.009\) across seeds, stable in sign), and margin convergence with
commit density and tower depth is uncertified work in progress.

\emph{State of the gate.} Every structural receipt family of
Theorem~\ref{thm:einstein-branch-entry-composed} carries a realized
witness at finite or one-particle level: topology/mesh (with explicit
branch selection), boundary-collar modular, null-net standardness,
screen-event, and the bulk-depth \((1,3)\) cone. The open obligations are
the cone-margin convergence study, the \(\mathsf{Cyc}\) limit clause, the
Lie-closure rate, second-quantized \(\mathsf{MI}\), cap-interior modular
data, and the physical-identification receipts. The realized geometric
branch is therefore not certified nonempty, and the composed theorem is
conditional. Public summaries must state exactly this: derivation complete
on the receipt branch; all structural receipt families realized at finite
or one-particle level, including a seed-stable Lorentzian \((1,3)\)
ancestry cone on the corpus-consistent multi-scale dynamics;
margin-convergence, limit-clause, cap-interior, and physical-receipt work
in progress.
\end{remark}

\subsection{Cosmological-constant / screen-capacity closure}

\begin{lemma}[Vacuum-Energy Blindness]\label{lem:vac}
For any null vector $k$ and any vacuum-energy contribution $T^{\mathrm{vac}}_{ab}=-\rho_{\mathrm{vac}}g_{ab}$,
\[
T^{\mathrm{vac}}_{kk}=0.
\]
\end{lemma}

\begin{proposition}[Structural Separation of $\Lambda$]\label{prop:lambda}
Local null-modular data fix $T_{ab}$ only up to $\phi g_{ab}$. Therefore $\Lambda$ is not determined by local overlap consistency alone. The intended global-capacity target is the cosmic record-closure readback fixed point of Definition~\ref{def:self-closure-density}; its map \(F\), fixed-point certificate, and coupling premises are unconstructed (CL-7).
\end{proposition}

\begin{corollary}[Cosmological capacity relation]\label{cor:lambda}
If a cosmic record-capacity fixed point is constructed and identified with the de Sitter static-patch
entropy,
\[
N_{\mathrm{CRC}}=S_{\mathrm{dS}},
\]
\noindent and the standard de Sitter entropy relation
\[
S_{\mathrm{dS}}=\frac{A_{\mathrm{dS}}}{4G}=\frac{3\pi}{G\Lambda},
\]
then
\[
\Lambda_{\mathrm{CRC}}=\frac{3\pi}{G N_{\mathrm{CRC}}}.
\]
Equivalently, for the geometric scale \(G_{\mathrm{geom}}=\ell_\star^2\), the conditional capacity relation fixes
the dimensionless product
\[
\Lambda_{\mathrm{CRC}}\ell_\star^2=\frac{3\pi}{N_{\mathrm{CRC}}}.
\]
The SI value of \(\Lambda_{\mathrm{CRC}}\) or of the scale product
\(\Lambda_{\mathrm{CRC}}N_{\mathrm{CRC}}\) requires the selected scale certificate.
\end{corollary}

\begin{corollary}[Conditional global screen-capacity closure of the Einstein branch]\label{cor:lambda-global}
Assume the hypotheses of Theorem~\ref{cor:einstein} and Corollary~\ref{cor:lambda}. Then on the same connected scaling branch,
\[
G_{ab}+\frac{3\pi}{G N_{\mathrm{CRC}}}\,g_{ab}=8\pi G\,\langle T_{ab}\rangle.
\]
Under the stated hypotheses, the local Einstein recovery closes globally at the cosmic
record-capacity fixed point \(N_{\mathrm{CRC}}\).  This corollary does not construct \(F\) or
discharge the capacity-coupling premises.
\end{corollary}

\begin{proof}
Theorem~\ref{cor:einstein} gives
\[
G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle
\]
on the connected scaling branch. Under its stated hypothesis, Corollary~\ref{cor:lambda} identifies
\[
\Lambda_{\mathrm{CRC}}=\frac{3\pi}{G N_{\mathrm{CRC}}}
\]
at the assumed cosmic record-capacity fixed point. Substituting that value of \(\Lambda\) yields the stated equation.
\end{proof}

\subsection{No-smuggling dependency discharge for the Einstein bridge}

\begin{theorem}[Einstein bridge dependency discharge (E0)]\label{thm:einstein-bridge-discharge}
Write OPH5 for Axioms~\ref{ax:screen}--\ref{ax:mar}: the \(S^2\) screen net,
overlap consistency, local MaxEnt/refinement, recoverable generalized entropy,
and MAR.  On any recovered-core, support-visible scaling branch of a cofinal
OPH regulator family satisfying quotient confluence and the regularity
hypotheses stated in Sections~2--5, OPH5 supplies the branch inputs used by the
Einstein bridge:
\begin{enumerate}[leftmargin=2em,label=(\roman*)]
\item the geometry readout factors through quotient normal forms via the
screen fold \(\chi_{S,r}\circ n_r\circ\pi_r\);
\item round-cap pairs carry the Lorentz/H3 readout because
\(\mathrm{Conf}^+(S^2)\cong \mathrm{PSL}(2,\mathbb C)\cong
\mathrm{SO}^+(3,1)\) and the observer rest space is
\(H^3\simeq\mathrm{SO}^+(3,1)/\mathrm{SO}(3)\);
\item the support-visible BW theorem on the extracted prime geometric subnet
fixes the \(2\pi\)-normalized cap modular flow;
\item the null modular bridge identifies the positive half-line translation
generator with the local null-stress charge on the same branch;
\item the bounded-interval kernel is supplied by
Lemma~\ref{lem:bounded-interval-kernel};
\item fixed-cap generalized-entropy stationarity is the MaxEnt/refinement
stationarity theorem for admissible cap-label-preserving variations;
\item the small-ball area term is the standard fixed-volume geometric identity
after the geometry readout has been discharged;
\item the carried collar and derivative remainders are \(o(\ell^4)\) by
Lemma~\ref{lem:diagonal-remainder}; and
\item all timelike directions are covered by cap-pair geometry as in
Lemma~\ref{lem:cap-pair-timelike-coverage}.
\end{enumerate}
Thus the finite consensus reduct supplies quotient normal forms, while OPH5 on
the declared recovered-core, support-visible scaling branch supplies the
geometric, modular, stress, entropy, and coverage inputs needed by the Einstein
bridge.  Bare finite consensus without those OPH5 branch closures does not
imply the Einstein equation.
\end{theorem}

\begin{proof}
The quotient reduct supplies schedule-independent normal forms; the screen-net
and support-visible extraction of Theorem~\ref{thm:geosubnet} make the
observer-readable cap data quotient-safe.  The cap automorphism and KMS/BW
normalization are Theorem~\ref{thm:bw}, and the Lorentz/H3 statement is the
standard conformal action of round cuts on \(S^2\).  Corollary~\ref{cor:n2},
Lemma~\ref{lem:translation}, and Theorem~\ref{thm:stress} supply the
half-sided modular pair, positive null generator, and half-line
generator/charge identity.  Axioms~\ref{ax:maxent} and \ref{ax:entropy}
together with Theorem~\ref{thm:equilibrium} supply the fixed-cap
generalized-entropy stationarity statement on the realized
cap-label-preserving MaxEnt family.  Lemmas~\ref{lem:bounded-interval-kernel},
\ref{lem:diagonal-remainder}, and \ref{lem:cap-pair-timelike-coverage}
discharge the remaining downstream bridge inputs.  The last sentence records
the scope: the theorem is an OPH5 recovered-core branch theorem, not a claim
about arbitrary terminating finite rewrite systems.
\end{proof}

\begin{lemma}[Bounded-interval kernel from null projective covariance (E0.5)]\label{lem:bounded-interval-kernel}
On the null blow-up of the support-visible geometric branch, assume the
half-line generator/charge identity, endpoint-Lipschitz renormalized interval
control, and affine/projective covariance of the interval-preserving null
action.  Then for a null interval \((a,b)\) the local interval modular
generator has the universal kernel
\[
K_{(a,b)}^{\mathrm{null}}
=2\pi\int_a^b \frac{(v-a)(b-v)}{b-a}\,T_{kk}(v)\,dv
+R_{(a,b)},
\]
where \(R_{(a,b)}\) is the controlled endpoint/collar remainder carried by the
same refinement family.  In the small-ball limit this is the ball modular
kernel used in Lemma~\ref{lem:smallball}.
\end{lemma}

\begin{proof}
The half-line bridge fixes the affine null translation generator as a local
stress charge.  Projective covariance transports this generator from
half-lines to finite intervals and fixes the unique quadratic interval weight
that vanishes at both endpoints and has the correct affine limit:
\((v-a)(b-v)/(b-a)\).  Endpoint-Lipschitz interval control prevents endpoint
counterterms from changing the leading local charge; the remaining
collar/endpoint contribution is exactly the carried \(R_{(a,b)}\).
\end{proof}

\begin{lemma}[Diagonal remainder lemma (E0.6)]\label{lem:diagonal-remainder}
Let \(\ell\) be the small-ball radius and \(\eta_\delta\to0\) the carried
collar/Markov/recovery error at collar scale \(\delta\) on the cofinal
refinement branch. Assume one declared family
\(\delta=\delta(\ell)\) satisfies the quantitative rate receipt
\(\eta_{\delta(\ell)}=o(\ell^4)\), uniformly on the region and cap family.
Consequently the interval endpoint,
collar, and long-wavelength derivative remainders do not contribute to the
Einstein coefficient in the \(\ell\to0\) bridge limit.
\end{lemma}

\begin{proof}
The rate premise controls the carried collar contribution uniformly by
\(o(\ell^4)\). The ordinary small-ball derivative remainders are of higher
order in \(\ell\), so their sum is \(o(\ell^4)\). Mere pointwise convergence
\(\eta_\delta\to0\) would permit a different stage for every radius and would
not prove this statement; Theorem~\ref{thm:uniform-scaling-family} supplies
one sufficient common-family receipt.
\end{proof}

\begin{lemma}[Cap-pair timelike coverage (E0.7)]\label{lem:cap-pair-timelike-coverage}
On the Lorentz/H3 branch of Theorem~\ref{thm:bw}, overlapping observer cap
pairs supply every local timelike direction needed for the scalar-to-tensor
upgrade.
\end{lemma}

\begin{proof}
By Proposition~\ref{prop:h3-frame-space}, every observer frame is a future
unit timelike vector \(u\in H^3\) with normalized sky
\[
\mathcal S_u=\{u+s:s\in u^\perp,\ \eta(s,s)=1\}.
\]
Let \(v\) be any future timelike vector and put
\[
r:=\sqrt{-\eta(v,v)},\qquad u:=v/r\in H^3.
\]
For any unit \(s\in u^\perp\), define
\[
q_\pm:=u\pm s.
\]
Then
\[
\eta(q_\pm,q_\pm)=\eta(u,u)+\eta(s,s)=-1+1=0,
\qquad
q_\pm^0>0,
\]
in a frame where \(u=u_0\), and hence in every proper orthochronous frame.
Moreover,
\[
\boxed{
v=\frac r2\,(q_++q_-).
}
\]
Thus normalized future null directions in observer skies cover every future
timelike direction once the observer-frame chart is supplied. The cap-pair
data select the corresponding local causal diamonds; the overlap atlas
therefore provides the all-directions hypothesis used in
Theorem~\ref{cor:einstein}. This argument does not say that two unnormalized
projective rays alone select a unique observer frame; the observer
normalization or equivalent causal-diamond scale data is also required.
\end{proof}

\begin{proposition}[Recovered-core stress closure (E2)]\label{prop:recovered-core-stress-closure}
If the recovered stress tensor is reconstructed from the full compatible
family of null and timelike modular charges on the recovered core, then it is
covariantly conserved on that branch:
\[
\nabla^a\langle T_{ab}\rangle=0 .
\]
\end{proposition}

\begin{proof}
The charge family is defined by overlap-compatible local modular generators.
For an infinitesimal recovered-core diamond, opposite faces inherit the same
overlap charge with opposite orientation, so the net first-order flux defect
vanishes in the refinement limit.  After the cap-pair tensor upgrade this
local charge conservation is exactly the covariant divergence-free condition.
\end{proof}

\begin{corollary}[OPH physical Einstein equation on the discharged branch (E1)]\label{cor:oph-physical-einstein-equation}
Under Theorem~\ref{thm:einstein-bridge-discharge}, the recovered-core scaling
branch satisfies
\[
G_{ab}+\Lambda g_{ab}=8\pi G_{\mathrm{geom}}\,
\langle T_{ab}\rangle
\]
modulo the local null-data ambiguity in \(\Lambda g_{ab}\). If the D6 cosmic
record-capacity hypothesis is discharged,
\[
\Lambda_{\mathrm{CRC}}\ell_\star^2=\frac{3\pi}{N_{\mathrm{CRC}}},
\qquad
G_{\mathrm{geom}}=\ell_\star^2 .
\]
\end{corollary}

\begin{proof}
Theorem~\ref{thm:einstein-bridge-discharge} supplies the geometry readout, BW
normalization, null-stress charge, bounded-interval kernel, fixed-cap
stationarity, small-ball area term, remainder control, and timelike coverage.
Theorems~\ref{thm:einstein} and \ref{cor:einstein} then give the tensor
Einstein equation modulo the expected metric ambiguity.  Corollary~\ref{cor:lambda-global}
and the scale convention \(G_{\mathrm{geom}}=\ell_\star^2\) give the displayed
conditional D6 capacity relation.
\end{proof}

\begin{theorem}[OPH Einstein-branch closure theorem]\label{thm:oph-einstein-branch-closure}
For a cofinal OPH5 regulator family on a recovered-core, support-visible
scaling branch satisfying quotient confluence, support-visible branch
regularity, and the hypotheses discharged in
Theorem~\ref{thm:einstein-bridge-discharge}, the scaling-limit Einstein branch
satisfies
\[
G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle
\]
modulo the expected local null-data ambiguity in \(\Lambda g_{ab}\). If the D6
capacity hypothesis is discharged,
\[
\Lambda=\frac{3\pi}{G N_{\mathrm{CRC}}}.
\]
\end{theorem}

\begin{proof}
Theorem~\ref{thm:einstein-bridge-discharge} turns the OPH5 recovered-core
branch into the exact hypothesis package required by the Jacobson-type bridge:
quotient-safe geometry readout, \(2\pi\)-normalized BW cap flow, local null
stress charge, bounded-interval ball kernel with \(o(\ell^4)\) remainder,
fixed-cap generalized-entropy stationarity, the fixed-volume small-ball area
identity, and all timelike directions.  Lemma~\ref{lem:smallball} gives the
bulk entropy variation coefficient \(8\pi^2\ell^4/15\), while
Theorem~\ref{thm:fixed-volume-small-ball-area} gives the area variation
coefficient \(-\pi\ell^4/(15G)\).  Theorem~\ref{thm:equilibrium} forces their
sum to vanish, yielding Theorem~\ref{thm:einstein}.  The scalar-to-tensor
upgrade in Theorem~\ref{cor:einstein} gives the tensor equation, and
Corollary~\ref{cor:lambda-global} then fixes the remaining metric term on the conditional D6
capacity branch.
\end{proof}

\begin{remark}[Einstein-branch falsifiers]\label{rem:einstein-branch-falsifiers}
The OPH Einstein branch fails if quotient-normal-form confluence fails; geometry
readout depends on hidden carrier coordinates, port labels, worker schedule, or
repair schedule; support-visible BW modular flow does not become the
\(2\pi\)-normalized cap-preserving conformal flow; the null-stress bridge fails
to identify the half-line generator with local stress charge; bounded-interval
transport fails to give the ball kernel with \(o(\ell^4)\) remainder;
fixed-cap MaxEnt stationarity fails for the declared admissible variations; the
small-ball area coefficient or area-law normalization fails; timelike-direction
completeness fails; or a supplied D6 readback map lacks a unique, target-independent fixed point.
\end{remark}

\begin{corollary}[Conditional de Sitter static-patch parameter display on the D6 branch]\label{cor:lambda-parameters}
Assume the hypotheses of Corollary~\ref{cor:lambda} and a supplied geometric scale
\(G_{\mathrm{geom}}=\ell_\star^2\). Then the assumed cosmic record-capacity fixed point gives the
coherent static-patch display
\[
S_{\mathrm{dS}}=N_{\mathrm{CRC}},
\qquad
A_{\mathrm{dS}}=4G N_{\mathrm{CRC}},
\qquad
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c}.
\]
Together with Corollary~\ref{cor:lambda-global}, this packages the conditional D6 branch as the proposed global closure
of the same Einstein branch plus the de Sitter entropy relation. The radius and timescale are
displayed after the selected scale certificate is supplied.
\end{corollary}

\begin{proof}
Corollary~\ref{cor:lambda} fixes \(\Lambda G_{\mathrm{geom}}=3\pi/N_{\mathrm{CRC}}\). Once
\(G_{\mathrm{geom}}\) is supplied by the selected scale certificate, the de Sitter entropy-area relation gives
\[
S_{\mathrm{dS}}=\frac{A_{\mathrm{dS}}}{4G}=N_{\mathrm{CRC}},
\]
and the standard static-patch formulas give the stated \(r_{\mathrm{dS}}\) and \(t_\Lambda\).
\end{proof}

\begin{remark}[Capacity normalization]\label{rem:lambda-capacity-normalization}
The entropy capacity and the bare horizon area ratio differ by the factor \(\pi\). In Planck units,
\[
N_{\mathrm{patch}}=\left(\frac{r_{\mathrm{dS}}}{\ell_P}\right)^2
=\frac{3}{\Lambda\ell_P^2},
\qquad
N_{\mathrm{scr}}=\pi N_{\mathrm{patch}}
=\frac{3\pi}{\Lambda\ell_P^2}.
\]
For the Planck--\(\Lambda\) central comparison \(\Lambda\ell_P^2\simeq2.844\times10^{-122}\), this gives
\(N_{\mathrm{patch}}\simeq1.055\times10^{122}\) and
\(N_{\Lambda}:=N_{\mathrm{scr}}\simeq3.313\times10^{122}\). The conditional D6 branch uses the
second quantity because \(N_{\mathrm{scr}}\) is defined as the de Sitter entropy capacity. This
number is a central-value comparison readout; the unconstructed map supplies no output.
\end{remark}

\begin{definition}[Cosmic record-closure capacity]\label{def:self-closure-density}
For a candidate entropy capacity \(N\), let \(\mathfrak U_N\) be the OPH universe candidate with
supplied active boundary capacity \(N\), let \(\operatorname{nf}\) be the quotient normal-form map
on the declared terminating/confluent repair surface, let \(\operatorname{Obs}\) select the stable
self-reading observer sector, and let \(\operatorname{Cap}_{\mathrm{read}}\) return the capacity
reconstructed by that sector. The capacity readback map is
\[
F(N)=
\operatorname{Cap}_{\mathrm{read}}
\bigl(\operatorname{Obs}(\operatorname{nf}(\mathfrak U_N))\bigr).
\]
The cosmic record-closure capacity target is the fixed point
\[
N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}}),
\qquad
\Lambda_{\mathrm{CRC}}=\frac{3\pi}{G N_{\mathrm{CRC}}}.
\]
This definition specifies the type and target of the readback construction. A construction of
\(F\), a self-map or contraction certificate, and proofs of premises CP-1--CP-3 remain required.
The screen-normalized count representation is as follows. Let \(\Omega^{\mathrm{sc}}_N\) denote
the terminal OPH normal forms at capacity \(N\) that are closed under repair, support at least one
stable observer/checkpoint subfederation, carry the recovered local package, and whose own horizon
record surface reads back capacity \(N\). Define
\[
\Pi(N):=\frac{|\Omega^{\mathrm{sc}}_N|}{\dim \mathcal H_{\partial,N}}
=|\Omega^{\mathrm{sc}}_N|e^{-N},
\qquad
\log\dim \mathcal H_{\partial,N}=N.
\]
This is a horizon record-capacity statement. It does not select the dimension of a primitive
observer algebra. Combined with the pixel area relation
\(P_\star=a_{\mathrm{cell}}/\ell_\star^2\), a capacity value would give the equal-area chart count
\[
K_{\mathrm{cell}}
=\frac{A_{\mathrm{screen}}}{a_{\mathrm{cell}}}
=\frac{4N_{\mathrm{CRC}}}{P_\star},
\]
which is about \(8.12\times10^{122}\) when evaluated at the Planck--\(\Lambda\) central comparison.
The value
\(P_\star/4\simeq0.408\) nats is an edge/cut density, not
\(\log\dim\mathcal H_{\mathrm{cell}}\) for an autonomous cell factor. A fixed elementary observer
carrier would require additional hypotheses about homogeneous cellulation, isomorphic cell
algebras, equivariant overlaps, refinement preservation, and selection of a one-cell or fixed-block
carrier.
The corresponding input-free selector target is
\[
N_\star=\operatorname{MAR}\arg\max_N\left[\log|\Omega^{\mathrm{sc}}_N|-N\right].
\]
Equivalently, with \(\ell(N)=\log|\Omega^{\mathrm{sc}}_N|-N\), the proposed stationarity map
\[
T_\eta(N)=N+\eta\ell'(N)
\]
would have a unique stable fixed point under the required derivative-sign certificate. Informally,
\(N_{\mathrm{CRC}}\) is the target capacity where the universe would read back its own boundary
without deficit or slack.
\end{definition}

\begin{remark}[Capacity fixed-point reading]\label{rem:self-closure-counting-target}
Definition~\ref{def:self-closure-density} gives the precise D6 screen-capacity target. Its formula
specifies the proposed domain and codomain of \(F\); an explicit map on the OPH finite normal-form
grammar has not been constructed. The full screen dimension supplies the proposed normalization
\(e^{-N}\) in the count representation. In differentiable form, the pressure certificate would be
the fixed-point condition \(T_\eta(N)=N\), equivalently
\[
\frac{d}{dN}\left[\log|\Omega^{\mathrm{sc}}_N|-N\right]=0.
\]
The Planck--\(\Lambda\) central comparison gives
\[
N_{\Lambda}=N_{\mathrm{scr}}\simeq3.313\times10^{122}.
\]
Identifying this branch-location comparison with a fixed point is an additional conditional step in
Theorem~\ref{thm:lambda-stack}, subject to the map and premise obligations above.
\end{remark}

\begin{remark}[Observed-age benchmark boundary]\label{rem:lambda-age}
Under the conditional D6 closure, the branch quantity \(t_\Lambda\) is the associated de Sitter
timescale. The observed cosmic age \(t_0\) is a downstream FLRW comparison quantity outside the D6
theorem outputs, after one chooses a cosmological model above the local/global D5\(\to\)D6 stack. On
the flat \(\Lambda\)CDM benchmark,
\[
t_0=\frac{2}{3H_0\sqrt{\Omega_\Lambda}}
\sinh^{-1}\!\left(\sqrt{\frac{\Omega_\Lambda}{\Omega_m}}\right).
\]
\end{remark}

\begin{definition}[Clocked FLRW continuation boundary]\label{def:clocked-flrw-boundary}
A clocked FLRW continuation above the D6 gravity branch is a tuple
\[
(g_{ab},\chi,u^a,h_{ab},a(\tau),\kappa,T_{ab},\mathsf{Top})
\]
where \(u_a=-N\nabla_a\chi\), \(u^au_a=-1\), \(h_{ab}=g_{ab}+u_au_b\), the \(u\)-orthogonal
slices are homogeneous and isotropic, and
\[
K(\tau)=\frac{\kappa}{a(\tau)^2},\qquad {}^{(3)}R=6K(\tau),\qquad \kappa\in\{-1,0,+1\}.
\]
The topology policy \(\mathsf{Top}\) records whether globally inequivalent flat quotients such as
\(\mathbb R^3\) and \(T^3\) are distinguished or identified. The observer-facing \(H^3\) record
atlas used elsewhere is a Lorentz/rest-space chart; it is not by itself an FLRW curvature
measurement.
\end{definition}

\begin{lemma}[FLRW curvature as visible scalar holonomy]\label{lem:flrw-curvature-holonomy}
On a clocked homogeneous-isotropic spatial slice of Definition~\ref{def:clocked-flrw-boundary},
let \(\nabla^{(3)}\) be the spatial Levi--Civita connection. The small-loop holonomy in the
\(u\)-\(v\) plane satisfies
\[
\operatorname{Hol}_{\partial\Box_{uv}}(\nabla^{(3)})
=
\exp\!\left(KA_\Box J_{uv}+O(A_\Box^{3/2})\right),
\]
where \(A_\Box\) is the loop area and \(J_{uv}\) is the infinitesimal rotation generator in that
two-plane. On a visibly separated OPH refinement system, the refinement-limit scalar spatial
holonomy vanishes if and only if \(K=0\). Thus the flat FLRW branch is the zero-visible spatial
holonomy branch.
\end{lemma}

\begin{proof}
The displayed formula is the standard infinitesimal holonomy expansion for a connection with
constant sectional curvature. If \(K=0\), every area-normalized small-loop curvature readout
vanishes. Conversely, if \(K\ne0\), the area-normalized holonomy converges to \(KJ_{uv}\) in each
visible two-plane. Visible separation forbids quotienting this nonzero family away as a mere gauge
representative difference. Homogeneity and isotropy leave no independent scalar spatial-curvature
obstruction beyond \(K\), so vanishing refinement-limit scalar holonomy forces \(K=0\).
\end{proof}

\begin{remark}[Flatness is not a D6 output]\label{rem:flrw-holonomy-boundary}
Lemma~\ref{lem:flrw-curvature-holonomy} only names the OPH meaning of an FLRW flat branch. A
selection statement needs an additional cosmological continuation hypothesis or theorem. Capacity
closure at D6 does not select \(\kappa=0\): de Sitter admits \(\kappa=0,+1,-1\) FLRW presentations
with the same local expansion relation \(H^2+\kappa/a^2\). Curvature damping likewise gives only
\(\dot K=-2HK\) and hence bounds \(|K|\) or \(|\Omega_K|\) along a fixed sector; it does not change
\(\kappa\). The allowed branch labels are
\(\textsc{DirectTheorem}\), \(\textsc{ConditionalCMH}\), \(\textsc{ExplicitAssumption}\), and
\(\textsc{OpenTheorem}\), with \(\textsc{OpenTheorem}\) as the default.
\end{remark}

\begin{theorem}[Conditional cosmological minimal holonomy]\label{thm:conditional-cmh}
Fix a clocked cosmological boundary datum \(B_{\cos,r}\) containing the clock, congruence, source
and stress packets, screen checkpoints, orientation data, and topology policy, but not \(\kappa\)
when flatness is to be derived. Let \(\widetilde C^{\rm FLRW}_{b,r}\) be the raw FLRW fiber over
that boundary. Suppose a refinement-natural functional \(J_{\rm curv}\) on the physical quotient
measures only quotient-visible spatial Levi--Civita curvature obstruction and satisfies
\(J_{\rm curv}=0\) exactly on \(\kappa=0\). If a flat extension exists and the zero set is a single
physical class after the topology policy, then the selected fiber
\[
C^{\rm sel}_{b,r}
=
\operatorname*{argmin}_{C\in\widetilde C^{\rm FLRW}_{b,r}}J_{\rm curv}(C)
\]
has \(\kappa=0\), uniquely modulo that topology policy.
\end{theorem}

\begin{proof}
The hypotheses put every candidate in one clocked boundary fiber, so \(J_{\rm curv}\) compares
extensions without changing source, stress, clock, or screen data. Since a flat extension exists,
the infimum of \(J_{\rm curv}\) is zero. The equivalence \(J_{\rm curv}=0\iff\kappa=0\) forces every
minimizer into the flat sector, and the topology policy turns the zero set into one physical class.
\end{proof}

\begin{theorem}[Conditional cosmological-constant / screen-capacity closure stack]\label{thm:lambda-stack}
Assume the hypotheses of Theorem~\ref{cor:einstein}, the cosmic record-capacity fixed point
\[
N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}}),
\]
its conditional de Sitter entropy identification
\[
N_{\mathrm{CRC}}=S_{\mathrm{dS}},
\]
\noindent the standard de Sitter entropy relation
\[
S_{\mathrm{dS}}=\frac{A_{\mathrm{dS}}}{4G}=\frac{3\pi}{G\Lambda},
\]
the selected scale certificate \(G_{\mathrm{geom}}=\ell_\star^2\),
and the standard de Sitter static-patch formulas
\[
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c}.
\]
Then:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2em]
\item the local null-modular data determine the Einstein branch only modulo a metric term \(\Lambda g_{ab}\);
\item the same branch closes globally as
\[
G_{ab}+\frac{3\pi}{G N_{\mathrm{CRC}}}\,g_{ab}=8\pi G\,\langle T_{ab}\rangle;
\]
\item the assumed D6 closure, together with the selected scale certificate, gives the static-patch display
\[
S_{\mathrm{dS}}=N_{\mathrm{CRC}},
\qquad
A_{\mathrm{dS}}=4G N_{\mathrm{CRC}},
\qquad
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c};
\]
\item the observed cosmic age \(t_0\) is not an additional theorem output of this stack and is a downstream FLRW benchmark.
\end{enumerate}
Under the stated hypotheses, the cosmological-constant package forms one local/global theorem stack:
the local null-modular branch leaves exactly the null-invisible metric freedom, the assumed cosmic
record-capacity fixed point closes that same Einstein branch globally, and the SI static-patch
display uses the selected scale certificate.
\end{theorem}

\begin{proof}
Item \textup{(i)} is Proposition~\ref{prop:lambda}, whose local ambiguity statement rests on the null-data blindness isolated by Lemma~\ref{lem:vac} together with the D5 Einstein branch. Item \textup{(ii)} is Corollary~\ref{cor:lambda-global}. Item \textup{(iii)} is Corollary~\ref{cor:lambda-parameters}. Item \textup{(iv)} is Remark~\ref{rem:lambda-age}.
\end{proof}

Theorem~\ref{thm:lambda-stack} packages the conditional local/global D5\(\to\)D6 handoff. Its D6
hypotheses are the local Einstein branch, a cosmic record-capacity fixed point
\(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})\), the identification
\(N_{\mathrm{CRC}}=S_{\mathrm{dS}}\), the standard de Sitter entropy relation, the selected scale
certificate, and the standard static-patch radius/time formulas. These hypotheses are external to
the local null-modular reconstruction. A constructed \(F\), its fixed-point certificate, and
premises CP-1--CP-3 are open. If supplied, the readback closure would fix the capacity and the
selected scale certificate would supply the SI display. This separation reorganizes the
vacuum-energy problem without completing its global closure.

\begin{remark}[Uniqueness lemmas L2 and L3 for the capacity coordinate]\label{rem:l2-l3-capacity}
The project consistency stack records the uniqueness schema attached to this D6 target. Lemma L2:
if the readback map \(F\) is constructed with a certified contraction interval, meaning an
interval-arithmetic evaluation that certifies a self-map with a derivative bound below one, the
Banach fixed-point theorem gives existence and uniqueness of \(N_{\mathrm{CRC}}\) on that interval.
The existing exclusions of several declared-structure candidates, whose fixed points lie between
1 and \(10^{3}\) nats, do not construct the required map. Lemma L3 is correspondingly conditional:
under L1 for the pixel coordinate \(P\) together with a discharged L2, the SLH principle set admits
at most one pair \((P,N)\). The label G2-GAP-1 denotes the further conditional identification of a
readback fixed point with the electroweak bridge capacity. It assumes CP-1, the balance condition
\(\Pi_{\mathrm{EW}}=\beta_{\mathrm{EW}}P\); CP-2, the port-load inversion form; and CP-3, the
averaging carrier. Those premises yield the G2 bridge-coordinate enclosure
\(N_{\mathrm{EW}}^{\mathrm{G2}}=3.5321315434\times10^{122}\) at relative width
\(1.6\times10^{-25}\). They supply no constructed readback map and no unconditional D6 fixed-point
enclosure.
\end{remark}

\section{Gauge Reconstruction and Standard Model Structure}

\subsection{Compact gauge reconstruction}

At any fixed UV cutoff, edge-center completion equips collars with finitely many sector labels, boundary charge carriers, and finite-dimensional intertwiner spaces. These are fixed-cutoff collar data, not refinement-limit assumptions. The local MaxEnt / collar-mixing package established earlier controls only fixed-cutoff recoverability, modular-support localization, and carried error terms on the realized branch. It is logically separate from whether transportable edge sectors survive refinement, and it supplies no theorem that the refinement-limit sector category is trivial or nontrivial.

On the ordinary or central-defect branch, path-independent movement of collar charges is supplied by the overlap-gluing theorem. Theorem~\ref{thm:transport-from-gluing} constructs transport from paths in the overlap recharting groupoid and proves the exact combined criterion: on the ordinary branch the represented loop holonomy must be trivial; on the central branch \([z]_\Sigma=0\) must first strictify the triangle defect and at least one allowed strictification must have trivial sector holonomy. On the genuinely noncentral branch, \(o^{(2)}_\Sigma=0\) must first strictify the higher associator, after which at least one allowed strict \(G_\Sigma\)-valued representative must have trivial represented holonomy. A nonzero \(o^{(2)}_\Sigma\) remains a higher-gauge sector, while an orbit for which every strict representative has residual loop holonomy is not an ordinary path-independent DR sector. The full orbit \(q_\Sigma\) need not determine a unique ordinary \(H^1\) class and is not itself the strictification test.

For the ordinary or central-defect bosonic zero-obstruction branch, the fixed-cutoff categories
\(\mathsf{Sect}^{\mathrm{bos}}_r\) and their forgetful fibers are theorem-produced. The
refinement/fiber ladder is constructed below only on a cofinal tail carrying the explicit
compact-gauge refinement receipt of Definition~\ref{def:compact-gauge-refinement-receipt}. On
such a tail, the resulting directed colimit
\[
\mathsf{Sect}_\infty := \varinjlim_r \mathsf{Sect}^{\mathrm{bos}}_r
\]
is the category on which Doplicher--Roberts / Tannaka reconstruction is applied. Without that
receipt this colimit is a conditional object, not an output of the finite-state refinement maps.
The theorem below is neutral about whether \(\mathsf{Sect}_\infty\) is trivial or nontrivial: if
only the tensor unit persists, the reconstructed compact group is the trivial group.
In the terminology of the project consistency stack, this reconstruction is the carrier of stack
row C4 (transportable-charge consistency): under the declared compact-gauge refinement receipt
and the stated clause inputs, coherent transport of internal labels across overlaps is the
requirement that removes the gauge menu.

\subsubsection{Classification is not realization}

\begin{proposition}[Obstruction neutrality of the Standard Model selection step]\label{prop:obstruction-neutrality}
The ordinary trivial-holonomy condition, the combined central condition
\([z]_\Sigma=0\) plus a trivial-holonomy strictification, and the combined noncentral condition
\(o^{(2)}_\Sigma=0\) plus an allowed strict representative with trivial represented
\(G_\Sigma\)-holonomy are transportability
conditions. After one common stagewise strict representative is chosen, they permit an
ordinary transportable bosonic sector category generated only by sectors trivial under that
choice; they do not select
\[
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6}.
\]
On a zero-obstruction branch carrying the compact-gauge refinement receipt, DR/Tannaka
reconstruction returns
\[
G=\mathrm{Aut}_\otimes(\mathcal F)
\]
for the constructed sector category and fiber functor. If the category is trivial, \(G\) is
trivial; in general \(G\) is whatever compact group that tensor-fiber data reconstructs. The
Standard Model quotient enters only after Axiom~\ref{ax:mar} is applied to a nonempty realized
one-Higgs chiral sector package.
\end{proposition}

\begin{proof}
Theorem~\ref{thm:transport-from-gluing} identifies associator strictifiability together with
vanishing residual represented loop holonomy with strict path-independent transport, and with no
more structure than that. Theorems
\ref{thm:fixed-cutoff-bosonic-sector-category}, \ref{thm:refinement-functor-fiber-descent}, and
\ref{thm:sector-colimit} use that transport condition together with the explicit refinement
receipt to build the ordinary bosonic refinement-limit sector category and its finite-dimensional
fiber functor. Theorem~\ref{thm:compactgauge} then
reconstructs \(G\) from \((\mathsf{Sect}_\infty,\mathcal F)\). None of those steps names a weak
doublet, color triplet, Higgs doublet, hypercharge lattice, generation count, or finite
\(\mathbb Z_6\) kernel. Those data are supplied by the MAR-realized branch through
Theorem~\ref{thm:realized-sm-branch}.
\end{proof}

\begin{definition}[Compact-gauge refinement receipt]\label{def:compact-gauge-refinement-receipt}
Let \(R_0\) be a cofinal tail of the separated refinement set. A compact-gauge refinement receipt
on \(R_0\) consists of the following data and checks for every \(r\preceq s\) in \(R_0\).
\begin{enumerate}
\item \emph{Finite extendability.} The finite-state restriction
\(\rho_{sr}:Q_s\to Q_r\) is supplied with a surjectivity certificate and the restrictions compose.
Thus every coarse record has at least one fine extension, and only on this certified branch does
commutative pullback give an injective unital map
\[
\rho_{sr}^*:C(Q_r)\hookrightarrow C(Q_s),\qquad
\rho_{sr}^*f=f\circ\rho_{sr}.
\]
\item \emph{Noncommutative collar embeddings.} For each retained collar and its refinement, write
\[
\mathcal A_{\mathrm{EC},r}(B)=\bigoplus_{\alpha\in A_r}M_{d_{\alpha,r}}(\mathbb C),
\qquad
\mathcal A_{\mathrm{EC},s}(B_s)=\bigoplus_{\beta\in A_s}M_{d_{\beta,s}}(\mathbb C).
\]
The receipt supplies nonnegative multiplicities \(m_{\beta\alpha}^{rs}\) and unitaries
\[
V_\beta^{rs}:\bigoplus_{\alpha\in A_r}
  \bigl(\mathbb C^{d_{\alpha,r}}\otimes\mathbb C^{m_{\beta\alpha}^{rs}}\bigr)
  \xrightarrow{\ \simeq\ }\mathbb C^{d_{\beta,s}},
\qquad
d_{\beta,s}=\sum_\alpha m_{\beta\alpha}^{rs}d_{\alpha,r},
\]
and defines, rather than infers,
\[
\bigl(\jmath_{rs}^{B}(a)\bigr)_\beta
=V_\beta^{rs}
 \left[\bigoplus_\alpha\bigl(a_\alpha\otimes
 \mathbf 1_{m_{\beta\alpha}^{rs}}\bigr)\right]
 (V_\beta^{rs})^*.
\]
Every coarse \(\alpha\) must occur for some \(\beta\), which is exactly the injectivity check.
For the center-tracking branch used below, every \(\beta\) has a unique coarse shadow
\(\operatorname{sh}_{sr}(\beta)\), meaning
\(m_{\beta\alpha}^{rs}>0\) for exactly one \(\alpha\). Then and only then for this block form does
\(\jmath_{rs}^{B}\) carry the whole coarse center into the fine center, and
\[
\jmath_{rs}^{B}(P_{\alpha,r})
=\sum_{\beta:\operatorname{sh}_{sr}(\beta)=\alpha}P_{\beta,s}.
\]
For \(r\preceq s\preceq t\), the receipt verifies
\[
m_{\gamma\alpha}^{rt}=\sum_\beta
m_{\gamma\beta}^{st}m_{\beta\alpha}^{rs}
\]
and coherence of the \(V\)'s, equivalently
\(\jmath_{rt}^{B}=\jmath_{st}^{B_s}\circ\jmath_{rs}^{B}\) after the declared collar
identifications.
\item \emph{Charge refinement.} The receipt supplies continuous surjective homomorphisms
\[
\pi_{sr}^{\Sigma}:\widehat K_{\Sigma,s}\twoheadrightarrow\widehat K_{\Sigma,r},
\qquad
\pi_{rr}^{\Sigma}=\mathrm{id},qquad
\pi_{tr}^{\Sigma}=\pi_{sr}^{\Sigma}\circ\pi_{ts}^{\Sigma},
\]
together with one common stagewise strict representative \(U^{\mathrm{str}}_r\) at every
\(r\in R_0\). The maps intertwine overlap transport and these common choices, including the
chosen central or crossed-module strictification where applicable and the represented action of
every closed overlap loop; the representative is not changed object by object. In particular,
closed fine loops with trivial coarse shadow must act trivially rather than create new residual
holonomy. For every visible seed carrier
\(W_{\alpha,r}\), its pullback \((\pi_{sr}^{\Sigma})^*W_{\alpha,r}\) lies in
\(\mathsf{Sect}^{\mathrm{bos}}_s\), and its chosen refined collar realization has support
\(\jmath_{rs}^{B}(P_{\alpha,r})\). Fine central blocks under that support are realization blocks
of the same pulled-back charge; they do not define a categorical direct sum with a larger carrier.
\item \emph{Finite tensor realization.} Every finite tensor word in visible seeds and conjugates,
and every invariant subobject projection in its intertwiner algebra, has a compatible finite
concatenated-collar realization. These realizations respect tensor product, duals, subobjects,
overlap transport, and the preceding refinement maps. This is a family of finite realizations,
one for each finite word; it does not place an infinite simple skeleton inside one finite collar
algebra.
\end{enumerate}
The finite-set restrictions of Theorem~\ref{thm:consensusrefinement} do not by themselves provide
the matrix multiplicities, center condition, compact-group surjections, or tensor realizations in
this receipt.
\end{definition}

\begin{theorem}[RefinementFunctorAndFiberDescent]\label{thm:refinement-functor-fiber-descent}
Let \(R\) be the separated cofinal OPH refinement system used by
Theorem~\ref{thm:consensusrefinement}, and suppose a cofinal tail \(R_0\subset R\) carries a
compact-gauge refinement receipt in the sense of
Definition~\ref{def:compact-gauge-refinement-receipt}. For each \(r\in R_0\), let
\(\mathsf{Sect}^{\mathrm{bos}}_r\) be the fixed-cutoff zero-obstruction bosonic collar-sector
category constructed in Theorem~\ref{thm:fixed-cutoff-bosonic-sector-category}, with strict
transport supplied by Theorem~\ref{thm:transport-from-gluing}. Then for every
\(r\preceq s\) in \(R_0\), pullback along \(\pi_{sr}^{\Sigma}\) defines a fully faithful symmetric
strong monoidal \(^*\)-functor
\[
U_{rs}:\mathsf{Sect}^{\mathrm{bos}}_r\longrightarrow \mathsf{Sect}^{\mathrm{bos}}_s
\]
carrying \(\mathbf 1_r\) to \(\mathbf 1_s\), preserving irreducibles and zero-obstruction
transportable sector classes, and satisfying coherent composition identifications
\[
U_{st}\circ U_{rs}=U_{rt}
\qquad (r\preceq s\preceq t).
\]
The canonical fixed-cutoff forgetful functors
\[
F_r:\mathsf{Sect}^{\mathrm{bos}}_r\longrightarrow \mathsf{Hilb}_{\mathrm{fd}}
\]
are objectwise finite-dimensional and obey
\[
F_s\circ U_{rs}=F_r
\]
with identity monoidal comparisons satisfying the refinement-composition coherence equation.
\end{theorem}

\begin{proof}
Fix \(r\preceq s\) in the certified tail. For a representation
\(X=(H_X,\varrho_X)\), define
\[
U_{rs}X
:=(\pi_{sr}^{\Sigma})^*X
=\bigl(H_X,\varrho_X\circ\pi_{sr}^{\Sigma}\bigr),
\qquad
U_{rs}(f):=f.
\]
The generator-landing and finite-tensor clauses of the receipt put this pullback in
\(\mathsf{Sect}^{\mathrm{bos}}_s\). Since \(\pi_{sr}^{\Sigma}\) is surjective, a linear map
between two pulled-back carriers intertwines the fine actions exactly when it intertwines the
coarse actions. Hence
\[
\operatorname{Hom}_{\widehat K_{\Sigma,s}}(U_{rs}X,U_{rs}Y)
=
\operatorname{Hom}_{\widehat K_{\Sigma,r}}(X,Y).
\]
Thus \(U_{rs}\) is fully faithful, \(^*\)-preserving, and preserves irreducibility; in particular,
a coarse simple does not split into several fine simples on the certified branch.

Pullback preserves the trivial representation, tensor products, conjugates, evaluation and
coevaluation, and the canonical bosonic flip. With the standard underlying-Hilbert-space
identifications these are symmetric strong monoidal identities. Exact composition of the
\(\pi\)'s gives \(U_{st}U_{rs}=U_{rt}\) on objects and morphisms. Compatibility of the \(\pi\)'s
with overlap transport and obstruction data, required by the receipt, carries the common
\(U^{\mathrm{str}}_r\) to the common \(U^{\mathrm{str}}_s\): the central or crossed-module defect
remains strictified and every represented fine-loop action remains trivial, including loops with
trivial coarse shadow. No sector-specific change of strict representative is used.
Thus zero obstruction persists. The separately supplied \(\jmath_{rs}^{B}\) records
where a seed is realized in the refined collar algebra; its central summands are not used to alter
the carrier or to define \(U_{rs}\).

Define \(F_r(H_X,\varrho_X)=H_X\) and \(F_r(f)=f\). This is the ordinary faithful symmetric
strong monoidal forgetful functor, so every fiber is finite-dimensional objectwise even when the
category has infinitely many simple classes. Pullback changes only the group action. Therefore
\[
F_sU_{rs}X=H_X=F_rX,
\qquad
F_sU_{rs}(f)=f=F_r(f).
\]
The comparison \(\theta_{rs,X}\) is the identity on \(H_X\). Naturality and monoidality are
identity diagrams, and
\(\theta_{rt}=\theta_{rs}\circ(\theta_{st}U_{rs})\) is literal equality.

Finally, the algebra portion of the receipt is not deduced from the finite-state map. Surjectivity
of \(\rho_{sr}\) proves only the injectivity of the commutative pullback \(\rho_{sr}^*\). The
displayed multiplicity formula directly verifies that \(\jmath_{rs}^{B}\) is a unital
\(^*\)-homomorphism; occurrence of every coarse block proves injectivity, the unique-shadow
condition proves the stated center formula, and multiplicity/coherent-unitary composition proves
functorial composition. This discharges the noncommutative refinement obligation independently of
the representation pullback construction.
\end{proof}

\begin{remark}[The \(\U(1)\) charge-one refinement test]\label{rem:u1-charge-refinement-test}
Let \(\widehat K_{\Sigma,r}=\U(1)\) and suppose the fixed collar sees the charge-one carrier
\(W_1(z)=z\), retained as a seed by the common stagewise representative
\(U^{\mathrm{str}}_r\). The category of Definition~\ref{def:fixed-cutoff-collar-sectors} contains
\[
W_n=W_1^{\otimes n}\quad(n\geq 0),
\qquad
W_{-n}=(W_1^*)^{\otimes n}\quad(n>0),
\]
so it has the infinite simple family indexed by \(\mathbb Z\). In particular charge two exists as
\(W_2=W_1\otimes W_1\). Its subobject idempotent, equivalently the unique nonzero central
projection in its intertwiner algebra, is
\[
\mathbf 1_{W_2}\in
\operatorname{End}_{\U(1)}(W_1^{\otimes2})\cong\mathbb C;
\]
in a certified physical realization this is the corresponding idempotent in the two-collar
concatenated algebra. It is not asserted to be a projector in the original one-collar finite
algebra \(\mathcal A_{\mathrm{EC},r}(B)\). Under the next certified refinement,
\[
U_{rs}(W_2)=(\pi_{sr}^{\Sigma})^*W_2
=\bigl((\pi_{sr}^{\Sigma})^*W_1\bigr)^{\otimes2}
\]
remains simple by surjectivity, its projector pulls back to the identity, and
\(F_s(U_{rs}W_2)=\mathbb C=F_r(W_2)\) with comparison map
\(\mathrm{id}_{\mathbb C}\). Thus tensor closure is explicit and does not hide an infinite center
inside one finite algebra. A finite fusion or charge-truncated alternative would require a
different stated category and an explicit associative fusion quotient; it is not used here.
\end{remark}

\begin{remark}[Conditionality of the refinement limit]\label{rem:refinement-receipt-conditionality}
Without Definition~\ref{def:compact-gauge-refinement-receipt}, the stagewise tensor-generated
categories and their forgetful functors exist, but the functors \(U_{rs}\), their compatible
fibers, the directed colimit, and \(\operatorname{Aut}_\otimes(\mathcal F)\) are not outputs of the
finite-state consensus refinement maps. All refinement-limit gauge statements below are therefore
conditional on a cofinal tail carrying that receipt.
\end{remark}

\begin{theorem}[Construction of the refinement-stable bosonic sector category]\label{thm:sector-colimit}
Assume Axioms~\ref{ax:screen}--\ref{ax:entropy}. On the ordinary or central-defect bosonic
zero-obstruction branch, suppose a cofinal tail \(R_0\) carries the compact-gauge refinement
receipt of Definition~\ref{def:compact-gauge-refinement-receipt}. Let the fixed-cutoff sector categories
\(\mathsf{Sect}^{\mathrm{bos}}_r\) be those constructed in
Theorem~\ref{thm:fixed-cutoff-bosonic-sector-category}, and let the refinement functors and
stagewise finite-dimensional bosonic fibers be those constructed in
Theorem~\ref{thm:refinement-functor-fiber-descent}. Then the directed colimit
\[
\mathsf{Sect}_\infty:=\varinjlim_{r\in R_0} \mathsf{Sect}^{\mathrm{bos}}_r
\]
inherits a well-defined semisimple rigid symmetric \(C^*\)-tensor structure. Its tensor unit is
the persistent vacuum sector, its tensor product is induced from collar concatenation, its duals
are induced from orientation reversal / charge conjugation, and its braiding is the induced
bosonic spacelike-exchange symmetry of the \(3+1\)-dimensional branch. The finite-dimensional
stagewise fibers descend to a faithful bosonic fiber functor
\[
\mathcal F:\mathsf{Sect}_\infty\to\mathsf{Hilb}_{\mathrm{fd}}.
\]
The theorem is neutral about nontriviality: if only the tensor unit persists, then
\(\mathsf{Sect}_\infty\) is the trivial bosonic tensor category.
\end{theorem}

\begin{proof}
The fixed-cutoff categorical structure is supplied by
Theorem~\ref{thm:fixed-cutoff-bosonic-sector-category}. The fully faithful symmetric monoidal
\(^*\)-refinement functors, their composition coherence, their preservation of zero-obstruction
transportable sector classes on the certified cofinal tail, and the compatible finite-dimensional
forgetful fibers are constructed from the receipt in
Theorem~\ref{thm:refinement-functor-fiber-descent}.

The directed colimit category has objects represented by refinement tails that agree from some stage onward
and morphisms represented by eventual intertwiner classes. Faithfulness of the \(U_{rs}\) makes
the morphism equivalence relation separated: a nonzero finite-stage intertwiner cannot become
zero on a cofinal tail. The tensor unit on each fixed-cutoff category is carried to the tensor
unit by every \(U_{rs}\), so the vacuum tail defines \(\mathbf 1_\infty\).

For objects represented by tails \(X_r\) and \(Y_r\), define
\[
[X]\otimes [Y]:=[X_r\otimes_r Y_r]
\]
at any sufficiently fine common stage. This is independent of the chosen stage because the
monoidal structure maps of \(U_{rs}\) identify
\[
U_{rs}(X_r\otimes_r Y_r)
\cong
U_{rs}(X_r)\otimes_s U_{rs}(Y_r).
\]
The same argument descends the associators, unitors, duality evaluation and coevaluation maps,
and the bosonic symmetry. Since each fixed-cutoff category is rigid, symmetric, semisimple, and
\(C^*\), and since the refinement functors preserve \(^*\), direct sums, and subobjects, the
colimit inherits the same structure on persistent tails.

For the fiber functor, choose a representative \(X_r\) of a colimit object \([X]\) and define
\[
\mathcal F([X]):=F_r(X_r)
\]
using the literal carrier identifications
\[
F_s(U_{rs}X_r)=F_r(X_r)
\]
from Theorem~\ref{thm:refinement-functor-fiber-descent}. The composition compatibility of those
identities makes this independent of representative. On morphisms, \(\mathcal F\) is induced
by the eventual action of the corresponding finite-stage \(F_r\). Objectwise finite
dimensionality, monoidality, and faithfulness descend from the stagewise \(F_r\)'s. Thus
\(\mathcal F:\mathsf{Sect}_\infty\to\mathsf{Hilb}_{\mathrm{fd}}\) is a faithful bosonic fiber
functor.
\end{proof}

\begin{theorem}[Compact gauge reconstruction in the bosonic branch]\label{thm:compactgauge}
Assume Axioms~\ref{ax:screen}--\ref{ax:entropy} and work on the ordinary or central-defect
bosonic zero-obstruction branch. Suppose a cofinal tail carries the compact-gauge refinement
receipt of Definition~\ref{def:compact-gauge-refinement-receipt}, and let
\[
\mathcal F:\mathsf{Sect}_\infty\to\mathsf{Hilb}_{\mathrm{fd}}
\]
be the faithful bosonic fiber functor constructed in Theorem~\ref{thm:sector-colimit} from
Theorems~\ref{thm:transport-from-gluing},
\ref{thm:fixed-cutoff-bosonic-sector-category}, and
\ref{thm:refinement-functor-fiber-descent}. Let
\(\mathrm{Aut}_\otimes(\mathcal F)\) denote the group of unitary symmetric
monoidal natural automorphisms of \(\mathcal F\). Then
\[
G:=\mathrm{Aut}_\otimes(\mathcal F)
\]
is a compact group and
\[
\mathsf{Sect}_\infty\simeq \mathrm{Rep}(G)
\]
as a symmetric \(C^*\)-tensor category with fiber functor. In particular \(G\) is uniquely
determined up to isomorphism by the constructed pair \((\mathsf{Sect}_\infty,\mathcal F)\).
\end{theorem}

\begin{proof}
Theorem~\ref{thm:transport-from-gluing} supplies
the strict zero-obstruction transport criterion. Theorem~\ref{thm:fixed-cutoff-bosonic-sector-category}
constructs the fixed-cutoff bosonic symmetric \(C^*\)-tensor categories.
Given the explicit compact-gauge refinement receipt,
Theorem~\ref{thm:refinement-functor-fiber-descent} constructs the fully faithful monoidal
\(^*\)-refinement functors and compatible finite-dimensional forgetful fibers, and
Theorem~\ref{thm:sector-colimit} descends them to \((\mathsf{Sect}_\infty,\mathcal F)\).

Fix a small skeleton of \(\mathsf{Sect}_\infty\). For each object \(X\), a unitary symmetric
monoidal natural automorphism \(\eta\in\mathrm{Aut}_\otimes(\mathcal F)\) has a unitary component
\(\eta_X\in U(\mathcal F(X))\). Hence
\[
\mathrm{Aut}_\otimes(\mathcal F)
\hookrightarrow
\prod_X U(\mathcal F(X)),
\qquad
\eta\mapsto(\eta_X)_X.
\]
Naturality imposes the closed relations
\[
\mathcal F(f)\eta_X=\eta_Y\mathcal F(f)
\qquad(f:X\to Y),
\]
and monoidality imposes the closed relations
\[
\eta_{X\otimes Y}
=
J_{X,Y}(\eta_X\otimes\eta_Y)J_{X,Y}^{-1},
\qquad
\eta_{\mathbf 1}=\mathrm{id}_{\mathbb C}.
\]
Thus \(G=\mathrm{Aut}_\otimes(\mathcal F)\) is a closed subgroup of a product of compact unitary
groups, and is compact.

Doplicher--Roberts / Tannaka reconstruction applies to the rigid symmetric \(C^*\)-tensor
category with faithful finite-dimensional bosonic fiber functor constructed above, giving
\[
\mathsf{Sect}_\infty\simeq\mathrm{Rep}(G).
\]
Uniqueness follows because the reconstructed compact group is the tensor automorphism group of
the fiber functor. If \(\mathsf{Sect}_\infty\) is trivial, then \(G\) is the trivial compact group;
the realized nontrivial branch is supplied by Theorem~\ref{thm:mar-witness-landing}, not hidden as
a hypothesis in this reconstruction theorem.
\end{proof}

Theorem~\ref{thm:compactgauge} is a Tannakian-level statement: it produces the compact group
\(G\) and the equivalence \(\mathsf{Sect}_\infty\simeq\mathrm{Rep}(G)\) from the constructed
category and fiber functor, and nothing more. No observable net \(O\mapsto\mathcal A(O)\),
no realization of the persistent sectors as localized transportable endomorphisms, and no field
algebra \(\mathcal F_{\mathrm{net}}\) with fixed-point identity \(\mathcal A=\mathcal
F_{\mathrm{net}}^{\,G}\) is constructed or claimed in this paper. The Doplicher--Haag--Roberts/DR
field-net level requires the additional net-realization hypotheses (observable net, localized
endomorphisms, unitary transporters, locality/duality, finite statistics with conjugates, and
sector completeness) stated as the DHR/DR realization hypotheses in the synthesis paper; any
field-algebra language on this lane is conditional on that package. Vanishing collar/represented
holonomy is the categorical transport input to that package, not a substitute for net-level DHR
transportability.

If a fermionic sign object is present, the correct reconstruction statement is super-Tannakian
instead of purely Tannakian. This paper does not prove the full fermionic/chiral extension; it
works only in the bosonic internal-gauge branch once the fixed-cutoff sector packages and their
monoidal refinement transport have been constructed from that receipt.

\begin{theorem}[Gauge-sector classification--selection factorization]\label{thm:gauge-selection-factorization}
On the OPH compact-gauge lane, conditional on a cofinal tail carrying the compact-gauge refinement
receipt, the realized Standard Model claim factors as
\[
\begin{aligned}
\text{overlap/gluing data}
&\longrightarrow \text{associator strictification test}
\longrightarrow \text{strict-representative holonomy test}\\
&\longrightarrow \mathsf{Sect}_\infty
\longrightarrow G=\mathrm{Aut}_\otimes(\mathcal F)
\longrightarrow \mathfrak S_{\mathrm{MAR}}.
\end{aligned}
\]
The first arrow computes the central or crossed-module associator defect and strictifies it when
possible. The second computes represented holonomy across the allowed strict representatives. The
third keeps only sectors for which at least one such representative has trivial loop action. The fourth reconstructs the compact
group from the persistent tensor category and fiber functor. These are classification and
reconstruction steps. The final arrow is the realization/selection step: MAR acts on realized
admissible sector packages, not on obstruction classes alone.
\end{theorem}

\begin{proof}
The first three arrows are Theorem~\ref{thm:transport-from-gluing}: nonzero \([z]_\Sigma\) or
nonzero \(o^{(2)}_\Sigma\) blocks strictification, while a strictifiable associator proceeds only if the
orbit contains an allowed strict representative with trivial sector holonomy. The fourth arrow is Theorem~\ref{thm:compactgauge}.
Proposition~\ref{prop:obstruction-neutrality} shows that these arrows are neutral about the Standard
Model quotient. The final arrow is Axiom~\ref{ax:mar}
applied to the nonempty witness class of Theorem~\ref{thm:mar-witness-landing}, with uniqueness
summarized in Theorem~\ref{thm:realized-sm-branch}.
\end{proof}

\subsection{MAR minimality and the Standard Model quotient}

Throughout this subsection, $\chi_{\mathrm{cpl}}$ means the dimension of the minimal coupled carrier supporting the required weak-type and color-type nonabelian charges on a common block. It is not the abstract minimal faithful representation dimension of the final gauge group.

\begin{definition}[Weak-type and color-type nonabelian roles]
A weak-type nonabelian charge is a pseudoreal nonabelian doublet role. A color-type nonabelian charge is an intrinsically complex nonabelian role, meaning that its nonabelian factor itself acts by an irreducible representation not equivalent to its conjugate. Abelian twisting of a pseudoreal nonabelian irreducible representation does not count as a color-type role.
\end{definition}

The derivation of the Standard Model quotient separates into five steps:
\begin{enumerate}[leftmargin=2em]
\item existence of a compact reconstructed group;
\item identification of the minimal nonabelian sector content;
\item identification of the minimal coupled carrier;
\item uniqueness of the connected abelian factor once admitted on that carrier;
\item determination of product gauge structure up to finite quotient, then of the global finite quotient from the realized matter spectrum.
\end{enumerate}

\begin{lemma}[Minimal nonabelian sector content]\label{lem:mincontent}
Any admissible low-energy sector must contain both a weak-type pseudoreal nonabelian charge role and an intrinsically complex color-type nonabelian charge role.
\end{lemma}

\begin{proof}
Light chiral matter requires left-handed multiplets and right-handed singlets to carry inequivalent gauge data. A pseudoreal doublet structure is the minimal way to realize the weak sector without immediately producing vectorlike masses. A genuinely complex nonabelian representation is required to distinguish quarks from antiquarks. A single nonabelian simple factor cannot simultaneously supply both a minimal weak-type role and an intrinsically complex color-type role; abelian twisting does not count toward the color-type requirement.
\end{proof}

\begin{lemma}[Connected 2D pseudoreal image classification]\label{lem:su2class}
Let $H$ be a connected compact group with a faithful irreducible $2$-dimensional pseudoreal unitary representation. Then the connected derived subgroup of its image is conjugate to $\SU(2)$. Equivalently, the nonabelian factor acting in that role is $\SU(2)$ up to finite central quotient.
\end{lemma}

\begin{proof}[Proof sketch]
Irreducibility places the image inside $\U(2)$ with scalar commutant. Its connected derived subgroup is therefore a connected compact subgroup of $\SU(2)$. The connected compact subgroups of $\SU(2)$ are either tori or $\SU(2)$ itself. The representation is nonabelian and pseudoreal, so the torus case is excluded. Hence the derived subgroup is conjugate to $\SU(2)$, with only a finite central kernel left invisible in the representation.
\end{proof}

\begin{lemma}[Connected 3D intrinsically complex image classification]\label{lem:su3class}
Let $H$ be a connected compact group with a faithful irreducible intrinsically complex $3$-dimensional unitary representation. Then the connected derived subgroup of its image is conjugate to $\SU(3)$. Equivalently, the nonabelian factor acting in that role is $\SU(3)$ up to finite central quotient.
\end{lemma}

\begin{proof}[Proof sketch]
Because the representation is irreducible on $\mathbb C^3$, the semisimple part of the Lie algebra of the image acts irreducibly on $\mathbb C^3$. A product of two nontrivial simple factors would force a tensor-product decomposition of dimension at least $4$, so only one simple factor can occur. Among compact simple Lie algebras, the only ones with nontrivial irreducible representations of dimension at most $3$ are $\mathfrak{su}(2)$ and $\mathfrak{su}(3)$. The $3$-dimensional $\mathfrak{su}(2)$ representation is real, not intrinsically complex, whereas the fundamental $\mathfrak{su}(3)$ representation is intrinsically complex. Therefore the connected derived subgroup is conjugate to $\SU(3)$, again up to finite central kernel.
\end{proof}

\begin{lemma}[Minimal coupled carrier under MAR]\label{lem:carrier}
Within the connected positive-dimensional Lie admissible class used by MAR, and under the weak-type / intrinsically complex color-type criteria above, the minimal coupled carrier supporting both roles on a common block has the form
\[
V=\mathbb C^3\otimes \mathbb C^2,
\qquad
\chi_{\mathrm{cpl}}=6.
\]
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:su2class}, the minimal weak-type nonabelian role is the pseudoreal doublet of $\SU(2)$, hence has dimension $2$. By Lemma~\ref{lem:su3class}, the minimal intrinsically complex color-type nonabelian role is the triplet of $\SU(3)$, hence has dimension $3$.

By definition of $\chi_{\mathrm{cpl}}$, the weak-type and color-type roles must act nontrivially on one common irreducible nonabelian block. Disconnected direct-sum summands do not qualify. Commuting irreducible actions on such a common block therefore require dimension at least the product of the minimal weak and color dimensions:
\[
\chi_{\mathrm{cpl}}\ge 2\cdot 3=6.
\]
Equality is achieved by the tensor-product carrier $\mathbb C^3\otimes\mathbb C^2$. The block-diagonal representation $\mathbb C^3\oplus \mathbb C^2$ of $S(U(3)\times U(2))$ is faithful of dimension $5$, but it is not coupled and hence is not the MAR minimizer. The explicit color-type criterion excludes connected non-semisimple counterexamples of $U(2)$ type.
\end{proof}

\begin{remark}\label{rem:connectedlie}
The dimension comparisons used in Lemma~\ref{lem:carrier} apply to the positive-dimensional connected Lie image carrying the admissible nonabelian charges, equivalently to the identity component of the reconstructed group on that sector. Finite, disconnected, or connected non-semisimple counterexamples exist. They are outside the admissible class fixed by the explicit weak-type / color-type criteria.
\end{remark}

MAR supplies existence of a connected abelian factor; the next lemma proves only uniqueness and identification on the minimal coupled carrier.

\begin{lemma}[Uniqueness of the connected abelian factor on the minimal coupled carrier]\label{lem:commutant}
Inside $\U(6)$, the commutant of $\SU(3)\times\SU(2)$ acting on $\mathbb C^3\otimes \mathbb C^2$ is exactly $\U(1)$.
\end{lemma}

\begin{proof}
The $\SU(3)$ action is irreducible on the first tensor factor and trivial on the second. The $\SU(2)$ action is irreducible on the second tensor factor and trivial on the first. By Schur's lemma, any operator commuting with both actions is scalar on each irreducible factor. Hence the full commutant is a single $\U(1)$.
\end{proof}

\begin{theorem}[Product Gauge Structure up to Finite Quotient]\label{thm:sm}
Assume Axiom~\ref{ax:mar}, the hypotheses of Theorem~\ref{thm:compactgauge} on the ordinary or central-defect realized low-energy branch, the weak-type / color-type MAR inputs above, and that the realized connected gauge image acts faithfully on the minimal coupled carrier. Then the realized connected gauge structure has the form
\[
G_{\mathrm{phys}}=
\frac{\SU(3)\times\SU(2)\times\U(1)}{\Gamma}
\]
for some finite central subgroup $\Gamma$.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:compactgauge} yields some compact group $G$. Lemma~\ref{lem:mincontent} identifies the minimal admissible sector content, Lemmas~\ref{lem:su2class} and \ref{lem:su3class} identify the connected nonabelian factors realizing the minimal weak-type and color-type roles, and Lemma~\ref{lem:carrier} fixes the minimal coupled carrier. The tensor-product structure of that carrier implies commuting weak and color actions, so the connected semisimple part of the realized image is locally $\SU(3)\times\SU(2)$. Axiom~\ref{ax:mar} supplies the existence of one connected abelian charge factor acting nontrivially on the coupled carrier, and Lemma~\ref{lem:commutant} shows that any such connected abelian factor is necessarily a single $\U(1)$. A compact connected Lie group with Lie algebra $\mathfrak{su}(3)\oplus\mathfrak{su}(2)\oplus\mathfrak{u}(1)$ is a quotient of $\SU(3)\times\SU(2)\times\U(1)$ by a finite central subgroup. Faithfulness rules out an invisible extra torus, so the only ambiguity is the finite central quotient $\Gamma$.
\end{proof}

\begin{theorem}[Hypercharge lattice on the realized matter package]\label{thm:hypercharge}
Assume gauge group $\SU(N_c)\times\SU(2)\times\U(1)_Y$, one generation of chiral matter $(Q,u^c,d^c,L,e^c)$, one Higgs doublet $H$, and Yukawa terms
\[
QHu^c,\qquad QH^\dagger d^c,\qquad LH^\dagger e^c.
\]
Then anomaly cancellation and Yukawa invariance determine the hypercharge ratios up to an overall \(\U(1)_Y\) normalization:
\[
Y_L=-N_cY_Q,\quad
Y_H=N_cY_Q,\quad
Y_u=-(N_c+1)Y_Q,\quad
Y_d=(N_c-1)Y_Q,\quad
Y_e=2N_cY_Q.
\]
Fixing the normalization by $Q=T_3+Y$ and $Q(\nu_L)=0$ gives
\[
Y_Q=\frac{1}{2N_c}.
\]
For $N_c=3$ one recovers the exact Standard Model lattice
\[
Y_Q=\frac16,\quad
Y_L=-\frac12,\quad
Y_u=-\frac23,\quad
Y_d=\frac13,\quad
Y_e=1,\quad
Y_H=\frac12.
\]
\end{theorem}

\begin{proof}
Yukawa invariance gives
\[
Y_u=-(Y_Q+Y_H),\qquad
Y_d=-Y_Q+Y_H,\qquad
Y_e=-Y_L+Y_H.
\]
The mixed anomalies yield
\[
N_cY_Q+Y_L=0,
\]
and
\[
2N_cY_Q+N_cY_u+N_cY_d+2Y_L+Y_e=0.
\]
Solving the first anomaly gives
\[
Y_L=-N_cY_Q.
\]
Substituting the Yukawa relations and $Y_L=-N_cY_Q$ into the mixed gravitational anomaly then yields
\[
Y_H=N_cY_Q,\qquad
Y_u=-(N_c+1)Y_Q,\qquad
Y_d=(N_c-1)Y_Q,\qquad
Y_e=2N_cY_Q.
\]
With these relations in place, the $\SU(N_c)^2\U(1)$ and $\U(1)^3$ anomalies cancel identically. The normalization of $Y_Q$ is fixed by the electric charge operator $Q=T_3+Y$ together with $Q(\nu_L)=0$, which implies
\[
Y_L=-\frac12=-N_cY_Q,
\qquad\text{hence}\qquad
Y_Q=\frac{1}{2N_c}.
\]
\end{proof}

\begin{proposition}[Borel--Weil carrier for the one-Higgs branch]\label{prop:bw-higgs-carrier}
On the realized one-Higgs electroweak branch, suppose the support-visible weak chart is locally
\[
C_{\rm EW}\cong\mathbb{CP}^1
\]
with the \(\SU(2)_L\) action and Hopf-fiber \(\U(1)\) weight normalized by the OPH hypercharge lattice. If the scalar carrier is required to be minimal, holomorphic, nontrivial, one-Higgs, and Yukawa-completable, then the canonical local carrier is
\[
H_{\rm OPH}=H^0(C_{\rm EW},\mathcal O(1))\cong\mathbb C^2.
\]
With the OPH convention fixed by \(Q(\phi^0)=T_3(\phi^0)+Y(\phi^0)=0\) on the lower component, this carrier has \(Y(H_{\rm OPH})=+1/2\). Projectivization and symmetry breaking are distinct. For
\[
\phi_0=\frac{v}{\sqrt2}\binom{0}{1},\qquad v\ne0,
\]
the projective ray has stabilizer
\[
\operatorname{Stab}([\phi_0])
\cong \U(1)_{T_3}\times\U(1)_Y
\]
on the lifted electroweak product, whereas the nonzero vacuum vector has stabilizer
\[
\operatorname{Stab}(\phi_0)=\U(1)_Q,
\qquad Q=T_3+Y.
\]
Both statements are understood modulo the finite central identifications fixed by the physical gauge quotient. Thus \(\mathbb P(H_{\rm OPH})\cong\mathbb{CP}^1\) classifies carrier rays but cannot by itself identify the unbroken electromagnetic diagonal, because it forgets the scalar hypercharge phase.
\end{proposition}

\begin{proof}
Borel--Weil gives \(H^0(\mathbb{CP}^1,\mathcal O(n))\cong{\rm Sym}^n(\mathbb C^2)^*\) for \(n\ge0\), up to the dual convention. The \(n=0\) section space is a singlet and cannot be the weak Higgs doublet. The first nontrivial holomorphic section carrier is \(n=1\), giving the two-complex-dimensional fundamental \(\SU(2)\) representation. Sections are scalar \(0\)-form fields valued in the internal line bundle, so the Lorentz spin-zero statement follows after the OPH Lorentz branch separates this internal weak chart from the external tangent representation. The Hopf weight fixes the abelian charge up to sign and normalization; Theorem~\ref{thm:hypercharge}, the \(\mathbb Z_6\) quotient convention, and \(Q(\phi^0)=0\) select \(Y=+1/2\).

It remains to distinguish the two stabilizers. Use the paper's integer normalization \(q=6Y\), so the Higgs has \(q_H=3\). On the cover \(\widetilde G_{\rm EW}=\SU(2)_L\times\U(1)_q\), write the action as
\[
(g,z)\phi=z^3g\phi.
\]
An element of \(\SU(2)\) preserves the line \(\mathbb C\phi_0\) exactly when it is
\[
g=\begin{pmatrix}a&0\\0&a^{-1}\end{pmatrix},
\qquad a\in\U(1).
\]
The scalar \(z^3\) never changes the ray, so
\[
\operatorname{Stab}_{\widetilde G_{\rm EW}}([\phi_0])
=
\left\{
\left(
\begin{pmatrix}a&0\\0&a^{-1}\end{pmatrix},z
\right):a,z\in\U(1)
\right\}
\cong\U(1)_{T_3}\times\U(1)_Y.
\]
In particular, every pure hypercharge phase fixes \([\phi_0]\). Exact invariance of the vector imposes the additional equation \(z^3a^{-1}=1\), hence
\[
\operatorname{Stab}_{\widetilde G_{\rm EW}}(\phi_0)
=
\left\{
\left(
\begin{pmatrix}z^3&0\\0&z^{-3}\end{pmatrix},z
\right):z\in\U(1)
\right\}.
\]
Equivalently, in conventional angle variables,
\[
e^{i\alpha T_3}e^{i\beta Y}\phi_0
=e^{i(\beta-\alpha)/2}\phi_0.
\]
The ray is unchanged for independent \(\alpha\) and \(\beta\), while vector invariance ties them locally by \(\beta=\alpha\), leaving the generator \(Q=T_3+Y\). Passing to the physical gauge group divides both stabilizers by the inherited finite central kernel and leaves the connected vector stabilizer \(\U(1)_Q\). Higher \(\mathcal O(n)\) give larger \(\SU(2)\) multiplets and fail one-Higgs minimality.
\end{proof}

\begin{remark}[Carrier only, not the Higgs mass]
Proposition~\ref{prop:bw-higgs-carrier} identifies the representation, charge convention, and symmetry-breaking geometry of the OPH one-Higgs slot. It does not derive the weak scale, the Higgs quartic, \(m_H\), or Coleman--Weinberg dynamics; those remain D10/D11 quantitative and hierarchy/naturality branch statements.
\end{remark}

\begin{corollary}[Three Colors on the realized MAR branch]\label{cor:nc}
Under the hypotheses of Theorem~\ref{thm:sm}, the realized color-type factor acts in the fundamental triplet on the coupled carrier. Hence the realized quark doublet carries exactly
\[
N_c=3.
\]
\end{corollary}

\begin{proof}
Lemma~\ref{lem:su3class} identifies the minimal intrinsically complex color-type role in the connected Lie admissible class as the \(3\)-dimensional fundamental of \(\SU(3)\). Lemma~\ref{lem:carrier} then shows that MAR realizes this role on the coupled block \(\mathbb C^3\otimes\mathbb C^2\). The color multiplicity of the realized weak doublet \(Q\) is therefore fixed by the same D8 carrier to be \(3\). No later admissibility selector is needed to promote oddness to the specific value \(3\).
\end{proof}

\begin{corollary}[Three Generations on the realized MAR branch]\label{cor:ng}
Under the hypotheses of Theorem~\ref{thm:sm}, with \(N_c=3\) from Corollary~\ref{cor:nc}, the CP-capability and weak-sector UV clauses contained in Axiom~\ref{ax:mar} force
\[
N_g=3.
\]
\end{corollary}

\begin{proof}
On the realized one-Higgs chiral branch, intrinsic CKM CP capability requires
\[
\frac{(N_g-1)(N_g-2)}{2}>0,
\]
hence $N_g\ge 3$. For one Higgs doublet, the one-loop weak-sector coefficient is
\[
b_2=\frac{11}{3}C_A-\frac{2}{3}\sum_f T(R_f)-\frac{1}{3}\sum_s T(R_s)
=
\frac{22}{3}-\frac{N_g(N_c+1)}{3}-\frac16
=
\frac{43}{6}-\frac{N_g(N_c+1)}{3}.
\]
Asymptotic freedom therefore implies
\[
N_g(N_c+1)<\frac{43}{2}.
\]
With \(N_c=3\), this gives
\[
4N_g<\frac{43}{2},
\qquad\text{hence}\qquad
N_g\le 5.
\]
These are not extra post-MAR selectors: they are the explicit numerical consequences of the CP-capability and weak-sector UV clauses present in Axiom~\ref{ax:mar} on the same realized branch. Once the first three MAR components are fixed by the D8 color/weak structure, the fourth component \(N_g\) is minimized on the allowed set \(\{3,4,5\}\), so \(N_g=3\).
\end{proof}

\begin{corollary}[MAR-minimal SM package is unique up to physical equivalence]\label{cor:mar-sm-unique}
On the ordinary or central zero-obstruction bosonic branch, assume the MAR-admissible class is nonempty and contains the explicit realized one-Higgs chiral matter package used in Theorem~\ref{thm:sm} through Corollary~\ref{cor:ng}. Then every MAR-minimal representative has the same observer-visible Standard Model package,
\[
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6},
\qquad
N_c=3,\qquad
N_g=3,
\]
with the hypercharge lattice of Theorem~\ref{thm:hypercharge}. The only residual freedom is physical equivalence in the sense of Definition~\ref{def:mar-space}.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:mar-well-founded} supplies MAR minima. Lemmas~\ref{lem:su2class}--\ref{lem:commutant} fix the minimal weak, color, coupled-carrier, and connected abelian roles at the least first three complexity entries. Corollary~\ref{cor:nc} fixes \(N_c=3\), Corollary~\ref{cor:ng} fixes \(N_g=3\), Theorem~\ref{thm:hypercharge} fixes the charge lattice, and Proposition~\ref{prop:z6} fixes the finite kernel. Definition~\ref{def:mar-space} removes only relabelings, gauge-center conventions, and inert implementation data.
\end{proof}

\begin{remark}[Witten parity on the realized color branch]\label{rem:witten-parity}
With \(N_c=3\), each generation contributes \(N_c+1=4\) left-handed \(\SU(2)\) doublets, so Witten's global anomaly constraint is automatically satisfied generation by generation. In this theorem stack the anomaly is therefore a consistency check on the realized triplet-doublet package, not the step that creates the color count \cite{witten82}.
\end{remark}

\begin{proposition}[Global quotient from the realized matter spectrum]\label{prop:z6}
If the realized matter spectrum carries the hypercharges of Theorem~\ref{thm:hypercharge} with $N_c=3$, then the subgroup of $\SU(3)\times\SU(2)\times\U(1)$ acting trivially on all realized states is exactly $\mathbb Z_6$.
\end{proposition}

\begin{proof}
Write $q:=6Y\in\mathbb Z$ and $\eta:=e^{i\pi/3}$, so the $\U(1)$ factor acts by $\eta^q$ on charge-$q$ multiplets. The element
\[
g_0:=(\omega_3,-1,\eta)
\]
acts trivially on the realized matter and Higgs multiplets:
\[
Q:\ \omega_3(-1)\eta=1,\qquad
u^c:\ \omega_3^{-1}\eta^{-4}=1,\qquad
d^c:\ \omega_3^{-1}\eta^2=1,
\]
\[
L:\ (-1)\eta^{-3}=1,\qquad
e^c:\ \eta^6=1,\qquad
H:\ (-1)\eta^3=1.
\]
Its powers therefore generate a subgroup of order six acting trivially on all realized states. Conversely, any central element acting trivially on $e^c$ must have $\U(1)$ part $\eta^n$, and triviality on $Q$ then fixes the $\SU(3)$ and $\SU(2)$ center factors uniquely. Hence every trivial central element is a power of $g_0$, so the kernel is exactly $\mathbb Z_6$.
\end{proof}

\begin{remark}[Formal algebra core of hypercharge and the \(Z_6\) quotient]
\label{rem:formal-hypercharge-z6-core}
The algebraic part of Theorem~\ref{thm:hypercharge} and
Proposition~\ref{prop:z6} has an OPHProofChain finite Lean audit: Yukawa invariance together
with the stated anomaly equations fixes the hypercharge ray, the neutrino
neutrality convention fixes the normalized lattice \(Y_Q=1/(2N_c)\), and for
\(N_c=3\) the subgroup acting trivially on the realized one-generation
matter-plus-Higgs package is exactly the cyclic group generated by
\((\omega_3,-1,e^{i\pi/3})\), hence is isomorphic to \(\mathbb Z_6\).  The
formalization covers this algebra; it does not replace the MAR-admissibility
and realized matter-package hypotheses that select the branch on which the
algebra is applied.
\end{remark}

\begin{remark}[Arithmetic toy model for finite quotient labels]
DULA's congruence-grading construction gives a simple number-theoretic analogue of this
bookkeeping~\cite{dula2025}. For integers coprime to \(6\), the number of prime factors
congruent to \(5\) modulo \(6\), counted with multiplicity and reduced modulo \(2\), is an
additive finite label that determines whether the product is \(1\) or \(5\) modulo \(6\). OPH uses
this only as a toy model for the same formal pattern used
here: local factor or sector data accumulate in a finite abelian label, and that label determines
the global quotient or obstruction class.
\end{remark}

\begin{corollary}[Standard Model Gauge Group]
Under Theorem~\ref{thm:sm}, Theorem~\ref{thm:hypercharge}, Corollaries~\ref{cor:ng} and \ref{cor:nc}, and Proposition~\ref{prop:z6},
\[
G_{\mathrm{phys}}=
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6}.
\]
\end{corollary}

\begin{proof}
Theorem~\ref{thm:sm} yields the product structure up to finite quotient, and Proposition~\ref{prop:z6} fixes that quotient to $\mathbb Z_6$ once the realized hypercharge lattice and $N_c=3$ are in place.
\end{proof}

\begin{corollary}[Structural electroweak force and charges]\label{cor:electroweak-force}
On the realized one-Higgs branch of Theorem~\ref{thm:hypercharge} and Corollary~\ref{cor:mar-sm-unique}, the electroweak gauge factor has Lie algebra
\[
\mathfrak{su}(2)_L\oplus\mathfrak{u}(1)_Y.
\]
The Higgs doublet \(H=(1,2)_{1/2}\) selects a nonzero neutral vacuum vector
\[
\phi_0=\frac{v}{\sqrt2}\binom{0}{1},\qquad v\ne0,
\]
with
\[
Q\phi_0=(T_3+Y)\phi_0=0,
\]
so its vector stabilizer has unbroken generator
\[
Q=T_3+Y,
\]
and the unbroken gauge factor is \(\U(1)_Q\). The charged weak generators give
\[
W^\pm=\frac{1}{\sqrt2}(W^1\mp iW^2),
\]
while the neutral \(\SU(2)_L\) and \(\U(1)_Y\) gauge fields span the \(Z/A_Q\) connection basis on the D10 quantitative branch. Thus the recovered structural package contains the charged \(W^\pm\) connection directions, the neutral broken \(Z\) direction, the unbroken electromagnetic connection direction \(A_Q\), and the exact charge operator \(Q=T_3+Y\). These algebraic and connection labels alone assert neither a propagating mode nor a quantum particle. The mixing angle, \(v\), and the numerical \(W/Z\) masses belong to the D10 running/matching surface instead of this recovered-core structural corollary.
\end{corollary}

\begin{proof}
The D8 result fixes the weak-type role to the \(\SU(2)\) doublet and the connected abelian role to \(\U(1)_Y\). Theorem~\ref{thm:hypercharge} fixes \(Y_H=1/2\) and the matter hypercharge lattice, while Proposition~\ref{prop:bw-higgs-carrier} identifies the same one-Higgs slot with the minimal nontrivial holomorphic section carrier on the local weak chart. For conventional angles \(\alpha,\beta\), the action on the chosen nonzero vector is
\[
e^{i\alpha T_3}e^{i\beta Y}\phi_0
=e^{i(\beta-\alpha)/2}\phi_0.
\]
Thus the vector is fixed exactly by the diagonal relation \(\beta=\alpha\), locally, and its connected stabilizer is generated by \(Q=T_3+Y\). By contrast, its projective ray is fixed for independent \(\alpha\) and \(\beta\); that larger projective stabilizer is not the unbroken gauge group. The two noncommuting charged \(\SU(2)\) generators are broken directions and combine into the \(W^\pm\) connection components; the orthogonal neutral broken direction defines the \(Z\) connection component, while the gauge field of the unbroken vector stabilizer is the electromagnetic connection component \(A_Q\). The global \(\mathbb Z_6\) quotient fixes the compatible charge lattice used in Proposition~\ref{prop:z6} and only adds the corresponding finite central identification to this stabilizer calculation. None of these algebraic labels alone asserts a kinetic term, propagating mode, or quantum particle.
\end{proof}

\begin{corollary}[Conditional Maxwell sector on the realized \texorpdfstring{\(\U(1)_Q\)}{U(1)Q} branch]\label{cor:maxwell-sector}
On the realized ordinary zero-obstruction one-Higgs branch, let \(A_Q\) be the support-visible connection component on the unbroken electromagnetic factor \(\U(1)_Q\) of Corollary~\ref{cor:electroweak-force}. Then
\[
F_Q=dA_Q.
\]
Assume in addition the low-energy Lorentzian Maxwell action with conserved current \(J_Q\),
\[
S_{\mathrm{EM}}[A_Q,J_Q]
=
-\frac{1}{2g_Q^2}\int F_Q\wedge *F_Q
+\int A_Q\wedge *J_Q,
\]
equivalently
\[
S_{\mathrm{EM}}[A_Q]
=
-\frac{1}{4g_Q^2}
\int F_{Q,\mu\nu}F_Q^{\mu\nu}\,d^4x
\]
for the pure field term. Its Euler--Lagrange equations are
\[
dF_Q=0,
\qquad
d*F_Q=g_Q^2 *J_Q.
\]
In local coordinates,
\[
\partial_{[\lambda}F_{Q,\mu\nu]}=0,
\qquad
\partial_\mu F_Q^{\mu\nu}=g_Q^2 J_Q^\nu.
\]
After canonical electromagnetic normalization, these are Maxwell's equations. The numerical value of \(g_Q\), equivalently \(\alpha_{\mathrm{em}}\), belongs to the D10 Ward-projected electromagnetic readout. The compact-group reconstruction and connection label do not themselves supply this action or its nonzero kinetic coefficient; they are independent hypotheses of this corollary.
\end{corollary}

\begin{proof}
Corollary~\ref{cor:electroweak-force} supplies the unbroken electromagnetic factor \(\U(1)_Q\) with generator \(Q=T_3+Y\). The compact-gauge curvature theorem supplies a support-visible continuum connection and curvature
\[
F=dA+A\wedge A
\]
on the compact-gauge scaling chart. Restricting to \(\U(1)_Q\) removes the Lie-bracket term because \(\mathfrak u(1)\) is abelian, hence
\[
F_Q=dA_Q.
\]
The identity \(d^2=0\) gives \(dF_Q=0\).

For the sourced equation, vary
\[
S_{\mathrm{EM}}[A_Q,J_Q]
=
-\frac{1}{2g_Q^2}\int F_Q\wedge *F_Q
+\int A_Q\wedge *J_Q.
\]
Since \(\delta F_Q=d(\delta A_Q)\), integration by parts on compactly supported variations gives
\[
\delta S_{\mathrm{EM}}
=
\int \delta A_Q\wedge
\left(
\frac{1}{g_Q^2}d*F_Q-*J_Q
\right)
\]
up to the boundary term. Stationarity for arbitrary \(\delta A_Q\) gives
\[
d*F_Q=g_Q^2 *J_Q.
\]
Applying \(d\) to the sourced equation gives \(d*J_Q=0\), the current-conservation compatibility condition. The component equations are the standard homogeneous and inhomogeneous Maxwell equations with the OPH coupling convention.
\end{proof}

\begin{definition}[Carrier-mode and quantum-particle receipts]
\label{def:carrier-particle-receipts}
Fix the structural invariant speed \(c_\star\). A classical massless carrier-mode receipt for a
field \(q_X\) consists of a stated background and phase, an explicit quadratic action
with positive nonzero physical kinetic coefficient, a gauge fixing or constraint reduction with physical projector
\(\Pi_X\), and a positive reduced Hamiltonian. Separately, the action Hessian restricted to the
physical subspace must have
\[
K_X^{\mathrm{phys}}(\omega,\mathbf k)
=Z_X\bigl(\omega^2-c_\star^2|\mathbf k|^2\bigr)\Pi_X,
\qquad Z_X>0,
\]
so the free reduced Green function is
\[
D_X^{\mathrm{phys}}(\omega,\mathbf k)
=\frac{i\,\Pi_X/Z_X}
{\omega^2-c_\star^2|\mathbf k|^2+i0}.
\]
This is an action-level classical-mode statement, not a particle-mass statement.

A quantum-particle receipt additionally supplies: a positive-energy vacuum quantization; a
physical Hilbert space obtained by constraint reduction or BRST cohomology; a physical two-point
function with K\"all\'en--Lehmann measure
\[
d\rho_X(\mu^2)
=Z_X^{\mathrm{pole}}\delta(\mu^2)d\mu^2+d\rho_X^{\mathrm{cont}}(\mu^2),
\qquad Z_X^{\mathrm{pole}}>0;
\]
or an equivalent joint energy--momentum spectrum containing a positive-residue
\(p^0>0,\ p^2=0\) mass shell (at fixed \(\mathbf k\),
\(\omega=c_\star|\mathbf k|\));
and the stability/asymptotic-state or LSZ hypotheses appropriate to the phase, including a
deconfined asymptotic sector for a colored carrier. Only the combined classical and quantum
receipt licenses a massless quantum-particle claim. A compact group, connection label, or
classical field equation alone does not pass either missing step.
\end{definition}

\begin{theorem}[Action-level carrier modes on the Maxwell, pure-Yang--Mills, and Einstein branches]
\label{thm:carrier-mode-gates}
The following statements hold under the displayed additional action, background, field-content,
and phase hypotheses.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2em]
\item On the source-free ordinary electromagnetic vacuum branch \(J_Q=0\), assume the Maxwell action of
Corollary~\ref{cor:maxwell-sector} with \(0<g_Q^2<\infty\) and no Higgs, Stueckelberg, medium, or
nonlocal quadratic mass operator. Radiation gauge leaves two transverse components and
\[
H_Q^{(2)}=\frac{1}{2g_Q^2}\int
\bigl(|\mathbf E_T|^2+|\mathbf B|^2\bigr)d^3x,
\qquad
K_{Q,T}=g_Q^{-2}
\bigl(\omega^2-c_\star^2|\mathbf k|^2\bigr)\Pi_T,
\qquad \operatorname{rank}\Pi_T=2.
\]
In covariant \(\xi\)-gauge the free kernel has inverse
\[
D^Q_{\mu\nu}(k)
=\frac{-ig_Q^2}{k^2+i0}
\left(\eta_{\mu\nu}-(1-\xi)\frac{k_\mu k_\nu}{k^2+i0}\right),
\]
whose longitudinal part decouples from a conserved current. Hence the branch has two classical
massless electromagnetic carrier modes.

\item Let a compact group \(G\) carry the Lorentzian two-derivative pure Yang--Mills action with
\(0<g^2<\infty\), expanded about the topologically trivial background in a gauge
\(\bar A_\mu=0\), in a perturbative or deconfined phase with no Higgs condensate. Writing the
perturbation as \(a_\mu^a\), its quadratic action is
\[
S_{\mathrm{YM}}^{(2)}
=-\frac{1}{4g^2}\sum_a\int
\bigl(\partial_\mu a_\nu^a-\partial_\nu a_\mu^a\bigr)
\bigl(\partial^\mu a^{a,\nu}-\partial^\nu a^{a,\mu}\bigr)d^4x.
\]
Lorenz gauge gives the standard covariant inverse, while Gauss' law and radiation gauge leave two
transverse components per generator, with
\[
H_{\mathrm{YM}}^{(2)}
=\frac{1}{2g^2}\sum_a\int
\bigl(|\mathbf E_T^a|^2+|\mathbf B^a|^2\bigr)d^3x\geq0,
\]
with strict positivity on nonzero reduced finite-energy modes of
\(\mathbf k\neq0\) under the stated boundary conditions. Their kernel and free transverse Green
function are
\[
K^{ab}_{\mathrm{YM},T}
=\delta^{ab}g^{-2}
\bigl(\omega^2-c_\star^2|\mathbf k|^2\bigr)\Pi_T,
\qquad
D^{ab}_{\mathrm{YM},T}
=\frac{i g^2\delta^{ab}\Pi_T}
{\omega^2-c_\star^2|\mathbf k|^2+i0}.
\]
Consequently there are \(2\dim G\) transverse classical modes and the corresponding gauge-fixed
free \(k^2=0\) pole. This is a perturbative quadratic statement. It does not give a gauge-invariant
asymptotic gluon on the confined QCD branch; the positive gauge-invariant Yang--Mills gap and the
colored connection pole concern different spectral questions.

\item In addition to the derived classical Einstein equation, assume the two-derivative
Einstein--Hilbert action with \(G>0\) about a Minkowski vacuum with \(\Lambda=0\), without higher-curvature
kinetic terms, bimetric mixing, or extra scalar/vector fields. De Donder gauge and residual-gauge
reduction give the two transverse-traceless components with
\[
S_{\mathrm{TT}}^{(2)}
=\frac{1}{64\pi G}\int
\left[(\partial_t h_{ij}^{\mathrm{TT}})^2
-c_\star^2(\nabla h_{ij}^{\mathrm{TT}})^2\right]d^4x,
\]
\[
H_{\mathrm{TT}}^{(2)}
=\frac{1}{64\pi G}\int
\left[(\partial_t h_{ij}^{\mathrm{TT}})^2
+c_\star^2(\nabla h_{ij}^{\mathrm{TT}})^2\right]d^3x,
\qquad
D^{\mathrm{TT}}_{ij,kl}(k)
\propto\frac{i\Pi^{\mathrm{TT}}_{ij,kl}}{k^2+i0},
\qquad \operatorname{rank}\Pi^{\mathrm{TT}}=2.
\]
Thus the pure Einstein linearization has two classical massless spin-two wave modes. On a curved
Einstein background the appropriate object is the Lichnerowicz spectrum with stated boundary
conditions, not an automatic Poincar\'e particle pole.
\end{enumerate}
\end{theorem}

\begin{proof}
For item~\textup{(i)}, the second variation of the Maxwell action is the standard vector kinetic
Hessian. Gauss' law removes the longitudinal canonical pair, leaving two transverse polarizations
with positive Hamiltonian and dispersion \(\omega^2=c_\star^2|\mathbf k|^2\); inversion after
gauge fixing gives the displayed propagator. For item~\textup{(ii)},
\(F^a_{\mu\nu}=\partial_\mu A^a_\nu-\partial_\nu A^a_\mu+O(A^2)\), so the quadratic Hessian is
one Maxwell Hessian per Lie-algebra generator and the nonabelian interactions begin at cubic
order. For item~\textup{(iii)}, the second variation of the Einstein--Hilbert action is the
Fierz--Pauli kinetic form. De Donder gauge and its residual freedom reduce it to the displayed
transverse-traceless action with \(+\) and \(\times\) polarizations. These calculations establish
the classical receipt of Definition~\ref{def:carrier-particle-receipts}; none constructs its
quantum Hilbert-space, physical spectral-measure, or asymptotic-state clauses.
\end{proof}

\begin{corollary}[Conditional particle interpretation]
\label{cor:conditional-carrier-particles}
If a branch in Theorem~\ref{thm:carrier-mode-gates} is also supplied with the quantum-particle
receipt of Definition~\ref{def:carrier-particle-receipts}, its positive-residue
\(\delta(\mu^2)\) contribution defines a massless particle pole with the displayed physical
polarizations. Without that receipt, this paper claims only the corresponding classical or
perturbative carrier mode. In particular, compact-group reconstruction does not itself create a
Maxwell kinetic term or deconfined phase, and the classical Einstein equation does not itself
create a graviton state.
\end{corollary}

\begin{remark}[Hard quadratic terms versus the physical spectrum]
The zero hard parameters in the displayed Maxwell, pure-Yang--Mills, and pure-Einstein quadratic
operators are branch-specific action statements, not universal exact particle masses. Gauge or
diffeomorphism redundancy can coexist with Higgs/Stueckelberg completions, plasma or medium
self-energies, confinement, higher-derivative poles, bimetric sectors, or additional massive
fields. Excluding those possibilities requires the declared field-content and phase hypotheses.
\end{remark}

\begin{remark}[Maxwell branch boundary]
Corollary~\ref{cor:maxwell-sector} concerns the ordinary electromagnetic branch. Topologically
singular sectors with magnetic sources obey modified homogeneous equations. On the certified
support-visible compact simple nonabelian branch, Theorem~\ref{thm:oph-yang-mills-gap} gives a
positive gauge-invariant repair gap under its named finite and continuum receipts. On the abelian
branch, the Maxwell action and phase hypotheses of Theorem~\ref{thm:carrier-mode-gates} give two
classical massless transverse modes; a photon particle requires
Corollary~\ref{cor:conditional-carrier-particles}.
\end{remark}

\begin{theorem}[Realized compact-gauge witness and physical UV landing]\label{thm:mar-witness-landing}
On the ordinary or central zero-obstruction bosonic branch, suppose a cofinal tail carries the
compact-gauge refinement receipt of Definition~\ref{def:compact-gauge-refinement-receipt}. Then
the OPH compact reference architecture admits an OPH-realizable cofinal heat-kernel edge-sector witness
\[
\mathcal W_{\mathrm{SM}}
=
\{Q_i,u_i^c,d_i^c,L_i,e_i^c,H\}_{i=1}^{3}
\]
with
\[
Q_i=(3,2)_{1/6},\qquad
u_i^c=(\bar 3,1)_{-2/3},\qquad
d_i^c=(\bar 3,1)_{1/3},
\]
\[
L_i=(1,2)_{-1/2},\qquad
e_i^c=(1,1)_1,\qquad
H=(1,2)_{1/2}.
\]
Every witness sector has positive realized support on the compact heat-kernel branch, and the witness is MAR-admissible. Hence the MAR-admissible class used above is nonempty. Every OPH-admissible microscopic UV completion of this realized branch has observer-visible low-energy package, modulo physical equivalence in Definition~\ref{def:mar-space},
\[
\mathfrak S_{\mathrm{SM}}
=
\left(
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6},
\mathcal R_{\mathrm{SM}},
H,
\mathcal Y_{\mathrm{SM}}
\right),
\qquad
N_c=3,\qquad N_g=3,
\]
with the hypercharge lattice of Theorem~\ref{thm:hypercharge}.
\end{theorem}

\begin{proof}
Use the fixed-cutoff compact-gauge patch-carrier architecture on the zero-obstruction branch. The
microphysics carrier may be represented by finite gauge-register, quantum-link, or federated
echosahedral regulator charts; only the declared overlap sector algebra and refinement-compatible
compact labels are used here. At a sufficiently fine compact cutoff, retain the Peter--Weyl labels
listed in \(\mathcal W_{\mathrm{SM}}\). They are finite-dimensional unitary representations of
\(\SU(3)\times\SU(2)\times\U(1)\), and with integer normalization \(q=6Y\)
Proposition~\ref{prop:z6} shows that the generator \(g_0=(\omega_3,-1,e^{i\pi/3})\) acts trivially
on exactly the displayed matter and Higgs multiplets. The witness therefore descends to the
quotient \((\SU(3)\times\SU(2)\times\U(1))/\mathbb Z_6\).

The fixed-cutoff edge heat-kernel law on the microphysics surface gives sector weights
\[
p_R(t)\propto d_R e^{-tC_2(R)}
\]
on the compact branch. For finite \(t\), \(d_R>0\) and \(e^{-tC_2(R)}>0\), so every witness projector has positive support. On the tail certified by the stated receipt, the refinement functors of Theorem~\ref{thm:refinement-functor-fiber-descent} carry those zero-obstruction labels forward, and Theorem~\ref{thm:sector-colimit} places the corresponding objects in \(\mathsf{Sect}_\infty\).

The witness is loop-coherent by the zero-obstruction branch. Theorem~\ref{thm:hypercharge} supplies anomaly cancellation and one-Higgs Yukawa completeness on the displayed chiral package; Lemmas~\ref{lem:su2class}--\ref{lem:carrier} give the weak-type and color-type roles on the minimal coupled carrier; Corollary~\ref{cor:nc} gives \(N_c=3\); and Corollary~\ref{cor:ng} gives \(N_g=3\) from the CP-capability and weak-sector UV clauses in Axiom~\ref{ax:mar}. Thus \(\mathcal W_{\mathrm{SM}}\) is an occupied MAR-admissible package.

Proposition~\ref{prop:mar-well-founded} supplies minima for the resulting nonempty admissible class. Corollary~\ref{cor:mar-sm-unique} and Proposition~\ref{prop:z6} identify every MAR-minimal observer-visible package with the displayed Standard Model package. Finally, Remark~\ref{rem:mar-uniqueness} and Definition~\ref{def:mar-space} remove only microscopic regulator choices, implementation hiding, gauge-center conventions, generation relabeling, charge-conjugation convention, and inert ancillary stabilization. Thus any OPH-admissible UV completion of the realized branch lands on the same observer-visible low-energy package, not on a unique microscopic representative.
\end{proof}

\begin{theorem}[Realized Standard Model branch]\label{thm:realized-sm-branch}
Assume:
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=2em]
\item the ordinary or central zero-obstruction bosonic branch of
Theorem~\ref{thm:transport-from-gluing};
\item a cofinal tail carrying the compact-gauge refinement receipt of
Definition~\ref{def:compact-gauge-refinement-receipt}, together with the fixed-cutoff bosonic sector category, refinement/fiber descent, and compact-group
reconstruction of Theorems~\ref{thm:fixed-cutoff-bosonic-sector-category},
\ref{thm:refinement-functor-fiber-descent}, \ref{thm:sector-colimit}, and
\ref{thm:compactgauge};
\item a nonempty realized one-Higgs chiral MAR-admissible class, witnessed by
\(\mathcal W_{\mathrm{SM}}\) in Theorem~\ref{thm:mar-witness-landing};
\item the weak-type and intrinsically complex color-type roles on a common coupled carrier;
\item one connected abelian charge factor acting nontrivially on that carrier; and
\item the anomaly-free, one-Higgs Yukawa-complete, CP-capable, and weak-sector UV clauses of
Axiom~\ref{ax:mar}.
\end{enumerate}
Then MAR minima exist, and every MAR-minimal observer-visible package in that class is physically
equivalent to
\[
\left(
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6},
\mathcal R_{\mathrm{SM}},
H,
\mathcal Y_{\mathrm{SM}}
\right),
\qquad
N_c=3,\qquad N_g=3,
\]
where the matter package is
\[
\mathcal W_{\mathrm{SM}}
=
\{Q_i,u_i^c,d_i^c,L_i,e_i^c,H\}_{i=1}^{3},
\]
with
\[
Q_i=(3,2)_{1/6},\quad
u_i^c=(\bar 3,1)_{-2/3},\quad
d_i^c=(\bar 3,1)_{1/3},\quad
L_i=(1,2)_{-1/2},\quad
e_i^c=(1,1)_1,\quad
H=(1,2)_{1/2}.
\]
\end{theorem}

\begin{proof}
Proposition~\ref{prop:mar-well-founded} gives existence of MAR minima because the admissible
class is nonempty and \(C(\mathfrak S)\in\mathbb N^4\) is well ordered lexicographically.
Lemmas~\ref{lem:su2class} and \ref{lem:su3class} identify the minimal weak-type and color-type
connected nonabelian roles as \(\SU(2)\) and \(\SU(3)\). Lemma~\ref{lem:carrier} puts those roles
on the minimal coupled carrier \(\mathbb C^3\otimes\mathbb C^2\), not on the uncoupled
\(\mathbb C^3\oplus\mathbb C^2\), and Lemma~\ref{lem:commutant} identifies the unique connected
abelian commutant as \(\U(1)\). Theorem~\ref{thm:sm} therefore gives product structure up to
finite central quotient. Theorem~\ref{thm:hypercharge} fixes the hypercharge lattice,
Corollary~\ref{cor:nc} fixes \(N_c=3\), Corollary~\ref{cor:ng} fixes \(N_g=3\) as a
MAR-branch consequence instead of as anomaly cancellation alone, and Proposition~\ref{prop:z6}
fixes the global kernel. Corollary~\ref{cor:mar-sm-unique} then identifies all minima modulo
the physical equivalence relation of Definition~\ref{def:mar-space}.
\end{proof}

\begin{corollary}[Product-Group Consequences]
The adjoint representation of the full connected gauge group contains only
\[
(8,1,0)\oplus(1,3,0)\oplus(1,1,0).
\]
Equivalently, the adjoint representation of the derived gauge group contains only
\[
(8,1,0)\oplus(1,3,0).
\]
There are no mixed $(3,2,\pm 5/6)$ gauge generators. Hence the ordinary simple-GUT
gauge-mediated proton-decay channel is absent. This adjoint-content statement does not by itself
supply a gauge-field kinetic term, select a phase, or determine a particle mass; those questions
are governed by Definition~\ref{def:carrier-particle-receipts} and
Theorem~\ref{thm:carrier-mode-gates}.
\end{corollary}

\begin{remark}
The same product-group structure removes the usual grand-unification monopole sector. In the present framework, any retained coupling-unification discussion does not proceed by embedding the gauge group into a simple group that is later broken. It proceeds, if at all, only through the separate D10 calibration branch built from shared edge heat-kernel data together with the printed running/matching/threshold/scheme conventions and extra calibration assumptions. Absence of gauge-mediated proton decay and unification-like running therefore coexist without tension on that branch. Any confinement statement is a separate infrared dynamical issue, not a corollary of the product-group adjoint argument alone.
\end{remark}

\subsection{Fundamental scales}

The quantitative D10 branch is a forward quantitative-closure sector, not part of the recovered-core theorem package. Its particle-physics scale variable is
\[
P \equiv a_{\mathrm{cell}}/\ell_\star^2,
\]
with the selected no-\(G\) scale certificate, which supplies \(\ell_\star^2=3\pi/B_\star\) and
becomes the usual Planck-area display after \(G_{\mathrm{SI}}=c^3\ell_\star^2/\hbar\). The same quantitative
surface also uses the realized discrete gauge data of the structural branch, in particular
\[
N_c=3,
\qquad
\beta_{\mathrm{EW}}=N_c+1=4.
\]
The logical direction is therefore
\[
P
\longmapsto
\bigl(M_U(P),E_{\mathrm{cell}}(P)\bigr)
\longmapsto
\alpha_U(P)
\longmapsto
\bigl(t_U(P),t_{\mathrm{tr}}(P)\bigr)
\longmapsto
\bigl(t_2(P),t_3(P),v(P)\bigr)
\longmapsto
\alpha_i(\mu_\ast;P).
\]
The edge-law input on this lane is split explicitly by claim tier. The fixed-cutoff
same-overlap thermal/Casimir theorem is carried on the separate microphysics surface. This
compact paper imports that closure through the declared merge boundary: one fixed-cutoff
edge-law package below, then the compact-group / Peter--Weyl lift used in the D10 pixel
constraint above it. The compact-group lift is a declared D10 branch handoff, while
large-\(N_{\mathrm{edge}}\) and critical-string claims belong to the continuation lane. The
finite-cutoff Casimir branch itself is not a missing input. No hardware evidence, private run
log, or laboratory module claim is imported into this D10 theorem step.
The declared runtime forward subgraph does not read measured electroweak targets when it evaluates
the internal transmutation parameters.  Those quantities enter its printed output as comparison
coordinates.  This runtime separation is not a proof of target-free historical ancestry,
of a complete source dependency graph, or of a unique promotable repair branch.
The forward transmutation certificate makes the narrower runtime order explicit: its source-side
algebra reconstructs the same \(\alpha_U(P)\), hence the same unified diffusion parameter
\[
t_U(P)=4\pi^2\alpha_U(P),
\]
and transmutation exponent
\[
t_{\mathrm{tr}}(P)=\frac{2\pi}{(N_c+1)\alpha_U(P)}
\]
as the pixel-closure solve itself. Here the paper-side transmutation factor is the same
\(\beta_{\mathrm{EW}}=N_c+1\) used below; legacy overloaded \(\beta\)-ratios are compare-only
diagnostic readouts and are not part of the theorem contract.

This fixes the hierarchy interpretation used by the compact paper. The cosmic capacity target
\(N_{\mathrm{CRC}}\) belongs to the conditional global horizon-capacity branch. The electroweak hierarchy is
local:
\[
\frac{v}{E_\star}
=
P_\star^{-1/2}
\exp\!\left[-\frac{2\pi}{4\alpha_U(P_\star)}\right].
\]
The hierarchy bundle certifies this local branch by the interval
\[
I_U=[0.041123336195630494,\;0.041125336195630496],
\]
with a Krawczyk image
\[
K(I_U)\subset
[0.0411243357185544983,\;0.0411243366727064662]
\subset \mathrm{int}(I_U)
\]
and a strictly negative derivative enclosure
\[
\mathcal F'(\alpha_U;P_\star)\in[-10.995768,\,-10.985284].
\]
The CODATA-conditioned comparison branch then gives
\[
\begin{aligned}
\alpha_U(P_\star)&=0.041124336195630495,\\
\frac{v}{E_\star}&=2.0199803239725553\times10^{-17},\\
\log_{10}\frac{E_\star}{v}&=16.69465286086613.
\end{aligned}
\]
The source-audit branch gives
\[
\begin{aligned}
P_{\mathrm{cand}}&=\decnum{1.63097209569432901817967892561191884270169},\\
\frac{v(P_{\mathrm{cand}})}{E_\star}&=2.0198114150099223\times10^{-17},
\end{aligned}
\]
and is the branch to use when the public Thomson endpoint is excluded upstream.
A converged precision-100 rerun supersedes this printed \(P_{\mathrm{cand}}\) beyond
digit 10; the certified forward pixel is \(P_{\mathrm{fwd}}=1.630972095858897\ldots\).
The Higgs naturalness row is read on the same D10/D11 normal-form surface. The displayed
\(m_H=H_{\mathrm{OPH}}(P_\star)\) is a conditional D11 coordinate on its declared
running, matching, and threshold surface, not yet an observer-visible complex pole. The split
into a bare scalar mass plus a cutoff correction is a regulator coordinate description. The
conditional source-to-Higgs coarse-graining square has the displayed selected-surface defect bound
\[
\epsilon_H=0,\qquad \epsilon_H\in[0,0],
\]
with measured weak-scale, Higgs/top, \(W/Z\), gravity, Planck-area, and \(\Lambda\) inputs
excluded from the declared runtime contract.  That exclusion does not establish prospective
provenance for the selected formulas. Promotion to a physical Higgs pole requires the
strict source-root, independent physical-scale, QT1--QT5, RG/scheme, D11-rigidity,
uncertainty, complex-pole, and no-target dependency-DAG gates.
The adjacent electroweak projection bridge defines
\[
\Pi_{\mathrm{EW}}(P,N)
=
\frac{24\pi}{\alpha_U(P)\log(N/\pi)}.
\]
The target \(\Pi_{\mathrm{EW}}(P_\star,N_{\mathrm{CRC}})=4P_\star\) is equivalent to
\[
\mathcal B_{\mathrm{EW}}(P,N)
:=
\alpha_U(P)\log(N/\pi)-\frac{6\pi}{P}=0,
\]
or \(N_{\mathrm{EW}}(P)=\pi\exp[6\pi/(P\alpha_U(P))]\). On the public endpoint branch this
target is \(3.5323546226929906511187512962330547600462\times10^{122}\). The distinct
Planck--\(\Lambda\) central comparison is \(N_{\Lambda}\simeq3.313\times10^{122}\); the
\(6.6\%\) central-value gap relative to \(N_{\Lambda}\) is a conditional mismatch because the
readback map \(F\) and premises CP-1--CP-3 remain open.
The factor \(12\) in the exponent has the screen-sieve theorem as its geometric source:
on the triangulated \(S^2\) branch, \(q_v=6-\deg(v)\) obeys
\(\sum_v q_v=12\); convex MaxEnt defect cost spreads this into twelve unit
fivefold defects; edge-center collars make them central ports; \(A_5\) symmetry
places them on the icosahedral vertex orbit.
With reversible write/check orientation, the same branch supplies a 24-slot
oriented repair register; the hierarchy exponent uses that 24-fold repair
normalization.

\paragraph{Bosonic mass-prediction boundary.}
The result just proved is dimensionless.  It fixes a branch value of
\(v/E_\star\), once the named pixel and unified-coupling packet are supplied;
it does not by itself fix \(v\) in GeV.  The public-endpoint coordinate
\(P_C\) and the source-audit coordinate \(P_{\mathrm{cand}}\) must also remain
separate.  They give nearby but distinct values of \(\alpha_U\) and
\(v/E_\star\).  The selected scale theorem above is conditional on the
supplied no-\(G\) clock certificate, and a strict particle-mass claim inherits
the open source construction of that certificate rather than treating its SI
display as an input.

\begin{theorem}[Structural electroweak and absolute-scale
underdetermination]\label{thm:boson-structural-scale-no-go}
The realized Standard Model quotient, one Higgs doublet, three colors, and
three generations do not determine numerical \(W\), \(Z\), or Higgs masses.
Moreover, a source packet that determines only dimensionless couplings and
\(r_v:=v/E_\star\), without independently determining the physical scale
\(E_\star\), cannot determine those masses in GeV.
\end{theorem}

\begin{proof}
For the one-doublet electroweak Lagrangian, with
\(V(H)=-\mu^2H^\dagger H+\lambda_H(H^\dagger H)^2\), one has
\[
v^2=\frac{\mu^2}{\lambda_H},\qquad
m_W=\frac{g_2v}{2},\qquad
m_Z=\frac v2\sqrt{g_2^2+g_Y^2},\qquad
m_H=\sqrt{2\lambda_H}\,v.
\]
Positive continuous changes of \(g_2,g_Y,\mu^2,\lambda_H\) preserve the
gauge quotient, representations, anomaly relations, charge lattice, color
count, generation count, and Higgs multiplicity while changing all three
masses.  Thus the structural package needs an additional quantitative source
law.  If that law fixes only \(r_v\), then for any \(c>0\) the replacement
\(E_\star\mapsto cE_\star\), \(v\mapsto cv\) preserves every dimensionless
equation and sends \((m_W,m_Z,m_H)\mapsto c(m_W,m_Z,m_H)\).  An independent
clock, length, energy, or spectral-scale theorem is therefore necessary.
\end{proof}

\begin{theorem}[Source-extension non-entailment for the boson
lane]\label{thm:boson-source-extension-no-go}
Let $T_0$ be the structural OPH theory through the realized Standard Model
quotient and one-Higgs branch, but without a separately emitted D10 path
measure, D11 split character, absolute clock Hamiltonian, or renormalized
two-point kernel. If two extensions of $T_0$ assign different values to one
of those objects, then $T_0$ does not entail that value. In particular, for
sufficiently small $c,d,a,b,\epsilon$, the families
\[
 \tau_2=-c\eta^2,\qquad
 \delta n=d(1-\rho_{\rm EW})\eta^2,
\]
\[
 \pi_y\mapsto\pi_y+a\eta^N,\qquad
 \pi_\lambda\mapsto\pi_\lambda+b\eta^N,
\]
and the inverse two-point functions
\[
 F_1(s)=s-m_R^2,\qquad F_2(s)=s-m_R^2-\epsilon
\]
preserve the corresponding structural, analytic, and target-free premises
while changing respectively the $W/Z$, Higgs/top, and pole outputs.
Therefore two-channel exhaustion, a running-mass chart, and target-free
analyticity do not by themselves emit the missing source laws.
\end{theorem}

\begin{proof}
Semantic entailment requires agreement in every model of $T_0$. On the open
positive domain, differentiation gives
\(\partial_c M_W\ne0\), \(\partial_d M_Z\ne0\),
\(\partial_a m_t\ne0\), and \(\partial_b m_H\ne0\). The two displayed inverse
two-point functions have zeros $m_R^2$ and $m_R^2+\epsilon$. Thus each pair
supplies source extensions that obey the named common premises but disagree on
the proposed output.
\end{proof}

\begin{proposition}[Non-vacuity of a finite source carrier]
Any finite polynomial can be represented formally as a weighted path sum by
introducing one path per monomial. Consequently, a path table is source
evidence only if its primitive transitions, admissibility and depth bound,
quotient action, response map, weights, signs, exhaustive enumeration,
rigidity or strict MAR gap, and no-target dependency DAG were fixed
independently of the desired coefficients.
\end{proposition}

\begin{proof}
For $p(x)=\sum_\alpha c_\alpha x^\alpha$, introduce a formal path
\(\gamma_\alpha\) with weight $c_\alpha$ and character $x^\alpha$. Its
weighted character is exactly $p$. Hence mere representability cannot
distinguish source emission from coefficient encoding; the listed independent
carrier obligations provide that distinction.
\end{proof}

\begin{proposition}[Conditional clock attachment and gap stability]
Let a declared clock transition have physical frequency \(\nu_{\rm clk}\),
used as an operational unit convention, and let the same source branch emit
its dimensionless gap \(\varepsilon_{\rm clk}>0\).  Then
\[
E_\star=\frac{h\nu_{\rm clk}}{\varepsilon_{\rm clk}}.
\]
Equivalently, if the source emits
\(\gamma_\star=\ell_\star\nu_{\rm clk}/c\), then
\(\ell_\star=c\gamma_\star/\nu_{\rm clk}\) and
\(E_\star=\hbar\nu_{\rm clk}/\gamma_\star\).  If two certified clock
Hamiltonians differ by at most \(\epsilon\) in operator norm, an isolated
selected gap changes by at most \(2\epsilon\).
\end{proposition}

\begin{proof}
The scale identities are algebraic.  The gap bound follows by applying the
standard eigenvalue perturbation bound to each of the two isolated levels.
If \(\nu_{\rm clk}\) is used as measured calibration rather than as the
declared unit convention, the result is a calibrated scale, not a source-only
prediction.
\end{proof}

For a refinement sequence of label-preserving clock Hamiltonians
\(\widehat H_r\), the stronger summability condition
\[
 \sum_r\|\widehat H_{r+1}-\iota_r\widehat H_r\iota_r^*\|<\infty
\]
together with uniform isolation of the selected levels makes the emitted gaps
a positive Cauchy sequence. This proves refinement stability of a supplied
clock packet; it does not generate the electromagnetic, electron, nuclear, or
atomic entries of that packet.

\begin{proposition}[Electroweak running-mass chart]
If one frozen renormalization convention uniquely supplies
\(v(\mu),\alpha_2(\mu),\alpha_Y(\mu)\), and \(\lambda_H(\mu)\), then
\[
m_W(\mu)=v(\mu)\sqrt{\pi\alpha_2(\mu)},
\qquad
m_Z(\mu)=v(\mu)\sqrt{\pi\bigl(\alpha_2(\mu)+\alpha_Y(\mu)\bigr)},
\]
\[
\sin^2\theta_W(\mu)=
\frac{\alpha_Y(\mu)}{\alpha_2(\mu)+\alpha_Y(\mu)},
\qquad
m_H^2(\mu)=2\lambda_H(\mu)v^2(\mu).
\]
For GUT-normalized \(\alpha_1\), \(\alpha_Y=(3/5)\alpha_1\).
These identities close the algebraic chart from running parameters to running
mass coordinates.  They neither select the D10 transport law nor convert a
running coordinate into a physical complex pole.
\end{proposition}

\begin{theorem}[D10 source-uniqueness and inverse-adapter boundary]
Let \(\mathfrak G_{10}\) be the class of D10 repair laws satisfying the
declared source constraints and let \(\mathcal M_{WZ}\) be the mass chart.  A
unique source prediction follows only if \(\mathcal M_{WZ}\) is constant on
\(\mathfrak G_{10}\), or a target-independent source selector chooses one
member.  An exact value obtained by solving an invertible local mass chart
against measured \(W/Z\) targets is an inverse calibration, not a prediction.
\end{theorem}

\begin{proof}
If \(\Gamma_1,\Gamma_2\in\mathfrak G_{10}\) obey all declared premises but
\(\mathcal M_{WZ}(\Gamma_1)\ne\mathcal M_{WZ}(\Gamma_2)\), those premises
entail neither output.  A further source-side selector is required.  For the
adapter statement, if the Jacobian of a local chart \(F:\Theta\to\mathbb R^n\)
is nonsingular, the inverse-function theorem gives a local inverse
\(\theta(m)=F^{-1}(m)\).  Exact equality
\(F(\theta(m_{\rm measured}))=m_{\rm measured}\) then follows from local
invertibility, independently of whether OPH emits \(\theta\).
\end{proof}

The present corpus exhibits the first case explicitly.  Beneath the candidate
repair chart it admits
\[
\tau_2^{\rm exact}=-c\,\eta_{\rm source}^2,
\qquad
\delta n^{\rm exact}=d(1-\rho_{\rm EW})\eta_{\rm source}^2,
\qquad
\rho_{\rm EW}:=\frac{\alpha_2-\alpha_Y}{\alpha_2+\alpha_Y},
\]
with more than one displayed source-compatible choice of \((c,d)\) and
different mass readouts.  The selected-carrier chart emits
\[
(m_W,m_Z)_{\rm carrier}
=(80.38629169244275,\ 91.18290444674243)\ {\rm GeV},
\]
whereas the frozen comparison adapter reported by the particle surface is
\[
(m_W,m_Z)_{\rm value\ law}
=(80.37700001539531,\ 91.18797807794321)\ {\rm GeV}.
\]
The distinct target-frozen inverse adapter uses
\[
(m_W,m_Z)_{\rm inverse\ adapter}
=(80.3625,\ 91.1879)\ {\rm GeV}.
\]
The older rounded pair \((80.377,91.18797809193725)\,\mathrm{GeV}\) is retained
only as a legacy boundary alias.  All three rows are useful executable comparison checks.
None is a closed D10 source theorem. These running/chart or inverse-adapter coordinates are
noncommensurate with PDG Breit--Wigner parameters and converted complex-pole coordinates until a
complete scheme map specifies the input definition, self-energies, analytic continuation, width
convention, and conversion. The two-loop transport and pole-packet exercises implement
hybrid or partial prescriptions on known \(W/Z\) data. Their adverse pulls are inconclusive tests of
those prescriptions and do not establish a \(1\)--\(2\%\) physical defect in D10.

\begin{proposition}[Conditional color-amplitude and color-trace
arithmetic]\label{prop:conditional-ew-color-weights}
Let \(V_c\simeq\mathbb C^{N_c}\).  Assume that the charged repair is the norm
of \(N_c\) orthogonal color-equivalent amplitudes, each with reduced weak
matrix element \(1/2\), and that hypercharge screening is the trace of a
color-blind loop.  Then the raw multiplicity weights are
\[
c_W=\frac{\sqrt{N_c}}2,
\qquad
c_Y=N_c.
\]
In the normalized chart
\(\delta n=d(1-\rho_{\rm EW})\eta_{\rm source}^2\), where
\((\alpha_2+\alpha_Y)(1-\rho_{\rm EW})=2\alpha_Y\), the same neutral trace is
represented by \(d=N_c/2\).  For \(N_c=3\), this gives
\(c_W=\sqrt3/2\), raw trace weight \(c_Y=3\), and chart coefficient
\(d=3/2\).
\end{proposition}

\begin{proof}
The charged invariant norm is
\(\bigl(\sum_{r=1}^{N_c}|a/2|^2\bigr)^{1/2}
=\sqrt{N_c}|a|/2\).  A color-blind loop \(kI_{V_c}\) has trace \(N_ck\).
Finally,
\((\alpha_2+\alpha_Y)d(1-\rho_{\rm EW})\eta^2
=2\alpha_Y(N_c/2)\eta^2=N_c\alpha_Y\eta^2\), which proves the normalized
coordinate identity.
\end{proof}

Proposition~\ref{prop:conditional-ew-color-weights} proves only this
arithmetic.  It defines the historical color-balanced quadratic candidate,
not the complete D10 value law below: the latter has a distinct primitive
activity and higher path character, and gives a different \(W\) coordinate.
A proof of the \(\sqrt{N_c}/2\) and \(N_c\) multiplicities would therefore
establish that alternative quadratic model rather than derive the archived
complete repair.

\begin{definition}[D10 quotient-path certificate]\label{def:d10-quotient-path-certificate}
Write
\[
\rho_{\rm EW}:=\frac{\alpha_2-\alpha_Y}{\alpha_2+\alpha_Y},
\qquad
\eta=\rho_{\rm EW}\alpha_U,
\qquad
b_{\rm tr}:=N_c+1=4,
\qquad
\lambda_{\rm EW}:=\frac{\eta\alpha_U}{4}
=\frac{\eta^2}{4\rho_{\rm EW}}.
\]
A D10 quotient-path certificate consists of the following finite statements.
\begin{enumerate}[leftmargin=2em,label=\textup{QT\arabic*.}]
\item After hidden representatives, port labels, and scheduler coordinates
are quotiented out, the real, CP-even, color-singlet, charge-preserving
response module through two returns is exactly
\(\mathcal R_{10}=\mathbb R q_2\oplus\mathbb R q_n\), with no third scalar or
charged-neutral off-block term.
\item The primitive response is of bidegree \((1,1)\) in
\((\eta,\alpha_U)\), one primitive event has a fixed unit response
normalization, and the quotient probability measure assigns weight \(1/4\) to
each of the four transmutation slots, giving \(\lambda_{\rm EW}\).
\item Explicit carrier path lists, with one factor of \(\eta\) per return and
uniform color-orbit measure \(1/3\), have primitive, one-return, and two-return incidences respectively
\((1,2/3,1)\) on \(q_2\) and \((1,4/3,2)\) on \(q_n\).  The diagonal
\(\mathbb Z_6\) projector in the declared response representation has
normalized trace \(1/6\), source amplitude \(\rho_{\rm EW}\), and subtracts
\((\rho_{\rm EW}/6)\eta^2\) from each degree-two character.  Thus
\[
C_2=1+\frac23\eta+\left(1-\frac{\rho_{\rm EW}}{6}\right)\eta^2,
\qquad
C_n=1+\frac43\eta+\left(2-\frac{\rho_{\rm EW}}{6}\right)\eta^2.
\]
\item Mismatch descent assigns the contracting sign to \(q_2\), the uplifting
sign to \(q_n\), and the parallel hypercharge coordinate minimizes
\[
\mathcal J_Y(t)
=\frac12(1+4\tau_2^2)t^2+(\tau_2+2\eta)t.
\]
\item The displayed paths exhaust the admissible response class: deeper
paths, alternative central weights, and mixed terms are quotient-trivial,
absent, or separated by a positive target-independent MAR gap.
\end{enumerate}
\end{definition}

\begin{theorem}[Conditional target-free D10 quotient
transport]\label{thm:conditional-d10-quotient-transport}
Assume a source-eligible pixel packet emits
\((\alpha_U,\alpha_2,\alpha_Y,v,\eta)\) with no measured \(W/Z\), measured
\(v\), fitted electroweak parameter, or calibrated proxy as an ancestor, and
assume Definition~\ref{def:d10-quotient-path-certificate}.  Then the quotient
emits one unique repair on every certified physical-domain interval for which
\(\widehat\alpha_2>0\) and \(\widehat\alpha_Y>0\):
\[
\tau_2=-\lambda_{\rm EW}C_2,
\qquad
\delta n=\lambda_{\rm EW}C_n,
\qquad
\tau_Y=-\frac{\tau_2+2\eta}{1+4\tau_2^2}.
\]
With \(\alpha_{Y,*}=\alpha_Y(1-2\eta)\), the repaired couplings are
\[
\widehat\alpha_2=\alpha_2(1+\tau_2),
\]
\[
\widehat\alpha_Y
=\alpha_{Y,*}
+\alpha_Y\frac{8\eta\tau_2^2-\tau_2}{1+4\tau_2^2}
+(\alpha_2+\alpha_Y)\delta n
=\alpha_Y(1+\tau_Y)+(\alpha_2+\alpha_Y)\delta n.
\]
The canonically normalized D10 mass coordinates and accompanying effective
readouts are therefore
\[
M_W^{(10)}=v\sqrt{\pi\widehat\alpha_2},
\qquad
M_Z^{(10)}=v\sqrt{\pi(\widehat\alpha_2+\widehat\alpha_Y)},
\]
\[
\alpha_{\rm em,eff}^{-1}
=\frac{\widehat\alpha_2+\widehat\alpha_Y}
{\widehat\alpha_2\widehat\alpha_Y},
\qquad
\sin^2\theta_{W,\rm eff}
=\frac{\widehat\alpha_Y}{\widehat\alpha_2+\widehat\alpha_Y}.
\]
\end{theorem}

\begin{proof}
QT1 reduces every response to the two displayed coordinates.  QT2 fixes their
common primitive activity.  The two path-incidence rows and the common
\(\mathbb Z_6\) subtraction in QT3 give \(C_2\) and \(C_n\), while QT4 fixes
their signs.  Since \(1+4\tau_2^2>0\), \(\mathcal J_Y\) is strictly convex and
its unique minimizer is the displayed \(\tau_Y\).  Substitution gives the two
repaired couplings and the standard one-Higgs mass chart.  QT5 removes every
remaining admissible deformation, proving uniqueness on the certified class.
\end{proof}

The archived calibration tuple specializes this implication to
\[
\begin{aligned}
\rho_{\rm EW}&=0.5385291530498766\ldots,\\
\tau_2&=-0.0002311623001746158\ldots,\\
\delta n&=0.0002346358802434819\ldots,
\end{aligned}
\]
\[
\bigl(M_W^{(10)},M_Z^{(10)}\bigr)
=
\bigl(80.37700001539531,\ 91.18797807794321\bigr)\ {\rm GeV}.
\]
This verifies the algebra of the archived value law.  It does not prove that
the archived tuple is a same-branch evaluation of the strict source-audit
pixel, nor does it prove QT1--QT5.  Promotion requires explicit finite path
lists and quotient canonicalization, exact incidence and central-trace
checks, the fibre Gram calculation, a positive rigidity gap, and a same-branch
no-target dependency DAG.  The conditional quotient-transport theorem closes
the implication from that certificate; deriving the certificate from the
finite D10 carrier remains the source-entailment obligation.  The carrier must
be frozen independently as an observer-like self-reading patch with bounded
local state, ports, readback records, and admissible feedback/repair moves; it
may contain neither the desired incidence
coefficients nor mass targets.  An untrusted exact enumerator must then emit
the complete path/orbit, response-rank, central-projector, fibre, deformation,
and provenance witnesses for a small independent checker; constructing a
carrier around the desired table would establish only a realization witness.
In particular, group order six supplies the averaging coefficient \(1/6\),
not a normalized projector trace of \(1/6\).  The certificate must distinguish
the physical matter representation, on which the quotient-center generator is
trivial and the projector is the identity, from any declared D10
center-label/transport representation with a one-dimensional invariant sector;
it must then derive the trace, source amplitude, and subtraction sign there.

\begin{definition}[D11 split-character certificate]\label{def:d11-split-certificate}
A D11 certificate consists of five finite obligations.
\begin{enumerate}[leftmargin=2em,label=\textup{DS\arabic*.}]
\item One strict source branch supplies the canonical D10 tuple and a frozen
pre-split D11 carrier with no Higgs/top target ancestry.
\item Exact quotient response has precisely two independent physical split
coordinates, for the top-Yukawa and Higgs-quartic directions.
\item Explicit carrier characters derive \(\rho_{HT}\), \(R_T\), \(R_H\),
\(\pi_y\), \(\pi_\lambda\), and the Jacobian coefficient \(-16/9\), rather
than storing those desired polynomials as carrier rules.
\item Oriented mismatch descent fixes the signs, canonical normalization, and
positive physical domain of the split.
\item An exhaustive admissible-deformation quotient proves rigidity, or an
independently justified target-free selector has a positive winner gap.
\end{enumerate}
\end{definition}

The existing D11 artifact verifies the downstream evaluation after these
objects are declared.  It does not emit Definition~\ref{def:d11-split-certificate};
DS1--DS5 therefore remain source assumptions.

\begin{theorem}[Conditional completion of the bosonic pole-mass
lane]\label{thm:conditional-boson-pole-completion}
Suppose a unique target-free source root emits
\((P_\star,\alpha_U(P_\star),E_\star)\); a quotient-transport theorem emits one
D10 electroweak repair; Definition~\ref{def:d11-split-certificate} emits
\((y_t,\lambda_H)\); and a frozen beta-function, threshold, matching, and
scheme packet transports these data uniquely to low energy.  Suppose further
that branch rigidity or a target-independent MAR selector removes all
admissible alternatives.  For each \(B\), let \(C_B\) be a declared contour
on a declared Riemann sheet, and let \(\Gamma_B^{\rm phys}(s,\xi)\) be the
source-closed BRST-complete physical inverse two-point block, including all
declared mixing fields after the Ward/Slavnov--Taylor projection.  Suppose
that, after analytic continuation to that sheet,
\[
D_B(s,\xi):=\det\Gamma_B^{\rm phys}(s,\xi)
\]
has exactly one simple physical zero \(s_B\) inside \(C_B\), no zero on
\(C_B\), and a certified Rouch\'e bound against a reference determinant on
\(C_B\).  Assume also the Nielsen identity
\(\partial_\xi D_B=C_B^{(\xi)}D_B\), nonzero physical residue, and a declared
uncertainty bound.  Then
\[
\sqrt{s_B}=M_B-\frac i2\Gamma_B,
\qquad M_B>0,\quad \Gamma_B\ge0,
\]
defines a unique source-separated triple \((M_W,M_Z,M_H)\), with the declared
uncertainty intervals, provided a hash-bound acyclic dependency record proves
that no measured mass or calibrated proxy is an ancestor of the outputs and a
prospective claim hash freezes the source artifacts, code, configuration,
branch selectors, scheme packet, and outputs before held-out comparison.
\end{theorem}

\begin{proof}
Picard--Lindel\"of gives unique RG transport on each threshold interval, and
deterministic matching composes those intervals.  The running-mass chart then
gives unique low-energy coordinates.  For each pole contour, the bound
\(|D_B-D_{B,0}|<|D_{B,0}|\) preserves the number of enclosed zeros by
Rouch\'e's theorem; simplicity gives the usual implicit-function stability
bound, and the Nielsen identity makes the pole gauge-parameter independent.
An invertible analytic field change multiplies the determinant by a nonzero
factor and therefore preserves its zero set.  Rigidity removes alternative source maps, and the acyclic
ancestor test makes each deterministic leaf a function only of the committed
source records. Uniform determinant convergence on the pole contours preserves
the isolated zero and forces the refinement zeros to converge. If a kernel
defect is bounded by \(\epsilon\), \(a=D'_B(s_0)\ne0\), and
\(|D''_B|\le K\), every radius satisfying
\[
 \epsilon<|a|r-\frac K2r^2
\]
encloses the unique displaced pole. The selected square-root branch propagates
this disk to mass and width bounds. Collision resistance makes a post-freeze
alteration a different claim identity. Composition gives the stated triple.
\end{proof}

A runtime DAG proves separation of the final computation from explicit target
inputs; it cannot by itself prove that a formula was historically invented
without target inspection. That stronger provenance statement requires
disclosure and a genuinely prospective freeze.

The D11 calculation evaluates
\(m_H=125.1995304097179\,\mathrm{GeV}\) on its declared running, matching, and
threshold surface, together with the companion top coordinate
\(m_t=172.3523553288312\,\mathrm{GeV}\).  These are back-solved from the
measured pair through the synchronization-scale scan, so they are a
target-anchored fit that validates the formula stack and carries no predictive
content; the target-free headline for this pair is the double-criticality
family (\(\lambda=0\), \(\beta_\lambda=0\) at one source scale), whose frozen
boundary-scale candidate gives \((m_H,m_t)=(125.77,\,172.63)\,\mathrm{GeV}\) at
two loops with \(m_H=125.72\,\mathrm{GeV}\) on the fit-free curve at the
measured top.  Even as a fit this D11 coordinate is a conditional downstream
result: it inherits the source-root, physical-scale, D10 selection, DS1--DS5,
RG/scheme, rigidity, provenance, uncertainty, and complex-pole gates.  For \(W/Z\), the
missing derivation of the quotient-path certificate is the central new
physical theorem.  No
full source-only \((M_W,M_Z,M_H)\) pole-mass prediction is promoted here.
The generic implication stack is complete at this point. The remaining work is
source emission, not another algebraic implication: the corpus does
not contain the factorized clock packet \(\mathfrak C_{\rm clk}\), the
independently weighted and rigid D10 carrier \(\mathfrak C_{10}\), the D11
split-character carrier \(\mathfrak C_{11}\), or the BRST-complete pole-kernel
packet \(\mathfrak P_{\rm pole}\). Numerical agreement, an inverse adapter, or
a hand-encoded path table cannot substitute for any of these four objects.

The scales fixed directly from \(P\) are
\[
M_U(P)=\frac{E_P}{e^{2\pi}}\,P^{1/6},
\qquad
E_{\mathrm{cell}}(P)=\frac{E_P}{\sqrt P}.
\]
The factor \(e^{-2\pi}\) is the same modular normalization used on the Lorentz/BW side, and \(P^{1/6}\) is the cell-area scaling relation carried by the present D10 implementation.

\paragraph{Golden-ratio equilibrium benchmark.}
The total/bulk/edge hierarchy has one exact self-similar balance point. Writing
\[
x(C):=\frac{S_{\mathrm{gen}}(C)}{S_{\mathrm{bulk}}(C)}
=
1+\frac{\langle L_C\rangle}{S_{\mathrm{bulk}}(C)},
\]
the exact self-similar balance condition
\[
\frac{S_{\mathrm{gen}}(C)}{S_{\mathrm{bulk}}(C)}
=
\frac{S_{\mathrm{bulk}}(C)}{\langle L_C\rangle}
\]
gives
\[
x=\frac{1}{x-1},
\qquad
x^2-x-1=0.
\]
Hence the unique positive equilibrium point is
\[
x=\varphi:=\frac{1+\sqrt5}{2}.
\]
Equivalently, the equilibrium-breaking order parameter
\[
A_\varphi(x):=x-1-\frac1x
\]
vanishes exactly at \(x=\varphi\). In that sense \(\varphi\) is the exact self-similar balance
point instead of a numerological comparison constant. The synthesis paper gives the outer/inner
closure relation that fixes the realized value of \(P\) by matching that detuning to the inner
electromagnetic observation scale emitted by the same cell. The role of the equilibrium theorem is
to explain why the realized value sits close to \(\varphi\). Exact equilibrium is too symmetric to
support durable records, structure, and dynamics, so the realized branch sits at a small
equilibrium-breaking detuning away from it. The technical question for the quantitative branch is
the size of that detuning together with the reduced-residual/root-control analysis of the printed
solve.

The one-dimensional internal variable solved on the D10 branch is the unified coupling \(\alpha_U\). For a trial value of \(\alpha_U\), define
\[
v(\alpha_U,P)
:=
E_{\mathrm{cell}}(P)\,
\exp\!\left(-\frac{2\pi}{\beta_{\mathrm{EW}}\alpha_U}\right).
\]
Run the one-loop D10 couplings from
\[
\alpha_1(M_U)=\alpha_2(M_U)=\alpha_3(M_U)=\alpha_U
\]
down to a scale \(\mu\) using
\[
\alpha_i^{-1}(\mu;\alpha_U,P)
=
\alpha_U^{-1}
+
\frac{b_i}{2\pi}\log\frac{M_U(P)}{\mu},
\]
with the printed one-loop coefficients \(b_i\). Let \(\mu_\ast=\mu_\ast(\alpha_U,P)\) be the fixed point determined by the tree-level \(Z\)-mass relation
\[
\mu_\ast
=
\frac{v(\alpha_U,P)}{2}\,
\sqrt{g_2(\mu_\ast)^2+g_Y(\mu_\ast)^2},
\qquad
\alpha_Y=\frac35\,\alpha_1.
\]
At that fixed point define
\[
t_2(\alpha_U,P)=4\pi^2\alpha_2(\mu_\ast;\alpha_U,P),
\qquad
t_3(\alpha_U,P)=4\pi^2\alpha_3(\mu_\ast;\alpha_U,P).
\]

Let \(\bar\ell_{\SU(2)}(t)\) and \(\bar\ell_{\SU(3)}(t)\) denote the nonabelian edge-entropy functions appearing in the D10 pixel constraint. The pixel-closure functional is
\[
\mathcal F(\alpha_U;P)
:=
\bar\ell_{\SU(2)}\!\bigl(t_2(\alpha_U,P)\bigr)
+
\bar\ell_{\SU(3)}\!\bigl(t_3(\alpha_U,P)\bigr)
-\frac{P}{4}.
\]
The printed D10 package takes \(\alpha_U(P)\) to be the branch value selected by solving
\[
\mathcal F(\alpha_U;P)=0.
\]
Only after that forward solve are the internal transmutation parameters fixed:
\[
t_U(P):=4\pi^2\alpha_U(P),
\qquad
t_{\mathrm{tr}}(P):=\frac{2\pi}{(N_c+1)\alpha_U(P)},
\]
and with them the downstream scale data
\[
t_2(P):=t_2(\alpha_U(P),P),
\qquad
t_3(P):=t_3(\alpha_U(P),P),
\qquad
v(P):=v(\alpha_U(P),P).
\]
Thus the branch runs from OPH input \(P\) to the internal transmutation data
\((t_U(P),t_{\mathrm{tr}}(P))\), then to the downstream local scale data
\((t_2(P),t_3(P),v(P))\), and only then to the low-energy couplings. It does not use measured
\(\alpha_i(m_Z)\) to infer those internal \(t\)-parameters.

Every quoted D10 electroweak number is downstream of this forward map. In particular, the
source-locked running-family anchor \(a_0(P)=\alpha_{\mathrm{em}}^{-1}(m_Z^2;P)\), the
declared electromagnetic transport family \(\alpha_{\mathrm{em}}^{-1}(q^2;P)\) and \(\sin^2\theta_W(q^2;P)\), and the frozen public
compare-only \(W/Z\) running/chart rows sit on the printed quantitative surface. The Thomson endpoint
\[
\alpha_{\mathrm{Th}}^{-1}(P)=\lim_{q^2\to0}\alpha_{\mathrm{em}}^{-1}(q^2;P)
\]
on the Ward-projected \(\U(1)_Q\) lane is declared through the
source-spectral reduction theorem and remains gated by the populated source
spectral measure payload, same-scheme remainder, and interval certificate. When compared with
observation, these rows check the printed implementation on the quantitative-closure branch recorded
in the theorem checklist. Their coordinates remain noncommensurate with PDG Breit--Wigner and
converted complex-pole coordinates until the full scheme map is supplied. The repository
carries a numerical witness for the outer/inner fixed-point closure, and the public endpoint
value is kept out of the closure solve.

\section{Relation to Holography and Existing UV Frameworks}

OPH belongs to the holographic family of ideas, but its primitive data are different from those used in asymptotic-boundary constructions. The distinction matters because several of the central claims of this paper, including the treatment of $\Lambda$, the handling of factorization, and the emergence of gauge structure, depend on it.

\subsection{Static-patch screen versus asymptotic boundary}

In asymptotic-boundary holography one starts from a dual theory at infinity and reconstructs the bulk inward. Here one starts from a finite-capacity screen equipped with a net of local patch algebras and reconstructs the effective bulk from overlap consistency. The primitive object is therefore a family of observer patches with nontrivial overlaps, not a single global boundary theory.

This shift has two technical consequences. First, subsystem factorization is treated from the beginning as a gluing problem with centers and sector labels. Second, the physical role of the horizon is local and operational: every observer has direct access only to a patch algebra, and global law is whatever survives reconciliation on overlaps.

\subsection{Positive $\Lambda$ and finite capacity}

The D5\(\to\)D6 cosmological-capacity stack is conditional: the null-modular reconstruction of Section~\ref{sec:gravity} determines the stress tensor only up to a metric term, so local null data do not fix $\Lambda$. The proposed global capacity target is the cosmic record-capacity fixed-point equation
\[
N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})
\]
together with the conditional de Sitter entropy identification
\[
N_{\mathrm{CRC}}=S_{\mathrm{dS}},
\]
\noindent the standard de Sitter entropy relation
\[
S_{\mathrm{dS}}=\frac{A_{\mathrm{dS}}}{4G}=\frac{3\pi}{G\Lambda},
\]
On that same branch this yields the dimensionless relation
\[
\Lambda_{\mathrm{CRC}}G_{\mathrm{geom}}=\frac{3\pi}{N_{\mathrm{CRC}}}.
\]
After the selected scale certificate supplies \(G_{\mathrm{geom}}=\ell_\star^2\), this is displayed as
\(\Lambda_{\mathrm{CRC}}=3\pi/(G_{\mathrm{geom}}N_{\mathrm{CRC}})\) and gives the static-patch
package
\[
S_{\mathrm{dS}}=N_{\mathrm{CRC}},
\qquad
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c},
\]
while the observed cosmic age is a downstream FLRW benchmark instead of an additional D6 theorem output. The compact paper is therefore formulated in a de Sitter-first language: the positive cosmological-constant capacity relation is tied to finite capacity instead of a deformation of a negative-$\Lambda$ starting point. A construction of \(F\), its fixed-point certificate, and proofs of CP-1--CP-3 remain required. The electroweak bridge coordinate \(N_{\mathrm{EW}}\simeq3.532\times10^{122}\) and the Planck--\(\Lambda\) comparison \(N_{\Lambda}\simeq3.313\times10^{122}\) differ by about \(6.6\%\) relative to \(N_{\Lambda}\). The evidence supports a conditional central-value mismatch; no established contradiction follows.
The input-free global closure target is the cosmic record-closure readback fixed point
\[
N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}}),
\qquad
F(N)=\operatorname{Cap}_{\mathrm{read}}
\bigl(\operatorname{Obs}(\operatorname{nf}(\mathfrak U_N))\bigr).
\]
The screen-normalized self-closure density is its count representation:
\[
\Pi(N)=|\Omega^{\mathrm{sc}}_N|e^{-N}.
\]
In differentiable form, the proposed stationarity map
\(T_\eta(N)=N+\eta\,d\log\Pi(N)/dN\) would have a unique stable fixed point under the required
derivative-sign certificate. The de Sitter entropy identification remains one of the theorem's
conditional hypotheses.

\subsection{Factorization, gauge structure, and the string sector}

The factorization problem of gauge theory and gravity is often treated as a technical nuisance. Here it is part of the architecture. Edge-center completion turns the collar center into a first-class object, and the entropy split
\[
S_{\mathrm{gen}}=\langle L_C\rangle + S_{\mathrm{bulk}}
\]
is then a structural consequence instead of an added prescription.

In the bosonic EFT branch, Theorem~\ref{thm:transport-from-gluing} supplies the strict zero-obstruction transport criterion and Theorem~\ref{thm:fixed-cutoff-bosonic-sector-category} constructs the fixed-cutoff bosonic collar-sector categories. Compact gauge reconstruction across cutoffs additionally requires the explicit compact-gauge refinement receipt; from it Theorem~\ref{thm:refinement-functor-fiber-descent} constructs the refinement functors and compatible forgetful fibers. Crossed-module data handle the genuinely noncentral fixed-cutoff branch separately when \(o^{(2)}_\Sigma\ne0\); the ordinary compact-group theorem does not. If \(o^{(2)}_\Sigma=0\), that branch enters the ordinary theorem only on representations with trivial residual \(G_\Sigma\)-holonomy. This obstruction calculus is a classification and routing theorem. On the receipt-certified branch, DR/Tannaka reconstruction yields some compact group \(G=\mathrm{Aut}_\otimes(\mathcal F)\) from the zero-obstruction transportable sector category. On the realized MAR-admissible branch with the explicit realized one-generation chiral matter plus one-Higgs package, minimal admissibility selects the Standard Model quotient. This differs sharply from approaches in which the gauge group is specified in advance.

The worldsheet relation is similarly reversed. The edge partition function
\[
Z_{\mathrm{edge}}(t)=\sum_R d_R^2 e^{-t C_2(R)}
\]
is the closed partition function obtained after gluing the open-edge weights
\[
p_R(t)\propto d_R e^{-tC_2(R)}.
\]

\begin{theorem}[OPH-to-2D-Yang--Mills edge partition theorem]\label{thm:edge-2dym}
Assume the compact-group heat-kernel branch supplied by the fixed-cutoff edge-sector law together
with the compact-group / Peter--Weyl lift used in the bosonic gauge lane, in the same
quadratic-Casimir normalization as the compact heat kernel. Equivalently, assume the open-edge
weights satisfy
\[
p_R(t)\propto d_R e^{-tC_2(R)}
\]
on a compact gauge group \(G\), and define the closed edge partition function by gluing the two
edge boundaries:
\[
Z_{\mathrm{edge}}(t)=\sum_R d_R^2 e^{-tC_2(R)}.
\]
Then:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2em]
\item the closed edge partition function is exactly the compact-group heat kernel at the identity,
\[
Z_{\mathrm{edge}}(t)=K_t(1);
\]
\item the same sum is therefore the standard compact-group two-dimensional Yang--Mills
heat-kernel partition function at identity, equivalently the closed-surface heat-kernel partition
sum on that branch;
\item the Chapman--Kolmogorov law for \(K_t\) is the corresponding collar-sewing rule for the OPH
edge partition.
\end{enumerate}
Thus the OPH edge-sector partition reorganizes exactly into the two-dimensional Yang--Mills
heat-kernel form before any large-\(N_{\mathrm{edge}}\) continuation is invoked.
\end{theorem}

\begin{proof}
The fixed-cutoff edge-sector theorem gives the heat-kernel weights \(d_R e^{-tC_2(R)}\) on the
compact-group branch. Gluing the two edge boundaries contributes a second factor of \(d_R\), so the
closed partition function is the displayed sum. Peter--Weyl identifies
\[
\sum_R d_R \chi_R(g)e^{-tC_2(R)}
\]
with the compact-group heat kernel \(K_t(g)\), and evaluating at the identity \(g=1\) gives
\[
K_t(1)=\sum_R d_R \chi_R(1)e^{-tC_2(R)}=\sum_R d_R^2 e^{-tC_2(R)}=Z_{\mathrm{edge}}(t),
\]
since \(\chi_R(1)=d_R\). The Chapman--Kolmogorov law for \(K_t\) is exactly the semigroup gluing
law, so it gives the collar-sewing rule on the same branch.
\end{proof}

\paragraph{Scope boundary.}
The imported inputs are exactly the fixed-cutoff edge heat-kernel / Casimir law, the compact
gauge-group / Peter--Weyl lift, the quadratic-Casimir heat-kernel normalization on that lift, and
the Peter--Weyl heat-kernel identity. The external content is any large-\(N_{\mathrm{edge}}\)
regime, the Gross--Taylor dictionary on that regime, and every further critical-string
ingredient. The theorem above proves the OPH-to-2D-Yang--Mills partition reorganization itself; it
does not by itself produce a worldsheet genus expansion. The four-dimensional compact-gauge
repair-gap theorem is the separate support-visible repair-dynamics result in
Theorem~\ref{thm:oph-yang-mills-gap}.

\begin{theorem}[Criterion for a controlled large-$N_{\mathrm{edge}}$ worldsheet effective description]\label{thm:worldsheet-largeN}
Assume Theorem~\ref{thm:edge-2dym} and a large-$N_{\mathrm{edge}}$
realization of the compact-group heat-kernel branch, with \(N_{\mathrm{edge}}\neq N_c=3\), for
which the 't Hooft-style variable
\[
\tau:=tN_{\mathrm{edge}}
\]
is kept in a compact interval \(I\subset (0,\infty)\). Suppose that for every truncation
order \(G\ge 0\) there exist coefficient functions \(F_g:I\to\mathbb R\) and constants
\(C_{G,I}\) such that
\[
\log Z_{\mathrm{edge}}\!\left(\frac{\tau}{N_{\mathrm{edge}}}\right)
=
\sum_{g=0}^{G} N_{\mathrm{edge}}^{2-2g} F_g(\tau)
+
R_{G+1}(\tau,N_{\mathrm{edge}})
\]
with
\[
\bigl|R_{G+1}(\tau,N_{\mathrm{edge}})\bigr|
\le
C_{G,I}N_{\mathrm{edge}}^{-2G}
\qquad(\tau\in I).
\]
Then this branch defines a controlled theorem-level worldsheet effective description of the edge
dynamics, with control parameters \(N_{\mathrm{edge}}^{-2}\), the fixed-\(\tau\) window \(I\),
and the truncation order \(G\).
\end{theorem}

\begin{proof}
Theorem~\ref{thm:edge-2dym} puts the edge partition function on the compact-group heat-kernel /
two-dimensional Yang--Mills surface. On that surface, the standard Gross--Taylor dictionary reads
a genus expansion of the displayed form as a closed-worldsheet rewriting of the free energy. The
stated large-\(N_{\mathrm{edge}}\) assumption supplies that expansion on the fixed-\(\tau\) window
\(I\), together with an explicit truncation bound. Therefore the worldsheet rewriting is
controlled by the displayed parameters \(N_{\mathrm{edge}}^{-2}\), \(I\), and \(G\). The
statement is only an effective description on the declared branch: it does not by itself construct
a critical worldsheet CFT, derive modular invariance, worldsheet supersymmetry, anomaly
cancellation, GSO projection, or full massless-spectrum matching.
\end{proof}

\paragraph{External inputs.}
The criterion theorem uses the declared large-\(N_{\mathrm{edge}}\) regime and the imported
Gross--Taylor large-\(N\) worldsheet dictionary for two-dimensional Yang--Mills. The external
content is the existence of the large-\(N_{\mathrm{edge}}\) sequence, the fixed-\(\tau\) window on
which the genus expansion holds, and the uniform remainder control. Any further lift to critical
superstring structure requires worldsheet supersymmetry, critical dimension, modular invariance,
anomaly cancellation, GSO projection, and full massless-spectrum matching beyond the present
declared continuation theorem.

\begingroup
\footnotesize
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}p{0.32\textwidth}>{\raggedright\arraybackslash}p{0.34\textwidth}@{}}
\toprule
Feature & Asymptotic-boundary holography & OPH \\
\midrule
Primitive data & Boundary theory at infinity & Finite-capacity screen with observer-patch net \\
Factorization across cuts & Subtle and often indirect & Explicit edge-center completion with central labels \\
Status of $\Lambda$ & External background datum & Conditional global target after local null reconstruction; construction of \(F\), its fixed-point certificate, CP-1--CP-3, and the identification \(N_{\mathrm{CRC}}=N_{\mathrm{scr}}\) remain open \\
Gauge group & Usually specified as part of the model & Reconstructed from edge sectors, then fixed on the realized MAR branch \\
String sector & Fundamental dual description & Controlled large-$N_{\mathrm{edge}}$ worldsheet effective description of edge dynamics on the stated branch \\
\bottomrule
\end{tabular}
\endgroup

\section{Support Levels and Falsifiability}\label{sec:claim-tiers}

The recovered core is
\[
(D1\text{--}D5)\cup(D7\text{--}D9),
\]
namely the relativity chain together with the realized Standard Model structural chain. D6 is the
conditional global-closure target for that Einstein branch, with \(F\), its fixed-point certificate,
and CP-1--CP-3 open. D10 is the integrated quantitative-closure branch, and D12 collects
phenomenological continuations.

\subsection{Prediction check by support level}

\paragraph{Prospective-evidence ledger.}
The evidence ledger records zero discriminating frozen-prospective hits. The \(S_3\)
six-state hardware benchmark reproduces a programmed ratio also predicted by ordinary quantum
mechanics, so it carries no OPH discrimination weight. The repository first records its code,
results, and documentation together and therefore does not establish a pre-run freeze. The
electroweak two-loop and
pole-packet computations use known \(W/Z\) data to check declared prescriptions. Their status is
known-data prescription checks, with no prospective prediction. The implemented transport and pole
maps are hybrid or partial and lack a full scheme conversion. Their adverse pulls therefore
constrain those prescriptions inconclusively and do not establish a universal \(1\)--\(2\%\) defect
in D10.

\begingroup
\footnotesize
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.20\textwidth}>{\raggedright\arraybackslash}p{0.31\textwidth}>{\raggedright\arraybackslash}p{0.39\textwidth}@{}}
\toprule
Tier & Representative outputs & What would actually falsify the tier \\
\midrule
\endhead
\bottomrule
\endfoot
Phase I recovered core (Theorem~\ref{thm:master}; D1--D5, D7--D9) & Confluence of overlap repair, Lorentz kinematics, the three-dimensional observer-facing spatial chart, the Jacobson-type Einstein branch in the stated scaling regime, receipt-conditional compact gauge reconstruction in the bosonic branch, the controlled four-dimensional Euclidean Yang--Mills form and compact-gauge repair-gap mechanism under the declared compact-gauge continuum/transfer assumptions, the realized Standard Model quotient chain on the explicit realized matter package, the exact hypercharge lattice on that realized matter package, the realized color triplet \(N_c=3\), the generation count \(N_g=3\), and the product-group consequence of no gauge-mediated proton decay; the Standard Model content is conditional on the MAR admissibility-clause inputs, and realized-branch nonemptiness is open & A mathematical failure in the derivation chain, loss of the Yang--Mills form or exact repair-gap branch conditions, or data that require a different realized gauge quotient, different realized hypercharges, a different color or generation count on the admissible branch, or gauge-mediated proton decay \\
Phase II global self-closure target (D6) & Conditional consequences of a cosmic record-closure fixed point \(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})\): \(\Lambda_{\mathrm{CRC}}\ell_\star^2=3\pi/N_{\mathrm{CRC}}\), \(S_{\mathrm{dS}}=N_{\mathrm{CRC}}\), and, after the selected OPH scale certificate, \(\Lambda_{\mathrm{CRC}}=\frac{3\pi}{G N_{\mathrm{CRC}}}\), \(r_{\mathrm{dS}}=\sqrt{3/\Lambda_{\mathrm{CRC}}}\), and \(t_\Lambda=r_{\mathrm{dS}}/c\). The formula \(F(N)=\operatorname{Cap}_{\mathrm{read}}(\operatorname{Obs}(\operatorname{nf}(\mathfrak U_N)))\) and count representation \(N_\star=\operatorname{MAR}\arg\max_N(\log|\Omega^{\mathrm{sc}}_N|-N)\) specify the target. The map, fixed-point certificate, CP-1--CP-3, and entropy identification are open; any retained capacity-level neutrino side estimate is legacy bookkeeping; the observed cosmic age is a downstream FLRW benchmark & A constructed readback map that lacks the required fixed point, or failure of the conditional capacity relation after its premises are discharged, would falsify D6 without erasing the recovered core \\
Phase II quantitative-closure branch (D10) & forward transmutation data \(\alpha_U(P)\), \(t_U(P)\), \(t_{\mathrm{tr}}(P)\), pixel-closure gauge-coupling consistency, \(\alpha_i(m_Z)\), the declared anchor \(a_0(P)=\alpha_{\mathrm{em}}^{-1}(m_Z^2;P)\), and the declared electroweak transport family \((W,Z,\alpha_{\mathrm{em}}^{-1}(q^2),\sin^2\theta_W(q^2),v)\). Four endpoint coordinates are kept separate: the source/root witness \(136.9948351646\ldots\), the mixed-provenance no-hadron diagnostic \(137.0359595008\ldots\), the OPH-plus-empirical hadron-closure result \(136.2636589431\) on \([136.1583832834,136.3690975240]\), and the measured Thomson endpoint \(137.035999177(21)\). Converged precision-100 reruns supersede the printed witness tail beyond digit 9 (certified \(136.994835177413\ldots\); CL-6) and record the certified gauge-width-map fixed point \(137.035660136946577\ldots\) (CL-2). Both certified roots belong to incomplete declared maps and have no physical Thomson-endpoint status. The exploratory V1 grid emitted \(S_{\mathrm{hadronic}}\in[0.5578,1.0543]\), which contains the compare-only value \(0.8954\) but spans \(1.17\times10^8\) historical v2 tolerance widths; v3 registers no active decision threshold. V1 was not target-blind: target constants were embedded in its source, the directing session had target access, and its emitter used \(P=1.6309720959\ldots\) while the target used \(P=1.6309682094\ldots\). It also mislabeled the residual coordinate \(0.0414658\ldots\) as the required total payload; the total endpoint target is \(8.7280337\ldots\). V1 is therefore exploratory and has no promotion weight. The \(137.0359595008\ldots\) packet stays on record as a display packet only. The empirical row imports \(e^+e^-\to\mathrm{hadrons}\) data and does not promote a source-only endpoint. Its interval misses the measured endpoint and requires a same-scheme anchor correction of \([0.6485541111,0.8547920666]\). The 24-register count does not determine the nonconstant OPH-QCD hadronic backend; its two-current spectral measure is only the running-\(\alpha\)/HVP marginal, while HLbL and rare-decay rows require higher-point and transition spectral sectors & Failure of the completed \(A_T(P)\) interval root or integrated quantitative closure once \(P\) and the printed running/matching/scheme conventions are imposed, or failure of the explicit OPH-QCD quotient ensemble, source QCD parameter map, Ward current ledger, two-current/higher-point/transition spectral exports, same-scheme remainder, no-target-leak dependency record, empirical source disclosure, and interval-certificate records \\
Phase III phenomenological continuations (D12 and beyond) & Flavor ans\"atze, charged-lepton continuation ans\"atze beyond exact centered readback, \(H^3\) record-worldline stitching certificates, texture branches, the target-informed weighted-cycle / Majorana-holonomy neutrino candidate, further neutrino mass/mixing refinements, dark-sector response laws, early compact-object/JWST source-release audit lanes, conditional screen-spectrum and CMB/inflation-replacement kernels, \(H_0/S_8\) and growth continuations, heuristic baryogenesis continuations, proton-spin bookkeeping, proton-lifetime estimates beyond the gauge-channel exclusion, black-hole spectroscopy templates, physical black-hole evaporation/ringdown bridge programs, controlled large-\(N_{\mathrm{edge}}\) string/worldsheet effective descriptions, conjectural critical-superstring extensions, and other downstream phenomenology & The weighted-cycle candidate fails the NuFIT 6.1 normal-ordering \((\sin^2\theta_{23},\delta_{\mathrm{CP}})\) profile: \(\Delta\chi^2=20.12\) with the tabulated atmospheric likelihood and \(18.44\) without it, above the two-parameter \(3\sigma\) contour value \(11.83\)~\cite{nufit61}. A separate basis audit finds that the claimed shared-basis recovery defined \(U_{\nu,\mathrm{shared}}=U_eU_{\mathrm{wc}}\), making \(U_e^\dagger U_{\nu,\mathrm{shared}}=U_{\mathrm{wc}}\) an identity rather than an independent flavor derivation. The stored charged-lepton source is open and has a nearly degenerate singular spectrum, so it does not define a stable physical \(U_e\). The convention scan excludes only row, column, and orientation relabelings of the stored candidate; it does not derive or exhaust source-side physical basis placements. This rejects that candidate, without falsifying the recovered core. Other continuation failures retract only their corresponding branches \\
\end{longtable}
\endgroup

\paragraph{Hadronic target-contract correction.}
The D10 summary above is superseded on one point: V1's scorer used the correct
CL-1 total endpoint coordinate, but historical target v2 itself equates that
total with the residual \(0.0414658610\ldots\). V2 also assigns one scalar to
two inequivalent maps. At the registered point the CL-1 total target is
\(8.7280337037\ldots\); CL-2 adds \(\alpha_U(P)\) and therefore has total
target \(8.6869093675\ldots\). Their zero-electroweak effective-\(S\)
diagnostics are \(0.8954001326\ldots\) and \(0.8870666249\ldots\),
respectively. Historical v2 remains immutable provenance but cannot score a
verdict. The v3 corrective contract separates coordinate and map types but is
a permanently inactive post-target-access erratum scaffold. A detached
successor must bind a complete method frozen before genuinely withheld data,
or use an audited clean-room producer with no target access, and must
preregister its uncertainty, maximum-width, and three-way decision policy. A
future producer must then emit a target-blind transport function or certified
enclosure over \(P\), after which CL-1 and CL-2 are solved and judged
independently.

\begin{proposition}[No semantic promotion by relabeling]\label{prop:no-semantic-promotion}
Let \(X_r\) be a finite OPH branch with declared quotient state, finite records,
and branch-local diagnostic or calibration fields \(Y_r\). Suppose a proposed
physical observable \(O^{\mathrm{phys}}_r\) is obtained only by renaming \(Y_r\)
or by applying a deterministic post-processing map \(g(Y_r)\), with no
additional source-separated carrier, calibration map, detector or readout
algebra, error budget, negative controls, and frozen validation target. Then
\(O^{\mathrm{phys}}_r\) has the same information ancestry as \(Y_r\) and is not
an independent physical observable. It may be recorded only as a finite theorem,
diagnostic, or calibration display. Promotion to a physical claim requires a
bridge object whose source roots, readout map, residual ledger, and controls are
independent of the target physical label being asserted.
\end{proposition}

\begin{proof}
A deterministic relabeling or post-processing map does not add new information,
new source roots, or a new operational readout. Every dependency of
\(O^{\mathrm{phys}}_r=g(Y_r)\) therefore factors through the same finite records
and quotient data that produced \(Y_r\). Any leakage, calibration circularity, or
target-derived value present in \(Y_r\) is inherited by the relabeled object.
Physical promotion asserts more than finite equality inside the regulator: it
asserts agreement with an independently specified operational or continuum
quantity. That assertion requires extra data, namely a source-separated bridge,
a declared readout/calibration map, residual bounds, negative controls, and a
frozen target. Without those objects, the proposed observable is only another
name for the original finite diagnostic or calibration display.
\end{proof}

Consequently, a capacity count is not an exterior mass without an independent
energy readout; an append-only archive is not radiation without a source,
propagation, and detector channel; a finite repair spectrum is not a physical
normal-mode spectrum without a continuum operator and readout bridge; and an
exact finite reconstruction threshold is not a Page time without a physical
radiation entropy curve and exterior time calibration.

Phase I is the recovered-core level, Phase II is adjacent but non-core, and Phase III contains phenomenological continuations. The D6 row permits the conditional holonomy reading of FLRW flatness in Lemma~\ref{lem:flrw-curvature-holonomy}; it does not support an inflation replacement, CMB likelihood, or high-\(H_0\) branch. The conditional screen-spectrum theorem supports the declared finite-screen branch as a MaxEnt Gaussian screen covariance after the quotient-ensemble selector, scalar-readout, positive repair-operator, and fixed expected quadratic release-energy evidence pass; the tilt, scalar release amplitude, primordial radial lift, and physical TT/TE/EE spectra require their separate finite-source, source-provenance, lift, Boltzmann, and likelihood gates. Low-\(H_0\), Planck-like \(S_8\) dark/anomaly rows are diagnostic continuation checks unless a finite covariant collar-packet parent emits the homogeneous anomaly load, perturbative source functions, recipient stress and exchange-current closure for any nonzero exchange branch, active-fiber and physical-clock evidence for any stated \(\Gamma_{\mathrm{rec}}\), a first-principles dependency DAG, pooled global reducers, and frozen source/calculation/statistical hashes before fitting cosmological data. On the exact finite packet-closed quotient branch, the fixed-cutoff consensus surface does define an affine OPH closure map: the schedule-independent settled-form projection pushes forward to a continuous idempotent self-map of the finite packet simplex, its image is exactly the settled-form simplex, and its fixed points are exactly the packets supported on quotient settled forms. That closure statement is not an ensemble selector; physical probabilities require the quotient base measure/action or intrinsic projective prior stated near Axiom~\ref{ax:maxent}. That finite branch supplies grammar for the proposed cosmic readback map \(F\) and self-closing observer settled-form density \(\Omega^{\mathrm{sc}}_N\). The formula and screen-normalized density specify the D6 target. They do not construct \(F\) or its fixed point; interpretive strange-loop discussions and the full habitat theorem sit outside these levels and are not needed for the finite packet-quotient fixed-point statement.

The dark-cosmology abundance selector in
\texttt{cosmology/oph\_dark\_matter\_paper.tex} is an application of the
quotient-ensemble surface: it is the finite expectation of a quotient-visible
load observable under a declared source release law.

\begin{remark}[Round-one public-data comparison ledger]\label{rem:round-one-cosmology-ledger}
The first frozen comparison audit separates encouraging conditional checks from
excluded extrapolations and invalidated diagnostics.  None of the following
rows promotes a D12 continuation into the recovered core.
\begin{center}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.22\textwidth}>{\raggedright\arraybackslash}p{0.29\textwidth}>{\raggedright\arraybackslash}p{0.39\textwidth}@{}}
\toprule
Surface & Numerical comparison & Claim boundary \\
\midrule
Analytic screen tilt &
\(n_s=1-P_\star/48=0.9660214956\), or \(+0.267\sigma\) relative to the Planck-2018 summary \(0.9649\pm0.0042\); a conventional CAMB transfer with one profiled amplitude gives \(\chi^2/N_{\rm bin}=0.954498\), versus \(0.944496\) for the Planck-like baseline over 83 PR3 TT bins &
Positive conditional arithmetic/transfer check.  The \(P_\star/48\) reserve-to-RG identity, scalar release amplitude, radial lift, conventional background inputs, and official likelihood remain open or imported.\\
Settled-galaxy RAR &
The fixed conditional \(\mathbb Z_6\) branch gives aggregate RMS \(0.132834\) dex on 2,693 public RAR rows, versus \(0.132947\) dex at the same-data effective-scale optimum &
Positive retrospective fixed-formula check, not a blind prediction: \(a_{0,\rm OPH}\) is a benchmark and the exact collar coefficient is conditional; shared galaxy nuisances are not profiled in this aggregate statistic.\\
BTFR &
An error-aware orthogonal fit gives slope \(3.84565\pm0.08582\); the asymptotic OPH slope \(4\) is \(1.80\sigma\) high and lies in the published systematic range \(3.5\)--\(4.0\) &
Positive slope check.  At \(100\,\mathrm{km\,s^{-1}}\) the fixed \(\mathbb Z_6\) normalization is \(0.13476\) dex high, a \(6.47\sigma\) statistical-only pull before global mass-to-light, distance, inclination, and sample systematics.  The BTFR table overlaps SPARC.\\
Cassini external field &
Universal application of the same static equation gives \(Q_2=3.62018\times10^{-26}\,\mathrm{s^{-2}}\) on the conditional \(\mathbb Z_6\) branch, a \(19.22\sigma\) fixed-input residual against the published Cassini summary &
Strong exclusion of the natural universal/full-source static extension.  The current paper scopes the law to old settled galaxies and has no Solar-System applicability theorem; a source-derived applicability, screening, coarse-graining, or transport gate is therefore required.\\
Simulation-clock TT and compressed cosmology &
The archived finite-clock comparison reports total diagonal
\(\Delta\chi^2=+39.26\) versus the baseline; the subsequent covariant rerun
used a reducible transition chain with \(\lambda_2=1\) that the old readiness
gate incorrectly accepted. The archived compressed row used a rejected
neutrino input and no attached covariance &
Invalid for physical scoring. Reducible or periodic chains now fail the
finite-clock certificate gate, and the compressed row remains retracted. No
OPH mathematics verdict follows.\\
\bottomrule
\end{tabular}
\end{center}
The comparison code, public table hashes, run receipts, and no-data-use labels
are maintained in the OPH-FPE comparison bundle.  In particular, the good
analytic \(P_\star/48\) row must not be substituted for the distinct
simulation-clock row after inspecting the latter's residuals.
\end{remark}

The gamma-ray morphology continuation obeys the same boundary. An OPH gamma
component is not an arbitrary residual in a photon map. It is admissible only as
a frozen forward projection
\[
I_{\rm OPH}=\Pi_{\gamma,r}(\mathfrak G_{\gamma,r})
\]
from a proof-carrying gamma source artifact, with a declared quotient/source
law, transported-stress or boundary-record route, photon-response bridge,
line-of-sight projection, count-space instrument operator, foreground and
alternative-template registry, no-data-use DAG, positivity gate, identifiability
test, held-out validation, cross-tracer check, and null tests. Transported
anomaly stress does not directly emit gamma rays on the neutral branch unless a
separate electromagnetic-current theorem is supplied; it can only modulate
ordinary photon-production channels or enter through a boundary-record
projection. Thus gamma rows are D12 morphology tests, not excess-power claims.

\begin{proposition}[Boltzmann-transfer and frozen-likelihood gate]\label{prop:compact-boltzmann-frozen-gate}
A scalar dark/anomaly parent that emits only
\(\rho_A(a)\), \(\rho_{A,\mathrm{eq}}(a)\), and \(B_A(k,a)\) does not determine a
physical TT/TE/EE, BAO, lensing, or growth prediction. A physical OPH
dark/anomaly source for an Einstein--Boltzmann solver must instead be emitted by
a finite covariant collar-packet parent
\[
\mathcal P_r[X,g]=(C_r,Z_r,A_r,R_r,G_r,\pi_r[X],L_r[X],Q_r,D_r),
\]
where the finite packet states \(Z_r\) split the anomaly and any recipient
stress channels, \(\pi_r\) is the finite equilibrium packet functional, \(L_r\)
is the repair generator, \(Q_r\) records the energy-momentum reaction channels,
and \(D_r\) records any causal auxiliary response. Its source certificate must
first declare whether the local source is fixed-reference anomalous modular
energy or nonlinear CMI stress. The local BW branch fixes the coefficient
\(15/(8\pi^2)\) for a source variable proved to equal the anomalous local
modular energy. Identifying finite collar CMI with that source additionally
requires the D12 CMI-to-anomalous-modular-source matching theorem or an
explicit continuation hypothesis with a residual ledger; raw
\(I(A:D\mid B)\) is otherwise a recoverability diagnostic. The same certificate
must
derive
\[
\rho_A,\quad B_A,\quad \Gamma_{\mathrm{rec}},\quad
w_A,\quad c_{s,A}^2,\quad \sigma_A,\quad Q_A^\mu
\]
from that same parent, satisfy exact total stress-energy closure, build \(B_A\)
from the anomaly-frame baryon density \(n_b^{(A)}=-u_{A\mu}J_b^\mu\), pass
finite domain-of-dependence, subluminal-characteristic, retarded-response,
stability, local-frame, quotient-invariance, gauge-invariant perturbation, and
refinement-convergence checks, and recover the CDM branch when exchange,
pressure, sound speed, and anisotropic stress are switched off. If the exchange
branch is nonzero, an explicit recipient stress tensor and equal-and-opposite
exchange current are hard parts of the certificate. A transition-matrix spectral number remains
\(\gamma_{\mathrm{repair\ step}}\) until the physical clock, active fiber, and
common-parent response pole have been certified. The likelihood stage is
physical only after immutable source, solver, and likelihood hashes are frozen
before the data comparison.
\end{proposition}

\begin{proof}
The scalar triple \((\rho_A,\rho_{A,\mathrm{eq}},B_A)\) omits the fluid closure
data \(w_A,c_{s,A}^2,\sigma_A\), the covariant exchange current \(Q_A^\mu\), the
repair rate, and the recipient sector required by the Bianchi identity when
energy is transferred. Different packet dynamics can share the same scalar
tables while producing different metric sources or different gauge-fixed
perturbation variables. The CMI functional also has zero first variation at an
exact Markov reference, while fixed-reference modular energy is generically
linear, so raw CMI cannot be substituted for the BW modular source without the
separate matching theorem. A finite covariant packet parent supplies the missing
stress moments and their reaction channels; total conservation then enforces
\(\sum_z\nabla_\mu T_z^{\mu\nu}=0\) at the source level, and the anomaly-frame
baryon density removes the gauge-fixed-density ambiguity in \(B_A\). Frozen
hashes are the no-data-use firewall for the transfer and likelihood stage. Thus
diagnostic CAMB/CLASS curves or compressed likelihood rows become physical OPH
predictions only with those receipts.
\end{proof}

\begin{proposition}[CMB source provenance and pooled-reducer gate]\label{prop:compact-cmb-source-provenance-gate}
Promoting any of
\[
\eta_R,\quad \gamma_{\mathrm{repair\ step}}\hbox{ or certified }\Gamma_{\mathrm{rec}},
\quad A_\zeta,\quad q_{\mathrm{IR}},
\quad \ell_{\mathrm{IR}},\quad B_A(k,a),\quad \rho_A(a),\quad N_{\mathrm{CRC}}
\]
requires an immutable source-provenance certificate.  The certificate is a
finite dependency DAG whose nodes record the source report, source hash,
parents, no-CMB-data flag, and measurement-use flags for each promoted
quantity.  A node that simultaneously asserts no CMB data use and a
measurement fit, for example \(\texttt{no\_cmb\_data\_used=true}\) and
\(\texttt{fit\_to\_Planck=true}\), fails closed.  Nonlinear estimators for
tilt, amplitude, inverse precision, rank, condition number, isocurvature
leakage, \(B_A\), \(\rho_A\), and \(\Gamma_{\mathrm{rec}}\) are evaluated only
after additive sufficient statistics have been pooled globally with validated
units, coordinate grids, coverage, duplicate policy, interpolation policy, and
covariance; a transition diagnostic remains \(\gamma_{\mathrm{repair\ step}}\)
until the active-fiber, physical-clock, and common-parent response receipts
pass.  Shard-local nonlinear averages do not satisfy the gate.
\(N_{\mathrm{CRC}}\) is treated only as the conditional D6 target unless a constructed readback map,
fixed-point certificate, and additive capacity schema prove the required closure and disjoint
coverage before any summation.
Official likelihood and CDM-limit checks are global checks; shard-local
\(\texttt{any()}\) rollups do not promote a physical CMB input contract.
\end{proposition}

\begin{proof}
The listed quantities are inputs to later primordial or Boltzmann claims.  If
one of them is selected by a measurement-aware fit, a shard-local nonlinear
average, or an additive count with overlapping coverage, the value fails the
source-readback contract.  A dependency DAG fixes the
measurement-firewall order, and pooled sufficient statistics are the invariant
objects under repartition of the run.  Therefore only the DAG-plus-pooling
certificate is stable under public re-execution; all other rows remain
diagnostics.
\end{proof}

\begin{proposition}[First-principles screen-to-primordial gate]\label{prop:compact-source-only-primordial-gate}
The modular repair scalar \(R_C=I(A:D|B)\) is a repair/readback defect, not the
geometric curvature perturbation.  On a source-stress-complete rank-one
normal-form branch, the geometric scalar is the relational volume readout
\[
q_\zeta=\frac13\log(J_X/\bar J_X)
=\frac13\log\frac{dV_h}{a^3dV_{\bar h}},
\]
equals uniform-total-density curvature after monopole and dipole removal.  If
the total effective pressure is barotropic on that branch, then the exact
curvature covector obeys
\[
\mathcal L_u\zeta_a
=
-\frac{\Theta}{3(\rho+p_{\rm eff})}\Gamma_a^{\rm eff}
=0 .
\]
The source clock is the unique future-oriented timelike eigenline of the total
stress tensor when \(\rho+p>0\), the line is nondegenerate and hypersurface
orthogonal, and the density is monotone.  Primordial promotion additionally
requires source-stress closure, a freeze-tail certificate, the scalar
refinement map \(R_r=J_{r+1,r}C_{r+1,r}\), simple isolated leading nonconstant
eigenvalue with certified gap, conformal precision intertwiner, spatial
curvature branch receipt, adiabatic growing-mode receipt, source-side
isocurvature and phase-coherence bounds, a declared radial prior with the
correct flat or curved shell kernel, the radial null-space report, and a
forward-projection residual certificate.  The finite code must certify these
quantities from source artifacts; it may not choose the eigenmode, sign,
dimension, amplitude, or curvature branch by optimizing CMB data.  Without those
receipts, \(A_s\), \(n_s\), running, isocurvature, phase coherence, and
TT/TE/EE spectra are Phase III conditional outputs outside recovered-core
prediction claim.
\end{proposition}

\subsection{Recovered-core discriminators}

Once the support boundary is made explicit, the sharpest discriminators are the ones that do not depend on auxiliary flavor, dark-sector proposals, heuristic baryogenesis continuations, or string ans\"atze.

\subsubsection{Realized Standard Model gauge structure}

On the realized MAR-admissible branch, this paper fixes
\[
G_{\mathrm{phys}}=
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6},
\qquad
N_g=3,
\qquad
N_c=3,
\]
with the exact one-generation hypercharge lattice. Here the count statements are internal to the same realized branch: the D8 minimal coupled-carrier theorem stack fixes the color triplet and hence \(N_c=3\); CKM phase counting and weak-sector asymptotic freedom then bound \(N_g\); MAR fixes the smallest realized value \(N_g=3\); and Witten parity is only a consistency check on the resulting triplet-doublet package.
\[
Y_Q=\frac16,\qquad
Y_L=-\frac12,\qquad
Y_u=-\frac23,\qquad
Y_d=\frac13,\qquad
Y_e=1,\qquad
Y_H=\frac12.
\]
Evidence that the realized low-energy gauge structure or realized hypercharges differ from these values would directly contradict the recovered core.

\subsubsection{Known-force and charge coverage}

This paper does not leave any known long-range or Standard Model gauge force unassigned. The coverage is explicit by tier:
\begin{itemize}[leftmargin=2em]
\item \textbf{Gravity}: D3--D5 recover Lorentz kinematics, the three-dimensional observer-facing spatial chart, the null-stress bridge, and the Jacobson-type Einstein branch, with \(T_{ab}\) as the stress-energy source. D6 is the conditional global-capacity target for the remaining metric term. On the additional pure Einstein--Hilbert/Minkowski action branch, Theorem~\ref{thm:carrier-mode-gates} gives two classical transverse-traceless modes; a graviton state requires the quantum-particle receipt.
\item \textbf{Strong interaction}: D8--D9 recover the \(\SU(3)_c\) color factor, the color triplet \(N_c=3\), quark color triplet/antitriplet assignments, and the eight gluon generators \((8,1,0)\). Confinement and hadron spectra are separate infrared QCD questions, not missing gauge-charge assignments.
\item \textbf{Weak interaction}: D8--D9 recover the \(\SU(2)_L\) weak doublet structure, the one-Higgs branch, and the charged weak carriers \(W^\pm\) from the broken \(\SU(2)_L\) generators. D10 supplies the quantitative running/matching readout for \(v\) and the \(W/Z\) running/chart comparison rows.
\item \textbf{Hypercharge and electromagnetism}: Theorem~\ref{thm:hypercharge}, Proposition~\ref{prop:z6}, and Corollary~\ref{cor:electroweak-force} fix the \(\U(1)_Y\) lattice, the unbroken generator \(Q=T_3+Y\), integer charge for color singlets, and the electromagnetic connection label \(A_Q\). Corollary~\ref{cor:maxwell-sector} gives the Maxwell equations \(dF_Q=0\) and \(d*F_Q=g_Q^2*J_Q\) only after the low-energy Maxwell action is supplied. Theorem~\ref{thm:carrier-mode-gates} then gives two classical transverse modes; a photon particle requires Corollary~\ref{cor:conditional-carrier-particles}. The empirical Thomson row is a D10 endpoint evaluation with external hadron data; source-only endpoint closure remains open.
\end{itemize}

\subsubsection{Product-group corollary}

Because the realized gauge structure is a product group up to the finite central quotient fixed above, its connected adjoint has no mixed \((3,2,\pm 5/6)\) generator or connection component. This algebraic statement is not a particle-spectrum claim. Hence
\[
\tau_p^{(\mathrm{gauge})}=\infty
\]
for gauge-mediated proton decay. Observation of proton decay specifically attributable to gauge-boson exchange would therefore falsify the realized product-group branch.

\subsubsection{Relativity branch}

The relativity claim is sharp about its scope: given the support-visible geometric-modular theorem and the stated null-bridge conditions in the intended scaling regime, and the same realized cap-label-preserving MaxEnt family satisfying the derived fixed-cap generalized-entropy stationarity theorem for admissible fixed-cap MaxEnt variations on that branch, this paper predicts Lorentz kinematics on the screen, the three-dimensional observer-facing spatial chart, and a Jacobson-type Einstein branch. What is being tested here is the existence of that scaling regime and its branch conditions, not a fixed-cutoff matrix-algebra identity.

\subsection{What does \emph{not} count as a contradiction of the recovered core}

The following do \emph{not} falsify Theorem~\ref{thm:master} if they fail as stated:
\begin{enumerate}[leftmargin=2em]
\item the uniform $\mathbb Z_6$ center-label ensemble and the associated $\varepsilon=1/6$ flavor ansatz;
\item charged-lepton continuation ans\"atze beyond the exact centered-readback / common-shift frontier, texture exponents, or legacy capacity-level neutrino side estimates;
\item modular-anomaly dark-sector response ans\"atze, including MOND/RAR-style scaling claims;
\item heuristic baryogenesis continuations based on extra suppression-counting assumptions; a baryogenesis theorem requires a concrete out-of-equilibrium mechanism, derived CP-odd source terms, justified defect/sphaleron counting, washout control, and a freeze-out computation of the final asymmetry;
\item strong-CP continuations; the available corpus does not derive the bare QCD angle \(\theta_{\mathrm{QCD}}\), the physical anomaly-invariant combination \(\bar\theta\), or a proof that \(\bar\theta=0\);
\item proton-spin ans\"atze or proton-lifetime estimates beyond the structural exclusion of gauge-mediated decay;
\item discrete-horizon spectroscopy templates, physical black-hole evaporation claims, Page-curve/island closure, or QNM/ringdown predictions;
\item application-level material, topological-phase, plasma, or device claims that require their own
quotient-intrinsic source laws, material actions, repair ledgers, public receipts, and promotion
gates;
\item controlled large-$N_{\mathrm{edge}}$ string/worldsheet effective descriptions.
\end{enumerate}
These are all post-Phase-I, non-core branches. Some are Phase-II implemented estimates or conditional continuation checks, while the rest are Phase-III continuations. None is part of this paper's recovered relativity-plus-Standard-Model core.

\section{Common Objections and Clarifications}

\subsection{\texorpdfstring{Is the use of $P$ circular?}{Is the use of P circular?}}

The pixel area \(P\) is fixed by the outer/inner closure condition in the synthesis paper. That
condition matches the outer pixel detuning to the inner electromagnetic observation scale emitted
by the same cell. Within the printed quantitative implementation, that \(P\) first fixes \(M_U(P)\) and \(E_{\mathrm{cell}}(P)\), then a
one-dimensional pixel-closure solve fixes \(\alpha_U(P)\), equivalently the internal transmutation
data \(t_U(P)\) and \(t_{\mathrm{tr}}(P)\), and only then do \(t_2(P)\), \(t_3(P)\), \(v(P)\), and
the running electroweak outputs appear. Quantities algebraically entangled with that quantitative
branch are on the Phase-II implementation surface: they are forward-emitted there, and
comparison with observation checks that printed implementation instead of enlarging the
recovered-core claim set.

Operationally, changing \(P\) moves the quantitative family
\[
(\alpha_U,\alpha_i(m_Z),a_0,\alpha_{\mathrm{em}}^{-1}(q^2),\sin^2\theta_W(q^2))
\]
through that forward solve. It does not alter the parameter-free structural outputs such as the
gauge quotient or hypercharge lattice. Downstream matter-sector continuations, including
charged-lepton continuation ans\"atze beyond the exact centered-readback / common-shift frontier,
are outside this SM/GR derivation paper's recovered-core theorem package.

\subsection{Does a fixed UV cell size break Lorentz invariance?}

The UV regulator is placed on the screen algebra. The emergent bulk spacetime has no microscopic
bulk lattice in this formulation. Lorentz kinematics arise from the continuum modular action on
caps, summarized in Corollary~\ref{cor:lorentz}.

Spherical geometry is the bridge that makes this possible. A support-visible observer cut is
charted by \(S^2\). Round caps on that chart carry the modular flows used by the BW branch, and
orientation-preserving conformal maps of the same sphere give
\[
\Conf^+(S^2)\cong \mathrm{SO}^+(3,1).
\]
The Lorentz group therefore enters as the symmetry of observer-facing cap geometry. A finite
echosahedral or cellulated carrier sits on the regulator side; the Lorentz claim concerns the
support-visible scaling limit of the spherical cap chart extracted from that carrier.
The observer rest-space chart is
\[
H^3\simeq \mathrm{SO}^+(3,1)/\mathrm{SO}(3),
\qquad
\dim H^3=3,
\]
so the spatial dimension follows from the same Lorentz branch. Finite point-cloud dimension fits belong to separate evidence gates.

This is conceptually similar to other continuum limits in statistical mechanics and lattice field theory. A regulator may break a symmetry at finite cutoff while the infrared fixed point restores it exactly. Here the restoration is stronger than a generic RG expectation because the modular-flow theorem identifies the symmetry group itself:
\[
\Conf^+(S^2)\cong \mathrm{SO}^+(3,1).
\]
Residual Lorentz violation would therefore have to arise from a failure of the support-visible modular-flow theorem. A UV cell size by itself is insufficient.
The UV-side burden on the Lorentz branch is therefore the support-visible scaling theorem on the prime geometric subnet, not the mere existence of a finite cell size.

\subsection{Why use type-I algebras if continuum QFT uses type III?}

Type I is a regulator statement. At every finite cutoff the patch and collar algebras are finite-dimensional matrix algebras, so entropy, recovery maps, and
\[
K=-\log\rho
\]
are literal finite-dimensional objects. The Lorentz branch is \emph{not} a claim that the continuum observer algebra stays in that class. The refinement picture is
\[
\text{finite type-I regulator net}
\;\longrightarrow\;
\text{scaling-limit observer net } \mathcal A_\infty,
\]
and the limit can leave the regulator class. Axiom~\ref{ax:maxent} controls the realized state-side branch across refinement; it does \emph{not} by itself prove that the refinement limit is type I or that the emitted scaling-limit pair lies in the BW / canonical cap phase with standard geometric modular action.

On the geometric-subnet branch of Theorem~\ref{thm:bw}, the scaling-limit cap algebras may be non-type-I and, in the continuum-QFT case of interest, are expected to be type III. Then there is generally no cap density matrix \(\rho_C\in \mathcal A_\infty^{\mathrm{geo}}(C)\) and no bounded operator \(K_C=-\log\rho_C\) inside the limit algebra. The correct continuum object is the modular automorphism group of the pair \((\mathcal A_\infty^{\mathrm{geo}}(C),\omega_\infty^{\mathrm{geo},C})\), which on that branch acts geometrically and typically outerly.

There is therefore no contradiction between using type-I regulators and aiming at a type-III continuum. The finite regulator provides the collar decomposition, recovery control, and carried errors. What the fixed-cutoff MaxEnt package adds is control of the realized state-side branch through one common finite-dimensional multiplier family under refinement. Theorem~\ref{thm:bw} does not require the continuum algebra to be type I and does not require a full-algebra unregularized common spectral floor. It extracts the support-visible prime geometric cap pair, proves the geometric modular automorphism statement on that observer-facing limit, and leaves only the false stronger full-algebra statement unclaimed.

This is analogous to ordinary lattice field theory: one computes at finite regulator in a type-I algebra and then asks which continuum algebraic phase the scaling limit realizes. The additional structural point here is that the realized state-side branch is controlled under refinement. Theorem~\ref{thm:bw} extracts the support-visible cap pair on the prime geometric subnet and proves BW rigidity at automorphism level from the finite cap-normal certificate: regularized modular transport, weak-\(*\)/GNS extraction, support-readable modular covariance, BW framing, held-out oriented cross-ratio rigidity, and independently normalized geometric \(2\pi\)-KMS convergence with wrong-scale controls. Only stronger claims about off-support full-algebra directions, certificate production from bare finite consensus, or unique microscopic phase representatives lie outside that theorem.
\subsection{UV branch and scaling-limit scope}

At fixed cutoff, Axiom~\ref{ax:maxent} yields a quasi-local finite-range interacting branch, and Propositions~\ref{prop:gauge} and \ref{prop:ancillauv} show that the physical normal form is unique only modulo quotient-level OPH-stable equivalence, while the terminal expectation functionals on the declared fixed-point / quotient-local physical algebras are schedule-independent on that carrier even when microscopic representatives differ by gauge labels globally or by sector labels on one regional quotient-local glued state. The invariant fixed by the axiom language is the class \([\mathfrak U]_{\mathrm{OPH}}\) of the physical branch modulo implementation hiding and inert ancillary stabilization, not a unique microscopic representative. The genuinely noncentral topological case is also closed at fixed cutoff by the higher-gauge package of Theorems~\ref{thm:hgdatum}--\ref{thm:hgtransport} and Proposition~\ref{prop:hginteracting}, so the fixed-cutoff topological UV surface is closed on the ordinary, central-defect, and crossed-module branches alike. Beyond fixed cutoff, Theorem~\ref{thm:bw} closes the support-visible continuum modular/geometric lift on the prime geometric subnet. On the bosonic compact-gauge lane, Theorems~\ref{thm:transport-from-gluing} and \ref{thm:fixed-cutoff-bosonic-sector-category} supply the zero-obstruction fixed-stage category and symmetric braiding; the monoidal refinement ladder, compatible forgetful fiber, colimit, and realized cofinal witness additionally require Definition~\ref{def:compact-gauge-refinement-receipt} before Theorems~\ref{thm:refinement-functor-fiber-descent}, \ref{thm:sector-colimit}, and \ref{thm:mar-witness-landing} apply.
The consensus paper also classifies that D1 lane explicitly: on each fixed finite patch net,
the accepted relation induces the quotient maps \(\operatorname{locRep}_\lambda\) and
\(\operatorname{Rep}_\lambda\), normal-form computation is finite-state and decidable with the
Lyapunov step bound, the layered carrier gives the finite \(H_B\wedge H_{\mathrm{fib}}\) witness,
the automatic approximate-stability inputs are the collar-local splice and record controls, and
long-run noisy approximate consensus requires the separate fair-block contraction certificate.
Computational universality for growing patch-net families is an expressive-power question in the
consensus paper, not a premise for the Lorentz, local Einstein, compact-gauge, or realized
Standard Model branches.

\subsection{Why is charge quantization possible without a simple GUT?}

The framework uses the global quotient and anomaly structure instead of a simple-group embedding. Once the realized matter content is fixed, the subgroup acting trivially on all states is exactly $\mathbb Z_6$, and the anomaly equations force the sixth-integer hypercharge lattice. Integer electric charge for color singlets is then a property of the realized quotient structure. A simple unified gauge group is not required.

\section{Discussion}

The framework is strongest where the outputs are discrete or structurally rigid:
\begin{enumerate}[leftmargin=2em]
\item the Lorentz branch on the support-visible extracted prime geometric cap pair;
\item the scaling-limit Einstein branch under the E0 dependency discharge, the derived fixed-cap generalized-entropy stationarity theorem for admissible fixed-cap MaxEnt variations, the null modular bridge, and the bounded-interval kernel;
\item the Standard Model gauge quotient chain on the explicit realized matter package;
\item exact hypercharges and structural electroweak force content on the realized one-generation matter package with one Higgs doublet;
\item the realized color triplet \(N_c=3\) and generation count \(N_g=3\) on the realized MAR-admissible branch;
\item the compact quantitative layer with one certified fixed point of an incomplete local map and
one conditional global-capacity target, kept explicit as a secondary layer outside Phase I.
\end{enumerate}

The local MaxEnt branch gives a finite-range interacting fixed-cutoff dynamics, Propositions~\ref{prop:gauge} and \ref{prop:ancillauv} fix uniqueness of the UV branch only modulo OPH-stable equivalence, and Theorems~\ref{thm:hgdatum}--\ref{thm:hgtransport} with Proposition~\ref{prop:hginteracting} close the genuinely noncentral topological branch at fixed cutoff. The continuum BW/geometric lift is closed in the support-visible sense by Theorem~\ref{thm:bw} once the finite cap-normal certificate is carried. The unregularized full-algebra common-floor route is deliberately not claimed, because Proposition~\ref{prop:commonfloor-collapse} shows that off-support directions can collapse while every finite stage remains faithful and Markov. The observer-facing theorem uses regularized modular transport, weak-\(*\)/GNS extraction of the support-visible prime cap pair, support-readable modular covariance, BW framing, oriented cross-ratio rigidity, and geometric \(2\pi\)-KMS normalization with wrong-scale controls; this is the content needed for the Lorentz, null-stress, and local Einstein branches. Producing that finite cap-normal certificate from bare finite consensus is excluded by the underdetermination no-go of Theorem~\ref{thm:incidence-underdetermination}; on towers carrying the computable incidence/mesh/cross-ratio/normalization receipts it is produced from repair normal forms by Theorem~\ref{thm:certificate-production}. The parent Einstein branch-entry obligation is the production or empirical selection of those receipts, together with the D4-standardness and event-manifold receipt families of \S\ref{subsec:null-net-standardness} and \S\ref{subsec:event-manifold}. With the stress, entropy-bridge, and uniform small-diamond packets of \S\ref{subsec:einstein-branch-closure}, the derivation chain is complete as the composed conditional theorem \ref{thm:einstein-branch-entry-composed}. Realized-branch nonemptiness, a repair tower that carries the finite receipts on its own output, is the branch-entry gate; every structural receipt family carries a realized witness at finite or one-particle level, and the margin-convergence, limit-clause, cap-interior, and physical-receipt obligations are work in progress (Remark~\ref{rem:realized-branch-status}).

\paragraph{Shared excitation dictionary and flavor theorem boundaries.}
The D10 quantitative-closure branch gives integrated gauge-coupling closure on the displayed carrier. The pixel fixed-point equation fixes the arithmetic bridge from \(P\) through \(\alpha_U(P)\), the transmutation data, and the electroweak source anchor. The public Ward-projected Thomson endpoint is downstream of a low-energy transport layer: charged-lepton vacuum polarization is explicit, while the OPH-QCD hadronic precision backend remains a separate source payload. That backend must provide the QCD quotient ensemble, source QCD parameter map, Euclidean slab/vacuum-transfer construction, hadronic Hilbert quotient, Ward-normalized current ledger, two-current spectral export, same-scheme finite remainder, and no-target-leak DAG. Its two-current spectral measure is sufficient only for the running-\(\alpha\)/HVP marginal; HLbL and rare-decay long-distance rows require higher-point and transition spectral data from the same backend. The exact \(W/Z\) running/chart surface is a compare-only sidecar. Its coordinates are noncommensurate with PDG Breit--Wigner and converted complex-pole coordinates until a complete scheme map is supplied. Source spectral measure payloads, same-scheme remainders, and interval certificates document that comparison surface, while empirical hadron closure supplies no promotion of the fine-structure endpoint to a source-only theorem. On the declared runtime surface the running/matching packet is a declared-convention contract with displayed scope; a theorem deriving every coefficient, threshold, and conversion is outside that contract. The separate D6 cosmological-parameter package is a conditional target at the cosmic record-capacity fixed point \(N_{\mathrm{CRC}}=F(N_{\mathrm{CRC}})\); \(F\), its fixed-point certificate, and CP-1--CP-3 remain open. On the flavor side the manuscript treats one shared OPH excitation dictionary as the only proof-facing family datum; lane-specific integers are not introduced independently. For each realized same-label refinement arrow \(e\) on the three-generation bundle, let \(\omega_e\) be the same-label overlap holonomy scalar, let
\[
d_e:=1-\omega_e
\]
be the derived edge defect, let \(g_e\) be the same-label gap scalar, and define
\[
q_e:=\sqrt{g_e d_e},
\qquad
\eta_e:=\log q_e-\frac13\sum_f \log q_f,
\qquad
\mu_e:=\frac{e^{\eta_e}}{\frac13\sum_f e^{\eta_f}}.
\]
These are the common descendants of overlap holonomy and edge-defect data. They exist once the same-label gap and overlap witnesses are fixed, and they are the shared family-side input used by the charged, quark, and neutrino continuations.

To include the charge-side bookkeeping explicitly, let \(s_e\) denote the realized sector-charge step carried by the same-label arrow \(e\). For any lane-specific readout \(\gamma\) on the realized same-label transport graph, let
\[
m_{\gamma,e}\in\mathbb Z_{\ge 0}
\]
be the multiplicity with which \(\gamma\) traverses the elementary same-label excitation arrow \(e\). Equivalently, along the realized transport path one has
\[
s_\gamma=\sum_e m_{\gamma,e}s_e.
\]
The associated excitation weight and excitation action are
\[
A_\gamma
:=
-\sum_e m_{\gamma,e}\log q_e
=
-\log\!\Bigl(\prod_e q_e^{\,m_{\gamma,e}}\Bigr),
\qquad
Y_\gamma^{\mathrm{exc}}
:=
\prod_e q_e^{\,m_{\gamma,e}}.
\]
So overlap holonomy, edge defects, gap data, and sector-charge transport determine the suppression law before any base choice is made. What earlier D12 language called a ``texture exponent'' or ``defect count'' is therefore not an extra primitive beyond the structural branch. The primitive flavor-side integers are the transport multiplicities \(m_{\gamma,e}\). A one-number exponent in ``units of \(\log 6\)'' is only the compressed summary
\[
n_\gamma^{(6)}:=A_\gamma/\log 6,
\]
and it becomes a literal defect count only after the additional uniform sixfold center-label collapse compatible with the realized
\[
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6}
\]
quotient. Without that extra collapse, this layer contains the multiplicity vector
\(m_{\gamma,\bullet}\) and the excitation action \(A_\gamma\). A standalone flavor
integer belongs only to the extra collapse.

The imported realized-branch input here is the D9 result that the same realized branch carries the color triplet \(N_c=3\) and the generation count \(N_g=3\).
This shared dictionary feeds the downstream particle continuations. Their lane-specific theorem
objects, exact witnesses, and quantitative closures are developed in
Ref.~\cite{ophparticles}. On the compact-paper surface, the dictionary serves as the common
family-side input beneath those continuations. Old base-6 exponents are compare-only
compressions of excitation action and have no role as primitive flavor data.

\paragraph{Non-hadron output lane.}
For reader-facing outputs, the non-hadron surface is explicit and lane-split. The gauge and
gravity chains fix connection and metric carrier roles. Under the additional action/background
hypotheses of Theorem~\ref{thm:carrier-mode-gates}, their reduced quadratic kernels have
\[
K_X^{\mathrm{phys}}
=Z_X\bigl(\omega^2-c_\star^2|\mathbf k|^2\bigr)\Pi_X,
\]
which is a classical or perturbative mode receipt rather than a zero-GeV particle-mass output.
No photon, gluon, or graviton mass row is promoted until the quantum-particle receipt of
Definition~\ref{def:carrier-particle-receipts} passes. The electroweak quantitative-closure chain
\[
\text{Axioms }1\text{--}5 \longrightarrow D7\text{--}D10
\]
has an archived conditional value-law sidecar
\[
(M_W,M_Z)=
(80.37700001539531,\ 91.18797807794321)\,\mathrm{GeV}
\]
on the conditional value-law surface.  The separate target-frozen inverse adapter is
\((80.3625,91.1879)\,\mathrm{GeV}\); the older rounded boundary aliases are not that
adapter.  Both pairs are compare-only beneath the source spectral measure payload,
same-scheme remainder, and interval certificate. The D11 Higgs/top formulas close a conditional downstream split calculation on the declared D10/D11 quantitative surface; they do not promote a full source-only pole mass.  Write the repair-chart coupling ratio as
\[
\rho_{\mathrm{EW}}:=\frac{\alpha_2-\alpha_Y}{\alpha_2+\alpha_Y},
\]
to distinguish it from the transmutation multiplicity
\(b_{\mathrm{tr}}=N_c+1=4\).  On the archived candidate D10 repair tuple \((\eta_{\mathrm{source}},\rho_{\mathrm{EW}},\lambda_{EW},\tau_{2,\mathrm{tree}}^{\mathrm{exact}},\delta n_{\mathrm{tree}}^{\mathrm{exact}})\), define
\[
\rho_{HT}=\log\!\bigl(1+\tau_{2,\mathrm{tree}}^{\mathrm{exact}}\bigr),
\]
\[
R_T=
-\tau_{2,\mathrm{tree}}^{\mathrm{exact}}\eta_{\mathrm{source}}^2
+\Bigl(1+\frac{\rho_{\mathrm{EW}}}{28}\Bigr)\eta_{\mathrm{source}}^6
+\frac{\eta_{\mathrm{source}}^8}{14}
+\frac{\eta_{\mathrm{source}}^9}{27},
\]
\[
R_H=
\eta_{\mathrm{source}}^5
-\frac{3}{25}\eta_{\mathrm{source}}^6
+\frac{\lambda_{EW}\eta_{\mathrm{source}}^6}{18}
+\frac{\eta_{\mathrm{source}}^8}{2\rho_{\mathrm{EW}}}.
\]
Then the forward split coordinates are
\[
\pi_y=
\frac{\eta_{\mathrm{source}}+\left(\frac32+\frac{\rho_{\mathrm{EW}}}4\right)\rho_{HT}+R_T}{\sqrt{\pi}},
\qquad
\pi_\lambda=
\frac{\eta_{\mathrm{source}}-\left(\frac43-\frac{\rho_{\mathrm{EW}}}{54}\right)\rho_{HT}+R_H}{\sqrt{\pi}},
\]
and the declared D11 Jacobian reads out
\[
\delta y_t(\mu_t)=\pi_y\,y_t^{\mathrm{core}}(\mu_t),
\qquad
\delta\lambda(\mu_t)=-\frac{16}{9}\pi_\lambda\,\lambda^{\mathrm{core}}(\mu_t).
\]
On that same declared surface,
\[
m_H=125.1995304097179~\mathrm{GeV},
\qquad
m_t^{D11}=172.3523553288312~\mathrm{GeV}.
\]
These are back-solved from the measured pair through the synchronization-scale
scan, so the row is a target-anchored fit rather than a prediction: it lands on
the 2025 PDG Higgs average by construction. The target-free headline for this
pair is the double-criticality family, whose frozen boundary-scale candidate
gives \((m_H,m_t)=(125.77,\,172.63)~\mathrm{GeV}\) at two loops with
\(m_H=125.72~\mathrm{GeV}\) on the fit-free curve at the measured top. The
same surface emits a companion top coordinate. It is not a separate public quark-mass row. The
quark target audit uses a distinct PDG 2025 cross-section extraction coordinate. The bridge to the auxiliary
direct-top PDG row is closed as a corpus-limited codomain no-go; the auxiliary row is compare-only.
A source-side extraction-response kernel is outside the emitted corpus.
The one-scalar companion seed
\[
\sigma_{D11,\mathrm{HT}}=\frac{\alpha_U\cos(2\theta_{W0})}{\sqrt{\pi}}
\]
is on disk only as the lower-rank fixed-ray companion branch with \(\pi_y=\pi_\lambda=\sigma_{D11,\mathrm{HT}}\). The exact inverse slice on the same D11 Jacobian is compare-only and does not define the conditional forward surface.
The same D11 Jacobian also has a compare-only exact inverse slice at the canonical Higgs/top reference pair
\[
(m_H,m_t)=
(125.1995304097179,\ 172.3523553288312)\,\mathrm{GeV}.
\]
Detailed particle-spectrum continuation statements are carried by Ref.~\cite{ophparticles}. That companion paper develops the quark source-spread non-identifiability theorem and target-audit boundary, the charged-lepton determinant-line boundary, a target-informed weighted-cycle neutrino comparison candidate, the \(H^3\) record-worldline stitch certificate for localized observer-visible record tokens, and the hadron execution boundary. Within the restricted quark-shape family used by the older audit, the compatible ordered spread data form a two-parameter positive fiber with a free \((\mathbb R_{>0})^2\) rescaling action. This is a valid non-identifiability lower bound, not the generic physical interface. A common-scale comparison instead uses six dimensionless Yukawa coordinates, one mean and two centered coordinates in each sector. At \(M_Z\), the audit gives \(\rho_u=1.1108888543\) and \(\rho_d=0.7519410008\), so the reciprocal-ray condition fails with product \(0.8353228768\). Even after four endpoint Yukawas are supplied, the best reciprocal shape misses the held-out charm and strange values by \(21.556\%\); the failure persists across the tested scales through \(10^{16}\,\mathrm{GeV}\), with held-out errors from \(19.93\%\) to \(21.56\%\). The generic interface is \((\mu_u,\sigma_u,\rho_u,\mu_d,\sigma_d,\rho_d)\). Generation-blind flavor-singlet source scalars also cannot select a nonzero fixed bifundamental Yukawa representative. A source-derived flavor-orbit selector and a physical quark--Higgs carrier are missing, and numeric quark rows remain outside the source-only prediction surface. The stored dimensionful quark matrices are mass-texture audit witnesses; a physical Yukawa claim additionally requires one common renormalization scale, threshold transport, the running Higgs expectation value, and dimensionless normalization. The neutrino candidate descends from a hand-written flavor template and fails the NuFIT 6.1 correlated \((\sin^2\theta_{23},\delta_{\mathrm{CP}})\) profile~\cite{nufit61}; it has no theorem or prediction status. The \(H^3\) stitch certificate is conditional on a declared hyperboloid atlas, common clock line, real transverse interface, sector/gauge transport, ID-independent assignment gap, and refinement contraction check; it is not a species, mass, charge, or scattering-amplitude derivation. The hadron backend is a source-backend boundary with empirical closure policy documented. The compact paper promotes no source-only hadron masses. Empirical hadron closure values use a separate \(e^+e^-\to\mathrm{hadrons}\) payload class. These particle-continuation statements do not belong to the compact-paper claim surface.

An earlier formula-discovery audit evaluates a frozen two-mode quark ansatz and, after interpreting a
dimensionless template coordinate as one GeV, reproduces the six mixed-convention comparison
coordinates with a maximum central-value residual of \(0.2946\%\).  This does not alter the
preceding theorem boundary.  The formulas were designed with knowledge of the comparison
spectrum; five load-bearing flavor inputs descend from the repository's explicitly hand-written
family-transport template; the selected \(P\) branch has an internal Stage-5 quark-model ancestor;
and no dimensionful normalization, common-scale Yukawa packet, or RG/threshold transport is
emitted.  The exact content that survives the audit is narrower: the transposition Cayley graph of
\(S_3\) has Laplacian spectrum \(0,3,6\) with multiplicities \(1,4,1\), so its heat-gap ratio is
\(e^{-3\tau}\) once a heat time is supplied; and
\(L=\operatorname{ctr}(-1,x,1)\), \(Q=\operatorname{ctr}(1,x^2,1)\) span the centered
three-vector plane for \(x\ne\pm1\).  A normalized unitary-conjugation-invariant linear response
has rank-one weight \(1/d\), and a fully left-right-isotropic \(d\times d\) matrix width has slot
weight \(1/d^2\).  The proposed \(1/25,1/2,1/5,1/10,1/4\) arithmetic therefore follows only after
the \(5\times5\) heat register, the modules of dimensions \(2,5,10,4\), their signs, and their
physical response laws are assumed; OPH has not selected those channels or excluded competitors.
None of these identities attaches a physical family carrier, heat time, mass unit, or Yukawa
trajectory.  The numerical table is therefore retained only as a
post-hoc, target-informed template-ansatz diagnostic, not as a source-only postdiction, prediction,
or theorem; public numeric quark rows remain withheld.

A subsequent Representation-Slot Cumulant Closure (RSCC) proposal removes the five legacy
template decimals from the \emph{leaf} evaluator.  It declares
\(F=\mathbf 1\oplus2V_{\mathrm{std}}\), hence \(\dim F=5\) and
\(\dim F_0=4\), and builds a response ledger with composite dimensions
\((29,432,22,32,840,1008,432,1584)\).  Rank-over-dimension arithmetic and the
Gaussian identity
\(\frac12(2w^2r/d)=w^2r/d\) are exact after that ledger, a continuous Gaussian
support, isotropic covariance, ranks, and signs are assumed.  They do not select the ledger.
\(S_3\)-invariance alone leaves a five-dimensional commutant on
\(\mathbf 1\oplus2V_{\mathrm{std}}\), the proposed \(F\) has no sign-sector heat mode at
eigenvalue \(6\), and the existing invariant \(24\)-slot register theorem supplies only a common
count, not a family non-singlet.  Full unitary isotropy across heterogeneous direct-sum blocks,
two-cumulant truncation, orientation independence, the negative covariance signs, and the physical
regular-heat-to-\(F\) attachment are therefore additional premises.

Conditional on those premises and the inherited ray, even-response, affine-mean, and charged-scale
laws, RSCC deterministically emits dimensionless coordinates.  Combining them with the D10
\(v\) display gives a \(0.29436\%\) maximum residual against the same mixed-convention table.  This
agreement is retrospective: the chosen ledger dimensions closely rationalize the visible
effective coordinates, the \(P\) witness retains internal Stage-5 quark ancestry, and the D10 scale
comes from a nonmatching candidate branch.  Moreover, deleting every RSCC \(w^2\) correction and
the whole \(\delta_g\) correction improves the same retrospective maximum residual to
\(0.21423\%\); the detailed covariance ledger is not selected by that comparison.  RSCC is thus a
quarantined retrospective formula specification, not a physical flavor closure.  It
discharges none of the source-root, carrier/refinement, channel-functor, affine-law, physical-readout,
or RG/scheme receipts.

The further-theorem audit corrects one premise and makes the strongest conditional statement
precise.  On a finite source spectrum, MaxEnt with fixed mean and covariance is an
exponential-quadratic Gibbs law, not a Gaussian density.  On support
({-2,-1,0,1,2}), the probability vectors
((1/12,1/6,1/2,1/6,1/12)) and
((1/16,1/4,3/8,1/4,1/16)) both have mean zero and variance one but fourth cumulants
zero and (-1/2), respectively.  Thus finite MaxEnt and the first two moments cannot justify
RSCC's two-cumulant truncation.  A genuine repair would require either an exported refinement
array with Lindeberg/mixing and covariance-convergence control, or an exact primitive-path closure.

The proposed Quark Flavor Register Closure (QFRC) supplies the latter only as a
\emph{conditional certificate schema}.  Given QF1--QF9, which explicitly declare the typed
registers, all primitive paths, ranks, multiplicities, signs, winding character, path exhaustion,
refinement naturality, and a positive-gap selector, normalized trace forces the displayed RSCC
rank-over-dimension coefficients, with no continuous projector-amplitude deformation.  This is
exact conditional rigidity, not derivation of QF1--QF9.  Neutral-register countermodels show why
the broad structural signature cannot choose the ledger, and the carrier exports no
physical QFRC certificate.  The accompanying equivariant-selector, absolute-scale, scheme, and RG
results likewise sharpen the obstruction or prove well-posedness after their inputs are supplied;
they do not supply those inputs.  Consequently every F1--F6 receipt remains open and numerical
quark rows remain withheld.

A targeted simulator assay tests the separate Primitive Oriented Family Transport (POFT) proposal
without fitting a feature map.  The predeclared observable is the edge average of the natural
three-label permutation representation carried by each saved $S_3$ gauge edge.  In one fresh
$4{,}096$-patch BW run and three archived $4{,}096/65{,}536$-patch carriers, totaling
$830{,}066$ edges, the normalized singular triples are
$(1,0.00522,0.00134)$, $(1,0.00552,0.00361)$,
$(1,0.00179,0.00002)$, and $(1,0.00071,0.00028)$.
They are compatible with the Haar-equilibrated rank-one operator, whereas POFT requires
approximately $(1,0.5515,0.2552)$ for $T_0$ and
$(1,0.5462,0.2745)$ for $T_1$; every maximum singular-ratio distance exceeds $0.5407$.
The saved carrier also exports neither a complex oriented family amplitude nor an explicit
coarse-to-fine edge intertwiner.  Thus the direct $S_3$ edge carrier does not emit POFT's
$T_0,T_1$.  A source-derived complex lift would define a different carrier. Defining that lift by
the requirement that it reproduce POFT would be circular.

The obstruction persists at the axiom level without adding any premise.  MAR orders admissible
packages by \(C(\mathfrak S)=(\chi_{\mathrm{cpl}},N_{\mathrm{nonab}},N_c,N_g)\); Yukawa
eigenvalues are not entries of this order.  Starting from any generic admissible pair, independent
positive rescalings of the centered up/down log spectra preserve the gauge representations,
anomalies, hypercharges, Higgs content, generation count, CKM frames, CP capability, and MAR score,
while changing the quark masses.  The resulting packages are physically inequivalent because the
physical-equivalence relation preserves Yukawa invariants.  Hence Axioms 1--5 and fixed \(P\) admit
a continuous family of equal-MAR-score quark spectra.  Interpreting ``minimal'' as the smallest
positive Yukawa does not repair the problem: the positive family has infimum zero and no positive
minimum (and admitting zero selects massless/degenerate quarks).  A unique numerical spectrum
therefore cannot be obtained from the stated MAR definition.  Any future flavor-closure functional
must at least be nonconstant on this independent up/down spread-rescaling orbit; a sufficient
source-carrier, response, scale, and RG contract may enforce that condition, but no such contract
is physically instantiated by the repository.  RSCC records one retrospective
formula-level specification for parts of that contract; every physical receipt remains open.

\paragraph{Local unification surface and exact-release frontier.}
The local quantitative bridge can be stated without inflating the recovered-core claim. On the
bosonic side, the declared pixel input \(P\) fixes the D10/D11 trunk
\[
P\longmapsto \alpha_U(P) \longmapsto \bigl(t_U(P),t_{\mathrm{tr}}(P)\bigr)\longmapsto v(P),
\]
after which the archived D10 value law supplies a candidate electroweak transport
package and the D11 formulas supply a conditional downstream split map with
\[
\rho_{HT}=\log\!\bigl(1+\tau_{2,\mathrm{tree}}^{\mathrm{exact}}\bigr),
\qquad
(\pi_y,\pi_\lambda)\longmapsto (m_t,m_H)
\]
by the declared D11 Jacobian, with no inverse readback in the executable forward
map.  This runtime property does not prove the quotient-path certificate or
erase historical branch-selection exposure. The D10/P/fine-structure chain is
the declared arithmetic bridge on this quantitative surface. The electroweak
\(W/Z\) and running-family rows carry separate public comparison artifacts:
the source spectral measure payload, same-scheme remainder, and interval
certificate. A full scheme map is required before the \(W/Z\) coordinates can be compared as PDG
Breit--Wigner or converted complex-pole observables. The same D11 Jacobian emits its conditional
Higgs/top coordinate.
On the gravity side, the same D10 pixel law packages the shared edge entropy,
\[
\ellbar_{\mathrm{SU(2)}}(t_{2,\mathrm{run}})
\;+\;
\ellbar_{\mathrm{SU(3)}}(t_{3,\mathrm{run}})
=
P/4.
\]
Together with \(a_{\mathrm{cell}}=P\ell_\star^2\), the Newton area-law dictionary gives
\(G_{\mathrm{geom}}=\ell_\star^2\); the pixel \(P\) cancels.
The complete bosonic release burden includes a strict source root, a
source-derived D10 quotient-path certificate, an independently source-closed
physical \(E_\star\), a frozen and certified
RG/threshold/matching/scheme packet, complex-pole and uncertainty receipts,
branch rigidity, and a hash-bound no-target dependency DAG.  The familiar-unit
readout is part of this burden: a dimensionless hierarchy ratio cannot become a
GeV pole mass until the physical scale is independently closed.  On the
gravity side,
Proposition~\ref{prop:sharededgeentropy} gives
\[
\ellbar_{\mathrm{shared}}
=
\ellbar_{\mathrm{SU(2)}}(t_{2,\mathrm{run}})
\;+\;
\ellbar_{\mathrm{SU(3)}}(t_{3,\mathrm{run}})
=
P/4,
\]
and Proposition~\ref{prop:gsi} gives the local SI readout
\[
G_{\mathrm{SI}}=\frac{c^3\ell_\star^2}{\hbar}
\]
from the selected scale certificate.
The same proposition fixes the full familiar-unit package:
\[
L_{\mathrm{loc}}=\sqrt{a_{\mathrm{cell}}}\,\widehat L(P),\qquad
t_{\mathrm{loc}}=\frac{\sqrt{a_{\mathrm{cell}}}}{c_\star}\,\widehat T(P),
\]
\[
E_{\mathrm{loc}}=\frac{\hbar c_\star}{\sqrt{a_{\mathrm{cell}}}}\,\widehat E(P),\qquad
\Theta_{\mathrm{loc}}=\frac{\hbar c_\star}{k_B\sqrt{a_{\mathrm{cell}}}}\,\widehat\Theta(P),
\]
with dimensionless \(\widehat L,\widehat T,\widehat E,\widehat\Theta\). Meters and seconds are
therefore read from the single local ruler \(\sqrt{a_{\mathrm{cell}}}\) together with the
structural Lorentz output \(c_\star\), while GeV and Kelvin are downstream familiar-unit displays of the
inverse local ruler through \(\hbar\) and \(k_B\).
On that declared extension surface the local display values are
\[
\begin{aligned}
c&=299792458\,\mathrm{m/s},\\
G&=6.674299995910528\times10^{-11}\,\mathrm{m^3\,kg^{-1}\,s^{-2}},
\end{aligned}
\]
\[
(M_W,M_Z)_{\rm conditional}=
(80.37700001539531,\ 91.18797807794321)\,\mathrm{GeV},
\qquad
M_H^{\rm conditional}=125.1995304097179\,\mathrm{GeV},
\]
with the separate target-frozen inverse adapter
\[
(M_W,M_Z)_{\rm inverse\ adapter}=(80.3625,\ 91.1879)\,\mathrm{GeV}.
\]
The structural result is the common invariant null cone and speed \(c_\star\). The displayed
decimal \(c=299792458\,\mathrm{m/s}\) is exact by the SI definition of the metre and is therefore
a unit convention, not a predicted magnitude. The
displayed \(G\) row is emitted by the selected scale certificate instead of by
back-solving \(a_{\mathrm{cell}}/P\) against the rounded benchmark \(6.6743\times10^{-11}\). The
same certificate turns the dimensionless \(\Lambda_{\mathrm{CRC}}\ell_\star^2\)
capacity relation into an SI static-patch display.
These boson coordinates comprise separate conditional and comparison rows. The first \(W/Z\)
pair is a running/chart value-law candidate, the second is an inverse comparison
adapter, and the Higgs entry is a conditional D11 coordinate on the declared
surface. The \(W/Z\) rows are noncommensurate with PDG Breit--Wigner and converted complex-pole
coordinates until the full scheme map is supplied. Theorem~\ref{thm:conditional-boson-pole-completion}
states the additional conditions required for a physical pole-mass triple.

Particle-spectrum continuation boundaries beyond the compact SM/GR ledger are stated in Ref.~\cite{ophparticles}.

The paper does not claim complete closure of all low-energy observables.\footnote{Questions outside this theorem package do not alter the specific claim set established here. Even a separate habitat theorem for OPH state-and-law data would not enlarge this SM/GR derivation paper's Phase-I scope unless the actual closure map, invariant admissible sector, and stability hypotheses were also proved at the same tier.}
\section{Finite Quotient Ensembles and Simulation Claim Tiers}

\input{tex_fragments/FINITE_QUOTIENT_ENSEMBLE_THEOREMS.tex}

\section{Conclusion}

Observer-Patch Holography starts from overlap consistency of observer patches and yields, within one framework, several effective structures usually treated separately in modern fundamental physics. This SM/GR derivation paper supports a unique schedule-independent quotient normal form for overlap repair from each fixed initial physical quotient state, with same-boundary uniqueness only under the additional unique-extension condition, and hence a quotient-level physical UV branch only modulo boundary redundancy, implementation hiding, and inert ancillary stabilization. It also supports a Lorentz branch on the extracted prime geometric cap pair and a Jacobson-type Einstein branch whose OPH5 recovered-core dependencies are discharged by Theorem~\ref{thm:einstein-bridge-discharge}. The D6 extension is a conditional global-closure target for that gravity lane; \(F\), its fixed-point certificate, CP-1--CP-3, and the capacity-to-de Sitter identification remain open. The recovered core also supports the Standard Model gauge quotient with exact hypercharges and structural electroweak force content on the realized matter package on the realized MAR one-Higgs branch in the bosonic internal-gauge sector, plus the realized color triplet \(N_c=3\) and generation count \(N_g=3\) on that branch. After an independently supplied Maxwell action, the electromagnetic connection branch gives Maxwell's equations and two classical transverse modes; a photon particle remains conditional on the quantum receipt. The paper also gives a conditional support-visible compact-gauge Yang--Mills form together with repair-gap accounting of the Yang--Mills mass gap under the separately named finite and continuum receipts, and a separate integrated quantitative-closure branch. Phenomenological continuations are discussed separately from the recovered core.

The epistemic position of the recovered core arrives with its receipts. The construction carries zero continuous dials; each declared pixel map has a machine-certified interval proof of exactly one fixed point on its stated numerical domain; the program's formalized subset comprises 111 sorry-free Lean theorems covering the consensus core and the capacity-coupling algebra; a standing falsification program holds frozen, externally timestamped targets with a permanent executed record; and a hostile forty-two-finding adversarial third-party audit reproduced the certified interval arithmetic and identified no false theorem in the recovered mathematical core, with the two implementation defects it exposed repaired behind fail-closed gates.

The framework therefore presents general relativity and the Standard Model as effective descriptions arising from the five-axiom basis together with the support-visible BW scaling theorem, geometric-subnet construction, and categorical gauge reconstruction. The local quantitative claim surface is equally explicit: the named pixel branches organize the dimensionless electroweak hierarchy and the candidate D10/D11 mass charts, while the shared cell/edge identity enters the Newton area law.  The archived D10 value law is an exact implication of the quotient-path certificate in Definition~\ref{def:d10-quotient-path-certificate}; deriving that certificate from the finite carrier remains open.  The selected no-\(G\) scale certificate controls the conditional classical-regime gravity normalization through \(\ell_\star^2=3\pi/B_\star\), the invariant causal speed \(c_\star\) is the structural Lorentz output, and the familiar-unit package reads meters, seconds, GeV, and Kelvin from the single local ruler \(\sqrt{a_{\mathrm{cell}}}=\sqrt{P}\,\ell_\star\) with \(\hbar\) and \(k_B\) used only as display conventions. The exact SI coordinate \(c=299792458\,\mathrm{m/s}\) remains a unit convention, not a predicted decimal. No \(W/Z/H\) complex-pole triple is promoted by this compact paper. Separate continuation boundaries concern sharper quantitative control, a fuller fermionic gauge branch, and theorem-side local exact-release objects beyond the corpus-backed surfaces stated here.

\appendix
\input{tex_fragments/COMPACT_TECHNICAL_SUPPLEMENT_PORT.tex}

\begin{thebibliography}{99}
\bibitem{observableNormalForms}
B.~M\"uller, D.~Matscheko, and J.~Hill,
\emph{Observation-Determined Normal Forms: Stability, Obstructions, and Refinement in Constraint and Rewrite Systems},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/observable_normal_forms.pdf}.

\bibitem{ophsynthesis}
B.~M\"uller, A.~Osika, M.~Poneder, K.~Xue, B.~Cassie, P.~Nguyen, M.~A.~Visser, K.~A.~Anirudha, D.~Matscheko, and J.~Hill,
\emph{Observers Are All You Need},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/observers_are_all_you_need.pdf}.

\bibitem{ophconsensus}
B.~M\"uller, K.~Xue, K.~A.~Anirudha, D.~Matscheko, and J.~Hill,
\emph{Reality as a Consensus Protocol: The Fixed-Point Computation That Implements Physics},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/reality_as_consensus_protocol.pdf}.

\bibitem{ophparticles}
B.~M\"uller, A.~Osika, M.~Poneder, K.~Xue, M.~A.~Visser, and D.~Matscheko,
\emph{Deriving the Particle Zoo from Observer Consistency},
2026.
Available at \url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/deriving_the_particle_zoo_from_observer_consistency.pdf}.

\bibitem{matschekoProofChain}
D.~Matscheko,
\emph{OPHProofChain Lean 4 Audit},
GitHub repository directory, 2026.
Available at \url{https://github.com/dmatscheko/chi_nu_test/tree/main/proof_chain/}.

\bibitem{dula2025}
DULA - GR OK 4,
\emph{The DULA Theorem: Graded Monoid Homomorphisms for Prime Congruences},
September 19, 2025.
Available at \url{https://fermatslibrary.com/p/74724608}.

\bibitem{nufit61}
I.~Esteban, M.~C.~Gonzalez-Garcia, M.~Maltoni, I.~Martinez-Soler, J.~P.~Pinheiro, and T.~Schwetz,
\emph{NuFit-6.0: Updated global analysis of three-flavor neutrino oscillations},
JHEP \textbf{12} (2024) 216, arXiv:2410.05380,
with the NuFIT 6.1 (2025) profile-table release at \url{https://www.nu-fit.org/?q=node/309}.

\input{tex_fragments/FOUNDATIONAL_REFERENCES.tex}
\end{thebibliography}

\end{document}
